### 2018-03-22 paper/jcgs-template/jcgs-template.tex
initial commit with draft, code, and GiR experiments

%&latex
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\begin{document}

%\bibliographystyle{natbib}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Title}
  \author{Author 1\thanks{
    The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
    Department of YYY, University of XXX\\
    and \\
    Author 2 \\
    Department of ZZZ, University of WWW}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Title}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
The text of your abstract.  200 or fewer words.
\end{abstract}

\noindent%
{\it Keywords:}  3 to 6 keywords, that do not appear in the title
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
\label{sec:intro}

Body of paper.  Margins in this document are roughly 0.75 inches all
around, letter size paper.

\begin{figure}
\begin{center}
\includegraphics[width=3 in]{fig1.pdf}
\end{center}
\caption{Consistency comparison in fitting surrogate model in the tidal
power example. \label{fig:first}}
\end{figure}

\begin{table}
\caption{D-optimality values for design $X$ under five different scenarios.  \label{tab:tabone}}
\begin{center}
\begin{tabular}{rrrrr}
one & two & three & four & five\\\hline
1.23 & 3.45 & 5.00 & 1.21 & 3.41 \\
1.23 & 3.45 & 5.00 & 1.21 & 3.42 \\
1.23 & 3.45 & 5.00 & 1.21 & 3.43 \\
\end{tabular}
\end{center}
\end{table}

\begin{itemize}
\item Note that figures and tables (such as Figure~\ref{fig:first} and
Table~\ref{tab:tabone}) should appear in the paper, not at the end or
in separate files.
\item In the latex source, near the top of the file the command
\verb+\newcommand{\blind}{1}+ can be used to hide the authors and
acknowledgements, producing the required blinded version.
\item Remember that in the blind version, you should not identify authors
indirectly in the text.  That is, don't say ``In Smith et. al.  (2009) we
showed that ...''.  Instead, say ``Smith et. al. (2009) showed that ...''.
\item These points are only intended to remind you of some requirements.
Please refer to the instructions for authors
at \url{http://amstat.tandfonline.com/action/authorSubmission?journalCode=ubes20&page=instructions#}
\item For more about ASA\ style, please see \url{http://journals.taylorandfrancis.com/amstat/asa-style-guide/}
\item If you have supplementary material (e.g., software, data, technical
proofs), identify them in the section below.  In early stages of the
submission process, you may be unsure what to include as supplementary
material.  Don't worry---this is something that can be worked out at later stages.
\end{itemize}

\section{Methods}
\label{sec:meth}
Don't take any of these section titles seriously.  They're just for
illustration.

\section{Verifications}
\label{sec:verify}
This section will be just long enough to illustrate what a full page of
text looks like, for margins and spacing.

\cite{Campbell02}, \cite{Schubert13}, \cite{Chi81}

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
{\bf With this spacing we have 30 lines per page.}
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

\section{Conclusion}
\label{sec:conc}

\bigskip
\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

\begin{description}

\item[Title:] Brief description. (file type)

\item[R-package for  MYNEW routine:] R-package ÒMYNEWÓ containing code to perform the diagnostic methods described in the article. The package also contains all datasets used as examples in the article. (GNU zipped tar file)

\item[HIV data set:] Data set used in the illustration of MYNEW method in Section~ 3.2. (.txt file)

\end{description}

\section{BibTeX}

We hope you've chosen to use BibTeX!\ If you have, please feel free to use the package natbib with any bibliography style you're comfortable with. The .bst file Chicago was used here, and agsm.bst has been included here for your convenience.

\bibliographystyle{Chicago}

\bibliography{Bibliography-MM-MC}
\end{document}

### 2018-03-22 paper/paper.tex
initial commit with draft, code, and GiR experiments

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL 
\usepackage[algo2e]{algorithm2e}
\usepackage{algorithmic}  
\usepackage{algorithm}
\usepackage[toc,page]{appendix}
%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\begin{document}
\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf A Continuous-time Multicast Network Model}
  \author{Bomin Kim\thanks{
    The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
    Department of Statistics, Pennsylvania State University,\\
  Aaron Schein\\
  College of Information and Computer Sciences, UMass Amherst,\\
    Bruce Desmarais\\
    Department of Political Science, Pennsylvania State University,\\
    and\\
    Hanna Wallach\\
    Microsoft Research NYC}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf A Continuous-time Multicast Network Model}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
We introduce the continuous-time multicast network model---a generative model for directed edges with multiple recipients or multiple senders. To define the model, we
integrate a dynamic version of the exponential random graph model (ERGM) and generalized linear model approach to understand who communicates with whom, and when. We use
the model to analyze emails sent between department managers in Montgomery county government in North Carolina, and international sanctions data concerning the threats and use of economic sanctions by states. Our applications demonstrate that the model is effective at predicting and explaining continuous-time networks involving edges with multiple recipients or senders.
	\end{abstract}

\noindent%
{\it Keywords:}  3 to 6 keywords, that do not appear in the title
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}\label{sec:intro}
\section{A Continuous-time Multicast Network Model}\label{sec:generative process}
Data generated under the model consists of $D$ unique edges. A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of recipients $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$. For simplicity, we assume that edges are ordered by time such that $t_d < t_{d+1}$.
\subsection{Tie Generating Process}\label{subsec: Tie}
For every possible author--recipient pair $(a,r)_{a \neq r}$, we define the ``recipient intensity", which is the likelihood of edge $d$ being sent from $a$ to $r$:
\begin{equation}
\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr},
\end{equation}
where $\boldsymbol{b}$ is $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of network features which vary depending on the hypotheses regarding canonical processes relevant to network theory such as popularity, reciprocity, and transitivity. We place a Normal prior $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$.

Next, we hypothesize ``If $a$ were the sender of edge $d$, who would be the recipient(s)?" To do this, we draw each sender's set of recipients from a non-empty Gibbs measure \cite{fellows2017removing}---a probability measure we defined in order to 1) allow multiple recipients or ``multicast", 2) prevent from obtaining zero recipient, and 3) ensure tractable normalizing constant. Because we allows multicast, we draw a binary (0/1) vector $\boldsymbol{u}_{ad}= (u_{ad1},
\ldots, u_{adA})$
\begin{equation} \boldsymbol{u}_{ad}  \sim
\mbox{Gibbs}(\delta, \boldsymbol{\lambda}_{ad}),
\end{equation}
where $\delta$ is a real number controlling the average number of recipients and $\boldsymbol{\lambda}_{id}= \{\lambda_{adr}\}_{r=1}^A$. We place a Normal prior $\delta \sim N(\mu_\delta,\sigma^2_\delta)$. In particular, we define $\mbox{Gibbs}(\delta, \boldsymbol{\lambda}_{ad})$ as
\begin{equation}
\begin{aligned}
&p(\boldsymbol{u}_{ad}|\delta, \boldsymbol{\lambda}_{ad}) = \frac{\exp\Big\{\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0 )\big) + \sum_{r\neq a} (\delta+\lambda_{adr})u_{adr}\Big\}}{Z(\delta,\boldsymbol{\lambda}_{ad})} ,
\end{aligned}
\label{eqn:Gibbs}
\end{equation}
where $Z(\delta,\boldsymbol{\lambda}_{ad})= \prod_{r \neq a} (\mbox{exp}\{\delta+\lambda_{adr}\} + 1)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm. We provide the derivation of the normalizing constant as a tractable form in the supplementary material.

\subsection{Time Generating Process}\label{subsec:Time}
Similarly, we hypothesize ``If $a$ were the sender of edge $d$, when would it be sent?" and define the ``timing rate" for sender $a$
\begin{equation}
\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad}),
\end{equation}
where $\boldsymbol{\eta}$ is $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of time-related covariates, e.g., any feature that could affect timestamps of the edge, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.

In modeling ``when", we do not directly model the timestamp $t_d$. Instead, we assume that each sender's the time-increment or ``time to next edge" (i.e., $\tau_{d} = t_d-t_{d-1}$) is drawn from a specific distribution in the exponential family.  We follow the generalized linear model framework:
\begin{equation}
\begin{aligned}
E(\tau_{ad}) &= \mu_{ad},\\
V(\tau_{ad}) &= V(\mu_{ad}),
\end{aligned}
\end{equation}
where $\tau_{ad}$ is a positive real number. Possible choices of distribution include Exponential, Weibull, Gamma, and lognormal\footnote{lognormal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling. Based on the choice of distribution, we may introduce any additional parameter (e.g., $\sigma_\tau^2$) to account for the variance. We use $\phi_\tau(\cdot; \mu, \sigma_\tau^2)$ and $\Phi_\tau(\cdot; \mu, \sigma_\tau^2)$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $\sigma^2$.

\subsection{Observed Data}\label{subsec:Observed}
Finally, we choose the sender, recipients, and timestamp---which will be observed---by selecting the sender--recipient-set pair with the smallest time-increment \cite{snijders1996stochastic}:
\begin{equation}
\begin{aligned}
a_d &= \mbox{argmin}_{a}(\tau_{ad}),\\
\boldsymbol{r}_d &= \boldsymbol{u}_{a_d d},\\
t_d &=t_{d-1} + \tau_{a_d d}.
\end{aligned}
\end{equation}
Therefore, it is a sender-driven process in that the recipients and timestamp of an edge is determined by the sender's urgency to send the edge to chosen recipients. 
	\begin{algorithm}[H]
		\spacingset{1}
		\SetAlgoLined
		\caption{Generating Process}
		\For{d=1 to D}{
			\For{a=1 to $A$}{
				\For{r=1 to $A$}{
					\If {r $\neq$ a} {
						form $\boldsymbol{x}_{adr}$\\
						set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
					}  }
					draw $\boldsymbol{u}_{ad}  \sim
					\mbox{Gibbs}(\delta, \boldsymbol{\lambda}_{ad})$\\
					form $\boldsymbol{y}_{ad}$\\
					set $\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad})$\\
					draw $\tau_{ad} \sim \phi_\tau(\mu_{ad}, \sigma_\tau^2)$
				}
				set $a_d= \mbox{argmin}_{a}(\tau_{ad})$\\
				set $\boldsymbol{r}_d = \boldsymbol{u}_{a_d d}$\\
				set $t_d =t_{d-1} + \min_a\tau_{ad}$
			}
			\label{alg:generative}
		\end{algorithm}
\spacingset{1.45}
\section{Posterior Inference}\label{sec:inference}
Our inference goal is to invert the generative process to obtain the posterior distribution over the unknown parameters, conditioned on the observed data and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta, {\mu}_\delta,\sigma^2_\delta)$. We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each parameter from its conditional posterior given the observed data, hyperparamters, and the current values of the other parameters. We express each parameter’s conditional posterior in a closed form using the data augmentation schemes in $\boldsymbol{u}$ \cite{tanner1987calculation}. In this section, we provide each latent variable's conditional posterior. \\ \newline
First, since $u_{adr}$ is a binary random variable, new values may be sampled directly using
\begin{equation}
\begin{aligned}
&P(u_{adr}=1| \boldsymbol{u}_{ad\backslash r}, \boldsymbol{b}, \delta, \boldsymbol{x})
\propto \mbox{exp}\{\delta+\lambda_{adr}\};\\
&P(u_{adr}=0| \boldsymbol{u}_{ad\backslash r},\boldsymbol{b}, \delta, \boldsymbol{x})\propto \text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 ),
\end{aligned}
\label{eqn:latentreceiver}
\end{equation}
where $I(\cdot)$ is the indicator function that is used to prevent from the instances where a sender chooses zero number of recipients.\\ \newline
New values for continuous variables $\delta, \boldsymbol{b},$ and $\boldsymbol{\eta}$ and $\sigma^2_\tau$ (if applicable) cannot be sampled directly from their conditional posteriors, but may instead be obtained using the Metropolis--Hastings algorithm. With uninformative priors (i.e., $N({0},\infty)$), the conditional posterior over $\delta$ and $\boldsymbol{b}$ is
\begin{equation}
P(\boldsymbol{b}, \delta| \boldsymbol{u}, \boldsymbol{x})\propto \prod_{d=1}^D
\prod_{a=1}^A \frac{\exp\Big\{\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0)\big) + \sum\limits_{r \neq a} (\delta+\lambda_{adr})u_{adr}\Big\}}{Z(\delta,\boldsymbol{\lambda}_{ad})},
\end{equation}
where the two variables share the conditional posterior and thus can be jointly sampled. Likewise, assuming uninformative priors on $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$) and $\sigma_{\tau}^2$ (i.e., half-Cauchy($\infty$)), the conditional posterior is
\begin{equation}
P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\propto \prod_{d=1}^D\Big(\phi_{\tau}(\tau_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-\Phi_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)\Big).
\end{equation}

 \begin{algorithm}[H]
 			\spacingset{1}
 	\SetAlgoLined
 	\caption{MCMC Algorithm}
 	set initial values of $\boldsymbol{b}, \delta, \boldsymbol{\eta}, \sigma_\tau^2$\\
 	\For{o=1 to outer}{
 	 		\For{d=1 to D}{
 			\For{a = 1 to A}{
 				\For{r = a to A}{
 					\If {r $\neq$ a} {
 						update $u_{adr}$ using Gibbs update --- Equation (7)
 					}
	 			}
 			}
 		 		\For{n=1 to inner1}{
 		 			update $\boldsymbol{b}$ and $\delta$ using Metropolis-Hastings --- Equation (8)
 				}
 		\For{n=1 to inner2}{
 				update $\boldsymbol{\eta}$ and $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (9)
 		}
 			\For{n=1 to inner3}{
 				update $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (9)
 			}
 	}
 }
 	Summarize the results with: \\last chain of $\boldsymbol{b}$ and $\delta$, and last chain of $\boldsymbol{\eta}$ and $\sigma_\tau^2$ 
 \end{algorithm}
\section{Case Studies}\label{sec:case studies}
We now present two case studies applying our method to 1) county government emails (single sender multiple recipients) and 2) international sanctions (multiple senders single recipient). For each case study,
we formulate the network statistics $\boldsymbol{x}$ and timestamp statistics $\boldsymbol{y}$ and ground them in
illustrative examples. We then report a suite of experiments that test our method’s ability to form the posterior distribution over latent variables for different types of data. 
 	   \subsection{Case Study 1: County Government Emails}\label{subsec:Emails}
 	  	   \subsubsection{Montgomary County Data}\label{subsubsec:Montgomery}
 	   Our data come from the North Carolina county government email dataset collected by \cite{ben2017transparency} that includes internal email corpora covering the inboxes and outboxes of managerial-level employees of North Carolina county governments. Out of over twenty counties, we chose Montgomery County to 1) test our model using data with a lot of multicast edges (16.76\%), and 2) limit the scope of this initial application. The Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012. 
 	   \subsubsection{Covariates}\label{subsec:Covariates_email}
In the example of email networks, we form the covariate vector $\boldsymbol{x}_{adr}$ using dynamic network statistics on three time intervals prior to and including $t_{d-1}$. We compute eight network statistics within each time interval \cite{PerryWolfe2012}, where the intervals are $(t_{d-1}-384h, t_{d-1}-96h], (t_{d-1}-96h, t_{d-1}-24h]$ and $(t_{d-1}-24h, t_{d-1}]$. We define the intervals to have equal length in the log-scale, and use $i=1$ to denote the earliest interval---i.e., $(t_{d-1}-384h, t_{d-1}-96h]$---and i = 3 to denote the latest. 
\begin{itemize}
	 			\spacingset{1}
	\item[1.] outdegree$(a,i)=\sum\limits_{d^\prime:t_{d^\prime \in i}} I(a_{d^\prime} = a)$;
	\item[2.] indegree$(r,i)=\sum\limits_{d^\prime:t_{d^\prime \in i}} I(u_{d^\prime r} = 1)$;
	\item[3.] send$(a,r,i)=\sum\limits_{d^\prime:t_{d^\prime \in i}} I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
	\item[4.] receive$(a,r,i)=\mbox{send}(r,a,i)$;
	\item[5.] 2-send$(a,r,i) = \sum\limits_{\substack{i^\prime, i^{\prime\prime}\geq i:\\i^\prime = i \mbox{ \small or }i^{\prime\prime}=i}}\sum\limits_{h \neq a, r} \mbox{send}(a,h,i^\prime)\mbox{send}(h,r,i^{\prime\prime})$;
	\item[6.] 2-receive$(a,r,i) = \sum\limits_{\substack{i^\prime, i^{\prime\prime}\geq i:\\i^\prime = i \mbox{ \small or }i^{\prime\prime}=i}}\sum\limits_{h \neq a, r} \mbox{send}(h,a,i^\prime)\mbox{send}(r,h,i^{\prime\prime})$;
	\item[6.] sibling$(a,r,i) =\sum\limits_{\substack{i^\prime, i^{\prime\prime}\geq i:\\i^\prime = i \mbox{ \small or }i^{\prime\prime}=i}}\sum\limits_{h \neq a, r} \mbox{send}(h,a,i^\prime)\mbox{send}(h,r,i^{\prime\prime})$;
	\item[6.] cosibling$(a,r,i) =\sum\limits_{\substack{i^\prime, i^{\prime\prime}\geq i:\\i^\prime = i \mbox{ \small or }i^{\prime\prime}=i}}\sum\limits_{h \neq a, r} \mbox{send}(a,h,i^\prime)\mbox{send}(r,h,i^{\prime\prime})$;
\end{itemize}
where $I(\cdot)$ is an indicator function. Note that in order to obtain two-path statistics (i.e., 2-send, 2-receive, sibling, and cosibling) within a single time interval $i$, we compute the number of two-paths from $a$ to $r$ by summing over the pairs of intervals $(i^\prime, i^{\prime\prime})$ where the earlier email in the path was sent during interval $i$.

For time-related covariates $\boldsymbol{y}_{ad}$,

\subsubsection{Experiment}\label{subsubsec:Experiment_email}
\subsubsection{Posterior Predictive Checks}\label{subsubsec:PPC_email} 	   
 	    	   Finally, we perform posterior predictive checks \cite{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data. We formally generated entirely new data, by simulating ties and timestamps $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{sec:inference}. For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email network: indegree distribution, outdegree distribution, recipient size distribution, time-increments distribution, the edgewise shared partner distribution, and the geodesic distance distribution. We then generated 500 synthetic networks from the posterior predictive distribution.
 	    	   \begin{algorithm}[H]
 	    	   	\spacingset{1}
 	    	   	\caption{Generate new data for PPC}
 	    	   	\begin{algorithmic}
 	    	   		\STATE \textbf{Input}: number of new data to generate $R$,\\
 	    	   		estimated latent variables $(\boldsymbol{u}, \boldsymbol{b}, \delta, \boldsymbol{\eta},  \sigma_\tau^2)$\\
 	    	   		\vskip 0.1in

 	    	   		\FOR{$r=1$ {\bfseries to}  $R$}
 	    	   		\FOR{$d = 1$ {\bfseries to}  $D$} 
 	    	   		\STATE  Compute $\boldsymbol{x}_{d}$ and $\boldsymbol{y}_{d}$ given $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{[1:(d-1)]}$
 	    	   		\STATE	Draw ($a_{d}$, $\boldsymbol{r}_{d}$, $t_{d}$) following Section \ref{sec:generative process}\\
 	    	   		\ENDFOR
 	    	   		\STATE Store every $r^{th}$ new data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ 
 	    	   		\ENDFOR
 	    	   	\end{algorithmic}
 	    	   \end{algorithm}       
\subsection{Case Study 2: International Sanctions}\label{subsec:International Sanctions}
\subsubsection{Threat and Imposition of Sanctions (TIES) Data}\label{subsubsec:TIES}
We processed the threat and imposition of sanctions (TIES) data \citep{morgan2014threat} that includes the records of international sanctions---defined as actions that one or more countries take to limit or end their economic relations with a target country in an effort to persuade that country to change one or more of its policies---from 1945 to 2005.
\subsubsection{Covariates}\label{subsec:Covariates_sanction}
\subsubsection{Experiment}\label{subsec:Experiment_sanction}
\subsubsection{Posterior Predictive Checks}\label{subsubsec:PPC_sanction} 	   
\section{Conclusion}\label{sec:conclusion}
\newpage
\bibliographystyle{agsm}
\bibliography{multicastnetwork}
\begin{appendices}
\section{Normalizing constant of Gibbs measure}\label{sec: non-empty Gibbs measure}
The non-empty Gibbs measure \cite{fellows2017removing} defines the probability of author $a$ selecting the binary recipient vector $\boldsymbol{u}_{ad}$ as
\begin{equation*} 
\begin{aligned}
& P(\boldsymbol{u}_{ad}| \delta, \boldsymbol{\lambda}_{ad} ) = \frac{\exp\Big\{ \mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} (\delta+\lambda_{adr})u_{adr} \Big\}}{Z(\delta,\boldsymbol{\lambda}_{ad})}.
\end{aligned}
\end{equation*}

To use this distribution efficiently, we derive a closed-form expression for $Z(\delta,\boldsymbol{\lambda}_{id})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (\textit{i.e.} $\forall \boldsymbol{u}_{ad} \in [0,1]^A$). We recognize that if $\boldsymbol{u}_{ad}$ were drawn via independent Bernoulli distributions in which $P({u}_{adr}=1|\delta, \boldsymbol{\lambda}_{ad})$ was given by logit$(\delta+\lambda_{adr})$, then 
\begin{equation*}
P(\boldsymbol{u}_{ad}|\delta, \boldsymbol{\lambda}_{ad}) \propto \exp\Big\{\sum_{r \neq a } (\delta+\lambda_{adr})u_{adr}\Big\}.  	 
\end{equation*}
This is straightforward to verify by looking at 
\begin{equation*}
\begin{aligned}
&P(u_{adr}=1|\boldsymbol{u}_{ad[-r]}, \delta, \boldsymbol{\lambda}_{ad})
=\frac{ \exp{(\delta+\lambda_{adr})}}{\exp{(\delta+\lambda_{adr})} + 1}.\end{aligned}\end{equation*}
We denote the logistic-Bernoulli normalizing constant as $Z^{l}(\delta,\boldsymbol{\lambda}_{ad})$, which is defined as 
\begin{equation*}
Z^{l}(\delta,\boldsymbol{\lambda}_{ad})=\sum_{\boldsymbol{u}_{ad} \in [0,1]^{A}} \exp\Big\{\sum_{r\neq a} (\delta+\lambda_{adr})u_{adr}\Big\}.
\end{equation*}
Now, since 
\begin{equation*}
\begin{aligned}
&\exp\Big\{ \mbox{log}\Big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\Big) + \sum_{r \neq a} (\delta+\lambda_{adr})u_{adr} \Big\}\\&= \exp\Big\{  \sum_{r \neq a} (\delta+\lambda_{adr})u_{adr} \Big\},
\end{aligned}
\end{equation*}
except when $\lVert \boldsymbol{u}_{ad} \rVert_1=0$, we note that 
\begin{equation*}
\begin{aligned}
Z(\delta,\boldsymbol{\lambda}_{ad})& = Z^{l}(\delta,\boldsymbol{\lambda}_{ad}) -\exp\Big\{ \sum\limits_{\forall u_{adr}=0}(\delta+\lambda_{adr})u_{adr} \Big\}
\\& = Z^{l}(\delta,\lambda_{a}^{(d)}) -  1.
\end{aligned}
\end{equation*}
We can therefore derive a closed form expression for $Z(\delta,\boldsymbol{\lambda}_{ad})$ via a closed form expression for $Z^{l}(\delta,\boldsymbol{\lambda}_{ad})$. This can be done by looking at the probability of the zero vector under the logistic-Bernoulli model:
\begin{equation*}
\begin{aligned}
&\frac{\exp\Big\{ \sum\limits_{\forall u_{adr}=0}(\delta+\lambda_{adr})u_{adr} \Big\}}{Z^{l}(\delta,\boldsymbol{\lambda}_{ad})}= \prod_{r \neq a}   \Big(1-\frac{ \exp{(\delta+\lambda_{adr})}}{\exp{(\delta+\lambda_{adr})} + 1}\Big).
\end{aligned}  
\end{equation*}
Then, we have 
\begin{equation*}
\begin{aligned}
& \frac{1}{Z^{l}(\delta,\boldsymbol{\lambda}_{ad})} &= \prod\limits_{r \neq a}\frac{1}{ \exp(\delta+\lambda_{adr})+ 1}.
\end{aligned}  
\end{equation*}
Finally, the closed form expression for the normalizing constant under the non-empty Gibbs measure is  \begin{equation*}
\begin{aligned}Z(\delta,\boldsymbol{\lambda}_{ad}) = \prod_{r \neq a } \big(\mbox{exp}\{\delta+\lambda_{adr}\} + 1\big)-1.
\end{aligned}  
\end{equation*}

	\end{appendices}
\end{document}

### 2018-03-22 GiR/GiR.R

@@ -1,0 +1,34 @@
+library(pkg)
+library(FastGP)
+library(MCMCpack)
+library(LaplacesDemon)
+set.seed(526113322)
+nDocs = 100
+node = 1:4
+netstat = c("dyadic")
+timestat = c("timeofday", "dayofweek")
+timestat = c()
+L = 3
+P = 6
+prior.b = list(rep(0.5, P), 0.5* diag(P))
+prior.delta = c(-5, 0.1)
+#prior.eta = list(rep(2.5, length(node) + length(timestat)), 0.5*diag(length(node) +length(timestat)))
+prior.eta = list(rep(2.5, 2), 0.5*diag(2))
+prior.tau = 0.5
+sigma.Q = c(0.05, 0.001, 0.01, 0.05)
+
+b = prior.b[[1]]
+eta = prior.eta[[1]]
+delta = prior.delta[1]
+sigma_tau = prior.tau
+support = gibbs.measure.support(length(node)-1)
+base.data = GenerateDocs(500, node, b, eta, delta, sigma_tau, support, netstat, timestat,
+                        base.data= NULL, backward = FALSE, base = TRUE)
+
+
+Outer = 5
+Inner = c(50, 50, 50)
+Schein <- Schein(1000, nDocs, node, prior.b, prior.delta, prior.eta, prior.tau, sigma.Q, Outer, Inner,
+               netstat = c("dyadic"), timestat = timestat,
+              base.data = base.data, generate_PP_plots = TRUE)
+

### 2018-03-22 GiR/timemodeling.R

@@ -1,0 +1,149 @@
+# only common mean
+nDocs = 50
+s2 = 1
+node = 10
+X = matrix(1, nDocs, node)
+	eta.true = rnorm(1, 0, 1)
+	mu = eta.true[1] *  X
+	obs = rep(NA, nDocs)
+	sender = rep(NA, nDocs)
+	for (d in 1:nDocs) {
+		times = rlnorm(node, mu[d,], s2)
+		obs[d] = min(times)
+		sender[d] = which(times == obs[d])
+	}
+post.old = function(eta.old, obs, sender) {
+	 mu = eta.old * X
+	 sum(sapply(1:nDocs, function(d) dlnorm(obs[d], mu[d,sender[d]], s2, log = TRUE) + sum(sapply(c(1:node)[-sender[d]], function(x) plnorm(obs[d], mu[d, x], s2, lower.tail = FALSE, log.p = TRUE)))))
+	}
+eta.grid = seq(-10, 10, by = 0.01)
+y = sapply(eta.grid, function(x) post.old(x, obs, sender))
+plot(eta.grid, y)
+c(eta.true,eta.grid[which(y==max(y))])
+
+#mean --- test of s2
+nDocs = 100
+s2 = rhalfcauchy(1, 0.5)
+node = 4
+X = matrix(1, nDocs, node)
+	eta.true = rnorm(1, 0, 1)
+	mu = eta.true[1]* X 
+	obs = rep(NA, nDocs)
+	sender = rep(NA, nDocs)
+	for (d in 1:nDocs) {
+		times = rlnorm(node, mu[d,], s2)
+		obs[d] = min(times)
+		sender[d] = which(times == obs[d])
+	}
+post.old = function(eta.old, obs, sender, s2) {
+	 mu = eta.old[1]* X
+	sum(sapply(1:nDocs, function(d) dlnorm(obs[d], mu[d,sender[d]], s2, log = TRUE) + sum(sapply(c(1:node)[-sender[d]], function(x) plnorm(obs[d], mu[d, x], s2, lower.tail = FALSE, log.p = TRUE)))))
+	}
+	
+s2.grid = seq(0.1, 10, by = 0.01)
+y = sapply(s2.grid, function(x) post.old(eta.true, obs, sender, x))
+plot(s2.grid, y)
+c(s2,s2.grid[which(y==max(y))])
+
+
+
+#mean + one covariate
+nDocs = 10
+s2 = 1
+node = 4
[…]

### 2018-03-22 pkg/R/RcppExports.R

@@ -1,0 +1,143 @@
+# Generated by using Rcpp::compileAttributes() -> do not edit by hand
+# Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
+
+sortuniq <- function(x) {
+    .Call('_pkg_sortuniq', PACKAGE = 'pkg', x)
+}
+
+Mahalanobis <- function(x, center, cov) {
+    .Call('_pkg_Mahalanobis', PACKAGE = 'pkg', x, center, cov)
+}
+
+ei <- function(M) {
+    .Call('_pkg_ei', PACKAGE = 'pkg', M)
+}
+
+dmvnorm_arma <- function(x, mean, sigma) {
+    .Call('_pkg_dmvnorm_arma', PACKAGE = 'pkg', x, mean, sigma)
+}
+
+rmvnorm_arma <- function(n, mu, Sigma) {
+    .Call('_pkg_rmvnorm_arma', PACKAGE = 'pkg', n, mu, Sigma)
+}
+
+priorsum <- function(var, mu, x) {
+    .Call('_pkg_priorsum', PACKAGE = 'pkg', var, mu, x)
+}
+
+tabulateC <- function(x, max) {
+    .Call('_pkg_tabulateC', PACKAGE = 'pkg', x, max)
+}
+
+transpose <- function(x) {
+    .Call('_pkg_transpose', PACKAGE = 'pkg', x)
+}
+
+callRMultinom <- function(x) {
+    .Call('_pkg_callRMultinom', PACKAGE = 'pkg', x)
+}
+
+multinom_vec <- function(nSample, props) {
+    .Call('_pkg_multinom_vec', PACKAGE = 'pkg', nSample, props)
+}
+
+which_int <- function(value, x) {
+    .Call('_pkg_which_int', PACKAGE = 'pkg', value, x)
+}
+
+which_num <- function(value, x) {
+    .Call('_pkg_which_num', PACKAGE = 'pkg', value, x)
+}
+
+rdirichlet_cpp <- function(num_samples, alpha_m) {
+    .Call('_pkg_rdirichlet_cpp', PACKAGE = 'pkg', num_samples, alpha_m)
+}
+
+which_cpp <- function(value, x) {
+    .Call('_pkg_which_cpp', PACKAGE = 'pkg', value, x)
+}
+
+expconst <- function(consts) {
+    .Call('_pkg_expconst', PACKAGE = 'pkg', consts)
+}
+
[…]

### 2018-03-22 pkg/R/core.R

@@ -1,0 +1,641 @@
+#' @useDynLib pkg
+#' @import stats
+#' @import grDevices
+#' @import graphics
+#' @import RcppArmadillo
+#' @importFrom Rcpp sourceCpp
+#' @importFrom reshape melt
+#' @importFrom coda mcmc geweke.diag
+#' @importFrom combinat permn
+#' @importFrom mgcv uniquecombs
+#' @importFrom lubridate wday hour
+#' @importFrom LaplacesDemon dhalfcauchy rhalfcauchy
+#' @importFrom truncnorm rtruncnorm dtruncnorm
+
+tvapply = function(...) transpose(vapply(...))
+
+#' @title gibbs.measure.support
+#' @description List out the support of Gibbs measure
+#'
+#' @param n length of the vector to be sampled 
+#'
+#' @return  a 2^n x n binary matrix representing the support of the binary Gibbs measure in n elements
+#'
+#' @export
+gibbs.measure.support = function(n) {
+	gibbs.support = rbind(rep(1, n))
+	for(i in 1:(n-1)){
+		gibbs.mat.i = do.call('rbind',permn(c(rep(1, i), rep(0, n-i))))
+		gibbs.support = rbind(gibbs.support, gibbs.mat.i)
+	}
+	out = as.matrix(unique(gibbs.support))
+	return(out)
+}
+
+#' @title r.gibbs.measure
+#' @description List out the support of Gibbs measure
+#'
+#' @param nsamp the number of binary vector samples to draw
+#' @param lambda.i a vector of coefficients according to which each element
+#' @param delta a positive real valued parameter that controls the density penalty 
+#' @param support support of Gibbs measure
+#'
+#' @return nsamp number of samples with each row denoting binary vector
+#'
+#' @export
+r.gibbs.measure <- function(nsamp, lambda.i, delta, support) {
+	#gibbsNormalizer = prod(exp(delta+lambda.i)+1)-1
+	logitNumerator = vapply(1:nrow(support), function(s) {
+		sum((delta+lambda.i)*support[s,])
+		}, c(1))		
+	samp = lmultinom(logitNumerator)
+	return(support[samp,])	
+}
+
+#' @title adaptive.MH 
+#' @description adaptive Metropolis Hastings to maintain target acceptance rate
+#'
[…]

### 2018-03-22 pkg/src/RcppExports.cpp

@@ -1,0 +1,499 @@
+// Generated by using Rcpp::compileAttributes() -> do not edit by hand
+// Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
+
+#include <RcppArmadillo.h>
+#include <Rcpp.h>
+
+using namespace Rcpp;
+
+// sortuniq
+NumericVector sortuniq(NumericVector x);
+RcppExport SEXP _pkg_sortuniq(SEXP xSEXP) {
+BEGIN_RCPP
+    Rcpp::RObject rcpp_result_gen;
+    Rcpp::RNGScope rcpp_rngScope_gen;
+    Rcpp::traits::input_parameter< NumericVector >::type x(xSEXP);
+    rcpp_result_gen = Rcpp::wrap(sortuniq(x));
+    return rcpp_result_gen;
+END_RCPP
+}
+// Mahalanobis
+arma::vec Mahalanobis(arma::mat x, arma::rowvec center, arma::mat cov);
+RcppExport SEXP _pkg_Mahalanobis(SEXP xSEXP, SEXP centerSEXP, SEXP covSEXP) {
+BEGIN_RCPP
+    Rcpp::RObject rcpp_result_gen;
+    Rcpp::RNGScope rcpp_rngScope_gen;
+    Rcpp::traits::input_parameter< arma::mat >::type x(xSEXP);
+    Rcpp::traits::input_parameter< arma::rowvec >::type center(centerSEXP);
+    Rcpp::traits::input_parameter< arma::mat >::type cov(covSEXP);
+    rcpp_result_gen = Rcpp::wrap(Mahalanobis(x, center, cov));
+    return rcpp_result_gen;
+END_RCPP
+}
+// ei
+arma::vec ei(arma::mat M);
+RcppExport SEXP _pkg_ei(SEXP MSEXP) {
+BEGIN_RCPP
+    Rcpp::RObject rcpp_result_gen;
+    Rcpp::RNGScope rcpp_rngScope_gen;
+    Rcpp::traits::input_parameter< arma::mat >::type M(MSEXP);
+    rcpp_result_gen = Rcpp::wrap(ei(M));
+    return rcpp_result_gen;
+END_RCPP
+}
+// dmvnorm_arma
+arma::vec dmvnorm_arma(arma::mat x, arma::rowvec mean, arma::mat sigma);
[…]

### 2018-03-22 pkg/src/sampler.cpp

@@ -1,0 +1,662 @@
+#include <RcppArmadillo.h>
+#include <cmath>
+#include <Rinternals.h>
+#include <R_ext/Rdynload.h>
+// [[Rcpp::depends(RcppArmadillo)]]
+
+using std::log;
+using std::exp;
+using std::max;
+using std::min;
+using std::abs;
+using std::sqrt;
+using std::pow;
+using namespace Rcpp; 
+
+void R_init_markovchain(DllInfo* info) {
+	R_registerRoutines(info, NULL, NULL, NULL, NULL);
+	R_useDynamicSymbols(info, TRUE);	
+}
+
+extern void dsyev_( char *jobz, char *uplo, int *n, double *a, int *lda,
+                   double *w, double *work, int *lwork, int *info );
+
+const double log2pi = std::log(2.0 * M_PI);
+
+// [[Rcpp::export]]
+NumericVector sortuniq (NumericVector x){
+    return sort_unique(x);
+}
+
+// [[Rcpp::export]]
+arma::vec Mahalanobis(arma::mat x, arma::rowvec center, arma::mat cov){
+    int n = x.n_rows;
+    arma::mat x_cen;
+    x_cen.copy_size(x);
+    for (int i=0; i < n; i++) {
+        x_cen.row(i) = x.row(i) - center;
+    }
+    return sum((x_cen * cov.i()) % x_cen, 1);
+}
+// [[Rcpp::export]]
+arma::vec ei(arma::mat M) {
+    return arma::eig_sym(M);
+}
+
+// [[Rcpp::export]]
+arma::vec dmvnorm_arma (arma::mat x,  arma::rowvec mean,  arma::mat sigma){
+    arma::vec distval = Mahalanobis(x, mean, sigma);
+    arma::vec ei_sigma = ei(sigma);
+    double logdet = sum(arma::log(ei_sigma));
+    arma::vec logretval = -((x.n_cols * log2pi + logdet + distval)/2) ;
+    return(logretval);
+}
+
+// [[Rcpp::export]]
+arma::mat rmvnorm_arma(int n,
+                  const arma::vec& mu,
+                  const arma::mat& Sigma) {
+    unsigned int p = Sigma.n_cols;
+    Rcpp::NumericVector draw = Rcpp::rnorm(n*p);
+    arma::mat Z = arma::mat(draw.begin(), n, p, false, true);
+    arma::mat Y = arma::repmat(mu, 1, n).t()+Z * arma::chol(Sigma);
+    return Y;
+}
+
[…]

### 2018-04-04 paper/paper.tex
MulticastNetwork overall update---GiR, paper, Montgomery

@@
 where $\boldsymbol{b}$ is $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of network features which vary depending on the hypotheses regarding canonical processes relevant to network theory such as popularity, reciprocity, and transitivity.
+In addition, we include intercept term to account for the average (or baseline) number of recipients.
 We place a Normal prior $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$.
@@
 \begin{equation} \boldsymbol{u}_{ad}  \sim
-\mbox{Gibbs}(\delta, \boldsymbol{\lambda}_{ad}),
+\mbox{Gibbs}(\boldsymbol{\lambda}_{ad}),
 \end{equation}
-where $\delta$ is a real number controlling the average number of recipients and $\boldsymbol{\lambda}_{id}= \{\lambda_{adr}\}_{r=1}^A$.
-We place a Normal prior $\delta \sim N(\mu_\delta,\sigma^2_\delta)$.
-In particular, we define $\mbox{Gibbs}(\delta, \boldsymbol{\lambda}_{ad})$ as
+where $\boldsymbol{\lambda}_{id}= \{\lambda_{adr}\}_{r=1}^A$. In particular, we define $\mbox{Gibbs}(\boldsymbol{\lambda}_{ad})$ as
 \begin{equation}
 \begin{aligned}
-&p(\boldsymbol{u}_{ad}|\delta, \boldsymbol{\lambda}_{ad}) = \frac{\exp\Big\{\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0 )\big) + \sum_{r\neq a} (\delta+\lambda_{adr})u_{adr}\Big\}}{Z(\delta,\boldsymbol{\lambda}_{ad})} ,
+&p(\boldsymbol{u}_{ad}|\delta, \boldsymbol{\lambda}_{ad}) = \frac{\exp\Big\{\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0 )\big) + \sum_{r\neq a} \lambda_{adr}u_{adr}\Big\}}{Z(\boldsymbol{\lambda}_{ad})} ,
 \end{aligned}
@@
 \end{equation}
-where $Z(\delta,\boldsymbol{\lambda}_{ad})= \prod_{r \neq a} (\mbox{exp}\{\delta+\lambda_{adr}\} + 1)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
+where $Z(\boldsymbol{\lambda}_{ad})= \prod_{r \neq a} \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
+This is equivalent to assume independent Bernoulli trial on each $u_{adr}$ with probability of 1 being logit($\lambda_{adr}$), excluding the case when all $u_{adr}=0$.
 We provide the derivation of the normalizing constant as a tractable form in the supplementary material.
@@
 Based on the choice of distribution, we may introduce any additional parameter (e.g., $\sigma_\tau^2$) to account for the variance.
-We use $\phi_\tau(\cdot; \mu, \sigma_\tau^2)$ and $\Phi_\tau(\cdot; \mu, \sigma_\tau^2)$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $\sigma^2$.
+We use $f_\tau(\cdot; \mu, \sigma_\tau^2)$ and $F_\tau(\cdot; \mu, \sigma_\tau^2)$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $\sigma^2$.
 
@@
 					draw $\boldsymbol{u}_{ad}  \sim
-					\mbox{Gibbs}(\delta, \boldsymbol{\lambda}_{ad})$\\
+					\mbox{Gibbs}(\boldsymbol{\lambda}_{ad})$\\
 					form $\boldsymbol{y}_{ad}$\\
 					set $\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad})$\\
-					draw $\tau_{ad} \sim \phi_\tau(\mu_{ad}, \sigma_\tau^2)$
+					draw $\tau_{ad} \sim f_\tau(\mu_{ad}, \sigma_\tau^2)$
 				}
@@
 \section{Posterior Inference}\label{sec:inference}
-Our inference goal is to invert the generative process to obtain the posterior distribution over the unknown parameters, conditioned on the observed data and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta, {\mu}_\delta,\sigma^2_\delta)$.
+Our inference goal is to invert the generative process to obtain the posterior distribution over the unknown parameters, conditioned on the observed data and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
 We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each parameter from its conditional posterior given the observed data, hyperparamters, and the current values of the other parameters.
@@
 \begin{aligned}
-&P(u_{adr}=1| \boldsymbol{u}_{ad\backslash r}, \boldsymbol{b}, \delta, \boldsymbol{x})
-\propto \mbox{exp}\{\delta+\lambda_{adr}\};\\
-&P(u_{adr}=0| \boldsymbol{u}_{ad\backslash r},\boldsymbol{b}, \delta, \boldsymbol{x})\propto \text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 ),
+&P(u_{adr}=1| \boldsymbol{u}_{ad\backslash r}, \boldsymbol{b}, \boldsymbol{x})
+\propto \mbox{exp}(\lambda_{adr});\\
+&P(u_{adr}=0| \boldsymbol{u}_{ad\backslash r},\boldsymbol{b}, \boldsymbol{x})\propto \text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 ),
 \end{aligned}
@@
 where $I(\cdot)$ is the indicator function that is used to prevent from the instances where a sender chooses zero number of recipients.\\ \newline
-New values for continuous variables $\delta, \boldsymbol{b},$ and $\boldsymbol{\eta}$ and $\sigma^2_\tau$ (if applicable) cannot be sampled directly from their conditional posteriors, but may instead be obtained using the Metropolis--Hastings algorithm.
-With uninformative priors (i.e., $N({0},\infty)$), the conditional posterior over $\delta$ and $\boldsymbol{b}$ is
+New values for continuous variables $\boldsymbol{b},$ and $\boldsymbol{\eta}$ and $\sigma^2_\tau$ (if applicable) cannot be sampled directly from their conditional posteriors, but may instead be obtained using the Metropolis--Hastings algorithm.
+With uninformative priors (i.e., $N({0},\infty)$), the conditional posterior over $\boldsymbol{b}$ is
 \begin{equation}
-P(\boldsymbol{b}, \delta| \boldsymbol{u}, \boldsymbol{x})\propto \prod_{d=1}^D
-\prod_{a=1}^A \frac{\exp\Big\{\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0)\big) + \sum\limits_{r \neq a} (\delta+\lambda_{adr})u_{adr}\Big\}}{Z(\delta,\boldsymbol{\lambda}_{ad})},
+P(\boldsymbol{b}| \boldsymbol{u}, \boldsymbol{x})\propto \prod_{d=1}^D
+\prod_{a=1}^A \frac{\exp\Big\{\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0)\big) + \sum\limits_{r \neq a} \lambda_{adr}u_{adr}\Big\}}{Z(\boldsymbol{\lambda}_{ad})},
 \end{equation}
@@
 \begin{equation}
-P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\propto \prod_{d=1}^D\Big(\phi_{\tau}(\tau_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-\Phi_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)\Big).
+P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)\Big).
 \end{equation}
@@
  	\caption{MCMC Algorithm}
- 	set initial values of $\boldsymbol{b}, \delta, \boldsymbol{\eta}, \sigma_\tau^2$\\
+ 	set initial values of $\boldsymbol{b}, \boldsymbol{\eta}, \sigma_\tau^2$\\
  	\For{o=1 to outer}{
@@
  		 		\For{n=1 to inner1}{
- 		 			update $\boldsymbol{b}$ and $\delta$ using Metropolis-Hastings --- Equation (8)
+ 		 			update $\boldsymbol{b}$ using Metropolis-Hastings --- Equation (8)
  				}
@@
  }
- 	Summarize the results with: \\last chain of $\boldsymbol{b}$ and $\delta$, and last chain of $\boldsymbol{\eta}$ and $\sigma_\tau^2$ 
+ 	Summarize the results with: \\last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ and $\sigma_\tau^2$ 
  \end{algorithm}
+
+ \section{Getting It Right}\label{sec:GiR}
+ \begin{figure}[H]
+ 	\centering
+ 	\includegraphics[width=1\textwidth, trim = 0.5cm 1cm 0.5cm 1cm, clip=true]{Multicast_Schein.pdf}	
+ 	\caption {Schein test results when we run 5 outer iterations and 5 inner iterations using 20,000 samples (with $D = 100, A = 5, P = 5, Q = 3$)}
+ 	\label{figure:GiR}
+ \end{figure}
+
 \section{Case Studies}\label{sec:case studies}
@@
  	   \subsubsection{Covariates}\label{subsec:Covariates_email}
-In the example of email networks, we form the covariate vector $\boldsymbol{x}_{adr}$ using dynamic network statistics on three time intervals prior to and including $t_{d-1}$.
-We compute eight network statistics within each time interval \cite{PerryWolfe2012}, where the intervals are $(t_{d-1}-384h, t_{d-1}-96h], (t_{d-1}-96h, t_{d-1}-24h]$ and $(t_{d-1}-24h, t_{d-1}]$.
-We define the intervals to have equal length in the log-scale, and use $i=1$ to denote the earliest interval---i.e., $(t_{d-1}-384h, t_{d-1}-96h]$---and i = 3 to denote the latest.
+In the example of email networks, we form the covariate vector $\boldsymbol{x}_{adr}$ using time-varying network statistics based on the time interval prior to and including $t_{d-1}$.
+Along with intercept term, we compute eight network statistics \cite{PerryWolfe2012}, where the time interval tracks 3 days prior to the last email was sent $l_d = (t_{d-1}-96h, t_{d-1}]$.
 \begin{itemize}
 	 			\spacingset{1}
-	\item[1.] outdegree$(a,i)=\sum\limits_{d^\prime:t_{d^\prime \in i}} I(a_{d^\prime} = a)$;
-	\item[2.] indegree$(r,i)=\sum\limits_{d^\prime:t_{d^\prime \in i}} I(u_{d^\prime r} = 1)$;
-	\item[3.] send$(a,r,i)=\sum\limits_{d^\prime:t_{d^\prime \in i}} I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
-	\item[4.] receive$(a,r,i)=\mbox{send}(r,a,i)$;
-	\item[5.] 2-send$(a,r,i) = \sum\limits_{\substack{i^\prime, i^{\prime\prime}\geq i:\\i^\prime = i \mbox{ \small or }i^{\prime\prime}=i}}\sum\limits_{h \neq a, r} \mbox{send}(a,h,i^\prime)\mbox{send}(h,r,i^{\prime\prime})$;
-	\item[6.] 2-receive$(a,r,i) = \sum\limits_{\substack{i^\prime, i^{\prime\prime}\geq i:\\i^\prime = i \mbox{ \small or }i^{\prime\prime}=i}}\sum\limits_{h \neq a, r} \mbox{send}(h,a,i^\prime)\mbox{send}(r,h,i^{\prime\prime})$;
-	\item[6.] sibling$(a,r,i) =\sum\limits_{\substack{i^\prime, i^{\prime\prime}\geq i:\\i^\prime = i \mbox{ \small or }i^{\prime\prime}=i}}\sum\limits_{h \neq a, r} \mbox{send}(h,a,i^\prime)\mbox{send}(h,r,i^{\prime\prime})$;
-	\item[6.] cosibling$(a,r,i) =\sum\limits_{\substack{i^\prime, i^{\prime\prime}\geq i:\\i^\prime = i \mbox{ \small or }i^{\prime\prime}=i}}\sum\limits_{h \neq a, r} \mbox{send}(a,h,i^\prime)\mbox{send}(r,h,i^{\prime\prime})$;
+	\item[1.] intercept $\boldsymbol{x}_{adr1} =1$;
+	\item[2.] outdegree $\boldsymbol{x}_{adr2} =\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+	\item[3.] indegree $\boldsymbol{x}_{adr3}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
+	\item[4.] send $\boldsymbol{x}_{adr4}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
+	\item[5.] receive $\boldsymbol{x}_{adr5}=\mbox{send}(r,a)$;
+	\item[6.] 2-send $\boldsymbol{x}_{adr6} = \sum\limits_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(h,r)$;
+	\item[7.] 2-receive $\boldsymbol{x}_{adr7}= \sum\limits_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(r,h)$;
+	\item[8.] sibling $\boldsymbol{x}_{adr8}=\sum\limits_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(h,r)$;
+	\item[9.] cosibling $\boldsymbol{x}_{adr9}=\sum\limits_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(r,h)$;
 \end{itemize}
-where $I(\cdot)$ is an indicator function.
-Note that in order to obtain two-path statistics (i.e., 2-send, 2-receive, sibling, and cosibling) within a single time interval $i$, we compute the number of two-paths from $a$ to $r$ by summing over the pairs of intervals $(i^\prime, i^{\prime\prime})$ where the earlier email in the path was sent during interval $i$.
+where $I(\cdot)$ is an indicator function.\\ \newline
+For time-related covariates $\boldsymbol{y}_{ad}$ in Section \ref{subsec:Time}, we form the covariate vector $\boldsymbol{y}_{ad}$ using the seven statistics which may possibly effect ``time to send the next document".
+Note that these statistics could depend on $a$ only, $d$ (or $t_d$) only, or both $a$ and $d$.
+Specifically, the statistics are
+\begin{itemize}
+	\spacingset{1}
+	\item[1.] intercept $\boldsymbol{y}_{ad1} =1$;
+	\item[2.] outdegree $\boldsymbol{y}_{ad2} =\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+	\item[3.] indegree $\boldsymbol{y}_{ad3}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
+	\item[4.] gender $\boldsymbol{y}_{ad4}=I(a= \mbox{female})$;
+	\item[5.] manager $\boldsymbol{y}_{ad5}=I(a= \mbox{County Manager})$;
+	\item[6.] weekend $\boldsymbol{y}_{ad6} = I(t_{d-1}= \mbox{weekend})$;
+	\item[7.] am/pm $\boldsymbol{y}_{ad7}= I(t_{d-1}= \mbox{pm})$;
+\end{itemize}
+\subsubsection{Parameter Estimation and Interpretation}\label{subsubsec:Result_email}
+\subsection{Case Study 2: International Sanctions}\label{subsec:International Sanctions}
+\subsubsection{Threat and Imposition of Sanctions (TIES) Data}\label{subsubsec:TIES}
+We processed the threat and imposition of sanctions (TIES) data \citep{morgan2014threat} that includes the records of international sanctions---defined as actions that one or more countries take to limit or end their economic relations with a target country in an effort to persuade that country to change one or more of its policies---from 1945 to 2005.
+\subsubsection{Covariates}\label{subsec:Covariates_sanction}
+\subsubsection{Parameter Estimation and Interpretation}\label{subsubsec:Result_sanction}
 
-For time-related covariates $\boldsymbol{y}_{ad}$,
+\subsection{Experiment}\label{subsubsec:Experiment_email}
+We evaluate the model's ability to predict ties from the Montgomery County email network and the threat and imposition of sanctions (TIES) data, conditioned on their ``training" part of the data.
+We separately formed a test split of each three components---author, recipients, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
+Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, estimates of latent variables, and current estimates of test data.
+The full conditional posterior distributions for ``test" author, recipients, and timestamps are provided in the supplementary material.
+We then run inference to update the latent variables given the imputed and observed data.
+We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for ``test" data.
+Algorithm \ref{alg:PPE} outlines this procedure.
 
-\subsubsection{Experiment}\label{subsubsec:Experiment_email}
-\subsubsection{Posterior Predictive Checks}\label{subsubsec:PPC_email} 	   
- 	    	   Finally, we perform posterior predictive checks \cite{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data.
+\begin{algorithm}[H]
+	\spacingset{1}
+	\caption{Out-of-Sample Tie Predictions}
+	\label{alg:PPE}
+	\begin{algorithmic}
+		\STATE {\bfseries Input:} data $ \{ (a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, \\
+		number of new data to generate $R$,\\
+		hyperparameters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$\\
+		\vskip 0.1in
+		\textbf{Test splits:}	
+		\STATE Draw test authors with $p=0.1$ (out of $D$ authors) 
+		\STATE Draw test elements of recipient vector 
+		with $p=0.1$ (out of $D\times (A-1)$ receipient indicators $\{\{\boldsymbol{r}_{dr}\}_{r\in [A]_{\backslash a_d}}\}_{d=1}^D$)
+		\STATE Draw test timestamps with $p=0.1$  (out of $D$ timestamps) 
+		\STATE Set the ``test" data as ``missing" (NA)
+		\vskip 0.1in
+		\textbf{Imputation and inference:}	
+		\STATE Initialize the parameters $(\boldsymbol{b}, \boldsymbol{\eta}, \boldsymbol{u}, \sigma^2_\tau)$
+		\FOR{$r=1$ {\bfseries to}  $R$}
+		\FOR{$d=1$ {\bfseries to}  $D$}
+		\IF{$a_d=$  NA}
+		\FOR{$a=1$ {\bfseries to} $A$}
+		\STATE Compute $\pi_{a} $ using $P(a_d= a | \cdot)$
+		\ENDFOR
+		\STATE Draw $a_d \sim \mbox{Multinomial}(\pi)$
+		\ENDIF
+		\FOR{$r\in [A]_{\backslash a_d}$}
+		\IF{$r_{dr}=$ NA}
+		\STATE Draw $r_{dr}$ using $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$ 
+		\ENDIF
+		\ENDFOR
+		\IF{$t_d=$ NA}
+		\STATE Draw proposal $\boldsymbol{\tau}^{new}_d \sim f_\tau(\mu_{a_dd}, \sigma^2_\tau)$
+		\STATE Use Metropolis-Hastings to decide accept or reject using the probability
+		\begin{equation*}
+		\footnotesize
+		\frac{P(\boldsymbol{\tau}^{new}_d|\mu_{a_dd}, \sigma^2_\tau) P(\boldsymbol{\tau}^{new}_d| \cdot)}{P(\boldsymbol{\tau}^{old}_d|\mu_{a_dd}, \sigma^2_\tau) P(\boldsymbol{\tau}^{old}_d| \cdot)},
+		\end{equation*}
+		where $\boldsymbol{\tau}^{old}_d$ is from earlier iteration.
+		\ENDIF
+		\STATE Run inference and update $(\boldsymbol{b}, \boldsymbol{\eta},\boldsymbol{u}, \sigma^2_\tau)$ given the imputed and observed data
+		\ENDFOR
+		\STATE Store the estimates for ``test" data
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+NOTE: we assume independent Bernoulli trial on $u_{adr}$. Then, does it matter to have test `elements' for the recipient vector instead of having the test `recipient vectors'?
+
+\subsection{Posterior Predictive Checks}\label{subsubsec:PPC_email} 	   
+Finally, we perform posterior predictive checks \cite{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data and the threat and imposition of sanctions (TIES) data.
 We formally generated entirely new data, by simulating ties and timestamps $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{sec:inference}.
-For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email network: indegree distribution, outdegree distribution, recipient size distribution, time-increments distribution, the edgewise shared partner distribution, and the geodesic distance distribution.
+For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data and the threat and imposition of sanctions (TIES) data: indegree distribution, outdegree distribution, recipient size distribution, time-increments distribution, the edgewise shared partner distribution, and the geodesic distance distribution.
 We then generated 500 synthetic networks from the posterior predictive distribution.
@@
 		\STATE \textbf{Input}: number of new data to generate $R$,\\
- 	    	   		estimated latent variables $(\boldsymbol{u}, \boldsymbol{b}, \delta, \boldsymbol{\eta},  \sigma_\tau^2)$\\
+		estimated latent variables $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta},  \sigma_\tau^2)$\\
 		\vskip 0.1in
@@
 \end{algorithm}
-\subsection{Case Study 2: International Sanctions}\label{subsec:International Sanctions}
-\subsubsection{Threat and Imposition of Sanctions (TIES) Data}\label{subsubsec:TIES}
-We processed the threat and imposition of sanctions (TIES) data \citep{morgan2014threat} that includes the records of international sanctions---defined as actions that one or more countries take to limit or end their economic relations with a target country in an effort to persuade that country to change one or more of its policies---from 1945 to 2005.
-\subsubsection{Covariates}\label{subsec:Covariates_sanction}
-\subsubsection{Experiment}\label{subsec:Experiment_sanction}
-\subsubsection{Posterior Predictive Checks}\label{subsubsec:PPC_sanction} 	   
+
 \section{Conclusion}\label{sec:conclusion}
@@
 \begin{aligned}
-& P(\boldsymbol{u}_{ad}| \delta, \boldsymbol{\lambda}_{ad} ) = \frac{\exp\Big\{ \mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} (\delta+\lambda_{adr})u_{adr} \Big\}}{Z(\delta,\boldsymbol{\lambda}_{ad})}.
+& P(\boldsymbol{u}_{ad}|\boldsymbol{\lambda}_{ad} ) = \frac{\exp\Big\{ \mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big\}}{Z(\boldsymbol{\lambda}_{ad})}.
 \end{aligned}
@@
 
-To use this distribution efficiently, we derive a closed-form expression for $Z(\delta,\boldsymbol{\lambda}_{id})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (\textit{i.e.} $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
-We recognize that if $\boldsymbol{u}_{ad}$ were drawn via independent Bernoulli distributions in which $P({u}_{adr}=1|\delta, \boldsymbol{\lambda}_{ad})$ was given by logit$(\delta+\lambda_{adr})$, then
+To use this distribution efficiently, we derive a closed-form expression for $Z(\boldsymbol{\lambda}_{id})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (\textit{i.e.} $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
+We recognize that if $\boldsymbol{u}_{ad}$ were drawn via independent Bernoulli distributions in which $P({u}_{adr}=1|\delta, \boldsymbol{\lambda}_{ad})$ was given by logit$(\lambda_{adr})$, then
 \begin{equation*}
-P(\boldsymbol{u}_{ad}|\delta, \boldsymbol{\lambda}_{ad}) \propto \exp\Big\{\sum_{r \neq a } (\delta+\lambda_{adr})u_{adr}\Big\}.  	 
+P(\boldsymbol{u}_{ad}|\boldsymbol{\lambda}_{ad}) \propto \exp\Big\{\sum_{r \neq a } \lambda_{adr}u_{adr}\Big\}.  	 
 \end{equation*}
@@
 \begin{aligned}
-&P(u_{adr}=1|\boldsymbol{u}_{ad[-r]}, \delta, \boldsymbol{\lambda}_{ad})
-=\frac{ \exp{(\delta+\lambda_{adr})}}{\exp{(\delta+\lambda_{adr})} + 1}.\end{aligned}\end{equation*}
-We denote the logistic-Bernoulli normalizing constant as $Z^{l}(\delta,\boldsymbol{\lambda}_{ad})$, which is defined as 
+&P(u_{adr}=1|\boldsymbol{u}_{ad[-r]}, \boldsymbol{\lambda}_{ad})
+=\frac{ \exp{(\lambda_{adr})}}{\exp{(\lambda_{adr})} + 1}.\end{aligned}\end{equation*}
+We denote the logistic-Bernoulli normalizing constant as $Z^{l}(\boldsymbol{\lambda}_{ad})$, which is defined as 
 \begin{equation*}
-Z^{l}(\delta,\boldsymbol{\lambda}_{ad})=\sum_{\boldsymbol{u}_{ad} \in [0,1]^{A}} \exp\Big\{\sum_{r\neq a} (\delta+\lambda_{adr})u_{adr}\Big\}.
+Z^{l}(\delta,\boldsymbol{\lambda}_{ad})=\sum_{\boldsymbol{u}_{ad} \in [0,1]^{A}} \exp\Big\{\sum_{r\neq a} \lambda_{adr}u_{adr}\Big\}.
 \end{equation*}
@@
 \begin{aligned}
-&\exp\Big\{ \mbox{log}\Big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\Big) + \sum_{r \neq a} (\delta+\lambda_{adr})u_{adr} \Big\}\\&= \exp\Big\{  \sum_{r \neq a} (\delta+\lambda_{adr})u_{adr} \Big\},
+&\exp\Big\{ \mbox{log}\Big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\Big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big\}\\&= \exp\Big\{  \sum_{r \neq a} \lambda_{adr}u_{adr} \Big\},
 \end{aligned}
@@
 \begin{aligned}
-Z(\delta,\boldsymbol{\lambda}_{ad})& = Z^{l}(\delta,\boldsymbol{\lambda}_{ad}) -\exp\Big\{ \sum\limits_{\forall u_{adr}=0}(\delta+\lambda_{adr})u_{adr} \Big\}
-\\& = Z^{l}(\delta,\lambda_{a}^{(d)}) -  1.
+Z(\boldsymbol{\lambda}_{ad})& = Z^{l}(\boldsymbol{\lambda}_{ad}) -\exp\Big\{ \sum\limits_{\forall u_{adr}=0}\lambda_{adr}u_{adr} \Big\}
+\\& = Z^{l}(\lambda_{a}^{(d)}) -  1.
 \end{aligned}
@@
 \begin{aligned}
-&\frac{\exp\Big\{ \sum\limits_{\forall u_{adr}=0}(\delta+\lambda_{adr})u_{adr} \Big\}}{Z^{l}(\delta,\boldsymbol{\lambda}_{ad})}= \prod_{r \neq a}   \Big(1-\frac{ \exp{(\delta+\lambda_{adr})}}{\exp{(\delta+\lambda_{adr})} + 1}\Big).
+&\frac{\exp\Big\{ \sum\limits_{\forall u_{adr}=0}\lambda_{adr}u_{adr} \Big\}}{Z^{l}(\boldsymbol{\lambda}_{ad})}= \prod_{r \neq a}   \Big(1-\frac{ \exp{(\lambda_{adr})}}{\exp{(\lambda_{adr})} + 1}\Big).
 \end{aligned}  
@@
 \begin{aligned}
-& \frac{1}{Z^{l}(\delta,\boldsymbol{\lambda}_{ad})} &= \prod\limits_{r \neq a}\frac{1}{ \exp(\delta+\lambda_{adr})+ 1}.
+& \frac{1}{Z^{l}(\boldsymbol{\lambda}_{ad})} &= \prod\limits_{r \neq a}\frac{1}{ \exp(\lambda_{adr})+ 1}.
 \end{aligned}  
@@
 Finally, the closed form expression for the normalizing constant under the non-empty Gibbs measure is  \begin{equation*}
-\begin{aligned}Z(\delta,\boldsymbol{\lambda}_{ad}) = \prod_{r \neq a } \big(\mbox{exp}\{\delta+\lambda_{adr}\} + 1\big)-1.
+\begin{aligned}Z(\boldsymbol{\lambda}_{ad}) = \prod_{r \neq a } \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1.
 \end{aligned}  

### 2018-04-04 GiR/GiR.R

@@ -3,7 +3,7 @@ library(FastGP)
 library(MCMCpack)
 library(LaplacesDemon)
 set.seed(526113322)
-nDocs = 100
+nDocs = 50
 node = 1:4
 netstat = c("dyadic")
 #timestat = c("timeofday", "dayofweek")
@@ -14,7 +14,7 @@ prior.b = list(rep(0.5, P), 0.5* diag(P))
 prior.delta = c(-3, 0.1)
 #prior.eta = list(rep(2.5, length(node) + length(timestat)), 0.5*diag(length(node) +length(timestat)))
 prior.eta = list(rep(2.5, 1), 0.5*diag(1))
-prior.tau =  c(2,1)
+prior.tau =  c(5,1)
 sigma.Q = c(0.075, 0.005, 0.25, 0.05)
 
 b = prior.b[[1]]

### 2018-04-04 GiR/Multicast_rcpp.cpp

@@ -1,0 +1,185 @@
+#include <RcppArmadillo.h>
+#include <cmath>
+#include <Rinternals.h>
+#include <R_ext/Rdynload.h>
+// [[Rcpp::depends(RcppArmadillo)]]
+
+using std::log;
+using std::exp;
+using std::max;
+using std::min;
+using std::abs;
+using std::sqrt;
+using std::pow;
+using namespace Rcpp; 
+
+void R_init_markovchain(DllInfo* info) {
+	R_registerRoutines(info, NULL, NULL, NULL, NULL);
+	R_useDynamicSymbols(info, TRUE);	
+}
+
+extern void dsyev_( char *jobz, char *uplo, int *n, double *a, int *lda,
+                   double *w, double *work, int *lwork, int *info );
+
+const double log2pi = std::log(2.0 * M_PI);
+
+// [[Rcpp::export]]
+arma::vec Mahalanobis(arma::mat x, arma::rowvec center, arma::mat cov){
+    int n = x.n_rows;
+    arma::mat x_cen;
+    x_cen.copy_size(x);
+    for (int i=0; i < n; i++) {
+        x_cen.row(i) = x.row(i) - center;
+    }
+    return sum((x_cen * cov.i()) % x_cen, 1);
+}
+
+// [[Rcpp::export]]
+arma::vec ei(arma::mat M) {
+    return arma::eig_sym(M);
+}
+
+// [[Rcpp::export]]
+arma::vec dmvnorm_arma (arma::mat x,  arma::rowvec mean,  arma::mat sigma){
+    arma::vec distval = Mahalanobis(x, mean, sigma);
+    arma::vec ei_sigma = ei(sigma);
+    double logdet = sum(arma::log(ei_sigma));
+    arma::vec logretval = -((x.n_cols * log2pi + logdet + distval)/2) ;
+    return(logretval);
+}
+
+// [[Rcpp::export]]
+arma::mat rmvnorm_arma(int n,
+                  const arma::vec& mu,
+                  const arma::mat& Sigma) {
+    unsigned int p = Sigma.n_cols;
+    Rcpp::NumericVector draw = Rcpp::rnorm(n*p);
+    arma::mat Z = arma::mat(draw.begin(), n, p, false, true);
+    arma::mat Y = arma::repmat(mu, 1, n).t()+Z * arma::chol(Sigma);
+    return Y;
+}
+
+// **********************************************************//
+//                  Transpose                                //
+// **********************************************************//
+// [[Rcpp::export]]
[…]

### 2018-04-04 code/Montgomery_processing.R

@@ -1,0 +1,82 @@
+source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
+library(lubridate)
+load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')
+Montgomery = Temporal_Email_Data$Montgomery
+email = Montgomery$email_data
+email$timepoints =  as.numeric(as.POSIXct(strptime(email[,1], "%d %b %Y %H:%M:%S")))
+email = email[order(email$timepoints), ]
+edge = list()
+initial =  as.numeric(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S")))
+for (d in 1:nrow(email)) {
+	t_d = email[d, 21] - initial
+	edge[[d]] = list(a_d = email[d,2], r_d = as.numeric(email[d,-c(1:2, 21)]), t_d = t_d)
+}
+
+# construct time covariates Y
+D = length(edge)
+A = length(Montgomery$manager_gender)
+Q = 7
+Y = array(1, dim = c(D,A,Q))
+for (a in 1:A) {
+	Y[,a,2] = 1* (Montgomery$manager_gender[a]=="Female")
+	Y[,a,3] = 1* (Montgomery$manager_department[a]=="County Manager")
+}
+timeunit = 3600
+Y[1,,6] = rep(as.numeric(wday(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
+Y[1,,7] = rep(pm(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))), A)
+for (d in 2:D) {
+	index = which(email$timepoints >= email$timepoints[d-1]-3*24*timeunit & email$timepoints < email$timepoints[d])
+	sent = email[index, 2]
+	received = email[index, 3:(2+A)]
+	Y[d, ,4] = tabulate(sent, A) 
+	Y[d, ,5] = colSums(received)
+	Y[d,,6] = rep(as.numeric(wday(as.POSIXct(strptime(email[d-1,1], "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
+	Y[d,,7] = rep(as.numeric(pm(as.POSIXct(strptime(email[d-1,1], "%d %b %Y %H:%M:%S")))), A)
+}
+
+
+send = function(data, a, r) {
[…]

### 2018-04-04 code/Multicast.R

@@ -3,7 +3,7 @@ library(combinat)
 library(mvtnorm)
 library(MCMCpack)
 library(Rcpp)
-sourceCpp('/Users/bomin8319/Desktop/MulticastNetwork/GiR/Multicast_rcpp.cpp')
+sourceCpp('/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast_rcpp.cpp')
 
 gibbs.measure.support = function(n) {
 	gibbs.support = rbind(rep(1, n))
@@ -16,7 +16,6 @@ gibbs.measure.support = function(n) {
 }
 
 r.gibbs.measure <- function(lambda.i, support) {
-	#gibbsNormalizer = prod(exp(delta+lambda.i)+1)-1
 	logitNumerator = vapply(1:nrow(support), function(s) {
 		sum(lambda.i*support[s,])
 		}, c(1))		
@@ -79,25 +78,14 @@ GiR_PP_Plots = function(Forward_stats, Backward_stats) {
                 x = 0.65, y = 0.15, cex = 0.4)
   }
 }      
- 
-lambda_cal = function(X, beta, delta) {
-	D = dim(X)[1]
-	A = dim(X)[2]
-	lambda = list()
-	for (d in 1:D) {
-		lambda[[d]] = lambda_cpp(X[d,,,], beta, delta)
-	}			
-	return(lambda)
-}  
 
-
-Generate = function(D, A, beta, delta, eta, sigma2, X, Y, support, timeunit = 3600) {
+Generate = function(D, A, beta, eta, sigma2, X, Y, support, timeunit = 3600) {
 	P = length(beta)
 	Q = length(eta)
 	u = list()
 	data = list()
 	t_d = 0
-	lambda = lambda_cal(X, beta, delta)
+	lambda = lapply(1:D, function(d) lambda_cpp(X[d,,,], beta))
 	mu = mu_cpp(Y, eta)
 	for (d in 1:D) {
 		u[[d]] = matrix(0, A, A)
@@ -110,48 +98,53 @@ Generate = function(D, A, beta, delta, eta, sigma2, X, Y, support, timeunit = 36
 		t_d = t_d + min(tau) * timeunit
 		data[[d]] = list(a_d = a_d, r_d = r_d, t_d = t_d)
 	}
-	return(list(data = data, u = u, beta = beta, delta = delta, eta = eta, sigma2 = sigma2, X = X, Y = Y))
[…]

### 2018-04-04 code/Multicast_rcpp.cpp

@@ -1,0 +1,230 @@
+#include <RcppArmadillo.h>
+#include <cmath>
+#include <Rinternals.h>
+#include <R_ext/Rdynload.h>
+// [[Rcpp::depends(RcppArmadillo)]]
+
+using std::log;
+using std::exp;
+using std::max;
+using std::min;
+using std::abs;
+using std::sqrt;
+using std::pow;
+using namespace Rcpp; 
+
+void R_init_markovchain(DllInfo* info) {
+	R_registerRoutines(info, NULL, NULL, NULL, NULL);
+	R_useDynamicSymbols(info, TRUE);	
+}
+
+extern void dsyev_( char *jobz, char *uplo, int *n, double *a, int *lda,
+                   double *w, double *work, int *lwork, int *info );
+
+const double log2pi = std::log(2.0 * M_PI);
+
+// [[Rcpp::export]]
+arma::vec Mahalanobis(arma::mat x, arma::rowvec center, arma::mat cov){
+    int n = x.n_rows;
+    arma::mat x_cen;
+    x_cen.copy_size(x);
+    for (int i=0; i < n; i++) {
+        x_cen.row(i) = x.row(i) - center;
+    }
+    return sum((x_cen * cov.i()) % x_cen, 1);
+}
+
+// [[Rcpp::export]]
+arma::vec ei(arma::mat M) {
+    return arma::eig_sym(M);
+}
+
+// [[Rcpp::export]]
+arma::vec dmvnorm_arma (arma::mat x,  arma::rowvec mean,  arma::mat sigma){
+    arma::vec distval = Mahalanobis(x, mean, sigma);
+    arma::vec ei_sigma = ei(sigma);
+    double logdet = sum(arma::log(ei_sigma));
+    arma::vec logretval = -((x.n_cols * log2pi + logdet + distval)/2) ;
+    return(logretval);
+}
+
+// [[Rcpp::export]]
+arma::mat rmvnorm_arma(int n,
+                  const arma::vec& mu,
+                  const arma::mat& Sigma) {
+    unsigned int p = Sigma.n_cols;
+    Rcpp::NumericVector draw = Rcpp::rnorm(n*p);
+    arma::mat Z = arma::mat(draw.begin(), n, p, false, true);
+    arma::mat Y = arma::repmat(mu, 1, n).t()+Z * arma::chol(Sigma);
+    return Y;
+}
+
+// **********************************************************//
+//                  Transpose                                //
+// **********************************************************//
+// [[Rcpp::export]]
[…]

### 2018-04-04 pkg/R/core.R

@@ -248,11 +248,7 @@ Inference = function(edge, node, sigma.Q, prior.b, prior.delta, prior.eta, prior
     }
      prior.old3 = log(dinvgamma(sigma_tau, prior.tau[1], prior.tau[2]))
      post.old3 = post.old2
-     for (inner in 1:Inner[3]) {
-      #sigma_tau.new = rtruncnorm(1, 0, Inf, sigma_tau, sqrt(sigma.Q[3]))
-      #while (sigma_tau.new > 10) {
-      #	sigma_tau.new = rtruncnorm(1, 0, Inf, sigma_tau, sqrt(sigma.Q[3]))
-      #}	
+     for (inner in 1:Inner[3]) {	
       sigma_tau.new = exp(rnorm(1, log(sigma_tau), sqrt(sigma.Q[3])))
       prior.new3 = log(dinvgamma(sigma_tau.new, prior.tau[1], prior.tau[2]))
       post.new3 =  Timepartsum(mu, sqrt(sigma_tau.new), senders[edge.trim], timeinc[edge.trim])

### 2018-04-11 TIES/TIES.R
change of time interval to one week

@@ -1,28 +1,36 @@
 library(readxl)
 TIES<-as.data.frame(read_excel("/Users/bomin8319/Desktop/MulticastNetwork/TIES/TIESv4.xls", col_names = TRUE))
 time = as.numeric(TIES[,1])
+time = sapply(time, function(x) substr(x, 1, nchar(x)-2))
 
-sender = c(cbind(TIES$sender1, TIES$sender2, TIES$sender3, TIES$sender4, TIES$sender5))
-sender = sender[-which(is.na(sender))] #105 unique senders
+senders = cbind(TIES$sender1, TIES$sender2, TIES$sender3, TIES$sender4, TIES$sender5)
+senders[which(is.na(senders[,1])),1] = 2000
+sender = c(senders)
+
+sender = sender[-which(is.na(sender))] #106 unique senders
 receiver = TIES$targetstate #169 unique targets
 
-node = sort(unique(union(sender, receiver))) #175 unique countries 
+node = sort(as.numeric(unique(union(sender, receiver)))) #176 unique nodes 
 
 COW = read.csv("/Users/bomin8319/Desktop/MulticastNetwork/TIES/COW country codes.csv")
 COW = unique(COW)
-node2 = cbind(node[-175], COW[which(COW$CCode %in% node), c(1,3)])
+
+node2 = cbind(sort(as.numeric(node[-c(175, 176)])), COW[which(COW$CCode %in% node), c(1,3)])
 node2 = as.matrix(node2)
 node2 = rbind(node2, c(1000, "EEC/EU", "European Economic Community/European Union"))
+node2 = rbind(node2, c(2000, "II", "International Institution"))
 node = as.data.frame(node2)
 colnames(node)[1] = "COWcode"
 rownames(node) = NULL
-node = data.frame(ID = 1:175, node)
+node = data.frame(ID = 1:176, node)
 node[,2] =  as.numeric(as.character(node[,2]))
 TIES <- cbind(TIES$caseid, TIES$sender1, TIES$sender2, TIES$sender3, TIES$sender4, TIES$sender5, TIES$targetstate)
 TIES[,1] = sapply(TIES[,1], function(x) substr(x, 1, nchar(x)-2))
+TIES[which(is.na(TIES[,2])),2] = rep(2000, sum(is.na(TIES[,2])))
+
[…]

### 2018-04-11 TIES/TIES_EDA.R

@@ -1,0 +1,49 @@
+library(readxl)
+TIES_raw <-as.data.frame(read_excel("/Users/bomin8319/Desktop/MulticastNetwork/TIES/TIESv4.xls", col_names = TRUE))
+
+
+######Below generates node (Line 6 - 22)#####
+senders = cbind(TIES_raw$sender1, TIES_raw$sender2, TIES_raw$sender3, TIES_raw$sender4, TIES_raw$sender5)
+senders[which(is.na(senders[,1])),1] = 2000
+sender = c(senders)
+sender = sender[-which(is.na(sender))] #106 unique senders
+receiver = TIES_raw$targetstate #169 unique targets
+node = sort(as.numeric(unique(union(sender, receiver)))) #176 unique nodes 
+COW = read.csv("/Users/bomin8319/Desktop/MulticastNetwork/TIES/COW country codes.csv")
+COW = unique(COW)
+node2 = cbind(sort(as.numeric(node[-c(175, 176)])), COW[which(COW$CCode %in% node), c(1,3)])
+node2 = as.matrix(node2)
+node2 = rbind(node2, c(1000, "EEC/EU", "European Economic Community/European Union"))
+node2 = rbind(node2, c(2000, "II", "International Institution"))
+node = as.data.frame(node2)
+colnames(node)[1] = "COWcode"
+rownames(node) = NULL
+node = data.frame(ID = 1:176, node)
+node[,2] =  as.numeric(as.character(node[,2]))
+############################################
+head(node)
+
+
+#####Below generates edges (Line 27 - 35)########
+TIES <- cbind(TIES_raw$caseid, TIES_raw$sender1, TIES_raw$sender2, TIES_raw$sender3, TIES_raw$sender4, TIES_raw$sender5, TIES_raw$targetstate)
+TIES[,1] = sapply(TIES[,1], function(x) substr(x, 1, nchar(x)-2))
+TIES[which(is.na(TIES[,2])),2] = rep(2000, sum(is.na(TIES[,2])))
+TIES[209, 1] = "19650630"  #one weird date which has June 31th -> fix to 30th
+TIES = as.data.frame(TIES)
+TIES[,1] = as.character(TIES[,1])
+TIES$time = vapply(TIES[,1], function(x) as.numeric(strptime(x, format = "%Y%m%d")), c(1))
+TIES = TIES[-which(is.na(TIES$time)),] #delete unknown dates
+colnames(TIES) = c("date", "sender1", "sender2", "sender3", "sender4", "sender5", "target", "unixtime")
[…]

### 2018-04-11 code/Montgomery_PPC.R

@@ -1,0 +1,55 @@
+source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
+library(lubridate)
+load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')
+Montgomery = Temporal_Email_Data$Montgomery
+email = Montgomery$email_data
+email = unique(email)
+email$timepoints =  as.numeric(as.POSIXct(strptime(email[,1], "%d %b %Y %H:%M:%S")))
+email = email[order(email$timepoints), ]
+edge = list()
+initialtime =  as.numeric(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S")))
+for (d in 1:nrow(email)) {
+	t_d = email[d, 21] - initialtime
+	edge[[d]] = list(a_d = email[d,2], r_d = as.numeric(email[d,-c(1:2, 21)]), t_d = t_d)
+}
+A = length(Montgomery$manager_gender)
+
+#observed statistics
+timeunit = 3600
+trim = which(email$timepoints >=3*24*timeunit+email$timepoints[1])
+
+indegree = tabulate(email[trim,2], A)
+outdegree = colSums(email[trim,3:20])
+recipients = tabulate(rowSums(email[trim,3:20]), A-1)
+timeinc = diff(email$timepoints[21:max(trim)])
+
+indegreedist = matrix(NA, 50, A)
+outdegreedist = matrix(NA, 50, A)
+recipientsdist = matrix(NA, 50, A-1)
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/code/PPC")
+for (n in 1:50) {
+	filename = paste0("Montgomery_PPC", n,".RData")
+	load(filename)
+	indegreedist[n, ] = tabulate(vapply(1:642, function(x) Montgomery_PPC[[x]]$a_d, c(1)), A)
+	outdegreedist[n, ] = rowSums(sapply(1:642, function(x) Montgomery_PPC[[x]]$r_d))
+	recipientsdist[n, ] = tabulate(vapply(1:642, function(x) sum(Montgomery_PPC[[x]]$r_d), c(1)), A-1)
+} 
+
+par(mfrow = c(3,1))
+
+boxplot(indegreedist)
+lines(indegree, col = 2)
+
+boxplot(outdegreedist)
+lines(outdegree, col = 2)
+
+boxplot(recipientsdist)
+lines(recipients, col = 2)
+
+
+
[…]

### 2018-04-11 code/Montgomery_processing.R

@@ -26,7 +26,7 @@ timeunit = 3600
 Y[1,,6] = rep(as.numeric(wday(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
 Y[1,,7] = rep(pm(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))), A)
 for (d in 2:D) {
-	index = which(email$timepoints >= email$timepoints[d-1]-3*24*timeunit & email$timepoints < email$timepoints[d])
+	index = which(email$timepoints >= email$timepoints[d-1]-7*24*timeunit & email$timepoints < email$timepoints[d])
 	sent = email[index, 2]
 	received = email[index, 3:(2+A)]
 	Y[d, ,4] = tabulate(sent, A) 
@@ -48,7 +48,7 @@ X = array(0, dim = c(D,A,A,P))
 X[,,,1] = 1
 timeunit = 3600
 for (d in 2:D) {
-	index = which(email$timepoints >= email$timepoints[d-1]-3*24*timeunit & email$timepoints < email$timepoints[d])
+	index = which(email$timepoints >= email$timepoints[d-1]-7*24*timeunit & email$timepoints < email$timepoints[d])
 	data = email[index, ]
 	sent = data[, 2]
 	received = data[, 3:(2+A)]
@@ -80,7 +80,7 @@ prior.beta = list(mean = c(-3, rep(0, P-1)), var = 2*diag(P))
 prior.eta = list(mean = c(5, rep(0, Q-1)), var = 2*diag(Q))
 prior.sigma2 = list(a = 2, b = 1)
 email$timepoints =  as.numeric(as.POSIXct(strptime(email[,1], "%d %b %Y %H:%M:%S")))
-trim = which(email$timepoints >=3*24*timeunit+email$timepoints[1])
+trim = which(email$timepoints >=7*24*timeunit+email$timepoints[1])
 edge = edge[trim]
 X = X[trim,,,]
 Y = Y[trim,,]
@@ -89,13 +89,17 @@ Montgomery_infer = Inference(edge, X, Y, 55000, c(5,1,1), 15000, prior.beta, pri
 
 save(Montgomery_infer, file = "Montgomery_infer.RData")
 
+load("/Users/bomin8319/Desktop/MulticastNetwork/code/Montgomery_infer.RData")
 initial = list()
[…]

### 2018-04-11 code/Multicast.R

@@ -126,7 +126,7 @@ PPC = function(D, A, beta, eta, sigma2, X, Y, timeunit = 3600, lasttime, u, init
   time = as.numeric(as.POSIXct(strptime(initial$time, "%d %b %Y %H:%M:%S")))
   for (d in 1:D) {
     if (d %% 10 == 0) print(d)
-    index = which(time >= t_d-3*24*timeunit & time <= t_d)
+    index = which(time >= t_d-7*24*timeunit & time <= t_d)
     sent = sender[index]
     received = receiver[index, ]
     outdegree = tabulate(sent, A)

### 2018-04-12 paper/paper.tex
allow tied events

@@
 {
-  \title{\bf A Continuous-time Multicast Network Model}
+  \title{\bf A Continuous-time Multicast \\Network Model}
   \author{Bomin Kim\thanks{
@@
 A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of recipients $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
-For simplicity, we assume that edges are ordered by time such that $t_d < t_{d+1}$.
+For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
 \subsection{Tie Generating Process}\label{subsec: Tie}
@@
 Therefore, it is a sender-driven process in that the recipients and timestamp of an edge is determined by the sender's urgency to send the edge to chosen recipients.
+Note that  our generative process accounts for tied events such that in case of tied events (i.e., multiple senders generated same time increments $\tau_d$), we observe all of the tied events\footnote{The order of tied events do not matter.} .
 	\begin{algorithm}[H]
@@
 				}
+				\textbf{For no tied events,}\\
 				set $a_d= \mbox{argmin}_{a}(\tau_{ad})$\\
 				set $\boldsymbol{r}_d = \boldsymbol{u}_{a_d d}$\\
-				set $t_d =t_{d-1} + \min_a\tau_{ad}$
+				set $t_d =t_{d-1} + \min_a\tau_{ad}$\\\\
+				\textbf{For $n$ tied events,} (i.e., $n$ senders generated same minimum time increments)\\
+				set $a_d, \ldots, a_{d+n}= \mbox{argmin}_{a}(\tau_{ad})$\\
+				set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n}= ,\boldsymbol{u}_{a_{d+n} d}$\\
+				set $t_d, \ldots, t_{d+n}=t_{d-1} + \min_a\tau_{ad}$\\
+				jump to $d = d+n+1$
 			}
@@
 where the two variables share the conditional posterior and thus can be jointly sampled.
-Likewise, assuming uninformative priors on $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$) and $\sigma_{\tau}^2$ (i.e., half-Cauchy($\infty$)), the conditional posterior is
+Likewise, assuming uninformative priors on $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$) and $\sigma_{\tau}^2$ (i.e., half-Cauchy($\infty$)), the conditional posterior for no-tied event case is
 \begin{equation}
@@
 \end{equation}
+Since we assme the existence of tied-event, the conditional posterior of $\boldsymbol{\eta}$ and $\sigma_{\tau}^2$ should be written as
+\begin{equation}
+P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, \sigma_\tau^2) \big)\Big),
+\end{equation}
+where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $D$ events ($M \leq D$). If $M=D$ (i.e., no tied events), Equation (10) reduces to Equation (9).
 
@@
  			}
+ 		}
  		 		\For{n=1 to inner1}{
@@
  		\For{n=1 to inner2}{
- 				update $\boldsymbol{\eta}$ and $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (9)
+ 				update $\boldsymbol{\eta}$ and $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (10)
  		}
  			\For{n=1 to inner3}{
- 				update $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (9)
- 			}
+ 				update $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (10)
  			}
@@
 In the example of email networks, we form the covariate vector $\boldsymbol{x}_{adr}$ using time-varying network statistics based on the time interval prior to and including $t_{d-1}$.
-Along with intercept term, we compute eight network statistics \cite{PerryWolfe2012}, where the time interval tracks 3 days prior to the last email was sent $l_d = (t_{d-1}-96h, t_{d-1}]$.
+Along with intercept term, we compute eight network statistics \cite{PerryWolfe2012}, where the time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{days}, t_{d-1}]$.
 \begin{itemize}

### 2018-04-12 code/Montgomery_processing.R

@@ -91,10 +91,10 @@ save(Montgomery_infer, file = "Montgomery_infer.RData")
 
 load("/Users/bomin8319/Desktop/MulticastNetwork/code/Montgomery_infer.RData")
 initial = list()
-initial$sender = email[1:21, 2]
-initial$receiver = email[1:21, 3:20]
-initial$time = email[1:21,1]
-for (n in 3:100) {
+initial$sender = email[1:(min(trim)-1), 2]
+initial$receiver = email[1:(min(trim)-1), 3:20]
+initial$time = email[1:(min(trim)-1),1]
+for (n in 1:100) {
   Montgomery_PPC = PPC(length(edge), A, colMeans(Montgomery_infer$beta), colMeans(Montgomery_infer$eta), 
                        mean(Montgomery_infer$sigma2), X, Y, timeunit = 3600, lasttime = email[min(trim-1), 21], 
                        Montgomery_infer$u, initial =initial)

### 2018-04-25 paper/paper.tex
code in pkg format

@@
 	\begin{algorithmic}
-		\STATE \textbf{Input}: number of new data to generate $R$,\\
+		\STATE \textbf{Input}: number of new data to generate $R$, covariates $\boldsymbol{x}$ and $\boldsymbol{y}$\\
 		estimated latent variables $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta},  \sigma_\tau^2)$\\
@@
 		\FOR{$d = 1$ {\bfseries to}  $D$} 
-		\STATE  Compute $\boldsymbol{x}_{d}$ and $\boldsymbol{y}_{d}$ given $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{[1:(d-1)]}$
 		\STATE	Draw ($a_{d}$, $\boldsymbol{r}_{d}$, $t_{d}$) following Section \ref{sec:generative process}\\

### 2018-04-25 Lab/Untitled.R

@@ -1,0 +1,35 @@
+#install the package from Github
+library(devtools)
+install_github("desmarais-lab/MulticastNetwork/pkg")
+
+#generate synthetic data
+
+
+
+
+#load our Montgomery county email data
+load("/Users/bomin8319/Box/gainlab_example/Bomin/Montgomery.RData")
+
+#data including sender a_d, reciever vector r_d, timestamp t_d
+edge = Montgomery$edge
+head(edge)
+
+#covariates affecting "who sends to whom"
+X = Montgomery$X
+head(X[100, 1, , ])
+ 
+#covariates affecting "when to send"
+Y = Montgomery$Y
+head(Y[100, , ])
+
+#run inference to estimate beta, eta, u, and sigma2
+prior.beta = list(mean = rep(0, P), var = 2*diag(P))
+prior.eta = list(mean = rep(0, Q), var = 2*diag(Q))
+prior.sigma2 = list(a = 2, b = 1)
+
+outer = 100
+inner = c(1, 1, 1)
+burn = 0
+
+Montgomery_infer = Inference(edge, X, Y, outer, inner, burn, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
+		  proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = , timedist = "lognormal")

### 2018-04-25 code/Caldwell.R

@@ -1,0 +1,83 @@
+for (i in 1:17) {
+ print(dim(Temporal_Email_Data[[i]]$email_data))
+}
+
+
+#Caldwell email data
+Caldwell_email = unique(Temporal_Email_Data[[2]]$email_data)
+time = as.numeric(as.POSIXct(strptime(Caldwell_email[,1], "%d %b %Y %H:%M:%S")))
+Caldwell_email = Caldwell_email[order(time),]
+
+email = Caldwell_email
+
+edge = list()
+initialtime =  as.numeric(as.POSIXct(strptime("01 Jan 2012 00:00:00", "%d %b %Y %H:%M:%S")))
+for (d in 1:nrow(email)) {
+	t_d = as.numeric(as.POSIXct(strptime(Caldwell_email[d,1], "%d %b %Y %H:%M:%S")))
+	edge[[d]] = list(a_d = email[d,2], r_d = as.numeric(email[d,-c(1:2)]), t_d = t_d)
+}
+
+library(lubridate)
+uniqtime = unique(time[order(time)])
+
+# construct time covariates Y
+D = length(edge)
+A = length(Caldwell$manager_gender)
+Q = 7
+Y = array(1, dim = c(D,A,Q))
+for (a in 1:A) {
+	Y[,a,2] = 1* (Caldwell$manager_gender[a]=="Female")
+	Y[,a,3] = 1* (Caldwell$manager_department[a]=="County Manager")
+}
+timeunit = 3600
+Y[1,,6] = rep(as.numeric(wday(as.POSIXct(strptime("01 Jan 2012 00:00:00", "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
+Y[1,,7] = rep(pm(as.POSIXct(strptime("01 Jan 2012 00:00:00", "%d %b %Y %H:%M:%S"))), A)
+for (d in 2:D) {
+	index = which(uniqtime >= uniqtime[which(uniqtime==uniqtime[d])-1]-7*24*timeunit & uniqtime < uniqtime[d])
+	sent = email[index, 2]
+	received = email[index, 3:(2+A)]
+	Y[d, ,4] = tabulate(sent, A) 
+	Y[d, ,5] = colSums(received)
+	Y[d,,6] = rep(as.numeric(wday(as.POSIXct(strptime(email[d-1,1], "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
[…]

### 2018-04-25 code/Montgomery_PPC.R

@@ -28,7 +28,7 @@ indegreedist = matrix(NA, 500, A)
 outdegreedist = matrix(NA,  500, A)
 recipientsdist = matrix(NA,  500, A-1)
 timedist = matrix(NA, 500, 621)
-setwd("/Users/bomin8319/Desktop/MulticastNetwork/code/PPC")
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/code")
 for (n in 1:500) {
 	filename = paste0("Montgomery_PPCnew", n,".RData")
 	load(filename)
@@ -49,8 +49,8 @@ lines(outdegree, col = 2)
 boxplot(indegreedist,ylim = c(0, 275),  main = "indegree")
 lines(indegree, col = 2)
 
-boxplot(recipientsdist, ylim = c(0, 515),  main = "receiver size")
-lines(recipients, col = 2)
+boxplot(recipientsdist[,1:14], ylim = c(0, 515),  main = "receiver size")
+lines(recipients[1:14], col = 2)
 
 
 hi = quantile(c(timedist[,-1]), c(.025, .975 ))

### 2018-04-25 code/Montgomery_PPE.R

@@ -86,21 +86,29 @@ edge = edge[trim]
 X = X[trim,,,]
 Y = Y[trim,,]
 
+set.seed(1)
 missing = list()
-
+missing[[1]] = matrix(0, nrow = dim(Y)[1], 1)
+missing[[1]][sample(1:dim(Y)[1], 62, replace = FALSE), ] = 1
+missing[[2]] = matrix(0, nrow = dim(Y)[1], A)
+missing[[2]][sample(1:(dim(Y)[1]*A), 1118, replace = FALSE)] = 1
+missing[[3]] = matrix(0, nrow = dim(Y)[1], 1)
+missing[[3]][sample(1:dim(Y)[1], 62, replace = FALSE), ] = 1
 
 
 load("/Users/bomin8319/Desktop/MulticastNetwork/code/Montgomery_infer.RData")
 initial = list()
-initial$sender = email[1:(min(trim)-1), 2]
-initial$receiver = email[1:(min(trim)-1), 3:20]
-initial$time = email[1:(min(trim)-1),1]
-for (n in 1:100) {
-  Montgomery_PPE = PPC(length(edge), A, colMeans(Montgomery_infer$beta), colMeans(Montgomery_infer$eta), 
-                       mean(Montgomery_infer$sigma2), X, Y, timeunit = 3600, lasttime = email[min(trim-1), 21], 
-                       Montgomery_infer$u, initial =initial)
-  filename = paste0("Montgomery_PPC", n,".RData")
-  save(Montgomery_PPC, file = filename)
+initial$beta = colMeans(Montgomery_infer$beta)
+initial$eta =  colMeans(Montgomery_infer$eta)
+initial$u = Montgomery_infer$u
+initial$sigma2 = mean(Montgomery_infer$sigma2)
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/code/PPE")
+Montgomery_PPE = list()
+for (n in 1:500) {
+	print(n)
+  Montgomery_PPE[[n]] = PPE(edge, missing, X, Y, 50, c(5,5,1), 0, prior.beta, prior.eta, prior.sigma2, initial = initial, proposal.var = c(0.0001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime)
+  filename = paste0("Montgomery_PPE", n,".RData")
+  save(Montgomery_PPE, file = filename)
 }
 
 

### 2018-04-25 code/Montgomery_processing.R

@@ -13,6 +13,7 @@ for (d in 1:nrow(email)) {
 	edge[[d]] = list(a_d = email[d,2], r_d = as.numeric(email[d,-c(1:2, 21)]), t_d = t_d)
 }
 
+uniqtime = unique(email$timepoints)
 # construct time covariates Y
 D = length(edge)
 A = length(Montgomery$manager_gender)
@@ -26,7 +27,7 @@ timeunit = 3600
 Y[1,,6] = rep(as.numeric(wday(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
 Y[1,,7] = rep(pm(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))), A)
 for (d in 2:D) {
-	index = which(email$timepoints >= email$timepoints[d-1]-7*24*timeunit & email$timepoints < email$timepoints[d])
+	index = which(email$timepoints >= uniqtime[which(uniqtime==email$timepoints[d])-1]-7*24*timeunit & email$timepoints < email$timepoints[d])
 	sent = email[index, 2]
 	received = email[index, 3:(2+A)]
 	Y[d, ,4] = tabulate(sent, A) 
@@ -43,12 +44,12 @@ sendraw = function(data, a, r) {
 # construct recipient covariates X
 D = length(edge)
 A = length(Montgomery$manager_gender)
-P = 9
+P = 11
 X = array(0, dim = c(D,A,A,P))
 X[,,,1] = 1
 timeunit = 3600
 for (d in 2:D) {
-	index = which(email$timepoints >= email$timepoints[d-1]-7*24*timeunit & email$timepoints < email$timepoints[d])
+	index = which(email$timepoints >= uniqtime[which(uniqtime==email$timepoints[d])-1]-7*24*timeunit & email$timepoints < email$timepoints[d])
 	data = email[index, ]
 	sent = data[, 2]
 	received = data[, 3:(2+A)]
@@ -71,34 +72,39 @@ for (d in 2:D) {
 				})) / 10
 			X[d, a, r, 9] = sum(sapply(c(1:A)[-c(a,r)], function(h) {
 				sendraw(data, a, h) * sendraw(data, r, h)
-				}))	/10		
+				}))	/10	
 		}
+	  X[d, a, , 10] = ifelse(outdegree[a] > 0, sum(X[d,a,,4]), 0)
[…]

### 2018-04-25 code/Montgomery_processing2.R

@@ -1,108 +1,0 @@
-source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
-library(lubridate)
-load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')
-Montgomery = Temporal_Email_Data$Montgomery
-email = Montgomery$email_data
-email = unique(email)
-email$timepoints =  as.numeric(as.POSIXct(strptime(email[,1], "%d %b %Y %H:%M:%S")))
-email = email[order(email$timepoints), ]
-edge = list()
-initialtime =  as.numeric(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S")))
-for (d in 1:nrow(email)) {
-	t_d = email[d, 21] - initialtime
-	edge[[d]] = list(a_d = email[d,2], r_d = as.numeric(email[d,-c(1:2, 21)]), t_d = t_d)
-}
-
-uniqtime = unique(email$timepoints)
-# construct time covariates Y
-D = length(edge)
-A = length(Montgomery$manager_gender)
-Q = 7
-Y = array(1, dim = c(D,A,Q))
-for (a in 1:A) {
-	Y[,a,2] = 1* (Montgomery$manager_gender[a]=="Female")
-	Y[,a,3] = 1* (Montgomery$manager_department[a]=="County Manager")
-}
-timeunit = 3600
-Y[1,,6] = rep(as.numeric(wday(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
-Y[1,,7] = rep(pm(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))), A)
-for (d in 2:D) {
-	index = which(email$timepoints >= uniqtime[which(uniqtime==email$timepoints[d])-1]-7*24*timeunit & email$timepoints < email$timepoints[d])
-	sent = email[index, 2]
-	received = email[index, 3:(2+A)]
-	Y[d, ,4] = tabulate(sent, A) 
-	Y[d, ,5] = colSums(received)
-	Y[d,,6] = rep(as.numeric(wday(as.POSIXct(strptime(email[d-1,1], "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
[…]

### 2018-04-25 code/Multicast.R

@@ -184,8 +184,8 @@ Inference = function(data, X, Y, outer, inner, burn, prior.beta, prior.eta, prio
 	
 	if (length(initial) > 0) {
 		u = initial$u
-		beta = initial$beta
-		eta = initial$eta
+		beta = matrix(initial$beta, nrow = 1)
+		eta = matrix(initial$eta, nrow = 1)
 		sigma2 = initial$sigma2
 	} else {
 		u = lapply(1:D, function(d) matrix(0, A, A))
@@ -209,14 +209,14 @@ Inference = function(data, X, Y, outer, inner, burn, prior.beta, prior.eta, prio
 		for (d in 1:D) {
 		  u[[d]][senders[d],] = data[[d]][[2]]
 		}
-		  prior.old1 = dmvnorm_arma(beta, prior.beta$mean, prior.beta$var)
+		prior.old1 = dmvnorm_arma(beta, prior.beta$mean, prior.beta$var)
     	post.old1 = Edgepartsum(lambda, u)
     	for (i1 in 1:inner[1]) {
 			beta.new = rmvnorm_arma(1, beta, proposal.var[1]*diag(P))
-     	prior.new1 = dmvnorm_arma(beta.new, prior.beta$mean, prior.beta$var)
+     		prior.new1 = dmvnorm_arma(beta.new, prior.beta$mean, prior.beta$var)
 			lambda = lapply(1:D, function(d) lambda_cpp(X[d,,,], beta.new))
 			post.new1 = Edgepartsum(lambda, u)
-      loglike.diff = prior.new1+post.new1-prior.old1-post.old1
+      		loglike.diff = prior.new1+post.new1-prior.old1-post.old1
 			if (log(runif(1, 0, 1)) < loglike.diff) {
         			beta = beta.new
         			prior.old1 = prior.new1
@@ -224,14 +224,14 @@ Inference = function(data, X, Y, outer, inner, burn, prior.beta, prior.eta, prio
 	      	}
 		}
 		prior.old2 = dmvnorm_arma(eta, prior.eta$mean, prior.eta$var) 
-    mu = mu_cpp(Y, eta)
-    post.old2 = Timepartsum(mu, sqrt(sigma2), senders, timeinc)
+    	mu = mu_cpp(Y, eta)
+    	post.old2 = Timepartsum(mu, sqrt(sigma2), senders, timeinc)
 		for (i2 in 1:inner[2]) {
 			eta.new = rmvnorm_arma(1, eta, proposal.var[2]*diag(Q))
[…]

### 2018-04-25 pkg/R/Multicast.R

@@ -1,0 +1,508 @@
+#' @useDynLib MulticastNetwork
+#' @import stats
+#' @import grDevices
+#' @import graphics
+#' @import RcppArmadillo
+#' @importFrom Rcpp sourceCpp
+#' @importFrom combinat permn
+#' @importFrom lubridate wday hour
+#' @importFrom MCMCpack rinvgamma dinvgamma
+
+
+#' @title gibbs.measure.support
+#' @description List out the support of Gibbs measure
+#'
+#' @param n length of the vector to be sampled
+#'
+#' @return a 2^n x n binary matrix representing the support of the binary Gibbs measure in n elements
+#'
+#' @export
+gibbs.measure.support = function(n) {
+	gibbs.support = rbind(rep(1, n))
+	for(i in 1:(n-1)){
+		gibbs.mat.i = do.call('rbind',permn(c(rep(1, i), rep(0, n-i))))
+		gibbs.support = rbind(gibbs.support, gibbs.mat.i)
+	}
+	out = as.matrix(unique(gibbs.support))
+	return(out)
+}
+
+#' @title r.gibbs.measure
+#' @description Sample a binary vector from Gibbs measure
+#'
+#' @param lambda.i lambda of sender i
+#' @param support support of Gibbs measure
+#'
+#' @return nsamp number of samples with each row denoting binary vector
+#'
+#' @export
+r.gibbs.measure <- function(lambda.i, support) {
+	logitNumerator = vapply(1:nrow(support), function(s) {
+		sum(lambda.i*support[s,])
+		}, c(1))		
+	samp = multinom_vec(exp(logitNumerator))
+	return(support[samp,])	
+}
+
+
+#' @title dinvgamma
+#' @description log of inverse-gamma pdf
+#'
+#' @param x Scalar location to evaluate density
+#' @param shape Scalar shape parameter
+#' @param scale Scalar shape parameter
+#'
+#' @return evaluate the density at x
+#'
+#' @export
+dinvgamma = function(x, shape, scale) {
+    alpha <- shape
+    beta <- scale
+    log.density <- alpha * log(beta) - lgamma(alpha) - (alpha + 
+        1) * log(x) - (beta/x)
+    return(log.density)
+}
+
+
+#' @title GiR_PP_Plots
+#' @description Generate PP-plots (probability-probability plot) for Gettig it Right test
+#'
+#' @param Forward_stats statistics obtained from forward sampling
[…]

### 2018-04-25 pkg/R/RcppExports.R

@@ -1,10 +1,6 @@
 # Generated by using Rcpp::compileAttributes() -> do not edit by hand
 # Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
 
-sortuniq <- function(x) {
-    .Call('_MulticastNetwork_sortuniq', PACKAGE = 'MulticastNetwork', x)
-}
-
 Mahalanobis <- function(x, center, cov) {
     .Call('_MulticastNetwork_Mahalanobis', PACKAGE = 'MulticastNetwork', x, center, cov)
 }
@@ -21,123 +17,55 @@ rmvnorm_arma <- function(n, mu, Sigma) {
     .Call('_MulticastNetwork_rmvnorm_arma', PACKAGE = 'MulticastNetwork', n, mu, Sigma)
 }
 
-priorsum <- function(var, mu, x) {
-    .Call('_MulticastNetwork_priorsum', PACKAGE = 'MulticastNetwork', var, mu, x)
+transpose <- function(x) {
+    .Call('_MulticastNetwork_transpose', PACKAGE = 'MulticastNetwork', x)
 }
 
 tabulateC <- function(x, max) {
     .Call('_MulticastNetwork_tabulateC', PACKAGE = 'MulticastNetwork', x, max)
 }
 
-transpose <- function(x) {
-    .Call('_MulticastNetwork_transpose', PACKAGE = 'MulticastNetwork', x)
-}
-
-callRMultinom <- function(x) {
-    .Call('_MulticastNetwork_callRMultinom', PACKAGE = 'MulticastNetwork', x)
-}
-
-multinom_vec <- function(nSample, props) {
-    .Call('_MulticastNetwork_multinom_vec', PACKAGE = 'MulticastNetwork', nSample, props)
-}
-
-which_int <- function(value, x) {
-    .Call('_MulticastNetwork_which_int', PACKAGE = 'MulticastNetwork', value, x)
-}
-
-which_num <- function(value, x) {
-    .Call('_MulticastNetwork_which_num', PACKAGE = 'MulticastNetwork', value, x)
-}
-
-rdirichlet_cpp <- function(num_samples, alpha_m) {
-    .Call('_MulticastNetwork_rdirichlet_cpp', PACKAGE = 'MulticastNetwork', num_samples, alpha_m)
-}
-
-which_cpp <- function(value, x) {
[…]

### 2018-04-25 pkg/R/core.R

@@ -1,625 +1,0 @@
-#' @useDynLib MulticastNetwork
-#' @import stats
-#' @import grDevices
-#' @import graphics
-#' @import RcppArmadillo
-#' @importFrom Rcpp sourceCpp
-#' @importFrom reshape melt
-#' @importFrom coda mcmc geweke.diag
-#' @importFrom combinat permn
-#' @importFrom mgcv uniquecombs
-#' @importFrom lubridate wday hour
-#' @importFrom LaplacesDemon dhalfcauchy rhalfcauchy
-#' @importFrom truncnorm rtruncnorm dtruncnorm
-#' @importFrom MCMCpack rinvgamma dinvgamma
-
-tvapply = function(...) transpose(vapply(...))
-
-#' @title gibbs.measure.support
-#' @description List out the support of Gibbs measure
-#'
-#' @param n length of the vector to be sampled 
-#'
-#' @return  a 2^n x n binary matrix representing the support of the binary Gibbs measure in n elements
-#'
-#' @export
-gibbs.measure.support = function(n) {
-	gibbs.support = rbind(rep(1, n))
-	for(i in 1:(n-1)){
-		gibbs.mat.i = do.call('rbind',permn(c(rep(1, i), rep(0, n-i))))
-		gibbs.support = rbind(gibbs.support, gibbs.mat.i)
-	}
-	out = as.matrix(unique(gibbs.support))
-	return(out)
-}
-
-#' @title r.gibbs.measure
-#' @description List out the support of Gibbs measure
-#'
-#' @param lambda.i a vector of coefficients according to which each element
-#' @param delta a positive real valued parameter that controls the density penalty 
-#' @param support support of Gibbs measure
-#'
-#' @return nsamp number of samples with each row denoting binary vector
-#'
-#' @export
-r.gibbs.measure <- function(lambda.i, delta, support) {
-	#gibbsNormalizer = prod(exp(delta+lambda.i)+1)-1
-	logitNumerator = vapply(1:nrow(support), function(s) {
-		sum((delta+lambda.i)*support[s,])
-		}, c(1))		
-	samp = lmultinom(logitNumerator)
-	return(support[samp,])	
-}
-
-#' @title adaptive.MH 
-#' @description adaptive Metropolis Hastings to maintain target acceptance rate
-#'
-#' @param sigma.Q proposal distribution variance parameter
[…]

### 2018-04-25 pkg/src/RcppExports.cpp

@@ -6,17 +6,6 @@
 
 using namespace Rcpp;
 
-// sortuniq
-NumericVector sortuniq(NumericVector x);
-RcppExport SEXP _MulticastNetwork_sortuniq(SEXP xSEXP) {
-BEGIN_RCPP
-    Rcpp::RObject rcpp_result_gen;
-    Rcpp::RNGScope rcpp_rngScope_gen;
-    Rcpp::traits::input_parameter< NumericVector >::type x(xSEXP);
-    rcpp_result_gen = Rcpp::wrap(sortuniq(x));
-    return rcpp_result_gen;
-END_RCPP
-}
 // Mahalanobis
 arma::vec Mahalanobis(arma::mat x, arma::rowvec center, arma::mat cov);
 RcppExport SEXP _MulticastNetwork_Mahalanobis(SEXP xSEXP, SEXP centerSEXP, SEXP covSEXP) {
@@ -67,16 +56,14 @@ BEGIN_RCPP
     return rcpp_result_gen;
 END_RCPP
 }
-// priorsum
-double priorsum(arma::mat var, arma::rowvec mu, arma::mat x);
-RcppExport SEXP _MulticastNetwork_priorsum(SEXP varSEXP, SEXP muSEXP, SEXP xSEXP) {
+// transpose
+arma::mat transpose(arma::mat x);
+RcppExport SEXP _MulticastNetwork_transpose(SEXP xSEXP) {
 BEGIN_RCPP
     Rcpp::RObject rcpp_result_gen;
     Rcpp::RNGScope rcpp_rngScope_gen;
-    Rcpp::traits::input_parameter< arma::mat >::type var(varSEXP);
-    Rcpp::traits::input_parameter< arma::rowvec >::type mu(muSEXP);
     Rcpp::traits::input_parameter< arma::mat >::type x(xSEXP);
-    rcpp_result_gen = Rcpp::wrap(priorsum(var, mu, x));
+    rcpp_result_gen = Rcpp::wrap(transpose(x));
     return rcpp_result_gen;
 END_RCPP
 }
@@ -89,327 +76,6 @@ BEGIN_RCPP
     Rcpp::traits::input_parameter< const IntegerVector& >::type x(xSEXP);
     Rcpp::traits::input_parameter< const signed >::type max(maxSEXP);
     rcpp_result_gen = Rcpp::wrap(tabulateC(x, max));
-    return rcpp_result_gen;
-END_RCPP
-}
-// transpose
-arma::mat transpose(arma::mat x);
[…]

### 2018-04-25 pkg/src/sampler.cpp

@@ -1,662 +1,0 @@
-#include <RcppArmadillo.h>
-#include <cmath>
-#include <Rinternals.h>
-#include <R_ext/Rdynload.h>
-// [[Rcpp::depends(RcppArmadillo)]]
-
-using std::log;
-using std::exp;
-using std::max;
-using std::min;
-using std::abs;
-using std::sqrt;
-using std::pow;
-using namespace Rcpp; 
-
-void R_init_markovchain(DllInfo* info) {
-	R_registerRoutines(info, NULL, NULL, NULL, NULL);
-	R_useDynamicSymbols(info, TRUE);	
-}
-
-extern void dsyev_( char *jobz, char *uplo, int *n, double *a, int *lda,
-                   double *w, double *work, int *lwork, int *info );
-
-const double log2pi = std::log(2.0 * M_PI);
-
-// [[Rcpp::export]]
-NumericVector sortuniq (NumericVector x){
-    return sort_unique(x);
-}
-
-// [[Rcpp::export]]
-arma::vec Mahalanobis(arma::mat x, arma::rowvec center, arma::mat cov){
-    int n = x.n_rows;
-    arma::mat x_cen;
-    x_cen.copy_size(x);
-    for (int i=0; i < n; i++) {
-        x_cen.row(i) = x.row(i) - center;
-    }
-    return sum((x_cen * cov.i()) % x_cen, 1);
-}
-// [[Rcpp::export]]
-arma::vec ei(arma::mat M) {
-    return arma::eig_sym(M);
-}
-
-// [[Rcpp::export]]
-arma::vec dmvnorm_arma (arma::mat x,  arma::rowvec mean,  arma::mat sigma){
-    arma::vec distval = Mahalanobis(x, mean, sigma);
-    arma::vec ei_sigma = ei(sigma);
-    double logdet = sum(arma::log(ei_sigma));
-    arma::vec logretval = -((x.n_cols * log2pi + logdet + distval)/2) ;
-    return(logretval);
-}
-
-// [[Rcpp::export]]
-arma::mat rmvnorm_arma(int n,
-                  const arma::vec& mu,
-                  const arma::mat& Sigma) {
-    unsigned int p = Sigma.n_cols;
-    Rcpp::NumericVector draw = Rcpp::rnorm(n*p);
-    arma::mat Z = arma::mat(draw.begin(), n, p, false, true);
-    arma::mat Y = arma::repmat(mu, 1, n).t()+Z * arma::chol(Sigma);
-    return Y;
-}
-
[…]

### 2018-04-25 Lab/pkg_tutorial.R
minor update in code

@@ -2,11 +2,6 @@
 library(devtools)
 install_github("desmarais-lab/MulticastNetwork/pkg")
 
-#generate synthetic data
-
-
-
-
 #load our Montgomery county email data
 load("/Users/bomin8319/Box/gainlab_example/Bomin/Montgomery.RData")
 
@@ -22,6 +17,9 @@ head(X[100, 1, , ])
 Y = Montgomery$Y
 head(Y[100, , ])
 
+#initial history before 7 days
+initial = Montgomery$initial
+
 #run inference to estimate beta, eta, u, and sigma2
 prior.beta = list(mean = rep(0, P), var = 2*diag(P))
 prior.eta = list(mean = rep(0, Q), var = 2*diag(Q))
@@ -32,4 +30,8 @@ inner = c(1, 1, 1)
 burn = 0
 
 Montgomery_infer = Inference(edge, X, Y, outer, inner, burn, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
-		  proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = , timedist = "lognormal")
+		  proposal.var = c(0.001, 0.001, 0.1), timeunit = 3600, lasttime = max(initial$time), timedist = "lognormal")
+
+Montgomery_PPC = PPC(length(edge), beta = colMeans(Montgomery_infer$beta), eta = colMeans(Montgomery_infer$eta), 
+                     sigma2 = mean(Montgomery_infer$sigma2), X, Y, timeunit = 3600, u = Montgomery_infer$u, 
+        			 lasttime = max(initial$time), timedist = "lognormal")

### 2018-04-25 code/Montgomery_processing.R

@@ -90,9 +90,9 @@ Y = Y[trim,,]
 Montgomery_infer = Inference(edge, X, Y, 55000, c(10,1,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
 		  proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "lognormal")
 
-Montgomery = list(edge = edge, X = X, Y = Y, initial = initial)
+Montgomery = list(edge = edge, X = X, Y = Y, lasttime = email[min(trim-1), 21])
 
-save(Montgomery_infer, file = "Montgomery_infer.RData")
+save(Montgomery, file = "Montgomery.RData")
 
 
 load("/Users/bomin8319/Desktop/Montgomery_infer.RData")

### 2018-04-25 pkg/R/Multicast.R

@@ -172,7 +172,6 @@ Generate = function(D, A, beta, eta, sigma2, X, Y, support, timeunit = 3600, tim
 #' @description Generate a collection of events according to the posterior predictive checks
 #'
 #' @param D number of events to be generated
-#' @param A vector of node id's (ID starting from 1)
 #' @param beta P-length vector of coefficients for recipients
 #' @param eta Q-length vector of coefficients for timestamps
 #' @param sigma2 variance parameter for the timestamps
@@ -180,25 +179,21 @@ Generate = function(D, A, beta, eta, sigma2, X, Y, support, timeunit = 3600, tim
 #' @param Y an array of dimension D x A x Q for covariates used for timestamps GLM
 #' @param timeunit hour (= 3600) or day (=3600*24) and so on
 #' @param u D-length list of latent receiver vectors
-#' @param initial sender, receiver, timestamps of the events used as initia history
+#' @param lasttime last timestamp of the event used as initial history (in unix.time format)
 #' @param timedist lognormal or exponential (will include others)
 #'
 #' @return generated data including (sender, recipients, timestamp)
 #'
 #' @export
-PPC = function(D, A, beta, eta, sigma2, X, Y, timeunit = 3600, u, initial = NULL, timedist = "lognormal") {
+PPC = function(D, beta, eta, sigma2, X, Y, timeunit = 3600, u, lasttime, timedist = "lognormal") {
   P = length(beta)
   Q = length(eta)
-  X = X
-  Y = Y
+  A = dim(X)[2]
   u = u
   data = list()
   lambda = list()
   mu = matrix(NA, D, A)
-  sender = initial$sender
-  receiver = initial$receiver
-  time = as.numeric(as.POSIXct(strptime(initial$time, "%d %b %Y %H:%M:%S")))
-  t_d = max(time)
+  t_d = lasttime
   d = 1
   while (d <= D) {
     lambda[[d]] = lambda_cpp(X[d,,,], beta)
@@ -215,9 +210,6 @@ PPC = function(D, A, beta, eta, sigma2, X, Y, timeunit = 3600, u, initial = NULL
       t_d = t_d + min(tau) * timeunit
       data[[d]] = list(a_d = a_d, r_d = r_d, t_d = t_d)
       d = d+1
-      sender = c(sender, a_d)
-      receiver = rbind(receiver, r_d)
-      time = c(time, t_d)
     }
   }
   return(data)

### 2018-04-27 Lab/pkg_tutorial.R
function for exp dist added

@@ -1,9 +1,10 @@
 #install the package from Github
 library(devtools)
 install_github("desmarais-lab/MulticastNetwork/pkg")
-
+library(MulticastNetwork)
 #load our Montgomery county email data
 load("/Users/bomin8319/Box/gainlab_example/Bomin/Montgomery.RData")
+names(Montgomery)
 
 #data including sender a_d, reciever vector r_d, timestamp t_d
 edge = Montgomery$edge
@@ -12,26 +13,41 @@ head(edge)
 #covariates affecting "who sends to whom"
 X = Montgomery$X
 head(X[100, 1, , ])
- 
+X = X[,,,c(1:5)]    #use few covariates for this application
+
 #covariates affecting "when to send"
 Y = Montgomery$Y
 head(Y[100, , ])
+Y = Y[,,c(1:5)]    #use few covariates for this application
 
-#initial history before 7 days
-initial = Montgomery$initial
 
+P = dim(X)[4]
+Q = dim(Y)[3]
 #run inference to estimate beta, eta, u, and sigma2
 prior.beta = list(mean = rep(0, P), var = 2*diag(P))
 prior.eta = list(mean = rep(0, Q), var = 2*diag(Q))
 prior.sigma2 = list(a = 2, b = 1)
 
-outer = 100
+outer = 500
 inner = c(1, 1, 1)
 burn = 0
 
-Montgomery_infer = Inference(edge, X, Y, outer, inner, burn, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
-		  proposal.var = c(0.001, 0.001, 0.1), timeunit = 3600, lasttime = max(initial$time), timedist = "lognormal")
+#this initial values are my results after convergence
+initialval = list()
+initialval$beta = c(-3.548488159, -0.108898033,  0.086928281,  0.274102964,  0.029273815)
+initialval$eta = c(7.38197540,  0.12883606, -1.07065227, -0.20698218, -0.05894448)
+initialval$sigma2 = 14.09288
+initialval$u = lapply(1:dim(X)[1], function(d) matrix(0, dim(X)[2], dim(X)[2]))
 
+#run infernece
+Montgomery_infer = Inference(edge, X, Y, outer, inner, burn, prior.beta, prior.eta, prior.sigma2, initialval = initialval,
+		  proposal.var = c(0.0001, 0.001, 0.1), timeunit = 3600, lasttime = Montgomery$lasttime, timedist = "lognormal")
+names(Montgomery_infer)
+
[…]

### 2018-04-27 code/Montgomery_processing.R

@@ -1,4 +1,6 @@
-source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
+#source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
+
+library(MulticastNetwork)
 library(lubridate)
 load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')
 Montgomery = Temporal_Email_Data$Montgomery
@@ -90,7 +92,10 @@ Y = Y[trim,,]
 Montgomery_infer = Inference(edge, X, Y, 55000, c(10,1,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
 		  proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "lognormal")
 
-Montgomery = list(edge = edge, X = X, Y = Y, lasttime = email[min(trim-1), 21])
+dimnames(X)[[4]] = c("intercept", "outdegree", "indegree", "send", "receive", "2send", "2receive", "sibling", "cosibling", "Nreceive", "outdegree*Nrecieve")
+dimnames(Y)[[3]] = c("intercept", "female", "manager", "outdegree", "indegree", "weekend", "pm")
+
+Montgomery = list(edge = edge, X = X, Y = Y, lasttime = email[min(trim-1), 21] - initialtime )
 
 save(Montgomery, file = "Montgomery.RData")
 
@@ -102,7 +107,7 @@ initial$receiver = email[1:(min(trim)-1), 3:20]
 initial$time = email[1:(min(trim)-1),1]
 for (n in 1:500) {
   Montgomery_PPC = PPC(length(edge), A, colMeans(Montgomery_infer$beta), colMeans(Montgomery_infer$eta), 
-                       mean(Montgomery_infer$sigma2), X, Y, timeunit = 3600, lasttime = email[min(trim-1), 21], 
+                       mean(Montgomery_infer$sigma2), X, Y, timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, 
                        Montgomery_infer$u, initial =initial)
   filename = paste0("Montgomery_PPCnew", n,".RData")
   save(Montgomery_PPC, file = filename)

### 2018-04-27 pkg/R/Multicast.R

@@ -155,7 +155,7 @@ Generate = function(D, A, beta, eta, sigma2, X, Y, support, timeunit = 3600, tim
 		if (timedist == "lognormal") {
             tau = rlnorm(A, mu[d, ], sqrt(sigma2))
         } else {
-            tau = rexp(A, exp(mu[d, ]))
+            tau = rexp(A, 1/exp(mu[d, ]))
         }
 		for (n in 1:length(which(tau == min(tau)))) {
 		a_d = which(tau == min(tau))
@@ -202,7 +202,7 @@ PPC = function(D, beta, eta, sigma2, X, Y, timeunit = 3600, u, lasttime, timedis
     if (timedist == "lognormal") {
         tau = rlnorm(A, mu[d, ], sqrt(sigma2))
     } else {
-        tau = rexp(A, exp(mu[d, ]))
+        tau = rexp(A, 1/exp(mu[d, ]))
     }
     for (n in 1:length(which(tau == min(tau)))) {
       a_d = which(tau == min(tau))

### 2018-04-27 pkg/R/RcppExports.R

@@ -29,6 +29,10 @@ Timepartsum <- function(mumat, sigma_tau, senders, timestamps) {
     .Call('_MulticastNetwork_Timepartsum', PACKAGE = 'MulticastNetwork', mumat, sigma_tau, senders, timestamps)
 }
 
+Timepartsum2 <- function(mumat, senders, timestamps) {
+    .Call('_MulticastNetwork_Timepartsum2', PACKAGE = 'MulticastNetwork', mumat, senders, timestamps)
+}
+
 Timepartindiv <- function(mu, sigma_tau, timestamp) {
     .Call('_MulticastNetwork_Timepartindiv', PACKAGE = 'MulticastNetwork', mu, sigma_tau, timestamp)
 }

### 2018-04-27 pkg/src/Multicast_rcpp.cpp

@@ -101,6 +101,24 @@ double Timepartsum (NumericMatrix mumat, double sigma_tau,
     return timesum;
 }
 
+// **********************************************************//
+//           Likelihood evaluation of Timepart--exp          //
+// **********************************************************//
+// [[Rcpp::export]]
+double Timepartsum2 (NumericMatrix mumat, IntegerVector senders, NumericVector timestamps){
+    int D = senders.size();
+    double timesum = 0;
+    for (unsigned int d = 0; d < D; d++) {
+        int a_d = senders[d] - 1;
+        timesum += R::dexp(timestamps[d], 1/exp(mumat(d, a_d)), TRUE);
+        for (unsigned int i = 0; i < mumat.ncol(); i++) {
+        if (i != a_d) {
+            timesum += R::pexp(timestamps[d], 1/exp(mumat(d, i)), FALSE, TRUE);
+    	  }
+        }
+    }
+    return timesum;
+}
 
 // **********************************************************//
 //              Likelihood evaluation of Timepart            //

### 2018-04-27 pkg/src/RcppExports.cpp

@@ -93,6 +93,19 @@ BEGIN_RCPP
     return rcpp_result_gen;
 END_RCPP
 }
+// Timepartsum2
+double Timepartsum2(NumericMatrix mumat, IntegerVector senders, NumericVector timestamps);
+RcppExport SEXP _MulticastNetwork_Timepartsum2(SEXP mumatSEXP, SEXP sendersSEXP, SEXP timestampsSEXP) {
+BEGIN_RCPP
+    Rcpp::RObject rcpp_result_gen;
+    Rcpp::RNGScope rcpp_rngScope_gen;
+    Rcpp::traits::input_parameter< NumericMatrix >::type mumat(mumatSEXP);
+    Rcpp::traits::input_parameter< IntegerVector >::type senders(sendersSEXP);
+    Rcpp::traits::input_parameter< NumericVector >::type timestamps(timestampsSEXP);
+    rcpp_result_gen = Rcpp::wrap(Timepartsum2(mumat, senders, timestamps));
+    return rcpp_result_gen;
+END_RCPP
+}
 // Timepartindiv
 NumericVector Timepartindiv(NumericVector mu, double sigma_tau, double timestamp);
 RcppExport SEXP _MulticastNetwork_Timepartindiv(SEXP muSEXP, SEXP sigma_tauSEXP, SEXP timestampSEXP) {
@@ -222,6 +235,7 @@ static const R_CallMethodDef CallEntries[] = {
     {"_MulticastNetwork_transpose", (DL_FUNC) &_MulticastNetwork_transpose, 1},
     {"_MulticastNetwork_tabulateC", (DL_FUNC) &_MulticastNetwork_tabulateC, 2},
     {"_MulticastNetwork_Timepartsum", (DL_FUNC) &_MulticastNetwork_Timepartsum, 4},
+    {"_MulticastNetwork_Timepartsum2", (DL_FUNC) &_MulticastNetwork_Timepartsum2, 3},
     {"_MulticastNetwork_Timepartindiv", (DL_FUNC) &_MulticastNetwork_Timepartindiv, 3},
     {"_MulticastNetwork_multinom_vec", (DL_FUNC) &_MulticastNetwork_multinom_vec, 1},
     {"_MulticastNetwork_normalizer", (DL_FUNC) &_MulticastNetwork_normalizer, 1},

### 2018-04-28 code/Montgomery_PPE.R
minor bug in PPE code

@@ -1,4 +1,5 @@
-source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
+#source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
+library(MulticastNetwork)
 library(lubridate)
 load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')
 Montgomery = Temporal_Email_Data$Montgomery
@@ -44,7 +45,7 @@ sendraw = function(data, a, r) {
 # construct recipient covariates X
 D = length(edge)
 A = length(Montgomery$manager_gender)
-P = 9
+P = 11
 X = array(0, dim = c(D,A,A,P))
 X[,,,1] = 1
 timeunit = 3600
@@ -72,8 +73,10 @@ for (d in 2:D) {
 				})) / 10
 			X[d, a, r, 9] = sum(sapply(c(1:A)[-c(a,r)], function(h) {
 				sendraw(data, a, h) * sendraw(data, r, h)
-				}))	/10		
+				}))	/10	
 		}
+	  X[d, a, , 10] = ifelse(outdegree[a] > 0, sum(X[d,a,,4]), 0)
+	  X[d, a, , 11] = X[d, a, , 2] * X[d, a, , 10] / 10
 	}
 }
 
@@ -96,7 +99,7 @@ missing[[3]] = matrix(0, nrow = dim(Y)[1], 1)
 missing[[3]][sample(1:dim(Y)[1], 62, replace = FALSE), ] = 1
 
 
-load("/Users/bomin8319/Desktop/MulticastNetwork/code/Montgomery_infer.RData")
+load("/Users/bomin8319/Desktop/MulticastNetwork/Montgomery_infer.RData")
 initial = list()
 initial$beta = colMeans(Montgomery_infer$beta)
 initial$eta =  colMeans(Montgomery_infer$eta)
@@ -106,7 +109,7 @@ setwd("/Users/bomin8319/Desktop/MulticastNetwork/code/PPE")
 Montgomery_PPE = list()
 for (n in 1:500) {
 	print(n)
-  Montgomery_PPE[[n]] = PPE(edge, missing, X, Y, 50, c(5,5,1), 0, prior.beta, prior.eta, prior.sigma2, initial = initial, proposal.var = c(0.0001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime)
[…]

### 2018-04-28 pkg/R/Multicast.R

@@ -409,12 +409,12 @@ PPE = function(data, missing, X, Y, outer, inner, burn, prior.beta, prior.eta, p
     	missingr = which(missing[[2]][d,]==1)
     	data[[d]][[2]][missingr] = u[[d]][senders[d], missingr]
         for (it in 1:length(missingr)) {
-        	receiverpredict[iter3, o] = data[[d]][[2]][missingr[it]]
+        	receiverpredict[iter2, o] = data[[d]][[2]][missingr[it]]
         	iter2 = iter2+1
         }
     }  
     for (d in timemissing) {
-    	tau_new = rlnorm(1, mu[d, senders[d]], MHprop.var)
+    	tau_new = rnorm(1, timeinc[d], MHprop.var)
     	prior.new0 = dlnorm(tau_new, mu[d, senders[d]], sqrt(sigma2), TRUE)
     	prior.old0 = dlnorm(timeinc[d], mu[d, senders[d]], sqrt(sigma2), TRUE)
     	post.new0 = Timepartindiv(mu[d,], sqrt(sigma2), tau_new)[senders[d]]

### 2018-04-28 Lab/pkg_tutorial.R
PPC code output changed

@@ -23,6 +23,7 @@ Y = Y[,,c(1:5)]    #use few covariates for this application
 
 P = dim(X)[4]
 Q = dim(Y)[3]
+A = dim(Y)[2]
 #run inference to estimate beta, eta, u, and sigma2
 prior.beta = list(mean = rep(0, P), var = 2*diag(P))
 prior.eta = list(mean = rep(0, Q), var = 2*diag(Q))
@@ -49,5 +50,32 @@ plot(Montgomery_infer$loglike, type = 'l')
 
 # generate data from the model estimates
 Montgomery_PPC = PPC(length(edge), beta = colMeans(Montgomery_infer$beta), eta = colMeans(Montgomery_infer$eta), 
-                     sigma2 = mean(Montgomery_infer$sigma2), X, Y, timeunit = 3600, u = Montgomery_infer$u, 
-        			 lasttime = Montgomery$lasttime, timedist = "lognormal")
+                     sigma2 = mean(Montgomery_infer$sigma2), X, Y, timeunit = 3600, u = Montgomery_infer$u, timedist = "lognormal")
+
+# prediction experiment
+# hide 10% of senders, receivers, and timestamps
+set.seed(1)
+missing = list()
+#missingness of senders
+missing[[1]] = matrix(0, nrow = dim(Y)[1], 1)    
+missing[[1]][sample(1:dim(Y)[1], 62, replace = FALSE), ] = 1
+#missingness of receivers
+missing[[2]] = matrix(0, nrow = dim(Y)[1], A)    
+missing[[2]][sample(1:(dim(Y)[1]*A), 1118, replace = FALSE)] = 1
+#missingness of timestamps
+missing[[3]] = matrix(0, nrow = dim(Y)[1], 1)
+missing[[3]][sample(1:dim(Y)[1], 62, replace = FALSE), ] = 1
+
+# use parameter estimates as initial values
+initial = list()
+initial$beta = colMeans(Montgomery_infer$beta)
+initial$eta =  colMeans(Montgomery_infer$eta)
+initial$u = Montgomery_infer$u
+initial$sigma2 = mean(Montgomery_infer$sigma2)
+
+#will generate 10 predictions (iterate two steps: imputation -> inference)
+Montgomery_PPE = PPE(edge, missing, X, Y, 10, c(5,5,1), 0, prior.beta, prior.eta, prior.sigma2, 
[…]

### 2018-04-28 pkg/R/Multicast.R

@@ -168,53 +168,6 @@ Generate = function(D, A, beta, eta, sigma2, X, Y, support, timeunit = 3600, tim
 	return(list(data = data, u = u, beta = beta, eta = eta, sigma2 = sigma2))
 }
 
-#' @title PPC
-#' @description Generate a collection of events according to the posterior predictive checks
-#'
-#' @param D number of events to be generated
-#' @param beta P-length vector of coefficients for recipients
-#' @param eta Q-length vector of coefficients for timestamps
-#' @param sigma2 variance parameter for the timestamps
-#' @param X an array of dimension D x A x A x P for covariates used for Gibbs measure
-#' @param Y an array of dimension D x A x Q for covariates used for timestamps GLM
-#' @param timeunit hour (= 3600) or day (=3600*24) and so on
-#' @param u D-length list of latent receiver vectors
-#' @param lasttime last timestamp of the event used as initial history (in unix.time format)
-#' @param timedist lognormal or exponential (will include others)
-#'
-#' @return generated data including (sender, recipients, timestamp)
-#'
-#' @export
-PPC = function(D, beta, eta, sigma2, X, Y, timeunit = 3600, u, lasttime, timedist = "lognormal") {
-  P = length(beta)
-  Q = length(eta)
-  A = dim(X)[2]
-  u = u
-  data = list()
-  lambda = list()
-  mu = matrix(NA, D, A)
-  t_d = lasttime
-  d = 1
-  while (d <= D) {
-    lambda[[d]] = lambda_cpp(X[d,,,], beta)
-    u[[d]] = u_cpp_d(lambda[[d]], u[[d]])
-    mu[d, ] = mu_cpp_d(Y[d,,], eta)
-    if (timedist == "lognormal") {
-        tau = rlnorm(A, mu[d, ], sqrt(sigma2))
-    } else {
-        tau = rexp(A, 1/exp(mu[d, ]))
-    }
-    for (n in 1:length(which(tau == min(tau)))) {
-      a_d = which(tau == min(tau))
-      r_d = u[[d]][a_d,]
-      t_d = t_d + min(tau) * timeunit
-      data[[d]] = list(a_d = a_d, r_d = r_d, t_d = t_d)
-      d = d+1
-    }
-  }
-  return(data)
-}
-
 #' @title Inference
 #' @description Iterate Markov Chain Monte Carlo (MCMC) algorithm to infer the parameters
 #'
[…]

### 2018-04-30 code/Montgomery_PPE.R
minor code updates

@@ -115,4 +115,20 @@ for (n in 1:500) {
 }
 
 
+load("/Users/bomin8319/Desktop/MulticastNetwork/Montgomery_infer2.RData")
+initial2 = list()
+initial2$beta = colMeans(Montgomery_infer2$beta)
+initial2$eta =  colMeans(Montgomery_infer2$eta)
+initial2$u = Montgomery_infer2$u
+initial2$sigma2 = mean(Montgomery_infer2$sigma2)
+
+Montgomery_PPE2 = list()
+for (n in 1:500) {
+	print(n)
+  Montgomery_PPE2[[n]] = PPE(edge, missing, X, Y, 50, c(5,5,1), 0, prior.beta, prior.eta, prior.sigma2, initial = initial2, proposal.var = c(0.0001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, MHprop.var = 0.1, timedist = "exponential")
+  filename = paste0("Montgomery_PPE2", n,"exp.RData")
+  save(Montgomery_PPE2, file = filename)
+}
+
+
 

### 2018-04-30 pkg/R/Multicast.R

@@ -333,6 +333,51 @@ PPC = function(D, beta, eta, sigma2, X, Y, timeunit = 3600, u, timedist = "logno
 }
 
 
+#' @title PPC_misssing
+#' @description Generate a collection of events according to the posterior predictive checks
+#'
+#' @param D number of events to be generated
+#' @param beta P-length vector of coefficients for recipients
+#' @param eta Q-length vector of coefficients for timestamps
+#' @param sigma2 variance parameter for the timestamps
+#' @param X an array of dimension D x A x A x P for covariates used for Gibbs measure
+#' @param Y an array of dimension D x A x Q for covariates used for timestamps GLM
+#' @param timeunit hour (= 3600) or day (=3600*24) and so on
+#' @param u D-length list of latent receiver vectors
+#' @param timedist lognormal or exponential (will include others)
+#'
+#' @return generated data including (sender, recipients, timestamp)
+#'
+#' @export
+PPC_missing = function(D, beta, eta, sigma2, X, Y, timeunit = 3600, u, timedist = "lognormal") {
+    P = length(beta)
+    Q = length(eta)
+    A = dim(X)[2]
+    u = u
+    data = list()
+    lambda = list()
+    mu = matrix(NA, D, A)
+    d = 1
+    while (d <= D) {
+        lambda[[d]] = lambda_cpp(X[d,,,], beta)
+        u[[d]] = u_cpp_d(lambda[[d]], u[[d]])
+        mu[d, ] = mu_cpp_d(Y[d,,], eta)
+        if (timedist == "lognormal") {
+            tau = rlnorm(A, mu[d, ], sqrt(sigma2))
+        } else {
+            tau = rexp(A, 1/exp(mu[d, ]))
+        }
+        for (n in 1:length(which(tau == min(tau)))) {
+            a_d = which(tau == min(tau))
+            r_d = u[[d]][a_d,]
+            t_d = min(tau) * timeunit
+            data[[d]] = list(a_d = a_d, r_d = r_d, t_d = t_d)
+            d = d+1
+        }
+    }
+    return(data)
+}
+
 #' @title PPE
 #' @description Posterior predictive experiments for
 #'
@@ -399,7 +444,11 @@ PPE = function(data, missing, X, Y, outer, inner, burn, prior.beta, prior.eta, p
[…]

### 2018-04-30 pkg/R/RcppExports.R

@@ -37,6 +37,10 @@ Timepartindiv <- function(mu, sigma_tau, timestamp) {
     .Call('_MulticastNetwork_Timepartindiv', PACKAGE = 'MulticastNetwork', mu, sigma_tau, timestamp)
 }
 
+Timepartindiv2 <- function(mu, timestamp) {
+    .Call('_MulticastNetwork_Timepartindiv2', PACKAGE = 'MulticastNetwork', mu, timestamp)
+}
+
 multinom_vec <- function(x) {
     .Call('_MulticastNetwork_multinom_vec', PACKAGE = 'MulticastNetwork', x)
 }

### 2018-04-30 pkg/src/Multicast_rcpp.cpp

@@ -139,6 +139,24 @@ NumericVector Timepartindiv (NumericVector mu, double sigma_tau, double timestam
 }
 
 // **********************************************************//
+//              Likelihood evaluation of Timepart            //
+// **********************************************************//
+// [[Rcpp::export]]
+NumericVector Timepartindiv2 (NumericVector mu, double timestamp){
+    int A = mu.size();
+    NumericVector out(A);
+    for (unsigned int a = 0; a < A; a++) {
+        out[a] += R::dexp(timestamp, 1/exp(mu[a]), TRUE);
+        for (unsigned int i = 0; i < A; i++) {
+            if (i != a) {
+                out[a] += R::pexp(timestamp, 1/exp(mu[i]), FALSE, TRUE);
+            }
+        }
+    }
+    return out;
+}
+
+// **********************************************************//
 //                    Multinomial Sampler                    //
 // **********************************************************//
 // [[Rcpp::export]]

### 2018-04-30 pkg/src/RcppExports.cpp

@@ -119,6 +119,18 @@ BEGIN_RCPP
     return rcpp_result_gen;
 END_RCPP
 }
+// Timepartindiv2
+NumericVector Timepartindiv2(NumericVector mu, double timestamp);
+RcppExport SEXP _MulticastNetwork_Timepartindiv2(SEXP muSEXP, SEXP timestampSEXP) {
+BEGIN_RCPP
+    Rcpp::RObject rcpp_result_gen;
+    Rcpp::RNGScope rcpp_rngScope_gen;
+    Rcpp::traits::input_parameter< NumericVector >::type mu(muSEXP);
+    Rcpp::traits::input_parameter< double >::type timestamp(timestampSEXP);
+    rcpp_result_gen = Rcpp::wrap(Timepartindiv2(mu, timestamp));
+    return rcpp_result_gen;
+END_RCPP
+}
 // multinom_vec
 int multinom_vec(NumericVector x);
 RcppExport SEXP _MulticastNetwork_multinom_vec(SEXP xSEXP) {
@@ -237,6 +249,7 @@ static const R_CallMethodDef CallEntries[] = {
     {"_MulticastNetwork_Timepartsum", (DL_FUNC) &_MulticastNetwork_Timepartsum, 4},
     {"_MulticastNetwork_Timepartsum2", (DL_FUNC) &_MulticastNetwork_Timepartsum2, 3},
     {"_MulticastNetwork_Timepartindiv", (DL_FUNC) &_MulticastNetwork_Timepartindiv, 3},
+    {"_MulticastNetwork_Timepartindiv2", (DL_FUNC) &_MulticastNetwork_Timepartindiv2, 2},
     {"_MulticastNetwork_multinom_vec", (DL_FUNC) &_MulticastNetwork_multinom_vec, 1},
     {"_MulticastNetwork_normalizer", (DL_FUNC) &_MulticastNetwork_normalizer, 1},
     {"_MulticastNetwork_Edgepartsum", (DL_FUNC) &_MulticastNetwork_Edgepartsum, 2},

### 2018-04-30 paper/paper.tex
paper draft update

@@
 \section{Introduction}\label{sec:intro}
+In recent decades, real-time digitized textual communication has developed into a ubiquitous form of social and professional interaction \citep{kanungo2008modeling, szostek2011dealing, burgess2004email, pew2016}.
+From the perspective of the computational social scientist, this has lead to a growing need for methods of modeling interactions that manifest as text exchanged in continuous time.
+A number of models that build upon topic modeling through Latent Dirichlet Allocation \citep{Blei2003} to incorporate link data as well as textual content have been developed recently \citep{mccallum2005author,lim2013twitter,Krafft2012}.
+These models are innovative in their extensions that incorporate network tie information.
+However, none of the models that are currently available in the literature integrate the rich random-graph structure offered by state of the art models for network structure---such as the exponential random graph model (ERGM) \citep{robins2007introduction,chatterjee2013estimating,hunter2008ergm}.
+The ERGM is the canonical model for modeling the structure of a static network.
+It is flexible enough to specify a generative model that accounts for nearly any pattern of tie formation (e.g., reciprocity, clustering, popularity effects) \citep{desmarais2017statistical}.
+Several models have been developed that handle time-stamped ties in which tie formation is governed by structural dynamics similar to those used in ERGMs \citep{PerryWolfe2012,Butts2008,snijders1996stochastic}, however, none of the models explicitly allows multicast---edge with single sender multiple recipients---which is a common property of digitalized textual interactions such as emails and online messages.
+We develop the continuous-time multicast network model which simultaneously models the multiple recipient selection processs and the time-to-next interactions which jointly govern time-stamped tie formation.
+
 \section{A Continuous-time Multicast Network Model}\label{sec:generative process}
@@
  \end{algorithm}
-
+ \iffalse
  \section{Getting It Right}\label{sec:GiR}
@@
  	\centering
- 	\includegraphics[width=1\textwidth, trim = 0.5cm 1cm 0.5cm 1cm, clip=true]{Multicast_Schein.pdf}	
+ 	\includegraphics[width=1\textwidth, trim = 0.5cm 1cm 0.5cm 1cm, clip=true]{plots_paper/Multicast_Schein.pdf}	
  	\caption {Schein test results when we run 5 outer iterations and 5 inner iterations using 20,000 samples (with $D = 100, A = 5, P = 5, Q = 3$)}
@@
  \end{figure}
-
+\fi
 \section{Case Studies}\label{sec:case studies}
@@
 \subsubsection{Parameter Estimation and Interpretation}\label{subsubsec:Result_email}
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=1\textwidth]{plots_paper/best-1.png}	
+		\caption {Posterior distribution of $\boldsymbol{b}$ estimates.}
+		\label{figure:betaresults}
+	\end{figure}
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=0.89\textwidth]{plots_paper/etaest-1.png}	
+		\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
+		\label{figure:etaresults}
+	\end{figure}
 \subsection{Case Study 2: International Sanctions}\label{subsec:International Sanctions}

### 2018-04-30 Emails/Montgomery_result.R

@@ -1,0 +1,155 @@
+#source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
+library(MulticastNetwork)
+library(lubridate)
+
+#####################################
+#inference results
+load("/Users/bomin8319/Desktop/MulticastNetwork/Montgomery_infer.RData")
+names(Montgomery_infer)
+
+library(anytime)
+library(ggplot2)
+library(MCMCpack)
+library(reshape2)
+library(gridExtra)
+library(ggrepel)
+library(RColorBrewer)
+
+colnames(Montgomery_infer$beta) = dimnames(Montgomery$X)[[4]]
+beta = data.frame(t(sapply(1:1000, function(i) Montgomery_infer$beta[40*i,])))
+colnames(beta)[6:7] = c("twosend", "tworeceive")
+beta.est = melt(beta[-1])
+colnames(beta.est)[1] = "netstats"
+colnames(beta.est)[2] = "b"
+ggplot(data = beta.est, aes(x = netstats, y = b, fill = netstats)) + geom_boxplot()+coord_flip()+ geom_hline(yintercept = 0.0, colour = "red", size = 0.5, linetype = "dashed")+labs(x = NULL, fill = "Covariates")
+
+colnames(Montgomery_infer$eta) = dimnames(Montgomery$Y)[[3]]
+eta = data.frame(t(sapply(1:1000, function(i) Montgomery_infer$eta[40*i,])))
+eta.est = melt(eta[-1])
+colnames(eta.est)[1] = "netstats"
+colnames(eta.est)[2] = "eta"
+ggplot(data = eta.est, aes(x = netstats, y = eta, fill = netstats)) + geom_boxplot()+coord_flip()+ geom_hline(yintercept = 0.0, colour = "red", size = 0.5, linetype = "dashed")+labs(x = NULL, fill = "Covariates")
+
+#####################################
+
+load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')
+Montgomery = Temporal_Email_Data$Montgomery
+email = Montgomery$email_data
+email = unique(email)
+email$timepoints =  as.numeric(as.POSIXct(strptime(email[,1], "%d %b %Y %H:%M:%S")))
+email = email[order(email$timepoints), ]
+edge = list()
[…]

### 2018-05-02 paper/paper.tex
PPC added

@@
 	In the example of email networks, we form the covariate vector $\boldsymbol{x}_{adr}$ using time-varying network statistics based on the time interval prior to and including $t_{d-1}$.
-Along with intercept term, we compute eight network statistics \cite{PerryWolfe2012}, where the time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{days}, t_{d-1}]$.
+Along with intercept term, we compute the network statistics \citep{PerryWolfe2012}, where the time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{days}, t_{d-1}]$.
 	\begin{itemize}
@@
 		\item[9.] cosibling $\boldsymbol{x}_{adr9}=\sum\limits_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(r,h)$;
+		\item[10.] Nreceive $\boldsymbol{x}_{adr10}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} \sum\limits_{r=1}^A I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
+		\item[11.] outdegree$*$Nreceive $\boldsymbol{x}_{adr11} = \boldsymbol{x}_{adr2}\times\boldsymbol{x}_{adr10}$
 	\end{itemize}
-where $I(\cdot)$ is an indicator function.\\ \newline
+	where $I(\cdot)$ is an indicator function, and the last covariate is the interaction term between outdegree and Nreceive.\\ \newline
 For time-related covariates $\boldsymbol{y}_{ad}$ in Section \ref{subsec:Time}, we form the covariate vector $\boldsymbol{y}_{ad}$ using the seven statistics which may possibly effect ``time to send the next document".
@@
 \end{algorithm}       
-
+\subsection{Montgomery County Data}
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.49\textwidth]{plots_paper/outdegreenew-1.png}	
+		\includegraphics[width=0.49\textwidth]{plots_paper/indegreenew-1.png}	
+				\includegraphics[width=0.49\textwidth]{plots_paper/recipientsizenew-1.png}	
+								\includegraphics[width=0.31\textwidth]{plots_paper/timeppnew.pdf}
+		\caption {PPC results.}
+		\label{figure:outdegree}
+	\end{figure}
+\subsection{International Sanctions}
 \section{Conclusion}\label{sec:conclusion}

### 2018-05-02 Emails/Montgomery_result.R

@@ -15,9 +15,12 @@ library(gridExtra)
 library(ggrepel)
 library(RColorBrewer)
 
+
 colnames(Montgomery_infer$beta) = dimnames(Montgomery$X)[[4]]
 beta = data.frame(t(sapply(1:1000, function(i) Montgomery_infer$beta[40*i,])))
+colnames(beta) = dimnames(Montgomery$X)[[4]][1:10]
 colnames(beta)[6:7] = c("twosend", "tworeceive")
+colnames(beta) = dimnames(Montgomery$X)[[4]][1:10]
 beta.est = melt(beta[-1])
 colnames(beta.est)[1] = "netstats"
 colnames(beta.est)[2] = "b"
@@ -31,7 +34,6 @@ colnames(eta.est)[2] = "eta"
 ggplot(data = eta.est, aes(x = netstats, y = eta, fill = netstats)) + geom_boxplot()+coord_flip()+ geom_hline(yintercept = 0.0, colour = "red", size = 0.5, linetype = "dashed")+labs(x = NULL, fill = "Covariates")
 
 #####################################
-
 load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')
 Montgomery = Temporal_Email_Data$Montgomery
 email = Montgomery$email_data
@@ -60,96 +62,134 @@ indegreedist = matrix(NA, 500, A)
 outdegreedist = matrix(NA,  500, A)
 recipientsdist = matrix(NA,  500, A-1)
 timedist = matrix(NA, 500, 621)
-setwd("/Users/bomin8319/Desktop/MulticastNetwork/code")
+#setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC")
+setwd("/Users/bomin8319/")
+
 for (n in 1:500) {
 	filename = paste0("Montgomery_PPCnew", n,".RData")
 	load(filename)
 	outdegreedist[n, ] = tabulate(vapply(1:621, function(x) Montgomery_PPC[[x]]$a_d, c(1)), A)
 	indegreedist[n, ] = rowSums(sapply(1:621, function(x) Montgomery_PPC[[x]]$r_d))
 	recipientsdist[n, ] = tabulate(vapply(1:621, function(x) sum(Montgomery_PPC[[x]]$r_d), c(1)), A-1)
-	timedist[n, ] = c(email$timepoints[42], diff(vapply(1:621, function(x) sum(Montgomery_PPC[[x]]$t_d), c(1)))) / timeunit
[…]

### 2018-05-02 code/Montgomery_PPE.R

@@ -105,11 +105,10 @@ initial$beta = colMeans(Montgomery_infer$beta)
 initial$eta =  colMeans(Montgomery_infer$eta)
 initial$u = Montgomery_infer$u
 initial$sigma2 = mean(Montgomery_infer$sigma2)
-setwd("/Users/bomin8319/Desktop/MulticastNetwork/code/PPE")
-Montgomery_PPE = list()
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPE")
 for (n in 1:500) {
 	print(n)
-  Montgomery_PPE[[n]] = PPE(edge, missing, X, Y, 50, c(5,5,1), 0, prior.beta, prior.eta, prior.sigma2, initial = initial, proposal.var = c(0.0001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, MHprop.var = 0.1, timedist = "lognormal")
+  Montgomery_PPE = PPE(edge, missing, X, Y, 50, c(5,5,1), 0, prior.beta, prior.eta, prior.sigma2, initial = initial, proposal.var = c(0.0001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, MHprop.var = 0.1, timedist = "lognormal")
   filename = paste0("Montgomery_PPE", n,".RData")
   save(Montgomery_PPE, file = filename)
 }
@@ -122,10 +121,9 @@ initial2$eta =  colMeans(Montgomery_infer2$eta)
 initial2$u = Montgomery_infer2$u
 initial2$sigma2 = mean(Montgomery_infer2$sigma2)
 
-Montgomery_PPE2 = list()
 for (n in 1:500) {
 	print(n)
-  Montgomery_PPE2[[n]] = PPE(edge, missing, X, Y, 50, c(5,5,1), 0, prior.beta, prior.eta, prior.sigma2, initial = initial2, proposal.var = c(0.0001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, MHprop.var = 0.1, timedist = "exponential")
[…]

### 2018-05-02 code/Montgomery_processing2.R

@@ -1,0 +1,116 @@
+#source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
+
+library(MulticastNetwork)
+library(lubridate)
+load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')
+Montgomery = Temporal_Email_Data$Montgomery
+email = Montgomery$email_data
+email = unique(email)
+email$timepoints =  as.numeric(as.POSIXct(strptime(email[,1], "%d %b %Y %H:%M:%S")))
+email = email[order(email$timepoints), ]
+edge = list()
+initialtime =  as.numeric(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S")))
+for (d in 1:nrow(email)) {
+	t_d = email[d, 21] - initialtime
+	edge[[d]] = list(a_d = email[d,2], r_d = as.numeric(email[d,-c(1:2, 21)]), t_d = t_d)
+}
+
+uniqtime = unique(email$timepoints)
+# construct time covariates Y
+D = length(edge)
+A = length(Montgomery$manager_gender)
+Q = 7
+Y = array(1, dim = c(D,A,Q))
+for (a in 1:A) {
+	Y[,a,2] = 1* (Montgomery$manager_gender[a]=="Female")
+	Y[,a,3] = 1* (Montgomery$manager_department[a]=="County Manager")
+}
+timeunit = 3600
+Y[1,,6] = rep(as.numeric(wday(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
+Y[1,,7] = rep(pm(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))), A)
+for (d in 2:D) {
+	index = which(email$timepoints >= uniqtime[which(uniqtime==email$timepoints[d])-1]-7*24*timeunit & email$timepoints < email$timepoints[d])
+	sent = email[index, 2]
+	received = email[index, 3:(2+A)]
+	Y[d, ,4] = tabulate(sent, A) 
+	Y[d, ,5] = colSums(received)
+	Y[d,,6] = rep(as.numeric(wday(as.POSIXct(strptime(email[d-1,1], "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
[…]

### 2018-05-08 paper/paper.tex
paper update

@@
 We introduce the continuous-time multicast network model---a generative model for directed edges with multiple recipients or multiple senders. To define the model, we
-integrate a dynamic version of the exponential random graph model (ERGM) and generalized linear model approach to understand who communicates with whom, and when. We use
-the model to analyze emails sent between department managers in Montgomery county government in North Carolina, and international sanctions data concerning the threats and use of economic sanctions by states.
-Our applications demonstrate that the model is effective at predicting and explaining continuous-time networks involving edges with multiple recipients or senders.
+integrate a dynamic version of the exponential random graph model (ERGM) and generalized linear model (GLM) approach to jointly understand who communicates with whom, and when. We use
+the model to analyze emails sent between department managers in Montgomery county government in North Carolina.
+Our application demonstrates that the model is effective at predicting and explaining continuous-time networks involving edges with multiple recipients.
 	\end{abstract}
@@
 In recent decades, real-time digitized textual communication has developed into a ubiquitous form of social and professional interaction \citep{kanungo2008modeling, szostek2011dealing, burgess2004email, pew2016}.
-From the perspective of the computational social scientist, this has lead to a growing need for methods of modeling interactions that manifest as text exchanged in continuous time.
+From the perspective of the computational social scientist, this has led to a growing need for methods of modeling interactions that manifest as text exchanged in continuous time.
 A number of models that build upon topic modeling through Latent Dirichlet Allocation \citep{Blei2003} to incorporate link data as well as textual content have been developed recently \citep{mccallum2005author,lim2013twitter,Krafft2012}.
@@
 The ERGM is the canonical model for modeling the structure of a static network.
-It is flexible enough to specify a generative model that accounts for nearly any pattern of tie formation (e.g., reciprocity, clustering, popularity effects) \citep{desmarais2017statistical}.
-Several models have been developed that handle time-stamped ties in which tie formation is governed by structural dynamics similar to those used in ERGMs \citep{PerryWolfe2012,Butts2008,snijders1996stochastic}, however, none of the models explicitly allows multicast---edge with single sender multiple recipients---which is a common property of digitalized textual interactions such as emails and online messages.
-We develop the continuous-time multicast network model which simultaneously models the multiple recipient selection processs and the time-to-next interactions which jointly govern time-stamped tie formation.
+It is flexible enough to specify a generative model that accounts for nearly any pattern of tie formation such as reciprocity, clustering, popularity effects \citep{desmarais2017statistical}.
+
+Several network models have been developed that handle time-stamped ties in which tie formation is governed by structural dynamics similar to those used in the ERGM \citep{Butts2008,Vu2011,snijders1996stochastic}.
+Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows multicast---edge with a single sender multiple recipients---which is a common property of digitalized textual interactions such as emails and online messages.
+For instance, \cite{snijders2007modeling} develops the co-evolution model which assumes that the network structure (``network") and the individual attributes (``behaviour") evolve simultaneously in a dynamic process, however, the model does not allow simultaneous changes within ``networks" or ``behaviour"---all within changes are ordered.
+Relatedly, \cite{PerryWolfe2012} treat multicast interactions via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
+Concentrating on better handling of multicast, we develop the continuous-time multicast network model which simultaneously models the two components that govern time-stamped tie formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
+
+In what follows, we introduce the continuous-time multicast network model by describing how we assume the generatve process of a time-stamped network data (Section 2), and deriving the sampling equations for Bayesian inference (Section 3), and apply the model to the Montgomery county government email data (Section 4).
+Finally, the paper finishes in Section 5 with conclusion and discussion.
 
@@
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
+While the model can be applied for networks with multiple senders and a single receiver, specifically by modifying $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ be the single recipient, here we only present the generative process for those involving a single sender but multiple receivers.
 \subsection{Tie Generating Process}\label{subsec: Tie}
@@
 
-Next, we hypothesize ``If $a$ were the sender of edge $d$, who would be the recipient(s)?" To do this, we draw each sender's set of recipients from a non-empty Gibbs measure \cite{fellows2017removing}---a probability measure we defined in order to 1) allow multiple recipients or ``multicast", 2) prevent from obtaining zero recipient, and 3) ensure tractable normalizing constant.
-Because we allows multicast, we draw a binary (0/1) vector $\boldsymbol{u}_{ad}= (u_{ad1},
+Next, we hypothesize ``If $a$ were the sender of edge $d$, who would be the recipient(s)?" To do this, we draw each sender's set of recipients from the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model to estimate the structure of graphs with binary nodes---with probability of 1 being logit($\lambda_{adr}$).
+In order to avoid the model degeneracy from having an empty recipient set, we define a probability measure ``MB$_{Gibbs}$" motivated by the non-empty Gibbs measure \citep{fellows2017removing} which excludes the all-zero vector from the support of MB distirbution.
+As a result, we 1) allow multiple recipients or ``multicast", 2) prevent from obtaining zero recipient, and 3) ensure tractable normalizing constant.
+To be specific, we draw a binary vector $\boldsymbol{u}_{ad}= (u_{ad1},
 \ldots, u_{adA})$ 
 \begin{equation} \boldsymbol{u}_{ad}  \sim
-\mbox{Gibbs}(\boldsymbol{\lambda}_{ad}),
+\mbox{MB}_{Gibbs}(\boldsymbol{\lambda}_{ad}),
 \end{equation}
-where $\boldsymbol{\lambda}_{id}= \{\lambda_{adr}\}_{r=1}^A$. In particular, we define $\mbox{Gibbs}(\boldsymbol{\lambda}_{ad})$ as
+where $\boldsymbol{\lambda}_{id}= \{\lambda_{adr}\}_{r=1}^A$. In particular, we define $\mbox{MB}_{Gibbs}(\boldsymbol{\lambda}_{ad})$ as
 \begin{equation}
@@
 where $Z(\boldsymbol{\lambda}_{ad})= \prod_{r \neq a} \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
-This is equivalent to assume independent Bernoulli trial on each $u_{adr}$ with probability of 1 being logit($\lambda_{adr}$), excluding the case when all $u_{adr}=0$.
+Again, this is equivalent to assume independent Bernoulli trial on each $u_{adr}$ with probability of 1 being logit($\lambda_{adr}$), excluding the case when all $u_{adr}=0$.
 We provide the derivation of the normalizing constant as a tractable form in the supplementary material.
@@
 In modeling ``when", we do not directly model the timestamp $t_d$.
-Instead, we assume that each sender's the time-increment or ``time to next edge" (i.e., $\tau_{d} = t_d-t_{d-1}$) is drawn from a specific distribution in the exponential family.
-We follow the generalized linear model framework:
+Instead, we assume that each sender's the time-increment or ``time to next interaction" (i.e., $\tau_{d} = t_d-t_{d-1}$) is drawn from a specific distribution in the exponential family.
+We follow the generalized linear model (GLM) framework \citep{nelder1972generalized}:
 \begin{equation}
@@
 \end{equation}
-where $\tau_{ad}$ is a positive real number.
-Possible choices of distribution include Exponential, Weibull, Gamma, and lognormal\footnote{lognormal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling.
+where $\tau_{ad}$ here is a positive real number.
+Possible choices of distribution include Exponential, Weibull, Gamma, and lognormal\footnote{lognormal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
 Based on the choice of distribution, we may introduce any additional parameter (e.g., $\sigma_\tau^2$) to account for the variance.
@@
 \subsection{Observed Data}\label{subsec:Observed}
-Finally, we choose the sender, recipients, and timestamp---which will be observed---by selecting the sender--recipient-set pair with the smallest time-increment \cite{snijders1996stochastic}:
+Finally, we choose the sender, recipients, and timestamp---which will be observed---by selecting the sender--recipient-set pair with the smallest time-increment \citep{snijders1996stochastic}:
 \begin{equation}
@@
 Therefore, it is a sender-driven process in that the recipients and timestamp of an edge is determined by the sender's urgency to send the edge to chosen recipients.
-Note that  our generative process accounts for tied events such that in case of tied events (i.e., multiple senders generated same time increments $\tau_d$), we observe all of the tied events\footnote{The order of tied events do not matter.} .
-	\begin{algorithm}[H]
+Note that  our generative process accounts for tied events such that in case of tied events (i.e., multiple senders generated exactly same time increments $\tau_d$), we observe all of the tied events without assigning the orders of tied events.
+Algorithm \ref{alg:generative} summarizes the generative process in Section \ref{sec:generative process}.
+	\begin{algorithm}[ht]
 		\spacingset{1}
@@
 			\For{a=1 to $A$}{
-				\For{r=1 to $A$}{
-					\If {r $\neq$ a} {
+				\For{r=1 to $A$ (r $\neq$ a)}{
 						form $\boldsymbol{x}_{adr}$\\
 						set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
-					}  }
+					}  
 					draw $\boldsymbol{u}_{ad}  \sim
@@
 In this section, we provide each latent variable's conditional posterior.
-\\ \newline
+
 First, since $u_{adr}$ is a binary random variable, new values may be sampled directly using
@@
 \end{equation}
-where $I(\cdot)$ is the indicator function that is used to prevent from the instances where a sender chooses zero number of recipients.\\ \newline
+where $I(\cdot)$ is the indicator function that is used to prevent from the instances where a sender chooses zero number of recipients.
+
 New values for continuous variables $\boldsymbol{b},$ and $\boldsymbol{\eta}$ and $\sigma^2_\tau$ (if applicable) cannot be sampled directly from their conditional posteriors, but may instead be obtained using the Metropolis--Hastings algorithm.
@@
 \end{equation}
-where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $D$ events ($M \leq D$). If $M=D$ (i.e., no tied events), Equation (10) reduces to Equation (9).
-
+where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $D$ events ($M \leq D$).
+If $M=D$ (i.e., no tied events), Equation (10) reduces to Equation (9).
+Algorithm \ref{alg:MCMC} provides the pseudocode.
  \begin{algorithm}[H]
@@
  			\For{a = 1 to A}{
- 				\For{r = a to A}{
- 					\If {r $\neq$ a} {
+ 				\For{r = 1 to A (r $\neq$ a)}{
  						update $u_{adr}$ using Gibbs update --- Equation (7)
- 					}
 	 			}
@@
  		\For{n=1 to inner2}{
- 				update $\boldsymbol{\eta}$ and $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (10)
+ 				update $\boldsymbol{\eta}$ using Metropolis-Hastings --- Equation (10)
  		}
@@
  	Summarize the results with: \\last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ and $\sigma_\tau^2$ 
+ 				\label{alg:MCMC}
  \end{algorithm}
- \iffalse
- \section{Getting It Right}\label{sec:GiR}
- \begin{figure}[H]
- 	\centering
- 	\includegraphics[width=1\textwidth, trim = 0.5cm 1cm 0.5cm 1cm, clip=true]{plots_paper/Multicast_Schein.pdf}	
- 	\caption {Schein test results when we run 5 outer iterations and 5 inner iterations using 20,000 samples (with $D = 100, A = 5, P = 5, Q = 3$)}
- 	\label{figure:GiR}
- \end{figure}
-\fi
 \section{Case Studies}\label{sec:case studies}
@@
 Along with intercept term, we compute the network statistics \citep{PerryWolfe2012}, where the time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{days}, t_{d-1}]$.
+Specifically, we use
 	\begin{itemize}
@@
 		\item[10.] Nreceive $\boldsymbol{x}_{adr10}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} \sum\limits_{r=1}^A I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
-		\item[11.] outdegree$*$Nreceive $\boldsymbol{x}_{adr11} = \boldsymbol{x}_{adr2}\times\boldsymbol{x}_{adr10}$
+		\item[11.] outdegree$*$Nreceive $\boldsymbol{x}_{adr11} = \boldsymbol{x}_{adr2}\times\boldsymbol{x}_{adr10};$
 	\end{itemize}
-	where $I(\cdot)$ is an indicator function, and the last covariate is the interaction term between outdegree and Nreceive.\\ \newline
+	where $I(\cdot)$ is an indicator function, and the last covariate is the interaction term between outdegree and Nreceive.
+As with the nodal (2, 3, 10, 11) and dyadic (4, 5) effects, the triadic (6--9) effects are designed so that their coefficient have a straightforward interpretation, which are illustrated in the next section.
+
 For time-related covariates $\boldsymbol{y}_{ad}$ in Section \ref{subsec:Time}, we form the covariate vector $\boldsymbol{y}_{ad}$ using the seven statistics which may possibly effect ``time to send the next document".
-Note that these statistics could depend on $a$ only, $d$ (or $t_d$) only, or both $a$ and $d$.
-Specifically, the statistics are
+Note that these statistics could depend on $a$ only (nodal effect), $d$ (or $t_d$) only (temporal effect), or both $a$ and $d$ (nodal \& temporal effect).
+Specifically, the statistics are defined as
 \begin{itemize}
@@
 	\item[6.] weekend $\boldsymbol{y}_{ad6} = I(t_{d-1}= \mbox{weekend})$;
-	\item[7.] am/pm $\boldsymbol{y}_{ad7}= I(t_{d-1}= \mbox{pm})$;
+	\item[7.] am/pm $\boldsymbol{y}_{ad7}= I(t_{d-1}= \mbox{pm})$.
 \end{itemize}
@@
 \begin{appendices}
-\section{Normalizing constant of Gibbs measure}\label{sec: non-empty Gibbs measure}
-The non-empty Gibbs measure \cite{fellows2017removing} defines the probability of author $a$ selecting the binary recipient vector $\boldsymbol{u}_{ad}$ as
+\section{Normalizing constant of MB$_{Gibbs}$}\label{sec: non-empty Gibbs measure}
+Our probability measure ``MB$_{Gibbs}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure \citep{fellows2017removing}---defines the probability of author $a$ selecting the binary recipient vector $\boldsymbol{u}_{ad}$ as
 \begin{equation*} 

### 2018-05-08 pkg/R/Multicast.R

@@ -332,57 +332,10 @@ PPC = function(D, beta, eta, sigma2, X, Y, timeunit = 3600, u, timedist = "logno
     return(data)
 }
 
-
-#' @title PPC_misssing
-#' @description Generate a collection of events according to the posterior predictive checks
-#'
-#' @param D number of events to be generated
-#' @param beta P-length vector of coefficients for recipients
-#' @param eta Q-length vector of coefficients for timestamps
-#' @param sigma2 variance parameter for the timestamps
-#' @param X an array of dimension D x A x A x P for covariates used for Gibbs measure
-#' @param Y an array of dimension D x A x Q for covariates used for timestamps GLM
-#' @param timeunit hour (= 3600) or day (=3600*24) and so on
-#' @param u D-length list of latent receiver vectors
-#' @param timedist lognormal or exponential (will include others)
-#'
-#' @return generated data including (sender, recipients, timestamp)
-#'
-#' @export
-PPC_missing = function(D, beta, eta, sigma2, X, Y, timeunit = 3600, u, timedist = "lognormal") {
-    P = length(beta)
-    Q = length(eta)
-    A = dim(X)[2]
-    u = u
-    data = list()
-    lambda = list()
-    mu = matrix(NA, D, A)
-    d = 1
-    while (d <= D) {
-        lambda[[d]] = lambda_cpp(X[d,,,], beta)
-        u[[d]] = u_cpp_d(lambda[[d]], u[[d]])
-        mu[d, ] = mu_cpp_d(Y[d,,], eta)
-        if (timedist == "lognormal") {
-            tau = rlnorm(A, mu[d, ], sqrt(sigma2))
-        } else {
-            tau = rexp(A, 1/exp(mu[d, ]))
-        }
-        for (n in 1:length(which(tau == min(tau)))) {
-            a_d = which(tau == min(tau))
-            r_d = u[[d]][a_d,]
-            t_d = min(tau) * timeunit
-            data[[d]] = list(a_d = a_d, r_d = r_d, t_d = t_d)
-            d = d+1
-        }
-    }
-    return(data)
-}
-
 #' @title PPE
 #' @description Posterior predictive experiments for
 #'
[…]

### 2018-05-09 paper/paper.tex
paper PPC writing done

@@
 
-In what follows, we introduce the continuous-time multicast network model by describing how we assume the generatve process of a time-stamped network data (Section 2), and deriving the sampling equations for Bayesian inference (Section 3), and apply the model to the Montgomery county government email data (Section 4).
+In what follows, we introduce the continuous-time multicast network model by describing how we assume the generatve process of a time-stamped network data (Section 2), and deriving the sampling equations for Bayesian inference (Section 3).
+Then, we apply the model to the Montgomery county government email data and perform two model validation tasks (Section 4).
 Finally, the paper finishes in Section 5 with conclusion and discussion.
@@
 \begin{equation}
-P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)\Big).
+P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)\Big),
 \end{equation}
-Since we assme the existence of tied-event, the conditional posterior of $\boldsymbol{\eta}$ and $\sigma_{\tau}^2$ should be written as
+where $f_{\tau}(\tau_{d}; \mu_{a_d d}, \sigma_\tau^2)$ is the probability that the $d^{th}$ observed time-increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean parameter, and $\prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)$ is the probability that the latent (or unobserved) senders for event $d$ all generated time-increments greater than $\tau_d$.
+Moreover, under the existence of tied-event, the conditional posterior of $\boldsymbol{\eta}$ and $\sigma_{\tau}^2$ should be written as
 \begin{equation}
@@
 Along with intercept term, we compute the network statistics \citep{PerryWolfe2012}, where the time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{days}, t_{d-1}]$.
-Specifically, we use
+To be specific, we use
 	\begin{itemize}
 		\spacingset{1}
-		\item[1.] intercept $\boldsymbol{x}_{adr1} =1$;
-		\item[2.] outdegree $\boldsymbol{x}_{adr2} =\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
-		\item[3.] indegree $\boldsymbol{x}_{adr3}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
-		\item[4.] send $\boldsymbol{x}_{adr4}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
-		\item[5.] receive $\boldsymbol{x}_{adr5}=\mbox{send}(r,a)$;
-		\item[6.] 2-send $\boldsymbol{x}_{adr6} = \sum\limits_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(h,r)$;
-		\item[7.] 2-receive $\boldsymbol{x}_{adr7}= \sum\limits_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(r,h)$;
-		\item[8.] sibling $\boldsymbol{x}_{adr8}=\sum\limits_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(h,r)$;
-		\item[9.] cosibling $\boldsymbol{x}_{adr9}=\sum\limits_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(r,h)$;
-		\item[10.] Nreceive $\boldsymbol{x}_{adr10}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} \sum\limits_{r=1}^A I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
-		\item[11.] outdegree$*$Nreceive $\boldsymbol{x}_{adr11} = \boldsymbol{x}_{adr2}\times\boldsymbol{x}_{adr10};$
+		\item[1.] intercept ${x}_{adr1} =1$;
+		\item[2.] outdegree ${x}_{adr2} =\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+		\item[3.] indegree ${x}_{adr3}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
+		\item[4.] send ${x}_{adr4}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
+		\item[5.] receive ${x}_{adr5}=\mbox{send}(r,a)$;
+		\item[6.] 2-send ${x}_{adr6} = \sum\limits_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(h,r)$;
+		\item[7.] 2-receive ${x}_{adr7}= \sum\limits_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(r,h)$;
+		\item[8.] sibling ${x}_{adr8}=\sum\limits_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(h,r)$;
+		\item[9.] cosibling ${x}_{adr9}=\sum\limits_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(r,h)$;
+		\item[10.] Nreceive ${x}_{adr10}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} \sum\limits_{r=1}^A I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
+		\item[11.] outdegree$*$Nreceive ${x}_{adr11} = {x}_{adr2}\times{x}_{adr10};$
 	\end{itemize}
 	where $I(\cdot)$ is an indicator function, and the last covariate is the interaction term between outdegree and Nreceive.
-As with the nodal (2, 3, 10, 11) and dyadic (4, 5) effects, the triadic (6--9) effects are designed so that their coefficient have a straightforward interpretation, which are illustrated in the next section.
+As with the nodal (2, 3, 10, 11) and dyadic (4, 5) effects, the triadic (6--9) effects are designed so that their coefficient have a straightforward interpretation, which are illustrated in Figure \ref{figure:netstats}.
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=0.55\textwidth]{plots_paper/triad.png}	
+			\caption {Visualization of triadic statistics.}
+			\label{figure:netstats}
+		\end{figure}
 
@@
 	\spacingset{1}
-	\item[1.] intercept $\boldsymbol{y}_{ad1} =1$;
-	\item[2.] outdegree $\boldsymbol{y}_{ad2} =\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
-	\item[3.] indegree $\boldsymbol{y}_{ad3}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
-	\item[4.] gender $\boldsymbol{y}_{ad4}=I(a= \mbox{female})$;
-	\item[5.] manager $\boldsymbol{y}_{ad5}=I(a= \mbox{County Manager})$;
-	\item[6.] weekend $\boldsymbol{y}_{ad6} = I(t_{d-1}= \mbox{weekend})$;
-	\item[7.] am/pm $\boldsymbol{y}_{ad7}= I(t_{d-1}= \mbox{pm})$.
+	\item[1.] intercept ${y}_{ad1} =1$;
+	\item[2.] outdegree ${y}_{ad2} =\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+	\item[3.] indegree ${y}_{ad3}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
+	\item[4.] gender ${y}_{ad4}=I(a= \mbox{female})$;
+	\item[5.] manager ${y}_{ad5}=I(a= \mbox{County Manager})$;
+	\item[6.] weekend ${y}_{ad6} = I(t_{d-1}= \mbox{weekend})$;
+	\item[7.] am/pm ${y}_{ad7}= I(t_{d-1}= \mbox{pm})$.
 \end{itemize}
 \subsubsection{Parameter Estimation and Interpretation}\label{subsubsec:Result_email}
-	\begin{figure}[H]
+Based on some preliminary experiments, we choose lognormal distribution to model time-to-next-email in Montgomery county email data, thus we estimate the variance parameter $\sigma_\tau^2$ with the prior specified as inverse-Gamma($2, 1$).
+In this section, we present the results based on 55,000 MCMC outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
+While the inner iterations for $\boldsymbol{\eta}$ and $\sigma_\tau^2$ are fixed as 1, we use 10 inner iterations for $\boldsymbol{b}$ to adjust for its slower convergence rate.
+	\begin{figure}[!b]
 	\centering
@@
 \end{figure}
-	\begin{figure}[ht]
+
+Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of the network effect coefficients $\boldsymbol{b}$.
+Since we use logit probability of $\lambda_{adr}$ for tie generating process (Section \ref{subsec: Tie}), we have
+\begin{equation*}
+\mbox{logit}(\lambda_{adr})=\log\Big(\frac{\lambda_{adr}}{1-\lambda_{adr}}\Big) =b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11},
+\end{equation*}
+and can interpret the parameter estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11})$.
+Firstly, we can see that the effect of send (i.e., ``number of times the actor $a$ sent emails to the actor $r$ over the last week'') is positive, implying that if the actor $a$ sent $n$ number of emails to $r$ last week, then the actor $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
+Similar interpretation can be applied for the statistics indegree and Nrecieve.
+For example, as the actor $r$ received $n$ emails and the actor $a$ sent emails to $n$ rececievers over the last week, the actor $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times and $\exp(0.047\times n)\approx(1.048)^n$ times, respectively, more likely to send an email to $r$.
+On the other hand, outdegree statistic has negative effect---i.e., if the actor $a$ sent $n$ number of emails to anyone last week, then the actor $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times likely to send an email to $r$---possibly due to its multicollinearity with the statistics send and Nreceive.
+This can be interpreted as ``if the actor $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of send) or 2) no broadcast or multicast emails (excluding the effect of Nreceive)'' then the actor $a$ is less likely to send an email to $r$.
+Rest of statistics are not statistically significant because their 95\% credible interval do not include 0.
+Surprisingly, none of the triadic effects seem to have significant effect on the tie generating process.
+
+	Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of the time-related coefficients $\boldsymbol{\eta}$.
+For this specific datset, we assume lognormal distribution (Section \ref{subsec:Time}) with the unit of time being an hour, so that the interpretation of $\hat{\boldsymbol{\eta}}$ should be based on
+\begin{equation*}
+\begin{aligned}
+&\log(\tau_{ad}) \sim N(\mu_{ad}, \sigma_\tau^2), \mbox{ with }\\
+&\mu_{ad} = \eta_{1}+\eta_{2} y_{ad2}\ldots+\eta_{7}y_{ad7}.
+\end{aligned}
+\end{equation*}
+To begin with, the posterior estimates of two temporal effects---weekend and pm---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after 12pm, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx(4.722)$ hours and $\exp(0.980)\approx(2.665)$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+On the contrary, the statistics manager, outdegree, and indegree turn out to shorten the time to next email.
+For example, being a county manager (i.e., the manager of the managers) lowers the expected $\log(\tau_{ad})$ by -1.070, since he or she needs to respond fastly to emails with important decisions.
+In addition, the manager in general sends or receives a lot more emails which may shorten the response time.
+This argument is supported by the posterior estimates for outdegree and indegree, where the estimated coefficients are approximately -0.206 and -0.060, respectively.
+Gender of the department manager is shown to have no significant effect on time-to-next-email.
+The posterior mean estimate of the variance parameter $\sigma^2_\tau$ is 14.093 with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time-increments in this data.
+	\begin{figure}[!t]
 		\centering
@@
 	\end{figure}
-\subsection{Case Study 2: International Sanctions}\label{subsec:International Sanctions}
-\subsubsection{Threat and Imposition of Sanctions (TIES) Data}\label{subsubsec:TIES}
-We processed the threat and imposition of sanctions (TIES) data \citep{morgan2014threat} that includes the records of international sanctions---defined as actions that one or more countries take to limit or end their economic relations with a target country in an effort to persuade that country to change one or more of its policies---from 1945 to 2005.
-\subsubsection{Covariates}\label{subsec:Covariates_sanction}
-\subsubsection{Parameter Estimation and Interpretation}\label{subsubsec:Result_sanction}
-
-\subsection{Experiment}\label{subsubsec:Experiment_email}
-We evaluate the model's ability to predict ties from the Montgomery County email network and the threat and imposition of sanctions (TIES) data, conditioned on their ``training" part of the data.
-We separately formed a test split of each three components---author, recipients, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
-Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, estimates of latent variables, and current estimates of test data.
-The full conditional posterior distributions for ``test" author, recipients, and timestamps are provided in the supplementary material.
-We then run inference to update the latent variables given the imputed and observed data.
-We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for ``test" data.
-Algorithm \ref{alg:PPE} outlines this procedure.
-
-\begin{algorithm}[H]
-	\spacingset{1}
-	\caption{Out-of-Sample Tie Predictions}
-	\label{alg:PPE}
-	\begin{algorithmic}
-		\STATE {\bfseries Input:} data $ \{ (a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, \\
-		number of new data to generate $R$,\\
-		hyperparameters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$\\
-		\vskip 0.1in
-		\textbf{Test splits:}	
-		\STATE Draw test authors with $p=0.1$ (out of $D$ authors) 
-		\STATE Draw test elements of recipient vector 
-		with $p=0.1$ (out of $D\times (A-1)$ receipient indicators $\{\{\boldsymbol{r}_{dr}\}_{r\in [A]_{\backslash a_d}}\}_{d=1}^D$)
-		\STATE Draw test timestamps with $p=0.1$  (out of $D$ timestamps) 
-		\STATE Set the ``test" data as ``missing" (NA)
-		\vskip 0.1in
-		\textbf{Imputation and inference:}	
-		\STATE Initialize the parameters $(\boldsymbol{b}, \boldsymbol{\eta}, \boldsymbol{u}, \sigma^2_\tau)$
-		\FOR{$r=1$ {\bfseries to}  $R$}
-		\FOR{$d=1$ {\bfseries to}  $D$}
-		\IF{$a_d=$  NA}
-		\FOR{$a=1$ {\bfseries to} $A$}
-		\STATE Compute $\pi_{a} $ using $P(a_d= a | \cdot)$
-		\ENDFOR
-		\STATE Draw $a_d \sim \mbox{Multinomial}(\pi)$
-		\ENDIF
-		\FOR{$r\in [A]_{\backslash a_d}$}
-		\IF{$r_{dr}=$ NA}
-		\STATE Draw $r_{dr}$ using $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$ 
-		\ENDIF
-		\ENDFOR
-		\IF{$t_d=$ NA}
-		\STATE Draw proposal $\boldsymbol{\tau}^{new}_d \sim f_\tau(\mu_{a_dd}, \sigma^2_\tau)$
-		\STATE Use Metropolis-Hastings to decide accept or reject using the probability
-		\begin{equation*}
-		\footnotesize
-		\frac{P(\boldsymbol{\tau}^{new}_d|\mu_{a_dd}, \sigma^2_\tau) P(\boldsymbol{\tau}^{new}_d| \cdot)}{P(\boldsymbol{\tau}^{old}_d|\mu_{a_dd}, \sigma^2_\tau) P(\boldsymbol{\tau}^{old}_d| \cdot)},
-		\end{equation*}
-		where $\boldsymbol{\tau}^{old}_d$ is from earlier iteration.
-		\ENDIF
-		\STATE Run inference and update $(\boldsymbol{b}, \boldsymbol{\eta},\boldsymbol{u}, \sigma^2_\tau)$ given the imputed and observed data
-		\ENDFOR
-		\STATE Store the estimates for ``test" data
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
-NOTE: we assume independent Bernoulli trial on $u_{adr}$. Then, does it matter to have test `elements' for the recipient vector instead of having the test `recipient vectors'?
-
-\subsection{Posterior Predictive Checks}\label{subsubsec:PPC_email} 	   
-Finally, we perform posterior predictive checks \cite{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data and the threat and imposition of sanctions (TIES) data.
-We formally generated entirely new data, by simulating ties and timestamps $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{sec:inference}.
-For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data and the threat and imposition of sanctions (TIES) data: indegree distribution, outdegree distribution, recipient size distribution, time-increments distribution, the edgewise shared partner distribution, and the geodesic distance distribution.
-We then generated 500 synthetic networks from the posterior predictive distribution.
-\begin{algorithm}[H]
+	\subsubsection{Posterior Predictive Checks}\label{subsubsec:PPC_email} 	   
+	We perform posterior predictive checks \cite{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data.
+We formally generated entirely new data, by simulating ties and timestamps $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{subsubsec:Result_email}.
+For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data: outdegree distribution, indegree distribution, recipient size distribution, and time-increments probability-probability (PP) plot.
+We then generated 500 synthetic networks from the posterior predictive distribution, according to Algorithm \ref{alg:PPC}.
+	\begin{algorithm}[!t]
 		\spacingset{1}
@@
 		\end{algorithmic}
+		 				\label{alg:PPC}
 	\end{algorithm}
-\subsection{Montgomery County Data}
-	\begin{figure}[H]
+
+	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks.
+Upper two plots show node-specific degree distributions, where the left one is the boxplots of 500 posterior predictive outdegree statistic and the right plot is the same one for indegree statistic.
+For both plots, the x-axis represents the node id's from 1 to 18, and the y-axis represents the number of emails sent or received by the node.
+When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of ties across the nodes.
+For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, without using node-specific indicators.
+Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
+Since we use more information in the recipient selection process (i.e., network effects) while we only rely on minimum time-increments when choosing the observed sender, these results are expected.
+Lower left plot is the distribution of recipient sizes, where the x-axis spans over the size of recipients 1 to 14 (which is the maximum size of observed recipients) and the y-axis denotes the number of documents with x-number of recipients.
+The result shows that our model is underestimating single-receiver documents while overestimating documents with two, three, and four recipients.
+One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the documents with $\geq 10$ number of recipients, so that the intercept estimate $b_1$ is slightly moved toward right.
+To improve the goodness of fit for recipient sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
+In the end, the plot on the lower right is the PP plot for time-increments, which is a graphical measure commonly used for assessing how closely two data sets agree, by plotting the two cumulative distribution functions against each other.
+The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time-increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
+	\begin{figure}[!t]
 		\centering
-		\includegraphics[width=0.49\textwidth]{plots_paper/outdegreenew-1.png}	
-		\includegraphics[width=0.49\textwidth]{plots_paper/indegreenew-1.png}	
-				\includegraphics[width=0.49\textwidth]{plots_paper/recipientsizenew-1.png}	
+		\includegraphics[width=0.495\textwidth]{plots_paper/outdegreenew-1.png}	
+		\includegraphics[width=0.495\textwidth]{plots_paper/indegreenew-1.png}	
+		\includegraphics[width=0.495\textwidth]{plots_paper/recipientsizenew-1.png}	
 		\includegraphics[width=0.31\textwidth]{plots_paper/timeppnew.pdf}
-		\caption {PPC results.}
-		\label{figure:outdegree}
+		\caption {PPC results: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
+Red lines in the first three plot depict the observed statistics, and the red line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
+		\label{figure:PPCresults}
 	\end{figure}
-\subsection{International Sanctions}
+	\subsubsection{Prediction Experiment}\label{subsubsec:Experiment_email}
+Lastly, we evaluate the model's ability to predict ties from the Montgomery County email data, conditioned on their ``training" part of the data.
+To perform the experiment, we separately formed a test split of each three components---sender, recipients, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
+Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, parameter estimates, and current values of test data.
+We then run inference to update the latent variables given the imputed and observed data.
+We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for ``test" data.
+Algorithm \ref{alg:PPE} outlines this procedure in detail, including the full conditional distributions for missing sender, recciever, and timestamps.
+	\begin{algorithm}[!t]
+		\spacingset{1}
+		\caption{Out-of-Sample Tie Predictions}
+		\label{alg:PPE}
+		\begin{algorithmic}
+			\STATE {\bfseries Input:} data $ \{ (a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, 
+			number of new data to generate $R$,
+			hyperparameters
+			\vskip 0.1in
+			\textbf{Test splits:}	
+			\STATE draw test authors with $p=0.1$ (out of $D$ authors) 
+			\STATE draw test recipients
+			with $p=0.1$ (out of $D\times (A-1)$ recipient indicators $\{\{\boldsymbol{r}_{dr}\}_{r\in [A]_{\backslash a_d}}\}_{d=1}^D$)
+			\STATE draw test timestamps with $p=0.1$  (out of $D$ timestamps) 
+			\STATE set the ``test" data as ``missing" (NA)
+			\vskip 0.1in
+			\textbf{Imputation and inference:}	
+			\STATE initialize the parameters $(\boldsymbol{b}, \boldsymbol{\eta}, \boldsymbol{u}, \sigma^2_\tau)$
+			\FOR{$r=1$ {\bfseries to}  $R$}
+			\FOR{$d=1$ {\bfseries to}  $D$}
+			\IF{$a_d=$  NA}
+			\FOR{$a=1$ {\bfseries to} $A$}
+			\STATE compute $\pi_{a} $ using $P(a_d= a | \cdot)=f_{\tau}(\tau_{d}; \mu_{a_dd}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)$
+			\ENDFOR
+			\STATE draw $a_d \sim \mbox{Multinomial}(\pi)$
+			\ENDIF
+			\FOR{$r\in [A]_{\backslash a_d}$}
+			\IF{$r_{dr}=$ NA}
+			\STATE draw $r_{dr}$ using $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$---Equation (7)
+			\ENDIF
+			\ENDFOR
+			\IF{$t_d=$ NA}
+			\STATE draw $\boldsymbol{\tau}^{new}_d$ from proposal distribution (e.g., $\boldsymbol{\tau}^{new}_d \sim N(\boldsymbol{\tau}^{old}_d, \sigma^2_{prop})$)
+			\STATE use Metropolis-Hastings to decide accept or reject using the probability
+			\begin{equation*}
+			\footnotesize
+			\frac{f_{\tau}(\tau^{new}_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big) }{f_{\tau}(\tau^{old}_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)},
+			\end{equation*}
+			where $\boldsymbol{\tau}^{old}_d$ is from earlier iteration.
+			\ENDIF
+			\STATE run inference and update $(\boldsymbol{b}, \boldsymbol{\eta},\boldsymbol{u}, \sigma^2_\tau)$ given the imputed and observed data
+			\ENDFOR
+			\STATE store the estimates for ``test" data
+			\ENDFOR
+		\end{algorithmic}
+	\end{algorithm}
+
+The goal of this task is to provide an effective answer to the question ``how are we filling in the missing information of the emails?" as well as to offer one standard way to determine the time-increment distribution in Section \ref{subsec:Time}.
+To do this, we compare the predictive performance from two distributions---lognormal and Exponential.
+We particularly choose Exponential distribution as an alternative to what we used earlier (i.e., lognormal) since Exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
+
+After running the experiment, we compare the prediction accuracy
+
+\subsection{Case Study 2: International Sanctions}\label{subsec:International Sanctions}
+\subsubsection{Threat and Imposition of Sanctions (TIES) Data}\label{subsubsec:TIES}
+We processed the threat and imposition of sanctions (TIES) data \citep{morgan2014threat} that includes the records of international sanctions---defined as actions that one or more countries take to limit or end their economic relations with a target country in an effort to persuade that country to change one or more of its policies---from 1945 to 2005.
+\subsubsection{Covariates}\label{subsec:Covariates_sanction}
+\subsubsection{Parameter Estimation and Interpretation}\label{subsubsec:Result_sanction}
+	\subsubsection{Posterior Predictive Checks}\label{subsubsec:PPC_sanction} 	 
+		\subsubsection{Prediction Experiment}\label{subsubsec:Experiment_sanction}  
 \section{Conclusion}\label{sec:conclusion}

### 2018-05-09 Emails/PPEnew.R
PPE results updated

@@ -1,0 +1,112 @@
+library(MulticastNetwork)
+load("/Users/bomin8319/Box/gainlab_example/Bomin/Montgomery.RData")
+edge = Montgomery$edge
+X = Montgomery$X
+Y = Montgomery$Y
+P = dim(X)[4]
+Q = dim(Y)[3]
+A = dim(Y)[2]
+
+#run inference to estimate beta, eta, u, and sigma2
+prior.beta = list(mean = c(-3.5, rep(0, P-1)), var = 2*diag(P))
+prior.eta = list(mean = c(7, rep(0, Q-1)), var = 2*diag(Q))
+prior.sigma2 = list(a = 2, b = 1)
+
+outer = 500
+inner = c(1, 1, 1)
+burn = 0
+
+#run infernece
+Montgomery_infer = Inference(edge, X, Y, outer, inner, burn, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
+		  proposal.var = c(0.0001, 0.001, 0.1), timeunit = 3600, lasttime = Montgomery$lasttime, timedist = "lognormal")
+
+# generate data from the model estimates
+#Montgomery_PPC = PPC(length(edge), beta = colMeans(Montgomery_infer$beta), eta = colMeans(Montgomery_infer$eta), 
+#                     sigma2 = mean(Montgomery_infer$sigma2), X, Y, timeunit = 3600, u = Montgomery_infer$u, timedist = "lognormal")
+
+
+set.seed(1)
+missing = list()
+#missingness of senders
+missing[[1]] = matrix(0, nrow = dim(Y)[1], 1)    
+missing[[1]][sample(1:dim(Y)[1], 62, replace = FALSE), ] = 1
+#missingness of receivers
+missing[[2]] = matrix(0, nrow = dim(Y)[1], A)    
+missing[[2]][sample(1:(dim(Y)[1]*A), 1118, replace = FALSE)] = 1
+#missingness of timestamps
+missing[[3]] = matrix(0, nrow = dim(Y)[1], 1)
+missing[[3]][sample(1:dim(Y)[1], 62, replace = FALSE), ] = 1
+
+
+for (d in 1:dim(Y)[1]) {
+	if (missing[[1]][d,1] == 1) {
+		edge[[d]]$a_d = NA
+	}
+	if (sum(missing[[2]][d,]) > 0) {
[…]

### 2018-05-09 pkg/R/Multicast.R

@@ -431,17 +431,17 @@ PPE = function(data, X, Y, outer, inner, burn, prior.beta, prior.eta, prior.sigm
     for (d in timemissing) {
     	tau_new = rnorm(1, timeinc[d], MHprop.var)
         if (timedist == "lognormal") {
-            prior.new0 = dlnorm(tau_new, mu[d, senders[d]], sqrt(sigma2), TRUE)
-            prior.old0 = dlnorm(timeinc[d], mu[d, senders[d]], sqrt(sigma2), TRUE)
+            #prior.new0 = dlnorm(tau_new, mu[d, senders[d]], sqrt(sigma2), TRUE)
+            #prior.old0 = dlnorm(timeinc[d], mu[d, senders[d]], sqrt(sigma2), TRUE)
             post.new0 = Timepartindiv(mu[d,], sqrt(sigma2), tau_new)[senders[d]]
             post.old0 = Timepartindiv(mu[d,], sqrt(sigma2), timeinc[d])[senders[d]]
         } else {
-            prior.new0 = dexp(tau_new, 1/exp(mu[d, senders[d]]), TRUE)
-            prior.old0 = dexp(timeinc[d], 1/exp(mu[d, senders[d]]), TRUE)
+            #prior.new0 = dexp(tau_new, 1/exp(mu[d, senders[d]]), TRUE)
+            #prior.old0 = dexp(timeinc[d], 1/exp(mu[d, senders[d]]), TRUE)
             post.new0 = Timepartindiv2(mu[d,], tau_new)[senders[d]]
             post.old0 = Timepartindiv2(mu[d,], timeinc[d])[senders[d]]
         }
-		loglike.diff = prior.new0+post.new0-prior.old0-post.old0
+		loglike.diff = post.new0-post.old0
     	if (log(runif(1, 0, 1)) < loglike.diff) {
         	timeinc[d] = tau_new
 	    }

### 2018-05-09 paper/paper.tex
PPE results updated
added a paragraph motivating the out of sample experiment

@@
 \usepackage{amsmath}
+\usepackage{bm}
 \usepackage{graphicx,psfrag,epsf}
@@
 	\subsubsection{Prediction Experiment}\label{subsubsec:Experiment_email}
+
+The HeEM ({\bf Hyper-edge event model)	has many component parts that need to be specified by the user (i.e., the selection of the event timing features ($\bm{y}$), the recipient selection features $(\bm{x}$), and the event time distribution ($g$)).
+Many of these components will be specified based on user expertise (e.g., regarding which features would drive recipient selection), but some decisions may require a data-driven approach to model specification.
+For example, though theoretical considerations may inform the specification of features, subject-matter expertise is unlikely to inform the decision regarding the family of the event time distribution.
+Furthermore, since different distribution families (and model specifications more generally) may involve different size parameter spaces, any data-driven approach to model comparison must guard against over-fitting the data.
+In this section we present a general-purpose approach to evaluating a HeEM specification using out-of-sample prediction.
+We illustrate this approach by comparing alternative distributional families for the event timing component of the model.
+
 Lastly, we evaluate the model's ability to predict ties from the Montgomery County email data, conditioned on their ``training" part of the data.
@@
 
-After running the experiment, we compare the prediction accuracy
+After running the experiment, we measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
+	\begin{figure}[!b]
+		\centering
+		\includegraphics[width=0.33\textwidth]{plots_paper/outdegreenew-1.png}	
+		\includegraphics[width=0.33\textwidth]{plots_paper/indegreenew-1.png}	
+		\includegraphics[width=0.33\textwidth]{plots_paper/recipientsizenew-1.png}	
+		\caption {PPE results}
+		\label{figure:PPEresults}
+	\end{figure}
 

### 2018-05-09 paper/paper.tex
PPE results
writing more about out of sample stuff
compiled pdf

@@
 
-The HeEM ({\bf Hyper-edge event model)	has many component parts that need to be specified by the user (i.e., the selection of the event timing features ($\bm{y}$), the recipient selection features $(\bm{x}$), and the event time distribution ($g$)).
+The HeEM ({\bf Hyper-edge event model})	has many component parts that need to be specified by the user (i.e., the selection of the event timing features ($\bm{y}$), the recipient selection features $(\bm{x}$), and the event time distribution ($g$)).
 Many of these components will be specified based on user expertise (e.g., regarding which features would drive recipient selection), but some decisions may require a data-driven approach to model specification.
@@
 We illustrate this approach by comparing alternative distributional families for the event timing component of the model.
+
+Good example article: \url{https://projecteuclid.org/download/pdfview_1/euclid.ba/1457383101}
 
@@
 		\centering
-		\includegraphics[width=0.33\textwidth]{plots_paper/outdegreenew-1.png}	
-		\includegraphics[width=0.33\textwidth]{plots_paper/indegreenew-1.png}	
-		\includegraphics[width=0.33\textwidth]{plots_paper/recipientsizenew-1.png}	
+		\includegraphics[width=0.495\textwidth]{plots_paper/senderpredict-1.png}	
+		\includegraphics[width=0.495\textwidth]{plots_paper/receiverpredict2-1.png}	
 		\caption {PPE results}

### 2018-05-10 ba/ba-sample.tex
changed to HeEM model

\RequirePackage{etoolbox}
\csdef{input@path}{%
 {sty/}% cls, sty files
 {img/}% eps files
}%
\csgdef{bibdir}{bib/}% bst, bib files

\documentclass[ba]{imsart}
%
\pubyear{0000}
\volume{00}
\issue{0}
\doi{0000}
\firstpage{1}
\lastpage{1}

%
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}

\startlocaldefs
\numberwithin{equation}{section}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\endlocaldefs

\begin{document}

\begin{frontmatter}
\title{A Hyper-edge Event Model\thanksref{T1}}
\runtitle{A Hyper-edge Event Model}
\thankstext{T1}{Footnote to the title with the ``thankstext'' command.}

\begin{aug}
\author{\fnms{Bomin} \snm{Kim}\thanksref{addr1,t1,t2,m1}\ead[label=e1]{first@somewhere.com}},
\author{\fnms{Aaron} \snm{Achein}\thanksref{addr1,t3,m1,m2}\ead[label=e2]{second@somewhere.com}},
\author{\fnms{Bruce} \snm{Desmarais}\thanksref{addr1,t3,m1,m2}\ead[label=e2]{second@somewhere.com}},
\and
\author{\fnms{Hanna} \snm{Wallach}\thanksref{addr2,t1,m2}
\ead[label=e3]{third@somewhere.com}
\ead[label=u1,url]{http://www.foo.com}}

\runauthor{Kim et al.}

\address[addr1]{Address of the First and Second authors
     Usually a few lines long 
    \printead{e1} % print email address of "e1"
    \printead*{e2}
}

\address[addr2]{Address of the Third author
    Usually a few lines long
    Usually a few lines long
    \printead{e3}
    \printead{u1}
}

\thankstext{t1}{Some comment}
\thankstext{t2}{First supporter of the project}
\thankstext{t3}{Second supporter of the project}

\end{aug}

\begin{abstract}
We introduce the hyper-edge event model (HeEM)---a generative model for directed edges with multiple recipients or multiple senders. To define the model, we
integrate a dynamic version of the exponential random graph model (ERGM) and generalized linear model (GLM) approach to jointly understand who communicates with whom, and when. We use
the model to analyze emails sent between department managers in Montgomery county government in North Carolina. Our application demonstrates that the model is effective at predicting and explaining time-stamped network data involving edges with multiple recipients.
\end{abstract}

\begin{keyword}[class=MSC]
\kwd[Primary ]{60K35}
\kwd{60K35}
\kwd[; secondary ]{60K35}
\end{keyword}

\begin{keyword}
\kwd{sample}
\kwd{\LaTeXe}
\end{keyword}

\end{frontmatter}

\section{Introduction}

The ends of words and sentences are marked by spaces. It doesn't
matter how many spaces you type; one is as good as 100.  The end of a
line counts as a space.

One or more blank lines denote the end of a paragraph.

Since any number of consecutive spaces are treated like a single one,
the formatting of the input file makes no difference to
\TeX, % The \TeX command generates the TeX logo.
but it makes a difference to you.  When you use
\LaTeX, % The \LaTeX command generates the LaTeX logo.
making your input file as easy to read as possible will be a great
help as you write your document and when you change it.  This sample
file shows how you can add comments to your own input file.

Because printing is different from typewriting, there are a number of
things that you have to do differently when preparing an input file
than if you were just typing the document directly.  Quotation marks
like ``this'' have to be handled specially, as do quotes within
quotes: ``\,`this' % \, separates the double and single quote.
is what I just wrote, not `that.'\,''

Dashes come in three sizes: a hyphen, %an intra-word dash,
a medium dash for number ranges like 1--2, and a punctuation dash in
place of a comma, semicolon, colon or parentheses ---like this.

A sentence-ending space should be larger than the space between words
within a sentence.  You sometimes have to type special commands in
conjunction with punctuation characters to get this right, as in the
following sentence.  Gnats, gnus,
etc.\ % `\ ' makes an inter-word space.
all begin with G\@.  % \@ marks end-of-sentence punctuation.
You should check the spaces after periods when reading your output to
make sure you haven't forgotten any special cases.  Generating an
ellipsis \ldots\ % `\ ' needed because TeX ignores spaces after
          % command names like \ldots made from \ + letters.
          %
          % Note how a `%' character causes TeX to ignore the
          % end of the input line, so these blank lines do not
          % start a new paragraph.
with the right spacing around the periods
requires a special  command.

\TeX\ interprets some common characters as commands, so you must type
special commands to generate them.  These characters include the
following:
%       \$ - arXiv do not like it...
        \& \% \# \{ and~\}.

In printing, text is emphasized by using an {\em
          italic\/} % The \/ command produces the tiny extra space that
               % should be added between a slanted and a following
               % unslanted letter.
type style.

\begin{em}
  A long segment of text can also be emphasized in this way.  Text
  within such a segment given additional emphasis with\/ {\em Roman}
  type.  Italic type loses its ability to emphasize and become simply
  distracting when used excessively.
\end{em}

It is sometimes necessary to prevent \TeX\ from breaking a line where
it might otherwise do so.  This may be at a space, as between the
``Mr.'' and ``Jones'' in
``Mr.~Jones'', % ~ produces an unbreakable interword space.
or within a word---especially when the word is a symbol like \mbox{\em
  itemnum\/} that makes little sense when hyphenated across lines.

\TeX\ is good at typesetting mathematical formulas like \( x-3y = 7 \)
or \( a_{1} > x^{2n} / y^{2n} > x' \).  Remember that a letter like
$x$ % $ ... $ and \( ... \) are equivalent
is a formula when it denotes a mathematical symbol, and should be
treated as one.

\section{Notes}

Footnotes\footnote{This is an example of a footnote.}  pose no
problem\footnote{And another one}.

\section{Displayed text}

Text is displayed by indenting it from the left margin.  Quotations
are commonly displayed.  There are short quotations
\begin{quote}
  This is a short a quotation.  It consists of a single paragraph of
  text.  There is no paragraph indentation.
\end{quote}
and longer ones.
\begin{quotation}
  This is a longer quotation.  It consists of two paragraphs of text.
  The beginning of each paragraph is indicated by an extra
  indentation.

  This is the second paragraph of the quotation.  It is just as dull
  as the first paragraph.
\end{quotation}
Another frequently displayed structure is a list.  The following is an
example of an {\em itemized} list, four levels deep.
\begin{itemize}
\item This is the first item of an itemized list.  Each item in the
  list is marked with a ``tick.''  The document style determines what
  kind of tick mark is used.
\item This is the second item of the list.  It contains another list
  nested inside it.  The three inner lists are an {\em itemized} list.
    \begin{itemize}
    \item This is the first item of an enumerated list that is nested
      within the itemized list.
    \item This is the second item of the inner list.  \LaTeX\ allows
      you to nest lists deeper than you really should.
    \end{itemize}
    This is the rest of the second item of the outer list.  It is no
    more interesting than any other part of the item.
   \item  This is the third item of the list.
\end{itemize}

The following is an example of an {\em enumerated} list, four levels
deep.
\begin{enumerate}
\item This is the first item of an enumerated list.  Each item in the
  list is marked with a ``tick.''  The document style determines what
  kind of tick mark is used.
\item This is the second item of the list.  It contains another list
  nested inside it.  The three inner lists are an {\em enumerated}
  list.
  \begin{enumerate}
  \item This is the first item of an enumerated list that is nested
    within the enumerated list.
  \item This is the second item of the inner list.  \LaTeX\ allows you
    to nest lists deeper than you really should.
  \end{enumerate}
  This is the rest of the second item of the outer list.  It is no
  more interesting than any other part of the item.
\item This is the third item of the list.
\end{enumerate}

The following is an example of a {\em description} list.
\begin{description}
\item[Cow] Highly intelligent animal that can produce milk out of grass.
\item[Horse] Less intelligent animal renowned for its legs.
\item[Human being] Not so intelligent animal convinced it can think.
\end{description}

You can even display poetry.
\begin{verse}
  There is an environment for verse
  \\ % The \\ command separates lines
  Whose features some poets will curse.  % within a stanza.

               % One or more blank lines separate stanzas.

  For instead of making\\
  Them do {\em all\/} line breaking, \\
  It allows them to put too many words on a line when they'd rather be
  forced to be terse.
\end{verse}

Mathematical formulas may also be displayed.  A displayed formula is
one-line long:

   \[  x' + y^{2} = z_{i}^{2};\]

   multiline formulas require special formatting instructions.

   Do not start a paragraph with a displayed equation, nor make one a
   paragraph by itself.

Example of a theorem:

\begin{thm}
All conjectures are interesting, but some conjectures are more
interesting than others.
\end{thm}

\begin{proof}
Obvious.
\end{proof}

\section{Tables and figures}
Cross reference to labeled table: As you can see in Table~\ref{sphericcase} on
page~\pageref{sphericcase} and also in Table~\ref{parset} on page~\pageref{parset}.

\begin{table*}
\begin{tabular}{crrrrc}
\hline
Equil. \\
Points & \multicolumn{1}{c}{$x$} & \multicolumn{1}{c}{$y$} & \multicolumn{1}{c}{$z$} & \multicolumn{1}{c}{$C$} &
S \\
\hline
$~~L_1$ & $-$2.485252241 & 0.000000000 & 0.017100631 & 8.230711648 & U \\
$~~L_2$ &    0.000000000 & 0.000000000 & 3.068883732 & 0.000000000 & S \\
$~~L_3$ &    0.009869059 & 0.000000000 & 4.756386544 & $-$0.000057922 & U \\
$~~L_4$ &    0.210589855 & 0.000000000 & $-$0.007021459 & 9.440510897 & U \\
$~~L_5$ &    0.455926604 & 0.000000000 & $-$0.212446624 & 7.586126667 & U \\
$~~L_6$ &    0.667031314 & 0.000000000 & 0.529879957 & 3.497660052 & U \\
$~~L_7$ &    2.164386674 & 0.000000000 & $-$0.169308438 & 6.866562449 & U \\
$~~L_8$ &    0.560414471 & 0.421735658 & $-$0.093667445 & 9.241525367 & U \\
$~~L_9$ &    0.560414471 & $-$0.421735658 & $-$0.093667445 & 9.241525367 & U
\\
$~~L_{10}$ & 1.472523232 & 1.393484549 & $-$0.083801333 & 6.733436505 & U \\
$~~L_{11}$ & 1.472523232 & $-$1.393484549 & $-$0.083801333 & 6.733436505 & U
\\ \hline
\end{tabular}
\caption{The spherical case ($I_1=0$, $I_2=0$)}
\label{sphericcase}
\end{table*}

A major point of difference lies in the value of the specific
production rate $\pi$ for large values of the specific growth rate
$\mu$.  Already in the early publications \cite{akaike,dyke,greene} it
appeared that high glucose concentrations in the production phase are
well correlated with a low penicillin yield (the ``glucose
effect''). It has been confirmed recently
\cite{akaike,dyke,greene,hilbe} that high glucose concentrations
inhibit the synthesis of the enzymes of the penicillin pathway, but
not the actual penicillin biosynthesis.  In other words, glucose
represses (and not inhibits) the penicillin biosynthesis.

These findings do not contradict the results of \cite{akaike} and of
\cite{hilbe} which were obtained for continuous culture fermentations.
Because for high values of the specific growth rate $\mu$ it is most
likely (as shall be discussed below) that maintenance metabolism
occurs, it can be shown that in steady state continuous culture
conditions, and with $\mu$ described by a Monod kinetics
\begin{equation}
    C_{s}  =  K_{M} \frac{\mu/\mu_{x}}{1-\mu/\mu_{x}} \label{cs}
\end{equation}
Pirt \& Rhigelato determined $\pi$ for $\mu$ between
$0.023$ and $0.086$ h$^{-1}$.
They also reported a value $\mu_{x} \approx 0.095$
h$^{-1}$, so that for their experiments $\mu/\mu_{x}$ is in the range
of $0.24$ to $0.9$.
Substituting $K _M$ in equation (\ref{cs}) by
the value $K_{M}=1$ g/L as used by \cite{akaike}, one finds
with the above equation $0.3 < C_{s} < 9$ g/L. This agrees with
the work of  \cite{hilbe}, who reported that penicillin biosynthesis
repression only occurs at glucose concentrations from $C_{s}=10$ g/L on.
The conclusion is that the glucose concentrations in the experiments of
Pirt \& Rhigelato probably were too low for glucose repression to be
detected. The experimental data published by Ryu \& Hospodka
are not detailed sufficiently to permit a similar analysis.

\begin{table}
\begin{tabular}{lrll}
\hline
\multicolumn{2}{l}{\it parameter} & {\it Set 1} & {\it Set 2}\\
\hline
$\mu_{x}$           & [h$^{-1}$]  & 0.092       & 0.11          \\
$K_{x}$             & [g/g DM]     & 0.15        & 0.006         \\
$\mu_{p}$           & [g/g DM h]  & 0.005       & 0.004         \\
$K_{p}$             & [g/L]        & 0.0002      & 0.0001        \\
$K_{i}$             & [g/L]        & 0.1         & 0.1           \\
$Y_{x/s}$           & [g DM/g]     & 0.45        & 0.47          \\
$Y_{p/s}$           & [g/g]        & 0.9         & 1.2           \\
$k_{h}$             & [h$^{-1}$]  & 0.04        & 0.01          \\
$m_{s}$             & [g/g DM h]  & 0.014       & 0.029         \\
\hline
\end{tabular}
\caption{Parameter sets used by Bajpai \& Reu\ss\ }\label{parset}
\end{table}

Bajpai \& Reu\ss\ decided to disregard the differences between time
constants for the two regulation mechanisms (glucose repression or
inhibition) because of the relatively very long fermentation times,
and therefore proposed a Haldane expression for $\pi$.

It is interesting that simulations with the \cite{hilbe} model for the
initial conditions given by these authors indicate that, when the
remaining substrate is fed at a constant rate, a considerable and
unrealistic amount of penicillin is produced when the glucose
concentration is still very high \cite{dyke,greene,hilbe} Simulations
with the Bajpai \& Reu\ss\ model correctly predict almost no
penicillin production in similar conditions.

% figure 1
\begin{figure} 
\includegraphics{fig001}
\caption[]{Pathway of the penicillin G biosynthesis.}
\label{penG}
\end{figure}

Sample of cross-reference to figure.
Figure~\ref{penG} shows that is not easy to get something on paper.

\section{Headings}

\subsection{Subsection}

Carr--Goldstein based their model on balancing methods and biochemical
know\-ledge. The original model (1980) contained an equation for the
oxygen dynamics which has been omitted in a second paper (1981). This
simplified model shall be discussed here.

\subsubsection{Subsubsection}

Carr--Goldstein based their model on balancing methods and biochemical
know\-ledge. The original model (1980) contained an equation for the
oxygen dynamics which has been omitted in a second paper (1981). This
simplified model shall be discussed here.

\section{Equations and the like}

Two equations:
\begin{equation}
    C_{s}  =  K_{M} \frac{\mu/\mu_{x}}{1-\mu/\mu_{x}} \label{ccs}
\end{equation}
and
\begin{equation}
    G = \frac{P_{\rm opt} - P_{\rm ref}}{P_{\rm ref}} \mbox{\ }100 \mbox{\ }(\%).
\end{equation}

Two equation arrays:

\begin{eqnarray}
  \frac{dS}{dt} & = & - \sigma X + s_{F} F\\
  \frac{dX}{dt} & = &   \mu    X\\
  \frac{dP}{dt} & = &   \pi    X - k_{h} P\\
  \frac{dV}{dt} & = &   F
\end{eqnarray}
and
\begin{eqnarray}
 \mu_{\rm substr} & = & \mu_{x} \frac{C_{s}}{K_{x}C_{x}+C_{s}}  \\
 \mu              & = & \mu_{\rm substr} - Y_{x/s}(1-H(C_{s}))(m_{s}+\pi /Y_{p/s}) \\
 \sigma           & = & \mu_{\rm substr}/Y_{x/s}+ H(C_{s}) (m_{s}+ \pi /Y_{p/s}).
\end{eqnarray}

\begin{supplement}
\sname{Supplement A}\label{suppA} 
\stitle{Title of the Supplement A}
\slink[url]{http://www.some-url-address.org/dowload/0000.zip}
\sdescription{Add description for supplement material.}
\end{supplement}

The following are some other citations to check that the bibliographc style
file is working correctly: \citet{akaike}, \citet*{akivarsq}, \citet{dyke},
\citet{greene}, \citet*{kstuart}, \citet{hilbetech}, \citet{hilbe},
\citet{hilbeglm}, \citet{maddalacntrsq}, and \citet*{companion}.

\bibliographystyle{ba}
\bibliography{sample}

\begin{acknowledgement}
And this is an acknowledgements section with a heading that was produced by the
$\backslash$section* command. Thank you all for helping me writing this
\LaTeX\ sample file. See \ref{suppA} for the supplementary material example.
\end{acknowledgement}

\end{document}

### 2018-05-10 paper/paper.tex
changed to HeEM model

@@
 {
-  \title{\bf A Continuous-time Multicast \\Network Model}
+  \title{\bf A Hyper-edge Event Model}
   \author{Bomin Kim\thanks{
@@
 } \fi
-
 \if1\blind
@@
   \begin{center}
-    {\LARGE\bf A Continuous-time Multicast Network Model}
+    {\LARGE\bf A Hyper-edge Event Model}
 \end{center}
@@
 \begin{abstract}
-We introduce the continuous-time multicast network model---a generative model for directed edges with multiple recipients or multiple senders. To define the model, we
-integrate a dynamic version of the exponential random graph model (ERGM) and generalized linear model (GLM) approach to jointly understand who communicates with whom, and when. We use
-the model to analyze emails sent between department managers in Montgomery county government in North Carolina.
-Our application demonstrates that the model is effective at predicting and explaining continuous-time networks involving edges with multiple recipients.
+We introduce the hyper-edge event model (HeEM)---a generative model for directed edges with multiple recipients or multiple senders. To define the model, we
+integrate a dynamic version of the exponential random graph model (ERGM) and generalized linear model (GLM) approach to jointly understand who communicates with whom, and when.
+We use the model to analyze emails sent between department managers in Montgomery county government in North Carolina.
+Our application demonstrates that the model is effective at predicting and explaining time-stamped network data involving edges with multiple recipients.
 	\end{abstract}
@@
 A number of models that build upon topic modeling through Latent Dirichlet Allocation \citep{Blei2003} to incorporate link data as well as textual content have been developed recently \citep{mccallum2005author,lim2013twitter,Krafft2012}.
-These models are innovative in their extensions that incorporate network tie information.
+These models are innovative in their extensions that incorporate network information.
 However, none of the models that are currently available in the literature integrate the rich random-graph structure offered by state of the art models for network structure---such as the exponential random graph model (ERGM) \citep{robins2007introduction,chatterjee2013estimating,hunter2008ergm}.
 The ERGM is the canonical model for modeling the structure of a static network.
-It is flexible enough to specify a generative model that accounts for nearly any pattern of tie formation such as reciprocity, clustering, popularity effects \citep{desmarais2017statistical}.
+It is flexible enough to specify a generative model that accounts for nearly any pattern of edge formation such as reciprocity, clustering, popularity effects \citep{desmarais2017statistical}.
 
-Several network models have been developed that handle time-stamped ties in which tie formation is governed by structural dynamics similar to those used in the ERGM \citep{Butts2008,Vu2011,snijders1996stochastic}.
-Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows multicast---edge with a single sender multiple recipients---which is a common property of digitalized textual interactions such as emails and online messages.
+Several network models have been developed that handle time-stamped events in which edge formation is governed by structural dynamics similar to those used in the ERGM \citep{Butts2008,Vu2011,snijders1996stochastic}.
+Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows hyper-edges---a connection between two or more vertices\footnote{A hyper-edge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
 For instance, \cite{snijders2007modeling} develops the co-evolution model which assumes that the network structure (``network") and the individual attributes (``behaviour") evolve simultaneously in a dynamic process, however, the model does not allow simultaneous changes within ``networks" or ``behaviour"---all within changes are ordered.
-Relatedly, \cite{PerryWolfe2012} treat multicast interactions via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
-Concentrating on better handling of multicast, we develop the continuous-time multicast network model which simultaneously models the two components that govern time-stamped tie formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
+Relatedly, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyper-edge which involve one sender and multiple receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
+Concentrating on better handling of hyper-edges, we develop the hyper-edge event model (HeEM) which simultaneously models the two components that govern time-stamped event formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
 
-In what follows, we introduce the continuous-time multicast network model by describing how we assume the generatve process of a time-stamped network data (Section 2), and deriving the sampling equations for Bayesian inference (Section 3).
+In what follows, we introduce the HeEM by describing how we assume the generatve process of a time-stamped event data (Section 2), and deriving the sampling equations for Bayesian inference (Section 3).
 Then, we apply the model to the Montgomery county government email data and perform two model validation tasks (Section 4).
@@
 
-\section{A Continuous-time Multicast Network Model}\label{sec:generative process}
+\section{A Hyper-Edge Event Model (HeEM)}\label{sec:generative process}
 Data generated under the model consists of $D$ unique edges.
@@
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
-While the model can be applied for networks with multiple senders and a single receiver, specifically by modifying $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ be the single recipient, here we only present the generative process for those involving a single sender but multiple receivers.
-\subsection{Tie Generating Process}\label{subsec: Tie}
+While the model can be applied for two type of hyper-edges---edges with (1) a single sender and multiple receivers, and (2) multiple senders and a single receiver---here we only present the generative process for those involving a single sender and multiple receivers (i.e., multicast).
+For the latter case of hyper-edges, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single recipient.
+\subsection{Edge Generating Process}\label{subsec: Tie}
 For every possible author--recipient pair $(a,r)_{a \neq r}$, we define the ``recipient intensity", which is the likelihood of edge $d$ being sent from $a$ to $r$:
@@
 				\For{r=1 to $A$ (r $\neq$ a)}{
-						form $\boldsymbol{x}_{adr}$\\
 						set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
@@
 					\mbox{Gibbs}(\boldsymbol{\lambda}_{ad})$\\
-					form $\boldsymbol{y}_{ad}$\\
 					set $\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad})$\\
@@
  \end{algorithm}
-\section{Case Studies}\label{sec:case studies}
-We now present two case studies applying our method to 1) county government emails (single sender multiple recipients) and 2) international sanctions (multiple senders single recipient).
-For each case study,
-we formulate the network statistics $\boldsymbol{x}$ and timestamp statistics $\boldsymbol{y}$ and ground them in
-illustrative examples. We then report a suite of experiments that test our method’s ability to form the posterior distribution over latent variables for different types of data. 
- 	   \subsection{Case Study 1: County Government Emails}\label{subsec:Emails}
- 	  	   \subsubsection{Montgomary County Data}\label{subsubsec:Montgomery}
+ 	   \section{Application to Montgomary County Emails}\label{subsec:Emails}
+ 	  We now present a case study applying our method to Montgomery county government email data. For this case study,
+ 	  we formulate the network statistics $\boldsymbol{x}$ and timestamp statistics $\boldsymbol{y}$ and ground them in illustrative examples.
+We then report a suite of experiments that test our method’s ability to form the posterior distribution over latent variables.
+ 	  	   \subsection{Data}\label{subsec:Montgomery}
  	   Our data come from the North Carolina county government email dataset collected by \cite{ben2017transparency} that includes internal email corpora covering the inboxes and outboxes of managerial-level employees of North Carolina county governments.
@@
 The Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
- 	   \subsubsection{Covariates}\label{subsec:Covariates_email}
+ 	   \subsection{Covariates}\label{subsec:Covariates_email}
 	In the example of email networks, we form the covariate vector $\boldsymbol{x}_{adr}$ using time-varying network statistics based on the time interval prior to and including $t_{d-1}$.
@@
 \end{itemize}
-\subsubsection{Parameter Estimation and Interpretation}\label{subsubsec:Result_email}
+\subsection{Parameter Estimation and Interpretation}\label{subsec:Result_email}
 Based on some preliminary experiments, we choose lognormal distribution to model time-to-next-email in Montgomery county email data, thus we estimate the variance parameter $\sigma_\tau^2$ with the prior specified as inverse-Gamma($2, 1$).
@@
 
-Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of the network effect coefficients $\boldsymbol{b}$.
-Since we use logit probability of $\lambda_{adr}$ for tie generating process (Section \ref{subsec: Tie}), we have
+Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$.
+Since we use logit probability of $\lambda_{adr}$ for edge generating process (Section \ref{subsec: Tie}), we have
 \begin{equation*}
@@
 Rest of statistics are not statistically significant because their 95\% credible interval do not include 0.
-Surprisingly, none of the triadic effects seem to have significant effect on the tie generating process.
+Surprisingly, none of the triadic effects seem to have significant effect on the edge generating process.
 
@@
 \end{equation*}
-To begin with, the posterior estimates of two temporal effects---weekend and pm---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after 12pm, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx(4.722)$ hours and $\exp(0.980)\approx(2.665)$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+	\begin{figure}[!b]
+		\centering
+		\includegraphics[width=0.89\textwidth]{plots_paper/etaest-1.png}	
+		\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
+		\label{figure:etaresults}
+	\end{figure}
+To begin with, the posterior estimates of two temporal effects---weekend and pm---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after 12pm, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
 On the contrary, the statistics manager, outdegree, and indegree turn out to shorten the time to next email.
@@
 The posterior mean estimate of the variance parameter $\sigma^2_\tau$ is 14.093 with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time-increments in this data.
-	\begin{figure}[!t]
-		\centering
-		\includegraphics[width=0.89\textwidth]{plots_paper/etaest-1.png}	
-		\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
-		\label{figure:etaresults}
-	\end{figure}
-	\subsubsection{Posterior Predictive Checks}\label{subsubsec:PPC_email} 	   
+	\subsection{Posterior Predictive Checks}\label{subsec:PPC_email} 	   
 	We perform posterior predictive checks \cite{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data.
-We formally generated entirely new data, by simulating ties and timestamps $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{subsubsec:Result_email}.
+We formally generated entirely new data, by simulating time-stamped events $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{subsec:Result_email}.
 For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data: outdegree distribution, indegree distribution, recipient size distribution, and time-increments probability-probability (PP) plot.
 We then generated 500 synthetic networks from the posterior predictive distribution, according to Algorithm \ref{alg:PPC}.
-	\begin{algorithm}[!t]
+	\begin{algorithm}[!b]
 		\spacingset{1}
@@
 	\end{algorithm}       
-
-	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks.
-Upper two plots show node-specific degree distributions, where the left one is the boxplots of 500 posterior predictive outdegree statistic and the right plot is the same one for indegree statistic.
-For both plots, the x-axis represents the node id's from 1 to 18, and the y-axis represents the number of emails sent or received by the node.
-When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of ties across the nodes.
-For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, without using node-specific indicators.
-Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
-Since we use more information in the recipient selection process (i.e., network effects) while we only rely on minimum time-increments when choosing the observed sender, these results are expected.
-Lower left plot is the distribution of recipient sizes, where the x-axis spans over the size of recipients 1 to 14 (which is the maximum size of observed recipients) and the y-axis denotes the number of documents with x-number of recipients.
-The result shows that our model is underestimating single-receiver documents while overestimating documents with two, three, and four recipients.
-One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the documents with $\geq 10$ number of recipients, so that the intercept estimate $b_1$ is slightly moved toward right.
-To improve the goodness of fit for recipient sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
-In the end, the plot on the lower right is the PP plot for time-increments, which is a graphical measure commonly used for assessing how closely two data sets agree, by plotting the two cumulative distribution functions against each other.
-The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time-increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
 	\begin{figure}[!t]
@@
 	\end{figure}
-	\subsubsection{Prediction Experiment}\label{subsubsec:Experiment_email}
+	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks.
+Upper two plots show node-specific degree distributions, where the left one is the boxplots of 500 posterior predictive outdegree statistic and the right plot is the same one for indegree statistic.
+For both plots, the x-axis represents the node id's from 1 to 18, and the y-axis represents the number of emails sent or received by the node.
+When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes.
+For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, without using node-specific indicators.
+Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
+Since we use more information in the recipient selection process (i.e., network effects) while we only rely on minimum time-increments when choosing the observed sender, these results are expected.
+Lower left plot is the distribution of recipient sizes, where the x-axis spans over the size of recipients 1 to 14 (which is the maximum size of observed recipients) and the y-axis denotes the number of documents with x-number of recipients.
+The result shows that our model is underestimating single-receiver documents while overestimating documents with two, three, and four recipients.
+One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the documents with $\geq 10$ number of recipients, so that the intercept estimate $b_1$ is slightly moved toward right.
+To improve the goodness of fit for recipient sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
+In the end, the plot on the lower right is the PP plot for time-increments, which is a graphical measure commonly used for assessing how closely two data sets agree, by plotting the two cumulative distribution functions against each other.
+The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time-increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
+	\subsection{Prediction Experiment}\label{subsec:Experiment_email}
 
-The HeEM ({\bf Hyper-edge event model})	has many component parts that need to be specified by the user (i.e., the selection of the event timing features ($\bm{y}$), the recipient selection features $(\bm{x}$), and the event time distribution ($g$)).
+The HeEM has many component parts that need to be specified by the user (i.e., the selection of the event timing features $\bm{y}$, the recipient selection features $\bm{x}$, and the event time distribution $f$).
 Many of these components will be specified based on user expertise (e.g., regarding which features would drive recipient selection), but some decisions may require a data-driven approach to model specification.
@@
 Furthermore, since different distribution families (and model specifications more generally) may involve different size parameter spaces, any data-driven approach to model comparison must guard against over-fitting the data.
-In this section we present a general-purpose approach to evaluating a HeEM specification using out-of-sample prediction.
+In this section we present a general-purpose approach to evaluating the HeEM specification using out-of-sample prediction.
 We illustrate this approach by comparing alternative distributional families for the event timing component of the model.
+\iffalse
+Good example article: \url{https://projecteuclid.org/download/pdfview_1/euclid.ba/1457383101}
+	\fi
 
-Good example article: \url{https://projecteuclid.org/download/pdfview_1/euclid.ba/1457383101}
-
-Lastly, we evaluate the model's ability to predict ties from the Montgomery County email data, conditioned on their ``training" part of the data.
+We evaluate the model's ability to predict edges and timestamps from the Montgomery County email data, conditioned on their ``training" part of the data.
 To perform the experiment, we separately formed a test split of each three components---sender, recipients, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
@@
 We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for ``test" data.
-Algorithm \ref{alg:PPE} outlines this procedure in detail, including the full conditional distributions for missing sender, recciever, and timestamps.
+Algorithm \ref{alg:PPE} outlines this procedure in detail.
 	\begin{algorithm}[!t]
 		\spacingset{1}
-		\caption{Out-of-Sample Tie Predictions}
+		\caption{Out-of-Sample Predictions}
 		\label{alg:PPE}
@@
 	\end{figure}
-
+\iffalse
 \subsection{Case Study 2: International Sanctions}\label{subsec:International Sanctions}
@@
 		\subsubsection{Prediction Experiment}\label{subsubsec:Experiment_sanction} 
+		\fi 
 \section{Conclusion}\label{sec:conclusion}

### 2018-05-13 paper/paper.tex
minor edits

@@
 Relatedly, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyper-edge which involve one sender and multiple receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
+Similarly, \cite{fan2009learning} treats multicast emails as multiple single-recipient edges and randomly jitter the sent times, to avoid the violation of continous-time model assumption.
 Concentrating on better handling of hyper-edges, we develop the hyper-edge event model (HeEM) which simultaneously models the two components that govern time-stamped event formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
@@
 We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each parameter from its conditional posterior given the observed data, hyperparamters, and the current values of the other parameters.
-We express each parameter’s conditional posterior in a closed form using the data augmentation schemes in $\boldsymbol{u}$ \cite{tanner1987calculation}.
+We express each parameter’s conditional posterior in a closed form using the data augmentation schemes in $\boldsymbol{u}$ \citep{tanner1987calculation}.
 In this section, we provide each latent variable's conditional posterior.
@@
 	\subsection{Posterior Predictive Checks}\label{subsec:PPC_email} 	   
-	We perform posterior predictive checks \cite{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data.
+	We perform posterior predictive checks \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data.
 We formally generated entirely new data, by simulating time-stamped events $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{subsec:Result_email}.
@@
 	\end{figure}
+
 	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks.
@@
 \end{equation*}
-Finally, the closed form expression for the normalizing constant under the non-empty Gibbs measure is  \begin{equation*}
+Finally, the closed form expression for the normalizing constant is  \begin{equation*}
 \begin{aligned}Z(\boldsymbol{\lambda}_{ad}) = \prod_{r \neq a } \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1.

### 2018-05-14 paper/paper.tex
importance sampling in PPE

@@
 Several network models have been developed that handle time-stamped events in which edge formation is governed by structural dynamics similar to those used in the ERGM \citep{Butts2008,Vu2011,snijders1996stochastic}.
-Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows hyper-edges---a connection between two or more vertices\footnote{A hyper-edge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
-For instance, \cite{snijders2007modeling} develops the co-evolution model which assumes that the network structure (``network") and the individual attributes (``behaviour") evolve simultaneously in a dynamic process, however, the model does not allow simultaneous changes within ``networks" or ``behaviour"---all within changes are ordered.
-Relatedly, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyper-edge which involve one sender and multiple receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
+Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows hyper-edges---a connection between two or more vertices generated simultaneously\footnote{A hyper-edge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
+For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyper-edge which involve one sender and multiple receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
 Similarly, \cite{fan2009learning} treats multicast emails as multiple single-recipient edges and randomly jitter the sent times, to avoid the violation of continous-time model assumption.
@@
  	\caption{MCMC Algorithm}
- 	set initial values of $\boldsymbol{b}, \boldsymbol{\eta}, \sigma_\tau^2$\\
+ 	set initial values of $\boldsymbol{b}, \boldsymbol{\eta}$, (and $\sigma_\tau^2$)\\
  	\For{o=1 to outer}{
@@
  				update $\boldsymbol{\eta}$ using Metropolis-Hastings --- Equation (10)
- 		}
- 			\For{n=1 to inner3}{
- 				update $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (10)
+ 				(if needed) update $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (10)
  		}
  }
- 	Summarize the results with: \\last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ and $\sigma_\tau^2$ 
+ 	Summarize the results with: \\last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ (and $\sigma_\tau^2$) 
  				\label{alg:MCMC}
@@
 			\ENDFOR
-			\STATE draw $a_d \sim \mbox{Multinomial}(\pi)$
+			\STATE draw $a_d \sim \mbox{Multinomial}(\pi_a)$
 			\ENDIF
@@
 			\IF{$t_d=$ NA}
-			\STATE draw $\boldsymbol{\tau}^{new}_d$ from proposal distribution (e.g., $\boldsymbol{\tau}^{new}_d \sim N(\boldsymbol{\tau}^{old}_d, \sigma^2_{prop})$)
-			\STATE use Metropolis-Hastings to decide accept or reject using the probability
-			\begin{equation*}
-			\footnotesize
-			\frac{f_{\tau}(\tau^{new}_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big) }{f_{\tau}(\tau^{old}_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)},
-			\end{equation*}
-			where $\boldsymbol{\tau}^{old}_d$ is from earlier iteration.
+			\STATE draw $\boldsymbol{\tau}^{new}_d$ from $f_{\tau}(\tau^{new}_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)$ via importance sampling (e.g., proposal distribution $g \sim \mbox{halfcauchy}(5)$)
 			\ENDIF
@@
 The goal of this task is to provide an effective answer to the question ``how are we filling in the missing information of the emails?" as well as to offer one standard way to determine the time-increment distribution in Section \ref{subsec:Time}.
-To do this, we compare the predictive performance from two distributions---lognormal and Exponential.
-We particularly choose Exponential distribution as an alternative to what we used earlier (i.e., lognormal) since Exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
+To do this, we compare the predictive performance from two distributions---lognormal and exponential.
+We particularly choose exponential distribution as an alternative to what we used earlier (i.e., lognormal) since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
 

### 2018-05-14 Emails/PPEnew.R

@@ -78,6 +78,8 @@ save(Montgomery_PPE2, file = "/Users/bomin8319/Desktop/MulticastNetwork/Emails/M
 
 
 names(Montgomery_PPE)
+
+#################
 truesender = sapply(Montgomery_PPE$sendermissing, function(d) edge[[d]]$a_d)
 predprob = Montgomery_PPE$senderprob/rowSums(Montgomery_PPE$senderprob)
 predprob2 = Montgomery_PPE2$senderprob/rowSums(Montgomery_PPE2$senderprob)
@@ -97,9 +99,9 @@ predprob = Montgomery_PPE$receiverprob
 predprob2 = Montgomery_PPE2$receiverprob
 
 probtrue = sapply(1:1118, function(d) predprob[d,truereceiver[d]+1])
-probtrue[probtrue==1] = 0.999
+#probtrue[probtrue==1] = 0.999
 probtrue2 = sapply(1:1118, function(d) predprob2[d,truereceiver[d]+1])
-probtrue2[probtrue2==1] = 0.999
+#probtrue2[probtrue2==1] = 0.999
 
 receiver = data.frame(probtrue = log(probtrue /(1-probtrue)), dist = rep("lognormal", 1118))
 receiver = rbind(receiver, data.frame(probtrue = log(probtrue2/(1-probtrue2)), dist = rep("exponential", 1118)))
@@ -109,7 +111,7 @@ receiver = melt(receiver)
 colnames(receiver)[3] = "logit"
 ggplot(data = receiver, aes(x = dist, y = logit, fill = dist))+geom_boxplot()
 ggplot(data = receiver, aes(x = logit, fill = dist))+geom_histogram(position = "dodge")
-boxplot(sapply(1:62, function(d) predprob[d,truesender[d]]), sapply(1:62, function(d) predprob2[d,truesender[d]]))
+#boxplot(sapply(1:62, function(d) predprob[d,truesender[d]]), sapply(1:62, function(d) predprob2[d,truesender[d]]))
 
 
 

### 2018-05-14 pkg/R/Multicast.R

@@ -7,6 +7,7 @@
 #' @importFrom combinat permn
 #' @importFrom lubridate wday hour
 #' @importFrom MCMCpack rinvgamma dinvgamma
+#' @importFrom LaplacesDemon rhalfcauchy dhalfcauchy
 
 
 #' @title gibbs.measure.support
@@ -404,9 +405,9 @@ PPE = function(data, X, Y, outer, inner, burn, prior.beta, prior.eta, prior.sigm
     iter3 = 1
     for (d in sendermissing) {
         if (timedist == "lognormal") {
-            probi = exp(Timepartindiv(mu[d,], sqrt(sigma2), timeinc[d]))
+            probi = Timepartindiv(mu[d,], sqrt(sigma2), timeinc[d])
         } else {
-            probi = exp(Timepartindiv2(mu[d,], timeinc[d]))
+            probi = Timepartindiv2(mu[d,], timeinc[d])
         }
         senders[d] = multinom_vec(probi)
         if (o > burn) {
@@ -421,30 +422,41 @@ PPE = function(data, X, Y, outer, inner, burn, prior.beta, prior.eta, prior.sigm
         	receiversample = u[[d]][senders[d], missingr[it]]
         	data[[d]][[2]][missingr[it]] = receiversample
         	if (o > burn) {
-        		logitprob = ifelse(sum(data[[d]][[2]][-missingr[it]])==0, 1, exp(lambda[[d]][senders[d], missingr[it]])/(exp(lambda[[d]][senders[d], missingr[it]])+1))
+        		logitprob = ifelse(sum(data[[d]][[2]][-missingr[it]])==0, 0.999, exp(lambda[[d]][senders[d], missingr[it]])/(exp(lambda[[d]][senders[d], missingr[it]])+1))
         		receiverprob[iter2, ] = receiverprob[iter2, ] + c(1-logitprob, logitprob)
         		receiverpredict[iter2, o-burn] = receiversample 
         	}
         	iter2 = iter2+1
         }
     }  
+    # for (d in timemissing) {
+    	# tau_new = rnorm(1, timeinc[d], MHprop.var)
+        # if (timedist == "lognormal") {
+            # post.new0 = Timepartindiv(mu[d,], sqrt(sigma2), tau_new)[senders[d]]
[…]

### 2018-05-14 pkg/src/Multicast_rcpp.cpp

@@ -135,7 +135,7 @@ NumericVector Timepartindiv (NumericVector mu, double sigma_tau, double timestam
             }
         }
     }
-    return out;
+    return exp(out);
 }
 
 // **********************************************************//
@@ -153,7 +153,7 @@ NumericVector Timepartindiv2 (NumericVector mu, double timestamp){
             }
         }
     }
-    return out;
+    return exp(out);
 }
 
 // **********************************************************//

### 2018-05-15 paper/paper.tex
PPE results added

@@
 After running the experiment, we measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
-	\begin{figure}[!b]
+First, we compare the correct sender probability for missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}$ in Algorithm \ref{alg:PPE}.
+The plot on the left shows that lognormal distribution reaches higher correct sender probability than exponential distribution, although their centers (e.g., medians) are similar.
+Secondly, we compute similar measure for recipients---correct recipient probability $P(r_{dr} = r^{obs}_{dr})$ in Algorithm \ref{alg:PPE} where $r^{obs}_{dr}$ is either 1 (received) or 0 (not received)---and visually compare the two distributions in logit scale (i.e., $\log(\frac{P(r_{dr} = r^{obs}_{dr})}{1-P(r_{dr} = r^{obs}_{dr})})$).
+Since the edge generating process (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there is no significant difference between lognormal and exponential in their performance of predicting unknown recipients.
+	\begin{figure}[!t]
 		\centering
-		\includegraphics[width=0.495\textwidth]{plots_paper/senderpredict-1.png}	
-		\includegraphics[width=0.495\textwidth]{plots_paper/receiverpredict2-1.png}	
-		\caption {PPE results}
+		\includegraphics[width=1\textwidth]{plots_paper/PPEplot-1.png}	
+		\caption {Comparison of predictive performance between lognormal and exponential distributions: boxplots for correct sender probability (\textit{left}), distribution of correct recipient probability in logit (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).}
 		\label{figure:PPEresults}

### 2018-05-15 Emails/PPEnew.R

@@ -79,6 +79,8 @@ save(Montgomery_PPE2, file = "/Users/bomin8319/Desktop/MulticastNetwork/Emails/M
 
 names(Montgomery_PPE)
 
+library(gridExtra)
+p = list()
 #################
 truesender = sapply(Montgomery_PPE$sendermissing, function(d) edge[[d]]$a_d)
 predprob = Montgomery_PPE$senderprob/rowSums(Montgomery_PPE$senderprob)
@@ -90,7 +92,7 @@ library(ggplot2)
 library(reshape)
 sender = melt(sender)
 colnames(sender)[3] = "correct"
-ggplot(data = sender, aes(x = dist, y = correct, fill = dist))+geom_boxplot()
+p[[1]]=ggplot(data = sender, aes(x = dist, y = correct, fill = dist))+geom_boxplot()
 boxplot(sapply(1:62, function(d) predprob[d,truesender[d]]), sapply(1:62, function(d) predprob2[d,truesender[d]]))
 
 ###############################################
@@ -110,8 +112,47 @@ library(reshape)
 receiver = melt(receiver)
 colnames(receiver)[3] = "logit"
 ggplot(data = receiver, aes(x = dist, y = logit, fill = dist))+geom_boxplot()
-ggplot(data = receiver, aes(x = logit, fill = dist))+geom_histogram(position = "dodge")
+p[[2]]=ggplot(data = receiver, aes(x = logit, fill = dist))+geom_histogram(position = "dodge")
 #boxplot(sapply(1:62, function(d) predprob[d,truesender[d]]), sapply(1:62, function(d) predprob2[d,truesender[d]]))
+
+
+#################################################
+truetime = sapply(Montgomery_PPE$timemissing, function(d) edge[[d]]$t_d-edge[[d-1]]$t_d)/3600
+predtime = Montgomery_PPE$timepredict
+predtime2 = Montgomery_PPE2$timepredict
+
+time = data.frame(MdAPE = sapply(1:62, function(d) median(abs((predtime[d,]-truetime[d])/truetime[d]))), dist = rep("lognormal", 62))
+time = rbind(time, data.frame(MdAPE = sapply(1:62, function(d) median(abs((predtime2[d,]-truetime[d])/truetime[d]))), dist = rep("exponential", 62)))
+
+time = melt(time)
+stats = boxplot.stats(time$value)$stats
+
+colnames(time)[3] = "MdAPE"
[…]

### 2018-05-15 paper/paper.tex
PPE comments and appendix B attached

@@
 \usepackage{algorithm}
+\usepackage{mathtools}
 \usepackage[toc,page]{appendix}
@@
 
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}
 \begin{document}
@@
 		\includegraphics[width=0.31\textwidth]{plots_paper/timeppnew.pdf}
-		\caption {PPC results: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
+		\caption {PPC results from lognormal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
 Red lines in the first three plot depict the observed statistics, and the red line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
@@
 
-The goal of this task is to provide an effective answer to the question ``how are we filling in the missing information of the emails?" as well as to offer one standard way to determine the time-increment distribution in Section \ref{subsec:Time}.
-To do this, we compare the predictive performance from two distributions---lognormal and exponential.
+Here, we specifically compare the predictive performance from two distributions---lognormal and exponential.
 We particularly choose exponential distribution as an alternative to what we used earlier (i.e., lognormal) since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
-
-After running the experiment, we measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
+We run the experiment and measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
 First, we compare the correct sender probability for missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}$ in Algorithm \ref{alg:PPE}.
@@
 Since the edge generating process (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there is no significant difference between lognormal and exponential in their performance of predicting unknown recipients.
+Finally, prediction errors for missing timestamps are measured using the median absolute percentage error (MdAPE) \citep{hyndman2006another}, where we take the median of absolute percentage errors $p_{di}$ for $i=1,\ldots,500$ for $d$th document, calculated as follows:
 	\begin{figure}[!t]
@@
 	\end{figure}
+\begin{equation*}
+p_{di} = \abs*{\frac{\tau^{obs}_d - \tau^{pred}_{di}}{\tau^{obs}_d}},
+\end{equation*}
+and we present boxplots for the MdAPE estimates on the right plot.
+As expected, we have huge benefit in the performance of timestamp prediction when we choose lognormal distribution over exponential.
+This difference can be explained by our variance estimate $\hat{\sigma}_\tau^2= 14.093$ in Section \ref{subsec:Result_email}, because exponential distribution omits the extra information on time-increments contained in the large variance estimate.
+All our findings in this section is further revealed in the PPC results from exponential distribution, which are attached in Appendix \ref{sec: PPCexp}.
+As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing information of the emails?" and 2) offer one standard way to determine the time-increment distribution in Section \ref{subsec:Time}.
+
 \iffalse
@@
 \begin{appendices}
-\section{Normalizing constant of MB$_{Gibbs}$}\label{sec: non-empty Gibbs measure}
+\section{Normalizing Constant of MB$_{Gibbs}$}\label{sec: non-empty Gibbs measure}
 Our probability measure ``MB$_{Gibbs}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure \citep{fellows2017removing}---defines the probability of author $a$ selecting the binary recipient vector $\boldsymbol{u}_{ad}$ as
@@
 \end{equation*}
-
+\newpage
+ \section{PPC Results from Exponential Distribution}\label{sec: PPCexp}
+ 	\begin{figure}[H]
+ 		\centering
+ 		\includegraphics[width=0.495\textwidth]{plots_paper/outdegree_exp-1.png}	
+ 		\includegraphics[width=0.495\textwidth]{plots_paper/indegree_exp-1.png}	
+ 		\includegraphics[width=0.495\textwidth]{plots_paper/recipientsize_exp-1.png}	
+ 		\includegraphics[width=0.31\textwidth]{plots_paper/timepp_exp-1.png}
+ 		\caption {PPC results from exponential distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
+Red lines in the first three plot depict the observed statistics, and the red line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
+ 		\label{figure:PPCexp}
+ 	\end{figure}
 	\end{appendices}

### 2018-05-15 Emails/Montgomery_result.R

@@ -63,7 +63,8 @@ outdegreedist = matrix(NA,  500, A)
 recipientsdist = matrix(NA,  500, A-1)
 timedist = matrix(NA, 500, 621)
 #setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC")
-setwd("/Users/bomin8319/")
+#setwd("/Users/bomin8319/")
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC2")
 
 for (n in 1:500) {
 	filename = paste0("Montgomery_PPCnew", n,".RData")
@@ -143,6 +144,66 @@ outdegree1 = data.frame(Outdegree = degreedist1)
 colnames(outdegree1) = c("Outdegree", "Nodes")
 ggplot(data = data, aes(x = Outdegree, y = Nodes)) +geom_boxplot() + geom_line(data = outdegree1, group = 1, col = 'red')
 
+#################################
+
+indegreedist = matrix(NA, 500, A)
+outdegreedist = matrix(NA,  500, A)
+recipientsdist = matrix(NA,  500, A-1)
+timedist = matrix(NA, 500, 621)
+#setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC")
+#setwd("/Users/bomin8319/")
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC2")
+
+for (n in 1:500) {
+	filename = paste0("Montgomery_PPCnew2", n,".RData")
+	load(filename)
+	outdegreedist[n, ] = tabulate(vapply(1:621, function(x) Montgomery_PPC2[[x]]$a_d, c(1)), A)
+	indegreedist[n, ] = rowSums(sapply(1:621, function(x) Montgomery_PPC2[[x]]$r_d))
+	recipientsdist[n, ] = tabulate(vapply(1:621, function(x) sum(Montgomery_PPC2[[x]]$r_d), c(1)), A-1)
+	timedist[n, ] = vapply(1:621, function(x) Montgomery_PPC2[[x]]$t_d, c(1))/ timeunit
+} 
+
+outdegreedist = data.frame(outdegreedist)
+colnames(outdegreedist)=1:18
+library(ggplot2)
+library(reshape)
+data = melt(outdegreedist)
+colnames(data) = c("Node", "Outdegree")
+
+outdegree = data.frame(Node = 1:18, Outdegree = outdegree)
[…]

### 2018-05-15 code/Montgomery_processing.R

@@ -115,3 +115,15 @@ for (n in 1:500) {
 
 
 
+
+load("/Users/bomin8319/Desktop/Montgomery_infer2.RData")
+initial = list()
+initial$sender = email[1:(min(trim)-1), 2]
+initial$receiver = email[1:(min(trim)-1), 3:20]
+initial$time = email[1:(min(trim)-1),1]
+for (n in 1:500) {
+  Montgomery_PPC = PPC(length(edge), A, colMeans(Montgomery_infer2$beta), colMeans(Montgomery_infer2$eta), 
+                       mean(Montgomery_infer2$sigma2), X, Y, timeunit = 3600, Montgomery_infer2$u, timedist = "exponential")
+  filename = paste0("Montgomery_PPCnew", n,".RData")
+  save(Montgomery_PPC, file = filename)
+}

### 2018-05-15 code/Montgomery_processing2.R

@@ -114,3 +114,12 @@ for (n in 1:500) {
 
 
 
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC2")
+for (n in 1:500) {
+	print(n)
+    Montgomery_PPC2 = PPC(length(edge), beta = colMeans(Montgomery_infer2$beta), eta = colMeans(Montgomery_infer2$eta),
+    sigma2 = mean(Montgomery_infer2$sigma2), X, Y, timeunit = 3600, u = Montgomery_infer2$u, timedist = "exponential")
+  filename = paste0("Montgomery_PPCnew2", n,".RData")
+  save(Montgomery_PPC2, file = filename)
+}
+

### 2018-05-15 paper/paper.tex
conclusion added

@@
  }
- 	Summarize the results with: \\last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ (and $\sigma_\tau^2$) 
+ 	Summarize the results with: last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ (and $\sigma_\tau^2$) 
  				\label{alg:MCMC}
@@
  	   Our data come from the North Carolina county government email dataset collected by \cite{ben2017transparency} that includes internal email corpora covering the inboxes and outboxes of managerial-level employees of North Carolina county governments.
-Out of over twenty counties, we chose Montgomery County to 1) test our model using data with a lot of multicast edges (16.76\%), and 2) limit the scope of this initial application.
-The Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
+Out of over twenty counties, we chose Montgomery County to 1) test our model using data with a lot of hyper-edges (16.76\%), all of which are a single sender multiple receiver cases, and 2) limit the scope of this initial application.
+To summarize, Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
  	   \subsection{Covariates}\label{subsec:Covariates_email}
@@
 \section{Conclusion}\label{sec:conclusion}
-\newpage
+Motivated by the relational event model \citep{Butts2008} and its variants for time-stamped networks, the hyper-edge event model (HeEM) can effectively learn the underlying edge generating and timestamp generating structures of event data, while allowing flexibity in the covariate specifications and the distributional assumption of time-increments.
+Accounting for the hyper-edge, we make better use of events with hyper-edges than modeling them as duplicate edges.
+In modeling the timestamps of the events, our generalized linear model (GLM) based formulation eliminates the need to stick with one distribution (e.g., exponential distribution), and we also provide an algorithm for predictive experiment that helps to learn which distribution better fits the data.
+To sum, the HeEM's flexible generative process thus leads to more accurate and precise inference on model parameters.
+
+We have demonstrated effectiveness of our model by analyzing Montgomery County government emails, which includes numerous hyper-edges.
+The estimated covariate effects reveal that the HeEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), while the model additionally allows separate covariates and the corresponding parameters for edge and timestamp generating processes.
+Although we illustrate the entire framework and application in the context
+of one type of hyper-edges, a single sender and multiple recipients, our model can be easily extended to allow the opposite case, a single recipient and multiple senders, by slight modification of the generating process.
+This extension involves promissing applications including international sanctions and co-sponsorship of bills.
+Furthermore, while currently the model's applicability is limited to small-sized networks since we assume fixed set of nodes across entire timepoints, we can adjust the model to allow time-varying nodes or improve its computational efficiency such that the model is well applicable to large-scale networks.
+Considering the recent explosion of network dataset with huge number of nodes (e.g., online comnunications), the development of model adjustments for better applicability are objects of future work.
 \bibliographystyle{agsm}
@@
 \end{equation*}
-\newpage
  \section{PPC Results from Exponential Distribution}\label{sec: PPCexp}

### 2018-05-15 paper/paper.tex
added some hyper-edge citations

@@
 Similarly, \cite{fan2009learning} treats multicast emails as multiple single-recipient edges and randomly jitter the sent times, to avoid the violation of continous-time model assumption.
-Concentrating on better handling of hyper-edges, we develop the hyper-edge event model (HeEM) which simultaneously models the two components that govern time-stamped event formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
+On the other hand, there have been numerous studies for hyper-edges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}.
+To our knowledge, there is a lack of extensive efforts to incorportate hyper-edge modeling into general statistical framework.
 
+Concentrating on developing a statistical network model with better handling of hyper-edges, we introduce the hyper-edge event model (HeEM) which simultaneously models the two components that govern time-stamped event formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
 In what follows, we introduce the HeEM by describing how we assume the generatve process of a time-stamped event data (Section 2), and deriving the sampling equations for Bayesian inference (Section 3).

### 2018-05-16 paper/paper.tex
paper structure change and writing update

--- 2018-05-15 paper/paper.tex
@@
 {
-  \title{\bf A Hyper-edge Event Model}
+  \title{\bf The Hyperedge Event Model}
   \author{Bomin Kim\thanks{
@@
   \begin{center}
-    {\LARGE\bf A Hyper-edge Event Model}
+    {\LARGE\bf The Hyperedge Event Model}
 \end{center}
@@
 \begin{abstract}
-We introduce the hyper-edge event model (HeEM)---a generative model for directed edges with multiple recipients or multiple senders. To define the model, we
+We introduce the hyperedge event model (HEM)---a generative model for directed edges with multiple recipients or multiple senders. To define the model, we
 integrate a dynamic version of the exponential random graph model (ERGM) and generalized linear model (GLM) approach to jointly understand who communicates with whom, and when.
@@
 In recent decades, real-time digitized textual communication has developed into a ubiquitous form of social and professional interaction \citep{kanungo2008modeling, szostek2011dealing, burgess2004email, pew2016}.
-From the perspective of the computational social scientist, this has led to a growing need for methods of modeling interactions that manifest as text exchanged in continuous time.
+From the perspective of the computational social scientist, this has led to a growing need for methods of modeling interactions that manifest as edges exchanged in continuous time.
 A number of models that build upon topic modeling through Latent Dirichlet Allocation \citep{Blei2003} to incorporate link data as well as textual content have been developed recently \citep{mccallum2005author,lim2013twitter,Krafft2012}.
@@
 Several network models have been developed that handle time-stamped events in which edge formation is governed by structural dynamics similar to those used in the ERGM \citep{Butts2008,Vu2011,snijders1996stochastic}.
-Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows hyper-edges---a connection between two or more vertices generated simultaneously\footnote{A hyper-edge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
-For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyper-edge which involve one sender and multiple receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
+Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows hyperedges---a connection between two or more vertices generated simultaneously\footnote{A hyperedge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
+For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involve one sender and multiple receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
 Similarly, \cite{fan2009learning} treats multicast emails as multiple single-recipient edges and randomly jitter the sent times, to avoid the violation of continous-time model assumption.
-Concentrating on better handling of hyper-edges, we develop the hyper-edge event model (HeEM) which simultaneously models the two components that govern time-stamped event formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
+On the other hand, there have been numerous studies for hyperedges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}.
+To our knowledge, there is a lack of extensive efforts to incorportate hyperedge modeling into general statistical framework.
 
-In what follows, we introduce the HeEM by describing how we assume the generatve process of a time-stamped event data (Section 2), and deriving the sampling equations for Bayesian inference (Section 3).
+Concentrating on developing a statistical network model with better handling of hyperedges, we introduce the hyperedge event model (HEM) which simultaneously models the two components that govern time-stamped event formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
+In what follows, we introduce the HEM by describing how we assume the generatve process of a time-stamped event data (Section 2), and deriving the sampling equations for Bayesian inference (Section 3).
 Then, we apply the model to the Montgomery county government email data and perform two model validation tasks (Section 4).
@@
 
-\section{A Hyper-Edge Event Model (HeEM)}\label{sec:generative process}
+\section{The Hyperedge Event Model (HEM)}\label{sec:generative process}
 Data generated under the model consists of $D$ unique edges.
@@
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
-While the model can be applied for two type of hyper-edges---edges with (1) a single sender and multiple receivers, and (2) multiple senders and a single receiver---here we only present the generative process for those involving a single sender and multiple receivers (i.e., multicast).
-For the latter case of hyper-edges, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single recipient.
+While the model can be applied for two type of hyperedges---edges with (1) a single sender and multiple receivers, and (2) multiple senders and a single receiver---here we only present the generative process for those involving a single sender and multiple receivers (i.e., multicast).
+For the latter case of hyperedges, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single recipient.
 \subsection{Edge Generating Process}\label{subsec: Tie}
@@
 Next, we hypothesize ``If $a$ were the sender of edge $d$, who would be the recipient(s)?" To do this, we draw each sender's set of recipients from the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model to estimate the structure of graphs with binary nodes---with probability of 1 being logit($\lambda_{adr}$).
-In order to avoid the model degeneracy from having an empty recipient set, we define a probability measure ``MB$_{Gibbs}$" motivated by the non-empty Gibbs measure \citep{fellows2017removing} which excludes the all-zero vector from the support of MB distirbution.
+In order to avoid the model degeneracy from having an empty recipient set, we define a probability measure ``MB$_{G}$" motivated by the non-empty Gibbs measure \citep{fellows2017removing} which excludes the all-zero vector from the support of the multivariabe Bernoulli distirbution.
 As a result, we 1) allow multiple recipients or ``multicast", 2) prevent from obtaining zero recipient, and 3) ensure tractable normalizing constant.
@@
 \begin{equation} \boldsymbol{u}_{ad}  \sim
-\mbox{MB}_{Gibbs}(\boldsymbol{\lambda}_{ad}),
+\mbox{MB}_{G}(\boldsymbol{\lambda}_{ad}),
 \end{equation}
-where $\boldsymbol{\lambda}_{id}= \{\lambda_{adr}\}_{r=1}^A$. In particular, we define $\mbox{MB}_{Gibbs}(\boldsymbol{\lambda}_{ad})$ as
+where $\boldsymbol{\lambda}_{id}= \{\lambda_{adr}\}_{r=1}^A$. In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ad})$ as
 \begin{equation}
@@
 where $\tau_{ad}$ here is a positive real number.
-Possible choices of distribution include Exponential, Weibull, Gamma, and lognormal\footnote{lognormal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
+Possible choices of distribution include exponential, Weibull, gamma, and lognormal\footnote{lognormal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
 Based on the choice of distribution, we may introduce any additional parameter (e.g., $\sigma_\tau^2$) to account for the variance.
@@
 \begin{equation}
-P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, \sigma_\tau^2) \big)\Big),
+\begin{aligned}
+&P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\\&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, \sigma_\tau^2) \big)\Big),
+\end{aligned}
 \end{equation}
@@
  		\For{n=1 to inner2}{
- 				update $\boldsymbol{\eta}$ using Metropolis-Hastings --- Equation (10)
+ 				update $\boldsymbol{\eta}$ using Metropolis-Hastings --- Equation (10)\\
  				(if needed) update $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (10)
@@
  	   Our data come from the North Carolina county government email dataset collected by \cite{ben2017transparency} that includes internal email corpora covering the inboxes and outboxes of managerial-level employees of North Carolina county governments.
-Out of over twenty counties, we chose Montgomery County to 1) test our model using data with a lot of hyper-edges (16.76\%), all of which are a single sender multiple receiver cases, and 2) limit the scope of this initial application.
+Out of over twenty counties, we chose Montgomery County to 1) test our model using data with a lot of hyperedges (16.76\%), all of which are a single sender multiple receiver cases, and 2) limit the scope of this initial application.
 To summarize, Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
@@
 	In the example of email networks, we form the covariate vector $\boldsymbol{x}_{adr}$ using time-varying network statistics based on the time interval prior to and including $t_{d-1}$.
-Along with intercept term, we compute the network statistics \citep{PerryWolfe2012}, where the time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{days}, t_{d-1}]$.
-To be specific, we use
+Given a set of interaction data, a primary modeling goal lies in determining which characteristics and behaviors of the senders and receivers are predictive of interaction.
+This email application specifically give rise to the following question: ``To what extent are nodal, dyadic or triadic network effects, as characterized
+by past interaction behaviors, relevant to predicting future events?" We employ the network statistics in \cite{PerryWolfe2012}, along with the intercept term, to address the question.
+Specifically, our time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{ days}, t_{d-1}]$.
+For $a \in [A], r \in [A]$, and $d \in [D]$, we define the effects
 	\begin{itemize}
 		\spacingset{1}
-		\item[1.] intercept ${x}_{adr1} =1$;
-		\item[2.] outdegree ${x}_{adr2} =\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
-		\item[3.] indegree ${x}_{adr3}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
-		\item[4.] send ${x}_{adr4}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
-		\item[5.] receive ${x}_{adr5}=\mbox{send}(r,a)$;
-		\item[6.] 2-send ${x}_{adr6} = \sum\limits_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(h,r)$;
-		\item[7.] 2-receive ${x}_{adr7}= \sum\limits_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(r,h)$;
-		\item[8.] sibling ${x}_{adr8}=\sum\limits_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(h,r)$;
-		\item[9.] cosibling ${x}_{adr9}=\sum\limits_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(r,h)$;
-		\item[10.] Nreceive ${x}_{adr10}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} \sum\limits_{r=1}^A I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
-		\item[11.] outdegree$*$Nreceive ${x}_{adr11} = {x}_{adr2}\times{x}_{adr10};$
+		\item[1.] intercept: ${x}_{adr1} =1$;
+		\item[2.] outdegree of sender $a$: ${x}_{adr2} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+		\item[3.] indegree of receiver $r$: ${x}_{adr3}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
+		\item[4.] send: ${x}_{adr4}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
+		\item[5.] receive: ${x}_{adr5}=\mbox{send}(r,a)$;
+		\item[6.] 2-send: ${x}_{adr6} = \sum_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(h,r)$;
+		\item[7.] 2-receive: ${x}_{adr7}= \sum_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(r,h)$;
+		\item[8.] sibling: ${x}_{adr8}=\sum_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(h,r)$;
+		\item[9.] cosibling: ${x}_{adr9}=\sum_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(r,h)$;
+		\item[10.] hyperedge size of sender $a$: ${x}_{adr10}=\sum_{d^\prime: t_{d^\prime} \in l_d} \sum_{r=1}^A I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
+		\item[11.] outdegree$*$hyperedge size: ${x}_{adr11} = {x}_{adr2}\times{x}_{adr10};$
 	\end{itemize}
-	where $I(\cdot)$ is an indicator function, and the last covariate is the interaction term between outdegree and Nreceive.
-As with the nodal (2, 3, 10, 11) and dyadic (4, 5) effects, the triadic (6--9) effects are designed so that their coefficient have a straightforward interpretation, which are illustrated in Figure \ref{figure:netstats}.
-		\begin{figure}[H]
+	where $I(\cdot)$ is an indicator function, and the last covariate is the interaction term between outdegree and hyperedge size.
+As with the nodal (2, 3, 10, 11) and dyadic (4, 5) effects, the triadic (6--9) effects are designed so that their coefficient have a straightforward interpretation.
+Dyadic statistics ``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
+In the example of triadic statistics, the covariate ``2-send" counts the pairs of emails involving some node $h$ distinct from $a$ and $r$ such that an email from $a$ to $h$ and $h$ to $r$ are separately observed within the last 7 days.
+Other triadic covariates behave similarly, and their interpretations are also analogous, which are illustrated in Figure \ref{figure:netstats}.
+		\begin{figure}[!t]
 			\centering
@@
 	\spacingset{1}
-	\item[1.] intercept ${y}_{ad1} =1$;
-	\item[2.] outdegree ${y}_{ad2} =\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
-	\item[3.] indegree ${y}_{ad3}=\sum\limits_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
-	\item[4.] gender ${y}_{ad4}=I(a= \mbox{female})$;
-	\item[5.] manager ${y}_{ad5}=I(a= \mbox{County Manager})$;
-	\item[6.] weekend ${y}_{ad6} = I(t_{d-1}= \mbox{weekend})$;
-	\item[7.] am/pm ${y}_{ad7}= I(t_{d-1}= \mbox{pm})$.
+	\item[1.] intercept: ${y}_{ad1} =1$;
+	\item[2.] outdegree of sender $a$: ${y}_{ad2} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+	\item[3.] indegree of sender $a$: ${y}_{ad3}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
+	\item[4.] gender of sender $a$: ${y}_{ad4}=I(a= \mbox{female})$;
+	\item[5.] manager status of sender $a$: ${y}_{ad5}=I(a= \mbox{County Manager})$;
+	\item[6.] weekend of event $d$: ${y}_{ad6} = I(t_{d-1}= \mbox{weekend})$;
+	\item[7.] am/pm of event $d$: ${y}_{ad7}= I(t_{d-1}= \mbox{pm})$.
 \end{itemize}
-\subsection{Parameter Estimation and Interpretation}\label{subsec:Result_email}
-Based on some preliminary experiments, we choose lognormal distribution to model time-to-next-email in Montgomery county email data, thus we estimate the variance parameter $\sigma_\tau^2$ with the prior specified as inverse-Gamma($2, 1$).
-In this section, we present the results based on 55,000 MCMC outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
-While the inner iterations for $\boldsymbol{\eta}$ and $\sigma_\tau^2$ are fixed as 1, we use 10 inner iterations for $\boldsymbol{b}$ to adjust for its slower convergence rate.
-	\begin{figure}[!b]
-	\centering
-	\includegraphics[width=1\textwidth]{plots_paper/best-1.png}	
-	\caption {Posterior distribution of $\boldsymbol{b}$ estimates.}
-	\label{figure:betaresults}
-\end{figure}
 
-Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$.
-Since we use logit probability of $\lambda_{adr}$ for edge generating process (Section \ref{subsec: Tie}), we have
-\begin{equation*}
-\mbox{logit}(\lambda_{adr})=\log\Big(\frac{\lambda_{adr}}{1-\lambda_{adr}}\Big) =b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11},
-\end{equation*}
-and can interpret the parameter estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11})$.
-Firstly, we can see that the effect of send (i.e., ``number of times the actor $a$ sent emails to the actor $r$ over the last week'') is positive, implying that if the actor $a$ sent $n$ number of emails to $r$ last week, then the actor $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
-Similar interpretation can be applied for the statistics indegree and Nrecieve.
-For example, as the actor $r$ received $n$ emails and the actor $a$ sent emails to $n$ rececievers over the last week, the actor $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times and $\exp(0.047\times n)\approx(1.048)^n$ times, respectively, more likely to send an email to $r$.
-On the other hand, outdegree statistic has negative effect---i.e., if the actor $a$ sent $n$ number of emails to anyone last week, then the actor $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times likely to send an email to $r$---possibly due to its multicollinearity with the statistics send and Nreceive.
-This can be interpreted as ``if the actor $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of send) or 2) no broadcast or multicast emails (excluding the effect of Nreceive)'' then the actor $a$ is less likely to send an email to $r$.
-Rest of statistics are not statistically significant because their 95\% credible interval do not include 0.
-Surprisingly, none of the triadic effects seem to have significant effect on the edge generating process.
-
-	Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of the time-related coefficients $\boldsymbol{\eta}$.
-For this specific datset, we assume lognormal distribution (Section \ref{subsec:Time}) with the unit of time being an hour, so that the interpretation of $\hat{\boldsymbol{\eta}}$ should be based on
-\begin{equation*}
-\begin{aligned}
-&\log(\tau_{ad}) \sim N(\mu_{ad}, \sigma_\tau^2), \mbox{ with }\\
-&\mu_{ad} = \eta_{1}+\eta_{2} y_{ad2}\ldots+\eta_{7}y_{ad7}.
-\end{aligned}
-\end{equation*}
-	\begin{figure}[!b]
-		\centering
-		\includegraphics[width=0.89\textwidth]{plots_paper/etaest-1.png}	
-		\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
-		\label{figure:etaresults}
-	\end{figure}
-To begin with, the posterior estimates of two temporal effects---weekend and pm---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after 12pm, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
-On the contrary, the statistics manager, outdegree, and indegree turn out to shorten the time to next email.
-For example, being a county manager (i.e., the manager of the managers) lowers the expected $\log(\tau_{ad})$ by -1.070, since he or she needs to respond fastly to emails with important decisions.
-In addition, the manager in general sends or receives a lot more emails which may shorten the response time.
-This argument is supported by the posterior estimates for outdegree and indegree, where the estimated coefficients are approximately -0.206 and -0.060, respectively.
-Gender of the department manager is shown to have no significant effect on time-to-next-email.
-The posterior mean estimate of the variance parameter $\sigma^2_\tau$ is 14.093 with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time-increments in this data.
-	\subsection{Posterior Predictive Checks}\label{subsec:PPC_email} 	   
-	We perform posterior predictive checks \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data.
-We formally generated entirely new data, by simulating time-stamped events $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{subsec:Result_email}.
-For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data: outdegree distribution, indegree distribution, recipient size distribution, and time-increments probability-probability (PP) plot.
-We then generated 500 synthetic networks from the posterior predictive distribution, according to Algorithm \ref{alg:PPC}.
-	\begin{algorithm}[!b]
-		\spacingset{1}
-		\caption{Generate new data for PPC}
-		\begin{algorithmic}
-			\STATE \textbf{Input}: number of new data to generate $R$, covariates $\boldsymbol{x}$ and $\boldsymbol{y}$\\
-			estimated latent variables $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta},  \sigma_\tau^2)$\\
-			\vskip 0.1in
-
-			\FOR{$r=1$ {\bfseries to}  $R$}
-			\FOR{$d = 1$ {\bfseries to}  $D$} 
-			\STATE	Draw ($a_{d}$, $\boldsymbol{r}_{d}$, $t_{d}$) following Section \ref{sec:generative process}\\
-			\ENDFOR
-			\STATE Store every $r^{th}$ new data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ 
-			\ENDFOR
-		\end{algorithmic}
-		 				\label{alg:PPC}
-	\end{algorithm}       
-	\begin{figure}[!t]
-		\centering
-		\includegraphics[width=0.495\textwidth]{plots_paper/outdegreenew-1.png}	
-		\includegraphics[width=0.495\textwidth]{plots_paper/indegreenew-1.png}	
-		\includegraphics[width=0.495\textwidth]{plots_paper/recipientsizenew-1.png}	
-		\includegraphics[width=0.31\textwidth]{plots_paper/timeppnew.pdf}
-		\caption {PPC results from lognormal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
-Red lines in the first three plot depict the observed statistics, and the red line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
-		\label{figure:PPCresults}
-	\end{figure}
-
-	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks.
-Upper two plots show node-specific degree distributions, where the left one is the boxplots of 500 posterior predictive outdegree statistic and the right plot is the same one for indegree statistic.
-For both plots, the x-axis represents the node id's from 1 to 18, and the y-axis represents the number of emails sent or received by the node.
-When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes.
-For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, without using node-specific indicators.
-Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
-Since we use more information in the recipient selection process (i.e., network effects) while we only rely on minimum time-increments when choosing the observed sender, these results are expected.
-Lower left plot is the distribution of recipient sizes, where the x-axis spans over the size of recipients 1 to 14 (which is the maximum size of observed recipients) and the y-axis denotes the number of documents with x-number of recipients.
-The result shows that our model is underestimating single-receiver documents while overestimating documents with two, three, and four recipients.
-One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the documents with $\geq 10$ number of recipients, so that the intercept estimate $b_1$ is slightly moved toward right.
-To improve the goodness of fit for recipient sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
-In the end, the plot on the lower right is the PP plot for time-increments, which is a graphical measure commonly used for assessing how closely two data sets agree, by plotting the two cumulative distribution functions against each other.
-The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time-increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
 	\subsection{Prediction Experiment}\label{subsec:Experiment_email}
 
-The HeEM has many component parts that need to be specified by the user (i.e., the selection of the event timing features $\bm{y}$, the recipient selection features $\bm{x}$, and the event time distribution $f$).
+	The HEM has many component parts that need to be specified by the user (i.e., the selection of the event timing features $\bm{y}$, the recipient selection features $\bm{x}$, and the event time distribution $f$).
 Many of these components will be specified based on user expertise (e.g., regarding which features would drive recipient selection), but some decisions may require a data-driven approach to model specification.
@@
 Furthermore, since different distribution families (and model specifications more generally) may involve different size parameter spaces, any data-driven approach to model comparison must guard against over-fitting the data.
-In this section we present a general-purpose approach to evaluating the HeEM specification using out-of-sample prediction.
+In this section we present a general-purpose approach to evaluating the HEM specification using out-of-sample prediction.
 We illustrate this approach by comparing alternative distributional families for the event timing component of the model.
-\iffalse
-Good example article: \url{https://projecteuclid.org/download/pdfview_1/euclid.ba/1457383101}
-	\fi
+Here, we specifically compare the predictive performance from two distributions---lognormal and exponential.
+We particularly choose exponential distribution as an alternative to what we used earlier (i.e., lognormal) since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
 
@@
 Algorithm \ref{alg:PPE} outlines this procedure in detail.
+We run the experiment and measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
+First, we compare the correct sender probability for missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
+The plot on the left shows that lognormal distribution reaches higher correct sender probability than exponential distribution, although their centers (e.g., medians) are similar.
+Secondly, we compute similar measure for recipients---correct recipient probability $P(r_{dr} = r^{obs}_{dr})$ in Algorithm \ref{alg:PPE} where $r^{obs}_{dr}$ is either 1 (received) or 0 (not received)---and visually compare the two distributions in logit scale (i.e., $\log(\frac{P(r_{dr} = r^{obs}_{dr}|\cdot)}{1-P(r_{dr} = r^{obs}_{dr})})$).
+Since the edge generating process (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there is no significant difference between lognormal and exponential in their performance of predicting unknown recipients.
+Finally, prediction errors for missing timestamps are measured using the median absolute percentage error (MdAPE) \citep{hyndman2006another}, where we take the median of absolute percentage errors $p_{di}$ for $i=1,\ldots,500$ for $d$th document, calculated as follows:
 		\begin{algorithm}[!t]
@@
 		\end{algorithm}
-
-Here, we specifically compare the predictive performance from two distributions---lognormal and exponential.
-We particularly choose exponential distribution as an alternative to what we used earlier (i.e., lognormal) since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
-We run the experiment and measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
-First, we compare the correct sender probability for missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}$ in Algorithm \ref{alg:PPE}.
-The plot on the left shows that lognormal distribution reaches higher correct sender probability than exponential distribution, although their centers (e.g., medians) are similar.
-Secondly, we compute similar measure for recipients---correct recipient probability $P(r_{dr} = r^{obs}_{dr})$ in Algorithm \ref{alg:PPE} where $r^{obs}_{dr}$ is either 1 (received) or 0 (not received)---and visually compare the two distributions in logit scale (i.e., $\log(\frac{P(r_{dr} = r^{obs}_{dr})}{1-P(r_{dr} = r^{obs}_{dr})})$).
-Since the edge generating process (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there is no significant difference between lognormal and exponential in their performance of predicting unknown recipients.
-Finally, prediction errors for missing timestamps are measured using the median absolute percentage error (MdAPE) \citep{hyndman2006another}, where we take the median of absolute percentage errors $p_{di}$ for $i=1,\ldots,500$ for $d$th document, calculated as follows:
 	\begin{figure}[!t]
@@
 This difference can be explained by our variance estimate $\hat{\sigma}_\tau^2= 14.093$ in Section \ref{subsec:Result_email}, because exponential distribution omits the extra information on time-increments contained in the large variance estimate.
-All our findings in this section is further revealed in the PPC results from exponential distribution, which are attached in Appendix \ref{sec: PPCexp}.
 As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing information of the emails?" and 2) offer one standard way to determine the time-increment distribution in Section \ref{subsec:Time}.
+	\subsection{Posterior Predictive Checks}\label{subsec:PPC_email} 	   
+	We perform posterior predictive checks \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data.
+We formally generated entirely new data, by simulating time-stamped events $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{subsec:Result_email}.
+For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data: outdegree distribution, indegree distribution, recipient size distribution, and time-increments probability-probability (PP) plot.
+We then generated 500 synthetic networks from the posterior predictive distribution, according to Algorithm \ref{alg:PPC}.
+	\begin{algorithm}[!b]
+		\spacingset{1}
+		\caption{Generate new data for PPC}
+		\begin{algorithmic}
+			\STATE \textbf{Input}: number of new data to generate $R$, covariates $\boldsymbol{x}$ and $\boldsymbol{y}$\\
+			estimated latent variables $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta},  \sigma_\tau^2)$\\
+			\vskip 0.1in
+
+			\FOR{$r=1$ {\bfseries to}  $R$}
+			\FOR{$d = 1$ {\bfseries to}  $D$} 
+			\STATE	Draw ($a_{d}$, $\boldsymbol{r}_{d}$, $t_{d}$) following Section \ref{sec:generative process}\\
+			\ENDFOR
+			\STATE Store every $r^{th}$ new data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ 
+			\ENDFOR
+		\end{algorithmic}
+		\label{alg:PPC}
+	\end{algorithm}       
+	\begin{figure}[!t]
+		\centering
+		\includegraphics[width=0.495\textwidth]{plots_paper/outdegreenew-1.png}	
+		\includegraphics[width=0.495\textwidth]{plots_paper/indegreenew-1.png}	
+		\includegraphics[width=0.495\textwidth]{plots_paper/recipientsizenew-1.png}	
+		\includegraphics[width=0.31\textwidth]{plots_paper/timeppnew.pdf}
+		\caption {PPC results from lognormal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
+Red lines in the first three plot depict the observed statistics, and the red line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
+		\label{figure:PPCresults}
+	\end{figure}
+
+	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using lognormal distribution.
+Upper two plots show node-specific degree distributions, where the left one is the boxplots of 500 posterior predictive outdegree statistic and the right plot is the same one for indegree statistic.
+For both plots, the x-axis represents the node id's from 1 to 18, and the y-axis represents the number of emails sent or received by the node.
+When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes.
+For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, without using node-specific indicators.
+Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
+Since we use more information in the recipient selection process (i.e., network effects) while we only rely on minimum time-increments when choosing the observed sender, these results are expected.
+Lower left plot is the distribution of recipient sizes, where the x-axis spans over the size of recipients 1 to 14 (which is the maximum size of observed recipients) and the y-axis denotes the number of documents with x-number of recipients.
+The result shows that our model is underestimating single-receiver documents while overestimating documents with two, three, and four recipients.
+One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the documents with $\geq 10$ number of recipients, so that the intercept estimate $b_1$ is slightly moved toward right.
+To improve the goodness of fit for recipient sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
+In the end, the plot on the lower right is the PP plot for time-increments, which is a graphical measure commonly used for assessing how closely two data sets agree, by plotting the two cumulative distribution functions against each other.
+The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time-increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
+All our findings in previous section is further revealed in the PPC results from exponential distribution, which are attached in Appendix \ref{sec: PPCexp}.
+\subsection{Parameter Estimates and Interpretation}\label{subsec:Result_email}
+Based on some preliminary experiments, we choose lognormal distribution to model time-to-next-email in Montgomery county email data, thus we estimate the variance parameter $\sigma_\tau^2$ with the prior specified as inverse-Gamma($2, 1$).
+In this section, we present the results based on 55,000 MCMC outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
+While the inner iterations for $\boldsymbol{\eta}$ and $\sigma_\tau^2$ are fixed as 1, we use 10 inner iterations for $\boldsymbol{b}$ to adjust for its slower convergence rate.
+	\begin{figure}[!b]
+	\centering
+	\includegraphics[width=1\textwidth]{plots_paper/best-1.png}	
+	\caption {Posterior distribution of $\boldsymbol{b}$ estimates.}
+	\label{figure:betaresults}
+\end{figure}
+
+Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$.
+Since we use logit probability of $\lambda_{adr}$ for edge generating process (Section \ref{subsec: Tie}), we have
+\begin{equation*}
+\mbox{logit}(\lambda_{adr})=\log\Big(\frac{\lambda_{adr}}{1-\lambda_{adr}}\Big) =b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11},
+\end{equation*}
+and can interpret the parameter estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11})$.
+Firstly, we can see that the effect of send (i.e., ``number of times the actor $a$ sent emails to the actor $r$ over the last week'') is positive, implying that if the actor $a$ sent $n$ number of emails to $r$ last week, then the actor $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
+Similar interpretation can be applied for the statistics indegree and Nrecieve.
+For example, as the actor $r$ received $n$ emails and the actor $a$ sent emails to $n$ rececievers over the last week, the actor $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times and $\exp(0.047\times n)\approx(1.048)^n$ times, respectively, more likely to send an email to $r$.
+On the other hand, outdegree statistic has negative effect---i.e., if the actor $a$ sent $n$ number of emails to anyone last week, then the actor $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times likely to send an email to $r$---possibly due to its multicollinearity with the statistics send and Nreceive.
+This can be interpreted as ``if the actor $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of send) or 2) no broadcast or multicast emails (excluding the effect of Nreceive)'' then the actor $a$ is less likely to send an email to $r$.
+Rest of statistics are not statistically significant because their 95\% credible interval do not include 0.
+Surprisingly, none of the triadic effects seem to have significant effect on the edge generating process.
+	\begin{figure}[!b]
+		\centering
+		\includegraphics[width=0.89\textwidth]{plots_paper/etaest-1.png}	
+		\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
+		\label{figure:etaresults}
+	\end{figure}
+	Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of the time-related coefficients $\boldsymbol{\eta}$.
+For this specific datset, we assume lognormal distribution (Section \ref{subsec:Time}) with the unit of time being an hour, so that the interpretation of $\hat{\boldsymbol{\eta}}$ should be based on
+\begin{equation*}
+\begin{aligned}
+&\log(\tau_{ad}) \sim N(\mu_{ad}, \sigma_\tau^2), \mbox{ with }\\
+&\mu_{ad} = \eta_{1}+\eta_{2} y_{ad2}\ldots+\eta_{7}y_{ad7}.
+\end{aligned}
+\end{equation*}
+To begin with, the posterior estimates of two temporal effects---weekend and pm---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after 12pm, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+On the contrary, the statistics manager, outdegree, and indegree turn out to shorten the time to next email.
+For example, being a county manager (i.e., the manager of the managers) lowers the expected $\log(\tau_{ad})$ by -1.070, since he or she needs to respond fastly to emails with important decisions.
+In addition, the manager in general sends or receives a lot more emails which may shorten the response time.
+This argument is supported by the posterior estimates for outdegree and indegree, where the estimated coefficients are approximately -0.206 and -0.060, respectively.
+Gender of the department manager is shown to have no significant effect on time-to-next-email.
+The posterior mean estimate of the variance parameter $\sigma^2_\tau$ is 14.093 with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time-increments in this data.
 
@@
 \section{Conclusion}\label{sec:conclusion}
-Motivated by the relational event model \citep{Butts2008} and its variants for time-stamped networks, the hyper-edge event model (HeEM) can effectively learn the underlying edge generating and timestamp generating structures of event data, while allowing flexibity in the covariate specifications and the distributional assumption of time-increments.
-Accounting for the hyper-edge, we make better use of events with hyper-edges than modeling them as duplicate edges.
+Motivated by the relational event model \citep{Butts2008} and its variants for time-stamped networks, the hyperedge event model (HEM) can effectively learn the underlying edge generating and timestamp generating structures of event data, while allowing flexibity in the covariate specifications and the distributional assumption of time-increments.
+Accounting for the hyperedges, we make better use of events with hyperedges than modeling them as duplicate edges.
 In modeling the timestamps of the events, our generalized linear model (GLM) based formulation eliminates the need to stick with one distribution (e.g., exponential distribution), and we also provide an algorithm for predictive experiment that helps to learn which distribution better fits the data.
-To sum, the HeEM's flexible generative process thus leads to more accurate and precise inference on model parameters.
+To sum, the HEM's flexible generative process thus leads to more accurate and precise inference on model parameters.
 
-We have demonstrated effectiveness of our model by analyzing Montgomery County government emails, which includes numerous hyper-edges.
-The estimated covariate effects reveal that the HeEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), while the model additionally allows separate covariates and the corresponding parameters for edge and timestamp generating processes.
+We have demonstrated effectiveness of our model by analyzing Montgomery County government emails, which includes numerous hyperedges.
+The estimated covariate effects reveal that the HEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), while the model additionally allows separate covariates and the corresponding parameters for edge and timestamp generating processes.
 Although we illustrate the entire framework and application in the context
-of one type of hyper-edges, a single sender and multiple recipients, our model can be easily extended to allow the opposite case, a single recipient and multiple senders, by slight modification of the generating process.
+of one type of hyperedges, a single sender and multiple recipients, our model can be easily extended to allow the opposite case, a single recipient and multiple senders, by slight modification of the generating process.
 This extension involves promissing applications including international sanctions and co-sponsorship of bills.

### 2018-05-16 code/Montgomery_processing2.R

@@ -114,6 +114,10 @@ for (n in 1:500) {
 
 
 
+Montgomery_infer2 = Inference(edge, X, Y, 55000, c(10,1,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
+proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = Montgomery$lasttime, timedist = "exponential")
+
+
 setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC2")
 for (n in 1:500) {
 	print(n)

### 2018-05-16 paper/paper.tex
minor writing revision

@@
 Several network models have been developed that handle time-stamped events in which edge formation is governed by structural dynamics similar to those used in the ERGM \citep{Butts2008,Vu2011,snijders1996stochastic}.
-Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows hyperedges---a connection between two or more vertices generated simultaneously\footnote{A hyperedge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
+Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows the hyperedge---a connection between two or more vertices generated simultaneously\footnote{A hyperedge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
 For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involve one sender and multiple receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
@@
  	   Our data come from the North Carolina county government email dataset collected by \cite{ben2017transparency} that includes internal email corpora covering the inboxes and outboxes of managerial-level employees of North Carolina county governments.
-Out of over twenty counties, we chose Montgomery County to 1) test our model using data with a lot of hyperedges (16.76\%), all of which are a single sender multiple receiver cases, and 2) limit the scope of this initial application.
+Out of over twenty counties, we chose Montgomery County to 1) test our model using data with large portion of emails with hyperedges (16.76\%), all of which are a single sender multiple receiver cases, and 2) limit the scope of this initial application.
 To summarize, Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
@@
 Dyadic statistics ``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
-In the example of triadic statistics, the covariate ``2-send" counts the pairs of emails involving some node $h$ distinct from $a$ and $r$ such that an email from $a$ to $h$ and $h$ to $r$ are separately observed within the last 7 days.
+In the example of triadic statistics, the covariate ``2-send" counts the pairs of emails involving some node $h$ distinct from $a$ and $r$ such that emails from $a$ to $h$ and $h$ to $r$ are both observed within the last 7 days.
 Other triadic covariates behave similarly, and their interpretations are also analogous, which are illustrated in Figure \ref{figure:netstats}.
@@
 			\includegraphics[width=0.55\textwidth]{plots_paper/triad.png}	
-			\caption {Visualization of triadic statistics.}
+			\caption {Visualization of triadic statistics: 2-send, 2-receive, sibling, and cosibling.}
 			\label{figure:netstats}
@@
 For time-related covariates $\boldsymbol{y}_{ad}$ in Section \ref{subsec:Time}, we form the covariate vector $\boldsymbol{y}_{ad}$ using the seven statistics which may possibly effect ``time to send the next document".
-Note that these statistics could depend on $a$ only (nodal effect), $d$ (or $t_d$) only (temporal effect), or both $a$ and $d$ (nodal \& temporal effect).
-Specifically, the statistics are defined as
+The covariates can be time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$), and they could depend on $a$ only (nodal effect), $d$ only (temporal effect), or both $a$ and $d$ (nodal \& temporal effect).
+Specifically, the timestamp statistics are defined as
 \begin{itemize}
@@
 \end{itemize}
-
-	\subsection{Prediction Experiment}\label{subsec:Experiment_email}
+Note that our time generating process in Section \ref{subsec:Time} is sender-orientd process where the sender deterimes ``when to send the email," thus we incorporate network statistics that depends on $a$ only---outdegree of sender $a$ and indegree of sender $a$ (not $r$ this time).
+\newpage
+	\subsection{Prediction Experiments}\label{subsec:Experiment_email}
 
@@
 The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time-increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
-All our findings in previous section is further revealed in the PPC results from exponential distribution, which are attached in Appendix \ref{sec: PPCexp}.
+All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC results from exponential distribution, which are attached in Appendix \ref{sec: PPCexp}.
 \subsection{Parameter Estimates and Interpretation}\label{subsec:Result_email}
@@
 Surprisingly, none of the triadic effects seem to have significant effect on the edge generating process.
-	\begin{figure}[!b]
+	\begin{figure}[!t]
 		\centering
@@
 	\end{figure}
+
 	Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of the time-related coefficients $\boldsymbol{\eta}$.
@@
 \begin{appendices}
-\section{Normalizing Constant of MB$_{Gibbs}$}\label{sec: non-empty Gibbs measure}
-Our probability measure ``MB$_{Gibbs}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure \citep{fellows2017removing}---defines the probability of author $a$ selecting the binary recipient vector $\boldsymbol{u}_{ad}$ as
+\section{Normalizing Constant of MB$_{G}$}\label{sec: non-empty Gibbs measure}
+Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure \citep{fellows2017removing}---defines the probability of author $a$ selecting the binary recipient vector $\boldsymbol{u}_{ad}$ as
 \begin{equation*} 

### 2018-05-17 paper/ba-HEM/ba-sample.tex
BA template

--- 2018-05-16 paper/paper.tex
@@
-\documentclass[12pt]{article}
+\RequirePackage{etoolbox}
+\csdef{input@path}{%
+ {sty/}% cls, sty files
+ {img/}% eps files
+}%
+\csgdef{bibdir}{bib/}% bst, bib files
+
+\documentclass[ba]{imsart}
+%
+\pubyear{0000}
+\volume{00}
+\issue{0}
+\doi{0000}
+\firstpage{1}
+\lastpage{1}
+
+%
+\usepackage{amsthm}
 \usepackage{amsmath}
-\usepackage{bm}
-\usepackage{graphicx,psfrag,epsf}
-\usepackage{enumerate}
 \usepackage{natbib}
-\usepackage{url} % not crucial - just used below for the URL 
 \usepackage[algo2e]{algorithm2e}
@@
 \usepackage{mathtools}
-\usepackage[toc,page]{appendix}
-%\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0}
-
-% DON'T change margins - should be 1 inch all around.
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-.5in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{1.3in}%
-\addtolength{\topmargin}{-.8in}%
-
-\DeclarePairedDelimiter\abs{\lvert}{\rvert}
-\begin{document}
+\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
+\usepackage{graphicx}
 \def\spacingset#1{\renewcommand{\baselinestretch}%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\startlocaldefs
+\numberwithin{equation}{section}
+\theoremstyle{plain}
+\newtheorem{thm}{Theorem}[section]
+\endlocaldefs
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}
+\begin{document}
 
-\if0\blind
-{
-  \title{\bf The Hyperedge Event Model}
-  \author{Bomin Kim\thanks{
-    The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
-    Department of Statistics, Pennsylvania State University,\\
-  Aaron Schein\\
-  College of Information and Computer Sciences, UMass Amherst,\\
-    Bruce Desmarais\\
-    Department of Political Science, Pennsylvania State University,\\
-    and\\
-    Hanna Wallach\\
-    Microsoft Research NYC}
-  \maketitle
-} \fi
-\if1\blind
-{
-  \bigskip
-  \bigskip
-  \bigskip
-  \begin{center}
-    {\LARGE\bf The Hyperedge Event Model}
-\end{center}
-  \medskip
-} \fi
+\begin{frontmatter}
+\title{The Hyperedge Event Model}
+\runtitle{The Hyperedge Event Model}
 
-\bigskip
+\begin{aug}
+\author{\fnms{Bomin} \snm{Kim}\thanksref{addr1,t1,t2,m1}\ead[label=e1]{bzk147@psu.edu}},
+\author{\fnms{Aaron} \snm{Schein}\thanksref{addr2,t3,m1,m2}\ead[label=e2]{second@somewhere.com}},
+\author{\fnms{Bruce} \snm{Desmarais}\thanksref{addr3,t3,m1,m2}\ead[label=e3]{second@somewhere.com}},
+\and
+\author{\fnms{Hanna} \snm{Wallach}\thanksref{addr4,t1,m2}
+\ead[label=e4]{third@somewhere.com}
+%\ead[label=u1,url]{http://www.foo.com}
+}
+\runauthor{Kim et al.}
+
+\address[addr1]{Department of Statistics, Pennsylvania State University
+    \printead{e1} % print email address of "e1"
+}
+\address[addr2]{College of Information and Computer Sciences, UMass Amherst
+	\printead{e2} % print email address of "e1"
+}
+\address[addr3]{Department of Political Science, Pennsylvania State University
+	\printead{e3} % print email address of "e1"
+}
+\address[addr4]{ Microsoft Research NYC
+    \printead{e3}
+}
+
+%\thankstext{t1}{Some comment}
+%\thankstext{t2}{First supporter of the project}
+%\thankstext{t3}{Second supporter of the project}
+
+\end{aug}
+
 \begin{abstract}
@@
 
-\noindent%
-{\it Keywords:}  3 to 6 keywords, that do not appear in the title
-\vfill
+\begin{keyword}[class=MSC]
+\kwd[Primary ]{60K35}
+\kwd{60K35}
+\kwd[; secondary ]{60K35}
+\end{keyword}
 
-\newpage
-\spacingset{1.45} % DON'T change the spacing!
-\section{Introduction}\label{sec:intro}
+\begin{keyword}
+\kwd{sample}
+\kwd{\LaTeXe}
+\end{keyword}
+
+\end{frontmatter}
+
+\section{Introduction}\label{sec:introduction}
+
 In recent decades, real-time digitized textual communication has developed into a ubiquitous form of social and professional interaction \citep{kanungo2008modeling, szostek2011dealing, burgess2004email, pew2016}.
@@
 Concentrating on developing a statistical network model with better handling of hyperedges, we introduce the hyperedge event model (HEM) which simultaneously models the two components that govern time-stamped event formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
-In what follows, we introduce the HEM by describing how we assume the generatve process of a time-stamped event data (Section 2), and deriving the sampling equations for Bayesian inference (Section 3).
-Then, we apply the model to the Montgomery county government email data and perform two model validation tasks (Section 4).
+In what follows, we introduce the HEM by describing how we assume the generatve process of a time-stamped event data (Section \ref{sec:generative process}), and deriving the sampling equations for Bayesian inference (Section \ref{sec:inference}).
+Then, we apply the model to the Montgomery county government email data and perform two model validation tasks (Section \ref{subsec:Emails}).
 Finally, the paper finishes in Section 5 with conclusion and discussion.
+\section{The Hyperedge Event Model}\label{sec:generative process}
 
-\section{The Hyperedge Event Model (HEM)}\label{sec:generative process}
 Data generated under the model consists of $D$ unique edges.
@@
 For the latter case of hyperedges, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single recipient.
+
 \subsection{Edge Generating Process}\label{subsec: Tie}
@@
 Again, this is equivalent to assume independent Bernoulli trial on each $u_{adr}$ with probability of 1 being logit($\lambda_{adr}$), excluding the case when all $u_{adr}=0$.
-We provide the derivation of the normalizing constant as a tractable form in the supplementary material.
+We provide the derivation of the normalizing constant as a tractable form in Appendix A.
 
@@
 We use $f_\tau(\cdot; \mu, \sigma_\tau^2)$ and $F_\tau(\cdot; \mu, \sigma_\tau^2)$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $\sigma^2$.
-
+	\begin{algorithm}[ht]
+		\SetAlgoLined
+		\caption{Generating Process}
+		\begin{algorithmic}
+		\FOR{d=1 to D}
+			\FOR{a=1 to $A$}
+				\FOR{r=1 to $A$ (r $\neq$ a)}
+				\STATE	set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
+					\ENDFOR
+					\STATE	draw $\boldsymbol{u}_{ad}  \sim
+				\mbox{Gibbs}(\boldsymbol{\lambda}_{ad})$
+				\STATE		set $\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad})$
+				\STATE		draw $\tau_{ad} \sim f_\tau(\mu_{ad}, \sigma_\tau^2)$
+					\ENDFOR
+				\STATE	\textbf{For no tied events,}
+				\STATE	set $a_d= \mbox{argmin}_{a}(\tau_{ad})$\
+			\STATE		set $\boldsymbol{r}_d = \boldsymbol{u}_{a_d d}$
+				\STATE	set $t_d =t_{d-1} + \min_a\tau_{ad}$
+				\STATE	\textbf{For $n$ tied events,} (i.e., $n$ senders generated same minimum time increments)\\
+				\STATE	set $a_d, \ldots, a_{d+n}= \mbox{argmin}_{a}(\tau_{ad})$
+				\STATE	set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n}= ,\boldsymbol{u}_{a_{d+n} d}$
+				\STATE	set $t_d, \ldots, t_{d+n}=t_{d-1} + \min_a\tau_{ad}$
+			\STATE		jump to $d = d+n+1$
+			\ENDFOR
+		\end{algorithmic}
+		\label{alg:generative}
+	\end{algorithm}
 \subsection{Observed Data}\label{subsec:Observed}
@@
 Algorithm \ref{alg:generative} summarizes the generative process in Section \ref{sec:generative process}.
-	\begin{algorithm}[ht]
-		\spacingset{1}
-		\SetAlgoLined
-		\caption{Generating Process}
-		\For{d=1 to D}{
-			\For{a=1 to $A$}{
-				\For{r=1 to $A$ (r $\neq$ a)}{
-						set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
-					}  
-					draw $\boldsymbol{u}_{ad}  \sim
-					\mbox{Gibbs}(\boldsymbol{\lambda}_{ad})$\\
-					set $\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad})$\\
-					draw $\tau_{ad} \sim f_\tau(\mu_{ad}, \sigma_\tau^2)$
-				}
-				\textbf{For no tied events,}\\
-				set $a_d= \mbox{argmin}_{a}(\tau_{ad})$\\
-				set $\boldsymbol{r}_d = \boldsymbol{u}_{a_d d}$\\
-				set $t_d =t_{d-1} + \min_a\tau_{ad}$\\\\
-				\textbf{For $n$ tied events,} (i.e., $n$ senders generated same minimum time increments)\\
-				set $a_d, \ldots, a_{d+n}= \mbox{argmin}_{a}(\tau_{ad})$\\
-				set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n}= ,\boldsymbol{u}_{a_{d+n} d}$\\
-				set $t_d, \ldots, t_{d+n}=t_{d-1} + \min_a\tau_{ad}$\\
-				jump to $d = d+n+1$
-			}
-			\label{alg:generative}
-		\end{algorithm}
-\spacingset{1.45}
 \section{Posterior Inference}\label{sec:inference}
@@
 \begin{aligned}
-&P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\\&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, \sigma_\tau^2) \big)\Big),
+&P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\\&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, \sigma_\tau^2) \times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, \sigma_\tau^2) \big)\Big),
 \end{aligned}
@@
 where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $D$ events ($M \leq D$).
-If $M=D$ (i.e., no tied events), Equation (10) reduces to Equation (9).
+If $M=D$ (i.e., no tied events), equation (3.4) reduces to equation (3.3).
 Algorithm \ref{alg:MCMC} provides the pseudocode.
@@
 	\caption{MCMC Algorithm}
- 	set initial values of $\boldsymbol{b}, \boldsymbol{\eta}$, (and $\sigma_\tau^2$)\\
- 	\For{o=1 to outer}{
- 	 		\For{d=1 to D}{
- 			\For{a = 1 to A}{
- 				\For{r = 1 to A (r $\neq$ a)}{
- 						update $u_{adr}$ using Gibbs update --- Equation (7)
-	 			}
- 			}
- 		}
- 		 		\For{n=1 to inner1}{
- 		 			update $\boldsymbol{b}$ using Metropolis-Hastings --- Equation (8)
- 				}
- 		\For{n=1 to inner2}{
- 				update $\boldsymbol{\eta}$ using Metropolis-Hastings --- Equation (10)\\
- 				(if needed) update $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (10)
- 		}
- }
- 	Summarize the results with: last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ (and $\sigma_\tau^2$) 
+	\begin{algorithmic}
+	\STATE set initial values of $\boldsymbol{b}, \boldsymbol{\eta}$, (and $\sigma_\tau^2$)\\
+	\FOR{o=1 to outer}
+		\FOR{d=1 to D}
+		 \FOR{a = 1 to A}
+			\FOR{r = 1 to A (r $\neq$ a)}
+					\STATE update $u_{adr}$ using Gibbs update --- equation (7)
+			\ENDFOR
+		\ENDFOR
+		\ENDFOR
+		\FOR{n=1 to inner1}
+			\STATE update $\boldsymbol{b}$ using Metropolis-Hastings --- equation (8)
+		\ENDFOR
+	\FOR{n=1 to inner2}
+			\STATE update $\boldsymbol{\eta}$ using Metropolis-Hastings --- equation (10)
+			\STATE (if needed) update $\sigma_\tau^2$ using Metropolis-Hastings --- equation (10)
+		\ENDFOR
+
+	\ENDFOR
+	\STATE	Summarize the results with: last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ (and $\sigma_\tau^2$) 
+\end{algorithmic}
 \label{alg:MCMC}
@@
  	   \begin{itemize}
-		\spacingset{1}
  	   	\item[1.] intercept: ${x}_{adr1} =1$;
@@
  	   	\centering
-			\includegraphics[width=0.55\textwidth]{plots_paper/triad.png}	
+ 	   	\includegraphics[width=0.55\textwidth]{img/triad.png}	
  	   	\caption {Visualization of triadic statistics: 2-send, 2-receive, sibling, and cosibling.}
@@
  	   \begin{itemize}
-	\spacingset{1}
  	   	\item[1.] intercept: ${y}_{ad1} =1$;
@@
  	   Note that our time generating process in Section \ref{subsec:Time} is sender-orientd process where the sender deterimes ``when to send the email," thus we incorporate network statistics that depends on $a$ only---outdegree of sender $a$ and indegree of sender $a$ (not $r$ this time).
-\newpage
+
 	\subsection{Prediction Experiments}\label{subsec:Experiment_email}
 
-	The HEM has many component parts that need to be specified by the user (i.e., the selection of the event timing features $\bm{y}$, the recipient selection features $\bm{x}$, and the event time distribution $f$).
+	The HEM has many component parts that need to be specified by the user (i.e., the selection of the event timing features $\boldsymbol{y}$, the recipient selection features $\boldsymbol{x}$, and the event time distribution $f$).
 Many of these components will be specified based on user expertise (e.g., regarding which features would drive recipient selection), but some decisions may require a data-driven approach to model specification.
@@
 			\IF{$r_{dr}=$ NA}
-				\STATE draw $r_{dr}$ using $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$---Equation (7)
+			\STATE draw $r_{dr}$ using $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$---equation (7)
 			\ENDIF
@@
 		\centering
-		\includegraphics[width=1\textwidth]{plots_paper/PPEplot-1.png}	
+		\includegraphics[width=1\textwidth]{img/PPEplot-1.png}	
 		\caption {Comparison of predictive performance between lognormal and exponential distributions: boxplots for correct sender probability (\textit{left}), distribution of correct recipient probability in logit (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).}
@@
 As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing information of the emails?" and 2) offer one standard way to determine the time-increment distribution in Section \ref{subsec:Time}.
+
 	\subsection{Posterior Predictive Checks}\label{subsec:PPC_email} 	   
@@
 		\centering
-		\includegraphics[width=0.495\textwidth]{plots_paper/outdegreenew-1.png}	
-		\includegraphics[width=0.495\textwidth]{plots_paper/indegreenew-1.png}	
-		\includegraphics[width=0.495\textwidth]{plots_paper/recipientsizenew-1.png}	
-		\includegraphics[width=0.31\textwidth]{plots_paper/timeppnew.pdf}
+		\includegraphics[width=0.495\textwidth]{img/outdegreenew-1.png}	
+		\includegraphics[width=0.495\textwidth]{img/indegreenew-1.png}	
+		\includegraphics[width=0.495\textwidth]{img/recipientsizenew-1.png}	
+		\includegraphics[width=0.31\textwidth]{img/timeppnew.pdf}
 		\caption {PPC results from lognormal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
@@
 The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time-increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
-All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC results from exponential distribution, which are attached in Appendix \ref{sec: PPCexp}.
+All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC results from exponential distribution, which are attached in Appendix B.
 	\subsection{Parameter Estimates and Interpretation}\label{subsec:Result_email}
@@
 		\centering
-	\includegraphics[width=1\textwidth]{plots_paper/best-1.png}	
+		\includegraphics[width=1\textwidth]{img/best-1.png}	
 		\caption {Posterior distribution of $\boldsymbol{b}$ estimates.}
@@
 For example, as the actor $r$ received $n$ emails and the actor $a$ sent emails to $n$ rececievers over the last week, the actor $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times and $\exp(0.047\times n)\approx(1.048)^n$ times, respectively, more likely to send an email to $r$.
-On the other hand, outdegree statistic has negative effect---i.e., if the actor $a$ sent $n$ number of emails to anyone last week, then the actor $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times likely to send an email to $r$---possibly due to its multicollinearity with the statistics send and Nreceive.
-This can be interpreted as ``if the actor $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of send) or 2) no broadcast or multicast emails (excluding the effect of Nreceive)'' then the actor $a$ is less likely to send an email to $r$.
+On the other hand, outdegree statistic has negative effect---i.e., if the actor $a$ sent $n$ number of emails to anyone last week, then the actor $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times likely to send an email to $r$---possibly due to its multicollinearity with the statistics send and hyperedge size.
+This can be interpreted as ``if the actor $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of send) or 2) no broadcast or multicast emails (excluding the effect of hyperedge size)'' then the actor $a$ is less likely to send an email to $r$.
 Rest of statistics are not statistically significant because their 95\% credible interval do not include 0.
@@
 		\centering
-		\includegraphics[width=0.89\textwidth]{plots_paper/etaest-1.png}	
+		\includegraphics[width=0.89\textwidth]{img/etaest-1.png}	
 		\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
@@
 
-\iffalse
-\subsection{Case Study 2: International Sanctions}\label{subsec:International Sanctions}
-\subsubsection{Threat and Imposition of Sanctions (TIES) Data}\label{subsubsec:TIES}
-We processed the threat and imposition of sanctions (TIES) data \citep{morgan2014threat} that includes the records of international sanctions---defined as actions that one or more countries take to limit or end their economic relations with a target country in an effort to persuade that country to change one or more of its policies---from 1945 to 2005.
-\subsubsection{Covariates}\label{subsec:Covariates_sanction}
-\subsubsection{Parameter Estimation and Interpretation}\label{subsubsec:Result_sanction}
-	\subsubsection{Posterior Predictive Checks}\label{subsubsec:PPC_sanction} 	 
-		\subsubsection{Prediction Experiment}\label{subsubsec:Experiment_sanction} 
-		\fi 
 \section{Conclusion}\label{sec:conclusion}
@@
 Considering the recent explosion of network dataset with huge number of nodes (e.g., online comnunications), the development of model adjustments for better applicability are objects of future work.
-\bibliographystyle{agsm}
-\bibliography{multicastnetwork}
-\begin{appendices}
-\section{Normalizing Constant of MB$_{G}$}\label{sec: non-empty Gibbs measure}
+
+\section*{Appendix}
+	\subsection*{Appendix A: Normalizing Constant of MB$_{G}$}\label{subsec: non-empty Gibbs measure}
 	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure \citep{fellows2017removing}---defines the probability of author $a$ selecting the binary recipient vector $\boldsymbol{u}_{ad}$ as
@@
 	\end{equation*}
- \section{PPC Results from Exponential Distribution}\label{sec: PPCexp}
+	\subsection*{Appendix B: PPC Results from Exponential Distribution}\label{subsec: PPCexp}
 	\begin{figure}[H]
 		\centering
- 		\includegraphics[width=0.495\textwidth]{plots_paper/outdegree_exp-1.png}	
- 		\includegraphics[width=0.495\textwidth]{plots_paper/indegree_exp-1.png}	
- 		\includegraphics[width=0.495\textwidth]{plots_paper/recipientsize_exp-1.png}	
- 		\includegraphics[width=0.31\textwidth]{plots_paper/timepp_exp-1.png}
+		\includegraphics[width=0.495\textwidth]{img/outdegree_exp-1.png}	
+		\includegraphics[width=0.495\textwidth]{img/indegree_exp-1.png}	
+		\includegraphics[width=0.495\textwidth]{img/recipientsize_exp-1.png}	
+		\includegraphics[width=0.31\textwidth]{img/timepp_exp-1.png}
 		\caption {PPC results from exponential distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
@@
 	\end{figure}
-	\end{appendices}
+
+\begin{acknowledgement}
+	This work was supported in part by the University of Massachusetts Amherst Center for Intelligent Information Retrieval and in part by National Science Foundation grants DGE-1144860, SES-1619644, and CISE-1320219.
+Any opinions, findings, and conclusions or recommendations are those of the authors and do not necessarily reflect those of the
+	sponsors.
+\end{acknowledgement}
+
+\begin{supplement}
+\sname{Supplement A}\label{suppA} 
+\stitle{Title of the Supplement A}
+\slink[url]{http://www.some-url-address.org/dowload/0000.zip}
+\sdescription{Add description for supplement material.}
+\end{supplement}
+
+\bibliographystyle{ba}
+\bibliography{multicastnetwork}
+
 \end{document}

### 2018-05-17 code/Montgomery_processing2.R

@@ -117,6 +117,7 @@ for (n in 1:500) {
 Montgomery_infer2 = Inference(edge, X, Y, 55000, c(10,1,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
 proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = Montgomery$lasttime, timedist = "exponential")
 
+save(Montgomery_infer2, file = "/Users/bomin8319/Desktop/Montgomery_infer2.RData")
 
 setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC2")
 for (n in 1:500) {

### 2018-05-17 paper/ba-HEM/ba-sample.tex
ba-HEM.pdf

@@
 We express each parameter’s conditional posterior in a closed form using the data augmentation schemes in $\boldsymbol{u}$ \citep{tanner1987calculation}.
-In this section, we provide each latent variable's conditional posterior.
+In this section, we provide each latent variable's conditional posterior, and demonstrate how we perform the prior-posterior simulator test of \cite{geweke2004getting} for the HEM.
 
+\subsection{Full Conditional Distributions}\label{subsec:conditionaldist}
 First, since $u_{adr}$ is a binary random variable, new values may be sampled directly using
@@
 \end{algorithm}
+\subsection{Getting It Right (GiR) Test} \label{subec:GiR}
+  Software development is integral to the objective of applying the HEM to real world data.
+Code review is a valuable process in any research computing context, and the prevalence of software bugs in statistical software is well documented \citep[e.g., ][]{altman2004numerical,mccullough2009accuracy}.
+With highly complex models such as the HEM, there are many ways in which software bugs can be introduced and go unnoticed.
+As such, we present a joint analysis of the integrity of our generative model, sampling equations, and software implementation.
+
+   \cite{geweke2004getting} introduced the ``Getting it Right'' (GiR) test---a joint distribution test of posterior simulators which can detect errors in sampling equations as well as coding errors---and it has been used to test the implementation of Bayesian inference algorithms \citep{zhao2016bayesian}.
+The test involves comparing the distributions of variables simulated from two joint distribution samplers, which we call ``forward" and ``backward" samples.
+The forward sampler draws unobservable variables from the prior and then generates the observable data conditional on the unobservables.
+The backward sampler alternates between the inference and an observables simulator, by running the inference code on observable data to obtain posterior estimates of the unobervable variables and then re-generating the observables given the inferred unobservables.
+The backward sampler is initialized by running an iteration of inference on observables drawn directly from the prior.
+Since the only information on which both the forward and backward samplers are based is the prior, if the sampling equations are correct and the code is implemented without bugs, each variable should have the same distribution in the forward and backward samples.
+
+   In the forward samples, both observable and unobservable variables are generated using Algorithm \ref{alg:generative}.
+In the backward samples, unobservable variables are generated using the sampling equations for inference, which we derived in Section \ref{subsec:conditionaldist}.
+For each forward and backward sample that consists of $D$ number of edges, we save these statistics:
+   \begin{itemize}
+   	\item[1.] Mean of observed recipient sizes $ \lVert \boldsymbol{r}_{d} \rVert_1 $ across $d=1,\ldots,D$,
+   	\item[2.] Mean of time-increments $\tau_d$ across $d=1,...,D$,
+   	\item[3.] $b_p$ value used to generate the samples $p = 1,...,P$,
+   	\item[4.] $\eta_p$ value used to generate the samples $p = 1,...,P$,
+   	\item[5.] $\sigma^2_\tau$ value used to generate the samples
+   \end{itemize}
+
+   To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using lognormal distibution for the time distribution $f$.
+We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
+We also calculated t-test and Mann-Whitney test p-values in order to test for differences in the distributions generated in the forward and backward samples.
+Before we calculated these statistics, we thinned our samples
+   by taking every 9th sample starting at the 10,000th sample for a resulting sample size of 10,000, in order to reduce the autocorrelation in the Markov chains.
+In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
+We depict the GiR results using probability-probability (PP) plots.
+To compare two samples with a PP-plot we calculate the empirical quantile in each sample of a set of values observed across the two samples, then plot the sets of quantiles in the two samples against each other.
+If the two samples are from equivalent distributions, the quantiles should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
+The GiR test results are depicted in Figure \ref{fig:PPplot}, which show that we pass the test on every statistic.
+   \begin{figure}[ht]
+   	\centering
+   			\includegraphics[width=1\textwidth]{img/etaest-1.png}	
+   	\label{fig:PPplot}
+   	\caption{Probability-Probability plot for the GiR test statistics.}
+   \end{figure}
+
  	   \section{Application to Montgomary County Emails}\label{subsec:Emails}
@@
 As with the nodal (2, 3, 10, 11) and dyadic (4, 5) effects, the triadic (6--9) effects are designed so that their coefficient have a straightforward interpretation.
+The statistics ``outdegree" and ``indegree" measures the gregariousness and popularity effect of the node by counting the number of emails sent from $a$ and received by $r$, respectively, within the last 7 days.
+Moreover, in order to capture individual tendency of writing multicast emails, we include the statistic ``hyperedge size"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of recipients are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
 Dyadic statistics ``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
@@
 We particularly choose exponential distribution as an alternative to what we used earlier (i.e., lognormal) since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
-
-	We evaluate the model's ability to predict edges and timestamps from the Montgomery County email data, conditioned on their ``training" part of the data.
-To perform the experiment, we separately formed a test split of each three components---sender, recipients, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
-Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, parameter estimates, and current values of test data.
-We then run inference to update the latent variables given the imputed and observed data.
-We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for ``test" data.
-Algorithm \ref{alg:PPE} outlines this procedure in detail.
-We run the experiment and measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
-First, we compare the correct sender probability for missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
-The plot on the left shows that lognormal distribution reaches higher correct sender probability than exponential distribution, although their centers (e.g., medians) are similar.
-Secondly, we compute similar measure for recipients---correct recipient probability $P(r_{dr} = r^{obs}_{dr})$ in Algorithm \ref{alg:PPE} where $r^{obs}_{dr}$ is either 1 (received) or 0 (not received)---and visually compare the two distributions in logit scale (i.e., $\log(\frac{P(r_{dr} = r^{obs}_{dr}|\cdot)}{1-P(r_{dr} = r^{obs}_{dr})})$).
-Since the edge generating process (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there is no significant difference between lognormal and exponential in their performance of predicting unknown recipients.
-Finally, prediction errors for missing timestamps are measured using the median absolute percentage error (MdAPE) \citep{hyndman2006another}, where we take the median of absolute percentage errors $p_{di}$ for $i=1,\ldots,500$ for $d$th document, calculated as follows:
 	\begin{algorithm}[!t]
@@
 	\end{algorithm}
+
+	We evaluate the model's ability to predict edges and timestamps from the Montgomery County email data, conditioned on their ``training" part of the data.
+To perform the experiment, we separately formed a test split of each three components---sender, recipients, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
+Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, parameter estimates, and current values of test data.
+We then run inference to update the latent variables given the imputed and observed data.
+We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for ``test" data.
+Algorithm \ref{alg:PPE} outlines this procedure in detail.
+We run the experiment and measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
+First, we compare the correct sender probability for missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
+The plot on the left shows that lognormal distribution reaches higher correct sender probability than exponential distribution, although their centers (e.g., medians) are similar.
+Secondly, we compute similar measure for recipients---correct recipient probability $P(r_{dr} = r^{obs}_{dr})$ in Algorithm \ref{alg:PPE} where $r^{obs}_{dr}$ is either 1 (received) or 0 (not received)---and visually compare the two distributions in logit scale (i.e., $\log(\frac{P(r_{dr} = r^{obs}_{dr}|\cdot)}{1-P(r_{dr} = r^{obs}_{dr})})$).
+Since the edge generating process (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there is no significant difference between lognormal and exponential in their performance of predicting unknown recipients.
+Finally, prediction errors for missing timestamps are measured using the median absolute percentage error (MdAPE) \citep{hyndman2006another}, where we take the median of absolute percentage errors $p_{di}$ for $i=1,\ldots,500$ for $d$th document, calculated as follows:
 	\begin{figure}[!t]
@@
 
+\begin{acknowledgement}
+	This work was supported in part by the University of Massachusetts Amherst Center for Intelligent Information Retrieval and in part by National Science Foundation grants DGE-1144860, SES-1619644, and CISE-1320219.
+Any opinions, findings, and conclusions or recommendations are those of the authors and do not necessarily reflect those of the
+	sponsors.
+\end{acknowledgement}
+
 \section*{Appendix}
@@
 
-\begin{acknowledgement}
-	This work was supported in part by the University of Massachusetts Amherst Center for Intelligent Information Retrieval and in part by National Science Foundation grants DGE-1144860, SES-1619644, and CISE-1320219.
-Any opinions, findings, and conclusions or recommendations are those of the authors and do not necessarily reflect those of the
-	sponsors.
-\end{acknowledgement}
-
 \begin{supplement}
@@
 \bibliographystyle{ba}
-\bibliography{multicastnetwork}
+\bibliography{baHEM}
 

### 2018-05-17 code/GiR.R

@@ -2,7 +2,7 @@ source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
 
 D = 100
 A = 5
-P = 5
+P = 4
 #Q = 3
 X = array(rnorm(D*A*A*P), dim = c(D,A,A,P))
 X[,,,1] = 1
@@ -19,12 +19,12 @@ support = gibbs.measure.support(A-1)
 prior.beta = list(mean = c(-3, rep(0, P-1)), var = diag(P))
 prior.eta = list(mean = rep(0, Q), var = diag(Q))
 prior.sigma2 = list(a = 3, b = 1)
-Nsamp = 500
-outer = 5
+Nsamp = 10^5
+outer = 10
 inner = c(5, 5, 1)
 burn = 0
 #Schein test
-result = matrix(NA, Nsamp, 2*(2+P+Q))
+result = matrix(NA, Nsamp, 2*(3+P+Q))
 for (n in 1:Nsamp) {
   if (n %% 100 == 0) print(n)
   beta = rmvnorm_arma(1, prior.beta$mean, prior.beta$var)
@@ -33,10 +33,13 @@ for (n in 1:Nsamp) {
   initial = Generate(D, A, beta, eta, sigma2, X, Y, support)
   infer = Inference(initial$data, X, Y, outer, inner, burn, prior.beta, prior.eta, prior.sigma2, 
                     initial = initial, proposal.var = c(0.01, 0.1, 0.01, 0.5), lasttime = 0)
-  result[n, ] = c(mean(vapply(initial$u, function(x) rowSums(x), rep(0, A))),
+  initial2 = Generate(D, A, infer$beta[outer,], infer$eta[outer,], infer$sigma2[outer,], X, Y, support)                  
+  result[n, ] = c(mean(vapply(initial$data, function(x) sum(x$r_d), c(1))),
+ 				 mean(vapply(2:D, function(d) initial$data[[d]]$t_d-initial$data[[d-1]]$t_d, c(1))),
                   initial$beta, initial$eta, initial$sigma2, 
-                  mean(vapply(infer$u, function(x) rowSums(x), rep(0, A))),
-                  infer$beta[outer,], infer$eta[outer,], infer$sigma2[outer,])			 
+                 mean(vapply(initial2$data, function(x) sum(x$r_d), c(1))),
[…]

### 2018-05-20 paper/ba-HEM/ba-sample.tex
PPE results updated

@@
 We use $f_\tau(\cdot; \mu, \sigma_\tau^2)$ and $F_\tau(\cdot; \mu, \sigma_\tau^2)$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $\sigma^2$.
-	\begin{algorithm}[ht]
+	\begin{algorithm}[!b]
 		\SetAlgoLined
@@
 Algorithm \ref{alg:MCMC} provides the pseudocode.
-\begin{algorithm}[H]
+\begin{algorithm}[!b]
 	\spacingset{1}
@@
    	\item[3.] $b_p$ value used to generate the samples $p = 1,...,P$,
-   	\item[4.] $\eta_p$ value used to generate the samples $p = 1,...,P$,
+   	\item[4.] $\eta_q$ value used to generate the samples $q = 1,...,Q$,
    	\item[5.] $\sigma^2_\tau$ value used to generate the samples
@@
 We also calculated t-test and Mann-Whitney test p-values in order to test for differences in the distributions generated in the forward and backward samples.
-Before we calculated these statistics, we thinned our samples
-   by taking every 9th sample starting at the 10,000th sample for a resulting sample size of 10,000, in order to reduce the autocorrelation in the Markov chains.
+Before we calculated these statistics, we thinned our samples by taking every 9th sample starting at the 10,000th sample for a resulting sample size of 10,000, in order to reduce the autocorrelation in the Markov chains.
 In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
@@
 If the two samples are from equivalent distributions, the quantiles should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
-The GiR test results are depicted in Figure \ref{fig:PPplot}, which show that we pass the test on every statistic.
+The GiR test results are depicted in Figure \ref{figure:GiRplot}, which show that we pass the test on every statistic.
    \begin{figure}[ht]
    	\centering
-   			\includegraphics[width=1\textwidth]{img/etaest-1.png}	
-   	\label{fig:PPplot}
+   	\includegraphics[width=1\textwidth]{img/GiRplot-1.png}	
    	\caption{Probability-Probability plot for the GiR test statistics.}
+   	   	\label{figure:GiRplot}
    \end{figure}
-
  	   \section{Application to Montgomary County Emails}\label{subsec:Emails}
- 	   We now present a case study applying our method to Montgomery county government email data. For this case study,
- 	   we formulate the network statistics $\boldsymbol{x}$ and timestamp statistics $\boldsymbol{y}$ and ground them in illustrative examples.
-We then report a suite of experiments that test our method’s ability to form the posterior distribution over latent variables.
- 	   \subsection{Data}\label{subsec:Montgomery}
+ 	   We now present a case study applying our method to Montgomery county government email data.
+ 	   %\subsection{Data}\label{subsec:Montgomery}
  	   Our data come from the North Carolina county government email dataset collected by \cite{ben2017transparency} that includes internal email corpora covering the inboxes and outboxes of managerial-level employees of North Carolina county governments.
@@
 To summarize, Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
+For this case study,
+ 	   we formulate the network statistics $\boldsymbol{x}$ and timestamp statistics $\boldsymbol{y}$ and ground them in illustrative examples.
+We then report a suite of experiments that test our method’s ability to form the posterior distribution over latent variables.
  	   \subsection{Covariates}\label{subsec:Covariates_email}
@@
 We run the experiment and measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
-First, we compare the correct sender probability for missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
-The plot on the left shows that lognormal distribution reaches higher correct sender probability than exponential distribution, although their centers (e.g., medians) are similar.
-Secondly, we compute similar measure for recipients---correct recipient probability $P(r_{dr} = r^{obs}_{dr})$ in Algorithm \ref{alg:PPE} where $r^{obs}_{dr}$ is either 1 (received) or 0 (not received)---and visually compare the two distributions in logit scale (i.e., $\log(\frac{P(r_{dr} = r^{obs}_{dr}|\cdot)}{1-P(r_{dr} = r^{obs}_{dr})})$).
-Since the edge generating process (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there is no significant difference between lognormal and exponential in their performance of predicting unknown recipients.
+We compare the predictions in terms of classification accuracy in predicting the authors and recipients, as well as prediction error in the timestamps.
+First, we compare the posterior probability of correct senders from missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
+We call this measure as ``correct sender posterior probability." The plot on the left demonstrates that both lognormal and exponential distributions acheive better predictive performance for senders compared to what is expected under random guess (dotted blue line at $1/18$), with lognormal distribution showing slightly higher performance than exponential distribution on average.
+Secondly, since the recipient vector is binary---$r_{dr}=1$ if received or $r_{dr}=0$ otherwise---we compute $F_1$ scores for recipient predictions, comparing the true recipient vector $\boldsymbol{r}^{obs}_{dr}$ and predicted recipient vectors $\boldsymbol{r}^{pred}_{dr}$ for missing recipient indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA).
+Although the edge generating process (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there exists noticeable difference between lognormal and exponential in their performance of predicting unknown recipients.
+Similar to the sender prediction, lognormal outperforms exponential in general.
 Finally, prediction errors for missing timestamps are measured using the median absolute percentage error (MdAPE) \citep{hyndman2006another}, where we take the median of absolute percentage errors $p_{di}$ for $i=1,\ldots,500$ for $d$th document, calculated as follows:
@@
 		\centering
-		\includegraphics[width=1\textwidth]{img/PPEplot-1.png}	
-		\caption {Comparison of predictive performance between lognormal and exponential distributions: boxplots for correct sender probability (\textit{left}), distribution of correct recipient probability in logit (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).}
+		\includegraphics[width=1\textwidth]{img/PPEplotnew-1.png}	
+		\caption {Comparison of predictive performance between lognormal and exponential distributions: boxplots for correct sender posterior probability (\textit{left}), distribution of correct recipient posterior probability in log-scale (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).
+The dotted blue lines in the left plot represents the correct sender probability expected by random guess---i.e., $1/A=1/18\approx0.056$.}
 		\label{figure:PPEresults}
@@
 	and we present boxplots for the MdAPE estimates on the right plot.
+For better visualization, we plot MdAPE estimates in log-scale since they are highly right-skewed.
 As expected, we have huge benefit in the performance of timestamp prediction when we choose lognormal distribution over exponential.
@@
 The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time-increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
-All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC results from exponential distribution, which are attached in Appendix B.
+All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC results from exponential distribution, and the plots comparing posterior checks between lognormal and exponential distributions are attached in Appendix B.
+
 	\subsection{Parameter Estimates and Interpretation}\label{subsec:Result_email}
@@
 	\end{equation*}
-	\subsection*{Appendix B: PPC Results from Exponential Distribution}\label{subsec: PPCexp}
+	\subsection*{Appendix B: Comparison of PPC Results: lognormal vs. exponential}\label{subsec: PPCexp}
+	\iffalse
 	\begin{figure}[H]
@@
 		\includegraphics[width=0.495\textwidth]{img/recipientsize_exp-1.png}	
-		\includegraphics[width=0.31\textwidth]{img/timepp_exp-1.png}
+		\includegraphics[width=0.31\textwidth]{img/timedist_exp-1.png}
 		\caption {PPC results from exponential distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
@@
 		\label{figure:PPCexp}
+	\end{figure}
+	\fi
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=0.495\textwidth]{img/outdegree_two-1.png}	
+			\includegraphics[width=0.495\textwidth]{img/indegree_two-1.png}	
+			\includegraphics[width=0.495\textwidth]{img/recipientsize_two-1.png}	
+			\includegraphics[width=0.31\textwidth]{img/timepp_two-1.png}
+			\caption {Comparison of PPC results between lognormal (\textit{red}) and exponential (\textit{green}) distributions: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
+Red lines in the first three plot depict the observed statistics, and the black line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
+			\label{figure:PPCtwo}
 		\end{figure}

### 2018-05-20 Emails/Montgomery_result.R

@@ -58,21 +58,21 @@ recipients = tabulate(rowSums(email[trim,3:20]), A-1)
 timeinc = diff(sort(email$timepoints)[43:max(trim)])/3600
 
 
-indegreedist = matrix(NA, 500, A)
-outdegreedist = matrix(NA,  500, A)
-recipientsdist = matrix(NA,  500, A-1)
-timedist = matrix(NA, 500, 621)
+indegreedist1 = matrix(NA, 500, A)
+outdegreedist1 = matrix(NA,  500, A)
+recipientsdist1 = matrix(NA,  500, A-1)
+timedist1 = matrix(NA, 500, 621)
 #setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC")
 #setwd("/Users/bomin8319/")
-setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC2")
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC")
 
 for (n in 1:500) {
 	filename = paste0("Montgomery_PPCnew", n,".RData")
 	load(filename)
-	outdegreedist[n, ] = tabulate(vapply(1:621, function(x) Montgomery_PPC[[x]]$a_d, c(1)), A)
-	indegreedist[n, ] = rowSums(sapply(1:621, function(x) Montgomery_PPC[[x]]$r_d))
-	recipientsdist[n, ] = tabulate(vapply(1:621, function(x) sum(Montgomery_PPC[[x]]$r_d), c(1)), A-1)
-	timedist[n, ] = vapply(1:621, function(x) Montgomery_PPC[[x]]$t_d, c(1))/ timeunit
+	outdegreedist1[n, ] = tabulate(vapply(1:621, function(x) Montgomery_PPC[[x]]$a_d, c(1)), A)
+	indegreedist1[n, ] = rowSums(sapply(1:621, function(x) Montgomery_PPC[[x]]$r_d))
+	recipientsdist1[n, ] = tabulate(vapply(1:621, function(x) sum(Montgomery_PPC[[x]]$r_d), c(1)), A-1)
+	timedist1[n, ] = c(Montgomery_PPC[[1]]$t_d -email$timepoints[42], vapply(2:621, function(x) Montgomery_PPC[[x]]$t_d - Montgomery_PPC[[x-1]]$t_d , c(1)))/ timeunit
 } 
 
 outdegreedist = data.frame(outdegreedist)
[…]

### 2018-05-20 Emails/PPEnew.R

@@ -75,11 +75,13 @@ Montgomery_PPE2 = PPE(edge, X, Y, 550, c(5,5,1), 50, prior.beta, prior.eta, prio
                      lasttime = Montgomery$lasttime, MHprop.var = 0.15, timedist = "exponential")
 
 save(Montgomery_PPE2, file = "/Users/bomin8319/Desktop/MulticastNetwork/Emails/Montgomery_PPE2.RData")
+save(Montgomery_PPE2, file = "/Users/bomin8319/Desktop/Montgomery_PPE2.RData")
 
 
 names(Montgomery_PPE)
 
 library(gridExtra)
+library(latex2exp)
 p = list()
 #################
 truesender = sapply(Montgomery_PPE$sendermissing, function(d) edge[[d]]$a_d)
@@ -92,7 +94,7 @@ library(ggplot2)
 library(reshape)
 sender = melt(sender)
 colnames(sender)[3] = "correct"
-p[[1]]=ggplot(data = sender, aes(x = dist, y = correct, fill = dist))+geom_boxplot()
+p[[1]]=ggplot(data = sender, aes(x = dist, y = correct, fill = dist))+geom_boxplot()+ylab("Correct sender posterior probability")+geom_hline(yintercept=1/18, col = 'blue', lty=2, lwd=1)
 boxplot(sapply(1:62, function(d) predprob[d,truesender[d]]), sapply(1:62, function(d) predprob2[d,truesender[d]]))
 
 ###############################################
@@ -107,13 +109,27 @@ probtrue2 = sapply(1:1118, function(d) predprob2[d,truereceiver[d]+1])
 
 receiver = data.frame(probtrue = log(probtrue /(1-probtrue)), dist = rep("lognormal", 1118))
 receiver = rbind(receiver, data.frame(probtrue = log(probtrue2/(1-probtrue2)), dist = rep("exponential", 1118)))
-library(ggplot2)
-library(reshape)
 receiver = melt(receiver)
 colnames(receiver)[3] = "logit"
 ggplot(data = receiver, aes(x = dist, y = logit, fill = dist))+geom_boxplot()
 p[[2]]=ggplot(data = receiver, aes(x = logit, fill = dist))+geom_histogram(position = "dodge")
 #boxplot(sapply(1:62, function(d) predprob[d,truesender[d]]), sapply(1:62, function(d) predprob2[d,truesender[d]]))
+
+######################
+library(MLmetrics)
+
[…]

### 2018-05-20 code/GiR.R

@@ -21,10 +21,10 @@ prior.eta = list(mean = rep(0, Q), var = diag(Q))
 prior.sigma2 = list(a = 3, b = 1)
 Nsamp = 10^5
 outer = 10
-inner = c(5, 5, 1)
+inner = c(5, 5, 5)
 burn = 0
 #Schein test
-result = matrix(NA, Nsamp, 2*(3+P+Q))
+result = matrix(NA, Nsamp, 2*(5+P+Q))
 for (n in 1:Nsamp) {
   if (n %% 100 == 0) print(n)
   beta = rmvnorm_arma(1, prior.beta$mean, prior.beta$var)
@@ -35,11 +35,45 @@ for (n in 1:Nsamp) {
                     initial = initial, proposal.var = c(0.01, 0.1, 0.01, 0.5), lasttime = 0)
   initial2 = Generate(D, A, infer$beta[outer,], infer$eta[outer,], infer$sigma2[outer,], X, Y, support)                  
   result[n, ] = c(mean(vapply(initial$data, function(x) sum(x$r_d), c(1))),
+                  var(vapply(initial$data, function(x) sum(x$r_d), c(1))),
  				 mean(vapply(2:D, function(d) initial$data[[d]]$t_d-initial$data[[d-1]]$t_d, c(1))),
+ 				var(vapply(2:D, function(d) initial$data[[d]]$t_d-initial$data[[d-1]]$t_d, c(1))),
                   initial$beta, initial$eta, initial$sigma2, 
                  mean(vapply(initial2$data, function(x) sum(x$r_d), c(1))),
+ 			var(vapply(initial2$data, function(x) sum(x$r_d), c(1))),
                   mean(vapply(2:D, function(d) initial2$data[[d]]$t_d-initial2$data[[d-1]]$t_d, c(1))),
+ 				var(vapply(2:D, function(d) initial2$data[[d]]$t_d-initial2$data[[d-1]]$t_d, c(1))),
                   initial2$beta, initial2$eta, initial2$sigma2)			 
 }
-par(mfrow=c(2,5))
-GiR_PP_Plots(result[,c(1:(3+P+Q))], result[,c((4+P+Q):(2*(3+P+Q)))])
+par(mfrow=c(3,4))
+GiR_PP_Plots(result[,c(1:(5+P+Q))], result[,c((6+P+Q):(2*(5+P+Q)))])
+
+Forward_stats = result[,c(1:(3+P+Q))]
+Backward_stats = result[,c((4+P+Q):(2*(3+P+Q)))]
[…]

### 2018-05-20 code/Montgomery_processing2.R

@@ -118,7 +118,7 @@ Montgomery_infer2 = Inference(edge, X, Y, 55000, c(10,1,1), 15000, prior.beta, p
 proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = Montgomery$lasttime, timedist = "exponential")
 
 save(Montgomery_infer2, file = "/Users/bomin8319/Desktop/Montgomery_infer2.RData")
-
+load("/Users/bomin8319/Desktop/MulticastNetwork/Montgomery_infer2.RData")
 setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC2")
 for (n in 1:500) {
 	print(n)

### 2018-05-20 pkg/src/Multicast_rcpp.cpp

@@ -110,10 +110,10 @@ double Timepartsum2 (NumericMatrix mumat, IntegerVector senders, NumericVector t
     double timesum = 0;
     for (unsigned int d = 0; d < D; d++) {
         int a_d = senders[d] - 1;
-        timesum += R::dexp(timestamps[d], 1/exp(mumat(d, a_d)), TRUE);
+        timesum += R::dexp(timestamps[d], exp(mumat(d, a_d)), TRUE);
         for (unsigned int i = 0; i < mumat.ncol(); i++) {
         if (i != a_d) {
-            timesum += R::pexp(timestamps[d], 1/exp(mumat(d, i)), FALSE, TRUE);
+            timesum += R::pexp(timestamps[d], exp(mumat(d, i)), FALSE, TRUE);
     	  }
         }
     }
@@ -146,10 +146,10 @@ NumericVector Timepartindiv2 (NumericVector mu, double timestamp){
     int A = mu.size();
     NumericVector out(A);
     for (unsigned int a = 0; a < A; a++) {
-        out[a] += R::dexp(timestamp, 1/exp(mu[a]), TRUE);
+        out[a] += R::dexp(timestamp, exp(mu[a]), TRUE);
         for (unsigned int i = 0; i < A; i++) {
             if (i != a) {
-                out[a] += R::pexp(timestamp, 1/exp(mu[i]), FALSE, TRUE);
+                out[a] += R::pexp(timestamp, exp(mu[i]), FALSE, TRUE);
             }
         }
     }

### 2018-05-20 paper/older/paper.tex
Bayesian analysis version added

--- 2018-05-16 paper/paper.tex
@@
 
-\section{The Hyperedge Event Model (HEM)}\label{sec:generative process}
+\section{The Hyperedge Event Model}\label{sec:generative process}
 Data generated under the model consists of $D$ unique edges.
@@
 		\caption{Generating Process}
-		\For{d=1 to D}{
-			\For{a=1 to $A$}{
-				\For{r=1 to $A$ (r $\neq$ a)}{
-						set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
-					}  
-					draw $\boldsymbol{u}_{ad}  \sim
-					\mbox{Gibbs}(\boldsymbol{\lambda}_{ad})$\\
-					set $\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad})$\\
-					draw $\tau_{ad} \sim f_\tau(\mu_{ad}, \sigma_\tau^2)$
-				}
-				\textbf{For no tied events,}\\
-				set $a_d= \mbox{argmin}_{a}(\tau_{ad})$\\
-				set $\boldsymbol{r}_d = \boldsymbol{u}_{a_d d}$\\
-				set $t_d =t_{d-1} + \min_a\tau_{ad}$\\\\
-				\textbf{For $n$ tied events,} (i.e., $n$ senders generated same minimum time increments)\\
-				set $a_d, \ldots, a_{d+n}= \mbox{argmin}_{a}(\tau_{ad})$\\
-				set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n}= ,\boldsymbol{u}_{a_{d+n} d}$\\
-				set $t_d, \ldots, t_{d+n}=t_{d-1} + \min_a\tau_{ad}$\\
-				jump to $d = d+n+1$
-			}
+		\begin{algorithmic}
+			\FOR{d=1 to D}
+			\FOR{a=1 to $A$}
+			\FOR{r=1 to $A$ (r $\neq$ a)}
+			\STATE	set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
+			\ENDFOR
+			\STATE	draw $\boldsymbol{u}_{ad}  \sim
+			\mbox{Gibbs}(\boldsymbol{\lambda}_{ad})$
+			\STATE		set $\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad})$
+			\STATE		draw $\tau_{ad} \sim f_\tau(\mu_{ad}, \sigma_\tau^2)$
+			\ENDFOR
+			\STATE	\textbf{For no tied events,}
+			\STATE	set $a_d= \mbox{argmin}_{a}(\tau_{ad})$\
+			\STATE		set $\boldsymbol{r}_d = \boldsymbol{u}_{a_d d}$
+			\STATE	set $t_d =t_{d-1} + \min_a\tau_{ad}$
+			\STATE	\textbf{For $n$ tied events,} (i.e., $n$ senders generated same minimum time increments)\\
+			\STATE	set $a_d, \ldots, a_{d+n}= \mbox{argmin}_{a}(\tau_{ad})$
+			\STATE	set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n}= ,\boldsymbol{u}_{a_{d+n} d}$
+			\STATE	set $t_d, \ldots, t_{d+n}=t_{d-1} + \min_a\tau_{ad}$
+			\STATE		jump to $d = d+n+1$
+			\ENDFOR
+		\end{algorithmic}
 		\label{alg:generative}
 	\end{algorithm}
-\spacingset{1.45}
 \section{Posterior Inference}\label{sec:inference}
@@
 where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $D$ events ($M \leq D$).
-If $M=D$ (i.e., no tied events), Equation (10) reduces to Equation (9).
+If $M=D$ (i.e., no tied events), equation (10) reduces to equation (9).
 Algorithm \ref{alg:MCMC} provides the pseudocode.
@@
 	\caption{MCMC Algorithm}
- 	set initial values of $\boldsymbol{b}, \boldsymbol{\eta}$, (and $\sigma_\tau^2$)\\
- 	\For{o=1 to outer}{
- 	 		\For{d=1 to D}{
- 			\For{a = 1 to A}{
- 				\For{r = 1 to A (r $\neq$ a)}{
- 						update $u_{adr}$ using Gibbs update --- Equation (7)
-	 			}
- 			}
- 		}
- 		 		\For{n=1 to inner1}{
- 		 			update $\boldsymbol{b}$ using Metropolis-Hastings --- Equation (8)
- 				}
- 		\For{n=1 to inner2}{
- 				update $\boldsymbol{\eta}$ using Metropolis-Hastings --- Equation (10)\\
- 				(if needed) update $\sigma_\tau^2$ using Metropolis-Hastings --- Equation (10)
- 		}
- }
- 	Summarize the results with: last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ (and $\sigma_\tau^2$) 
+	\begin{algorithmic}
+		\STATE set initial values of $\boldsymbol{b}, \boldsymbol{\eta}$, (and $\sigma_\tau^2$)\\
+		\FOR{o=1 to outer}
+		\FOR{d=1 to D}
+		\FOR{a = 1 to A}
+		\FOR{r = 1 to A (r $\neq$ a)}
+		\STATE update $u_{adr}$ using Gibbs update --- equation (7)
+		\ENDFOR
+		\ENDFOR
+		\ENDFOR
+		\FOR{n=1 to inner1}
+		\STATE update $\boldsymbol{b}$ using Metropolis-Hastings --- equation (8)
+		\ENDFOR
+		\FOR{n=1 to inner2}
+		\STATE update $\boldsymbol{\eta}$ using Metropolis-Hastings --- equation (10)
+		\STATE (if needed) update $\sigma_\tau^2$ using Metropolis-Hastings --- equation (10)
+		\ENDFOR
+
+		\ENDFOR
+		\STATE	Summarize the results with: last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ (and $\sigma_\tau^2$) 
+	\end{algorithmic}
 	\label{alg:MCMC}
@@
 				\IF{$r_{dr}=$ NA}
-				\STATE draw $r_{dr}$ using $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$---Equation (7)
+				\STATE draw $r_{dr}$ using $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$---equation (7)
 				\ENDIF

### 2018-05-21 code/GiR.R
GiR plot replaced

@@ -47,9 +47,9 @@ for (n in 1:Nsamp) {
 }
 par(mfrow=c(3,4))
 GiR_PP_Plots(result[,c(1:(5+P+Q))], result[,c((6+P+Q):(2*(5+P+Q)))])
-
-Forward_stats = result[,c(1:(3+P+Q))]
-Backward_stats = result[,c((4+P+Q):(2*(3+P+Q)))]
+save(result, file = "/Users/bomin8319/Desktop/result.RData")
+Forward_stats = result[,c(1:(5+P+Q))]
+Backward_stats = result[,c((6+P+Q):(2*(5+P+Q)))]
 colnames(Forward_stats) = c("Mean Recipient Size", "Mean Time-increments", sapply(1:P, function(p){paste0("b",p," Estimates")}), sapply(1:Q, function(q){paste0(expression(eta),q," Estimates")}), "Variance Estimate")
 plot = list()
 library(ggplot2)
@@ -69,11 +69,13 @@ library(ggplot2)
   		qx2[j] = mean(Backward_stats[, i] <= uniqueValues[j])
   	}
   	data = data.frame(qx1 = qx1, qx2 = qx2)
-	plot[[i]] =qplot(data = data, x = qx1, y = qx2, colour = I("blue"), size = I(0.5)) + labs(x = "Forward", y = "Backward")+geom_abline(intercept = 0, col = 'red') + theme(text = element_text(size = rel(3)), plot.title= element_text(size=rel(4)))
+	plot[[i]] =qplot(data = data, x = qx1, y = qx2, colour = I("blue"), size = I(0.5)) + labs(x = "Forward", y = "Backward")+geom_abline(intercept = 0, col = 'red') + theme(text = element_text(size = rel(3)), plot.title= element_text(size=rel(3.5)))
 	#+labs(title = expression(nms[i]))
 }	
 library(gridExtra)
 library(latex2exp)
-grid.arrange(arrangeGrob(plot[[1]]+labs(title = "Mean Recipient Size"),
-	plot[[2]]+labs(title = "Mean Time-increments"),plot[[3]]+labs(title = expression(b*" Estimates for p=1")),plot[[4]]+labs(title = expression(b*" Estimates for p=2")),plot[[5]]+labs(title = expression(b*" Estimates for p=3")),
[…]

### 2018-05-21 paper/ba-HEM/ba-sample.tex
GiR plot replaced
convergence diagnostics

@@
 In this section, we present the results based on 55,000 MCMC outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
-While the inner iterations for $\boldsymbol{\eta}$ and $\sigma_\tau^2$ are fixed as 1, we use 10 inner iterations for $\boldsymbol{b}$ to adjust for its slower convergence rate.
-	\begin{figure}[!b]
+While the inner iterations for  $\sigma_\tau^2$ is fixed as 1, we use 10 and 20 inner iterations for $\boldsymbol{\eta}$ and $\boldsymbol{b}$, respectively, to adjust for its slower convergence rate.
+Convergence diagnostics for MCMC including some traceplots and Geweke diagnostics \citep{geweke1991evaluating} can be found in Appendix C.
+	\begin{figure}[!t]
 		\centering
@@
 Surprisingly, none of the triadic effects seem to have significant effect on the edge generating process.
-	\begin{figure}[!t]
-		\centering
-		\includegraphics[width=0.89\textwidth]{img/etaest-1.png}	
-		\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
-		\label{figure:etaresults}
-	\end{figure}
 
@@
 The posterior mean estimate of the variance parameter $\sigma^2_\tau$ is 14.093 with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time-increments in this data.
+		\begin{figure}[!t]
+			\centering
+			\includegraphics[width=0.89\textwidth]{img/etaest-1.png}	
+			\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
+			\label{figure:etaresults}
+		\end{figure}
 
@@
 	\end{equation*}
+	\newpage
 	\subsection*{Appendix B: Comparison of PPC Results: lognormal vs. exponential}\label{subsec: PPCexp}
@@
 		\end{figure}
+		\newpage
+	\subsection*{Appendix C: Convergence Diagnostics}\label{subsec: convergence}
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.495\textwidth]{img/betatrace.pdf}	
+		\includegraphics[width=0.495\textwidth]{img/etatrace.pdf}	
+		\includegraphics[width=0.495\textwidth]{img/betageweke.pdf}	
+		\includegraphics[width=0.44\textwidth]{img/etageweke.pdf}
+		\caption {Convergence diagnostics from lognormal distribution: traceplots and density plots for $\boldsymbol{b}$ chains (\textit{upper left}) and $\boldsymbol{\eta}$ chains (\textit{upper right}), and geweke diagnostics for $\boldsymbol{b}$ chains (\textit{lower left}) and $\boldsymbol{\eta}$ chains (\textit{lower right}).}
+		\label{figure:convergencediag}
+	\end{figure}
 

### 2018-05-21 Emails/traceplot.R

@@ -1,0 +1,39 @@
+load('~/Desktop/MulticastNetwork/Emails/Montgomery_infer.RData')
+load('~/Desktop/MulticastNetwork/Emails/Montgomery_infer2.RData')
+
+library(ggplot2)
+library(ggmcmc)
+library(gridExtra)
+library(ggthemes)
+library(latex2exp)
+library(MCMCpack)
+beta = t(sapply(1:5000, function(x) Montgomery_infer2$beta[8*x, c(2,5,10)]))
+colnames(beta) = c("beta2","beta5", "beta10")
+S <-  ggs(mcmc(beta))
+plot = ggs_traceplot(S)
+density = ggs_density(S)
+grid.arrange(plot, density, ncol = 2, nrow = 1)
+
+
+beta = t(sapply(1:5000, function(x) Montgomery_infer2$beta[8*x, ]))
+colnames(beta) = c(sapply(1:11, function(x) paste0("beta",x)))
+S <-  ggs(mcmc(beta))
+ggs_geweke(S)
+
+
+
+eta = t(sapply(1:5000, function(x) Montgomery_infer$eta[8*x, c(2,7)]))
+eta = cbind(eta, sapply(1:5000, function(x) Montgomery_infer$sigma2[8*x]))
+colnames(eta) = c("eta2", "eta7", "sigma2")
+S2 <-  ggs(mcmc(eta))
+plot = ggs_traceplot(S)
+density = ggs_density(S)
+grid.arrange(plot, density, ncol = 2, nrow = 1)
+
+eta = t(sapply(1:5000, function(x) Montgomery_infer2$eta[8*x, ]))
+colnames(eta) = c(sapply(1:7, function(x) paste0("eta",x)))
+S <-  ggs(mcmc(eta))
+ggs_geweke(S)
+
+
+

### 2018-05-23 paper/ba-HEM/ba-sample.tex
revisions to the abstract

@@
 \begin{abstract}
-We introduce the hyperedge event model (HEM)---a generative model for directed edges with multiple recipients or multiple senders. To define the model, we
-integrate a dynamic version of the exponential random graph model (ERGM) and generalized linear model (GLM) approach to jointly understand who communicates with whom, and when.
-We use the model to analyze emails sent between department managers in Montgomery county government in North Carolina.
+We introduce the hyperedge event model (HEM)---a generative model for events that can be represented as directed edges with one sender and one or more recipients or one recipient and one or more senders.
+To define the model, we
+integrate a dynamic version of the exponential random graph model (ERGM) of edge structure with a survival model for event timing to jointly understand who interacts with whom, and when.
+The HEM offers three innovations with respect to the literature---first, it extends a growing class of dynamic network models to model hyperedges.
+Second, we derive a recipient-selection distribution that forces the sender to select at least one recipient.
+Third, we incorporate both a timing equation and an edge-formation equation into the model specification.
+We use the HEM to analyze emails sent among department managers in Montgomery County government in North Carolina.
 Our application demonstrates that the model is effective at predicting and explaining time-stamped network data involving edges with multiple recipients.
+We present a out-of-sample prediction experiment to illustrate how researchers can select between different specifications of the model.
 \end{abstract}

### 2018-05-24 paper/ba-HEM/ba-sample.tex
revisions until page 6 of BA draft

@@
 	{#1}\small\normalsize} \spacingset{1}
-
+\usepackage{fmtcount}
 \startlocaldefs
@@
 \author{\fnms{Bomin} \snm{Kim}\thanksref{addr1,t1,t2,m1}\ead[label=e1]{bzk147@psu.edu}},
-\author{\fnms{Aaron} \snm{Schein}\thanksref{addr2,t3,m1,m2}\ead[label=e2]{second@somewhere.com}},
-\author{\fnms{Bruce} \snm{Desmarais}\thanksref{addr3,t3,m1,m2}\ead[label=e3]{second@somewhere.com}},
+\author{\fnms{Aaron} \snm{Schein}\thanksref{addr2,t3,m1,m2}\ead[label=e2]{aschein@cs.umass.edu}},
+\author{\fnms{Bruce} \snm{Desmarais}\thanksref{addr3,t3,m1,m2}\ead[label=e3]{bdesmarais@psu.edu}},
 \and
 \author{\fnms{Hanna} \snm{Wallach}\thanksref{addr4,t1,m2}
-\ead[label=e4]{third@somewhere.com}
+\ead[label=e4]{hanna@dirichlet.net}
 %\ead[label=u1,url]{http://www.foo.com}
 }
-\runauthor{Kim et al.}
+\runauthor{B. Kim et al.}
 
@@
 \begin{abstract}
-We introduce the hyperedge event model (HEM)---a generative model for events that can be represented as directed edges with one sender and one or more recipients or one recipient and one or more senders.
+We introduce the hyperedge event model (HEM)---a generative model for events that can be represented as directed edges with one sender and one or more receivers or one receiver and one or more senders.
 To define the model, we
@@
 The HEM offers three innovations with respect to the literature---first, it extends a growing class of dynamic network models to model hyperedges.
-Second, we derive a recipient-selection distribution that forces the sender to select at least one recipient.
+Second, we derive a receiver-selection distribution that forces the sender to select at least one receiver.
 Third, we incorporate both a timing equation and an edge-formation equation into the model specification.
 We use the HEM to analyze emails sent among department managers in Montgomery County government in North Carolina.
-Our application demonstrates that the model is effective at predicting and explaining time-stamped network data involving edges with multiple recipients.
+Our application demonstrates that the model is effective at predicting and explaining time-stamped network data involving edges with multiple receivers.
 We present a out-of-sample prediction experiment to illustrate how researchers can select between different specifications of the model.
@@
 For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involve one sender and multiple receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
-Similarly, \cite{fan2009learning} treats multicast emails as multiple single-recipient edges and randomly jitter the sent times, to avoid the violation of continous-time model assumption.
+Similarly, \cite{fan2009learning} treats multicast emails as multiple single-receiver edges and randomly jitter the sent times, to avoid the violation of continous-time model assumption.
 On the other hand, there have been numerous studies for hyperedges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}.
@@
 
-Concentrating on developing a statistical network model with better handling of hyperedges, we introduce the hyperedge event model (HEM) which simultaneously models the two components that govern time-stamped event formation: 1) the recipient selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
+Concentrating on developing a statistical network model with better handling of hyperedges, we introduce the hyperedge event model (HEM) which simultaneously models the two components that govern time-stamped event formation: 1) the receiver selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
 In what follows, we introduce the HEM by describing how we assume the generatve process of a time-stamped event data (Section \ref{sec:generative process}), and deriving the sampling equations for Bayesian inference (Section \ref{sec:inference}).
@@
 Data generated under the model consists of $D$ unique edges.
-A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of recipients $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
+A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
-While the model can be applied for two type of hyperedges---edges with (1) a single sender and multiple receivers, and (2) multiple senders and a single receiver---here we only present the generative process for those involving a single sender and multiple receivers (i.e., multicast).
-For the latter case of hyperedges, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single recipient.
+While the model can be applied for two type of hyperedges---edges with (1) one sender and one or more receivers, and (2) one receiver and mone or more receivers---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast).
+For the latter case of hyperedges, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single receiver.
+Detailed generative process for directed edges with one receiver and one or more senders are provided in Appendix A.
 
-\subsection{Edge Generating Process}\label{subsec: Tie}
-For every possible author--recipient pair $(a,r)_{a \neq r}$, we define the ``recipient intensity", which is the likelihood of edge $d$ being sent from $a$ to $r$:
+\subsection{Hypothetical Edges}\label{subsec: Tie}
+For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---an approximate inverse logit of the probability that edge $d$ is being sent from the sender $a$ to receiver $r$---as a linear combination of network-based statistics:
 \begin{equation}
@@
 \end{equation}
-where $\boldsymbol{b}$ is $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of network features which vary depending on the hypotheses regarding canonical processes relevant to network theory such as popularity, reciprocity, and transitivity.
-In addition, we include intercept term to account for the average (or baseline) number of recipients.
+where $\boldsymbol{b}$ is a $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of network features which vary depending on the hypotheses regarding canonical processes relevant to network theory such as popularity, reciprocity, and transitivity.
+In addition, we include intercept term to account for the average (or baseline) number of receivers.
 We place a Normal prior $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$.
 
-Next, we hypothesize ``If $a$ were the sender of edge $d$, who would be the recipient(s)?" To do this, we draw each sender's set of recipients from the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model to estimate the structure of graphs with binary nodes---with probability of 1 being logit($\lambda_{adr}$).
-In order to avoid the model degeneracy from having an empty recipient set, we define a probability measure ``MB$_{G}$" motivated by the non-empty Gibbs measure \citep{fellows2017removing} which excludes the all-zero vector from the support of the multivariabe Bernoulli distirbution.
-As a result, we 1) allow multiple recipients or ``multicast", 2) prevent from obtaining zero recipient, and 3) ensure tractable normalizing constant.
+Next, we hypothesize ``If $a$ were the sender of edge $d$, who would be the receivers?" and derive a receiver-selection distribution.
+For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{th}$ row denotes sender $a$'s receiver vector of indicators---i.e., if node $r$ is the hypothetical receiver of sender $a$, then $u_{adr}=1$; otherwise $u_{adr}=0$.
+We then assume that each receiver vector $\boldsymbol{u}_{ad}$ comes from the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model to estimate the structure of graphs with binary nodes---with logit probability of $\boldsymbol{\lambda}_{ad}$.
+In order to avoid the model degeneracy from having an empty receiver set, we define a probability measure ``MB$_{G}$" motivated by the non-empty Gibbs measure \citep{fellows2017removing} which excludes the all-zero vector from the support of the multivariate Bernoulli distirbution.
+As a result, this measure helps us to 1) allow multiple sender--receiver pairs to co-exist, 2) force the sender to select at least one receiver, and 3) ensure tractable normalizing constant.
 To be specific, we draw a binary vector $\boldsymbol{u}_{ad}= (u_{ad1},
@@
 \end{equation}
-where $\boldsymbol{\lambda}_{id}= \{\lambda_{adr}\}_{r=1}^A$. In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ad})$ as
+where $\boldsymbol{\lambda}_{ad}= \{\lambda_{adr}\}_{r=1}^A$. In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ad})$ as
 \begin{equation}
 \begin{aligned}
-&p(\boldsymbol{u}_{ad}|\delta, \boldsymbol{\lambda}_{ad}) = \frac{\exp\Big\{\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0 )\big) + \sum_{r\neq a} \lambda_{adr}u_{adr}\Big\}}{Z(\boldsymbol{\lambda}_{ad})} ,
+&\Pr(\boldsymbol{u}_{ad}|\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0 )\big) + \sum_{r\neq a} \lambda_{adr}u_{adr}\Big) ,
 \end{aligned}
@@
 where $Z(\boldsymbol{\lambda}_{ad})= \prod_{r \neq a} \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
-Again, this is equivalent to assume independent Bernoulli trial on each $u_{adr}$ with probability of 1 being logit($\lambda_{adr}$), excluding the case when all $u_{adr}=0$.
-We provide the derivation of the normalizing constant as a tractable form in Appendix A.
+Again, this is equivalent to assuming independent Bernoulli trial on each $u_{adr}$ with probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
+We provide the derivation of the normalizing constant as a tractable form in Appendix B.
 
-\subsection{Time Generating Process}\label{subsec:Time}
-Similarly, we hypothesize ``If $a$ were the sender of edge $d$, when would it be sent?" and define the ``timing rate" for sender $a$
+\subsection{Hypothetical Timestamps}\label{subsec:Time}
+Similarly, we consider ``If $a$ were the sender of edge $d$, when would it be sent?" and define the ``timing rate" for the sender $a$
 \begin{equation}
@@
 \end{equation}
-where $\boldsymbol{\eta}$ is $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of time-related covariates, e.g., any feature that could affect timestamps of the edge, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
+where $\boldsymbol{\eta}$ is a $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of time-related covariates, e.g., any feature that could affect timestamps of the edge, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
 
-In modeling ``when", we do not directly model the timestamp $t_d$.
-Instead, we assume that each sender's the time-increment or ``time to next interaction" (i.e., $\tau_{d} = t_d-t_{d-1}$) is drawn from a specific distribution in the exponential family.
-We follow the generalized linear model (GLM) framework \citep{nelder1972generalized}:
+In modeling ``when," we do not directly model the timestamp $t_d$.
+Instead, we assume that each sender's ``time increment"---i.e., waiting time to next interaction---is drawn from a specific distribution in the exponential family.
+We define the time increment from edge $d-1$ to edge $d$ as $\tau_{d}$ (i.e., $\tau_{d}= t_d-t_{d-1}$) and specify the distribution of hypothetical timestamps with sender-specfic mean $\mu_{ad}$.
+Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume the mean and variance of the $\tau_{ad}$ satistify
 \begin{equation}
@@
 where $\tau_{ad}$ here is a positive real number.
-Possible choices of distribution include exponential, Weibull, gamma, and lognormal\footnote{lognormal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
-Based on the choice of distribution, we may introduce any additional parameter (e.g., $\sigma_\tau^2$) to account for the variance.
-We use $f_\tau(\cdot; \mu, \sigma_\tau^2)$ and $F_\tau(\cdot; \mu, \sigma_\tau^2)$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $\sigma^2$.
-	\begin{algorithm}[!b]
+Possible choices of distribution include exponential, Weibull, gamma, and log-normal\footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
+Based on the choice of distribution, we may introduce any additional latent variable (e.g., variance parameter $\sigma_\tau^2$ for log-normal and shape parameter $\theta$ for gamma) to account for the variance in time increments.
+We use $f_\tau(\cdot; \mu)$ and $F_\tau(\cdot; \mu)$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$.
+\subsection{Senders, Receivers, and Timestamps}\label{subsec:Observed}
+Finally, we choose the actual sender, receivers, and timestamp by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
+\begin{equation}
+\begin{aligned}
+a_d &= \mbox{argmin}_{a}(\tau_{ad}),\\
+\boldsymbol{r}_d &= \boldsymbol{u}_{a_d d},\\
+t_d &=t_{d-1} + \tau_{a_d d}.
+\end{aligned}
+\end{equation}
+Therefore, it is a sender-driven process in that the receivers and timestamp of an edge is jointly determined by the sender's urgency to send the edge to chosen receivers.
+Note that our generative process accounts for tied events such that in case of tied events (i.e., multiple senders generated exactly same time increments), we observe all of the tied events without assigning the orders of tied events.
+Algorithm \ref{alg:generative} summarizes the entire generative process for directed edges with one sender and one or more receivers, outlined in this section.
+	\begin{algorithm}[!t]
+		\spacingset{1}
 			\SetAlgoLined
-		\caption{Generating Process}
+		\caption{Generative Process: one sender and one or more receivers}
 		\begin{algorithmic}
@@
 			\STATE	draw $\boldsymbol{u}_{ad}  \sim
-				\mbox{Gibbs}(\boldsymbol{\lambda}_{ad})$
+			\mbox{MB}_G(\boldsymbol{\lambda}_{ad})$
 			\STATE		set $\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad})$
-				\STATE		draw $\tau_{ad} \sim f_\tau(\mu_{ad}, \sigma_\tau^2)$
+			\STATE		draw $\tau_{ad} \sim f_\tau(\mu_{ad}, V(\mu_{ad}))$
 			\ENDFOR
-				\STATE	\textbf{For no tied events,}
-				\STATE	set $a_d= \mbox{argmin}_{a}(\tau_{ad})$\
+
+			\IF{$n \geq 2$ tied events} 
+			\STATE	set $a_d, \ldots, a_{d+n-1}= \mbox{argmin}_{a}(\tau_{ad})$
+			\STATE	set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n-1}= ,\boldsymbol{u}_{a_{d+n-1} d}$
+			\STATE	set $t_d, \ldots, t_{d+n-1}=t_{d-1} + \min_a\tau_{ad}$
+			\STATE		jump to $d = d+n$
+				\ELSE
+				\STATE	set $a_d= \mbox{argmin}_{a}(\tau_{ad})$
 				\STATE		set $\boldsymbol{r}_d = \boldsymbol{u}_{a_d d}$
 				\STATE	set $t_d =t_{d-1} + \min_a\tau_{ad}$
-				\STATE	\textbf{For $n$ tied events,} (i.e., $n$ senders generated same minimum time increments)\\
-				\STATE	set $a_d, \ldots, a_{d+n}= \mbox{argmin}_{a}(\tau_{ad})$
-				\STATE	set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n}= ,\boldsymbol{u}_{a_{d+n} d}$
-				\STATE	set $t_d, \ldots, t_{d+n}=t_{d-1} + \min_a\tau_{ad}$
-			\STATE		jump to $d = d+n+1$
+				\ENDIF
 			\ENDFOR
@@
 	\end{algorithm}
-\subsection{Observed Data}\label{subsec:Observed}
-Finally, we choose the sender, recipients, and timestamp---which will be observed---by selecting the sender--recipient-set pair with the smallest time-increment \citep{snijders1996stochastic}:
+\section{Posterior Inference}\label{sec:inference}
+Our inference goal is to invert the generative process to obtain the posterior distribution over the latent variables---hypothetical edges $\{\boldsymbol{u}_d\}_{d=1}^D$, coefficients for edge coavriates $\boldsymbol{b}$, and coefficients for timestamp covariates $\boldsymbol{\eta}$---conditioned on the observed data $\{(a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, covariates $\{(\boldsymbol{x}_d, \boldsymbol{y}_d)\}_{d=1}^D$, and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
+We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each latent variable from its conditional posterior via a Metropolis-within-Gibbs sampling algorithm.
+In this section, we provide each latent variable's conditional posterior, and demonstrate how we perform the prior-posterior simulator test of \cite{geweke2004getting} for the HEM.
+At the end of this section, we provide the pseudocode of our MCMC algorithm in Algorithm \ref{alg:MCMC}.
+
+\subsection{Conditional Posteriors}\label{subsec:conditionaldist}
+\subsubsection{Hypothetical edges}
+In the HEM, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---are not possible.
+However, it is possible to augment the data by hypothetical edges $\boldsymbol{u}$ such that we can obtain their conditional posterior by collapsing the known distributions---$P(\boldsymbol{b}, \boldsymbol{u}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}| \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---through integrating out $\boldsymbol{u}$.
+We adapt this common tool in Bayesian statistics called ``data augmentation" \citep{tanner1987calculation,neal2015exact}.
+Since $u_{adr}$ is a binary random variable, its new value may be sampled directly from a multinomial distribution with probabilities
 \begin{equation}
 \begin{aligned}
-a_d &= \mbox{argmin}_{a}(\tau_{ad}),\\
-\boldsymbol{r}_d &= \boldsymbol{u}_{a_d d},\\
-t_d &=t_{d-1} + \tau_{a_d d}.
-\end{aligned}
-\end{equation}
-Therefore, it is a sender-driven process in that the recipients and timestamp of an edge is determined by the sender's urgency to send the edge to chosen recipients.
-Note that  our generative process accounts for tied events such that in case of tied events (i.e., multiple senders generated exactly same time increments $\tau_d$), we observe all of the tied events without assigning the orders of tied events.
-Algorithm \ref{alg:generative} summarizes the generative process in Section \ref{sec:generative process}.
-\section{Posterior Inference}\label{sec:inference}
-Our inference goal is to invert the generative process to obtain the posterior distribution over the unknown parameters, conditioned on the observed data and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
-We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each parameter from its conditional posterior given the observed data, hyperparamters, and the current values of the other parameters.
-We express each parameter’s conditional posterior in a closed form using the data augmentation schemes in $\boldsymbol{u}$ \citep{tanner1987calculation}.
-In this section, we provide each latent variable's conditional posterior, and demonstrate how we perform the prior-posterior simulator test of \cite{geweke2004getting} for the HEM.
-
-\subsection{Full Conditional Distributions}\label{subsec:conditionaldist}
-First, since $u_{adr}$ is a binary random variable, new values may be sampled directly using
-\begin{equation}
-\begin{aligned}
-&P(u_{adr}=1| \boldsymbol{u}_{ad\backslash r}, \boldsymbol{b}, \boldsymbol{x})
+&\Pr(u_{adr}=1| \boldsymbol{u}_{ad\backslash r}, \boldsymbol{b}, \boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})
 \propto \mbox{exp}(\lambda_{adr});\\
-&P(u_{adr}=0| \boldsymbol{u}_{ad\backslash r},\boldsymbol{b}, \boldsymbol{x})\propto \text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 ),
+&\Pr(u_{adr}=0| \boldsymbol{u}_{ad\backslash r},\boldsymbol{b}, \boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 ),
 \end{aligned}
@@
 \end{equation}
-where $I(\cdot)$ is the indicator function that is used to prevent from the instances where a sender chooses zero number of recipients.
-
-New values for continuous variables $\boldsymbol{b},$ and $\boldsymbol{\eta}$ and $\sigma^2_\tau$ (if applicable) cannot be sampled directly from their conditional posteriors, but may instead be obtained using the Metropolis--Hastings algorithm.
-With uninformative priors (i.e., $N({0},\infty)$), the conditional posterior over $\boldsymbol{b}$ is
+where $I(\cdot)$ is the indicator function that is used to prevent from the instances where a sender chooses zero number of receivers. 
+\subsubsection{Coefficients for edge covariates}
+Unlike hypothetical edges above, new values for $\boldsymbol{b}$ cannot be sampled directly from its conditional posterior, but may instead be obtained using the Metropolis--Hastings algorithm.
+Assuming an uninformative prior (i.e., $N({0},\infty)$), the conditional posterior over $\boldsymbol{b}$ is
 \begin{equation}
-P(\boldsymbol{b}| \boldsymbol{u}, \boldsymbol{x})\propto \prod_{d=1}^D
-\prod_{a=1}^A \frac{\exp\Big\{\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0)\big) + \sum\limits_{r \neq a} \lambda_{adr}u_{adr}\Big\}}{Z(\boldsymbol{\lambda}_{ad})},
+\Pr(\boldsymbol{b}| \boldsymbol{u}, \boldsymbol{x}, \boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D
+\prod_{a=1}^A \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0)\big) + \sum\limits_{r \neq a} \lambda_{adr}u_{adr}\Big).
 \end{equation}
-where the two variables share the conditional posterior and thus can be jointly sampled.
-Likewise, assuming uninformative priors on $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$) and $\sigma_{\tau}^2$ (i.e., half-Cauchy($\infty$)), the conditional posterior for no-tied event case is
+\subsubsection{Coefficients for timestamp covariates}
+Likewise, we use Metropolis-Hastings algorithm to update the latent variable $\boldsymbol{\eta}$.
+Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for no-tied event case is
 \begin{equation}
-P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)\Big),
+\Pr(\boldsymbol{\eta}| \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
+\label{eqn:latenttime}
 \end{equation}
-where $f_{\tau}(\tau_{d}; \mu_{a_d d}, \sigma_\tau^2)$ is the probability that the $d^{th}$ observed time-increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean parameter, and $\prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)$ is the probability that the latent (or unobserved) senders for event $d$ all generated time-increments greater than $\tau_d$.
-Moreover, under the existence of tied-event, the conditional posterior of $\boldsymbol{\eta}$ and $\sigma_{\tau}^2$ should be written as
+where $f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))$ is the probability that the $d^{th}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{a_d d}$, and $\prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d},V(\mu_{a_d d})) \big)$ is the probability that the rest of (unobserved) senders for event $d$ all generated time increments greater than $\tau_d$.
+Moreover, under the existence of tied-event, the conditional posterior of $\boldsymbol{\eta}$ is written as
 \begin{equation}
 \begin{aligned}
-&P(\boldsymbol{\eta}, \sigma_\tau^2| \boldsymbol{u}, \boldsymbol{y})\\&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, \sigma_\tau^2) \times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, \sigma_\tau^2) \big)\Big),
+\Pr(\boldsymbol{\eta}| \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, V(\mu_{a_d d})) \\&\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
 \end{aligned}
+\label{eqn:latenttime2}
 \end{equation}
 where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $D$ events ($M \leq D$).
-If $M=D$ (i.e., no tied events), equation (3.4) reduces to equation (3.3).
-Algorithm \ref{alg:MCMC} provides the pseudocode.
-\begin{algorithm}[!b]
+If $M=D$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
+Note that when we have the latent variable to quantify the variance in time increments (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case of tied events) for the additional Metropolis-Hastings update---e.g., $\Pr(\sigma^2_\tau| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution and $\Pr(\theta| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma distribution.
+\begin{algorithm}[!t]
 	\spacingset{1}
@@
 	\begin{algorithmic}
-	\STATE set initial values of $\boldsymbol{b}, \boldsymbol{\eta}$, (and $\sigma_\tau^2$)\\
+	\STATE set initial values of $\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta}$
 	\FOR{o=1 to outer}
@@
    \begin{itemize}
-   	\item[1.] Mean of observed recipient sizes $ \lVert \boldsymbol{r}_{d} \rVert_1 $ across $d=1,\ldots,D$,
-   	\item[2.] Mean of time-increments $\tau_d$ across $d=1,...,D$,
+   	\item[1.] Mean of observed receiver sizes $ \lVert \boldsymbol{r}_{d} \rVert_1 $ across $d=1,\ldots,D$,
+   	\item[2.] Mean of time increments $\tau_d$ across $d=1,...,D$,
    	\item[3.] $b_p$ value used to generate the samples $p = 1,...,P$,
@@
 
-   To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using lognormal distibution for the time distribution $f$.
+   To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using log-normal distibution for the time distribution $f$.
 We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
@@
    \end{figure}
- 	   \section{Application to Montgomary County Emails}\label{subsec:Emails}
+ 	   \section{Application to Email Data}\label{subsec:Emails}
  	   We now present a case study applying our method to Montgomery county government email data.
@@
 The statistics ``outdegree" and ``indegree" measures the gregariousness and popularity effect of the node by counting the number of emails sent from $a$ and received by $r$, respectively, within the last 7 days.
-Moreover, in order to capture individual tendency of writing multicast emails, we include the statistic ``hyperedge size"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of recipients are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
+Moreover, in order to capture individual tendency of writing multicast emails, we include the statistic ``hyperedge size"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of receivers are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
 Dyadic statistics ``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
@@
  	   \end{itemize}
- 	   Note that our time generating process in Section \ref{subsec:Time} is sender-orientd process where the sender deterimes ``when to send the email," thus we incorporate network statistics that depends on $a$ only---outdegree of sender $a$ and indegree of sender $a$ (not $r$ this time).
+ 	   Note that our generative process for timestamps in Section \ref{subsec:Time} is sender-orientd process where the sender deterimes ``when to send the email," thus we incorporate network statistics that depends on $a$ only---outdegree of sender $a$ and indegree of sender $a$ (not $r$ this time).
 
-	\subsection{Prediction Experiments}\label{subsec:Experiment_email}
+	\subsection{Model Selection}\label{subsec:Experiment_email}
 
-	The HEM has many component parts that need to be specified by the user (i.e., the selection of the event timing features $\boldsymbol{y}$, the recipient selection features $\boldsymbol{x}$, and the event time distribution $f$).
-Many of these components will be specified based on user expertise (e.g., regarding which features would drive recipient selection), but some decisions may require a data-driven approach to model specification.
+	The HEM has many component parts that need to be specified by the user (i.e., the selection of the event timing features $\boldsymbol{y}$, the receiver selection features $\boldsymbol{x}$, and the event time distribution $f$).
+Many of these components will be specified based on user expertise (e.g., regarding which features would drive receiver selection), but some decisions may require a data-driven approach to model specification.
 For example, though theoretical considerations may inform the specification of features, subject-matter expertise is unlikely to inform the decision regarding the family of the event time distribution.
@@
 We illustrate this approach by comparing alternative distributional families for the event timing component of the model.
-Here, we specifically compare the predictive performance from two distributions---lognormal and exponential.
-We particularly choose exponential distribution as an alternative to what we used earlier (i.e., lognormal) since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
+Here, we specifically compare the predictive performance from two distributions---log-normal and exponential.
+We particularly choose exponential distribution as an alternative to what we used earlier (i.e., log-normal) since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
 	\begin{algorithm}[!t]
@@
 			\textbf{Test splits:}	
-			\STATE draw test authors with $p=0.1$ (out of $D$ authors) 
-			\STATE draw test recipients
-			with $p=0.1$ (out of $D\times (A-1)$ recipient indicators $\{\{\boldsymbol{r}_{dr}\}_{r\in [A]_{\backslash a_d}}\}_{d=1}^D$)
+			\STATE draw test senders with $p=0.1$ (out of $D$ senders) 
+			\STATE draw test receivers
+			with $p=0.1$ (out of $D\times (A-1)$ receiver indicators $\{\{\boldsymbol{r}_{dr}\}_{r\in [A]_{\backslash a_d}}\}_{d=1}^D$)
 			\STATE draw test timestamps with $p=0.1$  (out of $D$ timestamps) 
@@
 			\textbf{Imputation and inference:}	
-			\STATE initialize the parameters $(\boldsymbol{b}, \boldsymbol{\eta}, \boldsymbol{u}, \sigma^2_\tau)$
+			\STATE initialize the latent variables $(\boldsymbol{b}, \boldsymbol{\eta}, \boldsymbol{u}, \sigma^2_\tau)$
 			\FOR{$r=1$ {\bfseries to}  $R$}
@@
 	We evaluate the model's ability to predict edges and timestamps from the Montgomery County email data, conditioned on their ``training" part of the data.
-To perform the experiment, we separately formed a test split of each three components---sender, recipients, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
-Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, parameter estimates, and current values of test data.
+To perform the experiment, we separately formed a test split of each three components---sender, receivers, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
+Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, model estimates, and current values of test data.
 We then run inference to update the latent variables given the imputed and observed data.
@@
 We run the experiment and measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
-We compare the predictions in terms of classification accuracy in predicting the authors and recipients, as well as prediction error in the timestamps.
+We compare the predictions in terms of classification accuracy in predicting the senders and receivers, as well as prediction error in the timestamps.
 First, we compare the posterior probability of correct senders from missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
-We call this measure as ``correct sender posterior probability." The plot on the left demonstrates that both lognormal and exponential distributions acheive better predictive performance for senders compared to what is expected under random guess (dotted blue line at $1/18$), with lognormal distribution showing slightly higher performance than exponential distribution on average.
-Secondly, since the recipient vector is binary---$r_{dr}=1$ if received or $r_{dr}=0$ otherwise---we compute $F_1$ scores for recipient predictions, comparing the true recipient vector $\boldsymbol{r}^{obs}_{dr}$ and predicted recipient vectors $\boldsymbol{r}^{pred}_{dr}$ for missing recipient indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA).
-Although the edge generating process (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there exists noticeable difference between lognormal and exponential in their performance of predicting unknown recipients.
-Similar to the sender prediction, lognormal outperforms exponential in general.
+We call this measure as ``correct sender posterior probability." The plot on the left demonstrates that both log-normal and exponential distributions acheive better predictive performance for senders compared to what is expected under random guess (dotted blue line at $1/18$), with log-normal distribution showing slightly higher performance than exponential distribution on average.
+Secondly, since the receiver vector is binary---$r_{dr}=1$ if received or $r_{dr}=0$ otherwise---we compute $F_1$ scores for receiver predictions, comparing the true receiver vector $\boldsymbol{r}^{obs}_{dr}$ and predicted receiver vectors $\boldsymbol{r}^{pred}_{dr}$ for missing receiver indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA).
+Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there exists noticeable difference between log-normal and exponential in their performance of predicting unknown receivers.
+Similar to the sender prediction, log-normal outperforms exponential in general.
 Finally, prediction errors for missing timestamps are measured using the median absolute percentage error (MdAPE) \citep{hyndman2006another}, where we take the median of absolute percentage errors $p_{di}$ for $i=1,\ldots,500$ for $d$th document, calculated as follows:
@@
 		\includegraphics[width=1\textwidth]{img/PPEplotnew-1.png}	
-		\caption {Comparison of predictive performance between lognormal and exponential distributions: boxplots for correct sender posterior probability (\textit{left}), distribution of correct recipient posterior probability in log-scale (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).
+		\caption {Comparison of predictive performance between log-normal and exponential distributions: boxplots for correct sender posterior probability (\textit{left}), distribution of correct receiver posterior probability in log-scale (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).
 The dotted blue lines in the left plot represents the correct sender probability expected by random guess---i.e., $1/A=1/18\approx0.056$.}
@@
 For better visualization, we plot MdAPE estimates in log-scale since they are highly right-skewed.
-As expected, we have huge benefit in the performance of timestamp prediction when we choose lognormal distribution over exponential.
-This difference can be explained by our variance estimate $\hat{\sigma}_\tau^2= 14.093$ in Section \ref{subsec:Result_email}, because exponential distribution omits the extra information on time-increments contained in the large variance estimate.
-As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing information of the emails?" and 2) offer one standard way to determine the time-increment distribution in Section \ref{subsec:Time}.
+As expected, we have huge benefit in the performance of timestamp prediction when we choose log-normal distribution over exponential.
+This difference can be explained by our variance estimate $\hat{\sigma}_\tau^2= 14.093$ in Section \ref{subsec:Result_email}, because exponential distribution omits the extra information on time increments contained in the large variance estimate.
+As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing information of the emails?" and 2) offer one standard way to determine the time increment distribution in Section \ref{subsec:Time}.
 
@@
 	We perform posterior predictive checks \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data.
-We formally generated entirely new data, by simulating time-stamped events $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred parameter values from the inference in Section \ref{subsec:Result_email}.
-For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data: outdegree distribution, indegree distribution, recipient size distribution, and time-increments probability-probability (PP) plot.
+We formally generated entirely new data, by simulating time-stamped events $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}.
+For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data: outdegree distribution, indegree distribution, receiver size distribution, and time increments probability-probability (PP) plot.
 We then generated 500 synthetic networks from the posterior predictive distribution, according to Algorithm \ref{alg:PPC}.
@@
 		\includegraphics[width=0.31\textwidth]{img/timeppnew.pdf}
-		\caption {PPC results from lognormal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
+		\caption {PPC results from log-normal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and time increments probability-probability (PP) plot  (\textit{lower right}).
 Red lines in the first three plot depict the observed statistics, and the red line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
@@
 
-	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using lognormal distribution.
+	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using log-normal distribution.
 Upper two plots show node-specific degree distributions, where the left one is the boxplots of 500 posterior predictive outdegree statistic and the right plot is the same one for indegree statistic.
@@
 Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
-Since we use more information in the recipient selection process (i.e., network effects) while we only rely on minimum time-increments when choosing the observed sender, these results are expected.
-Lower left plot is the distribution of recipient sizes, where the x-axis spans over the size of recipients 1 to 14 (which is the maximum size of observed recipients) and the y-axis denotes the number of documents with x-number of recipients.
-The result shows that our model is underestimating single-receiver documents while overestimating documents with two, three, and four recipients.
-One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the documents with $\geq 10$ number of recipients, so that the intercept estimate $b_1$ is slightly moved toward right.
-To improve the goodness of fit for recipient sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
-In the end, the plot on the lower right is the PP plot for time-increments, which is a graphical measure commonly used for assessing how closely two data sets agree, by plotting the two cumulative distribution functions against each other.
-The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time-increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
-All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC results from exponential distribution, and the plots comparing posterior checks between lognormal and exponential distributions are attached in Appendix B.
+Since we use more information in the receiver selection process (i.e., network effects) while we only rely on minimum time increments when choosing the observed sender, these results are expected.
+Lower left plot is the distribution of receiver sizes, where the x-axis spans over the size of receivers 1 to 14 (which is the maximum size of observed receivers) and the y-axis denotes the number of documents with x-number of receivers.
+The result shows that our model is underestimating single-receiver documents while overestimating documents with two, three, and four receivers.
+One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the documents with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right.
+To improve the goodness of fit for receiver sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
+In the end, the plot on the lower right is the PP plot for time increments, which is a graphical measure commonly used for assessing how closely two data sets agree, by plotting the two cumulative distribution functions against each other.
+The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
+All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC results from exponential distribution, and the plots comparing posterior checks between log-normal and exponential distributions are attached in Appendix \ref{subsec: PPCexp}.
 
-	\subsection{Parameter Estimates and Interpretation}\label{subsec:Result_email}
-	Based on some preliminary experiments, we choose lognormal distribution to model time-to-next-email in Montgomery county email data, thus we estimate the variance parameter $\sigma_\tau^2$ with the prior specified as inverse-Gamma($2, 1$).
+	\subsection{Exploratory Analysis}\label{subsec:Result_email}
+	Based on some preliminary experiments, we choose log-normal distribution to model time-to-next-email in Montgomery county email data, thus we estimate the variance $\sigma_\tau^2$ with the prior specified as inverse-Gamma($2, 1$).
 In this section, we present the results based on 55,000 MCMC outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
 While the inner iterations for  $\sigma_\tau^2$ is fixed as 1, we use 10 and 20 inner iterations for $\boldsymbol{\eta}$ and $\boldsymbol{b}$, respectively, to adjust for its slower convergence rate.
-Convergence diagnostics for MCMC including some traceplots and Geweke diagnostics \citep{geweke1991evaluating} can be found in Appendix C.
+Convergence diagnostics for MCMC including some traceplots and Geweke diagnostics \citep{geweke1991evaluating} can be found in Appendix \ref{subsec: convergence}.
 	\begin{figure}[!t]
@@
 	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$.
-Since we use logit probability of $\lambda_{adr}$ for edge generating process (Section \ref{subsec: Tie}), we have
+Since we use logit probability of $\lambda_{adr}$ for generative process for edges (Section \ref{subsec: Tie}), we have
 	\begin{equation*}
@@
 	\end{equation*}
-	and can interpret the parameter estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11})$.
+	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11})$.
 	Firstly, we can see that the effect of send (i.e., ``number of times the actor $a$ sent emails to the actor $r$ over the last week'') is positive, implying that if the actor $a$ sent $n$ number of emails to $r$ last week, then the actor $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
@@
 Rest of statistics are not statistically significant because their 95\% credible interval do not include 0.
-Surprisingly, none of the triadic effects seem to have significant effect on the edge generating process.
+Surprisingly, none of the triadic effects seem to have significant effect on the generative process of edges.
 
 	Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of the time-related coefficients $\boldsymbol{\eta}$.
-For this specific datset, we assume lognormal distribution (Section \ref{subsec:Time}) with the unit of time being an hour, so that the interpretation of $\hat{\boldsymbol{\eta}}$ should be based on
+For this specific datset, we assume log-normal distribution (Section \ref{subsec:Time}) with the unit of time being an hour, so that the interpretation of $\hat{\boldsymbol{\eta}}$ should be based on
 	\begin{equation*}
@@
 Gender of the department manager is shown to have no significant effect on time-to-next-email.
-The posterior mean estimate of the variance parameter $\sigma^2_\tau$ is 14.093 with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time-increments in this data.
+The posterior mean estimate of the variance parameter $\sigma^2_\tau$ is 14.093 with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time increments in this data.
 		\begin{figure}[!t]
@@
 \section{Conclusion}\label{sec:conclusion}
-Motivated by the relational event model \citep{Butts2008} and its variants for time-stamped networks, the hyperedge event model (HEM) can effectively learn the underlying edge generating and timestamp generating structures of event data, while allowing flexibity in the covariate specifications and the distributional assumption of time-increments.
+Motivated by the relational event model \citep{Butts2008} and its variants for time-stamped networks, the hyperedge event model (HEM) can effectively learn the underlying edge generating and timestamp generating structures of event data, while allowing flexibity in the covariate specifications and the distributional assumption of time increments.
 Accounting for the hyperedges, we make better use of events with hyperedges than modeling them as duplicate edges.
@@
 We have demonstrated effectiveness of our model by analyzing Montgomery County government emails, which includes numerous hyperedges.
-The estimated covariate effects reveal that the HEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), while the model additionally allows separate covariates and the corresponding parameters for edge and timestamp generating processes.
+The estimated covariate effects reveal that the HEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), while the model additionally allows separate covariates and the corresponding parameters for generative processes of edges and timestamps.
 Although we illustrate the entire framework and application in the context
-of one type of hyperedges, a single sender and multiple recipients, our model can be easily extended to allow the opposite case, a single recipient and multiple senders, by slight modification of the generating process.
+of one type of hyperedges, a single sender and multiple receivers, our model can be easily extended to allow the opposite case, a single receiver and multiple senders, by slight modification of the generative process.
 This extension involves promissing applications including international sanctions and co-sponsorship of bills.
@@
 \section*{Appendix}
-	\subsection*{Appendix A: Normalizing Constant of MB$_{G}$}\label{subsec: non-empty Gibbs measure}
-	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure \citep{fellows2017removing}---defines the probability of author $a$ selecting the binary recipient vector $\boldsymbol{u}_{ad}$ as
+	\subsection*{Appendix A: Alternative Generative Process} \label{appendix:alternativeGP}
+		\begin{algorithm}[!ht]
+			\SetAlgoLined
+			\caption{Generative Process: one receiver and one or more senders}
+			\begin{algorithmic}
+				\FOR{d=1 to D}
+				\FOR{r=1 to $A$}
+				\FOR{a=1 to $A$ (a $\neq$ r)}
+				\STATE	set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
+				\ENDFOR
+				\STATE	draw $\boldsymbol{u}_{rd}  \sim
+				\mbox{MB}_G(\boldsymbol{\lambda}_{rd})$
+				\STATE		set $\mu_{rd} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{rd})$
+				\STATE		draw $\tau_{rd} \sim f_\tau(\mu_{rd}, \sigma_\tau^2)$
+				\ENDFOR
+				\IF {$n \geq 2$ tied events} 
+				\STATE	set ${r}_d=\mbox{argmin}_{r}(\tau_{rd})$
+				\STATE	set $\boldsymbol{a}_d=\boldsymbol{u}_{r_d d},\ldots,\boldsymbol{a}_{d+n-1}= ,\boldsymbol{u}_{r_{d+n-1} d}$
+				\STATE	set $t_d, \ldots, t_{d+n-1}=t_{d-1} + \min_r\tau_{rd}$
+				\STATE		jump to $d = d+n$
+				\ELSE
+				\STATE	set ${r}_d = \mbox{argmin}_{r}(\tau_{rd}) $
+				\STATE	set $\boldsymbol{a}_d= \boldsymbol{u}_{r_d d}$
+				\STATE	set $t_d =t_{d-1} + \min_r\tau_{rd}$
+				\ENDIF
+				\ENDFOR
+			\end{algorithmic}
+			\label{alg:generative2}
+		\end{algorithm}
+	\subsection*{Appendix B: Normalizing Constant of MB$_{G}$}\label{appendix: non-empty Gibbs measure}
+	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure---defines the probability of sender $a$ selecting the binary receiver vector $\boldsymbol{u}_{ad}$ as
 	\begin{equation*} 
 	\begin{aligned}
-	& P(\boldsymbol{u}_{ad}|\boldsymbol{\lambda}_{ad} ) = \frac{\exp\Big\{ \mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big\}}{Z(\boldsymbol{\lambda}_{ad})}.
+	& \Pr(\boldsymbol{u}_{ad}|\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big),
 	\end{aligned}
 	\end{equation*}
+	where $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$ as defined in Secton \ref{subsec: Tie}.
 
-	To use this distribution efficiently, we derive a closed-form expression for $Z(\boldsymbol{\lambda}_{id})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (\textit{i.e.} $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
-We recognize that if $\boldsymbol{u}_{ad}$ were drawn via independent Bernoulli distributions in which $P({u}_{adr}=1|\delta, \boldsymbol{\lambda}_{ad})$ was given by logit$(\lambda_{adr})$, then
+	To use this distribution efficiently, we derive a closed-form expression for $Z(\boldsymbol{\lambda}_{ad})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (\textit{i.e.} $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
+We recognize that if $\boldsymbol{u}_{ad}$ were drawn via independent Bernoulli distributions in which $\Pr({u}_{adr}=1|\boldsymbol{b}, \boldsymbol{x}_{ad})$ was given by logit$(\lambda_{adr})$, then
 	\begin{equation*}
-	P(\boldsymbol{u}_{ad}|\boldsymbol{\lambda}_{ad}) \propto \exp\Big\{\sum_{r \neq a } \lambda_{adr}u_{adr}\Big\}.  	 
+	\Pr(\boldsymbol{u}_{ad}|\boldsymbol{b}, \boldsymbol{x}_{ad}) \propto \exp\Big(\sum_{r \neq a } \lambda_{adr}u_{adr}\Big).  	 
 	\end{equation*}
@@
 	\begin{aligned}
-	&P(u_{adr}=1|\boldsymbol{u}_{ad[-r]}, \boldsymbol{\lambda}_{ad})
-	=\frac{ \exp{(\lambda_{adr})}}{\exp{(\lambda_{adr})} + 1}.\end{aligned}\end{equation*}
+	&\Pr(u_{adr}=1|\boldsymbol{u}_{ad[-r]}, \boldsymbol{b}, \boldsymbol{x}_{ad})
+	=\frac{\exp{(\lambda_{adr})}}{\exp{(\lambda_{adr})} + 1}.
+	\end{aligned}\end{equation*}
 	We denote the logistic-Bernoulli normalizing constant as $Z^{l}(\boldsymbol{\lambda}_{ad})$, which is defined as 
 	\begin{equation*}
-	Z^{l}(\delta,\boldsymbol{\lambda}_{ad})=\sum_{\boldsymbol{u}_{ad} \in [0,1]^{A}} \exp\Big\{\sum_{r\neq a} \lambda_{adr}u_{adr}\Big\}.
+	Z^{l}( \boldsymbol{\lambda}_{ad})=\sum_{\boldsymbol{u}_{ad} \in [0,1]^{A}} \exp\Big(\sum_{r\neq a} \lambda_{adr}u_{adr}\Big).
 	\end{equation*}
@@
 	\begin{aligned}
-	&\exp\Big\{ \mbox{log}\Big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\Big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big\}\\&= \exp\Big\{  \sum_{r \neq a} \lambda_{adr}u_{adr} \Big\},
+	&\exp\Big(\mbox{log}\Big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\Big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big)= \exp\Big( \sum_{r \neq a} \lambda_{adr}u_{adr} \Big),
 	\end{aligned}
@@
 	\begin{aligned}
-	Z(\boldsymbol{\lambda}_{ad})& = Z^{l}(\boldsymbol{\lambda}_{ad}) -\exp\Big\{ \sum\limits_{\forall u_{adr}=0}\lambda_{adr}u_{adr} \Big\}
-	\\& = Z^{l}(\lambda_{a}^{(d)}) -  1.
+	Z(\boldsymbol{\lambda}_{ad})& = Z^{l}(\boldsymbol{\lambda}_{ad}) -\exp\Big( \sum\limits_{\forall u_{adr}=0}\lambda_{adr}u_{adr} \Big)
+	\\& = Z^{l}(\boldsymbol{\lambda}_{ad}) -  1.
 	\end{aligned}
 	\end{equation*}
-	We can therefore derive a closed form expression for $Z(\delta,\boldsymbol{\lambda}_{ad})$ via a closed form expression for $Z^{l}(\delta,\boldsymbol{\lambda}_{ad})$.
+	We can therefore derive a closed form expression for $Z(\boldsymbol{\lambda}_{ad})$ via a closed form expression for $Z^{l}(\boldsymbol{\lambda}_{ad})$.
 This can be done by looking at the probability of the zero vector under the logistic-Bernoulli model:
@@
 	\begin{aligned}
-	&\frac{\exp\Big\{ \sum\limits_{\forall u_{adr}=0}\lambda_{adr}u_{adr} \Big\}}{Z^{l}(\boldsymbol{\lambda}_{ad})}= \prod_{r \neq a}   \Big(1-\frac{ \exp{(\lambda_{adr})}}{\exp{(\lambda_{adr})} + 1}\Big).
+	&\frac{1}{Z^{l}(\boldsymbol{\lambda}_{ad})}\exp\Big(\sum\limits_{\forall u_{adr}=0}\lambda_{adr}u_{adr} \Big)= \prod_{r \neq a}   \Big(1-\frac{ \exp{(\lambda_{adr})}}{\exp{(\lambda_{adr})} + 1}\Big).
 	\end{aligned}  
@@
 	\newpage
-	\subsection*{Appendix B: Comparison of PPC Results: lognormal vs. exponential}\label{subsec: PPCexp}
+	\subsection*{Appendix C: Comparison of PPC Results: log-normal vs. exponential}\label{appendix: PPCexp}
 	\iffalse
@@
 		\includegraphics[width=0.31\textwidth]{img/timedist_exp-1.png}
-		\caption {PPC results from exponential distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
+		\caption {PPC results from exponential distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and time increments probability-probability (PP) plot  (\textit{lower right}).
 Red lines in the first three plot depict the observed statistics, and the red line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
@@
 			\includegraphics[width=0.31\textwidth]{img/timepp_two-1.png}
-			\caption {Comparison of PPC results between lognormal (\textit{red}) and exponential (\textit{green}) distributions: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), recipient size distribution (\textit{lower left}), and time-increments probability-probability (PP) plot  (\textit{lower right}).
+			\caption {Comparison of PPC results between log-normal (\textit{red}) and exponential (\textit{green}) distributions: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and time increments probability-probability (PP) plot  (\textit{lower right}).
 Red lines in the first three plot depict the observed statistics, and the black line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
@@
 		\newpage
-	\subsection*{Appendix C: Convergence Diagnostics}\label{subsec: convergence}
+	\subsection*{Appendix D: Convergence Diagnostics}\label{appendix: convergence}
 	\begin{figure}[H]
@@
 		\includegraphics[width=0.44\textwidth]{img/etageweke.pdf}
-		\caption {Convergence diagnostics from lognormal distribution: traceplots and density plots for $\boldsymbol{b}$ chains (\textit{upper left}) and $\boldsymbol{\eta}$ chains (\textit{upper right}), and geweke diagnostics for $\boldsymbol{b}$ chains (\textit{lower left}) and $\boldsymbol{\eta}$ chains (\textit{lower right}).}
+		\caption {Convergence diagnostics from log-normal distribution: traceplots and density plots for $\boldsymbol{b}$ chains (\textit{upper left}) and $\boldsymbol{\eta}$ chains (\textit{upper right}), and geweke diagnostics for $\boldsymbol{b}$ chains (\textit{lower left}) and $\boldsymbol{\eta}$ chains (\textit{lower right}).}
 		\label{figure:convergencediag}

### 2018-05-24 code/Montgomery_processing2.R

@@ -46,7 +46,7 @@ sendraw = function(data, a, r) {
 # construct recipient covariates X
 D = length(edge)
 A = length(Montgomery$manager_gender)
-P = 10
+P = 14
 X = array(0, dim = c(D,A,A,P))
 X[,,,1] = 1
 timeunit = 3600
@@ -58,7 +58,8 @@ for (d in 2:D) {
 	outdegree = tabulate(sent, A)
 	indegree = colSums(received)
 	for (a in 1:A) {
-		for (r in c(1:A)[-a]) {
+		for (r in c(1:A)) {
+		  if (r != a) {
 			X[d, a, r, 2] = outdegree[a]  
 			X[d, a, r, 3] = indegree[r]	
 			X[d, a, r, 4] = sendraw(data, a, r)
@@ -75,8 +76,13 @@ for (d in 2:D) {
 			X[d, a, r, 9] = sum(sapply(c(1:A)[-c(a,r)], function(h) {
 				sendraw(data, a, h) * sendraw(data, r, h)
 				}))	/10	
+		  }
+		    X[d, a, , 12] = 1* (Montgomery$manager_gender[a]=="Female")
+			  X[d, a, r, 13] =1* (Montgomery$manager_gender[r]=="Female")
+			  X[d, a, r, 14] =1* (Montgomery$manager_gender[a]==Montgomery$manager_gender[r])
 		}
 	  X[d, a, , 10] = ifelse(outdegree[a] <sum(X[d,a,,4]),sum(X[d,a,,4])/outdegree[a] , 1)
+	  X[d, a, , 11] = X[d, a, , 2] * X[d, a, , 10] / 10
 	}
 }
 
@@ -88,11 +94,25 @@ trim = which(email$timepoints >=7*24*timeunit+email$timepoints[1])
 edge = edge[trim]
 X = X[trim,,,]
 Y = Y[trim,,]
-Montgomery_infer = Inference(edge, X, Y, 55000, c(10,1,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
-		  proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "lognormal")
-save(Montgomery_infer, file = "Montgomery_infer.RData")
+Montgomery_infer = Inference(edge, X, Y, 55000, c(20,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
[…]

### 2018-05-24 paper/ba-HEM/ba-sample.tex
revisions until PPC

@@
 \author{\fnms{Aaron} \snm{Schein}\thanksref{addr2,t3,m1,m2}\ead[label=e2]{aschein@cs.umass.edu}},
-\author{\fnms{Bruce} \snm{Desmarais}\thanksref{addr3,t3,m1,m2}\ead[label=e3]{bdesmarais@psu.edu}},
+\author{\fnms{Bruce} \snm{A. Desmarais}\thanksref{addr3,t3,m1,m2}\ead[label=e3]{bdesmarais@psu.edu}},
 \and
@@
 \end{equation}
-where $\boldsymbol{b}$ is a $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of network features which vary depending on the hypotheses regarding canonical processes relevant to network theory such as popularity, reciprocity, and transitivity.
+where $\boldsymbol{b}$ is a $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of receiver selection features which vary depending on the hypotheses regarding canonical processes relevant to network theory such as popularity, reciprocity, and transitivity.
 In addition, we include intercept term to account for the average (or baseline) number of receivers.
@@
 \end{equation}
-where $\boldsymbol{\eta}$ is a $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of time-related covariates, e.g., any feature that could affect timestamps of the edge, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
+where $\boldsymbol{\eta}$ is a $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features, e.g., any covariates that could affect timestamps of the edge, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
 
@@
 		\begin{algorithmic}
+				\STATE \textbf{Input}: number of edges and nodes $(D, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and the coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
+				\vskip 0.1in
 			\FOR{d=1 to D}
@@
 \prod_{a=1}^A \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0)\big) + \sum\limits_{r \neq a} \lambda_{adr}u_{adr}\Big).
+\label{eqn:latentedge}
 \end{equation}
@@
 If $M=D$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
-Note that when we have the latent variable to quantify the variance in time increments (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case of tied events) for the additional Metropolis-Hastings update---e.g., $\Pr(\sigma^2_\tau| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution and $\Pr(\theta| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma distribution.
+Note that when we have the latent variable to quantify the variance in time increments $V(\cdot)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional Metropolis-Hastings update---e.g., $\Pr(\sigma^2_\tau| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution and $\Pr(\theta| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma distribution.
 \begin{algorithm}[!t]
@@
 	\begin{algorithmic}
-	\STATE set initial values of $\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta}$
-	\FOR{o=1 to outer}
+	\STATE \textbf{Input}: number of outer and inner iterations $(O, I_1, I_2)$ and initial values of $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta})$
+				\vskip 0.1in
+	\FOR{o=1 to O}
 		\FOR{d=1 to D}
@@
 			\FOR{r = 1 to A (r $\neq$ a)}
-					\STATE update $u_{adr}$ using Gibbs update --- equation (7)
+					\STATE update $u_{adr}$ using Gibbs update --- equation (\ref{eqn:latentreceiver})
 			\ENDFOR
@@
 		\ENDFOR
-		\FOR{n=1 to inner1}
-			\STATE update $\boldsymbol{b}$ using Metropolis-Hastings --- equation (8)
+		\FOR{n=1 to $I_1$}
+			\STATE update $\boldsymbol{b}$ using Metropolis-Hastings --- equation (\ref{eqn:latentedge})
 		\ENDFOR
-	\FOR{n=1 to inner2}
-			\STATE update $\boldsymbol{\eta}$ using Metropolis-Hastings --- equation (10)
-			\STATE (if needed) update $\sigma_\tau^2$ using Metropolis-Hastings --- equation (10)
+	\FOR{n=1 to $I_2$}
+			\STATE update $\boldsymbol{\eta}$ using Metropolis-Hastings --- equation (\ref{eqn:latenttime}) or equation (\ref{eqn:latenttime2}) 
+			\STATE (if needed) update the latent variable for $V(\cdot)$ using Metropolis-Hastings --- equation (\ref{eqn:latenttime}) or equation (\ref{eqn:latenttime2}) 
 		\ENDFOR
@@
 	\ENDFOR
-	\STATE	Summarize the results with: last chain of $\boldsymbol{b}$, and last chain of $\boldsymbol{\eta}$ (and $\sigma_\tau^2$) 
+	\STATE	summarize the results with the last chain of $\boldsymbol{b}$ and $\boldsymbol{\eta}$
 \end{algorithmic}
@@
    	\item[4.] $\eta_q$ value used to generate the samples $q = 1,...,Q$,
-   	\item[5.] $\sigma^2_\tau$ value used to generate the samples
+   	\item[5.] $\sigma^2_\tau$ value used to generate the samples in log-normal distribution
    \end{itemize}
 
-   To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using log-normal distibution for the time distribution $f$.
+   To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using log-normal distibution for the time increments $f_\tau$.
 We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
@@
 We depict the GiR results using probability-probability (PP) plots.
-To compare two samples with a PP-plot we calculate the empirical quantile in each sample of a set of values observed across the two samples, then plot the sets of quantiles in the two samples against each other.
+To compare two samples with PP plots we calculate the empirical quantile in each sample of a set of values observed across the two samples, then plot the sets of quantiles in the two samples against each other.
 If the two samples are from equivalent distributions, the quantiles should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
@@
    	\includegraphics[width=1\textwidth]{img/GiRplot-1.png}	
-   	\caption{Probability-Probability plot for the GiR test statistics.}
+   	\caption{Probability-probability (PP) plots for the GiR test statistics.}
    	   	\label{figure:GiRplot}
@@
  	   We now present a case study applying our method to Montgomery county government email data.
- 	   %\subsection{Data}\label{subsec:Montgomery}
  	   Our data come from the North Carolina county government email dataset collected by \cite{ben2017transparency} that includes internal email corpora covering the inboxes and outboxes of managerial-level employees of North Carolina county governments.
-Out of over twenty counties, we chose Montgomery County to 1) test our model using data with large portion of emails with hyperedges (16.76\%), all of which are a single sender multiple receiver cases, and 2) limit the scope of this initial application.
+Out of over twenty counties, we chose Montgomery County to 1) test our model using data with large proportion of hyperedges (16.76\%), all of which are emails sent from one sender to two or more receivers, and 2) limit the scope of this initial application.
 To summarize, Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
 For this case study,
- 	   we formulate the network statistics $\boldsymbol{x}$ and timestamp statistics $\boldsymbol{y}$ and ground them in illustrative examples.
-We then report a suite of experiments that test our method’s ability to form the posterior distribution over latent variables.
+ 	   we formulate the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$ and ground them in illustrative examples.
+We then report a suite of experiments that test the HEM's ability to form the posterior distribution over latent variables.
  	   \subsection{Covariates}\label{subsec:Covariates_email}
- 	   In the example of email networks, we form the covariate vector $\boldsymbol{x}_{adr}$ using time-varying network statistics based on the time interval prior to and including $t_{d-1}$.
-Given a set of interaction data, a primary modeling goal lies in determining which characteristics and behaviors of the senders and receivers are predictive of interaction.
-This email application specifically give rise to the following question: ``To what extent are nodal, dyadic or triadic network effects, as characterized
- 	   by past interaction behaviors, relevant to predicting future events?" We employ the network statistics in \cite{PerryWolfe2012}, along with the intercept term, to address the question.
+ 	   \subsubsection{Edge covariates}
+ 	   Given a set of network data, a primary modeling goal of the generative process for edges lies in determining which characteristics and behaviors are predictive of the receiver selection.
+This email application specifically give rise to the following question: ``To what extent are nodal, dyadic or triadic network effects relevant to predicting future emails?" As an illustrative example, we form the receiver selection features $\boldsymbol{x}$ for Montgomery County email data using some nodal statistics and interval-based network statistics.
+First, we include the gender information of sender and receiver, as well as their homophily indicator.
+For dyadic and triadic network effects, we summarize past interaction behaviors based on the time interval prior to and including $t_{d-1}$.
 Specifically, our time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{ days}, t_{d-1}]$.
-For $a \in [A], r \in [A]$, and $d \in [D]$, we define the effects
+For $a \in [A], r \in [A]$, and $d \in [D]$, we define 14 covariates for $\boldsymbol{x}_{adr}$:
  	   \begin{itemize}
  	   	\item[1.] intercept: ${x}_{adr1} =1$;
- 	   	\item[2.] outdegree of sender $a$: ${x}_{adr2} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
- 	   	\item[3.] indegree of receiver $r$: ${x}_{adr3}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
- 	   	\item[4.] send: ${x}_{adr4}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
- 	   	\item[5.] receive: ${x}_{adr5}=\mbox{send}(r,a)$;
- 	   	\item[6.] 2-send: ${x}_{adr6} = \sum_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(h,r)$;
- 	   	\item[7.] 2-receive: ${x}_{adr7}= \sum_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(r,h)$;
- 	   	\item[8.] sibling: ${x}_{adr8}=\sum_{h \neq a, r} \mbox{send}(h,a)\mbox{send}(h,r)$;
- 	   	\item[9.] cosibling: ${x}_{adr9}=\sum_{h \neq a, r} \mbox{send}(a,h)\mbox{send}(r,h)$;
- 	   	\item[10.] hyperedge size of sender $a$: ${x}_{adr10}=\sum_{d^\prime: t_{d^\prime} \in l_d} \sum_{r=1}^A I(a_{d^\prime} = a)I(u_{d^\prime r} = 1)$;
- 	   	\item[11.] outdegree$*$hyperedge size: ${x}_{adr11} = {x}_{adr2}\times{x}_{adr10};$
+ 	   	 \item[2.] gender of sender: ${x}_{adr2} = I(\mbox{gender of sender } a= \mbox{female});$
+ 	   	 \item[3.] gender of receiver: ${x}_{adr3} = I(\mbox{gender of receiver } r= \mbox{female});$
+ 	   	 \item[4.] gender homophily: ${x}_{adr4} = I({x}_{adr2}={x}_{adr3});$ 	   		
+ 	   	\item[5.] outdegree of sender: ${x}_{adr5} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+ 	   	\item[6.] indegree of receiver: ${x}_{adr6}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
+ 	   	\item[7.] hyperedge size of sender: ${x}_{adr7}=\sum_{d^\prime: t_{d^\prime} \in l_d} \sum_{r=1}^A I(a_{d^\prime} = a)\,I(u_{d^\prime r} = 1)$;
+ 	  \item[8.] interaction between outdegree and hyperedge size: ${x}_{adr8} = {x}_{adr5}\times{x}_{adr7};$
+ 	   	\item[9.] send: ${x}_{adr9}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)\,I(u_{d^\prime r} = 1)$;
+ 	   	\item[10.] receive: ${x}_{adr10}=\mbox{send}(r,a)$;
+ 	   	\item[11.] 2-send: ${x}_{adr11} = \sum_{h \neq a, r} \mbox{send}(a,h)\,\mbox{send}(h,r)$;
+ 	   	\item[12.] 2-receive: ${x}_{adr12}= \sum_{h \neq a, r} \mbox{send}(h,a)\,\mbox{send}(r,h)$;
+ 	   	\item[13.] sibling: ${x}_{adr13}=\sum_{h \neq a, r} \mbox{send}(h,a)\,\mbox{send}(h,r)$;
+ 	   	\item[14.] cosibling: ${x}_{adr14}=\sum_{h \neq a, r} \mbox{send}(a,h)\,\mbox{send}(r,h)$;
  	 	   \end{itemize}
- 	   where $I(\cdot)$ is an indicator function, and the last covariate is the interaction term between outdegree and hyperedge size.
-As with the nodal (2, 3, 10, 11) and dyadic (4, 5) effects, the triadic (6--9) effects are designed so that their coefficient have a straightforward interpretation.
+ 	   where $I(\cdot)$ is an indicator function.
+The network statistics (5--14) are designed so that their coefficient have a straightforward interpretation.
 The statistics ``outdegree" and ``indegree" measures the gregariousness and popularity effect of the node by counting the number of emails sent from $a$ and received by $r$, respectively, within the last 7 days.
-Moreover, in order to capture individual tendency of writing multicast emails, we include the statistic ``hyperedge size"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of receivers are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
-Dyadic statistics ``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
+Moreover, in order to capture individual tendency of send emails to two or more receivers, we include the statistic ``hyperedge size"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of receivers are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
+We also include the interaction term between outdegree and hyperedge size.
+Next, we employ dyadic and triadic network statistics from \cite{PerryWolfe2012}.
+Dyadic statistics``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
 In the example of triadic statistics, the covariate ``2-send" counts the pairs of emails involving some node $h$ distinct from $a$ and $r$ such that emails from $a$ to $h$ and $h$ to $r$ are both observed within the last 7 days.
@@
  	   	\centering
- 	   	\includegraphics[width=0.55\textwidth]{img/triad.png}	
+ 	   	\includegraphics[width=0.65\textwidth]{img/triad-1.png}	
  	   	\caption {Visualization of triadic statistics: 2-send, 2-receive, sibling, and cosibling.}
@@
 
- 	   For time-related covariates $\boldsymbol{y}_{ad}$ in Section \ref{subsec:Time}, we form the covariate vector $\boldsymbol{y}_{ad}$ using the seven statistics which may possibly effect ``time to send the next document".
-The covariates can be time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$), and they could depend on $a$ only (nodal effect), $d$ only (temporal effect), or both $a$ and $d$ (nodal \& temporal effect).
-Specifically, the timestamp statistics are defined as
+ 	    	   \subsubsection{Timestamp covariates}
+ 	   For the event timing features $\boldsymbol{y}$ introduced in Section \ref{subsec:Time}, we identify a set of covariates which may possibly effect ``time to the next email." Similar to the edge covariates, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
+In addition, we select some edge-specific covariates based on the temporal aspect of the $(d-1)^{th}$ email---e.g., whether the previous email was sent (1) during the weekend and (2) before or past midday (AM/PM)---since we expect the email interactions within county government to be less active during the weekend and in the evening.
+To be specific, the timestamp statistics are defined as
  	   \begin{itemize}
  	   	\item[1.] intercept: ${y}_{ad1} =1$;
- 	   	\item[2.] outdegree of sender $a$: ${y}_{ad2} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
- 	   	\item[3.] indegree of sender $a$: ${y}_{ad3}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
- 	   	\item[4.] gender of sender $a$: ${y}_{ad4}=I(a= \mbox{female})$;
- 	   	\item[5.] manager status of sender $a$: ${y}_{ad5}=I(a= \mbox{County Manager})$;
- 	   	\item[6.] weekend of event $d$: ${y}_{ad6} = I(t_{d-1}= \mbox{weekend})$;
- 	   	\item[7.] am/pm of event $d$: ${y}_{ad7}= I(t_{d-1}= \mbox{pm})$.
+ 	   \item[2.] gender of sender: ${y}_{ad2}=I(\mbox{gender of sender }a= \mbox{female})$;
+ 	   \item[3.] manager status of sender: ${y}_{ad3}=I(\mbox{sender }a \mbox{ is the County Manager})$;
+ 	   	\item[4.] outdegree of sender: ${y}_{ad4} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+ 	   	\item[5.] indegree of sender: ${y}_{ad5}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
+ 	   	\item[6.] weekend indicator of previous email: ${y}_{ad6} = I(t_{d-1} \mbox{ is during the } \mbox{weekend})$;
+ 	   	\item[7.] AM/PM of previous email: ${y}_{ad7}= I(t_{d-1} \mbox{ in } \mbox{PM})$.
  	   \end{itemize}
@@
 
-	The HEM has many component parts that need to be specified by the user (i.e., the selection of the event timing features $\boldsymbol{y}$, the receiver selection features $\boldsymbol{x}$, and the event time distribution $f$).
+	The HEM has many component parts that need to be specified by the user (i.e., the receiver selection features $\boldsymbol{x}$, the selection of the event timing features $\boldsymbol{y}$, and the distribution of time increments $f$).
 Many of these components will be specified based on user expertise (e.g., regarding which features would drive receiver selection), but some decisions may require a data-driven approach to model specification.
@@
 Here, we specifically compare the predictive performance from two distributions---log-normal and exponential.
-We particularly choose exponential distribution as an alternative to what we used earlier (i.e., log-normal) since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor oriented models \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
+We particularly choose the log-normal distribution based on some exploratory analysis (e.g., histogram and simple regressions) on raw time increments data, and take exponential distribution as an alternative since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
 	\begin{algorithm}[!t]
@@
 		\begin{algorithmic}
-			\STATE {\bfseries Input:} data $ \{ (a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, 
-			number of new data to generate $R$,
-			hyperparameters
+			\STATE {\bfseries Input}: data $ \{ (a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, 
+			number of new data to generate $R$, and initial values of $(\boldsymbol{b}, \boldsymbol{\eta}, \boldsymbol{u}, \sigma^2_\tau)$
 			\vskip 0.1in
-			\textbf{Test splits:}	
-			\STATE draw test senders with $p=0.1$ (out of $D$ senders) 
-			\STATE draw test receivers
-			with $p=0.1$ (out of $D\times (A-1)$ receiver indicators $\{\{\boldsymbol{r}_{dr}\}_{r\in [A]_{\backslash a_d}}\}_{d=1}^D$)
-			\STATE draw test timestamps with $p=0.1$  (out of $D$ timestamps) 
-			\STATE set the ``test" data as ``missing" (NA)
+			\textbf{Test splits} (with $p=0.1$):	
+			\STATE draw test senders (out of $D$ senders) 
+			\STATE draw test receivers (out of $D\times (A-1)$ receiver indicators $\{\{\boldsymbol{r}_{dr}\}_{r\in [A]_{\backslash a_d}}\}_{d=1}^D$)
+			\STATE draw test timestamps  (out of $D$ timestamps) 
+			\STATE set the test data as ``missing" (NA)
 			\vskip 0.1in
 			\textbf{Imputation and inference:}	
-			\STATE initialize the latent variables $(\boldsymbol{b}, \boldsymbol{\eta}, \boldsymbol{u}, \sigma^2_\tau)$
 			\FOR{$r=1$ {\bfseries to}  $R$}
@@
 			\FOR{$a=1$ {\bfseries to} $A$}
-			\STATE compute $\pi_{a} $ using $P(a_d= a | \cdot)=f_{\tau}(\tau_{d}; \mu_{a_dd}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)$
+			\STATE compute $\pi_{a}=P(a_d= a | \cdot)$ using equation (\ref{eqn:latenttime}) (without the product term)
 			\ENDFOR
-			\STATE draw $a_d \sim \mbox{Multinomial}(\pi_a)$
+			\STATE draw $a_d \sim \mbox{multinomial}(\pi_a)$
 			\ENDIF
@@
 			\IF{$r_{dr}=$ NA}
-			\STATE draw $r_{dr}$ using $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$---equation (7)
+			\STATE draw $r_{dr}$ from multinomial with probability $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$ using equation (\ref{eqn:latentreceiver})
 			\ENDIF
@@
 			\IF{$t_d=$ NA}
-			\STATE draw $\boldsymbol{\tau}^{new}_d$ from $f_{\tau}(\tau^{new}_{d}; \mu_{a_d d}, \sigma_\tau^2)\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, \sigma_\tau^2) \big)$ via importance sampling (e.g., proposal distribution $g \sim \mbox{halfcauchy}(5)$)
+			\STATE draw $\boldsymbol{\tau}^{new}_d$ from equation (\ref{eqn:latenttime}) (without the product term) via importance sampling\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
 			\ENDIF
-			\STATE run inference and update $(\boldsymbol{b}, \boldsymbol{\eta},\boldsymbol{u}, \sigma^2_\tau)$ given the imputed and observed data
+			\STATE run inference and update $(\boldsymbol{u},\boldsymbol{b}, \boldsymbol{\eta})$ given the imputed and observed data
 			\ENDFOR
-			\STATE store the estimates for ``test" data
+			\STATE store the estimates for test data
 			\ENDFOR
@@
 
-	We evaluate the model's ability to predict edges and timestamps from the Montgomery County email data, conditioned on their ``training" part of the data.
-To perform the experiment, we separately formed a test split of each three components---sender, receivers, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
+	We evaluate the model's ability to predict edges and timestamps from Montgomery County email data, conditioned on their ``training" part of the data.
+To perform the experiment, we separately formed a test split of each three model components---sender, receivers, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
 Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, model estimates, and current values of test data.
 We then run inference to update the latent variables given the imputed and observed data.
-We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for ``test" data.
+We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for test data.
 Algorithm \ref{alg:PPE} outlines this procedure in detail.
-We run the experiment and measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
-We compare the predictions in terms of classification accuracy in predicting the senders and receivers, as well as prediction error in the timestamps.
-First, we compare the posterior probability of correct senders from missing documents $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
-We call this measure as ``correct sender posterior probability." The plot on the left demonstrates that both log-normal and exponential distributions acheive better predictive performance for senders compared to what is expected under random guess (dotted blue line at $1/18$), with log-normal distribution showing slightly higher performance than exponential distribution on average.
-Secondly, since the receiver vector is binary---$r_{dr}=1$ if received or $r_{dr}=0$ otherwise---we compute $F_1$ scores for receiver predictions, comparing the true receiver vector $\boldsymbol{r}^{obs}_{dr}$ and predicted receiver vectors $\boldsymbol{r}^{pred}_{dr}$ for missing receiver indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA).
-Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, there exists noticeable difference between log-normal and exponential in their performance of predicting unknown receivers.
-Similar to the sender prediction, log-normal outperforms exponential in general.
-Finally, prediction errors for missing timestamps are measured using the median absolute percentage error (MdAPE) \citep{hyndman2006another}, where we take the median of absolute percentage errors $p_{di}$ for $i=1,\ldots,500$ for $d$th document, calculated as follows:
+
+	We run the experiment and measure the predictive performance of two separate time distributions using $N=500$ predicted samples, by comparing the predictions in terms of classification accuracy in predicting the senders and receivers, as well as prediction error in the timestamps.
+First, we compare the posterior probability of correct senders for each of missing emails $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
+We call this measure as ``correct sender posterior probability." On the left of Figure \ref{figure:PPEresults}, we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails.
+The results show that both log-normal and exponential distributions acheive better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing slightly higher performance than exponential distribution on average.
+Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA) by taking the harmonic mean of precision and recall:
+	\begin{equation}
+	\begin{aligned}
+	F_1 =2\cdot\frac{\mbox{precision}\cdot \mbox{recall}}{\mbox{precision}+ \mbox{recall}}, &\mbox{ where } \\
+			\mbox{recall}  = \frac{\mbox{TP}}{\mbox{TP+FN}} \mbox{ and } \mbox{precision} & =\frac{\mbox{TP}}{\mbox{TP+FP}},
+			\end{aligned}
+	\end{equation}
+	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$).
+Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, the middle plot in Figure \ref{figure:PPEresults} reveals noticeable difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal outperforms exponential.
+Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:
+		\begin{equation}
+		e_{\tau_d} = \mbox{median}\Big(\abs*{\frac{\tau^{obs}_d - \tau^{pred_1}_{d}}{\tau^{obs}_d}},\ldots, \abs*{\frac{\tau^{obs}_d - \tau^{pred_N}_{d}}{\tau^{obs}_d}}\Big).
+		\end{equation}
+	The right plot of Figure \ref{figure:PPEresults} presents boxplots for the time prediction errors.
+where plot the estimates in a log-scale.
+Surprisingly, we have a huge benefit in the performance of timestamp prediction when we assume log-normal distribution for time-increments compared to exponential distribution.
+This difference can be explained by overdispersion in exponential distribution, because there exists greater variability in the time increments of emails than would be expected under exponential distribution.
+As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing components of time-stamped network data?" and 2) offer one standard way to determine the distribution of time increments in Section \ref{subsec:Time}.
 	\begin{figure}[!t]
@@
 		\includegraphics[width=1\textwidth]{img/PPEplotnew-1.png}	
-		\caption {Comparison of predictive performance between log-normal and exponential distributions: boxplots for correct sender posterior probability (\textit{left}), distribution of correct receiver posterior probability in log-scale (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).
+		\caption {Comparison of predictive performance between log-normal and exponential distributions: boxplots for correct sender posterior probability (\textit{left}), $F_1$ scores from receiver predictions (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).
 The dotted blue lines in the left plot represents the correct sender probability expected by random guess---i.e., $1/A=1/18\approx0.056$.}
@@
 	\end{figure}
-	\begin{equation*}
-	p_{di} = \abs*{\frac{\tau^{obs}_d - \tau^{pred}_{di}}{\tau^{obs}_d}},
-	\end{equation*}
-	and we present boxplots for the MdAPE estimates on the right plot.
-For better visualization, we plot MdAPE estimates in log-scale since they are highly right-skewed.
-As expected, we have huge benefit in the performance of timestamp prediction when we choose log-normal distribution over exponential.
-This difference can be explained by our variance estimate $\hat{\sigma}_\tau^2= 14.093$ in Section \ref{subsec:Result_email}, because exponential distribution omits the extra information on time increments contained in the large variance estimate.
-As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing information of the emails?" and 2) offer one standard way to determine the time increment distribution in Section \ref{subsec:Time}.
-
 	\subsection{Posterior Predictive Checks}\label{subsec:PPC_email} 	   
-	We perform posterior predictive checks \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for the Montgomery County email data.
-We formally generated entirely new data, by simulating time-stamped events $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}.
-For the test of goodness-of-fit in terms of network dynamics, we use multiple network statistics that summarize meaningful aspects of the Montgomery County email data: outdegree distribution, indegree distribution, receiver size distribution, and time increments probability-probability (PP) plot.
-We then generated 500 synthetic networks from the posterior predictive distribution, according to Algorithm \ref{alg:PPC}.
-	\begin{algorithm}[!b]
+In this section, we perform posterior predictive checks (PPC) \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for Montgomery County email data.
+We formally generated entirely new data, by simulating $N=500$ synthetic email data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}, where the pseudocode is outlined in Algorithm \ref{alg:PPC}.
+For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution, indegree distribution, receiver size distribution, and probability-probability (PP) plot for time increments.
+	\begin{algorithm}[!t]
 		\spacingset{1}
@@
 		\begin{algorithmic}
-			\STATE \textbf{Input}: number of new data to generate $R$, covariates $\boldsymbol{x}$ and $\boldsymbol{y}$\\
-			estimated latent variables $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta},  \sigma_\tau^2)$\\
+			\STATE \textbf{Input}: number of data to generate $R$, covariates $(\boldsymbol{x},\boldsymbol{y})$, and estimated values of $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta})$\\
 			\vskip 0.1in
@@
 			\FOR{$d = 1$ {\bfseries to}  $D$} 
-			\STATE	Draw ($a_{d}$, $\boldsymbol{r}_{d}$, $t_{d}$) following Section \ref{sec:generative process}\\
+			\STATE	Draw ($a_{d}$, $\boldsymbol{r}_{d}$, $t_{d}$) following Algorithm \ref{alg:generative}\\
 			\ENDFOR
@@
 	\end{algorithm}
+
+	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using log-normal distribution, which shows better performance in Section \ref{subsec:Experiment_email}.
+Upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic data, where the left one for outdegree statistic and the right plot is for indegree statistic.
+For both plots, the x-axis represents the nodes ($A=1,\ldots,18$), and the y-axis represents the number of emails sent or received by the node.
+When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes.
+For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, showing acceptable fit to the data.
+Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
+Since we use more information in the receiver selection process (i.e., network effects) while we rely solely on minimum time increments when choosing the observed sender, these results are expected.
+Lower left plot is the distribution of receiver sizes, where the x-axis spans over the size of receivers 1 to 14 (which is the maximum size of observed receivers) and the y-axis denotes the number of emails with x-number of receivers.
+The result shows that our model is underestimating emails with one receiver while overestimating emails with two, three, and four receivers.
+One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the emails with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right.
+To improve the goodness of fit for receiver sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
+In the end, the plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions against each other in order to assess how closely two data sets agree.
+Here, the closeness to the diagonal line gives a measure of the difference between the distribution of simulated time increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
+All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the comparison between log-normal and exponential distributions are attached in Appendix C.
 	\begin{figure}[!t]
@@
 		\includegraphics[width=0.31\textwidth]{img/timeppnew.pdf}
-		\caption {PPC results from log-normal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and time increments probability-probability (PP) plot  (\textit{lower right}).
-Red lines in the first three plot depict the observed statistics, and the red line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
+		\caption {PPC results from log-normal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and PP plot for time increments (\textit{lower right}).
+Blue lines denote the observed statistics (in the first three plots) or the diagonal line connecting $(0, 0)$ and $(1, 1)$ (in the last plot).}
 		\label{figure:PPCresults}
 	\end{figure}
-
-	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using log-normal distribution.
-Upper two plots show node-specific degree distributions, where the left one is the boxplots of 500 posterior predictive outdegree statistic and the right plot is the same one for indegree statistic.
-For both plots, the x-axis represents the node id's from 1 to 18, and the y-axis represents the number of emails sent or received by the node.
-When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes.
-For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, without using node-specific indicators.
-Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
-Since we use more information in the receiver selection process (i.e., network effects) while we only rely on minimum time increments when choosing the observed sender, these results are expected.
-Lower left plot is the distribution of receiver sizes, where the x-axis spans over the size of receivers 1 to 14 (which is the maximum size of observed receivers) and the y-axis denotes the number of documents with x-number of receivers.
-The result shows that our model is underestimating single-receiver documents while overestimating documents with two, three, and four receivers.
-One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the documents with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right.
-To improve the goodness of fit for receiver sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
-In the end, the plot on the lower right is the PP plot for time increments, which is a graphical measure commonly used for assessing how closely two data sets agree, by plotting the two cumulative distribution functions against each other.
-The resulting goodness of fit of the diagonal line gives a measure of the difference between the distribution of simulated time increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
-All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC results from exponential distribution, and the plots comparing posterior checks between log-normal and exponential distributions are attached in Appendix \ref{subsec: PPCexp}.
 
@@
 			\begin{algorithmic}
+			\STATE \textbf{Input}: number of edges and nodes $(D, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and the coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
+							\vskip 0.1in				
 				\FOR{d=1 to D}
@@
 	\end{equation*}
-	Finally, the closed form expression for the normalizing constant is  \begin{equation*}
+	Finally, the closed form expression for the normalizing constant is  
+	\begin{equation*}
 	\begin{aligned}Z(\boldsymbol{\lambda}_{ad}) = \prod_{r \neq a } \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1.
@@
 	\end{equation*}
-	\newpage
 	\subsection*{Appendix C: Comparison of PPC Results: log-normal vs. exponential}\label{appendix: PPCexp}
-	\iffalse
-	\begin{figure}[H]
-		\centering
-		\includegraphics[width=0.495\textwidth]{img/outdegree_exp-1.png}	
-		\includegraphics[width=0.495\textwidth]{img/indegree_exp-1.png}	
-		\includegraphics[width=0.495\textwidth]{img/recipientsize_exp-1.png}	
-		\includegraphics[width=0.31\textwidth]{img/timedist_exp-1.png}
-		\caption {PPC results from exponential distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and time increments probability-probability (PP) plot  (\textit{lower right}).
-Red lines in the first three plot depict the observed statistics, and the red line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
-		\label{figure:PPCexp}
-	\end{figure}
-	\fi
 		\begin{figure}[H]
@@
 			\includegraphics[width=0.31\textwidth]{img/timepp_two-1.png}
-			\caption {Comparison of PPC results between log-normal (\textit{red}) and exponential (\textit{green}) distributions: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and time increments probability-probability (PP) plot  (\textit{lower right}).
-Red lines in the first three plot depict the observed statistics, and the black line in the last plot is the diagonal line connecting $(0, 0)$ and $(1, 1)$.}
+			\caption {Comparison of PPC results between log-normal (\textit{red}) and exponential (\textit{green}) distributions: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and PPplot for time increments (\textit{lower right}).
+Blue lines denote the observed statistics (in the first three plots) or the diagonal line connecting $(0, 0)$ and $(1, 1)$ (in the last plot).}
 			\label{figure:PPCtwo}                                          

### 2018-05-24 paper/ba-HEM/ba-sample.tex
revisions until page 17 of BA draft

@@
 From the perspective of the computational social scientist, this has led to a growing need for methods of modeling interactions that manifest as edges exchanged in continuous time.
-A number of models that build upon topic modeling through Latent Dirichlet Allocation \citep{Blei2003} to incorporate link data as well as textual content have been developed recently \citep{mccallum2005author,lim2013twitter,Krafft2012}.
-These models are innovative in their extensions that incorporate network information.
-However, none of the models that are currently available in the literature integrate the rich random-graph structure offered by state of the art models for network structure---such as the exponential random graph model (ERGM) \citep{robins2007introduction,chatterjee2013estimating,hunter2008ergm}.
-The ERGM is the canonical model for modeling the structure of a static network.
-It is flexible enough to specify a generative model that accounts for nearly any pattern of edge formation such as reciprocity, clustering, popularity effects \citep{desmarais2017statistical}.
+In recent decades, several dynamic network models which could handle time-stamped events with temporal granularity have been developed, where their edge formations are governed by structural dynamics similar to those used in the exponential random graph model (ERGM)---the canonical model for modeling the structure of a static network.
+For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} study the network evolutions as a consequence of \textit{micro-steps}---i.e., actors making choices to form a new tie or withdraw an existing tie.
+On the other hand, event-based network models \citep{Butts2008,Vu2011,hunter2011dynamic} provide a general regression framework for longitudinal networks by modeling an edge as a realization of continuous time survival process.
+Those models are flexible enough to specify a generative model that accounts for nearly any pattern of edge formation such as reciprocity, clustering, popularity effects \citep{desmarais2017statistical}, thus very useful to understand which traits and behaviours are predictive of interactions.
 
-Several network models have been developed that handle time-stamped events in which edge formation is governed by structural dynamics similar to those used in the ERGM \citep{Butts2008,Vu2011,snijders1996stochastic}.
-Those models are very useful to understand which traits and behaviours are predictive of interactions, however, none of the models explicitly allows the hyperedge---a connection between two or more vertices generated simultaneously\footnote{A hyperedge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
-For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involve one sender and multiple receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), but their model parameter estimation relies on likelihood approximation which leads to bias.
-Similarly, \cite{fan2009learning} treats multicast emails as multiple single-receiver edges and randomly jitter the sent times, to avoid the violation of continous-time model assumption.
-On the other hand, there have been numerous studies for hyperedges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}.
-To our knowledge, there is a lack of extensive efforts to incorportate hyperedge modeling into general statistical framework.
+However, most studies above are limited to modeling edges with one sender and one receivers.
+To our knowledge, none of the existing continuous-time network models in statistical literature explicitly allow hyperedges---a connection between two or more vertices generated simultaneously\footnote{A hyperedge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
+For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involve one sender and one or more receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), to construct approximate likelihood function in their inferential framework for model parameters.
+Similarly, \cite{fan2009learning} duplicates emails sent from one sender to one or more receivers and randomly jitter the sent times, in order to avoid the violation of continous time model assumption.
+There have been numerous studies for hyperedges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}---with lack of extensive efforts to incorportate hyperedge modeling into general statistical framework.
 
-Concentrating on developing a statistical network model with better handling of hyperedges, we introduce the hyperedge event model (HEM) which simultaneously models the two components that govern time-stamped event formation: 1) the receiver selection processs that allows multiple senders or receivers, and 2) the time-to-next interactions with flexible distributional choices.
-In what follows, we introduce the HEM by describing how we assume the generatve process of a time-stamped event data (Section \ref{sec:generative process}), and deriving the sampling equations for Bayesian inference (Section \ref{sec:inference}).
-Then, we apply the model to the Montgomery county government email data and perform two model validation tasks (Section \ref{subsec:Emails}).
+Concentrating on developing a statistical network model with better handling of hyperedges, we introduce the hyperedge event model (HEM) which jointly models the two components that govern time-stamped event formation: 1) the receiver selection processs that allows directed edges with one sender and one or more receivers or one receiver and one or more senders, and 2) the timing equation that models time increments (i.e., time to next event) with flexible distributional choices.
+In what follows, we introduce the HEM by describing how we assume the generatve process of a time-stamped event data (Section \ref{sec:generative process}), and deriving the conditional posteriors for Bayesian inference along with code review tests (Section \ref{sec:inference}).
+Then, we demonstrate the model's applicability by analyzing one of the county government email network---the Montgomery county email data---via model selection, posterior predictive checks, and exploratory analysis (Section \ref{subsec:Emails}).
 Finally, the paper finishes in Section 5 with conclusion and discussion.
@@
 Data generated under the model consists of $D$ unique edges.
-A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
+A single edge, indexed by $d \in [D]$, is represented by the three components: a sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and a timestamp $t_d \in (0, \infty)$.
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
@@
 \subsection{Hypothetical Edges}\label{subsec: Tie}
-For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---an approximate inverse logit of the probability that edge $d$ is being sent from the sender $a$ to receiver $r$---as a linear combination of network-based statistics:
+For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---an approximate inverse logit of the probability that edge $d$ is being sent from sender $a$ to receiver $r$---as a linear combination of statistics relevant to the receiver selection process:
 \begin{equation}
@@
 Again, this is equivalent to assuming independent Bernoulli trial on each $u_{adr}$ with probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
-We provide the derivation of the normalizing constant as a tractable form in Appendix B.
+We provide detailed derivation steps for the normalizing constant in Appendix B.
 
 \subsection{Hypothetical Timestamps}\label{subsec:Time}
-Similarly, we consider ``If $a$ were the sender of edge $d$, when would it be sent?" and define the ``timing rate" for the sender $a$
+Similarly, we consider ``If $a$ were the sender of edge $d$, when would it be sent?" and define the ``timing rate" for sender $a$
 \begin{equation}
@@
 Possible choices of distribution include exponential, Weibull, gamma, and log-normal\footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
-Based on the choice of distribution, we may introduce any additional latent variable (e.g., variance parameter $\sigma_\tau^2$ for log-normal and shape parameter $\theta$ for gamma) to account for the variance in time increments.
-We use $f_\tau(\cdot; \mu)$ and $F_\tau(\cdot; \mu)$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$.
+Based on the choice of distribution, we may introduce any additional latent variable (e.g., shape parameter $k$ for Weibull, shape parameter $\theta$ for gamma, and variance parameter $\sigma_\tau^2$ for log-normal) to account for the variance in time increments.
+We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
 \subsection{Senders, Receivers, and Timestamps}\label{subsec:Observed}
@@
 \subsubsection{Coefficients for edge covariates}
-Unlike hypothetical edges above, new values for $\boldsymbol{b}$ cannot be sampled directly from its conditional posterior, but may instead be obtained using the Metropolis--Hastings algorithm.
+Unlike hypothetical edges above, new values for $\boldsymbol{b}$ cannot be sampled directly from its conditional posterior, but may instead be obtained using the Metropolis--Hastings (M-H) algorithm.
 Assuming an uninformative prior (i.e., $N({0},\infty)$), the conditional posterior over $\boldsymbol{b}$ is
@@
 \subsubsection{Coefficients for timestamp covariates}
-Likewise, we use Metropolis-Hastings algorithm to update the latent variable $\boldsymbol{\eta}$.
+Likewise, we use the M-H algorithm to update the latent variable $\boldsymbol{\eta}$.
 Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for no-tied event case is
@@
 If $M=D$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
-Note that when we have the latent variable to quantify the variance in time increments $V(\cdot)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional Metropolis-Hastings update---e.g., $\Pr(\sigma^2_\tau| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution and $\Pr(\theta| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma distribution.
+Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional M-H update---e.g., $\Pr(k| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution.
 \begin{algorithm}[!t]
@@
 			\FOR{r = 1 to A (r $\neq$ a)}
-					\STATE update $u_{adr}$ using Gibbs update --- equation (\ref{eqn:latentreceiver})
+					\STATE update $u_{adr}$ using Gibbs update ---equation (\ref{eqn:latentreceiver})
 			\ENDFOR
@@
 		\FOR{n=1 to $I_1$}
-			\STATE update $\boldsymbol{b}$ using Metropolis-Hastings --- equation (\ref{eqn:latentedge})
+			\STATE update $\boldsymbol{b}$ using M-H algorithm---equation (\ref{eqn:latentedge})
 		\ENDFOR
 	\FOR{n=1 to $I_2$}
-			\STATE update $\boldsymbol{\eta}$ using Metropolis-Hastings --- equation (\ref{eqn:latenttime}) or equation (\ref{eqn:latenttime2}) 
-			\STATE (if needed) update the latent variable for $V(\cdot)$ using Metropolis-Hastings --- equation (\ref{eqn:latenttime}) or equation (\ref{eqn:latenttime2}) 
+			\STATE update $\boldsymbol{\eta}$ using M-H algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
 		\ENDFOR
-
+			\IF {extra parameter for $V(\mu)$} 
+			\STATE update the variance parameter using M-H algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
+				\ENDIF
 	\ENDFOR
@@
    	\item[1.] Mean of observed receiver sizes $ \lVert \boldsymbol{r}_{d} \rVert_1 $ across $d=1,\ldots,D$,
-   	\item[2.] Mean of time increments $\tau_d$ across $d=1,...,D$,
-   	\item[3.] $b_p$ value used to generate the samples $p = 1,...,P$,
-   	\item[4.] $\eta_q$ value used to generate the samples $q = 1,...,Q$,
-   	\item[5.] $\sigma^2_\tau$ value used to generate the samples in log-normal distribution
+   	   	\item[2.] Variance of observed receiver sizes $ \lVert \boldsymbol{r}_{d} \rVert_1 $ across $d=1,\ldots,D$,
+   	\item[3.] Mean of time increments $\tau_d$ across $d=1,...,D$,
+   	   	\item[4.] Variance of time increments $\tau_d$ across $d=1,...,D$,
+   	\item[5.] $b_p$ value used to generate the samples $p = 1,...,P$,
+   	\item[6.] $\eta_q$ value used to generate the samples $q = 1,...,Q$,
+   	\item[7.] $\sigma^2_\tau$ value used to generate the samples in log-normal distribution
    \end{itemize}
@@
  	   we formulate the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$ and ground them in illustrative examples.
-We then report a suite of experiments that test the HEM's ability to form the posterior distribution over latent variables.
+We then report a suite of experiments that test the HEM's ability to form the posterior distribution over its latent variables.
  	   \subsection{Covariates}\label{subsec:Covariates_email}
@@
  	   	\centering
- 	   	\includegraphics[width=0.65\textwidth]{img/triad-1.png}	
+ 	   	\includegraphics[width=0.6\textwidth]{img/triad-1.png}	
  	   	\caption {Visualization of triadic statistics: 2-send, 2-receive, sibling, and cosibling.}
@@
 	\end{equation}
-	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$).
-Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, the middle plot in Figure \ref{figure:PPEresults} reveals noticeable difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal outperforms exponential.
-Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:
-		\begin{equation}
-		e_{\tau_d} = \mbox{median}\Big(\abs*{\frac{\tau^{obs}_d - \tau^{pred_1}_{d}}{\tau^{obs}_d}},\ldots, \abs*{\frac{\tau^{obs}_d - \tau^{pred_N}_{d}}{\tau^{obs}_d}}\Big).
-		\end{equation}
-	The right plot of Figure \ref{figure:PPEresults} presents boxplots for the time prediction errors.
-where plot the estimates in a log-scale.
-Surprisingly, we have a huge benefit in the performance of timestamp prediction when we assume log-normal distribution for time-increments compared to exponential distribution.
-This difference can be explained by overdispersion in exponential distribution, because there exists greater variability in the time increments of emails than would be expected under exponential distribution.
-As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing components of time-stamped network data?" and 2) offer one standard way to determine the distribution of time increments in Section \ref{subsec:Time}.
 		\begin{figure}[!t]
@@
 		\end{figure}
+	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$).
+Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, the middle plot in Figure \ref{figure:PPEresults} reveals noticeable difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal outperforms exponential.
+Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:
+		\begin{equation}
+		e_{\tau_d} = \mbox{median}\Big(\abs*{\frac{\tau^{obs}_d - \tau^{pred_1}_{d}}{\tau^{obs}_d}},\ldots, \abs*{\frac{\tau^{obs}_d - \tau^{pred_N}_{d}}{\tau^{obs}_d}}\Big).
+		\end{equation}
+	The right plot of Figure \ref{figure:PPEresults} presents boxplots for the median absolute relative errors.
+where plot the estimates in a log-scale.
+Surprisingly, we have a huge benefit in the performance of timestamp prediction when we assume log-normal distribution for time-increments compared to exponential distribution.
+This difference can be explained by overdispersion in exponential distribution, because there exists greater variability in the time increments of emails than would be expected under exponential distribution.
+As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing components of time-stamped network data?" and 2) offer one standard way to determine the distribution of time increments in Section \ref{subsec:Time}.
+
 	\subsection{Posterior Predictive Checks}\label{subsec:PPC_email} 	   
 In this section, we perform posterior predictive checks (PPC) \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for Montgomery County email data.
-We formally generated entirely new data, by simulating $N=500$ synthetic email data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}, where the pseudocode is outlined in Algorithm \ref{alg:PPC}.
+We formally generated entirely new data, by simulating $N=500$ synthetic email data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}\iffalse, where the pseudocode is outlined in Algorithm \ref{alg:PPC}\fi.
 For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution, indegree distribution, receiver size distribution, and probability-probability (PP) plot for time increments.
+\iffalse
 	\begin{algorithm}[!t]
@@
 		\label{alg:PPC}
-	\end{algorithm}
+	\end{algorithm}     \fi
 
@@
 	\subsection{Exploratory Analysis}\label{subsec:Result_email}
-	Based on some preliminary experiments, we choose log-normal distribution to model time-to-next-email in Montgomery county email data, thus we estimate the variance $\sigma_\tau^2$ with the prior specified as inverse-Gamma($2, 1$).
-In this section, we present the results based on 55,000 MCMC outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
-While the inner iterations for  $\sigma_\tau^2$ is fixed as 1, we use 10 and 20 inner iterations for $\boldsymbol{\eta}$ and $\boldsymbol{b}$, respectively, to adjust for its slower convergence rate.
-Convergence diagnostics for MCMC including some traceplots and Geweke diagnostics \citep{geweke1991evaluating} can be found in Appendix \ref{subsec: convergence}.
+	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we choose to analyze Montgomery county email data and interpret the results using log-normal distribution.
+We assume weakly informative priors for latent variables such as $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b=\boldsymbol{0}, \Sigma_b = 2\times I_P)$, $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta=\boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, and $\sigma_\tau^2 \sim \mbox{inverse-Gamma}(a=2, b=1)$, and run MCMC algorithm in Algorithm \ref{alg:MCMC} with $O=55,000$ outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
+While the inner iterations for $\sigma_\tau^2$ is fixed as 1, we specify the inner iterations $I_1=20$ for $\boldsymbol{b}$ and $I_2=10$ for $\boldsymbol{\eta}$ to adjust for slower convergence rates.
+Convergence diagnostics including some traceplots and Geweke diagnostics \citep{geweke1991evaluating} are provided in Appendix D.
 	\begin{figure}[!t]
@@
 	\end{figure}
-
+	\subsubsection{Coefficients for edge covariates}
 	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$.
-Since we use logit probability of $\lambda_{adr}$ for generative process for edges (Section \ref{subsec: Tie}), we have
+Since we use the logit probability of $\lambda_{adr}$ when generating hypothetical edges in Section \ref{subsec: Tie}, we assume that
 	\begin{equation*}
-	\mbox{logit}(\lambda_{adr})=\log\Big(\frac{\lambda_{adr}}{1-\lambda_{adr}}\Big) =b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11},
+	\mbox{logit}(\lambda_{adr})=\log\Big(\frac{\lambda_{adr}}{1-\lambda_{adr}}\Big) =b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14},
 	\end{equation*}
-	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{11}x_{adr11})$.
-	Firstly, we can see that the effect of send (i.e., ``number of times the actor $a$ sent emails to the actor $r$ over the last week'') is positive, implying that if the actor $a$ sent $n$ number of emails to $r$ last week, then the actor $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
-Similar interpretation can be applied for the statistics indegree and Nrecieve.
-For example, as the actor $r$ received $n$ emails and the actor $a$ sent emails to $n$ rececievers over the last week, the actor $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times and $\exp(0.047\times n)\approx(1.048)^n$ times, respectively, more likely to send an email to $r$.
-On the other hand, outdegree statistic has negative effect---i.e., if the actor $a$ sent $n$ number of emails to anyone last week, then the actor $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times likely to send an email to $r$---possibly due to its multicollinearity with the statistics send and hyperedge size.
-This can be interpreted as ``if the actor $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of send) or 2) no broadcast or multicast emails (excluding the effect of hyperedge size)'' then the actor $a$ is less likely to send an email to $r$.
-Rest of statistics are not statistically significant because their 95\% credible interval do not include 0.
-Surprisingly, none of the triadic effects seem to have significant effect on the generative process of edges.
-
-	Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of the time-related coefficients $\boldsymbol{\eta}$.
-For this specific datset, we assume log-normal distribution (Section \ref{subsec:Time}) with the unit of time being an hour, so that the interpretation of $\hat{\boldsymbol{\eta}}$ should be based on
+	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14})$.
+	To begin with, we can see that the effect of the statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) is significant and positive with $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
+Similar interpretation can be applied for the covariates ``indegree" and ``hyperedge size".
+For example, if the receiver $r$ received $n$ number of emails and sender $a$ sent emails to $n$ number of rececievers over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times and $\exp(0.047\times n)\approx(1.048)^n$ times, respectively, more likely to send an email to $r$.
+On the contrary, the statistic ``outdegree" has significantly negative effect---i.e., if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$---possibly due to its multicollinearity with the statistics ``send" and/or ``hyperedge size".
+This result is likely to appear under the following scenario: if sender $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of ``send") and the email of interest is not a  2) broadcast email which is originally aimed at large number of receivers (excluding the effect of ``hyperedge size"), then sender $a$ is less likely to send an email to receiver $r$.
+Rest of statistics are not statistically significant in that their 95\% credible interval do not include 0.
+Surprisingly, none of the covariates for triadic network effects seem to have significant effect on the generative process of edges.
+		\subsubsection{Coefficients for timestamp covariates}
+	For timestamp covariates, Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{\eta}$.
+Since we assume log-normal distribution for time increments, the interpretation of $\hat{\boldsymbol{\eta}}$ should be based on
 	\begin{equation*}
@@
 	\end{equation*}
-	where $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$ as defined in Secton \ref{subsec: Tie}.
+	where the receiver intensity is a linear combination of edge covariates---i.e., $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$---as defined in Secton \ref{subsec: Tie}.
 

### 2018-05-25 paper/ba-HEM/ba-sample.tex
revisions except conclusion and updated plots

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
+
 \def\spacingset#1{\renewcommand{\baselinestretch}%
@@
 \begin{keyword}
-\kwd{sample}
-\kwd{\LaTeXe}
+\kwd{continuous time network model} 
+\kwd{email data analysis}
 \end{keyword}
@@
 The GiR test results are depicted in Figure \ref{figure:GiRplot}, which show that we pass the test on every statistic.
-   \begin{figure}[ht]
+   \begin{figure}[H]
    	\centering
-   	\includegraphics[width=1\textwidth]{img/GiRplot-1.png}	
+   	\begin{subfigure}[b]{0.2425\textwidth}
+   		   	\caption{Mean of $\lVert \boldsymbol{r}_{d} \rVert_1 $}
+   	\includegraphics[width=\textwidth]{img/plot1.png}	
+   	\end{subfigure}
+   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   	   		   		   	\caption{Variance of $\lVert \boldsymbol{r}_{d} \rVert_1 $}
+   	   		\includegraphics[width=\textwidth]{img/plot2.png}	
+   	   	\end{subfigure}
+   	   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   	   	   		   	   	   		\caption{Mean of $\tau_d$}
+   	   	   		\includegraphics[width=\textwidth]{img/plot3.png}	
+   	   	   	\end{subfigure}
+   	   	   	   	   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   	   	   	   	   	   		  	\caption{Variance of $\tau_d$}
+   	   	   	   	   	   		\includegraphics[width=\textwidth]{img/plot4.png}	
+   	   	   	   	   	   	\end{subfigure}
+   	   	   	   	   	   	   	   	   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   	   	   	   	   	   	   	   	   	   		\caption{Value of $b_1$}
+   	   	   	   	   	   	   	   	   	   		\includegraphics[width=\textwidth]{img/plot5.png}	
+   	   	   	   	   	   	   	   	   	   	\end{subfigure}
+   	   	   		   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   	   	   		   	   		\caption{Value of $b_2$}
+   	   	   		   	   		\includegraphics[width=\textwidth]{img/plot6.png}	
+   	   	   		   	   	\end{subfigure}   	   	   	   	   	   	   	
+   		   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   		   	   		\caption{Value of $b_3$}
+   		   	   		\includegraphics[width=\textwidth]{img/plot7.png}	
+   		   	   	\end{subfigure}   	   		   	   	
+   		   	   	   		   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   		   	   	   		   	   		\caption{Value of $b_4$}
+   		   	   	   		   	   		\includegraphics[width=\textwidth]{img/plot8.png}	
+   		   	   	   		   	   	\end{subfigure}   	   		   	   	
+   		   	   	   		   	   	   		   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   		   	   	   		   	   	   		   	   		\caption{Value of $\eta_1$}
+   		   	   	   		   	   	   		   	   		\includegraphics[width=\textwidth]{img/plot9.png}	
+   		   	   	   		   	   	   		   	   	\end{subfigure}   	   		   	   	
+   		     		   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   		     		   	   		\caption{Value of $\eta_2$}
+   		     		   	   		\includegraphics[width=\textwidth]{img/plot10.png}	
+   		     		   	   	\end{subfigure}   	   		   	   	
+   		   	     		   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   		   	     		   	   		\caption{Value of $\eta_3$}
+   		   	     		   	   		\includegraphics[width=\textwidth]{img/plot11.png}	
+   		   	     		   	   	\end{subfigure}   	   		   	   	  		   	   	 	
+   		   	     		   	   		     		   	   	\begin{subfigure}[b]{0.2425\textwidth}
+   		   	     		   	   		     		   	   		\caption{Value of $\sigma^2_\tau$}
+   		   	     		   	   		     		   	   		\includegraphics[width=\textwidth]{img/plot12.png}	
+   		   	     		   	   		     		   	   	\end{subfigure}   	   		   	   	   	   		   	   	   		   	   	
    	\caption{Probability-probability (PP) plots for the GiR test statistics.}
@@
  	   we formulate the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$ and ground them in illustrative examples.
-We then report a suite of experiments that test the HEM's ability to form the posterior distribution over its latent variables.
+We then report a suite of experiments---out-of-sample prediction for model selection and posterior predictive checks---that test the HEM's ability to form the posterior distribution over its latent variables.
+Finally, we demonstrate an exploratory analysis of Montgomery County email data using the model estimates to discover interesting patterns in organizational communication networks.
  	   \subsection{Covariates}\label{subsec:Covariates_email}
@@
 	\end{equation}
+	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$).
+Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, the middle plot in Figure \ref{figure:PPEresults} reveals noticeable difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal outperforms exponential.
+Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:
 			\begin{figure}[!t]
@@
 			\end{figure}
-	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$).
-Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, the middle plot in Figure \ref{figure:PPEresults} reveals noticeable difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal outperforms exponential.
-Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:
 		\begin{equation}
@@
 To improve the goodness of fit for receiver sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
-In the end, the plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions against each other in order to assess how closely two data sets agree.
-Here, the closeness to the diagonal line gives a measure of the difference between the distribution of simulated time increments and the observed ones, and our PP plot shows that we have great performance in reproducing the observed time distribution.
-All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the comparison between log-normal and exponential distributions are attached in Appendix C.
-	\begin{figure}[!t]
+In the end, the plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions---one for simulated time increments and another for observed time increments---against each other in order to assess how closely two data sets agree.
+Here, the closeness to the diagonal line connecting $(0, 0)$ and $(1, 1)$ gives a measure of difference between the simulated and observed time increments, and our PP plot shows that we have great performance in reproducing the observed time distribution.
+All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are attached in Appendix C.
+	\begin{figure}[!htb]
 		\centering
-		\includegraphics[width=0.495\textwidth]{img/outdegreenew-1.png}	
-		\includegraphics[width=0.495\textwidth]{img/indegreenew-1.png}	
-		\includegraphics[width=0.495\textwidth]{img/recipientsizenew-1.png}	
-		\includegraphics[width=0.31\textwidth]{img/timeppnew.pdf}
-		\caption {PPC results from log-normal distribution: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and PP plot for time increments (\textit{lower right}).
-Blue lines denote the observed statistics (in the first three plots) or the diagonal line connecting $(0, 0)$ and $(1, 1)$ (in the last plot).}
+		\begin{tabular}[t]{cc}
+		   	\begin{subfigure}[b]{0.495\textwidth}
+		   		\caption{Outdegree distribution}
+		\includegraphics[width=\textwidth]{img/outdegreenew-1.png}	
+		   	\end{subfigure}
+		   			   	\begin{subfigure}[b]{0.495\textwidth}
+		   			   		\caption{Indegree distribution}
+		   			   		\includegraphics[width=\textwidth]{img/indegreenew-1.png}	
+		   			   	\end{subfigure}\\
+			   	\begin{subfigure}[b]{0.495\textwidth}
+			   		\caption{Receiver size distribution}
+			   		\includegraphics[width=\textwidth]{img/recipientsizenew-1.png}	
+			   	\end{subfigure}
+			   	\begin{subfigure}[b]{0.495\textwidth}
+			   				\centering
+			   		\caption{PPplot for time increments}
+			   		\includegraphics[width=0.625\textwidth]{img/timeppnew.pdf}	
+			   	\end{subfigure}
+		\end{tabular}
+		\caption {PPC results from log-normal distribution. Blue lines denote the observed statistics in (a)--(c) and denotes the diagonal line in (d).}
 		\label{figure:PPCresults}
@@
 While the inner iterations for $\sigma_\tau^2$ is fixed as 1, we specify the inner iterations $I_1=20$ for $\boldsymbol{b}$ and $I_2=10$ for $\boldsymbol{\eta}$ to adjust for slower convergence rates.
-Convergence diagnostics including some traceplots and Geweke diagnostics \citep{geweke1991evaluating} are provided in Appendix D.
+Convergence diagnostics including the traceplots and Geweke diagnostics \citep{geweke1991evaluating} are provided in Appendix D.
 	\begin{figure}[!t]
@@
 	For timestamp covariates, Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{\eta}$.
-Since we assume log-normal distribution for time increments, the interpretation of $\hat{\boldsymbol{\eta}}$ should be based on
+Note that interpretations of the estimated coefficients for $\hat{\boldsymbol{\eta}}$ should be based on the specified timeunit of the datset, which we use ``hour" for Montgomery county email data.
+Moreover, since we assume log-normal distribution for time increments, we need careful interpretation regarding the timing equations
+			\begin{figure}[!t]
+				\centering
+				\includegraphics[width=0.89\textwidth]{img/etaest-1.png}	
+				\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
+				\label{figure:etaresults}
+			\end{figure}
 	\begin{equation*}
@@
 	\end{equation*}
-	To begin with, the posterior estimates of two temporal effects---weekend and pm---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after 12pm, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
-On the contrary, the statistics manager, outdegree, and indegree turn out to shorten the time to next email.
-For example, being a county manager (i.e., the manager of the managers) lowers the expected $\log(\tau_{ad})$ by -1.070, since he or she needs to respond fastly to emails with important decisions.
-In addition, the manager in general sends or receives a lot more emails which may shorten the response time.
-This argument is supported by the posterior estimates for outdegree and indegree, where the estimated coefficients are approximately -0.206 and -0.060, respectively.
-Gender of the department manager is shown to have no significant effect on time-to-next-email.
-The posterior mean estimate of the variance parameter $\sigma^2_\tau$ is 14.093 with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time increments in this data.
-		\begin{figure}[!t]
-			\centering
-			\includegraphics[width=0.89\textwidth]{img/etaest-1.png}	
-			\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
-			\label{figure:etaresults}
-		\end{figure}
+	To begin with, the posterior estimates of two temporal effects---``weekend" and 		AM/PM"---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after midday, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+On the contrary, the covariates ``manager", ``outdegree", and ``indegree" turn out to shorten the amount of time to next email.
+For example, being a county manager (i.e., the manager of department managers) lowers the expected value of $\log(\tau_{ad})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
+This argument is also supported by the posterior estimates for ``outdegree" and ``indegree" statistics, where the estimated coefficients are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
+Gender of the department manager is shown to have no significant effect on time increments.
+In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time increments of emails.
 
@@
 	\subsection*{Appendix A: Alternative Generative Process} \label{appendix:alternativeGP}
-		\begin{algorithm}[!ht]
+		\begin{algorithm}[H]
 			\SetAlgoLined
@@
 	\end{equation*}
+\newpage
 	\subsection*{Appendix C: Comparison of PPC Results: log-normal vs. exponential}\label{appendix: PPCexp}
@@
 			\centering
-			\includegraphics[width=0.495\textwidth]{img/outdegree_two-1.png}	
-			\includegraphics[width=0.495\textwidth]{img/indegree_two-1.png}	
-			\includegraphics[width=0.495\textwidth]{img/recipientsize_two-1.png}	
-			\includegraphics[width=0.31\textwidth]{img/timepp_two-1.png}
-			\caption {Comparison of PPC results between log-normal (\textit{red}) and exponential (\textit{green}) distributions: outdegree distribution (\textit{upper left}), indegree distribution (\textit{upper right}), receiver size distribution (\textit{lower left}), and PPplot for time increments (\textit{lower right}).
-Blue lines denote the observed statistics (in the first three plots) or the diagonal line connecting $(0, 0)$ and $(1, 1)$ (in the last plot).}
+			\begin{tabular}[t]{cc}
+				\begin{subfigure}[b]{0.495\textwidth}
+					\caption{Outdegree distribution}
+					\includegraphics[width=\textwidth]{img/outdegree_two-1.png}	
+				\end{subfigure}
+				\begin{subfigure}[b]{0.495\textwidth}
+					\caption{Indegree distribution}
+					\includegraphics[width=\textwidth]{img/indegree_two-1.png}	
+				\end{subfigure}\\
+				\begin{subfigure}[b]{0.495\textwidth}
+					\caption{Receiver size distribution}
+					\includegraphics[width=\textwidth]{img/recipientsize_two-1.png}	
+				\end{subfigure}
+				\begin{subfigure}[b]{0.495\textwidth}
+					\centering
+					\caption{PPplot for time increments}
+					\includegraphics[width=0.625\textwidth]{img/timepp_two-1.png}
+				\end{subfigure}
+			\end{tabular}
+			\caption {Comparison of PPC results between log-normal (\textit{red}) and exponential (\textit{green}) distributions.
+Blue lines denote the observed statistics in (a)--(c) and denotes the diagonal line in (d).}
 			\label{figure:PPCtwo}
@@
 			\centering
-		\includegraphics[width=0.495\textwidth]{img/betatrace.pdf}	
-		\includegraphics[width=0.495\textwidth]{img/etatrace.pdf}	
-		\includegraphics[width=0.495\textwidth]{img/betageweke.pdf}	
-		\includegraphics[width=0.44\textwidth]{img/etageweke.pdf}
-		\caption {Convergence diagnostics from log-normal distribution: traceplots and density plots for $\boldsymbol{b}$ chains (\textit{upper left}) and $\boldsymbol{\eta}$ chains (\textit{upper right}), and geweke diagnostics for $\boldsymbol{b}$ chains (\textit{lower left}) and $\boldsymbol{\eta}$ chains (\textit{lower right}).}
+			\begin{tabular}[t]{cc}
+				\begin{subfigure}[b]{0.495\textwidth}
+					\caption{Traceplots of $\boldsymbol{b}$}
+					\includegraphics[width=\textwidth]{img/betatrace.pdf}	
+				\end{subfigure}
+				\begin{subfigure}[b]{0.495\textwidth}
+					\caption{Traceplot of $\boldsymbol{\eta}$}
+					\includegraphics[width=\textwidth]{img/etatrace.pdf}	
+				\end{subfigure}\\
+				\begin{subfigure}[b]{0.495\textwidth}
+					\caption{Geweke diagnostics for $\boldsymbol{b}$}
+					\includegraphics[width=\textwidth]{img/betageweke.pdf}	
+				\end{subfigure}
+				\begin{subfigure}[b]{0.495\textwidth}
+					\centering
+					\caption{Geweke diagnostics for $\boldsymbol{\eta}$ and $\sigma^2_\tau$}
+					\includegraphics[width=0.89\textwidth]{img/etageweke.pdf}
+				\end{subfigure}
+			\end{tabular}
+			\caption {Convergence diagnostics from log-normal distribution.}
 			\label{figure:convergencediag}
 		\end{figure}
-
 	\begin{supplement}

### 2018-05-25 code/GiR.R

@@ -48,6 +48,8 @@ for (n in 1:Nsamp) {
 par(mfrow=c(3,4))
 GiR_PP_Plots(result[,c(1:(5+P+Q))], result[,c((6+P+Q):(2*(5+P+Q)))])
 save(result, file = "/Users/bomin8319/Desktop/result.RData")
+
+setwd("/Users/bomin8319/Desktop/")
 Forward_stats = result[,c(1:(5+P+Q))]
 Backward_stats = result[,c((6+P+Q):(2*(5+P+Q)))]
 colnames(Forward_stats) = c("Mean Recipient Size", "Mean Time-increments", sapply(1:P, function(p){paste0("b",p," Estimates")}), sapply(1:Q, function(q){paste0(expression(eta),q," Estimates")}), "Variance Estimate")
@@ -69,8 +71,11 @@ library(ggplot2)
   		qx2[j] = mean(Backward_stats[, i] <= uniqueValues[j])
   	}
   	data = data.frame(qx1 = qx1, qx2 = qx2)
-	plot[[i]] =qplot(data = data, x = qx1, y = qx2, colour = I("blue"), size = I(0.5)) + labs(x = "Forward", y = "Backward")+geom_abline(intercept = 0, col = 'red') + theme(text = element_text(size = rel(3)), plot.title= element_text(size=rel(3.5)))
+	plot[[i]] =qplot(data = data, x = qx1, y = qx2, colour = I("blue"), size = I(2)) + labs(x = "Forward", y = "Backward")+geom_abline(intercept = 0, col = 'red', size = I(1)) + theme(text = element_text(size = rel(5)), plot.title= element_text(size=rel(3.5)))
 	#+labs(title = expression(nms[i]))
+mname = paste0("plot", i, ".png")
+print(plot[[i]])
+ggsave(filename = mname)
 }	
 library(gridExtra)
 library(latex2exp)

### 2018-05-26 paper/ba-HEM/ba-sample.tex
plots with gender effects updated

@@
  	   Given a set of network data, a primary modeling goal of the generative process for edges lies in determining which characteristics and behaviors are predictive of the receiver selection.
-This email application specifically give rise to the following question: ``To what extent are nodal, dyadic or triadic network effects relevant to predicting future emails?" As an illustrative example, we form the receiver selection features $\boldsymbol{x}$ for Montgomery County email data using some nodal statistics and interval-based network statistics.
-First, we include the gender information of sender and receiver, as well as their homophily indicator.
-For dyadic and triadic network effects, we summarize past interaction behaviors based on the time interval prior to and including $t_{d-1}$.
+This email application specifically give rise to the following question: ``To what extent are nodal, dyadic or triadic network effects relevant to predicting future emails?" As an illustrative example, we form the receiver selection features $\boldsymbol{x}$ for Montgomery County email data using some nodal, dyadic, and triadic covariates.
+First, as we want to test whether gender plays a role in receiver selection process, we include three nodal covariates---the gender information of sender and receiver, and their homophily indicator.
+Additionally, we include four interval-based nodal network covariates---outdegree of sender, indegree of receiver, hyperedge size of sender, and the interaction between outdegree and hyperedge size---to study the effect of nodal behaviors on future interactions.
+For dyadic and triadic network effects, we employ the network statistics in \cite{PerryWolfe2012} and summarize past interaction behaviors based on the time interval prior to and including $t_{d-1}$.
 Specifically, our time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{ days}, t_{d-1}]$.
@@
 We also include the interaction term between outdegree and hyperedge size.
-Next, we employ dyadic and triadic network statistics from \cite{PerryWolfe2012}.
 Dyadic statistics``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
@@
  	   	\item[6.] weekend indicator of previous email: ${y}_{ad6} = I(t_{d-1} \mbox{ is during the } \mbox{weekend})$;
- 	   	\item[7.] AM/PM of previous email: ${y}_{ad7}= I(t_{d-1} \mbox{ in } \mbox{PM})$.
+ 	   	\item[7.] PM indicator of previous email: ${y}_{ad7}= I(t_{d-1} \mbox{ in } \mbox{PM})$.
  	   \end{itemize}
@@
 Algorithm \ref{alg:PPE} outlines this procedure in detail.
-
 We run the experiment and measure the predictive performance of two separate time distributions using $N=500$ predicted samples, by comparing the predictions in terms of classification accuracy in predicting the senders and receivers, as well as prediction error in the timestamps.
@@
 All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are attached in Appendix C.
-	\begin{figure}[!htb]
+	\begin{figure}[!t]
 		\centering
@@
 			   		\caption{PPplot for time increments}
-			   		\includegraphics[width=0.625\textwidth]{img/timeppnew.pdf}	
+			   		\includegraphics[width=0.6\textwidth]{img/timeppnew-1.png}	
 			   	\end{subfigure}
@@
 Convergence diagnostics including the traceplots and Geweke diagnostics \citep{geweke1991evaluating} are provided in Appendix D.
-	\begin{figure}[!t]
-		\centering
-		\includegraphics[width=1\textwidth]{img/best-1.png}	
-		\caption {Posterior distribution of $\boldsymbol{b}$ estimates.}
-		\label{figure:betaresults}
-	\end{figure}
+
 	\subsubsection{Coefficients for edge covariates}
-	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$.
+	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$, where (a) displays the coefficients for nodal covariates and (b) displays the coefficients for dyadic and triadic covariates.
 Since we use the logit probability of $\lambda_{adr}$ when generating hypothetical edges in Section \ref{subsec: Tie}, we assume that
@@
 	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14})$.
-	To begin with, we can see that the effect of the statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) is significant and positive with $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
-Similar interpretation can be applied for the covariates ``indegree" and ``hyperedge size".
-For example, if the receiver $r$ received $n$ number of emails and sender $a$ sent emails to $n$ number of rececievers over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times and $\exp(0.047\times n)\approx(1.048)^n$ times, respectively, more likely to send an email to $r$.
-On the contrary, the statistic ``outdegree" has significantly negative effect---i.e., if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$---possibly due to its multicollinearity with the statistics ``send" and/or ``hyperedge size".
+	To begin with, we find out that the effect of nodal coavariates ``gender of sender" and ``gender of receiver" are both significant in negative direction.
+\textbf{substantive interpretation on gender effects}.
+Next, the statistic ``outdegree" also has significantly negative effect---i.e., if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$---possibly due to its multicollinearity with the statistics ``hyperedge size" where the two terms' show significant interaction effect.
 This result is likely to appear under the following scenario: if sender $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of ``send") and the email of interest is not a  2) broadcast email which is originally aimed at large number of receivers (excluding the effect of ``hyperedge size"), then sender $a$ is less likely to send an email to receiver $r$.
-Rest of statistics are not statistically significant in that their 95\% credible interval do not include 0.
+Similar interpretation can be applied for the covariates ``indegree," but in the opposite direction.
+For example, if the receiver $r$ received $n$ number of emails over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $r$.
+
+	On the next plot for dyadic and triadic covariates, one thing we can check is that the effect of statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) is significant and positive with $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
+Another dyadic statistic ``receive" is not statistically significant in that its 95\% credible interval do not include 0.
 Surprisingly, none of the covariates for triadic network effects seem to have significant effect on the generative process of edges.
+		\begin{figure}[!t]
+			\centering
+			\begin{tabular}[t]{cc}
+				\begin{subfigure}[b]{0.495\textwidth}
+					\caption{Nodal covariates}
+					\includegraphics[width=\textwidth]{img/betanewplot2-1.png}	
+				\end{subfigure}
+				\begin{subfigure}[b]{0.495\textwidth}
+					\caption{Dyadic and triadic covariates}
+					\includegraphics[width=\textwidth]{img/betanewplot3-1.png}	
+				\end{subfigure}
+			\end{tabular}
+			\caption {Posterior distribution of $\boldsymbol{b}$ estimates.}
+			\label{figure:betaresults}
+		\end{figure}
 		\subsubsection{Coefficients for timestamp covariates}
@@
 Moreover, since we assume log-normal distribution for time increments, we need careful interpretation regarding the timing equations
-			\begin{figure}[!t]
-				\centering
-				\includegraphics[width=0.89\textwidth]{img/etaest-1.png}	
-				\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
-				\label{figure:etaresults}
-			\end{figure}
 	\begin{equation*}
@@
 In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time increments of emails.
-
+				\begin{figure}[!t]
+					\centering
+					\includegraphics[width=0.495\textwidth]{img/etaplotnew-1.png}	
+					\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
+					\label{figure:etaresults}
+				\end{figure}
 \section{Conclusion}\label{sec:conclusion}
@@
 					\caption{Traceplots of $\boldsymbol{b}$}
-					\includegraphics[width=\textwidth]{img/betatrace.pdf}	
+					\includegraphics[width=\textwidth]{img/betatrace-1.png}	
 				\end{subfigure}
@@
 					\caption{Traceplot of $\boldsymbol{\eta}$}
-					\includegraphics[width=\textwidth]{img/etatrace.pdf}	
+					\includegraphics[width=\textwidth]{img/etatrace-1.png}	
 				\end{subfigure}\\
@@
 					\caption{Geweke diagnostics for $\boldsymbol{b}$}
-					\includegraphics[width=\textwidth]{img/betageweke.pdf}	
+					\includegraphics[width=\textwidth]{img/betageweke-1.png}	
 				\end{subfigure}
@@
 					\caption{Geweke diagnostics for $\boldsymbol{\eta}$ and $\sigma^2_\tau$}
-					\includegraphics[width=0.89\textwidth]{img/etageweke.pdf}
+					\includegraphics[width=\textwidth]{img/etageweke-1.png}
 				\end{subfigure}

### 2018-05-26 Emails/Montgomery_result.R

@@ -14,24 +14,53 @@ library(reshape2)
 library(gridExtra)
 library(ggrepel)
 library(RColorBrewer)
+ggplotColours <- function(n = 6, h = c(0, 360) + 15){
+  if ((diff(h) %% 360) < 1) h[2] <- h[2] - 360/n
+  hcl(h = (seq(h[1], h[2], length = n)), c = 100, l = 65)
+}
+number_ticks <- function(n) {function(limits) pretty(limits, n)}
+colorsbeta = ggplotColours(13)
 
-
-colnames(Montgomery_infer$beta) = dimnames(Montgomery$X)[[4]]
-beta = data.frame(t(sapply(1:1000, function(i) Montgomery_infer$beta[40*i,])))
-colnames(beta) = dimnames(Montgomery$X)[[4]][1:10]
-colnames(beta)[6:7] = c("twosend", "tworeceive")
-colnames(beta) = dimnames(Montgomery$X)[[4]][1:10]
+colnames(Montgomery_infer$beta) = c("intercept", "outdegree", "indegree", "send", "receive",
+"two_send", "two_receive", "sibling", "cosibling", "hyperedge_size", "interaction", "gender_sender", "gender_receiver",
+"gender_homophily")
+beta = data.frame(t(sapply(1:5000, function(i) Montgomery_infer$beta[8*i,])))
+# colnames(beta) = dimnames(Montgomery$X)[[4]][1:10]
+# colnames(beta)[6:7] = c("twosend", "tworeceive")
+# colnames(beta) = dimnames(Montgomery$X)[[4]][1:10]
 beta.est = melt(beta[-1])
-colnames(beta.est)[1] = "netstats"
+colnames(beta.est)[1] = "covariates"
 colnames(beta.est)[2] = "b"
-ggplot(data = beta.est, aes(x = netstats, y = b, fill = netstats)) + geom_boxplot()+coord_flip()+ geom_hline(yintercept = 0.0, colour = "red", size = 0.5, linetype = "dashed")+labs(x = NULL, fill = "Covariates")
+beta.est[,1] = as.factor(beta.est[,1])
+beta.est$covariates <- factor(beta.est$covariates , levels = c("gender_sender", "gender_receiver",
+"gender_homophily", "outdegree", "indegree","hyperedge_size", "interaction", "send", "receive",
+"two_send", "two_receive", "sibling", "cosibling" ))
 
[…]

### 2018-05-26 Emails/traceplot.R

@@ -7,33 +7,38 @@ library(gridExtra)
 library(ggthemes)
 library(latex2exp)
 library(MCMCpack)
-beta = t(sapply(1:5000, function(x) Montgomery_infer2$beta[8*x, c(2,5,10)]))
-colnames(beta) = c("beta2","beta5", "beta10")
+beta = t(sapply(5000+c(1:5000), function(x) Montgomery_infer$beta[8*x, c(1,5,10)]))
+beta = t(sapply(1:5000, function(x) Montgomery_infer$beta[8*x,c(3,5,8)]))
+colnames(beta) = c("beta3","beta5", "beta8")
 S <-  ggs(mcmc(beta))
-plot = ggs_traceplot(S)
-density = ggs_density(S)
+plot = ggs_traceplot(S)+theme(plot.title = element_blank(),text = element_text(size = rel(4.25)),legend.position="none")+ scale_x_continuous(breaks=seq(0,5000,2500))
+density = ggs_density(S)+theme(plot.title = element_blank(),text = element_text(size = rel(4.5)),legend.position="none")
 grid.arrange(plot, density, ncol = 2, nrow = 1)
 
 
-beta = t(sapply(1:5000, function(x) Montgomery_infer2$beta[8*x, ]))
-colnames(beta) = c(sapply(1:11, function(x) paste0("beta",x)))
+beta = t(sapply(1:5000, function(x) Montgomery_infer$beta[8*x, ]))
+beta = t(sapply(1:800, function(x) Montgomery_infer$beta[50*x,]))
+colnames(beta) = c(sapply(1:14, function(x) paste0("beta",x)))
 S <-  ggs(mcmc(beta))
-ggs_geweke(S)
+S$Parameter <- factor(S$Parameter, levels = c(sapply(1:14, function(x) paste0("beta",x))))
+ggs_geweke(S)+scale_colour_manual(values = c("black","black"))+theme(plot.title = element_blank(),text = element_text(size = rel(4.25)),legend.position="none")
 
 
 
 eta = t(sapply(1:5000, function(x) Montgomery_infer$eta[8*x, c(2,7)]))
 eta = cbind(eta, sapply(1:5000, function(x) Montgomery_infer$sigma2[8*x]))
 colnames(eta) = c("eta2", "eta7", "sigma2")
-S2 <-  ggs(mcmc(eta))
-plot = ggs_traceplot(S)
-density = ggs_density(S)
+S <-  ggs(mcmc(eta))
[…]

### 2018-05-26 code/Montgomery_processing2.R

@@ -94,7 +94,17 @@ trim = which(email$timepoints >=7*24*timeunit+email$timepoints[1])
 edge = edge[trim]
 X = X[trim,,,]
 Y = Y[trim,,]
-Montgomery_infer = Inference(edge, X, Y, 55000, c(20,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
+Montgomery_infer = Inference(edge, X, Y, 55000, c(40,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
+                             proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "lognormal")
+save(Montgomery_infer, file= "/Users/bomin8319/Desktop/Montgomery_infer.RData")
+############################################################################
+initialval = list()
+initialval$u = Montgomery_infer$u
+initialval$beta = colMeans(Montgomery_infer$beta)
+initialval$eta = colMeans(Montgomery_infer$eta)
+initialval$sigma2 = mean(Montgomery_infer$sigma2)
+
+Montgomery_infer_new = Inference(edge, X, Y, 40000, c(40,10,1), 0, prior.beta, prior.eta, prior.sigma2, initialval = initialval,
                              proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "lognormal")
 
 

### 2018-05-26 paper/ba-HEM/ba-sample.tex
new PPC plots

@@
 Then, we demonstrate the model's applicability by analyzing one of the county government email network---the Montgomery county email data---via model selection, posterior predictive checks, and exploratory analysis (Section \ref{subsec:Emails}).
-Finally, the paper finishes in Section 5 with conclusion and discussion.
+Finally, the paper finishes in Section \ref{sec:conclusion} with conclusion and discussion.
 \section{The Hyperedge Event Model}\label{sec:generative process}
@@
 Data generated under the model consists of $D$ unique edges.
-A single edge, indexed by $d \in [D]$, is represented by the three components: a sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and a timestamp $t_d \in (0, \infty)$.
+A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of recipients $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
-While the model can be applied for two type of hyperedges---edges with (1) one sender and one or more receivers, and (2) one receiver and mone or more receivers---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast).
-For the latter case of hyperedges, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single receiver.
-Detailed generative process for directed edges with one receiver and one or more senders are provided in Appendix A.
+While the model can be applied for two type of hyperedges---edges with (1) a single sender and multiple receivers, and (2) multiple senders and a single receiver---here we only present the generative process for those involving a single sender and multiple receivers (i.e., multicast).
+For the latter case of hyperedges, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single recipient.
 
@@
 				\includegraphics[width=1\textwidth]{img/PPEplotnew-1.png}	
+										\includegraphics[width=0.4\textwidth]{img/modellabel.png}				
 			\caption {Comparison of predictive performance between log-normal and exponential distributions: boxplots for correct sender posterior probability (\textit{left}), $F_1$ scores from receiver predictions (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).
@@
 		   		\caption{Outdegree distribution}
-		\includegraphics[width=\textwidth]{img/outdegreenew-1.png}	
+		\includegraphics[width=\textwidth]{img/outdegree-1.png}	
 		   	\end{subfigure}
@@
 		   			   		\caption{Indegree distribution}
-		   			   		\includegraphics[width=\textwidth]{img/indegreenew-1.png}	
+		   			   		\includegraphics[width=\textwidth]{img/indegree-1.png}	
 		   			   	\end{subfigure}\\
@@
 			   		\caption{Receiver size distribution}
-			   		\includegraphics[width=\textwidth]{img/recipientsizenew-1.png}	
+			   		\includegraphics[width=\textwidth]{img/recipientsize-1.png}	
 			   	\end{subfigure}
@@
 			   		\caption{PPplot for time increments}
-			   		\includegraphics[width=0.6\textwidth]{img/timeppnew-1.png}	
+			   		\includegraphics[width=0.56\textwidth]{img/timePPplot-1.png}	
 			   	\end{subfigure}
@@
 					\caption{Outdegree distribution}
-					\includegraphics[width=\textwidth]{img/outdegree_two-1.png}	
+					\includegraphics[width=\textwidth]{img/outdegree2-1.png}	
 				\end{subfigure}
@@
 					\caption{Indegree distribution}
-					\includegraphics[width=\textwidth]{img/indegree_two-1.png}	
+					\includegraphics[width=\textwidth]{img/indegree2-1.png}	
 				\end{subfigure}\\
@@
 					\caption{Receiver size distribution}
-					\includegraphics[width=\textwidth]{img/recipientsize_two-1.png}	
+					\includegraphics[width=\textwidth]{img/recipientsize2-1.png}	
 				\end{subfigure}
@@
 					\caption{PPplot for time increments}
-					\includegraphics[width=0.625\textwidth]{img/timepp_two-1.png}
+					\includegraphics[width=0.56\textwidth]{img/timePPplot2-1.png}
 				\end{subfigure}
 			\end{tabular}
+						\includegraphics[width=0.4\textwidth]{img/modellabel.png}
 			\caption {Comparison of PPC results between log-normal (\textit{red}) and exponential (\textit{green}) distributions.

### 2018-05-26 Emails/Montgomery_result.R

@@ -93,7 +93,7 @@ recipientsdist1 = matrix(NA,  500, A-1)
 timedist1 = matrix(NA, 500, 621)
 #setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC")
 #setwd("/Users/bomin8319/")
-setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC")
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC4")
 
 for (n in 1:500) {
 	filename = paste0("Montgomery_PPCnew", n,".RData")
@@ -101,78 +101,53 @@ for (n in 1:500) {
 	outdegreedist1[n, ] = tabulate(vapply(1:621, function(x) Montgomery_PPC[[x]]$a_d, c(1)), A)
 	indegreedist1[n, ] = rowSums(sapply(1:621, function(x) Montgomery_PPC[[x]]$r_d))
 	recipientsdist1[n, ] = tabulate(vapply(1:621, function(x) sum(Montgomery_PPC[[x]]$r_d), c(1)), A-1)
-	timedist1[n, ] = c(Montgomery_PPC[[1]]$t_d -email$timepoints[42], vapply(2:621, function(x) Montgomery_PPC[[x]]$t_d - Montgomery_PPC[[x-1]]$t_d , c(1)))/ timeunit
-} 
-
-outdegreedist = data.frame(outdegreedist)
-colnames(outdegreedist)=1:18
+	timedist1[n, ] = vapply(1:621, function(x) Montgomery_PPC[[x]]$t_d, c(1))/ timeunit
+	} 
+###
+outdegreedist1 = data.frame(outdegreedist1)
+colnames(outdegreedist1)=1:18
 library(ggplot2)
 library(reshape)
-data = melt(outdegreedist)
+data = melt(outdegreedist1)
 colnames(data) = c("Node", "Outdegree")
 
 outdegree = data.frame(Node = 1:18, Outdegree = outdegree)
-ggplot(data = data, aes(x = Node, y = Outdegree)) +geom_boxplot() + geom_line(data = outdegree, col = 'red')
-
-indegreedist = data.frame(indegreedist)
-colnames(indegreedist)=1:18
[…]

### 2018-05-26 Emails/PPEnew.R

@@ -57,10 +57,10 @@ initial$eta =  colMeans(Montgomery_infer$eta)
 initial$u = Montgomery_infer$u
 initial$sigma2 = mean(Montgomery_infer$sigma2)
 
-#will generate 10 predictions (iterate two steps: imputation -> inference)
+#will generate 500 predictions (iterate two steps: imputation -> inference)
 Montgomery_PPE = PPE(edge, X, Y, 550, c(5,5,1), 50, prior.beta, prior.eta, prior.sigma2, 
                      initial = initial, proposal.var = c(0.0001, 0.001, 0.1), timeunit = 3600, 
-                     lasttime = Montgomery$lasttime, MHprop.var = 0.15, timedist = "lognormal")
+                     lasttime = email[min(trim-1), 21] - initialtime, MHprop.var = 0.15, timedist = "lognormal")
 
 save(Montgomery_PPE, file = "/Users/bomin8319/Desktop/MulticastNetwork/Emails/Montgomery_PPE.RData")
 

### 2018-05-26 code/Montgomery_processing2.R

@@ -94,10 +94,15 @@ trim = which(email$timepoints >=7*24*timeunit+email$timepoints[1])
 edge = edge[trim]
 X = X[trim,,,]
 Y = Y[trim,,]
-Montgomery_infer = Inference(edge, X, Y, 55000, c(40,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
+Montgomery_infer = Inference(edge, X, Y, 55000, c(20,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
                              proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "lognormal")
 save(Montgomery_infer, file= "/Users/bomin8319/Desktop/Montgomery_infer.RData")
 ############################################################################
+Montgomery_infer2 = Inference(edge, X, Y, 55000, c(20,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
+                             proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "exponential")
+###############################################
+
+
 initialval = list()
 initialval$u = Montgomery_infer$u
 initialval$beta = colMeans(Montgomery_infer$beta)
@@ -128,9 +133,10 @@ dimnames(Y)[[3]] = c("intercept", "female", "manager", "outdegree", "indegree", 
 Montgomery = list(edge = edge, X = X, Y = Y, lasttime = email[min(trim-1), 21] - initialtime )
 
 save(Montgomery, file = "Montgomery.RData")
-
+###################################################
 
 load("/Users/bomin8319/Desktop/Montgomery_infer.RData")
+
 initial = list()
 initial$sender = email[1:(min(trim)-1), 2]
 initial$receiver = email[1:(min(trim)-1), 3:20]

### 2018-05-26 paper/ba-HEM/ba-sample.tex
finished revising BA-HEM draft

@@
 We run the experiment and measure the predictive performance of two separate time distributions using $N=500$ predicted samples, by comparing the predictions in terms of classification accuracy in predicting the senders and receivers, as well as prediction error in the timestamps.
+We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
 First, we compare the posterior probability of correct senders for each of missing emails $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
-We call this measure as ``correct sender posterior probability." On the left of Figure \ref{figure:PPEresults}, we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails.
+We call this measure as ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails.
 The results show that both log-normal and exponential distributions acheive better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing slightly higher performance than exponential distribution on average.
@@
 	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$).
-Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, the middle plot in Figure \ref{figure:PPEresults} reveals noticeable difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal outperforms exponential.
+Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{figure:PPEresults} (b) reveals noticeable difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal outperforms exponential.
 Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:
@@
 			\centering
-				\includegraphics[width=1\textwidth]{img/PPEplotnew-1.png}	
+			\begin{tabular}[t]{ccc}
+				\begin{subfigure}[b]{0.33\textwidth}
+					\caption{Sender prediction}
+					\includegraphics[width=\textwidth]{img/senderpredict-1.png}	
+				\end{subfigure}
+				\begin{subfigure}[b]{0.33\textwidth}
+					\caption{Receiver prediction}
+					\includegraphics[width=\textwidth]{img/receiverpredict-1.png}	
+				\end{subfigure}
+				\begin{subfigure}[b]{0.33\textwidth}
+					\caption{Timestamp prediction}
+					\includegraphics[width=\textwidth]{img/timepredict-1.png}	
+				\end{subfigure}
+			\end{tabular}
 				\includegraphics[width=0.4\textwidth]{img/modellabel.png}				
-			\caption {Comparison of predictive performance between log-normal and exponential distributions: boxplots for correct sender posterior probability (\textit{left}), $F_1$ scores from receiver predictions (\textit{middle}), and boxplots for median absolute percentage error (\textit{right}).
-The dotted blue lines in the left plot represents the correct sender probability expected by random guess---i.e., $1/A=1/18\approx0.056$.}
+			\caption {Comparison of predictive performance between log-normal and exponential distributions: (a) correct sender posterior probability from sender predictions, (b) $F_1$ scores from receiver predictions, and (c) median absolute relative error from timestamp predictions.
+Blue line in (a) represents the correct sender probability expected by random guess---i.e., $1/A=1/18\approx0.056$.}
 			\label{figure:PPEresults}
 		\end{figure}		
+		\iffalse
+				\begin{figure}[!t]
+				\centering
+				\includegraphics[width=1\textwidth]{img/PPEplotnew-1.png}	
+			\end{figure}
+		\fi
 		\begin{equation}
@@
 		\end{equation}
-	The right plot of Figure \ref{figure:PPEresults} presents boxplots for the median absolute relative errors.
+	Figure \ref{figure:PPEresults} (c) presents boxplots for the median absolute relative errors.
 where plot the estimates in a log-scale.
@@
 	\subsubsection{Coefficients for edge covariates}
-	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$, where (a) displays the coefficients for nodal covariates and (b) displays the coefficients for dyadic and triadic covariates.
+	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$, where Figure \ref{figure:betaresults} (a) displays the coefficients for nodal covariates and \ref{figure:betaresults} (b) displays the coefficients for dyadic and triadic covariates.
 Since we use the logit probability of $\lambda_{adr}$ when generating hypothetical edges in Section \ref{subsec: Tie}, we assume that
@@
 	\end{equation*}
-	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14})$.
-	To begin with, we find out that the effect of nodal coavariates ``gender of sender" and ``gender of receiver" are both significant in negative direction.
-\textbf{substantive interpretation on gender effects}.
-Next, the statistic ``outdegree" also has significantly negative effect---i.e., if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$---possibly due to its multicollinearity with the statistics ``hyperedge size" where the two terms' show significant interaction effect.
-This result is likely to appear under the following scenario: if sender $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of ``send") and the email of interest is not a  2) broadcast email which is originally aimed at large number of receivers (excluding the effect of ``hyperedge size"), then sender $a$ is less likely to send an email to receiver $r$.
-Similar interpretation can be applied for the covariates ``indegree," but in the opposite direction.
-For example, if the receiver $r$ received $n$ number of emails over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $r$.
-
-	On the next plot for dyadic and triadic covariates, one thing we can check is that the effect of statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) is significant and positive with $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
-Another dyadic statistic ``receive" is not statistically significant in that its 95\% credible interval do not include 0.
-Surprisingly, none of the covariates for triadic network effects seem to have significant effect on the generative process of edges.
 			\begin{figure}[!t]
@@
 			\end{figure}
+	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14})$.
+	To begin with, we find out that the effect of nodal coavariates ``gender of sender" and ``gender of receiver" are both significant in negative direction.
+\textbf{substantive interpretation on gender effects}.
+Next, the statistic ``outdegree" also has significantly negative effect---i.e., if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$---possibly due to its multicollinearity with the statistics ``hyperedge size" where the two terms' show significant interaction effect.
+This result is likely to appear under the following scenario: if sender $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of ``send") and the email of interest is not a  2) broadcast email which is originally aimed at large number of receivers (excluding the effect of ``hyperedge size"), then sender $a$ is less likely to send an email to receiver $r$.
+Similar interpretation can be applied for the covariates ``indegree," but in the opposite direction.
+For example, if the receiver $r$ received $n$ number of emails over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $r$.
+
+	When we look at the effects of dyadic and triadic covariates, one thing we can check is that the effect of statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) is significant and positive with $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
+Another dyadic statistic ``receive" is not statistically significant in that its 95\% credible interval do not include 0.
+Surprisingly, none of the covariates for triadic network effects seem to have significant effect on the generative process of edges.
 		\subsubsection{Coefficients for timestamp covariates}
@@
 	\end{equation*}
-	To begin with, the posterior estimates of two temporal effects---``weekend" and 		AM/PM"---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after midday, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
-On the contrary, the covariates ``manager", ``outdegree", and ``indegree" turn out to shorten the amount of time to next email.
-For example, being a county manager (i.e., the manager of department managers) lowers the expected value of $\log(\tau_{ad})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
-This argument is also supported by the posterior estimates for ``outdegree" and ``indegree" statistics, where the estimated coefficients are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
-Gender of the department manager is shown to have no significant effect on time increments.
-In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists huge variability in the time increments of emails.
 				\begin{figure}[!t]
@@
 				\end{figure}	
+	To begin with, the posterior estimates of two temporal effects---``weekend" and ``PM"---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after midday, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+On the contrary, the covariates ``manager", ``outdegree", and ``indegree" turn out to shorten the amount of time to next email.
+For example, being a county manager (i.e., the manager of department managers) lowers the expected value of $\log(\tau_{ad})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
+This argument is also supported by the posterior estimates for ``outdegree" and ``indegree" statistics, where the estimated coefficients are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
+Gender of the department manager is shown to have no significant effect on time increments.
+In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists large variability in the time increments of emails.
 \section{Conclusion}\label{sec:conclusion}
-Motivated by the relational event model \citep{Butts2008} and its variants for time-stamped networks, the hyperedge event model (HEM) can effectively learn the underlying edge generating and timestamp generating structures of event data, while allowing flexibity in the covariate specifications and the distributional assumption of time increments.
-Accounting for the hyperedges, we make better use of events with hyperedges than modeling them as duplicate edges.
-In modeling the timestamps of the events, our generalized linear model (GLM) based formulation eliminates the need to stick with one distribution (e.g., exponential distribution), and we also provide an algorithm for predictive experiment that helps to learn which distribution better fits the data.
+Motivated by a growing class of dynamic network models which deal with edges exchanged in continuous time, the hyperedge event model (HEM) can effectively learn the underlying dynamics in edge and timestamp formations, providing novel insights to the literature.
+First, we explicitly model hyperedges by deriving a receiver-selection distribution that forces the sender to select at least one recevier, which is more realistic approach for events with one sender and one or more receivers and one or more sender and one receiver compared to treating them as pure duplicates.
+In modeling the timestamps (more precisely time increments) of events, our generalized linear model (GLM) based formulation offers new innovations by eliminating the need to stick with one parameter distribution (e.g., exponential distribution).
+To make better use of the proposed model, we provide an algorithm for predictive experiment that helps to learn which distribution better fits the data.
 To sum, the HEM's flexible generative process thus leads to more accurate and precise inference on model parameters.
 
-We have demonstrated effectiveness of our model by analyzing Montgomery County government emails, which includes numerous hyperedges.
-The estimated covariate effects reveal that the HEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), while the model additionally allows separate covariates and the corresponding parameters for generative processes of edges and timestamps.
-Although we illustrate the entire framework and application in the context
-of one type of hyperedges, a single sender and multiple receivers, our model can be easily extended to allow the opposite case, a single receiver and multiple senders, by slight modification of the generative process.
+We have demonstrated effectiveness of our model by analyzing Montgomery County government emails, where emails serve as the canonical example of directed edges with one sender and one or more receivers.
+The estimated effects for edge covariates reveal that the HEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), but we also learn about the effect of timestamp covariates on waiting time to next event, by integrating a survival model for event timing.
+Although we illustrate the entire framework and application in the context of one type of hyperedges, one sender and one or more receivers, our model can be easily extended to allow the opposite case, one or more sender and one receiver, by slight modification of the generative process (shown in Appendix A).
 This extension involves promissing applications including international sanctions and co-sponsorship of bills.
 Furthermore, while currently the model's applicability is limited to small-sized networks since we assume fixed set of nodes across entire timepoints, we can adjust the model to allow time-varying nodes or improve its computational efficiency such that the model is well applicable to large-scale networks.
-Considering the recent explosion of network dataset with huge number of nodes (e.g., online comnunications), the development of model adjustments for better applicability are objects of future work.
+Considering the recent explosion of network dataset with huge number of nodes (e.g., online comnunications), the development of model adjustments for better applicability are the object of future work.
 

### 2018-05-26 Emails/Montgomery_result.R

@@ -60,7 +60,7 @@ eta.est = melt(eta[-1])
 colnames(eta.est)[1] = "covariates"
 colnames(eta.est)[2] = "eta"
 eta.est[,1] = as.factor(eta.est[,1])
-ggplot(data = eta.est, aes(x = reorder(covariates,-as.numeric(covariates)), y = eta, fill =covariates)) + geom_boxplot()+coord_flip()+ geom_hline(yintercept = 0.0, colour = "blue", size =1, linetype = "dashed")+labs(x = NULL, fill = "Covariates")+theme(plot.title = element_blank(),text = element_text(size = rel(5.5)),legend.position="none")
+ggplot(data = eta.est, aes(x = reorder(covariates,-as.numeric(covariates)), y = eta, fill =covariates)) + geom_boxplot()+coord_flip()+ geom_hline(yintercept = 0.0, colour = "blue", size =1, linetype = "dashed")+labs(x = NULL, fill = "Covariates")+theme(plot.title = element_blank(),text = element_text(size = rel(5.5)),legend.position="none")+ylab(expression(eta))
 
 #####################################
 load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')

### 2018-05-26 Emails/PPEnew.R

@@ -88,13 +88,14 @@ truesender = sapply(Montgomery_PPE$sendermissing, function(d) edge[[d]]$a_d)
 predprob = Montgomery_PPE$senderprob/rowSums(Montgomery_PPE$senderprob)
 predprob2 = Montgomery_PPE2$senderprob/rowSums(Montgomery_PPE2$senderprob)
 
-sender = data.frame(probtrue = sapply(1:62, function(d) predprob[d,truesender[d]]), dist = rep("lognormal", 62))
-sender = rbind(sender, data.frame(probtrue = sapply(1:62, function(d) predprob2[d,truesender[d]]), dist = rep("exponential", 62)))
+sender = data.frame(probtrue = sapply(1:62, function(d) predprob[d,truesender[d]]), Dist = rep("log-normal", 62))
+sender = rbind(sender, data.frame(probtrue = sapply(1:62, function(d) predprob2[d,truesender[d]]), Dist = rep("exponential", 62)))
 library(ggplot2)
 library(reshape)
 sender = melt(sender)
 colnames(sender)[3] = "correct"
-p[[1]]=ggplot(data = sender, aes(x = dist, y = correct, fill = dist))+geom_boxplot()+ylab("Correct sender posterior probability")+geom_hline(yintercept=1/18, col = 'blue', lty=2, lwd=1)
+p[[1]]=ggplot(data = sender, aes(x = Dist, y = correct, fill = Dist))+geom_boxplot()+ylab(expression(pi))+geom_hline(yintercept=1/18, col = 'blue', lty=2, lwd=1)+theme(plot.title = element_blank(),text = element_text(size = rel(5.5)),legend.position="none")
+
 boxplot(sapply(1:62, function(d) predprob[d,truesender[d]]), sapply(1:62, function(d) predprob2[d,truesender[d]]))
 
 ###############################################
@@ -125,11 +126,11 @@ predreceiver2 = Montgomery_PPE2$receiverpredict
 probtrue = sapply(1:500, function(d) F1_Score(truereceiver, predreceiver[,d], 1))
 probtrue2 = sapply(1:500, function(d) F1_Score(truereceiver, predreceiver2[,d], 1))
 
-receiver = data.frame(F1score = probtrue, dist = rep("lognormal", 500))
-receiver = rbind(receiver, data.frame(F1score = probtrue2, dist = rep("exponential", 500)))
[…]

### 2018-05-28 paper/ba-HEM/ba-sample.tex
minor updates on the plots

@@
 We call this measure as ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails.
-The results show that both log-normal and exponential distributions acheive better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing slightly higher performance than exponential distribution on average.
+The results show that both log-normal and exponential distributions acheive better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing higher performance than exponential distribution.
 Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA) by taking the harmonic mean of precision and recall:
@@
 	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$).
-Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{figure:PPEresults} (b) reveals noticeable difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal outperforms exponential.
+Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{figure:PPEresults} (b) reveals slight difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal on average outperforms exponential.
 Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:

### 2018-05-28 Emails/Montgomery_result.R

@@ -156,7 +156,7 @@ recipientsdist2 = matrix(NA,  500, A-1)
 timedist2 = matrix(NA, 500, 621)
 #setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC")
 #setwd("/Users/bomin8319/")
-setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC3")
+setwd("/Users/bomin8319/Desktop/MulticastNetwork/Emails/PPC2")
 
 for (n in 1:500) {
 	filename = paste0("Montgomery_PPCnew2", n,".RData")

### 2018-05-28 code/Montgomery_processing2.R

@@ -100,6 +100,7 @@ save(Montgomery_infer, file= "/Users/bomin8319/Desktop/Montgomery_infer.RData")
 ############################################################################
 Montgomery_infer2 = Inference(edge, X, Y, 55000, c(20,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
                              proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "exponential")
+save(Montgomery_infer2, file= "/Users/bomin8319/Desktop/Montgomery_infer2.RData")
 ###############################################
 
 

### 2018-05-30 paper/ba-HEM/ba-sample.tex
revised intro

@@
 
-In recent decades, real-time digitized textual communication has developed into a ubiquitous form of social and professional interaction \citep{kanungo2008modeling, szostek2011dealing, burgess2004email, pew2016}.
-From the perspective of the computational social scientist, this has led to a growing need for methods of modeling interactions that manifest as edges exchanged in continuous time.
-In recent decades, several dynamic network models which could handle time-stamped events with temporal granularity have been developed, where their edge formations are governed by structural dynamics similar to those used in the exponential random graph model (ERGM)---the canonical model for modeling the structure of a static network.
-For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} study the network evolutions as a consequence of \textit{micro-steps}---i.e., actors making choices to form a new tie or withdraw an existing tie.
-On the other hand, event-based network models \citep{Butts2008,Vu2011,hunter2011dynamic} provide a general regression framework for longitudinal networks by modeling an edge as a realization of continuous time survival process.
-Those models are flexible enough to specify a generative model that accounts for nearly any pattern of edge formation such as reciprocity, clustering, popularity effects \citep{desmarais2017statistical}, thus very useful to understand which traits and behaviours are predictive of interactions.
+Processes that arise as time-stamped directed interactions are common in the social, natural, and phyiscal sciences.
+The data produced by such processes can be represented as dynamic directed networks---a data structure that has given rise to the development of several statistical model families.
+For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} characterize networks as evolving as the senders of edges decide to add an edge to or remove an edge from a network one edge at a time, one sender at a time.
+Event-based network models \citep{Butts2008,Vu2011,hunter2011dynamic,PerryWolfe2012} provide a general framework for modeling the realization of edges that occur as instances in continuous time streams of events.
+These models are flexible enough to specify a generative model that accounts for the ways in which past network structure begets future network structure (e.g., nodes that sent a lot of edges in the past will send a lot in the future, if node $i$ sent a tie to node $j$ recently, then node $j$ will send one to node $i$ in the near future).
+Thus, dynamic network models are very useful to understand which traits and behaviours are predictive of interactions.
 
-However, most studies above are limited to modeling edges with one sender and one receivers.
-To our knowledge, none of the existing continuous-time network models in statistical literature explicitly allow hyperedges---a connection between two or more vertices generated simultaneously\footnote{A hyperedge connecting just two nodes is simply a usual dyadic edge.}---which is a common property of digitalized textual interactions such as emails and online messages.
-For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involve one sender and one or more receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), to construct approximate likelihood function in their inferential framework for model parameters.
-Similarly, \cite{fan2009learning} duplicates emails sent from one sender to one or more receivers and randomly jitter the sent times, in order to avoid the violation of continous time model assumption.
-There have been numerous studies for hyperedges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}---with lack of extensive efforts to incorportate hyperedge modeling into general statistical framework.
+A major limitation of existing dynamic network models is that they apply to edges with one sender and one receiver.
+Many sources of dynamic network data arise as ``hyperedges'' \citep{karypis1999multilevel,ghoshal2009random,zlatic2009hypergraph,zhang2010hypergraph} that include one sender and multiple receivers or one receiver and multiple senders.
+For example, networks formed through the analysis of email \citep{newman2002email} arise with one sender and possibly multiple recipients;  networks formed between neurons via axons and dendrites have one sender and multiple recipients (axons) or one recipient and multiple senders (dendrites) \citep{partzsch2012developing}.
+Networks formed through the analysis of legislative bill cosponsorhip \citep{fowler2006legislative} arise with multiple senders (cosponsors) and one recipient (sponsor); and networks formed through the analysis of economic sanctions \citep{cranmer2014reciprocity} between countries arise with multiple sending countries and one target country.
+Existing models require that researchers alter hyperedge data to fit with the pairwise edge structure of the model.
+For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involves one sender and one or more receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), to construct approximate likelihood function in their inferential framework for model parameters.
+Similarly, \cite{fan2009learning} duplicates emails sent from one sender to one or more receivers and randomly jitter the sent times, in order to avoid the violation of the assumption that two events cannot occur at the exact same time.
+% There have been numerous studies for hyperedges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}---with lack of extensive efforts to incorportate hyperedge modeling into general statistical framework.
 
-Concentrating on developing a statistical network model with better handling of hyperedges, we introduce the hyperedge event model (HEM) which jointly models the two components that govern time-stamped event formation: 1) the receiver selection processs that allows directed edges with one sender and one or more receivers or one receiver and one or more senders, and 2) the timing equation that models time increments (i.e., time to next event) with flexible distributional choices.
-In what follows, we introduce the HEM by describing how we assume the generatve process of a time-stamped event data (Section \ref{sec:generative process}), and deriving the conditional posteriors for Bayesian inference along with code review tests (Section \ref{sec:inference}).
-Then, we demonstrate the model's applicability by analyzing one of the county government email network---the Montgomery county email data---via model selection, posterior predictive checks, and exploratory analysis (Section \ref{subsec:Emails}).
+We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern time-stamped event formation: 1) the formation of the vertices that are incident to the hyperedge, and 2) the timing of the event in which the edge manifests.
+In what follows, we introduce the HEM by defining a generative process for time and hyperedge attributed event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference and present tests of our software implementation (Section \ref{sec:inference}).
+After defining the structure of and deriving Bayesian inference methods for HEM, we demonstrate the model's applicability by analyzing data from a corpus of internal county government emails.
+In the application we illustrate model selection, posterior predictive checks, and exploratory analysis (Section \ref{subsec:Emails}).
 Finally, the paper finishes in Section \ref{sec:conclusion} with conclusion and discussion.
+
 \section{The Hyperedge Event Model}\label{sec:generative process}

### 2018-05-30 paper/ba-HEM/ba-sample.tex
typo & citation issue fixed

@@
 \address[addr4]{ Microsoft Research NYC
-    \printead{e3}
+    \printead{e4}
 }
@@
 After defining the structure of and deriving Bayesian inference methods for HEM, we demonstrate the model's applicability by analyzing data from a corpus of internal county government emails.
-In the application we illustrate model selection, posterior predictive checks, and exploratory analysis (Section \ref{subsec:Emails}).
+In the application we illustrate model selection, posterior predictive checks, and exploratory analysis (Section \ref{sec:Emails}).
 Finally, the paper finishes in Section \ref{sec:conclusion} with conclusion and discussion.
@@
    \end{figure}
- 	   \section{Application to Email Data}\label{subsec:Emails}
+ 	   \section{Application to Email Data}\label{sec:Emails}
  	   We now present a case study applying our method to Montgomery county government email data.

### 2018-05-30 paper/ba-HEM/ba-sample.tex
revising generative process

@@
 
-Data generated under the model consists of $D$ unique edges.
+In this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time.
+Data generated under the HEM consists of $D$ unique edges.
 A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of recipients $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
-While the model can be applied for two type of hyperedges---edges with (1) a single sender and multiple receivers, and (2) multiple senders and a single receiver---here we only present the generative process for those involving a single sender and multiple receivers (i.e., multicast).
-For the latter case of hyperedges, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single recipient.
+While the model can be applied for two types of hyperedges---edges with (1) a single sender and multiple receivers, and (2) multiple senders and a single receiver---here we only present the generative process for those involving a single sender and multiple receivers (i.e., multicast).
+For the latter case---one recipient and multiple senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single recipient.
 
@@
 \end{equation}
-where $\boldsymbol{b}$ is a $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of receiver selection features which vary depending on the hypotheses regarding canonical processes relevant to network theory such as popularity, reciprocity, and transitivity.
-In addition, we include intercept term to account for the average (or baseline) number of receivers.
+where $\boldsymbol{b}$ is a $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of receiver selection features.
+Such features can capture common network processes that include, but are not limited to, popularity, reciprocity, and transitivity, as well as the effects of attribute features defined on the sender, receivers, and/or sender-receiver pairs (e.g., the gender of the sender and/or receiver, an indicator of whether the sender is a supervisor of the receiver's).
+In addition, we include an intercept term to account for the average (or baseline) number of receivers.
 We place a Normal prior $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$.
 
-Next, we hypothesize ``If $a$ were the sender of edge $d$, who would be the receivers?" and derive a receiver-selection distribution.
+For each edge $d$ and each sender $a$, the HEM generates a list of hypothetical receivers that would be receivers on edge $d$ if $a$ were the sender.
 For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{th}$ row denotes sender $a$'s receiver vector of indicators---i.e., if node $r$ is the hypothetical receiver of sender $a$, then $u_{adr}=1$; otherwise $u_{adr}=0$.
-We then assume that each receiver vector $\boldsymbol{u}_{ad}$ comes from the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model to estimate the structure of graphs with binary nodes---with logit probability of $\boldsymbol{\lambda}_{ad}$.
-In order to avoid the model degeneracy from having an empty receiver set, we define a probability measure ``MB$_{G}$" motivated by the non-empty Gibbs measure \citep{fellows2017removing} which excludes the all-zero vector from the support of the multivariate Bernoulli distirbution.
-As a result, this measure helps us to 1) allow multiple sender--receiver pairs to co-exist, 2) force the sender to select at least one receiver, and 3) ensure tractable normalizing constant.
+We then assume that each receiver vector $\boldsymbol{u}_{ad}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
+In order to avoid generating edges with no receivers, we define a probability measure ``MB$_{G}$" motivated by the Gibbs measure \citep{fellows2017removing}.
+The probability measure we define amounts to a non-empty Gibbs measure, in which the all-zero vector is excluded from the support of the multivariate Bernoulli distirbution.
+As a result, this measure helps us to 1) allow a sender to select multiple receiver for a single edge, 2) force the sender to select at least one receiver, and 3) ensure a tractable normalizing constant.
 To be specific, we draw a binary vector $\boldsymbol{u}_{ad}= (u_{ad1},
@@
 where $Z(\boldsymbol{\lambda}_{ad})= \prod_{r \neq a} \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
-Again, this is equivalent to assuming independent Bernoulli trial on each $u_{adr}$ with probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
+Again, this is equivalent to assuming ithat each $u_{adr}$ is generated with the probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
 We provide detailed derivation steps for the normalizing constant in Appendix B.
@@
 \subsection{Hypothetical Timestamps}\label{subsec:Time}
-Similarly, we consider ``If $a$ were the sender of edge $d$, when would it be sent?" and define the ``timing rate" for sender $a$
+Similarly, for each sender and edge combination, the HEM generates a hypothetical time at which the edge would be generated. The timing rate for sender $a$ and edge $d$ is
+
 \begin{equation}
@@
 \end{equation}
-where $\boldsymbol{\eta}$ is a $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features, e.g., any covariates that could affect timestamps of the edge, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
+where $\boldsymbol{\eta}$ is a $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features---covariates that could affect timestamps of the edge, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
 
 In modeling ``when," we do not directly model the timestamp $t_d$.
-Instead, we assume that each sender's ``time increment"---i.e., waiting time to next interaction---is drawn from a specific distribution in the exponential family.
+Instead, we assume that each sender's ``time increment"---i.e., waiting time to next interaction since $t_{d-1}$---is drawn from a specific distribution in the exponential family.
 We define the time increment from edge $d-1$ to edge $d$ as $\tau_{d}$ (i.e., $\tau_{d}= t_d-t_{d-1}$) and specify the distribution of hypothetical timestamps with sender-specfic mean $\mu_{ad}$.
@@
 Possible choices of distribution include exponential, Weibull, gamma, and log-normal\footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
-Based on the choice of distribution, we may introduce any additional latent variable (e.g., shape parameter $k$ for Weibull, shape parameter $\theta$ for gamma, and variance parameter $\sigma_\tau^2$ for log-normal) to account for the variance in time increments.
+Based on the specific distribution, there may be a number of latent variables used in the time increment generation beyond the features used to model the rate (e.g., shape parameter $k$ for Weibull, shape parameter $\theta$ for gamma, and variance parameter $\sigma_\tau^2$ for log-normal).
 We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
 \subsection{Senders, Receivers, and Timestamps}\label{subsec:Observed}
-Finally, we choose the actual sender, receivers, and timestamp by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
+Let $a*_d$ be the sender for which the smallest time increment was generated for edge $d$.
+The author generated for document $d$ is  $a*_d$.
+The time increment for edge $d$ set to  $\tau_{a*d}$.
+The vector of receiver indicators for edge $d$ is set to \boldsymbol{u}_{a*d} of all time increments $\tau_{ad}$.
+The sender is set to the sender associated with the minimum time increment.
+The receivers are set to the Finally, we choose the actual sender, receivers, and timestamp by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
 \begin{equation}

### 2018-05-30 paper/ba-HEM/ba-sample.tex
revising generative process

@@
 \subsection{Senders, Receivers, and Timestamps}\label{subsec:Observed}
-Let $a*_d$ be the sender for which the smallest time increment was generated for edge $d$.
-The author generated for document $d$ is  $a*_d$.
-The time increment for edge $d$ set to  $\tau_{a*d}$.
-The vector of receiver indicators for edge $d$ is set to \boldsymbol{u}_{a*d} of all time increments $\tau_{ad}$.
-The sender is set to the sender associated with the minimum time increment.
-The receivers are set to the Finally, we choose the actual sender, receivers, and timestamp by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
+Finally, we choose the actual sender, receivers, and timestamp by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
 \begin{equation}

### 2018-05-30 paper/ba-HEM/ba-sample.tex
revision including diagram, section 2 and new PPE plot

@@
 Many sources of dynamic network data arise as ``hyperedges'' \citep{karypis1999multilevel,ghoshal2009random,zlatic2009hypergraph,zhang2010hypergraph} that include one sender and multiple receivers or one receiver and multiple senders.
-For example, networks formed through the analysis of email \citep{newman2002email} arise with one sender and possibly multiple recipients;  networks formed between neurons via axons and dendrites have one sender and multiple recipients (axons) or one recipient and multiple senders (dendrites) \citep{partzsch2012developing}.
-Networks formed through the analysis of legislative bill cosponsorhip \citep{fowler2006legislative} arise with multiple senders (cosponsors) and one recipient (sponsor); and networks formed through the analysis of economic sanctions \citep{cranmer2014reciprocity} between countries arise with multiple sending countries and one target country.
+For example, networks formed through the analysis of email \citep{newman2002email} arise with one sender and possibly multiple receviers;  networks formed between neurons via axons and dendrites have one sender and multiple receivers (axons) or one receiver and multiple senders (dendrites) \citep{partzsch2012developing}.
+Networks formed through the analysis of legislative bill cosponsorhip \citep{fowler2006legislative} arise with multiple senders (cosponsors) and one receiver (sponsor); and networks formed through the analysis of economic sanctions \citep{cranmer2014reciprocity} between countries arise with multiple sending countries and one target country.
 Existing models require that researchers alter hyperedge data to fit with the pairwise edge structure of the model.
@@
 
-In this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time.
 Data generated under the HEM consists of $D$ unique edges.
-A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of recipients $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
+A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
-While the model can be applied for two types of hyperedges---edges with (1) a single sender and multiple receivers, and (2) multiple senders and a single receiver---here we only present the generative process for those involving a single sender and multiple receivers (i.e., multicast).
-For the latter case---one recipient and multiple senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single recipient.
+While the model can be applied for two types of hyperedges---edges with (1) one sender and one or more receivers, and (2) one or more senders and one receiver---in this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time, specifically for those involving one sender and one or more receivers (i.e., multicast).
+As a part of the generating process, we draw candidate receivers and candidate timestamps for each sender, which are the auxiliary variables in the HEM that serve as candidate data.
+Finally, we generate the observable data from the candidate data by taking the sender who generated the minimum candidate timestamp as an observed sender, the corresponding receivers as observed receivers, and the observed time as the timestamp of previous edge plus the smallest time generated.
+We explain these steps in more detail below.
+For the latter type of hyperedges---one receiver and one or more senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which is analogous to the process used for multicasts.
 
-\subsection{Hypothetical Edges}\label{subsec: Tie}
+\subsection{Candidate Receivers}\label{subsec: Tie}
 For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---an approximate inverse logit of the probability that edge $d$ is being sent from sender $a$ to receiver $r$---as a linear combination of statistics relevant to the receiver selection process:
@@
 
-For each edge $d$ and each sender $a$, the HEM generates a list of hypothetical receivers that would be receivers on edge $d$ if $a$ were the sender.
-For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{th}$ row denotes sender $a$'s receiver vector of indicators---i.e., if node $r$ is the hypothetical receiver of sender $a$, then $u_{adr}=1$; otherwise $u_{adr}=0$.
+A basic assumption of the HEM is that, at any given time, everyone is planning to send a document to one or more receivers.
+So for each edge $d$ and each sender $a$, the HEM draws a list of candidate receivers that would be receivers on edge $d$ if $a$ were the sender.
+For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{th}$ row denotes sender $a$'s receiver vector of zeros and 1's---i.e., 1's imply the willingness of sender $a$ to send an edge to whom.
 We then assume that each receiver vector $\boldsymbol{u}_{ad}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
-In order to avoid generating edges with no receivers, we define a probability measure ``MB$_{G}$" motivated by the Gibbs measure \citep{fellows2017removing}.
+In order to avoid drawing edges with no receivers, we define a probability measure ``MB$_{G}$" motivated by the Gibbs measure \citep{fellows2017removing}.
 The probability measure we define amounts to a non-empty Gibbs measure, in which the all-zero vector is excluded from the support of the multivariate Bernoulli distirbution.
@@
 where $Z(\boldsymbol{\lambda}_{ad})= \prod_{r \neq a} \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
-Again, this is equivalent to assuming ithat each $u_{adr}$ is generated with the probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
+Again, this is equivalent to assuming that each $u_{adr}$ is drawn with the probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
 We provide detailed derivation steps for the normalizing constant in Appendix B.
 
-\subsection{Hypothetical Timestamps}\label{subsec:Time}
-Similarly, for each sender and edge combination, the HEM generates a hypothetical time at which the edge would be generated. The timing rate for sender $a$ and edge $d$ is
+\subsection{Candidate Timestamps}\label{subsec:Time}
+Similarly, for each sender and edge combination, the HEM draws a candidate time at which the edge would be generated. The timing rate for sender $a$ and edge $d$ is
 
@@
 Instead, we assume that each sender's ``time increment"---i.e., waiting time to next interaction since $t_{d-1}$---is drawn from a specific distribution in the exponential family.
-We define the time increment from edge $d-1$ to edge $d$ as $\tau_{d}$ (i.e., $\tau_{d}= t_d-t_{d-1}$) and specify the distribution of hypothetical timestamps with sender-specfic mean $\mu_{ad}$.
+We define the time increment from edge $d-1$ to edge $d$ as $\tau_{d}$ (i.e., $\tau_{d}= t_d-t_{d-1}$) and specify the distribution of candidate timestamps with sender-specfic mean $\mu_{ad}$.
 Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume the mean and variance of the $\tau_{ad}$ satistify
@@
 Possible choices of distribution include exponential, Weibull, gamma, and log-normal\footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
-Based on the specific distribution, there may be a number of latent variables used in the time increment generation beyond the features used to model the rate (e.g., shape parameter $k$ for Weibull, shape parameter $\theta$ for gamma, and variance parameter $\sigma_\tau^2$ for log-normal).
+Based on the specific distribution, we may need another latent variable to draw the time increment beyond the features used to model the rate to account for the variance of time increments $V(\mu)$---e.g., shape parameter $k$ for Weibull, shape parameter $\theta$ for gamma, and variance parameter $\sigma_\tau^2$ for log-normal.
 We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
 \subsection{Senders, Receivers, and Timestamps}\label{subsec:Observed}
-Finally, we choose the actual sender, receivers, and timestamp by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
+Finally, we generate the actual sender, receivers, and timestamp by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
 \begin{equation}
@@
 Therefore, it is a sender-driven process in that the receivers and timestamp of an edge is jointly determined by the sender's urgency to send the edge to chosen receivers.
-Note that our generative process accounts for tied events such that in case of tied events (i.e., multiple senders generated exactly same time increments), we observe all of the tied events without assigning the orders of tied events.
-Algorithm \ref{alg:generative} summarizes the entire generative process for directed edges with one sender and one or more receivers, outlined in this section.
+Note that our generative process accounts for tied events such that in case of tied events (i.e., multiple senders draw exactly same candidate timestamps), we observe all of the tied events without assigning the orders of tied events.
+Algorithm \ref{alg:generative} summarizes the entire generative process for directed edges with one sender and one or more receivers, and Figure \ref{figure:diagram} presents an illustrative example on how the $d$th edge is generated, assuming $t_{d-1} = 0$ for simplicity.
 	\begin{algorithm}[!t]
@@
 			\STATE	set $a_d, \ldots, a_{d+n-1}= \mbox{argmin}_{a}(\tau_{ad})$
-			\STATE	set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n-1}= ,\boldsymbol{u}_{a_{d+n-1} d}$
+			\STATE	set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n-1}=\boldsymbol{u}_{a_{d+n-1} d}$
 			\STATE	set $t_d, \ldots, t_{d+n-1}=t_{d-1} + \min_a\tau_{ad}$
@@
 	\end{algorithm}
+					\begin{figure}[ht]
+						\centering
+						\includegraphics[width=0.625\textwidth]{img/diagram2.png}	
+						\caption {An illustrative example of the generative process of the HEM.}
+						\label{figure:diagram}
+					\end{figure}
+
 \section{Posterior Inference}\label{sec:inference}
-Our inference goal is to invert the generative process to obtain the posterior distribution over the latent variables---hypothetical edges $\{\boldsymbol{u}_d\}_{d=1}^D$, coefficients for edge coavriates $\boldsymbol{b}$, and coefficients for timestamp covariates $\boldsymbol{\eta}$---conditioned on the observed data $\{(a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, covariates $\{(\boldsymbol{x}_d, \boldsymbol{y}_d)\}_{d=1}^D$, and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
+Our inference goal is to invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_d\}_{d=1}^D$, coefficients for edge coavriates $\boldsymbol{b}$, and coefficients for timestamp covariates $\boldsymbol{\eta}$---conditioned on the observed data $\{(a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, covariates $\{(\boldsymbol{x}_d, \boldsymbol{y}_d)\}_{d=1}^D$, and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
 We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each latent variable from its conditional posterior via a Metropolis-within-Gibbs sampling algorithm.
@@
 \subsection{Conditional Posteriors}\label{subsec:conditionaldist}
-\subsubsection{Hypothetical edges}
+\subsubsection{Candidate Receivers}
 In the HEM, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---are not possible.
-However, it is possible to augment the data by hypothetical edges $\boldsymbol{u}$ such that we can obtain their conditional posterior by collapsing the known distributions---$P(\boldsymbol{b}, \boldsymbol{u}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}| \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---through integrating out $\boldsymbol{u}$.
+However, it is possible to augment the data by candidate receivers $\boldsymbol{u}$ such that we can obtain their conditional posterior by collapsing the known distributions---$P(\boldsymbol{b}, \boldsymbol{u}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}| \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---through integrating out $\boldsymbol{u}$.
 We adapt this common tool in Bayesian statistics called ``data augmentation" \citep{tanner1987calculation,neal2015exact}.
@@
 \subsubsection{Coefficients for edge covariates}
-Unlike hypothetical edges above, new values for $\boldsymbol{b}$ cannot be sampled directly from its conditional posterior, but may instead be obtained using the Metropolis--Hastings (M-H) algorithm.
+Unlike the candidate receivers above, new values for $\boldsymbol{b}$ cannot be sampled directly from its conditional posterior, but may instead be obtained using the Metropolis--Hastings (M-H) algorithm.
 Assuming an uninformative prior (i.e., $N({0},\infty)$), the conditional posterior over $\boldsymbol{b}$ is
@@
 \end{equation}
-\subsubsection{Coefficients for timestamp covariates}
-Likewise, we use the M-H algorithm to update the latent variable $\boldsymbol{\eta}$.
-Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for no-tied event case is
-\begin{equation}
-\Pr(\boldsymbol{\eta}| \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
-\label{eqn:latenttime}
-\end{equation}
-where $f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))$ is the probability that the $d^{th}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{a_d d}$, and $\prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d},V(\mu_{a_d d})) \big)$ is the probability that the rest of (unobserved) senders for event $d$ all generated time increments greater than $\tau_d$.
-Moreover, under the existence of tied-event, the conditional posterior of $\boldsymbol{\eta}$ is written as
-\begin{equation}
-\begin{aligned}
-\Pr(\boldsymbol{\eta}| \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, V(\mu_{a_d d})) \\&\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
-\end{aligned}
-\label{eqn:latenttime2}
-\end{equation}
-where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $D$ events ($M \leq D$).
-If $M=D$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
-Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional M-H update---e.g., $\Pr(k| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution.
 \begin{algorithm}[!t]
@@
 \end{algorithm}
+\subsubsection{Coefficients for timestamp covariates}
+Likewise, we use the M-H algorithm to update the latent variable $\boldsymbol{\eta}$.
+Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for no-tied event case is
+\begin{equation}
+\Pr(\boldsymbol{\eta}| \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
+\label{eqn:latenttime}
+\end{equation}
+where $f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))$ is the probability that the $d^{th}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{a_d d}$, and $\prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d},V(\mu_{a_d d})) \big)$ is the probability that the rest of (unobserved) senders for event $d$ all draw time increments greater than $\tau_d$.
+Moreover, under the existence of tied-event, the conditional posterior of $\boldsymbol{\eta}$ is written as
+\begin{equation}
+\begin{aligned}
+\Pr(\boldsymbol{\eta}| \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, V(\mu_{a_d d})) \\&\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
+\end{aligned}
+\label{eqn:latenttime2}
+\end{equation}
+where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $D$ events ($M \leq D$).
+If $M=D$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
+Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional M-H update---e.g., $\Pr(k| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution.
 \subsection{Getting It Right (GiR) Test} \label{subec:GiR}
@@
    \end{itemize}
-
-   To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using log-normal distibution for the time increments $f_\tau$.
-We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
-We also calculated t-test and Mann-Whitney test p-values in order to test for differences in the distributions generated in the forward and backward samples.
-Before we calculated these statistics, we thinned our samples by taking every 9th sample starting at the 10,000th sample for a resulting sample size of 10,000, in order to reduce the autocorrelation in the Markov chains.
-In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
-We depict the GiR results using probability-probability (PP) plots.
-To compare two samples with PP plots we calculate the empirical quantile in each sample of a set of values observed across the two samples, then plot the sets of quantiles in the two samples against each other.
-If the two samples are from equivalent distributions, the quantiles should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
-The GiR test results are depicted in Figure \ref{figure:GiRplot}, which show that we pass the test on every statistic.
-   \begin{figure}[H]
+   \begin{figure}[!t]
    	\centering
@@
    \end{figure}   
+   To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using log-normal distibution for the time increments $f_\tau$.
+We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
+We also calculated t-test and Mann-Whitney test p-values in order to test for differences in the distributions generated in the forward and backward samples.
+Before we calculated these statistics, we thinned our samples by taking every 9th sample starting at the 10,000th sample for a resulting sample size of 10,000, in order to reduce the autocorrelation in the Markov chains.
+In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
+We depict the GiR results using probability-probability (PP) plots.
+To compare two samples with PP plots we calculate the empirical quantile in each sample of a set of values observed across the two samples, then plot the sets of quantiles in the two samples against each other.
+If the two samples are from equivalent distributions, the quantiles should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
+The GiR test results are depicted in Figure \ref{figure:GiRplot}, which show that we pass the test on every statistic.
+
  	   \section{Application to Email Data}\label{sec:Emails}
@@
 	\end{algorithm}     \fi  
-
-	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using log-normal distribution, which shows better performance in Section \ref{subsec:Experiment_email}.
-Upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic data, where the left one for outdegree statistic and the right plot is for indegree statistic.
-For both plots, the x-axis represents the nodes ($A=1,\ldots,18$), and the y-axis represents the number of emails sent or received by the node.
-When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes.
-For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, showing acceptable fit to the data.
-Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
-Since we use more information in the receiver selection process (i.e., network effects) while we rely solely on minimum time increments when choosing the observed sender, these results are expected.
-Lower left plot is the distribution of receiver sizes, where the x-axis spans over the size of receivers 1 to 14 (which is the maximum size of observed receivers) and the y-axis denotes the number of emails with x-number of receivers.
-The result shows that our model is underestimating emails with one receiver while overestimating emails with two, three, and four receivers.
-One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the emails with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right.
-To improve the goodness of fit for receiver sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
-In the end, the plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions---one for simulated time increments and another for observed time increments---against each other in order to assess how closely two data sets agree.
-Here, the closeness to the diagonal line connecting $(0, 0)$ and $(1, 1)$ gives a measure of difference between the simulated and observed time increments, and our PP plot shows that we have great performance in reproducing the observed time distribution.
-All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are attached in Appendix C.
 	\begin{figure}[!t]
@@
 
+	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using log-normal distribution, which shows better performance in Section \ref{subsec:Experiment_email}.
+Upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic data, where the left one for outdegree statistic and the right plot is for indegree statistic.
+For both plots, the x-axis represents the nodes ($A=1,\ldots,18$), and the y-axis represents the number of emails sent or received by the node.
+When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes.
+For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, showing acceptable fit to the data.
+Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
+Since we use more information in the receiver selection process (i.e., network effects) while we rely solely on minimum time increments when choosing the observed sender, these results are expected.
+Lower left plot is the distribution of receiver sizes, where the x-axis spans over the size of receivers 1 to 14 (which is the maximum size of observed receivers) and the y-axis denotes the number of emails with x-number of receivers.
+The result shows that our model is underestimating emails with one receiver while overestimating emails with two, three, and four receivers.
+One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the emails with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right.
+To improve the goodness of fit for receiver sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
+In the end, the plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions---one for simulated time increments and another for observed time increments---against each other in order to assess how closely two data sets agree.
+Here, the closeness to the diagonal line connecting $(0, 0)$ and $(1, 1)$ gives a measure of difference between the simulated and observed time increments, and our PP plot shows that we have great performance in reproducing the observed time distribution.
+All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are attached in Appendix C.
+
 	\subsection{Exploratory Analysis}\label{subsec:Result_email}
@@
 	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$, where Figure \ref{figure:betaresults} (a) displays the coefficients for nodal covariates and \ref{figure:betaresults} (b) displays the coefficients for dyadic and triadic covariates.
-Since we use the logit probability of $\lambda_{adr}$ when generating hypothetical edges in Section \ref{subsec: Tie}, we assume that
+Since we use the logit probability of $\lambda_{adr}$ when generating candidate receivers in Section \ref{subsec: Tie}, we assume that
 	\begin{equation*}
@@
 	\end{equation*}
+	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14})$.
+	To begin with, we find out that the effect of nodal coavariates ``gender of sender" and ``gender of receiver" are both significant in negative direction.
+\textbf{substantive interpretation on gender effects}.
+Next, the statistic ``outdegree" also has significantly negative effect---i.e., if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$---possibly due to its multicollinearity with the statistics ``hyperedge size" where the two terms' show significant interaction effect.
+This result is likely to appear under the following scenario: if sender $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of ``send") and the email of interest is not a  2) broadcast email which is originally aimed at large number of receivers (excluding the effect of ``hyperedge size"), then sender $a$ is less likely to send an email to receiver $r$.
+Similar interpretation can be applied for the covariates ``indegree," but in the opposite direction.
+For example, if the receiver $r$ received $n$ number of emails over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $r$.
+
+	When we look at the effects of dyadic and triadic covariates, one thing we can check is that the effect of statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) is significant and positive with $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
+Another dyadic statistic ``receive" is not statistically significant in that its 95\% credible interval do not include 0.
+Surprisingly, none of the covariates for triadic network effects seem to have significant effect on the generative process of edges.
 			\begin{figure}[!t]
@@
 			\end{figure}
-	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14})$.
-	To begin with, we find out that the effect of nodal coavariates ``gender of sender" and ``gender of receiver" are both significant in negative direction.
-\textbf{substantive interpretation on gender effects}.
-Next, the statistic ``outdegree" also has significantly negative effect---i.e., if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$---possibly due to its multicollinearity with the statistics ``hyperedge size" where the two terms' show significant interaction effect.
-This result is likely to appear under the following scenario: if sender $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of ``send") and the email of interest is not a  2) broadcast email which is originally aimed at large number of receivers (excluding the effect of ``hyperedge size"), then sender $a$ is less likely to send an email to receiver $r$.
-Similar interpretation can be applied for the covariates ``indegree," but in the opposite direction.
-For example, if the receiver $r$ received $n$ number of emails over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $r$.
 
-	When we look at the effects of dyadic and triadic covariates, one thing we can check is that the effect of statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) is significant and positive with $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
-Another dyadic statistic ``receive" is not statistically significant in that its 95\% credible interval do not include 0.
-Surprisingly, none of the covariates for triadic network effects seem to have significant effect on the generative process of edges.
 \subsubsection{Coefficients for timestamp covariates}
@@
 	\end{equation*}
+	To begin with, the posterior estimates of two temporal effects---``weekend" and ``PM"---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after midday, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+On the contrary, the covariates ``manager", ``outdegree", and ``indegree" turn out to shorten the amount of time to next email.
+For example, being a county manager (i.e., the manager of department managers) lowers the expected value of $\log(\tau_{ad})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
+This argument is also supported by the posterior estimates for ``outdegree" and ``indegree" statistics, where the estimated coefficients are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
+Gender of the department manager is shown to have no significant effect on time increments.
+In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists large variability in the time increments of emails.
 				\begin{figure}[!t]
@@
 				\end{figure}	
-	To begin with, the posterior estimates of two temporal effects---``weekend" and ``PM"---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after midday, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
-On the contrary, the covariates ``manager", ``outdegree", and ``indegree" turn out to shorten the amount of time to next email.
-For example, being a county manager (i.e., the manager of department managers) lowers the expected value of $\log(\tau_{ad})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
-This argument is also supported by the posterior estimates for ``outdegree" and ``indegree" statistics, where the estimated coefficients are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
-Gender of the department manager is shown to have no significant effect on time increments.
-In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists large variability in the time increments of emails.
 \section{Conclusion}\label{sec:conclusion}
@@
 				\STATE	set ${r}_d=\mbox{argmin}_{r}(\tau_{rd})$
-				\STATE	set $\boldsymbol{a}_d=\boldsymbol{u}_{r_d d},\ldots,\boldsymbol{a}_{d+n-1}= ,\boldsymbol{u}_{r_{d+n-1} d}$
+				\STATE	set $\boldsymbol{a}_d=\boldsymbol{u}_{r_d d},\ldots,\boldsymbol{a}_{d+n-1}=\boldsymbol{u}_{r_{d+n-1} d}$
 				\STATE	set $t_d, \ldots, t_{d+n-1}=t_{d-1} + \min_r\tau_{rd}$
@@
 	\end{equation*}
-\newpage
 	\subsection*{Appendix C: Comparison of PPC Results: log-normal vs. exponential}\label{appendix: PPCexp}

### 2018-05-30 Emails/PPEnew.R

@@ -147,6 +147,20 @@ stats = boxplot.stats(time$value)$stats
 colnames(time)[3] = "MdAPE"
 p[[3]]=ggplot(data = time, aes(x = Dist, y = MdAPE, fill = Dist))+geom_boxplot()+theme(legend.position = "bottom")+ylab("log(MdAPE)")+theme(plot.title = element_blank(),text = element_text(size = rel(5.5)),legend.position="none")
 
+#######################
+truetime = sapply(Montgomery_PPE$timemissing, function(d) edge[[d]]$t_d-edge[[d-1]]$t_d)/3600
+predtime = Montgomery_PPE$timepredict
+predtime2 = Montgomery_PPE2$timepredict
+
+time = data.frame(MdAPE = sapply(1:62, function(d) median(abs((predtime[d,]-truetime[d])/truetime[d]))), Dist = rep("log-normal", 62))
+time = rbind(time, data.frame(MdAPE = sapply(1:62, function(d) median(abs((predtime2[d,]-truetime[d])/truetime[d]))), Dist = rep("exponential", 62)))
+time = melt(time)
+stats = boxplot.stats(time$value)$stats
+
+colnames(time)[3] = "MdAPE"
+p[[3]]=ggplot(data = time, aes(x = Dist, y = MdAPE, fill = Dist))+geom_boxplot()+theme(legend.position = "bottom")+theme(plot.title = element_blank(),text = element_text(size = rel(5.5)),legend.position="none")+scale_y_continuous(trans = "log", breaks = trans_breaks("log", function(x) exp(x)), labels = scientific)
+
+
 
 ggplot(data = time, aes(x = MdAPE, fill = dist))+geom_histogram(position = "dodge")+theme(plot.title = element_blank(),text = element_text(size = rel(5.5)),legend.position="none")
 

### 2018-05-30 paper/ba-HEM/ba-sample.tex
revision including diagram, section 2 and new PPE plot

@@
 
+In this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time.
 Data generated under the HEM consists of $D$ unique edges.
@@
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
-While the model can be applied for two types of hyperedges---edges with (1) one sender and one or more receivers, and (2) one or more senders and one receiver---in this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time, specifically for those involving one sender and one or more receivers (i.e., multicast).
+While the model can be applied for two types of hyperedges---edges with (1) one sender and one or more receivers, and (2) one or more senders and one receiver---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast).
 As a part of the generating process, we draw candidate receivers and candidate timestamps for each sender, which are the auxiliary variables in the HEM that serve as candidate data.

### 2018-06-01 paper/ba-HEM/ba-sample.tex
through the generative process

@@
 While the model can be applied for two types of hyperedges---edges with (1) one sender and one or more receivers, and (2) one or more senders and one receiver---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast).
-As a part of the generating process, we draw candidate receivers and candidate timestamps for each sender, which are the auxiliary variables in the HEM that serve as candidate data.
-Finally, we generate the observable data from the candidate data by taking the sender who generated the minimum candidate timestamp as an observed sender, the corresponding receivers as observed receivers, and the observed time as the timestamp of previous edge plus the smallest time generated.
+One notable feature of the HEM generative process is that we draw auxiliary variables that serve as candidate data.
+Data is generated from the HEM through a sampling process applied to the auxiliary variables.
+The auxiliary variables drawn for edge $d$ include, for each sender $a$, a time increment from edge $d-1$ at which sender $a$ would send edge $d$, and an $A-1$ length vector indicating which nodes would receive edge $d$ if it were sent by sender $a$.
+The data generated for edge $d$ under the HEM corresponds to the sender that would send edge $d$ the soonest---at the smallest time increment from edge $d-1$.
+The receivers of edge $d$ generated under the HEM correspond to those receivers to which the sender with the minimum time increment would have sent edge $d$.
 We explain these steps in more detail below.
-For the latter type of hyperedges---one receiver and one or more senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which is analogous to the process used for multicasts.
+For hyperedges that involve one receiver and one or more senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).
 
 \subsection{Candidate Receivers}\label{subsec: Tie}
-For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---an approximate inverse logit of the probability that edge $d$ is being sent from sender $a$ to receiver $r$---as a linear combination of statistics relevant to the receiver selection process:
+For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---an approximate logit of the probability that edge $d$ is being sent from sender $a$ to receiver $r$---as a linear combination of statistics relevant to the receiver selection process:
 \begin{equation}
@@
 So for each edge $d$ and each sender $a$, the HEM draws a list of candidate receivers that would be receivers on edge $d$ if $a$ were the sender.
-For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{th}$ row denotes sender $a$'s receiver vector of zeros and 1's---i.e., 1's imply the willingness of sender $a$ to send an edge to whom.
+For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{th}$ row denotes sender $a$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $a$ intends to send edge $d$.
 We then assume that each receiver vector $\boldsymbol{u}_{ad}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
 In order to avoid drawing edges with no receivers, we define a probability measure ``MB$_{G}$" motivated by the Gibbs measure \citep{fellows2017removing}.
-The probability measure we define amounts to a non-empty Gibbs measure, in which the all-zero vector is excluded from the support of the multivariate Bernoulli distirbution.
-As a result, this measure helps us to 1) allow a sender to select multiple receiver for a single edge, 2) force the sender to select at least one receiver, and 3) ensure a tractable normalizing constant.
+The probability measure we define amounts to a non-empty Gibbs measure, in which the all-zero vector is excluded from the support of the multivariate Bernoulli distribution.
+As a result, this measure helps us to 1) allow a sender to select multiple receivers for a single edge, 2) force the sender to select at least one receiver, and 3) ensure a tractable normalizing constant for the receiver selection distribution.
 To be specific, we draw a binary vector $\boldsymbol{u}_{ad}= (u_{ad1},
@@
 where $Z(\boldsymbol{\lambda}_{ad})= \prod_{r \neq a} \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
-Again, this is equivalent to assuming that each $u_{adr}$ is drawn with the probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
+Again, this is approximately equivalent to assuming that each $u_{adr}$ is drawn with the probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
 We provide detailed derivation steps for the normalizing constant in Appendix B.
@@
 \subsection{Candidate Timestamps}\label{subsec:Time}
-Similarly, for each sender and edge combination, the HEM draws a candidate time at which the edge would be generated. The timing rate for sender $a$ and edge $d$ is
+Similarly, for each sender and edge combination, the HEM draws a candidate time at which the edge would be sent. The timing rate for sender $a$ and edge $d$ is
 
@@
 Possible choices of distribution include exponential, Weibull, gamma, and log-normal\footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
-Based on the specific distribution, we may need another latent variable to draw the time increment beyond the features used to model the rate to account for the variance of time increments $V(\mu)$---e.g., shape parameter $k$ for Weibull, shape parameter $\theta$ for gamma, and variance parameter $\sigma_\tau^2$ for log-normal.
+Based on the specific distribution, we may need other latent variables to draw the time increment, to account for the variance of time increments, beyond the coefficients for the features used to model the rate.
+$V(\mu)$---e.g., the shape parameter $k$ for the Weibull, the shape parameter $\theta$ for the gamma, and the variance parameter $\sigma_\tau^2$ for the log-normal.
 We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
 \subsection{Senders, Receivers, and Timestamps}\label{subsec:Observed}
-Finally, we generate the actual sender, receivers, and timestamp by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
+Finally, under the HEM the observed sender, receivers, and timestamp of edge $d$ is generated by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
 \begin{equation}
@@
 \end{equation}
-Therefore, it is a sender-driven process in that the receivers and timestamp of an edge is jointly determined by the sender's urgency to send the edge to chosen receivers.
+Therefore, it is a sender-driven process in that the receivers and timestamps of an edge are jointly determined by the sender's urgency to send the edge to the selected receivers.
 Note that our generative process accounts for tied events such that in case of tied events (i.e., multiple senders draw exactly same candidate timestamps), we observe all of the tied events without assigning the orders of tied events.

### 2018-06-01 paper/ba-HEM/ba-sample.tex
finished revisions

@@
 \section{Posterior Inference}\label{sec:inference}
-Our inference goal is to invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_d\}_{d=1}^D$, coefficients for edge coavriates $\boldsymbol{b}$, and coefficients for timestamp covariates $\boldsymbol{\eta}$---conditioned on the observed data $\{(a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, covariates $\{(\boldsymbol{x}_d, \boldsymbol{y}_d)\}_{d=1}^D$, and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
+In this section we describe how we invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_d\}_{d=1}^D$, coefficients for edge covariates $\boldsymbol{b}$, and coefficients for timestamp covariates $\boldsymbol{\eta}$---conditioned on the observed data $\{(a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, covariates $\{(\boldsymbol{x}_d, \boldsymbol{y}_d)\}_{d=1}^D$, and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
 We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each latent variable from its conditional posterior via a Metropolis-within-Gibbs sampling algorithm.
-In this section, we provide each latent variable's conditional posterior, and demonstrate how we perform the prior-posterior simulator test of \cite{geweke2004getting} for the HEM.
+In this section, we provide each latent variable's conditional posterior, and demonstrate how we perform the prior-posterior simulator test of \cite{geweke2004getting}, in which we evaluate the integrity of both our mathematical derivations and the sampling code, for the HEM.
 At the end of this section, we provide the pseudocode of our MCMC algorithm in Algorithm \ref{alg:MCMC}.
@@
 \subsubsection{Candidate Receivers}
-In the HEM, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---are not possible.
+In the HEM, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
 However, it is possible to augment the data by candidate receivers $\boldsymbol{u}$ such that we can obtain their conditional posterior by collapsing the known distributions---$P(\boldsymbol{b}, \boldsymbol{u}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}| \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---through integrating out $\boldsymbol{u}$.
@@
 Likewise, we use the M-H algorithm to update the latent variable $\boldsymbol{\eta}$.
-Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for no-tied event case is
+Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for an untied event case is
 \begin{equation}
@@
 where $f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))$ is the probability that the $d^{th}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{a_d d}$, and $\prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d},V(\mu_{a_d d})) \big)$ is the probability that the rest of (unobserved) senders for event $d$ all draw time increments greater than $\tau_d$.
-Moreover, under the existence of tied-event, the conditional posterior of $\boldsymbol{\eta}$ is written as
+Moreover, under the existence of tied events, the conditional posterior of $\boldsymbol{\eta}$ is written as
 \begin{equation}
@@
 The forward sampler draws unobservable variables from the prior and then generates the observable data conditional on the unobservables.
-The backward sampler alternates between the inference and an observables simulator, by running the inference code on observable data to obtain posterior estimates of the unobervable variables and then re-generating the observables given the inferred unobservables.
+The backward sampler alternates between the inference and an observables simulator by running the inference code on observable data to obtain posterior estimates of the unobservable variables and then re-generating the observables given the inferred unobservables.
 The backward sampler is initialized by running an iteration of inference on observables drawn directly from the prior.
@@
 In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
-We depict the GiR results using probability-probability (PP) plots.
-To compare two samples with PP plots we calculate the empirical quantile in each sample of a set of values observed across the two samples, then plot the sets of quantiles in the two samples against each other.
-If the two samples are from equivalent distributions, the quantiles should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
-The GiR test results are depicted in Figure \ref{figure:GiRplot}, which show that we pass the test on every statistic.
+We depict the GiR results using probability-probability (PP) plots, in which the empirical CDF values of the forward and backward samples are plotted on the $x$ and $y$ axes, respectively.
+If the two samples are from equivalent distributions, the empirical CDF values should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
+The GiR test results are depicted in Figure \ref{figure:GiRplot}.
+These results indicate that our sampling equations and software implementation pass the test on every statistic.
 
@@
  	   Our data come from the North Carolina county government email dataset collected by \cite{ben2017transparency} that includes internal email corpora covering the inboxes and outboxes of managerial-level employees of North Carolina county governments.
-Out of over twenty counties, we chose Montgomery County to 1) test our model using data with large proportion of hyperedges (16.76\%), all of which are emails sent from one sender to two or more receivers, and 2) limit the scope of this initial application.
-To summarize, Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
+Out of over twenty counties, we chose Montgomery County to 1) test our model using data with a large proportion of hyperedges (16.76\%), all of which are emails sent from one sender to two or more receivers, and 2) limit the scope of this initial application.
+The Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
 For this case study,
- 	   we formulate the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$ and ground them in illustrative examples.
-We then report a suite of experiments---out-of-sample prediction for model selection and posterior predictive checks---that test the HEM's ability to form the posterior distribution over its latent variables.
-Finally, we demonstrate an exploratory analysis of Montgomery County email data using the model estimates to discover interesting patterns in organizational communication networks.
+ 	   we formulate a HEM specification through definitions of the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$.
+We then report a suite of experiments---out-of-sample prediction for model selection and posterior predictive checks---that illustrate how alternative formulations of the HEM can be compared, and evaluate how well the HEM recovers the distribution of the observed data.
+Finally, we demonstrate an exploratory analysis of Montgomery County email data using the model estimates to discover substantively meaningful patterns in organizational communication networks.
  	   \subsection{Covariates}\label{subsec:Covariates_email}
  	   \subsubsection{Edge covariates}
- 	   Given a set of network data, a primary modeling goal of the generative process for edges lies in determining which characteristics and behaviors are predictive of the receiver selection.
-This email application specifically give rise to the following question: ``To what extent are nodal, dyadic or triadic network effects relevant to predicting future emails?" As an illustrative example, we form the receiver selection features $\boldsymbol{x}$ for Montgomery County email data using some nodal, dyadic, and triadic covariates.
-First, as we want to test whether gender plays a role in receiver selection process, we include three nodal covariates---the gender information of sender and receiver, and their homophily indicator.
-Additionally, we include four interval-based nodal network covariates---outdegree of sender, indegree of receiver, hyperedge size of sender, and the interaction between outdegree and hyperedge size---to study the effect of nodal behaviors on future interactions.
+ 	   A primary purpose of any network model is to use the posterior distributions to learn which features predict and/or explain edge formation (e.g., is edge formation reciprocal, are edges more likely to be formed among nodes with the same gender).
+This email application specifically give rise to the following question: ``To what extent are nodal, dyadic or triadic network effects relevant to predicting future emails?" As an illustrative example, we form the receiver selection features $\boldsymbol{x}$ for Montgomery County email data using nodal, dyadic, and triadic covariates.
+First, as we want to test whether gender plays a role in receiver selection process, we include three nodal covariates---the gender information of sender and receiver, and their homophily indicator (i.e., an indicator of whether the sender and receiver are of the same gender).
+Additionally, we include four interval-based nodal network covariates---outdegree of sender (i.e., the number of edges sent), indegree of receiver (the number of edges received), hyperedge size of sender (i.e., the number of total receivers of edges from the sender), and the interaction between (i.e., scalar product of) outdegree and hyperedge size---to study the effect of nodal behaviors on future interactions.
 For dyadic and triadic network effects, we employ the network statistics in \cite{PerryWolfe2012} and summarize past interaction behaviors based on the time interval prior to and including $t_{d-1}$.
@@
  	   where $I(\cdot)$ is an indicator function.
-The network statistics (5--14) are designed so that their coefficient have a straightforward interpretation.
-The statistics ``outdegree" and ``indegree" measures the gregariousness and popularity effect of the node by counting the number of emails sent from $a$ and received by $r$, respectively, within the last 7 days.
+The network statistics (5--14) are designed so that their coefficients have a straightforward interpretations.
+The statistics ``outdegree" and ``indegree" measure the gregariousness and popularity effects of the node by counting the number of emails sent from $a$ and received by $r$, respectively, within the last 7 days.
+The gregariousness effect refers to the tendency for nodes that sent many edges in the past to continue to do so in the future.
+The popularity effect refers to the tendency for nodes that received many edges in the past to continue to do so in the future.
 Moreover, in order to capture individual tendency of send emails to two or more receivers, we include the statistic ``hyperedge size"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of receivers are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
 We also include the interaction term between outdegree and hyperedge size.
+This interaction allows us to model a possible tradeoff between the hyperedge size and the total number of edges sent.
 Dyadic statistics``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
 In the example of triadic statistics, the covariate ``2-send" counts the pairs of emails involving some node $h$ distinct from $a$ and $r$ such that emails from $a$ to $h$ and $h$ to $r$ are both observed within the last 7 days.
-Other triadic covariates behave similarly, and their interpretations are also analogous, which are illustrated in Figure \ref{figure:netstats}.
+The 2-send statistic captures the tendency for emails to close transitive triads (i.e., triads in which $a$ sends to $r$ and $h$, and $r$ sends to $h$).
+We include other triadic covariates that behave similarly and exhibit analogous interpretations, which are illustrated in Figure \ref{figure:netstats}.
  	   \begin{figure}[!t]
@@
  	    	   \subsubsection{Timestamp covariates}
- 	   For the event timing features $\boldsymbol{y}$ introduced in Section \ref{subsec:Time}, we identify a set of covariates which may possibly effect ``time to the next email." Similar to the edge covariates, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
+ 	   For the event timing features $\boldsymbol{y}$ introduced in Section \ref{subsec:Time}, we identify a set of covariates which may effect ``time to the next email." Similar to the edge covariates, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
 In addition, we select some edge-specific covariates based on the temporal aspect of the $(d-1)^{th}$ email---e.g., whether the previous email was sent (1) during the weekend and (2) before or past midday (AM/PM)---since we expect the email interactions within county government to be less active during the weekend and in the evening.
@@
  	   \end{itemize}
- 	   Note that our generative process for timestamps in Section \ref{subsec:Time} is sender-orientd process where the sender deterimes ``when to send the email," thus we incorporate network statistics that depends on $a$ only---outdegree of sender $a$ and indegree of sender $a$ (not $r$ this time).
+ 	   Note that our generative process for timestamps in Section \ref{subsec:Time} is sender-oriented where the sender deterimes when to send the email, thus we incorporate network statistics that depends on $a$ only---outdegree of sender $a$ and indegree of sender $a$.
 
@@
 Here, we specifically compare the predictive performance from two distributions---log-normal and exponential.
-We particularly choose the log-normal distribution based on some exploratory analysis (e.g., histogram and simple regressions) on raw time increments data, and take exponential distribution as an alternative since exponential is the most commonly specified distribution for time-to-event data which is also used in the stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
+We particularly choose the log-normal distribution based on some exploratory analysis (e.g., histogram and simple regressions) on raw time increments data, and take exponential distribution as an alternative since exponential is the most commonly specified distribution for time-to-event data, and is also used in the stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
 	\begin{algorithm}[!t]
@@
 	We evaluate the model's ability to predict edges and timestamps from Montgomery County email data, conditioned on their ``training" part of the data.
-To perform the experiment, we separately formed a test split of each three model components---sender, receivers, and timestamps---by randomly selecting ``test" data with probability $p=0.1$.
-Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, model estimates, and current values of test data.
+To perform the experiment, we separately formed a test split of each three model components---sender, receivers, and timestamps---by randomly selecting ``test" data with probability $p=0.10$, and setting the test data to missing.
+Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, model estimates, and current values of imputed test data.
 We then run inference to update the latent variables given the imputed and observed data.
-We iterate the two steps---imputation and inference---multiple times to obtain enough number of estimates for test data.
+We iterate the two steps---imputation and inference---multiple times to obtain posterior samples of the held out test data.
 Algorithm \ref{alg:PPE} outlines this procedure in detail.
@@
 We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
-First, we compare the posterior probability of correct senders for each of missing emails $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
-We call this measure as ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails.
+First, we compare the posterior probability of correct senders for each of the missing emails $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
+We call this measure the ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails.
 The results show that both log-normal and exponential distributions acheive better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing higher performance than exponential distribution.
@@
 This difference can be explained by overdispersion in exponential distribution, because there exists greater variability in the time increments of emails than would be expected under exponential distribution.
-As illustrated above, we can use this out-of-sample prediction task for two usage---1) provide an effective answer to the question ``how are we filling in the missing components of time-stamped network data?" and 2) offer one standard way to determine the distribution of time increments in Section \ref{subsec:Time}.
+As illustrated above, we can use this out-of-sample prediction task for two uses---1) to provide an effective answer to the question ``how does the HEM perform at filling in the missing components of time-stamped network data?" and 2) to offer one standard way to determine the distribution of time increments in Section \ref{subsec:Time}.
 
@@
 In this section, we perform posterior predictive checks (PPC) \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for Montgomery County email data.
-We formally generated entirely new data, by simulating $N=500$ synthetic email data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the genenerative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}\iffalse, where the pseudocode is outlined in Algorithm \ref{alg:PPC}\fi.
-For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution, indegree distribution, receiver size distribution, and probability-probability (PP) plot for time increments.
+We formally generated entirely new data by simulating $N=500$ synthetic email datasets $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the generative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}\iffalse, where the pseudocode is outlined in Algorithm \ref{alg:PPC}\fi.
+For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution---the number of edges sent by each node, indegree distribution---the number of edges received by each node, receiver size distribution---the number of receivers on each edge, and a probability-probability (PP) plot for time increments.
 \iffalse
@@
 
-	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using log-normal distribution, which shows better performance in Section \ref{subsec:Experiment_email}.
-Upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic data, where the left one for outdegree statistic and the right plot is for indegree statistic.
+	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using the log-normal distribution, which shows better performance in Section \ref{subsec:Experiment_email}.
+The upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic samples, where the left one for outdegree statistic and the right plot is for indegree statistic.
 For both plots, the x-axis represents the nodes ($A=1,\ldots,18$), and the y-axis represents the number of emails sent or received by the node.
@@
 Since we use more information in the receiver selection process (i.e., network effects) while we rely solely on minimum time increments when choosing the observed sender, these results are expected.
-Lower left plot is the distribution of receiver sizes, where the x-axis spans over the size of receivers 1 to 14 (which is the maximum size of observed receivers) and the y-axis denotes the number of emails with x-number of receivers.
+The lower left plot is the distribution of receiver sizes, where the x-axis spans over the size of receivers 1 to 14 (which is the maximum size of observed receivers) and the y-axis denotes the number of emails with x-number of receivers.
 The result shows that our model is underestimating emails with one receiver while overestimating emails with two, three, and four receivers.
 One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the emails with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right.
-To improve the goodness of fit for receiver sizes, we can add more covariates (e.g., sender indicators) or assign strong prior structure on $b_1$.
-In the end, the plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions---one for simulated time increments and another for observed time increments---against each other in order to assess how closely two data sets agree.
+It would be an interesting problem in future research to consider how the hyperedge size distribution can be further modified to capture this distribution more accurately.
+The plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions---one for simulated time increments and another for observed time increments---against each other in order to assess how closely two data sets agree.
 Here, the closeness to the diagonal line connecting $(0, 0)$ and $(1, 1)$ gives a measure of difference between the simulated and observed time increments, and our PP plot shows that we have great performance in reproducing the observed time distribution.
-All our findings from predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are attached in Appendix C.
+Our findings from the predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are presented in Appendix C.
 
 	\subsection{Exploratory Analysis}\label{subsec:Result_email}
-	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we choose to analyze Montgomery county email data and interpret the results using log-normal distribution.
+	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we interpret the results from the HEM using the log-normal distribution.
 We assume weakly informative priors for latent variables such as $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b=\boldsymbol{0}, \Sigma_b = 2\times I_P)$, $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta=\boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, and $\sigma_\tau^2 \sim \mbox{inverse-Gamma}(a=2, b=1)$, and run MCMC algorithm in Algorithm \ref{alg:MCMC} with $O=55,000$ outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
@@
 	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$, where Figure \ref{figure:betaresults} (a) displays the coefficients for nodal covariates and \ref{figure:betaresults} (b) displays the coefficients for dyadic and triadic covariates.
-Since we use the logit probability of $\lambda_{adr}$ when generating candidate receivers in Section \ref{subsec: Tie}, we assume that
+Since we use the logit functional form
 	\begin{equation*}
@@
 	\end{equation*}
-	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratio $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14})$.
-	To begin with, we find out that the effect of nodal coavariates ``gender of sender" and ``gender of receiver" are both significant in negative direction.
-\textbf{substantive interpretation on gender effects}.
-Next, the statistic ``outdegree" also has significantly negative effect---i.e., if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$---possibly due to its multicollinearity with the statistics ``hyperedge size" where the two terms' show significant interaction effect.
-This result is likely to appear under the following scenario: if sender $a$ sent large number of emails over the last week but 1) not to $r$ (excluding the effect of ``send") and the email of interest is not a  2) broadcast email which is originally aimed at large number of receivers (excluding the effect of ``hyperedge size"), then sender $a$ is less likely to send an email to receiver $r$.
-Similar interpretation can be applied for the covariates ``indegree," but in the opposite direction.
-For example, if the receiver $r$ received $n$ number of emails over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $r$.
+	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratios $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14})$.
+	We find the effects of nodal coavariates ``gender of sender" and ``gender of receiver" are both nearly always negative in the posterior samples.
+The log odds that any other node will be added as a receiver of an email is approximately 0.5 less if the sender is a woman.
+The posterior distribution of the statistic ``outdegree" is mostly negative, if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$.
+However, this straightforward interpretation of the outdegree statistic only applies when the hyperedge size is low.
+The scenario in which a sender sends a lot of low-hyperedge-size emails may arise due to the use of email for a one-on-one conversation.
+The large positive estimates of the interaction between hyperedge size and outdegree indicate that those who have recently sent many emails with many receivers on each email are likely to continue sending these ``broadcast'' style emails.
+This scenario may arise from someone being responsible for distributing timely announcements.
+When we look at the effect of ``indegree," we see a clear popularity effect---those who have received a lot of emails a lot recently are likely to continue receiving a lot of emails.
+If the receiver $r$ received $n$ number of emails over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $r$.
 
-	When we look at the effects of dyadic and triadic covariates, one thing we can check is that the effect of statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) is significant and positive with $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
-Another dyadic statistic ``receive" is not statistically significant in that its 95\% credible interval do not include 0.
-Surprisingly, none of the covariates for triadic network effects seem to have significant effect on the generative process of edges.
+	When we look at the effects of dyadic and triadic covariates, one thing that stands out is the large and positive posterior distribution of the statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) with the posterior mean $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
+The posterior distributions for the reciprocity effect (receive), and the four triadic effects, are all fairly evenly spread around zero, so our results do not justify conclusions regarding the nature of these effects in the Montgomery county email network.
 			\begin{figure}[!t]
@@
 Note that interpretations of the estimated coefficients for $\hat{\boldsymbol{\eta}}$ should be based on the specified timeunit of the datset, which we use ``hour" for Montgomery county email data.
-Moreover, since we assume log-normal distribution for time increments, we need careful interpretation regarding the timing equations
+Moreover, since we assume log-normal distribution for time increments, the coefficients are interpreted in terms of the change in the average log time.
 	\begin{equation*}
@@
 	\end{equation*}
-	To begin with, the posterior estimates of two temporal effects---``weekend" and ``PM"---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after midday, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
-On the contrary, the covariates ``manager", ``outdegree", and ``indegree" turn out to shorten the amount of time to next email.
-For example, being a county manager (i.e., the manager of department managers) lowers the expected value of $\log(\tau_{ad})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
-This argument is also supported by the posterior estimates for ``outdegree" and ``indegree" statistics, where the estimated coefficients are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
-Gender of the department manager is shown to have no significant effect on time increments.
-In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists large variability in the time increments of emails.
+	The posterior estimates of two temporal effects---``weekend" and ``PM"---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after midday, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+On the contrary, the covariates ``manager", ``outdegree", and ``indegree"  shorten the amount of time to next email.
+For example, being a county manager (i.e., the lead county administrator) lowers the expected value of $\log(\tau_{ad})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
+The posterior estimates for the  ``outdegree" and ``indegree" statistics, where the posterior means are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
+These effects indicate that those who are involved in either sending or receiving a lot of emails recently are likely to send emails with greater speed.
+The posterior distribution for the effect of the gender of the manager is pretty evenly spread around zero.
+In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in the lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists large variability in the time increments of emails.
 				\begin{figure}[!t]
@@
 Motivated by a growing class of dynamic network models which deal with edges exchanged in continuous time, the hyperedge event model (HEM) can effectively learn the underlying dynamics in edge and timestamp formations, providing novel insights to the literature.
-First, we explicitly model hyperedges by deriving a receiver-selection distribution that forces the sender to select at least one recevier, which is more realistic approach for events with one sender and one or more receivers and one or more sender and one receiver compared to treating them as pure duplicates.
+The HEM explicitly models hyperedges through a receiver-selection distribution that forces the sender to select at least one recevier, which is a more realistic approach for events with one sender and one or more receivers and one or more sender and one receiver compared to treating them as pure duplicates.
 In modeling the timestamps (more precisely time increments) of events, our generalized linear model (GLM) based formulation offers new innovations by eliminating the need to stick with one parameter distribution (e.g., exponential distribution).
-To make better use of the proposed model, we provide an algorithm for predictive experiment that helps to learn which distribution better fits the data.
-To sum, the HEM's flexible generative process thus leads to more accurate and precise inference on model parameters.
+To our knowledge, the HEM is the only existing model that can be used to generate the sender, recipients, and time stamp of interactions in real time.
+To make better use of the proposed model, we provide an algorithm for predictive experiments that help to learn which specification of HEM provides a better fit to the data.
 
-We have demonstrated effectiveness of our model by analyzing Montgomery County government emails, where emails serve as the canonical example of directed edges with one sender and one or more receivers.
-The estimated effects for edge covariates reveal that the HEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), but we also learn about the effect of timestamp covariates on waiting time to next event, by integrating a survival model for event timing.
-Although we illustrate the entire framework and application in the context of one type of hyperedges, one sender and one or more receivers, our model can be easily extended to allow the opposite case, one or more sender and one receiver, by slight modification of the generative process (shown in Appendix A).
-This extension involves promissing applications including international sanctions and co-sponsorship of bills.
-Furthermore, while currently the model's applicability is limited to small-sized networks since we assume fixed set of nodes across entire timepoints, we can adjust the model to allow time-varying nodes or improve its computational efficiency such that the model is well applicable to large-scale networks.
+We have demonstrated the effectiveness of our model by analyzing Montgomery County government emails, where emails serve as a canonical example of directed edges with one sender and one or more receivers.
+The estimated effects for edge covariates reveal that the HEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), but we also learn about the effects of timestamp covariates by integrating a survival model for event timing.
+Although we illustrate the entire framework and application in the context of one type of hyperedge, one sender and one or more receivers, our model can be easily extended to allow the opposite case, one or more sender and one receiver, by slight modification of the generative process (shown in Appendix A).
+This extension involves promising applications to socio-political networks such as international sanctions and co-sponsorship of bills, and biological networks such as those formed through neural dendrites.
+%Furthermore, while the model's applicability is limited to small-sized networks since we assume fixed set of nodes across entire timepoints, we can adjust the model to allow time-varying nodes or improve its computational efficiency such that the model is well applicable to large-scale networks.
 Considering the recent explosion of network dataset with huge number of nodes (e.g., online comnunications), the development of model adjustments for better applicability are the object of future work.

### 2018-06-01 paper/ba-HEM/ba-sample.tex
de-capitalize section titles according to BA style guide

@@
 		\begin{keyword}
-\kwd{continuous time network model} 
+			\kwd{dynamic network model} 
+			\kwd{hyperedge}
+			\kwd{continuous time model}
 			\kwd{email data analysis}
@@
 
-\section{The Hyperedge Event Model}\label{sec:generative process}
+	\section{The hyperedge event model}\label{sec:generative process}
 
@@
 
-\subsection{Candidate Receivers}\label{subsec: Tie}
+	\subsection{Candidate receivers}\label{subsec: Tie}
 	For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---an approximate logit of the probability that edge $d$ is being sent from sender $a$ to receiver $r$---as a linear combination of statistics relevant to the receiver selection process:
@@
 Again, this is approximately equivalent to assuming that each $u_{adr}$ is drawn with the probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
-We provide detailed derivation steps for the normalizing constant in Appendix B.
+We provide detailed derivation steps for the normalizing constant $Z(\boldsymbol{\lambda}_{ad})$ in Appendix B.
 
-\subsection{Candidate Timestamps}\label{subsec:Time}
+	\subsection{Candidate timestamps}\label{subsec:Time}
 	Similarly, for each sender and edge combination, the HEM draws a candidate time at which the edge would be sent. The timing rate for sender $a$ and edge $d$ is
-
 	\begin{equation}
@@
 We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
-\subsection{Senders, Receivers, and Timestamps}\label{subsec:Observed}
+	\subsection{Senders, receivers, and timestamps}\label{subsec:Observed}
 	Finally, under the HEM the observed sender, receivers, and timestamp of edge $d$ is generated by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
@@
 
-\section{Posterior Inference}\label{sec:inference}
+	\section{Posterior inference}\label{sec:inference}
 	In this section we describe how we invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_d\}_{d=1}^D$, coefficients for edge covariates $\boldsymbol{b}$, and coefficients for timestamp covariates $\boldsymbol{\eta}$---conditioned on the observed data $\{(a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, covariates $\{(\boldsymbol{x}_d, \boldsymbol{y}_d)\}_{d=1}^D$, and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
@@
 
-\subsection{Conditional Posteriors}\label{subsec:conditionaldist}
-\subsubsection{Candidate Receivers}
+	\subsection{Conditional posteriors}\label{subsec:conditionaldist}
+	\subsubsection{Candidate receivers}
 	In the HEM, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
@@
 Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional M-H update---e.g., $\Pr(k| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution.
-\subsection{Getting It Right (GiR) Test} \label{subec:GiR}
+	\subsection{Getting it Right (GiR) test} \label{subec:GiR}
 	Software development is integral to the objective of applying the HEM to real world data.
@@
 	\end{itemize}
+
+	To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using log-normal distibution for the time increments $f_\tau$.
+We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
+We also calculated t-test and Mann-Whitney test p-values in order to test for differences in the distributions generated in the forward and backward samples.
+Before we calculated these statistics, we thinned our samples by taking every 9th sample starting at the 10,000th sample for a resulting sample size of 10,000, in order to reduce the autocorrelation in the Markov chains.
+In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
+We depict the GiR results using probability-probability (PP) plots, in which the empirical CDF values of the forward and backward samples are plotted on the $x$ and $y$ axes, respectively.
+If the two samples are from equivalent distributions, the empirical CDF values should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
+The GiR test results are depicted in Figure \ref{figure:GiRplot}.
+These results indicate that our sampling equations and software implementation pass the test on every statistic.
 		\begin{figure}[!t]
@@
 		\end{figure}   
-   To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using log-normal distibution for the time increments $f_\tau$.
-We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
-We also calculated t-test and Mann-Whitney test p-values in order to test for differences in the distributions generated in the forward and backward samples.
-Before we calculated these statistics, we thinned our samples by taking every 9th sample starting at the 10,000th sample for a resulting sample size of 10,000, in order to reduce the autocorrelation in the Markov chains.
-In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
-We depict the GiR results using probability-probability (PP) plots, in which the empirical CDF values of the forward and backward samples are plotted on the $x$ and $y$ axes, respectively.
-If the two samples are from equivalent distributions, the empirical CDF values should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
-The GiR test results are depicted in Figure \ref{figure:GiRplot}.
-These results indicate that our sampling equations and software implementation pass the test on every statistic.
-
- 	   \section{Application to Email Data}\label{sec:Emails}
+	\section{Application to email data}\label{sec:Emails}
 	We now present a case study applying our method to Montgomery county government email data.
@@
 
-	\subsection{Model Selection}\label{subsec:Experiment_email}
+	\subsection{Model selection}\label{subsec:Experiment_email}
 
@@
 
-	\subsection{Posterior Predictive Checks}\label{subsec:PPC_email} 	   
+	\subsection{Posterior predictive checks}\label{subsec:PPC_email} 	   
 	In this section, we perform posterior predictive checks (PPC) \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for Montgomery County email data.
@@
 
-	\subsection{Exploratory Analysis}\label{subsec:Result_email}
+	\subsection{Exploratory analysis}\label{subsec:Result_email}
 	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we interpret the results from the HEM using the log-normal distribution.
@@
 	\section*{Appendix}
-	\subsection*{Appendix A: Alternative Generative Process} \label{appendix:alternativeGP}
+	\subsection*{Appendix A: Alternative generative process} \label{appendix:alternativeGP}
 	\begin{algorithm}[H]
@@
 	\end{algorithm}
-	\subsection*{Appendix B: Normalizing Constant of MB$_{G}$}\label{appendix: non-empty Gibbs measure}
+	\subsection*{Appendix B: Normalizing constant of MB$_{G}$}\label{appendix: non-empty Gibbs measure}
 	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure---defines the probability of sender $a$ selecting the binary receiver vector $\boldsymbol{u}_{ad}$ as
@@
 		\end{equation*}
-	\subsection*{Appendix C: Comparison of PPC Results: log-normal vs. exponential}\label{appendix: PPCexp}
+		\subsection*{Appendix C: Comparison of PPC results: log-normal vs. exponential}\label{appendix: PPCexp}
 		\begin{figure}[H]
@@
 		\newpage
-	\subsection*{Appendix D: Convergence Diagnostics}\label{appendix: convergence}
+		\subsection*{Appendix D: Convergence diagnostics}\label{appendix: convergence}
 		\begin{figure}[H]
@@
 		\end{figure}
+
+		\iffalse
 		\begin{supplement}
@@
 		\end{supplement}
+		\fi
 

### 2018-06-01 paper/ba-HEM/ba-sample.tex
minor typo edits

@@
 We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
+	\newpage
 	\subsection{Senders, receivers, and timestamps}\label{subsec:Observed}
@@
 	\end{equation}
+	\begin{figure}[!t]
+		\centering
+		\includegraphics[width=0.625\textwidth]{img/diagram2.png}	
+		\caption {An illustrative example of the generative process of the HEM.}
+		\label{figure:diagram}
+	\end{figure}	
 		Therefore, it is a sender-driven process in that the receivers and timestamps of an edge are jointly determined by the sender's urgency to send the edge to the selected receivers.
@@
 	\end{algorithm}
-	\begin{figure}[ht]
-		\centering
-		\includegraphics[width=0.625\textwidth]{img/diagram2.png}	
-		\caption {An illustrative example of the generative process of the HEM.}
-		\label{figure:diagram}
-	\end{figure}
 
@@
 This interaction allows us to model a possible tradeoff between the hyperedge size and the total number of edges sent.
-Dyadic statistics``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
+Dyadic statistics ``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
 In the example of triadic statistics, the covariate ``2-send" counts the pairs of emails involving some node $h$ distinct from $a$ and $r$ such that emails from $a$ to $h$ and $h$ to $r$ are both observed within the last 7 days.
@@
 
-	When we look at the effects of dyadic and triadic covariates, one thing that stands out is the large and positive posterior distribution of the statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) with the posterior mean $\hat{b}_4 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
+	When we look at the effects of dyadic and triadic covariates, one thing that stands out is the large and positive posterior distribution of the statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) with the posterior mean $\hat{b}_9 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
 The posterior distributions for the reciprocity effect (receive), and the four triadic effects, are all fairly evenly spread around zero, so our results do not justify conclusions regarding the nature of these effects in the Montgomery county email network.
@@
 				\begin{tabular}[t]{cc}
-			\begin{subfigure}[b]{0.495\textwidth}
+					\begin{subfigure}[b]{0.4975\textwidth}
 						\caption{Nodal covariates}
@@
 					\end{subfigure}
-			\begin{subfigure}[b]{0.495\textwidth}
+					\begin{subfigure}[b]{0.4975\textwidth}
 						\caption{Dyadic and triadic covariates}
@@
 			\end{figure}
-
 	\subsubsection{Coefficients for timestamp covariates}
@@
 				\centering
-		\includegraphics[width=0.495\textwidth]{img/etaplotnew-1.png}	
+				\includegraphics[width=0.4975\textwidth]{img/etaplotnew-1.png}	
 				\caption {Posterior distribution of $\boldsymbol{\eta}$ estimates.}
@@
 		\end{equation*}
+		\newpage
 		\subsection*{Appendix C: Comparison of PPC results: log-normal vs. exponential}\label{appendix: PPCexp}

### 2018-06-19 paper/ba-HEM/ba-sample.tex
BA draft updated after Aaron's edits

@@
 The HEM offers three innovations with respect to the literature---first, it extends a growing class of dynamic network models to model hyperedges.
-Second, we derive a receiver-selection distribution that forces the sender to select at least one receiver.
+Second, we introduce a novel receiver-selection distribution that is natural for generating sets of recipients.
 Third, we incorporate both a timing equation and an edge-formation equation into the model specification.
@@
 Our application demonstrates that the model is effective at predicting and explaining time-stamped network data involving edges with multiple receivers.
-We present a out-of-sample prediction experiment to illustrate how researchers can select between different specifications of the model.
+We present an out-of-sample prediction experiment to illustrate how researchers can select between different specifications of the model.
 		\end{abstract}
@@
 	Processes that arise as time-stamped directed interactions are common in the social, natural, and phyiscal sciences.
-The data produced by such processes can be represented as dynamic directed networks---a data structure that has given rise to the development of several statistical model families.
-For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} characterize networks as evolving as the senders of edges decide to add an edge to or remove an edge from a network one edge at a time, one sender at a time.
+The data produced by such processes can be represented as dynamic directed networks---an object that has given rise to the development of several statistical model families.
+For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} characterize that networks are evolving as the senders of edges decide to add an edge to or remove an edge from a network one edge at a time, one sender at a time.
 Event-based network models \citep{Butts2008,Vu2011,hunter2011dynamic,PerryWolfe2012} provide a general framework for modeling the realization of edges that occur as instances in continuous time streams of events.
@@
 	A major limitation of existing dynamic network models is that they apply to edges with one sender and one receiver.
-Many sources of dynamic network data arise as ``hyperedges'' \citep{karypis1999multilevel,ghoshal2009random,zlatic2009hypergraph,zhang2010hypergraph} that include one sender and multiple receivers or one receiver and multiple senders.
-For example, networks formed through the analysis of email \citep{newman2002email} arise with one sender and possibly multiple receviers;  networks formed between neurons via axons and dendrites have one sender and multiple receivers (axons) or one receiver and multiple senders (dendrites) \citep{partzsch2012developing}.
+A lot of dynamic network data arise as ``hyperedges'' \citep{karypis1999multilevel,ghoshal2009random,zlatic2009hypergraph,zhang2010hypergraph} that include one sender and multiple receivers or one receiver and multiple senders.
+For example, email networks \citep{newman2002email} arise with one sender and possibly multiple receviers;  networks formed between neurons via axons and dendrites have one sender and multiple receivers (axons) or one receiver and multiple senders (dendrites) \citep{partzsch2012developing}.
 Networks formed through the analysis of legislative bill cosponsorhip \citep{fowler2006legislative} arise with multiple senders (cosponsors) and one receiver (sponsor); and networks formed through the analysis of economic sanctions \citep{cranmer2014reciprocity} between countries arise with multiple sending countries and one target country.
-Existing models require that researchers alter hyperedge data to fit with the pairwise edge structure of the model.
+Existing models require researchers to alter hyperedge data to fit with the pairwise edge structure of the model.
 For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involves one sender and one or more receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), to construct approximate likelihood function in their inferential framework for model parameters.
-Similarly, \cite{fan2009learning} duplicates emails sent from one sender to one or more receivers and randomly jitter the sent times, in order to avoid the violation of the assumption that two events cannot occur at the exact same time.
+Similarly, \cite{fan2009learning} duplicates emails sent from one sender to one or more receivers and randomly jitter the sent times in order to avoid the violation of the assumption that two events cannot occur at the exact same time.
 % There have been numerous studies for hyperedges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}---with lack of extensive efforts to incorportate hyperedge modeling into general statistical framework.
@@
 Data generated under the HEM consists of $D$ unique edges.
-A single edge, indexed by $d \in [D]$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = \{u_{dr} \}_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
+A single edge indexed by $d \in [D]$, where $[D]$ denotes a categorical set with $D$ levels $[D] = \{1,\ldots,D\}$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = (u_{dr})_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
@@
 We explain these steps in more detail below.
-For hyperedges that involve one receiver and one or more senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = \{u_{dr} \}_{a=1}^{A}$ and $r_d$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).
+For hyperedges that involve one receiver and one or more senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = (u_{dr})_{a=1}^{A}$ and $r_d$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).
 
@@
 	\end{equation}
-	where $\boldsymbol{\lambda}_{ad}= \{\lambda_{adr}\}_{r=1}^A$. In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ad})$ as
+	where $\boldsymbol{\lambda}_{ad}= (\lambda_{ad1},
+	\ldots, \lambda_{adA})$. In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ad})$ as
 	\begin{equation}
@@
 Again, this is approximately equivalent to assuming that each $u_{adr}$ is drawn with the probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
+This allows efficient inference since we can derive a closed-form normalizing constant which does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (i.e., $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
 We provide detailed derivation steps for the normalizing constant $Z(\boldsymbol{\lambda}_{ad})$ in Appendix B.
@@
 	In modeling ``when," we do not directly model the timestamp $t_d$.
-Instead, we assume that each sender's ``time increment"---i.e., waiting time to next interaction since $t_{d-1}$---is drawn from a specific distribution in the exponential family.
+Instead, we assume that each sender's ``time increment"---i.e., waiting time to next interaction since $t_{d-1}$---is drawn from a specific exponential family distribution.
 We define the time increment from edge $d-1$ to edge $d$ as $\tau_{d}$ (i.e., $\tau_{d}= t_d-t_{d-1}$) and specify the distribution of candidate timestamps with sender-specfic mean $\mu_{ad}$.
@@
 	In the HEM, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
-However, it is possible to augment the data by candidate receivers $\boldsymbol{u}$ such that we can obtain their conditional posterior by collapsing the known distributions---$P(\boldsymbol{b}, \boldsymbol{u}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}| \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---through integrating out $\boldsymbol{u}$.
-We adapt this common tool in Bayesian statistics called ``data augmentation" \citep{tanner1987calculation,neal2015exact}.
-Since $u_{adr}$ is a binary random variable, its new value may be sampled directly from a multinomial distribution with probabilities
+However, it is possible to augment the data by candidate receivers $\boldsymbol{u}$ such that we can obtain their conditional posterior by conditioning on samples of $\boldsymbol{u}$.
+%from $P(\boldsymbol{b}, \boldsymbol{u}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}| \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$.
+	We use this common tool in Bayesian statistics called ``data augmentation" \citep{tanner1987calculation,neal2015exact}.
+Since $u_{adr}$ is a binary random variable, its new value may be sampled directly from a Bernoulli distribution with probability $p_{adr} =\frac{\exp(\lambda_{adr})}{\exp(\lambda_{adr})+\text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 )}$, since
 	\begin{equation}
@@
 
-	\cite{geweke2004getting} introduced the ``Getting it Right'' (GiR) test---a joint distribution test of posterior simulators which can detect errors in sampling equations as well as coding errors---and it has been used to test the implementation of Bayesian inference algorithms \citep{zhao2016bayesian}.
-The test involves comparing the distributions of variables simulated from two joint distribution samplers, which we call ``forward" and ``backward" samples.
-The forward sampler draws unobservable variables from the prior and then generates the observable data conditional on the unobservables.
-The backward sampler alternates between the inference and an observables simulator by running the inference code on observable data to obtain posterior estimates of the unobservable variables and then re-generating the observables given the inferred unobservables.
-The backward sampler is initialized by running an iteration of inference on observables drawn directly from the prior.
-Since the only information on which both the forward and backward samplers are based is the prior, if the sampling equations are correct and the code is implemented without bugs, each variable should have the same distribution in the forward and backward samples.
+	\cite{geweke2004getting} introduced the ``Getting it Right'' (GiR) test---a joint distribution test of posterior simulators which can detect errors in sampling equations as well as software bugs---and it has been used to test the implementation of Bayesian inference algorithms \citep{zhao2016bayesian}.
+The test involves comparing the distributions of variables simulated from two joint distribution samplers, which we call ``forward" and ``backward" samplers.
+The ``forward" sampler draws joint samples of the latent and observable variables from the prior.
+The ``backward" sampler begins by first drawing a joint sample of the latent and observed variables from the prior.
+It then alternates between re-sampling the latent variables, conditioned on the observable variables, from the MCMC transition operator, and then re-sampling the observable variable, conditioned on the latent variables, from the model likelihood.
+If the MCMC transition operator is correctly derived and implemented, this process should asymptotically generate joint samples of the latent and observable variables from the prior, like the forward sampler.
 
@@
 	A primary purpose of any network model is to use the posterior distributions to learn which features predict and/or explain edge formation (e.g., is edge formation reciprocal, are edges more likely to be formed among nodes with the same gender).
-This email application specifically give rise to the following question: ``To what extent are nodal, dyadic or triadic network effects relevant to predicting future emails?" As an illustrative example, we form the receiver selection features $\boldsymbol{x}$ for Montgomery County email data using nodal, dyadic, and triadic covariates.
+This email application specifically gives rise to the following question: ``To what extent are nodal, dyadic or triadic network effects relevant to predicting future emails?" As an illustrative example, we form the receiver selection features $\boldsymbol{x}$ for Montgomery County email data using nodal, dyadic, and triadic covariates.
 First, as we want to test whether gender plays a role in receiver selection process, we include three nodal covariates---the gender information of sender and receiver, and their homophily indicator (i.e., an indicator of whether the sender and receiver are of the same gender).
@@
 The popularity effect refers to the tendency for nodes that received many edges in the past to continue to do so in the future.
-Moreover, in order to capture individual tendency of send emails to two or more receivers, we include the statistic ``hyperedge size"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of receivers are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
+Moreover, in order to capture the individual tendency of sent emails to two or more receivers, we include the statistic ``hyperedge size"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of receivers are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
 We also include the interaction term between outdegree and hyperedge size.
@@
 	\subsubsection{Timestamp covariates}
-	For the event timing features $\boldsymbol{y}$ introduced in Section \ref{subsec:Time}, we identify a set of covariates which may effect ``time to the next email." Similar to the edge covariates, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
+	For the event timing features $\boldsymbol{y}$, introduced in Section \ref{subsec:Time}, we identify a set of covariates which may affect ``time to the next email." Similar to the edge covariates, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
 In addition, we select some edge-specific covariates based on the temporal aspect of the $(d-1)^{th}$ email---e.g., whether the previous email was sent (1) during the weekend and (2) before or past midday (AM/PM)---since we expect the email interactions within county government to be less active during the weekend and in the evening.
@@
 	\end{itemize}
-	Note that our generative process for timestamps in Section \ref{subsec:Time} is sender-oriented where the sender deterimes when to send the email, thus we incorporate network statistics that depends on $a$ only---outdegree of sender $a$ and indegree of sender $a$.
+	Note that our generative process for timestamps in Section \ref{subsec:Time} is sender-oriented where the sender determines when to send the email; thus we incorporate network statistics that depend only on $a$---specifically, the in and outdegrees of sender $a$.
 
@@
 
-	The HEM has many component parts that need to be specified by the user (i.e., the receiver selection features $\boldsymbol{x}$, the selection of the event timing features $\boldsymbol{y}$, and the distribution of time increments $f$).
+	The HEM defines a flexible family of models, each of which is indexed/defined by a set of features (i.e., the receiver selection features $\boldsymbol{x}$, the selection of the event timing features $\boldsymbol{y}$, and the distribution of time increments $f$).
 Many of these components will be specified based on user expertise (e.g., regarding which features would drive receiver selection), but some decisions may require a data-driven approach to model specification.
@@
 			\IF{$a_d=$  NA}
-			\FOR{$a=1$ {\bfseries to} $A$}
-			\STATE compute $\pi_{a}=P(a_d= a | \cdot)$ using equation (\ref{eqn:latenttime}) (without the product term)
-			\ENDFOR
-			\STATE draw $a_d \sim \mbox{multinomial}(\pi_a)$
+			%\STATE compute the vector $\boldsymbol{\pi}_d$, from equation (\ref{eqn:latenttime}) (without the product term)
+			\STATE draw $a_d \sim \mbox{Categorical}(\boldsymbol{\pi}_d),$ where $\pi_{da}=f_{\tau}(\tau_{d}; \mu_{ad}, V(\mu_{ad}))\times \prod_{a^\prime\neq a}\big(1-F_{\tau}(\tau_{d}; \mu_{a^\prime d}, V(\mu_{a^\prime d})) \big)$
 			\ENDIF
@@
 			\IF{$r_{dr}=$ NA}
-			\STATE draw $r_{dr}$ from multinomial with probability $P(r_{dr}= 1 | \cdot)$ and $P(r_{dr}= 0| \cdot)$ using equation (\ref{eqn:latentreceiver})
+			\STATE draw $r_{dr} \sim \mbox{Bernoulli}(p_{dr}),$
+			where $p_{dr}=\frac{\exp(\lambda_{adr})}{\exp(\lambda_{adr})+\text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 )}$ %as defined in equation (\ref{eqn:latentreceiver})
 			\ENDIF
@@
 			\IF{$t_d=$ NA}
-			\STATE draw $\boldsymbol{\tau}^{new}_d$ from equation (\ref{eqn:latenttime}) (without the product term) via importance sampling\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
+			\STATE draw $\boldsymbol{\tau}^{new}_d \sim f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big),$ %from equation (\ref{eqn:latenttime}) (without the product term)
+			where we sample from this distribution using importance sampling\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
 			\ENDIF
@@
 
-	We evaluate the model's ability to predict edges and timestamps from Montgomery County email data, conditioned on their ``training" part of the data.
-To perform the experiment, we separately formed a test split of each three model components---sender, receivers, and timestamps---by randomly selecting ``test" data with probability $p=0.10$, and setting the test data to missing.
-Any missing variables were imputed by drawing samples from their conditional posterior distributions, given the observed data, model estimates, and current values of imputed test data.
-We then run inference to update the latent variables given the imputed and observed data.
-We iterate the two steps---imputation and inference---multiple times to obtain posterior samples of the held out test data.
+	We evaluated the model’s ability to predict out-of-sample edges and timestamps on Montgomery County email data.
+We generated a train—test split of the data by randomly selecting 10\% of sender, receiver, and time-stamp variables to be held out.
+Our model then imputed these missing variables during inference, sampling them from their conditional posterior along with the other latent variables.
 Algorithm \ref{alg:PPE} outlines this procedure in detail.
-We run the experiment and measure the predictive performance of two separate time distributions using $N=500$ predicted samples, by comparing the predictions in terms of classification accuracy in predicting the senders and receivers, as well as prediction error in the timestamps.
+We compare the predictive performance of two versions of the model, each with a different timing distribution over the time-increments using $N=500$.
 We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
@@
 We call this measure the ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails.
-The results show that both log-normal and exponential distributions acheive better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing higher performance than exponential distribution.
+The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing better performance than exponential distribution.
 Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA) by taking the harmonic mean of precision and recall:
@@
 Surprisingly, we have a huge benefit in the performance of timestamp prediction when we assume log-normal distribution for time-increments compared to exponential distribution.
-This difference can be explained by overdispersion in exponential distribution, because there exists greater variability in the time increments of emails than would be expected under exponential distribution.
+We speculate that this difference can be explained by overdispersion in exponential distribution, because there exists greater variability in the time increments of emails than would be expected under exponential distribution.
 As illustrated above, we can use this out-of-sample prediction task for two uses---1) to provide an effective answer to the question ``how does the HEM perform at filling in the missing components of time-stamped network data?" and 2) to offer one standard way to determine the distribution of time increments in Section \ref{subsec:Time}.
@@
 
-	To use this distribution efficiently, we derive a closed-form expression for $Z(\boldsymbol{\lambda}_{ad})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (\textit{i.e.} $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
+	To use this distribution efficiently, we derive a closed-form expression for $Z(\boldsymbol{\lambda}_{ad})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (i.e., $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
 We recognize that if $\boldsymbol{u}_{ad}$ were drawn via independent Bernoulli distributions in which $\Pr({u}_{adr}=1|\boldsymbol{b}, \boldsymbol{x}_{ad})$ was given by logit$(\lambda_{adr})$, then

### 2018-06-20 paper/ba-HEM/ba-sample.tex
addressed remianing comments

@@
 			We introduce the hyperedge event model (HEM)---a generative model for events that can be represented as directed edges with one sender and one or more receivers or one receiver and one or more senders.
-To define the model, we
+We
 			integrate a dynamic version of the exponential random graph model (ERGM) of edge structure with a survival model for event timing to jointly understand who interacts with whom, and when.
 The HEM offers three innovations with respect to the literature---first, it extends a growing class of dynamic network models to model hyperedges.
-Second, we introduce a novel receiver-selection distribution that is natural for generating sets of recipients.
-Third, we incorporate both a timing equation and an edge-formation equation into the model specification.
+The current state of the art approach to dealing with hyperedges is to inappropriately break them into separate edges/events.
+Second, the HEM involves a novel receiver-selection distribution that is based on established edge formation models, but assures non-empty receiver lists.
+Third, HEM integrates separate, but interacting, equations governing edge formation and event timing.
 We use the HEM to analyze emails sent among department managers in Montgomery County government in North Carolina.
@@
 Data generated under the HEM consists of $D$ unique edges.
-A single edge indexed by $d \in [D]$, where $[D]$ denotes a categorical set with $D$ levels $[D] = \{1,\ldots,D\}$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = (u_{dr})_{r=1}^{A}$, and the timestamp $t_d \in (0, \infty)$.
+A single edge indexed by $d \in [D]$, where $[D]$ denotes a categorical set with $D$ levels $[D] = \{1,\ldots,D\}$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = (u_{dr})_{r=1}^{A}$, such that $u_{dr}=1$ if $r$ is a receiver of edge $d$ and 0 otherwise, and the timestamp $t_d \in (0, \infty)$.
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
@@
 	\subsection{Candidate receivers}\label{subsec: Tie}
-	For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---an approximate logit of the probability that edge $d$ is being sent from sender $a$ to receiver $r$---as a linear combination of statistics relevant to the receiver selection process:
+	For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---the conditional logit of the probability that edge $d$ is sent from sender $a$ to receiver $r$---as a linear combination of statistics relevant to the receiver selection process:
 	\begin{equation}
@@
 	where $\boldsymbol{b}$ is a $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of receiver selection features.
-Such features can capture common network processes that include, but are not limited to, popularity, reciprocity, and transitivity, as well as the effects of attribute features defined on the sender, receivers, and/or sender-receiver pairs (e.g., the gender of the sender and/or receiver, an indicator of whether the sender is a supervisor of the receiver's).
+$\lambda_{adr}$ is the logit of the probability that edge $d$ is sent from sender $a$ to receiver $r$ conditional upon there being at least one other receiver to which sender $a$ sends edge $d$.
+In the case that there are no other receivers to which sender $a$ sends edge $d$, the logit of the probability that sender $a$ sends edge $d$ to receiver $r$ is $\infty$.
+The features in Equation 2.1 can capture common network processes that include, but are not limited to, popularity, reciprocity, and transitivity, as well as the effects of attribute features defined on the sender, receivers, and/or sender-receiver pairs (e.g., the gender of the sender and/or receiver, an indicator of whether the sender is a supervisor of the receiver's).
 In addition, we include an intercept term to account for the average (or baseline) number of receivers.
@@
 
-	A basic assumption of the HEM is that, at any given time, everyone is planning to send a document to one or more receivers.
-So for each edge $d$ and each sender $a$, the HEM draws a list of candidate receivers that would be receivers on edge $d$ if $a$ were the sender.
+	As we describe in greater detail below, under the HEM the sender of each edge is selected to be the sender that would send the respective edge with the greatest urgency.
+As such, under the HEM we assume that each sender would plan on sending each edge to some set of recipients at some time point.
+For each edge $d$ and each sender $a$, the HEM draws a list of candidate receivers that would be receivers on edge $d$ if $a$ were the sender.
 For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{th}$ row denotes sender $a$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $a$ intends to send edge $d$.
@@
 	\subsection{Candidate timestamps}\label{subsec:Time}
-	Similarly, for each sender and edge combination, the HEM draws a candidate time at which the edge would be sent. The timing rate for sender $a$ and edge $d$ is
+	To generate timing for each edge, the HEM first draws a candidate time at which the edge would be sent given the candidate sender and receiver combinations.
+The timing rate for sender $a$ and edge $d$ is
 	\begin{equation}

### 2018-06-20 paper/ba-HEM/ba-sample.tex
revisions after June 20th meeting

@@
 The HEM offers three innovations with respect to the literature---first, it extends a growing class of dynamic network models to model hyperedges.
-The current state of the art approach to dealing with hyperedges is to inappropriately break them into separate edges/events.
-Second, the HEM involves a novel receiver-selection distribution that is based on established edge formation models, but assures non-empty receiver lists.
-Third, HEM integrates separate, but interacting, equations governing edge formation and event timing.
+The current state-of-the-art approach to dealing with hyperedges is to inappropriately break them into separate edges/events.
+Second, our model involves a novel receiver-selection distribution that is based on established edge formation models, but assures non-empty receiver lists.
+Third, the HEM integrates separate, but interacting, equations governing edge formation and event timing.
 We use the HEM to analyze emails sent among department managers in Montgomery County government in North Carolina.
@@
 For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involves one sender and one or more receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), to construct approximate likelihood function in their inferential framework for model parameters.
-Similarly, \cite{fan2009learning} duplicates emails sent from one sender to one or more receivers and randomly jitter the sent times in order to avoid the violation of the assumption that two events cannot occur at the exact same time.
+Similarly, \cite{fan2009learning} duplicate emails sent from one sender to one or more receivers and randomly jitter the sent times in order to avoid the violation of the assumption that two events cannot occur at the exact same time.
 % There have been numerous studies for hyperedges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}---with lack of extensive efforts to incorportate hyperedge modeling into general statistical framework.
@@
 In what follows, we introduce the HEM by defining a generative process for time and hyperedge attributed event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference and present tests of our software implementation (Section \ref{sec:inference}).
-After defining the structure of and deriving Bayesian inference methods for HEM, we demonstrate the model's applicability by analyzing data from a corpus of internal county government emails.
+After defining the structure of and deriving Bayesian inference methods for the HEM, we demonstrate the model's applicability by analyzing data from a corpus of internal county government emails.
 In the application we illustrate model selection, posterior predictive checks, and exploratory analysis (Section \ref{sec:Emails}).
@@
 	In this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time.
-Data generated under the HEM consists of $D$ unique edges.
+Data generated under our model consists of $D$ unique edges.
 A single edge indexed by $d \in [D]$, where $[D]$ denotes a categorical set with $D$ levels $[D] = \{1,\ldots,D\}$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = (u_{dr})_{r=1}^{A}$, such that $u_{dr}=1$ if $r$ is a receiver of edge $d$ and 0 otherwise, and the timestamp $t_d \in (0, \infty)$.
 For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
-While the model can be applied for two types of hyperedges---edges with (1) one sender and one or more receivers, and (2) one or more senders and one receiver---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast).
-One notable feature of the HEM generative process is that we draw auxiliary variables that serve as candidate data.
+While the model can be applied to two types of hyperedges---edges with (1) one sender and one or more receivers, and (2) one or more senders and one receiver---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast).
+One notable feature of our model generative process is that we draw auxiliary variables that serve as candidate data.
 Data is generated from the HEM through a sampling process applied to the auxiliary variables.
@@
 As such, under the HEM we assume that each sender would plan on sending each edge to some set of recipients at some time point.
-For each edge $d$ and each sender $a$, the HEM draws a list of candidate receivers that would be receivers on edge $d$ if $a$ were the sender.
-For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{th}$ row denotes sender $a$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $a$ intends to send edge $d$.
+For each edge $d$ and each sender $a$, our model draws a list of candidate receivers that would be receivers on edge $d$ if $a$ were the sender.
+For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{\textrm{th}}$ row denotes sender $a$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $a$ intends to send edge $d$.
 We then assume that each receiver vector $\boldsymbol{u}_{ad}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
@@
 		\begin{aligned}
-			&\Pr(\boldsymbol{u}_{ad}|\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0 )\big) + \sum_{r\neq a} \lambda_{adr}u_{adr}\Big) ,
+			&\Pr(\boldsymbol{u}_{ad}|\,\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0 )\big) + \sum_{r\neq a} \lambda_{adr}u_{adr}\Big) ,
 		\end{aligned}
@@
 We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
-	\newpage
+
 	\subsection{Senders, receivers, and timestamps}\label{subsec:Observed}
@@
 	\subsubsection{Candidate receivers}
-	In the HEM, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
+	In our model, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\,\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\,\boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
 However, it is possible to augment the data by candidate receivers $\boldsymbol{u}$ such that we can obtain their conditional posterior by conditioning on samples of $\boldsymbol{u}$.
-%from $P(\boldsymbol{b}, \boldsymbol{u}|\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}| \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$.
+%from $P(\boldsymbol{b}, \boldsymbol{u}|\,\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}|\, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$.
 	We use this common tool in Bayesian statistics called ``data augmentation" \citep{tanner1987calculation,neal2015exact}.
@@
 		\begin{aligned}
-			&\Pr(u_{adr}=1| \boldsymbol{u}_{ad\backslash r}, \boldsymbol{b}, \boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})
+			&\Pr(u_{adr}=1| \,\boldsymbol{u}_{ad\backslash r}, \boldsymbol{b}, \boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})
 			\propto \mbox{exp}(\lambda_{adr});\\
-			&\Pr(u_{adr}=0| \boldsymbol{u}_{ad\backslash r},\boldsymbol{b}, \boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 ),
+			&\Pr(u_{adr}=0|\, \boldsymbol{u}_{ad\backslash r},\boldsymbol{b}, \boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 ),
 		\end{aligned}
@@
 	\subsubsection{Coefficients for edge covariates}
-	Unlike the candidate receivers above, new values for $\boldsymbol{b}$ cannot be sampled directly from its conditional posterior, but may instead be obtained using the Metropolis--Hastings (M-H) algorithm.
+	Unlike the candidate receivers above, new values for $\boldsymbol{b}$ cannot be sampled directly from its conditional posterior, but may instead be obtained using the Metropolis--Hastings (M--H) algorithm.
 Assuming an uninformative prior (i.e., $N({0},\infty)$), the conditional posterior over $\boldsymbol{b}$ is
 	\begin{equation}
-		\Pr(\boldsymbol{b}| \boldsymbol{u}, \boldsymbol{x}, \boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D
+		\Pr(\boldsymbol{b}| \,\boldsymbol{u}, \boldsymbol{x}, \boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D
 		\prod_{a=1}^A \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0)\big) + \sum\limits_{r \neq a} \lambda_{adr}u_{adr}\Big).
@@
 			\FOR{n=1 to $I_1$}
-			\STATE update $\boldsymbol{b}$ using M-H algorithm---equation (\ref{eqn:latentedge})
+			\STATE update $\boldsymbol{b}$ using M--H algorithm---equation (\ref{eqn:latentedge})
 			\ENDFOR
 			\FOR{n=1 to $I_2$}
-			\STATE update $\boldsymbol{\eta}$ using M-H algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
+			\STATE update $\boldsymbol{\eta}$ using M--H algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
 			\ENDFOR
 			\IF {extra parameter for $V(\mu)$} 
-			\STATE update the variance parameter using M-H algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
+			\STATE update the variance parameter using M--H algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
 			\ENDIF
@@
 	\subsubsection{Coefficients for timestamp covariates}
-	Likewise, we use the M-H algorithm to update the latent variable $\boldsymbol{\eta}$.
+	Likewise, we use the M--H algorithm to update the latent variable $\boldsymbol{\eta}$.
 Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for an untied event case is
 	\begin{equation}
-		\Pr(\boldsymbol{\eta}| \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
+		\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
 		\label{eqn:latenttime}
 	\end{equation}
-	where $f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))$ is the probability that the $d^{th}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{a_d d}$, and $\prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d},V(\mu_{a_d d})) \big)$ is the probability that the rest of (unobserved) senders for event $d$ all draw time increments greater than $\tau_d$.
+	where $f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))$ is the probability that the $d^{\textrm{th}}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{a_d d}$, and $\prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d},V(\mu_{a_d d})) \big)$ is the probability that the rest of (unobserved) senders for event $d$ all draw time increments greater than $\tau_d$.
 Moreover, under the existence of tied events, the conditional posterior of $\boldsymbol{\eta}$ is written as
@@
 		\begin{aligned}
-			\Pr(\boldsymbol{\eta}| \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, V(\mu_{a_d d})) \\&\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
+			\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, V(\mu_{a_d d})) \\&\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
 		\end{aligned}
@@
 If $M=D$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
-Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional M-H update---e.g., $\Pr(k| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution.
+Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional M--H update---e.g., $\Pr(k|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \,\boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution.
 	\subsection{Getting it Right (GiR) test} \label{subec:GiR}
-	Software development is integral to the objective of applying the HEM to real world data.
+	Software development is integral to the objective of applying our model to real world data.
 Code review is a valuable process in any research computing context, and the prevalence of software bugs in statistical software is well documented \citep[e.g., ][]{altman2004numerical,mccullough2009accuracy}.
@@
 For this case study,
-	we formulate a HEM specification through definitions of the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$.
-We then report a suite of experiments---out-of-sample prediction for model selection and posterior predictive checks---that illustrate how alternative formulations of the HEM can be compared, and evaluate how well the HEM recovers the distribution of the observed data.
+	we formulate our model specification through definitions of the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$.
+We then report a suite of experiments---out-of-sample prediction for model selection and posterior predictive checks---that illustrate how alternative formulations of the HEM can be compared, and evaluate how well our model recovers the distribution of the observed data.
 Finally, we demonstrate an exploratory analysis of Montgomery County email data using the model estimates to discover substantively meaningful patterns in organizational communication networks.
@@
 		\item[1.] intercept: ${x}_{adr1} =1$;
-		\item[2.] gender of sender: ${x}_{adr2} = I(\mbox{gender of sender } a= \mbox{female});$
-		\item[3.] gender of receiver: ${x}_{adr3} = I(\mbox{gender of receiver } r= \mbox{female});$
-		\item[4.] gender homophily: ${x}_{adr4} = I({x}_{adr2}={x}_{adr3});$ 	   		
-		\item[5.] outdegree of sender: ${x}_{adr5} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
-		\item[6.] indegree of receiver: ${x}_{adr6}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
-		\item[7.] hyperedge size of sender: ${x}_{adr7}=\sum_{d^\prime: t_{d^\prime} \in l_d} \sum_{r=1}^A I(a_{d^\prime} = a)\,I(u_{d^\prime r} = 1)$;
-		\item[8.] interaction between outdegree and hyperedge size: ${x}_{adr8} = {x}_{adr5}\times{x}_{adr7};$
-		\item[9.] send: ${x}_{adr9}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)\,I(u_{d^\prime r} = 1)$;
-		\item[10.] receive: ${x}_{adr10}=\mbox{send}(r,a)$;
-		\item[11.] 2-send: ${x}_{adr11} = \sum_{h \neq a, r} \mbox{send}(a,h)\,\mbox{send}(h,r)$;
-		\item[12.] 2-receive: ${x}_{adr12}= \sum_{h \neq a, r} \mbox{send}(h,a)\,\mbox{send}(r,h)$;
-		\item[13.] sibling: ${x}_{adr13}=\sum_{h \neq a, r} \mbox{send}(h,a)\,\mbox{send}(h,r)$;
-		\item[14.] cosibling: ${x}_{adr14}=\sum_{h \neq a, r} \mbox{send}(a,h)\,\mbox{send}(r,h)$;
+		\item[2.] $\mbox{gender}\_\,\mbox{sender}(a)$: ${x}_{adr2} = I(\mbox{gender of sender } a= \mbox{female});$
+		\item[3.] $\mbox{gender}\_\,\mbox{receiver}(r)$: ${x}_{adr3} = I(\mbox{gender of receiver } r= \mbox{female});$
+		\item[4.] $\mbox{gender}\_\,\mbox{homophily}(a, r)$: ${x}_{adr4} = I({x}_{adr2}={x}_{adr3});$ 	   		
+		\item[5.] $\mbox{outdegree}(a)$: ${x}_{adr5} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+		\item[6.] $\mbox{indegree}(r)$: ${x}_{adr6}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
+		\item[7.] $\mbox{hyperedge}\_\,\mbox{size}(a)$: ${x}_{adr7}=\sum_{d^\prime: t_{d^\prime} \in l_d} \sum_{r=1}^A I(a_{d^\prime} = a)\,I(u_{d^\prime r} = 1)$;
+		\item[8.] $\mbox{interaction}(a)$: ${x}_{adr8} = {x}_{adr5}\times{x}_{adr7};$
+		\item[9.] $\mbox{send}(a, r)$: ${x}_{adr9}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)\,I(u_{d^\prime r} = 1)$;
+		\item[10.] $\mbox{receive}(a, r)$: ${x}_{adr10}=\mbox{send}(r,a)$;
+		\item[11.] $\mbox{two}\_\,\mbox{send}(a, r)$: ${x}_{adr11} = \sum_{h \neq a, r} \mbox{send}(a,h)\,\mbox{send}(h,r)$;
+		\item[12.] $\mbox{two}\_\,\mbox{receive}(a, r)$: ${x}_{adr12}= \sum_{h \neq a, r} \mbox{send}(h,a)\,\mbox{send}(r,h)$;
+		\item[13.] $\mbox{sibling}(a, r)$: ${x}_{adr13}=\sum_{h \neq a, r} \mbox{send}(h,a)\,\mbox{send}(h,r)$;
+		\item[14.] $\mbox{cosibling}(a, r)$: ${x}_{adr14}=\sum_{h \neq a, r} \mbox{send}(a,h)\,\mbox{send}(r,h)$;
 	\end{itemize}
@@
 The network statistics (5--14) are designed so that their coefficients have a straightforward interpretations.
-The statistics ``outdegree" and ``indegree" measure the gregariousness and popularity effects of the node by counting the number of emails sent from $a$ and received by $r$, respectively, within the last 7 days.
+The function ``outdegree$(a)$" and ``indegree$(r)$" measure the gregariousness and popularity effects of the node by counting the number of emails sent from $a$ and received by $r$, respectively, within the last 7 days.
 The gregariousness effect refers to the tendency for nodes that sent many edges in the past to continue to do so in the future.
 The popularity effect refers to the tendency for nodes that received many edges in the past to continue to do so in the future.
-Moreover, in order to capture the individual tendency of sent emails to two or more receivers, we include the statistic ``hyperedge size"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of receivers are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
-We also include the interaction term between outdegree and hyperedge size.
+Moreover, in order to capture the individual tendency of sent emails to two or more receivers, we include the statistic ``$\mbox{hyperedge}\_\,\mbox{size}(a)$"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of receivers are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
+We also include the interaction term, ``$\mbox{interaction}(a)$", between outdegree and hyperedge size.
 This interaction allows us to model a possible tradeoff between the hyperedge size and the total number of edges sent.
-Dyadic statistics ``send" and ``receive" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
-In the example of triadic statistics, the covariate ``2-send" counts the pairs of emails involving some node $h$ distinct from $a$ and $r$ such that emails from $a$ to $h$ and $h$ to $r$ are both observed within the last 7 days.
-The 2-send statistic captures the tendency for emails to close transitive triads (i.e., triads in which $a$ sends to $r$ and $h$, and $r$ sends to $h$).
+Dyadic statistics ``send$(a, r)$" and ``receive$(a, r)$" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
+In the example of triadic statistics, the covariate ``$\mbox{two}\_\,\mbox{send}(a, r)$" counts the pairs of emails involving some node $h$ distinct from $a$ and $r$ such that emails from $a$ to $h$ and $h$ to $r$ are both observed within the last 7 days.
+This statistic captures the tendency for emails to close transitive triads (i.e., triads in which $a$ sends to $r$ and $h$, and $r$ sends to $h$).
 We include other triadic covariates that behave similarly and exhibit analogous interpretations, which are illustrated in Figure \ref{figure:netstats}.
@@
 For the event timing features $\boldsymbol{y}$, introduced in Section \ref{subsec:Time}, we identify a set of covariates which may affect ``time to the next email." Similar to the edge covariates, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
-In addition, we select some edge-specific covariates based on the temporal aspect of the $(d-1)^{th}$ email---e.g., whether the previous email was sent (1) during the weekend and (2) before or past midday (AM/PM)---since we expect the email interactions within county government to be less active during the weekend and in the evening.
+In addition, we select some edge-specific covariates based on the temporal aspect of the $(d-1)^{\textrm{th}}$ email---e.g., whether the previous email was sent (1) during the weekend and (2) before or past midday (AM/PM)---since we expect the email interactions within county government to be less active during the weekend and in the evening.
 To be specific, the timestamp statistics are defined as
@@
 		\item[1.] intercept: ${y}_{ad1} =1$;
-		\item[2.] gender of sender: ${y}_{ad2}=I(\mbox{gender of sender }a= \mbox{female})$;
-		\item[3.] manager status of sender: ${y}_{ad3}=I(\mbox{sender }a \mbox{ is the County Manager})$;
-		\item[4.] outdegree of sender: ${y}_{ad4} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
-		\item[5.] indegree of sender: ${y}_{ad5}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
-		\item[6.] weekend indicator of previous email: ${y}_{ad6} = I(t_{d-1} \mbox{ is during the } \mbox{weekend})$;
-		\item[7.] PM indicator of previous email: ${y}_{ad7}= I(t_{d-1} \mbox{ in } \mbox{PM})$.
+		\item[2.] $\mbox{gender}(a)$: ${y}_{ad2}=I(\mbox{gender of sender }a= \mbox{female})$;
+		\item[3.] $\mbox{manager}(a)$: ${y}_{ad3}=I(\mbox{sender }a \mbox{ is the County Manager})$;
+		\item[4.] $\mbox{outdegree}(a)$: ${y}_{ad4} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
+		\item[5.] $\mbox{indegree}(a)$: ${y}_{ad5}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
+		\item[6.] $\mbox{weekend}(d)$: ${y}_{ad6} = I(t_{d-1} \mbox{ is during the } \mbox{weekend})$;
+		\item[7.] $\mbox{PM}(d)$: ${y}_{ad7}= I(t_{d-1} \mbox{ in } \mbox{PM})$.
 	\end{itemize}
@@
 			\vskip 0.1in
-			\textbf{Test splits} (with $p=0.1$):	
+			\textbf{Test splits}:	
 			\STATE draw test senders (out of $D$ senders) 
@@
 			\IF{$a_d=$  NA}
-			%\STATE compute the vector $\boldsymbol{\pi}_d$, from equation (\ref{eqn:latenttime}) (without the product term)
-			\STATE draw $a_d \sim \mbox{Categorical}(\boldsymbol{\pi}_d),$ where $\pi_{da}=f_{\tau}(\tau_{d}; \mu_{ad}, V(\mu_{ad}))\times \prod_{a^\prime\neq a}\big(1-F_{\tau}(\tau_{d}; \mu_{a^\prime d}, V(\mu_{a^\prime d})) \big)$
+			\STATE compute the vector $\boldsymbol{\pi}_d$, where $\pi_{da}=f_{\tau}(\tau_{d}; \mu_{ad}, V(\mu_{ad}))\times \prod_{a^\prime\neq a}\big(1-F_{\tau}(\tau_{d}; \mu_{a^\prime d}, V(\mu_{a^\prime d})) \big)$
+			\STATE draw $a_d \sim \mbox{Categorical}(\boldsymbol{\pi}_d)$ 
 			\ENDIF
@@
 			\IF{$t_d=$ NA}
-			\STATE draw $\boldsymbol{\tau}^{new}_d \sim f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big),$ %from equation (\ref{eqn:latenttime}) (without the product term)
+			\STATE draw $\boldsymbol{\tau}^{\textrm{(new)}}_d \sim f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big),$ %from equation (\ref{eqn:latenttime}) (without the product term)
 			where we sample from this distribution using importance sampling\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
@@
 We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
-First, we compare the posterior probability of correct senders for each of the missing emails $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{obs}_{d}|\cdot)$ in Algorithm \ref{alg:PPE}.
+First, we compare the posterior probability of correct senders for each of the missing emails $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{\textrm{(obs)}}_{d}|\,\cdot)$ in Algorithm \ref{alg:PPE}.
 We call this measure the ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails.
@@
 	\end{equation}
-	with TP denoting true positive (i.e., $\boldsymbol{r}^{obs}_{dr}=\boldsymbol{r}^{pred}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{obs}_{dr}=1$ but $\boldsymbol{r}^{pred}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{obs}_{dr}=0$ but $\boldsymbol{r}^{pred}_{dr}=1$).
+with TP denoting true positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{dr}=\boldsymbol{r}^{\textrm{(pred)}}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{dr}=1$ but $\boldsymbol{r}^{\textrm{(pred)}}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{dr}=0$ but $\boldsymbol{r}^{\textrm{(pred)}}_{dr}=1$).
 Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{figure:PPEresults} (b) reveals slight difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal on average outperforms exponential.
-Finally, the prediction error for $d^{th}$ missing timestamp is estimated using the median of absolute relative errors\footnote{\cite{hyndman2006another} refer to this as median absolute percentage error (MdAPE).} across $N=500$ predictions:
+Finally, the prediction error for $d^{\textrm{th}}$ missing timestamp is estimated using the median of absolute relative errors, often referred to as  median absolute percentage error (MdAPE), across $N=500$ predictions:
 	\begin{figure}[!t]
@@
 	\end{figure}		
-	\iffalse
-	\begin{figure}[!t]
-		\centering
-		\includegraphics[width=1\textwidth]{img/PPEplotnew-1.png}	
-	\end{figure}
-	\fi
 	\begin{equation}
-		e_{\tau_d} = \mbox{median}\Big(\abs*{\frac{\tau^{obs}_d - \tau^{pred_1}_{d}}{\tau^{obs}_d}},\ldots, \abs*{\frac{\tau^{obs}_d - \tau^{pred_N}_{d}}{\tau^{obs}_d}}\Big).
+		\mbox{MdAPE}_{d} = \mbox{median}\Big(\Big\{\abs*{\frac{\tau^{\textrm{(obs)}}_d - \tau^{\textrm{(pred)}_1}_{d}}{\tau^{\textrm{(obs)}}_d}},\ldots, \abs*{\frac{\tau^{\textrm{(obs)}}_d - \tau^{\textrm{(pred)}_N}_{d}}{\tau^{\textrm{(obs)}}_d}}\Big\}\Big).
 	\end{equation}
-	Figure \ref{figure:PPEresults} (c) presents boxplots for the median absolute relative errors.
+	Figure \ref{figure:PPEresults} (c) presents boxplots for the median absolute percentage errors.
 where plot the estimates in a log-scale.
@@
 We formally generated entirely new data by simulating $N=500$ synthetic email datasets $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the generative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}\iffalse, where the pseudocode is outlined in Algorithm \ref{alg:PPC}\fi.
-For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution---the number of edges sent by each node, indegree distribution---the number of edges received by each node, receiver size distribution---the number of receivers on each edge, and a probability-probability (PP) plot for time increments.
+For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution---the number of edges sent by each node, indegree distribution---the number of edges received by each node, receiver size distribution---the number of receivers on each edge, and a probability--probability (P--P) plot for time increments.
 	\iffalse
@@
 			\ENDFOR
-			\STATE Store every $r^{th}$ new data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ 
+			\STATE Store every $r^{\textrm{th}}$ new data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$
 			\ENDFOR
@@
 	\end{equation*}
-	The posterior estimates of two temporal effects---``weekend" and ``PM"---indicate that if the ${(d-1)}^{th}$ email was sent during the weekend or after midday, then the time to $d^{th}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+	The posterior estimates of two temporal effects---``weekend" and ``PM"---indicate that if the ${(d-1)}^{\textrm{th}}$ email was sent during the weekend or after midday, then the time to $d^{\textrm{th}}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
 On the contrary, the covariates ``manager", ``outdegree", and ``indegree"  shorten the amount of time to next email.
@@
 	We have demonstrated the effectiveness of our model by analyzing Montgomery County government emails, where emails serve as a canonical example of directed edges with one sender and one or more receivers.
-The estimated effects for edge covariates reveal that the HEM is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), but we also learn about the effects of timestamp covariates by integrating a survival model for event timing.
+The estimated effects for edge covariates reveal that our model is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), but we also learn about the effects of timestamp covariates by integrating a survival model for event timing.
 Although we illustrate the entire framework and application in the context of one type of hyperedge, one sender and one or more receivers, our model can be easily extended to allow the opposite case, one or more sender and one receiver, by slight modification of the generative process (shown in Appendix A).
@@
 		\begin{aligned}
-			& \Pr(\boldsymbol{u}_{ad}|\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big),
+			& \Pr(\boldsymbol{u}_{ad}|\,\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big),
 		\end{aligned}
@@
 	To use this distribution efficiently, we derive a closed-form expression for $Z(\boldsymbol{\lambda}_{ad})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (i.e., $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
-We recognize that if $\boldsymbol{u}_{ad}$ were drawn via independent Bernoulli distributions in which $\Pr({u}_{adr}=1|\boldsymbol{b}, \boldsymbol{x}_{ad})$ was given by logit$(\lambda_{adr})$, then
+We recognize that if $\boldsymbol{u}_{ad}$ were drawn via independent Bernoulli distributions in which $\Pr({u}_{adr}=1|\,\boldsymbol{b}, \boldsymbol{x}_{ad})$ was given by logit$(\lambda_{adr})$, then
 	\begin{equation*}
-		\Pr(\boldsymbol{u}_{ad}|\boldsymbol{b}, \boldsymbol{x}_{ad}) \propto \exp\Big(\sum_{r \neq a } \lambda_{adr}u_{adr}\Big).  	 
+		\Pr(\boldsymbol{u}_{ad}|\,\boldsymbol{b}, \boldsymbol{x}_{ad}) \propto \exp\Big(\sum_{r \neq a } \lambda_{adr}u_{adr}\Big).
 	\end{equation*}
@@
 		\begin{aligned}
-			&\Pr(u_{adr}=1|\boldsymbol{u}_{ad[-r]}, \boldsymbol{b}, \boldsymbol{x}_{ad})
+			&\Pr(u_{adr}=1|\,\boldsymbol{u}_{ad[-r]}, \boldsymbol{b}, \boldsymbol{x}_{ad})
 			=\frac{\exp{(\lambda_{adr})}}{\exp{(\lambda_{adr})} + 1}.
@@
 		\end{equation*}
-		\newpage
+
 		\subsection*{Appendix C: Comparison of PPC results: log-normal vs. exponential}\label{appendix: PPCexp}

### 2018-06-21 paper/ba-HEM/ba-sample.tex
revision done by Bomin

@@
 The current state-of-the-art approach to dealing with hyperedges is to inappropriately break them into separate edges/events.
-Second, our model involves a novel receiver-selection distribution that is based on established edge formation models, but assures non-empty receiver lists.
+Second, our model involves a novel receiver selection distribution that is based on established edge formation models, but assures non-empty receiver lists.
 Third, the HEM integrates separate, but interacting, equations governing edge formation and event timing.
@@
 The data produced by such processes can be represented as dynamic directed networks---an object that has given rise to the development of several statistical model families.
-For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} characterize that networks are evolving as the senders of edges decide to add an edge to or remove an edge from a network one edge at a time, one sender at a time.
+For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} characterize that network evolutions occur as the senders decide to create or remove an edge from the existing network, one edge at a time.
 Event-based network models \citep{Butts2008,Vu2011,hunter2011dynamic,PerryWolfe2012} provide a general framework for modeling the realization of edges that occur as instances in continuous time streams of events.
@@
 
-	We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern time-stamped event formation: 1) the formation of the vertices that are incident to the hyperedge, and 2) the timing of the event in which the edge manifests.
+	We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern time-stamped event formation: 1) the formation of the vertices that are incident to the hyperedge, and 2) the timing of the event in which the hyperedge manifests.
 In what follows, we introduce the HEM by defining a generative process for time and hyperedge attributed event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference and present tests of our software implementation (Section \ref{sec:inference}).
@@
 	In this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time.
-Data generated under our model consists of $D$ unique edges.
-A single edge indexed by $d \in [D]$, where $[D]$ denotes a categorical set with $D$ levels $[D] = \{1,\ldots,D\}$, is represented by the three components: the sender $a_d \in [A]$, an indicator vector of receivers $\boldsymbol{r}_d = (u_{dr})_{r=1}^{A}$, such that $u_{dr}=1$ if $r$ is a receiver of edge $d$ and 0 otherwise, and the timestamp $t_d \in (0, \infty)$.
-For simplicity, we assume that edges are ordered by time such that $t_d \leq t_{d+1}$.
-While the model can be applied to two types of hyperedges---edges with (1) one sender and one or more receivers, and (2) one or more senders and one receiver---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast).
-One notable feature of our model generative process is that we draw auxiliary variables that serve as candidate data.
+Data generated under our model consists of $E$ unique hyperedge events occured between $A$ number of nodes.
+A single hyperedge event indexed by $e \in [E]$, where $[E]$ denotes a categorical set with $E$ levels $[E] = \{1,\ldots,E\}$, is represented by the three components: the sender $s_e \in [A]$, an indicator vector of receivers $\boldsymbol{r}_e$, such that $r_{ej}=1$ if $j \in [A]$ is a receiver of hyperedge event $e$ and 0 otherwise, and the timestamp $t_e \in (0, \infty)$.
+For simplicity, we assume that events are ordered by time such that $t_e \leq t_{e+1}$.
+While the model can be applied to two types of hyperedge events---events involving (1) one sender and one or more receivers, and (2) one or more senders and one receiver---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast).
+One notable feature of our generative process is that we draw auxiliary variables that serve as candidate data.
 Data is generated from the HEM through a sampling process applied to the auxiliary variables.
-The auxiliary variables drawn for edge $d$ include, for each sender $a$, a time increment from edge $d-1$ at which sender $a$ would send edge $d$, and an $A-1$ length vector indicating which nodes would receive edge $d$ if it were sent by sender $a$.
-The data generated for edge $d$ under the HEM corresponds to the sender that would send edge $d$ the soonest---at the smallest time increment from edge $d-1$.
-The receivers of edge $d$ generated under the HEM correspond to those receivers to which the sender with the minimum time increment would have sent edge $d$.
+The auxiliary variables drawn for event $e$ include, for each possible sender $i \in [A]$, a time increment from event $e-1$ at which sender $i$ would create event $e$, and an $A-1$ length vector indicating which nodes would be the receivers of event $e$ if it were directed by sender $i$.
+The data generated for event $e$ under the HEM corresponds to the sender that would create event $e$ the soonest---at the smallest time increment from event $e-1$.
+The receivers of event $e$ generated under the HEM correspond to those receivers toward which the sender with the minimum time increment would have directed event $e$.
 We explain these steps in more detail below.
-For hyperedges that involve one receiver and one or more senders, we treat $a_d$ to be an indicator vector of senders $\boldsymbol{a}_d = (u_{dr})_{a=1}^{A}$ and $r_d$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).
+For hyperedge events that involve one receiver and one or more senders, we treat $s_e$ to be an indicator vector of senders $\boldsymbol{s}_e$ and $r_e$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).
 
 	\subsection{Candidate receivers}\label{subsec: Tie}
-	For every possible sender--receiver pair $(a,r)_{a \neq r}$, we define the ``receiver intensity"---the conditional logit of the probability that edge $d$ is sent from sender $a$ to receiver $r$---as a linear combination of statistics relevant to the receiver selection process:
+	For every possible sender--receiver pair $(i,j)_{i \neq j}$, we define the ``receiver intensity"---the conditional logit of the probability that hyperedge event $e$ is being directed from sender $i$ to receiver $j$---as a linear combination of statistics relevant to the receiver selection process:
 	\begin{equation}
-		\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr},
+		\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej},
 	\end{equation}
-	where $\boldsymbol{b}$ is a $P$--dimensional vector of coefficients and $\boldsymbol{x}_{adr}$ is a set of receiver selection features.
-$\lambda_{adr}$ is the logit of the probability that edge $d$ is sent from sender $a$ to receiver $r$ conditional upon there being at least one other receiver to which sender $a$ sends edge $d$.
-In the case that there are no other receivers to which sender $a$ sends edge $d$, the logit of the probability that sender $a$ sends edge $d$ to receiver $r$ is $\infty$.
-The features in Equation 2.1 can capture common network processes that include, but are not limited to, popularity, reciprocity, and transitivity, as well as the effects of attribute features defined on the sender, receivers, and/or sender-receiver pairs (e.g., the gender of the sender and/or receiver, an indicator of whether the sender is a supervisor of the receiver's).
+	where $\boldsymbol{b}$ is a $P$--dimensional vector of coefficients and $\boldsymbol{x}_{iej}$ is a set of receiver selection features.
+$\lambda_{iej}$ is the logit of the probability that hyperedge event $e$ is directed from sender $i$ to receiver $j$, conditional upon there being at least one other receiver to which sender $i$ directs event $e$.
+In the case that there are no other receivers to which sender $i$ directs event $e$, the logit of the probability that sender $i$ directs event $e$ to receiver $j$ is $\infty$.
+The features in equation (2.1) can capture common network processes that include, but are not limited to, popularity, reciprocity, and transitivity, as well as the effects of attribute features defined on the sender, receivers, and/or sender-receiver pairs (e.g., the gender of the sender and/or receiver, an indicator of whether the sender is a supervisor of the receiver's).
 In addition, we include an intercept term to account for the average (or baseline) number of receivers.
@@
 
-	As we describe in greater detail below, under the HEM the sender of each edge is selected to be the sender that would send the respective edge with the greatest urgency.
-As such, under the HEM we assume that each sender would plan on sending each edge to some set of recipients at some time point.
-For each edge $d$ and each sender $a$, our model draws a list of candidate receivers that would be receivers on edge $d$ if $a$ were the sender.
-For an edge $d$, we first define an $A\times A$ matrix $\boldsymbol{u}_d$ where the $a^{\textrm{th}}$ row denotes sender $a$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $a$ intends to send edge $d$.
-We then assume that each receiver vector $\boldsymbol{u}_{ad}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
-In order to avoid drawing edges with no receivers, we define a probability measure ``MB$_{G}$" motivated by the Gibbs measure \citep{fellows2017removing}.
+	As we describe in greater detail below, under the HEM the sender of each hyperedge event is selected to be the sender that would create the respective event with the greatest urgency.
+As such, under the HEM we assume that each sender would plan on directing each event toward some set of receivers at some time point.
+For each event $e$ and each sender $i$, our model draws a list of candidate receivers that would be receivers of event $e$ if $i$ were the sender.
+For an event $e$, we first define an $A\times A$ matrix $\boldsymbol{u}_e$ where the $i$th row denotes sender $i$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $i$ intends to direct event $e$.
+We then assume that each receiver vector $\boldsymbol{u}_{ie}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
+In order to avoid drawing hyperedge events with no receivers, we define a probability measure ``MB$_{G}$" motivated by the Gibbs measure \citep{fellows2017removing}.
 The probability measure we define amounts to a non-empty Gibbs measure, in which the all-zero vector is excluded from the support of the multivariate Bernoulli distribution.
-As a result, this measure helps us to 1) allow a sender to select multiple receivers for a single edge, 2) force the sender to select at least one receiver, and 3) ensure a tractable normalizing constant for the receiver selection distribution.
-To be specific, we draw a binary vector $\boldsymbol{u}_{ad}= (u_{ad1},
-	\ldots, u_{adA})$ 
-	\begin{equation} \boldsymbol{u}_{ad}  \sim
-		\mbox{MB}_{G}(\boldsymbol{\lambda}_{ad}),
+As a result, this measure helps us to 1) allow a sender to select multiple receivers for a single event, 2) force the sender to select at least one receiver, and 3) ensure a tractable normalizing constant for the receiver selection distribution.
+To be specific, we draw a binary vector $\boldsymbol{u}_{ie}= (u_{ie1},
+	\ldots, u_{ieA})$ 
+	\begin{equation} \boldsymbol{u}_{ie}  \sim
+		\mbox{MB}_{G}(\boldsymbol{\lambda}_{ie}),
 	\end{equation}
-	where $\boldsymbol{\lambda}_{ad}= (\lambda_{ad1},
-	\ldots, \lambda_{adA})$. In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ad})$ as
+	where $\boldsymbol{\lambda}_{ie}= (\lambda_{ie1},
+	\ldots, \lambda_{ieA})$. In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ie})$ as
 	\begin{equation}
 		\begin{aligned}
-			&\Pr(\boldsymbol{u}_{ad}|\,\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0 )\big) + \sum_{r\neq a} \lambda_{adr}u_{adr}\Big) ,
+			&\Pr(\boldsymbol{u}_{ie}|\,\boldsymbol{b}, \boldsymbol{x}_{ie}) = \frac{1}{Z(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0 )\big) + \sum_{j\neq i} \lambda_{iej}u_{iej}\Big) ,
 		\end{aligned}
@@
 	\end{equation}
-	where $Z(\boldsymbol{\lambda}_{ad})= \prod_{r \neq a} \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
-Again, this is approximately equivalent to assuming that each $u_{adr}$ is drawn with the probability of 1 being logit($\lambda_{adr}$), excluding the case when $u_{adr}=0$ for all $r \in [A]$.
-This allows efficient inference since we can derive a closed-form normalizing constant which does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (i.e., $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
-We provide detailed derivation steps for the normalizing constant $Z(\boldsymbol{\lambda}_{ad})$ in Appendix B.
+	where $Z(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
+Again, this is approximately equivalent to assuming that each $u_{iej}$ is drawn with the probability of 1 being logit($\lambda_{iej}$), excluding the case when $u_{iej}=0$ for all $j \in [A]$.
+This allows efficient inference since we can derive a closed-form normalizing constant which does not require brute-force summation over the support of $\boldsymbol{u}_{ie}$ (i.e., $\forall \boldsymbol{u}_{ie} \in [0,1]^A$).
+We provide detailed derivation steps for the normalizing constant $Z(\boldsymbol{\lambda}_{ie})$ in Appendix B.
 
 	\subsection{Candidate timestamps}\label{subsec:Time}
-	To generate timing for each edge, the HEM first draws a candidate time at which the edge would be sent given the candidate sender and receiver combinations.
-The timing rate for sender $a$ and edge $d$ is
+	To generate timing for each event, the HEM first draws a candidate time at which the event would be created given the candidate sender and receiver combinations.
+The timing rate for sender $i$ and event $e$ is
 	\begin{equation}
-		\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad}),
+		\mu_{ie} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ie}),
 	\end{equation}
-	where $\boldsymbol{\eta}$ is a $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features---covariates that could affect timestamps of the edge, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
+	where $\boldsymbol{\eta}$ is a $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features---covariates that could affect timestamps of events, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
 
-	In modeling ``when," we do not directly model the timestamp $t_d$.
-Instead, we assume that each sender's ``time increment"---i.e., waiting time to next interaction since $t_{d-1}$---is drawn from a specific exponential family distribution.
-We define the time increment from edge $d-1$ to edge $d$ as $\tau_{d}$ (i.e., $\tau_{d}= t_d-t_{d-1}$) and specify the distribution of candidate timestamps with sender-specfic mean $\mu_{ad}$.
-Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume the mean and variance of the $\tau_{ad}$ satistify
+	In modeling ``when," we do not directly model the timestamp $t_e$.
+Instead, we assume that each sender's ``time increment"---i.e., waiting time to next event since $t_{e-1}$---is drawn from a specific exponential family distribution.
+We define the time increment from event $e-1$ to event $e$ as $\tau_{e}$ (i.e., $\tau_{e}= t_e-t_{e-1}$) and specify the distribution of candidate timestamps with sender-specfic mean $\mu_{ie}$.
+Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume the mean and variance of the $\tau_{ie}$ satistify
 	\begin{equation}
 		\begin{aligned}
-			E(\tau_{ad}) &= \mu_{ad},\\
-			V(\tau_{ad}) &= V(\mu_{ad}),
+			E(\tau_{ie}) &= \mu_{ie},\\
+			V(\tau_{ie}) &= V(\mu),
 		\end{aligned}
 	\end{equation}
-	where $\tau_{ad}$ here is a positive real number.
-Possible choices of distribution include exponential, Weibull, gamma, and log-normal\footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_d)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
+	where $\tau_{ie}$ here is a positive real number.
+Possible choices of distribution include exponential, Weibull, gamma, and log-normal\footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_e)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
 Based on the specific distribution, we may need other latent variables to draw the time increment, to account for the variance of time increments, beyond the coefficients for the features used to model the rate.
@@
 	\subsection{Senders, receivers, and timestamps}\label{subsec:Observed}
-	Finally, under the HEM the observed sender, receivers, and timestamp of edge $d$ is generated by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
+	Finally, under the HEM the observed sender, receivers, and timestamp of hyperedge event $e$ is generated by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
 	\begin{equation}
 		\begin{aligned}
-			a_d &= \mbox{argmin}_{a}(\tau_{ad}),\\
-			\boldsymbol{r}_d &= \boldsymbol{u}_{a_d d},\\
-			t_d &=t_{d-1} + \tau_{a_d d}.
+			s_e &= \mbox{argmin}_{i}(\tau_{ie}),\\
+			\boldsymbol{r}_e &= \boldsymbol{u}_{s_e e},\\
+			t_e &=t_{e-1} + \tau_{s_e e}.
 		\end{aligned}
@@
 		\centering
-		\includegraphics[width=0.625\textwidth]{img/diagram2.png}	
+		\includegraphics[width=0.625\textwidth]{img/diagramnew.png}	
 		\caption {An illustrative example of the generative process of the HEM.}
@@
 	\end{figure}	
-		Therefore, it is a sender-driven process in that the receivers and timestamps of an edge are jointly determined by the sender's urgency to send the edge to the selected receivers.
+		Therefore, it is a sender-driven process in that the receivers and timestamps of an event are jointly determined by the sender's urgency to direct the event to the selected receivers.
 Note that our generative process accounts for tied events such that in case of tied events (i.e., multiple senders draw exactly same candidate timestamps), we observe all of the tied events without assigning the orders of tied events.
-Algorithm \ref{alg:generative} summarizes the entire generative process for directed edges with one sender and one or more receivers, and Figure \ref{figure:diagram} presents an illustrative example on how the $d$th edge is generated, assuming $t_{d-1} = 0$ for simplicity.
+Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers, and Figure \ref{figure:diagram} presents an illustrative example on how the $e$th event is generated, assuming $t_{e-1} = 0$ and $A=5$ for simplicity.
 	\begin{algorithm}[!t]
@@
 		\SetAlgoLined
-		\caption{Generative Process: one sender and one or more receivers}
+		\caption{Generative process: one sender and one or more receivers}
 		\begin{algorithmic}
-			\STATE \textbf{Input}: number of edges and nodes $(D, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and the coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
+			\STATE \textbf{Input}: number of events and nodes $(E, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
 			\vskip 0.1in
-			\FOR{d=1 to D}
-			\FOR{a=1 to $A$}
-			\FOR{r=1 to $A$ (r $\neq$ a)}
-			\STATE	set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
+			\FOR{$e=1$ to $E$}
+			\FOR{$i=1$ to $A$}
+			\FOR{$j=1$ to $A$ ($j \neq i$)}
+			\STATE	set $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$
 			\ENDFOR
-			\STATE	draw $\boldsymbol{u}_{ad}  \sim
-			\mbox{MB}_G(\boldsymbol{\lambda}_{ad})$
-			\STATE		set $\mu_{ad} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ad})$
-			\STATE		draw $\tau_{ad} \sim f_\tau(\mu_{ad}, V(\mu_{ad}))$
+			\STATE	draw $\boldsymbol{u}_{ie}  \sim
+			\mbox{MB}_G(\boldsymbol{\lambda}_{ie})$
+			\STATE		set $\mu_{ie} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ie})$
+			\STATE		draw $\tau_{ie} \sim f_\tau(\mu_{ie}, V(\mu))$
 			\ENDFOR
@@
 			\IF{$n \geq 2$ tied events} 
-			\STATE	set $a_d, \ldots, a_{d+n-1}= \mbox{argmin}_{a}(\tau_{ad})$
-			\STATE	set $\boldsymbol{r}_d=\boldsymbol{u}_{a_d d},\ldots,\boldsymbol{r}_{d+n-1}=\boldsymbol{u}_{a_{d+n-1} d}$
-			\STATE	set $t_d, \ldots, t_{d+n-1}=t_{d-1} + \min_a\tau_{ad}$
-			\STATE		jump to $d = d+n$
+			\STATE	set $s_e,\ldots, s_{e+n-1}=\mbox{argmin}_{i}(\tau_{ie}),$
+			\STATE	set $\boldsymbol{r}_e=\boldsymbol{u}_{s_e e},\ldots,\boldsymbol{r}_{e+n-1}=\boldsymbol{u}_{s_{e+n-1} e}$
+			\STATE	set $t_e, \ldots, t_{e+n-1}=t_{e-1} + \min_i\tau_{ie}$
+			\STATE		jump to $e = e+n$
 			\ELSE
-			\STATE	set $a_d= \mbox{argmin}_{a}(\tau_{ad})$
-			\STATE		set $\boldsymbol{r}_d = \boldsymbol{u}_{a_d d}$
-			\STATE	set $t_d =t_{d-1} + \min_a\tau_{ad}$
+			\STATE	set $s_e= \mbox{argmin}_{i}(\tau_{ie})$
+			\STATE		set $\boldsymbol{r}_e = \boldsymbol{u}_{s_e e}$
+			\STATE	set $t_e =t_{e-1} + \min_i\tau_{ie}$
 			\ENDIF
@@
 	\section{Posterior inference}\label{sec:inference}
-	In this section we describe how we invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_d\}_{d=1}^D$, coefficients for edge covariates $\boldsymbol{b}$, and coefficients for timestamp covariates $\boldsymbol{\eta}$---conditioned on the observed data $\{(a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, covariates $\{(\boldsymbol{x}_d, \boldsymbol{y}_d)\}_{d=1}^D$, and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
+	In this section we describe how we invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_e\}_{e=1}^E$, coefficients for receiver selection features $\boldsymbol{b}$, and coefficients for event timing features $\boldsymbol{\eta}$---conditioned on the observed data $\{(s_e, \boldsymbol{r}_e, t_e)\}_{e=1}^E$, covariates $\{(\boldsymbol{x}_e, \boldsymbol{y}_e)\}_{e=1}^E$, and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
 We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each latent variable from its conditional posterior via a Metropolis-within-Gibbs sampling algorithm.
@@
 	\subsubsection{Candidate receivers}
-	In our model, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\,\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\,\boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
+	In our model, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\,\boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\,\boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
 However, it is possible to augment the data by candidate receivers $\boldsymbol{u}$ such that we can obtain their conditional posterior by conditioning on samples of $\boldsymbol{u}$.
@@
 	We use this common tool in Bayesian statistics called ``data augmentation" \citep{tanner1987calculation,neal2015exact}.
-Since $u_{adr}$ is a binary random variable, its new value may be sampled directly from a Bernoulli distribution with probability $p_{adr} =\frac{\exp(\lambda_{adr})}{\exp(\lambda_{adr})+\text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 )}$, since
+Since $u_{iej}$ is a binary random variable, its new value may be sampled directly from a Bernoulli distribution with probability $p_{iej} =\frac{\exp(\lambda_{iej})}{\exp(\lambda_{iej})+\text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 )}$, since
 	\begin{equation}
 		\begin{aligned}
-			&\Pr(u_{adr}=1| \,\boldsymbol{u}_{ad\backslash r}, \boldsymbol{b}, \boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})
-			\propto \mbox{exp}(\lambda_{adr});\\
-			&\Pr(u_{adr}=0|\, \boldsymbol{u}_{ad\backslash r},\boldsymbol{b}, \boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 ),
+			&\Pr(u_{iej}=1| \,\boldsymbol{u}_{ie\backslash j}, \boldsymbol{b}, \boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})
+			\propto \mbox{exp}(\lambda_{iej});\\
+			&\Pr(u_{iej}=0|\, \boldsymbol{u}_{ie\backslash j},\boldsymbol{b}, \boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 ),
 		\end{aligned}
@@
 	\end{equation}
-	where $I(\cdot)$ is the indicator function that is used to prevent from the instances where a sender chooses zero number of receivers. 
-	\subsubsection{Coefficients for edge covariates}
+	where the subscript ``$\backslash j$'' denotes a quantity excluding data from position $j$ and $I(\cdot)$ is the indicator function that is used to prevent from the instances where a sender selects zero number of receivers.
+	\subsubsection{Coefficients for receiver selection features}
 	Unlike the candidate receivers above, new values for $\boldsymbol{b}$ cannot be sampled directly from its conditional posterior, but may instead be obtained using the Metropolis--Hastings (M--H) algorithm.
@@
 	\begin{equation}
-		\Pr(\boldsymbol{b}| \,\boldsymbol{u}, \boldsymbol{x}, \boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D
-		\prod_{a=1}^A \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ad}\rVert_1 > 0)\big) + \sum\limits_{r \neq a} \lambda_{adr}u_{adr}\Big).
+		\Pr(\boldsymbol{b}| \,\boldsymbol{u}, \boldsymbol{x}, \boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{e=1}^E
+		\prod_{i=1}^A \frac{1}{Z(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0)\big) + \sum\limits_{j \neq i} \lambda_{iej}u_{iej}\Big).
 		\label{eqn:latentedge}
@@
 		\SetAlgoLined
-		\caption{MCMC Algorithm}
+		\caption{MCMC algorithm}
 		\begin{algorithmic}
@@
 			\vskip 0.1in
-			\FOR{o=1 to O}
-			\FOR{d=1 to D}
-			\FOR{a = 1 to A}
-			\FOR{r = 1 to A (r $\neq$ a)}
-			\STATE update $u_{adr}$ using Gibbs update ---equation (\ref{eqn:latentreceiver})
+			\FOR{$o=1$ to $O$}
+			\FOR{$e=1$ to $E$}
+			\FOR{$i = 1$ to $A$}
+			\FOR{$j = 1$ to $A$ ($j \neq i$)}
+			\STATE update $u_{iej}$ using Gibbs update ---equation (\ref{eqn:latentreceiver})
 			\ENDFOR
@@
 			\ENDFOR
-			\FOR{n=1 to $I_1$}
+			\FOR{$n=1$ to $I_1$}
 			\STATE update $\boldsymbol{b}$ using M--H algorithm---equation (\ref{eqn:latentedge})
 			\ENDFOR
-			\FOR{n=1 to $I_2$}
+			\FOR{$n=1$ to $I_2$}
 			\STATE update $\boldsymbol{\eta}$ using M--H algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
@@
 	\end{algorithm}
-	\subsubsection{Coefficients for timestamp covariates}
+	\subsubsection{Coefficients for event timing features}
 	Likewise, we use the M--H algorithm to update the latent variable $\boldsymbol{\eta}$.
@@
 	\begin{equation}
-		\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{d=1}^D\Big(f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
+		\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{e=1}^E\Big(f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, V(\mu)) \big)\Big),
 		\label{eqn:latenttime}
 	\end{equation}
-	where $f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))$ is the probability that the $d^{\textrm{th}}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{a_d d}$, and $\prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d},V(\mu_{a_d d})) \big)$ is the probability that the rest of (unobserved) senders for event $d$ all draw time increments greater than $\tau_d$.
+	where $f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))$ is the probability that the $e$th observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{s_e e}$, and $\prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie},V(\mu)) \big)$ is the probability that the rest of (unobserved) senders for event $e$ all draw time increments greater than $\tau_e$.
 Moreover, under the existence of tied events, the conditional posterior of $\boldsymbol{\eta}$ is written as
@@
 		\begin{aligned}
-			\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{d:t_d=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{a_d d}, V(\mu_{a_d d})) \\&\times \prod_{a \notin \{a_d\}_{d:t_d=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{a d}, V(\mu_{a_d d})) \big)\Big),
+			\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{e:t_e=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{s_e e}, V(\mu)) \\&\times \prod_{i \notin \{s_e\}_{e:t_e=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{ie}, V(\mu)) \big)\Big),
 		\end{aligned}
@@
 	\end{equation}
-	where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $D$ events ($M \leq D$).
-If $M=D$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
-Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional M--H update---e.g., $\Pr(k|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \,\boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution.
+	where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $E$ events ($M \leq E$).
+If $M=E$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
+Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional M--H update---e.g., $\Pr(k|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \,\boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution.
 	\subsection{Getting it Right (GiR) test} \label{subec:GiR}
@@
 
-	In the forward samples, both observable and unobservable variables are generated using Algorithm \ref{alg:generative}.
+	In the forward sampler, both observable and unobservable variables are generated using Algorithm \ref{alg:generative}.
 In the backward samples, unobservable variables are generated using the sampling equations for inference, which we derived in Section \ref{subsec:conditionaldist}.
-For each forward and backward sample that consists of $D$ number of edges, we save these statistics:
+For each forward and backward sample that consists of $E$ number of events, we save these statistics:
 	\begin{itemize}
-		\item[1.] Mean of observed receiver sizes $ \lVert \boldsymbol{r}_{d} \rVert_1 $ across $d=1,\ldots,D$,
-		\item[2.] Variance of observed receiver sizes $ \lVert \boldsymbol{r}_{d} \rVert_1 $ across $d=1,\ldots,D$,
-		\item[3.] Mean of time increments $\tau_d$ across $d=1,...,D$,
-		\item[4.] Variance of time increments $\tau_d$ across $d=1,...,D$,
+		\item[1.] Mean of observed receiver sizes $ \lVert \boldsymbol{r}_{e} \rVert_1 $ across $e=1,\ldots,E$,
+		\item[2.] Variance of observed receiver sizes $ \lVert \boldsymbol{r}_{e} \rVert_1 $ across $e=1,\ldots,E$,
+		\item[3.] Mean of time increments $\tau_e$ across $e=1,...,E$,
+		\item[4.] Variance of time increments $\tau_e$ across $e=1,...,E$,
 		\item[5.] $b_p$ value used to generate the samples $p = 1,...,P$,
@@
 
-	To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $D=100$ edges, $A=5$ actors, $P=4$ number of edge covariates, and $Q=3$ number of timestamp covariates per each forward or backward samples, using log-normal distibution for the time increments $f_\tau$.
+	To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $E=100$ events, $A=5$ nodes, $P=4$ number of receiver selection features, and $Q=3$ number of event timing features per each forward or backward sampler, using log-normal distibution for the time increments $f_\tau$.
 We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
@@
 In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
-We depict the GiR results using probability-probability (PP) plots, in which the empirical CDF values of the forward and backward samples are plotted on the $x$ and $y$ axes, respectively.
+We depict the GiR results using probability--probability (P--P) plots, in which the empirical CDF values of the forward and backward samples are plotted on the $x$ and $y$ axes, respectively.
 If the two samples are from equivalent distributions, the empirical CDF values should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
@@
 			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Mean of $\lVert \boldsymbol{r}_{d} \rVert_1 $}
+				\caption{Mean of $\lVert \boldsymbol{r}_{e} \rVert_1 $}
 				\includegraphics[width=\textwidth]{img/plot1.png}	
@@
 			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Variance of $\lVert \boldsymbol{r}_{d} \rVert_1 $}
+				\caption{Variance of $\lVert \boldsymbol{r}_{e} \rVert_1 $}
 				\includegraphics[width=\textwidth]{img/plot2.png}	
@@
 			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Mean of $\tau_d$}
+				\caption{Mean of $\tau_e$}
 				\includegraphics[width=\textwidth]{img/plot3.png}	
@@
 			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Variance of $\tau_d$}
+				\caption{Variance of $\tau_e$}
 				\includegraphics[width=\textwidth]{img/plot4.png}	
@@
 			\end{subfigure}   	   		   	   	   	   		   	   	   		   	   	
-			\caption{Probability-probability (PP) plots for the GiR test statistics.}
+			\caption{Probability--probability (P--P) plots for the GiR test statistics.}
 			\label{figure:GiRplot}
@@
 For this case study,
-	we formulate our model specification through definitions of the edge covariates $\boldsymbol{x}$ and timestamp covariates $\boldsymbol{y}$.
+	we formulate our model specification through definitions of the receiver selection features $\boldsymbol{x}$ and event timing features $\boldsymbol{y}$.
 We then report a suite of experiments---out-of-sample prediction for model selection and posterior predictive checks---that illustrate how alternative formulations of the HEM can be compared, and evaluate how well our model recovers the distribution of the observed data.
@@
 	\subsection{Covariates}\label{subsec:Covariates_email}
-	\subsubsection{Edge covariates}
+	\subsubsection{Receiver selection features}
 	A primary purpose of any network model is to use the posterior distributions to learn which features predict and/or explain edge formation (e.g., is edge formation reciprocal, are edges more likely to be formed among nodes with the same gender).
@@
 First, as we want to test whether gender plays a role in receiver selection process, we include three nodal covariates---the gender information of sender and receiver, and their homophily indicator (i.e., an indicator of whether the sender and receiver are of the same gender).
-Additionally, we include four interval-based nodal network covariates---outdegree of sender (i.e., the number of edges sent), indegree of receiver (the number of edges received), hyperedge size of sender (i.e., the number of total receivers of edges from the sender), and the interaction between (i.e., scalar product of) outdegree and hyperedge size---to study the effect of nodal behaviors on future interactions.
-For dyadic and triadic network effects, we employ the network statistics in \cite{PerryWolfe2012} and summarize past interaction behaviors based on the time interval prior to and including $t_{d-1}$.
-Specifically, our time interval tracks 7 days prior to the last email was sent $l_d = (t_{d-1}-7\mbox{ days}, t_{d-1}]$.
-For $a \in [A], r \in [A]$, and $d \in [D]$, we define 14 covariates for $\boldsymbol{x}_{adr}$:
+Additionally, we include four interval-based nodal network covariates---outdegree of sender (i.e., the number of emails sent), indegree of receiver (i.e., the number of emails received), hyperedge size of sender (i.e., the number of total receivers directed from the sender), and the interaction between (i.e., scalar product of) outdegree and hyperedge size---to study the effect of nodal behaviors on future interactions.
+For dyadic and triadic network effects, we employ the network statistics in \cite{PerryWolfe2012} and summarize past interaction behaviors based on the time interval prior to and including $t_{e-1}$.
+Specifically, our time interval tracks 7 days prior to the last email was sent $l_e= (t_{e-1}-7\mbox{ days}, t_{e-1}]$.
+For $i \in [A], j\in [A]$, and $e \in [E]$, we define 14 covariates for $\boldsymbol{x}_{iej}$:
 	\begin{itemize}
-		\item[1.] intercept: ${x}_{adr1} =1$;
-		\item[2.] $\mbox{gender}\_\,\mbox{sender}(a)$: ${x}_{adr2} = I(\mbox{gender of sender } a= \mbox{female});$
-		\item[3.] $\mbox{gender}\_\,\mbox{receiver}(r)$: ${x}_{adr3} = I(\mbox{gender of receiver } r= \mbox{female});$
-		\item[4.] $\mbox{gender}\_\,\mbox{homophily}(a, r)$: ${x}_{adr4} = I({x}_{adr2}={x}_{adr3});$ 	   		
-		\item[5.] $\mbox{outdegree}(a)$: ${x}_{adr5} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
-		\item[6.] $\mbox{indegree}(r)$: ${x}_{adr6}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime r} = 1)$;
-		\item[7.] $\mbox{hyperedge}\_\,\mbox{size}(a)$: ${x}_{adr7}=\sum_{d^\prime: t_{d^\prime} \in l_d} \sum_{r=1}^A I(a_{d^\prime} = a)\,I(u_{d^\prime r} = 1)$;
-		\item[8.] $\mbox{interaction}(a)$: ${x}_{adr8} = {x}_{adr5}\times{x}_{adr7};$
-		\item[9.] $\mbox{send}(a, r)$: ${x}_{adr9}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)\,I(u_{d^\prime r} = 1)$;
-		\item[10.] $\mbox{receive}(a, r)$: ${x}_{adr10}=\mbox{send}(r,a)$;
-		\item[11.] $\mbox{two}\_\,\mbox{send}(a, r)$: ${x}_{adr11} = \sum_{h \neq a, r} \mbox{send}(a,h)\,\mbox{send}(h,r)$;
-		\item[12.] $\mbox{two}\_\,\mbox{receive}(a, r)$: ${x}_{adr12}= \sum_{h \neq a, r} \mbox{send}(h,a)\,\mbox{send}(r,h)$;
-		\item[13.] $\mbox{sibling}(a, r)$: ${x}_{adr13}=\sum_{h \neq a, r} \mbox{send}(h,a)\,\mbox{send}(h,r)$;
-		\item[14.] $\mbox{cosibling}(a, r)$: ${x}_{adr14}=\sum_{h \neq a, r} \mbox{send}(a,h)\,\mbox{send}(r,h)$;
+		\item[1.] intercept: ${x}_{iej1} =1$;
+		\item[2.] $\mbox{gender}\_\,\mbox{sender}(i)$: ${x}_{iej2} = I(\mbox{gender of sender } i= \mbox{female});$
+		\item[3.] $\mbox{gender}\_\,\mbox{receiver}(j)$: ${x}_{iej3} = I(\mbox{gender of receiver } j= \mbox{female});$
+		\item[4.] $\mbox{gender}\_\,\mbox{homophily}(i, j)$: ${x}_{iej4} = I({x}_{iej2}={x}_{iej3});$ 	   		
+		\item[5.] $\mbox{outdegree}(i)$: ${x}_{iej5} =\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)$;
+		\item[6.] $\mbox{indegree}(r)$: ${x}_{iej6}=\sum_{d^\prime: t_{e^\prime} \in l_e} I(u_{e^\prime j} = 1)$;
+		\item[7.] $\mbox{hyperedge}\_\,\mbox{size}(i)$: ${x}_{iej7}=\sum_{e^\prime: t_{e^\prime} \in l_e} \sum_{j=1}^A I(s_{e^\prime} = i)\,I(u_{e^\prime j} = 1)$;
+		\item[8.] $\mbox{interaction}(i)$: ${x}_{iej8} = {x}_{iej5}\times{x}_{iej7};$
+		\item[9.] $\mbox{send}(i, j)$: ${x}_{iej9}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)\,I(u_{e^\prime j} = 1)$;
+		\item[10.] $\mbox{receive}(i,j)$: ${x}_{iej10}=\mbox{send}(j,i)$;
+		\item[11.] $\mbox{two}\_\,\mbox{send}(i,j)$: ${x}_{iej11} = \sum_{h \neq i,j} \mbox{send}(i,h)\,\mbox{send}(h,j)$;
+		\item[12.] $\mbox{two}\_\,\mbox{receive}(i,j)$: ${x}_{iej12}= \sum_{h \neq i, j} \mbox{send}(h,i)\,\mbox{send}(j,h)$;
+		\item[13.] $\mbox{sibling}(i, j)$: ${x}_{iej13}=\sum_{h \neq i, j} \mbox{send}(h,i)\,\mbox{send}(h,j)$;
+		\item[14.] $\mbox{cosibling}(i, j)$: ${x}_{iej14}=\sum_{h \neq i,j} \mbox{send}(i,h)\,\mbox{send}(j,h)$;
 	\end{itemize}
@@
 The network statistics (5--14) are designed so that their coefficients have a straightforward interpretations.
-The function ``outdegree$(a)$" and ``indegree$(r)$" measure the gregariousness and popularity effects of the node by counting the number of emails sent from $a$ and received by $r$, respectively, within the last 7 days.
-The gregariousness effect refers to the tendency for nodes that sent many edges in the past to continue to do so in the future.
-The popularity effect refers to the tendency for nodes that received many edges in the past to continue to do so in the future.
-Moreover, in order to capture the individual tendency of sent emails to two or more receivers, we include the statistic ``$\mbox{hyperedge}\_\,\mbox{size}(a)$"---the number of emails sent from $a$ within last 7 days where emails with $k$ number of receivers are counted as $k$ separate emails---as a variant of outdegree statistic, accounting for hyperedges.
-We also include the interaction term, ``$\mbox{interaction}(a)$", between outdegree and hyperedge size.
-This interaction allows us to model a possible tradeoff between the hyperedge size and the total number of edges sent.
-Dyadic statistics ``send$(a, r)$" and ``receive$(a, r)$" are defined as above such that these covariates measure the number of emails sent from $a$ to $r$ and $r$ to $a$, respectively, within the last 7 days.
-In the example of triadic statistics, the covariate ``$\mbox{two}\_\,\mbox{send}(a, r)$" counts the pairs of emails involving some node $h$ distinct from $a$ and $r$ such that emails from $a$ to $h$ and $h$ to $r$ are both observed within the last 7 days.
-This statistic captures the tendency for emails to close transitive triads (i.e., triads in which $a$ sends to $r$ and $h$, and $r$ sends to $h$).
+The function ``outdegree$(i)$" and ``indegree$(j)$" measure the gregariousness and popularity effects of the node by counting the number of emails sent from $i$ and received by $j$, respectively, within the last 7 days.
+The gregariousness effect refers to the tendency for nodes that created many events in the past to continue to do so in the future.
+The popularity effect refers to the tendency for nodes that were selected as receivers of many events in the past to continue to do so in the future.
+Moreover, in order to capture the individual tendency of senders to select two or more receivers, we include the statistic ``$\mbox{hyperedge}\_\,\mbox{size}(i)$"---the number of events directed from sender $i$ within last 7 days where events with $n$ number of receivers are counted as $n$ separate events---as a variant of outdegree statistic, accounting for hyperedges.
+We also include the interaction term, ``$\mbox{interaction}(i)$", between outdegree and hyperedge size.
+This interaction allows us to model a possible tradeoff between the hyperedge size and the total number of events created by $i$.
+Dyadic statistics ``send$(i, j)$" and ``receive$(i, j)$" are defined as above such that these covariates measure the number of events directed from $i$ to $j$ and $j$ to $i$, respectively, within the last 7 days.
+In the example of triadic statistics, the covariate ``$\mbox{two}\_\,\mbox{send}(i, j)$" counts the events involving some node $h$ distinct from $i$ and $j$ such that events from $i$ to $h$ and $h$ to $j$ are both observed within the last 7 days.
+This statistic captures the tendency for events to close transitive triads (i.e., triads in which $i$ directs to $j$ and $h$, and $j$ directs to $h$).
 We include other triadic covariates that behave similarly and exhibit analogous interpretations, which are illustrated in Figure \ref{figure:netstats}.
@@
 		\centering
-		\includegraphics[width=0.6\textwidth]{img/triad-1.png}	
-		\caption {Visualization of triadic statistics: 2-send, 2-receive, sibling, and cosibling.}
+		\includegraphics[width=0.75\textwidth]{img/triaddiagram.png}	
+		\caption {Visualization of triadic statistics: two\_\,send, two\_\,receive, sibling, and cosibling.}
 		\label{figure:netstats}
@@
 
-	\subsubsection{Timestamp covariates}
-For the event timing features $\boldsymbol{y}$, introduced in Section \ref{subsec:Time}, we identify a set of covariates which may affect ``time to the next email." Similar to the edge covariates, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
-In addition, we select some edge-specific covariates based on the temporal aspect of the $(d-1)^{\textrm{th}}$ email---e.g., whether the previous email was sent (1) during the weekend and (2) before or past midday (AM/PM)---since we expect the email interactions within county government to be less active during the weekend and in the evening.
+	\subsubsection{Event timing features}
+For the event timing features $\boldsymbol{y}$, introduced in Section \ref{subsec:Time}, we identify a set of covariates which may affect ``time to the next event." Similar to the receiver selection features, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
+In addition, we select some event-specific covariates based on the temporal aspect of the $(e-1)$th event---e.g., whether the previous email was sent (1) during the weekend and (2) before or past midday (AM/PM)---since we expect the email interactions within county government to be less active during the weekend and in the evening.
 To be specific, the timestamp statistics are defined as
 	\begin{itemize}
-		\item[1.] intercept: ${y}_{ad1} =1$;
-		\item[2.] $\mbox{gender}(a)$: ${y}_{ad2}=I(\mbox{gender of sender }a= \mbox{female})$;
-		\item[3.] $\mbox{manager}(a)$: ${y}_{ad3}=I(\mbox{sender }a \mbox{ is the County Manager})$;
-		\item[4.] $\mbox{outdegree}(a)$: ${y}_{ad4} =\sum_{d^\prime: t_{d^\prime} \in l_d} I(a_{d^\prime} = a)$;
-		\item[5.] $\mbox{indegree}(a)$: ${y}_{ad5}=\sum_{d^\prime: t_{d^\prime} \in l_d} I(u_{d^\prime a} = 1)$;
-		\item[6.] $\mbox{weekend}(d)$: ${y}_{ad6} = I(t_{d-1} \mbox{ is during the } \mbox{weekend})$;
-		\item[7.] $\mbox{PM}(d)$: ${y}_{ad7}= I(t_{d-1} \mbox{ in } \mbox{PM})$.
+		\item[1.] intercept: ${y}_{ie1} =1$;
+		\item[2.] $\mbox{gender}(i)$: ${y}_{ie2}=I(\mbox{gender of sender }i= \mbox{female})$;
+		\item[3.] $\mbox{manager}(i)$: ${y}_{ie3}=I(\mbox{sender }i \mbox{ is the County Manager})$;
+		\item[4.] $\mbox{outdegree}(i)$: ${y}_{ie4} =\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)$;
+		\item[5.] $\mbox{indegree}(i)$: ${y}_{ie5}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(u_{e^\prime i} = 1)$;
+		\item[6.] $\mbox{weekend}(e)$: ${y}_{ie6} = I(t_{e-1} \mbox{ is during the } \mbox{weekend})$;
+		\item[7.] $\mbox{PM}(e)$: ${y}_{ie7}= I(t_{e-1} \mbox{ in } \mbox{PM})$.
 	\end{itemize}
-	Note that our generative process for timestamps in Section \ref{subsec:Time} is sender-oriented where the sender determines when to send the email; thus we incorporate network statistics that depend only on $a$---specifically, the in and outdegrees of sender $a$.
+	Note that our generative process for timestamps in Section \ref{subsec:Time} is sender-oriented where the sender determines when to send the email; thus we incorporate network statistics that depend only on $i$---specifically, the in and outdegrees of sender $i$.
 
@@
 
-	The HEM defines a flexible family of models, each of which is indexed/defined by a set of features (i.e., the receiver selection features $\boldsymbol{x}$, the selection of the event timing features $\boldsymbol{y}$, and the distribution of time increments $f$).
+	The HEM defines a flexible family of models, each of which is indexed/defined by a set of features (i.e., the receiver selection features $\boldsymbol{x}$, the selection of event timing features $\boldsymbol{y}$, and the distribution of time increments $f$).
 Many of these components will be specified based on user expertise (e.g., regarding which features would drive receiver selection), but some decisions may require a data-driven approach to model specification.
-For example, though theoretical considerations may inform the specification of features, subject-matter expertise is unlikely to inform the decision regarding the family of the event time distribution.
+For example, though theoretical considerations may inform the specification of features, subject-matter expertise is unlikely to inform the decision regarding the family of event timing distribution.
 Furthermore, since different distribution families (and model specifications more generally) may involve different size parameter spaces, any data-driven approach to model comparison must guard against over-fitting the data.
@@
 		\spacingset{1}
-		\caption{Out-of-Sample Predictions}
+		\caption{Out-of-sample predictions}
 		\label{alg:PPE}
 		\begin{algorithmic}
-			\STATE {\bfseries Input}: data $ \{ (a_d, \boldsymbol{r}_d, t_d)\}_{d=1}^D$, 
-			number of new data to generate $R$, and initial values of $(\boldsymbol{b}, \boldsymbol{\eta}, \boldsymbol{u}, \sigma^2_\tau)$
+			\STATE {\bfseries Input}: data $ \{ (s_e, \boldsymbol{r}_e, t_e)\}_{e=1}^E$, 
+			number of new data to generate $D$, and initial values of $(\boldsymbol{b}, \boldsymbol{\eta}, \boldsymbol{u}, \sigma^2_\tau)$
 			\vskip 0.1in
 			\textbf{Test splits}:	
-			\STATE draw test senders (out of $D$ senders) 
-			\STATE draw test receivers (out of $D\times (A-1)$ receiver indicators $\{\{\boldsymbol{r}_{dr}\}_{r\in [A]_{\backslash a_d}}\}_{d=1}^D$)
-			\STATE draw test timestamps  (out of $D$ timestamps) 
+			\STATE draw test senders (out of $E$ senders) 
+			\STATE draw test receivers (out of $E\times (A-1)$ receiver indicators $\{\{\boldsymbol{r}_{ej}\}_{j\in [A]_{\backslash s_e}}\}_{e=1}^E$)
+			\STATE draw test timestamps  (out of $E$ timestamps) 
 			\STATE set the test data as ``missing" (NA)
@@
 			\textbf{Imputation and inference:}	
-			\FOR{$r=1$ {\bfseries to}  $R$}
 			\FOR{$d=1$ {\bfseries to}  $D$}
-			\IF{$a_d=$  NA}
-			\STATE compute the vector $\boldsymbol{\pi}_d$, where $\pi_{da}=f_{\tau}(\tau_{d}; \mu_{ad}, V(\mu_{ad}))\times \prod_{a^\prime\neq a}\big(1-F_{\tau}(\tau_{d}; \mu_{a^\prime d}, V(\mu_{a^\prime d})) \big)$
-			\STATE draw $a_d \sim \mbox{Categorical}(\boldsymbol{\pi}_d)$ 
+			\FOR{$e=1$ {\bfseries to}  $E$}
+			\IF{$s_e=$  NA}
+			\STATE compute $\boldsymbol{\pi}_e$, where $\pi_{ei}=f_{\tau}(\tau_{e}; \mu_{ie}, V(\mu))\times \prod_{i^\prime\neq i}\big(1-F_{\tau}(\tau_{e}; \mu_{i^\prime e}, V(\mu)) \big)$
+			\STATE draw $s_e \sim \mbox{Categorical}(\boldsymbol{\pi}_e)$ 
 			\ENDIF
-			\FOR{$r\in [A]_{\backslash a_d}$}
-			\IF{$r_{dr}=$ NA}
-			\STATE draw $r_{dr} \sim \mbox{Bernoulli}(p_{dr}),$
-			where $p_{dr}=\frac{\exp(\lambda_{adr})}{\exp(\lambda_{adr})+\text{I}(\lVert\boldsymbol{u}_{ad\backslash r}\rVert_1 > 0 )}$ %as defined in equation (\ref{eqn:latentreceiver})
+			\FOR{$j\in [A]_{\backslash s_e}$}
+			\IF{$r_{ej}=$ NA}
+			\STATE draw $r_{ej} \sim \mbox{Bernoulli}(p_{ej}),$
+			where $p_{ej}=\frac{\exp(\lambda_{iej})}{\exp(\lambda_{iej})+\text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 )}$ %as defined in equation (\ref{eqn:latentreceiver})
 			\ENDIF
 			\ENDFOR
-			\IF{$t_d=$ NA}
-			\STATE draw $\boldsymbol{\tau}^{\textrm{(new)}}_d \sim f_{\tau}(\tau_{d}; \mu_{a_d d}, V(\mu_{a_d d}))\times \prod_{a\neq a_d}\big(1-F_{\tau}(\tau_{d}; \mu_{a d}, V(\mu_{a_d d})) \big),$ %from equation (\ref{eqn:latenttime}) (without the product term)
-			where we sample from this distribution using importance sampling\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
+			\IF{$t_e=$ NA}
+			\STATE draw ${\tau}_e$ from its conditional distribution using importance sampling, %from equation (\ref{eqn:latenttime}) (without the product term) 
+	      where $P({\tau}_e|\, \cdot)\propto f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, V(\mu)) \big)$%\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
 			\ENDIF
@@
 
-	We evaluated the model’s ability to predict out-of-sample edges and timestamps on Montgomery County email data.
-We generated a train—test split of the data by randomly selecting 10\% of sender, receiver, and time-stamp variables to be held out.
+	We evaluated the model’s ability to predict out-of-sample events and timestamps on Montgomery County email data.
+We generated a train—test split of the data by randomly selecting 10\% of senders, receivers, and timestamp variables to be held out.
 Our model then imputed these missing variables during inference, sampling them from their conditional posterior along with the other latent variables.
 Algorithm \ref{alg:PPE} outlines this procedure in detail.
-We compare the predictive performance of two versions of the model, each with a different timing distribution over the time-increments using $N=500$.
+We compare the predictive performance of two versions of our model, each with a different timing distribution over the time increments using $N=500$.
 We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
-First, we compare the posterior probability of correct senders for each of the missing emails $\{d:a_d=\mbox{NA}\}$, which corresponds to $\pi_{a_{d}}=P(a_{d} = a^{\textrm{(obs)}}_{d}|\,\cdot)$ in Algorithm \ref{alg:PPE}.
-We call this measure the ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{a_{d}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{a_{d}}$---across the missing emails.
+First, we compare the posterior probability of correct senders for each of the missing emails $\{e:s_e=\mbox{NA}\}$, which corresponds to $\pi_{es_e}$ in Algorithm \ref{alg:PPE}.
+We call this measure the ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{es_{e}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{es_{e}}$---across the missing emails.
 The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing better performance than exponential distribution.
-Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $d$ and $r$ with $r_{dr}$=NA) by taking the harmonic mean of precision and recall:
+Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $e$ and $j$ with $r_{ej}$=NA) by taking the harmonic mean of precision and recall:
 	\begin{equation}
@@
 	\end{equation}
-with TP denoting true positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{dr}=\boldsymbol{r}^{\textrm{(pred)}}_{dr}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{dr}=1$ but $\boldsymbol{r}^{\textrm{(pred)}}_{dr}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{dr}=0$ but $\boldsymbol{r}^{\textrm{(pred)}}_{dr}=1$).
-Although the generative process for edges (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{figure:PPEresults} (b) reveals slight difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal on average outperforms exponential.
-Finally, the prediction error for $d^{\textrm{th}}$ missing timestamp is estimated using the median of absolute relative errors, often referred to as  median absolute percentage error (MdAPE), across $N=500$ predictions:
+with TP denoting true positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{ej}=\boldsymbol{r}^{\textrm{(pred)}}_{ej}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{ej}=1$ but $\boldsymbol{r}^{\textrm{(pred)}}_{ej}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{ej}=0$ but $\boldsymbol{r}^{\textrm{(pred)}}_{ej}=1$).
+Although the generative process for events (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{figure:PPEresults} (b) reveals slight difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal on average outperforms exponential.
+Finally, the prediction error for $d$th missing timestamp is estimated using the median of absolute relative errors, often referred to as  median absolute percentage error (MdAPE), across $N=500$ predictions:
 	\begin{figure}[!t]
@@
 	\begin{equation}
-		\mbox{MdAPE}_{d} = \mbox{median}\Big(\Big\{\abs*{\frac{\tau^{\textrm{(obs)}}_d - \tau^{\textrm{(pred)}_1}_{d}}{\tau^{\textrm{(obs)}}_d}},\ldots, \abs*{\frac{\tau^{\textrm{(obs)}}_d - \tau^{\textrm{(pred)}_N}_{d}}{\tau^{\textrm{(obs)}}_d}}\Big\}\Big).
+		\mbox{MdAPE}_{e} = \mbox{median}\Big(\Big\{\abs*{\frac{\tau^{\textrm{(obs)}}_e - \tau^{\textrm{(pred)}_1}_{e}}{\tau^{\textrm{(obs)}}_e}},\ldots, \abs*{\frac{\tau^{\textrm{(obs)}}_e - \tau^{\textrm{(pred)}_N}_{e}}{\tau^{\textrm{(obs)}}_e}}\Big\}\Big).
 	\end{equation}
@@
 where plot the estimates in a log-scale.
-Surprisingly, we have a huge benefit in the performance of timestamp prediction when we assume log-normal distribution for time-increments compared to exponential distribution.
+Surprisingly, we have a huge benefit in the performance of timestamp prediction when we assume log-normal distribution for time increments compared to exponential distribution.
 We speculate that this difference can be explained by overdispersion in exponential distribution, because there exists greater variability in the time increments of emails than would be expected under exponential distribution.
@@
 	In this section, we perform posterior predictive checks (PPC) \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for Montgomery County email data.
-We formally generated entirely new data by simulating $N=500$ synthetic email datasets $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$ from the generative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}\iffalse, where the pseudocode is outlined in Algorithm \ref{alg:PPC}\fi.
-For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution---the number of edges sent by each node, indegree distribution---the number of edges received by each node, receiver size distribution---the number of receivers on each edge, and a probability--probability (P--P) plot for time increments.
+We formally generated entirely new data by simulating $N=500$ synthetic email datasets $\{(s_{e}, \boldsymbol{r}_{e}, t_{e})\}_{e=1}^E$ from the generative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}\iffalse, where the pseudocode is outlined in Algorithm \ref{alg:PPC}\fi.
+For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution---the number of emails sent by each node, indegree distribution---the number of emails received by each node, receiver size distribution---the number of receivers on each emails, and a probability--probability (P--P) plot for time increments.
 	\iffalse
@@
 		\begin{algorithmic}
-			\STATE \textbf{Input}: number of data to generate $R$, covariates $(\boldsymbol{x},\boldsymbol{y})$, and estimated values of $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta})$\\
+			\STATE \textbf{Input}: number of data to generate $D$, covariates $(\boldsymbol{x},\boldsymbol{y})$, and estimated values of $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta})$\\
 			\vskip 0.1in
 
-			\FOR{$r=1$ {\bfseries to}  $R$}
-			\FOR{$d = 1$ {\bfseries to}  $D$} 
-			\STATE	Draw ($a_{d}$, $\boldsymbol{r}_{d}$, $t_{d}$) following Algorithm \ref{alg:generative}\\
+			\FOR{$d=1$ {\bfseries to}  $D$}
+			\FOR{$e= 1$ {\bfseries to}  $E$} 
+			\STATE	Draw ($s_{e}$, $\boldsymbol{r}_{e}$, $t_{e}$) following Algorithm \ref{alg:generative}\\
 			\ENDFOR
-			\STATE Store every $r^{\textrm{th}}$ new data $\{(a_{d}, \boldsymbol{r}_{d}, t_{d})\}_{d=1}^D$
+			\STATE Store every $d$th new data $\{(s_{e}, \boldsymbol{r}_{e}, t_{e})\}_{e=1}^E$
 			\ENDFOR
@@
 				\centering
-				\caption{PPplot for time increments}
+				\caption{P--P plot for time increments}
 				\includegraphics[width=0.56\textwidth]{img/timePPplot-1.png}	
@@
 It would be an interesting problem in future research to consider how the hyperedge size distribution can be further modified to capture this distribution more accurately.
-The plot on the lower right is the PP plot for time increments, which depicts the two cumulative distribution functions---one for simulated time increments and another for observed time increments---against each other in order to assess how closely two data sets agree.
-Here, the closeness to the diagonal line connecting $(0, 0)$ and $(1, 1)$ gives a measure of difference between the simulated and observed time increments, and our PP plot shows that we have great performance in reproducing the observed time distribution.
+The plot on the lower right is the P--P plot for time increments, which depicts the two cumulative distribution functions---one for simulated time increments and another for observed time increments---against each other in order to assess how closely two data sets agree.
+Here, the closeness to the diagonal line connecting $(0, 0)$ and $(1, 1)$ gives a measure of difference between the simulated and observed time increments, and our P--P plot shows that we have great performance in reproducing the observed timing distribution.
 Our findings from the predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are presented in Appendix C.
@@
 	\subsection{Exploratory analysis}\label{subsec:Result_email}
-	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we interpret the results from the HEM using the log-normal distribution.
+	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we interpret the results from the HEM using the log-normal distribution, with emphasis on understanding the effects of receiver selection and event timing features defined in Section \ref{subsec:Covariates_email}.
 We assume weakly informative priors for latent variables such as $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b=\boldsymbol{0}, \Sigma_b = 2\times I_P)$, $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta=\boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, and $\sigma_\tau^2 \sim \mbox{inverse-Gamma}(a=2, b=1)$, and run MCMC algorithm in Algorithm \ref{alg:MCMC} with $O=55,000$ outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
@@
 
-	\subsubsection{Coefficients for edge covariates}
+	\subsubsection{Coefficients for receiver selection features}
 	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$, where Figure \ref{figure:betaresults} (a) displays the coefficients for nodal covariates and \ref{figure:betaresults} (b) displays the coefficients for dyadic and triadic covariates.
@@
 	\begin{equation*}
-		\mbox{logit}(\lambda_{adr})=\log\Big(\frac{\lambda_{adr}}{1-\lambda_{adr}}\Big) =b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14},
+		\mbox{logit}(\lambda_{iej})=\log\Big(\frac{\lambda_{iej}}{1-\lambda_{iej}}\Big) =b_{1}+b_{2} x_{iej2}\ldots+b_{14}x_{iej14},
 	\end{equation*}
-	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratios $\frac{\lambda_{adr}}{1-\lambda_{adr}}=\exp(b_{1}+b_{2} x_{adr2}\ldots+b_{14}x_{adr14})$.
-	We find the effects of nodal coavariates ``gender of sender" and ``gender of receiver" are both nearly always negative in the posterior samples.
+	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratios $\frac{\lambda_{iej}}{1-\lambda_{iej}}=\exp(b_{1}+b_{2} x_{iej2}\ldots+b_{14}x_{iej14})$.
+First of all, we find the effects of nodal coavariates ``gender\_\,sender$(i)$" and ``gender\_\,receiver$(j)$" are both nearly always negative in the posterior samples.
 The log odds that any other node will be added as a receiver of an email is approximately 0.5 less if the sender is a woman.
-The posterior distribution of the statistic ``outdegree" is mostly negative, if sender $a$ sent $n$ number of emails to anyone last week, then sender $a$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $r$.
+The posterior distribution of the statistic ``outdegree$(i)$" is mostly negative, if sender $i$ sent $n$ number of emails to anyone last week, then sender $i$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $j$.
 However, this straightforward interpretation of the outdegree statistic only applies when the hyperedge size is low.
@@
 This scenario may arise from someone being responsible for distributing timely announcements.
-When we look at the effect of ``indegree," we see a clear popularity effect---those who have received a lot of emails a lot recently are likely to continue receiving a lot of emails.
-If the receiver $r$ received $n$ number of emails over the last week, sender $a$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $r$.
+When we look at the effect of ``indegree$(j)$," we see a clear popularity effect---those who have received a lot of emails a lot recently are likely to continue receiving a lot of emails.
+If the receiver $j$ received $n$ number of emails over the last week, sender $i$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $j$.
 
-	When we look at the effects of dyadic and triadic covariates, one thing that stands out is the large and positive posterior distribution of the statistic``send" (i.e., number of times sender $a$ sent emails to receiver $r$ over the last week) with the posterior mean $\hat{b}_9 = 0.274$, implying that if sender $a$ sent $n$ number of emails to $r$ last week, then sender $a$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $r$.
-The posterior distributions for the reciprocity effect (receive), and the four triadic effects, are all fairly evenly spread around zero, so our results do not justify conclusions regarding the nature of these effects in the Montgomery county email network.
+	When we look at the effects of dyadic and triadic covariates, one thing that stands out is the large and positive posterior distribution of the statistic ``send$(i,j)$" (i.e., number of times $i$ sent emails to $j$ over the last week) with the posterior mean $\hat{b}_9 = 0.274$, implying that if $i$ sent $n$ number of emails to $j$ last week, then sender $i$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $j$.
+The posterior distributions for the reciprocity effect (i.e., ``receive$(i, j)$''), and the four triadic effects, are all fairly evenly spread around zero, so our results do not justify conclusions regarding the nature of these effects in the Montgomery county email network.
 			\begin{figure}[!t]
@@
 			\end{figure}
-	\subsubsection{Coefficients for timestamp covariates}
-	For timestamp covariates, Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{\eta}$.
+	\subsubsection{Coefficients for event timing features}
+	For event timing features, Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{\eta}$.
 Note that interpretations of the estimated coefficients for $\hat{\boldsymbol{\eta}}$ should be based on the specified timeunit of the datset, which we use ``hour" for Montgomery county email data.
@@
 		\begin{aligned}
-			&\log(\tau_{ad}) \sim N(\mu_{ad}, \sigma_\tau^2), \mbox{ with }\\
-			&\mu_{ad} = \eta_{1}+\eta_{2} y_{ad2}\ldots+\eta_{7}y_{ad7}.
+			&\log(\tau_{ie}) \sim N(\mu_{ie}, \sigma_\tau^2), \mbox{ with }\\
+			&\mu_{ie} = \eta_{1}+\eta_{2} y_{ie2}\ldots+\eta_{7}y_{ie7}.
 		\end{aligned}
 	\end{equation*}
-	The posterior estimates of two temporal effects---``weekend" and ``PM"---indicate that if the ${(d-1)}^{\textrm{th}}$ email was sent during the weekend or after midday, then the time to $d^{\textrm{th}}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
-On the contrary, the covariates ``manager", ``outdegree", and ``indegree"  shorten the amount of time to next email.
-For example, being a county manager (i.e., the lead county administrator) lowers the expected value of $\log(\tau_{ad})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
-The posterior estimates for the  ``outdegree" and ``indegree" statistics, where the posterior means are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
+	The posterior estimates of two temporal effects---``weekend$(e)$" and ``PM$(e)$"---indicate that if the ${(e-1)}$th email was sent during the weekend or after midday, then the time to $e$th email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+On the contrary, the covariates ``manager$(i)$", ``outdegree$(i)$", and ``indegree$(i)$"  shorten the amount of time to next email.
+For example, being a county manager (i.e., the lead county administrator) lowers the expected value of $\log(\tau_{ie})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
+The posterior estimates for the  ``outdegree$(i)$" and ``indegree$(i)$" statistics, where the posterior means are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
 These effects indicate that those who are involved in either sending or receiving a lot of emails recently are likely to send emails with greater speed.
@@
 	\section{Conclusion}\label{sec:conclusion}
-	Motivated by a growing class of dynamic network models which deal with edges exchanged in continuous time, the hyperedge event model (HEM) can effectively learn the underlying dynamics in edge and timestamp formations, providing novel insights to the literature.
-The HEM explicitly models hyperedges through a receiver-selection distribution that forces the sender to select at least one recevier, which is a more realistic approach for events with one sender and one or more receivers and one or more sender and one receiver compared to treating them as pure duplicates.
+	Motivated by a growing class of dynamic network models which deal with events recorded in continuous time, the hyperedge event model (HEM) can effectively learn the underlying dynamics in events and their corresponding timestamp formations, providing novel insights to the literature.
+The HEM explicitly models hyperedges through a receiver selection distribution that forces the sender to select at least one recevier, which is a more realistic approach for events with one sender and one or more receivers and one or more sender and one receiver compared to treating them as pure duplicates.
 In modeling the timestamps (more precisely time increments) of events, our generalized linear model (GLM) based formulation offers new innovations by eliminating the need to stick with one parameter distribution (e.g., exponential distribution).
-To our knowledge, the HEM is the only existing model that can be used to generate the sender, recipients, and time stamp of interactions in real time.
+To our knowledge, the HEM is the only existing model that can be used to generate the sender, receivers, and timestamp of interactions in real time.
 To make better use of the proposed model, we provide an algorithm for predictive experiments that help to learn which specification of HEM provides a better fit to the data.
 
-	We have demonstrated the effectiveness of our model by analyzing Montgomery County government emails, where emails serve as a canonical example of directed edges with one sender and one or more receivers.
-The estimated effects for edge covariates reveal that our model is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), but we also learn about the effects of timestamp covariates by integrating a survival model for event timing.
+	We have demonstrated the effectiveness of our model by analyzing the Montgomery County government emails, where emails serve as a canonical example of directed hyperedge events with one sender and one or more receivers.
+The estimated effects for receiver selection features reveal that our model is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), but we also learn about the effects of event timing features by integrating a survival model for event timing.
 Although we illustrate the entire framework and application in the context of one type of hyperedge, one sender and one or more receivers, our model can be easily extended to allow the opposite case, one or more sender and one receiver, by slight modification of the generative process (shown in Appendix A).
@@
 		\SetAlgoLined
-		\caption{Generative Process: one receiver and one or more senders}
+		\caption{Generative process: one receiver and one or more senders}
 		\begin{algorithmic}
-			\STATE \textbf{Input}: number of edges and nodes $(D, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and the coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
+			\STATE \textbf{Input}: number of events and nodes $(E, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
 			\vskip 0.1in				
-			\FOR{d=1 to D}
-			\FOR{r=1 to $A$}
-			\FOR{a=1 to $A$ (a $\neq$ r)}
-			\STATE	set $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$
+			\FOR{$e=1$ to $E$}
+			\FOR{$j=1$ to $A$}
+			\FOR{$i=1$ to $A$ ($i \neq j$)}
+			\STATE	set $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$
 			\ENDFOR
-			\STATE	draw $\boldsymbol{u}_{rd}  \sim
-			\mbox{MB}_G(\boldsymbol{\lambda}_{rd})$
-			\STATE		set $\mu_{rd} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{rd})$
-			\STATE		draw $\tau_{rd} \sim f_\tau(\mu_{rd}, \sigma_\tau^2)$
+			\STATE	draw $\boldsymbol{u}_{je}  \sim
+			\mbox{MB}_G(\boldsymbol{\lambda}_{je})$
+			\STATE		set $\mu_{je} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{je})$
+			\STATE		draw $\tau_{je} \sim f_\tau(\mu_{je}, V(\mu))$
 			\ENDFOR
 			\IF {$n \geq 2$ tied events} 
-			\STATE	set ${r}_d=\mbox{argmin}_{r}(\tau_{rd})$
-			\STATE	set $\boldsymbol{a}_d=\boldsymbol{u}_{r_d d},\ldots,\boldsymbol{a}_{d+n-1}=\boldsymbol{u}_{r_{d+n-1} d}$
-			\STATE	set $t_d, \ldots, t_{d+n-1}=t_{d-1} + \min_r\tau_{rd}$
-			\STATE		jump to $d = d+n$
+			\STATE	set ${r}_e,\ldots, r_{e+n-1}=\mbox{argmin}_{j}(\tau_{je})$
+			\STATE	set $\boldsymbol{s}_e=\boldsymbol{u}_{r_e e},\ldots,\boldsymbol{s}_{e+n-1}=\boldsymbol{u}_{r_{e+n-1} d}$
+			\STATE	set $t_e, \ldots, t_{e+n-1}=t_{e-1} + \min_j\tau_{je}$
+			\STATE		jump to $e = e+n$
 			\ELSE
-			\STATE	set ${r}_d = \mbox{argmin}_{r}(\tau_{rd}) $
-			\STATE	set $\boldsymbol{a}_d= \boldsymbol{u}_{r_d d}$
-			\STATE	set $t_d =t_{d-1} + \min_r\tau_{rd}$
+			\STATE	set ${r}_e = \mbox{argmin}_{j}(\tau_{je}) $
+			\STATE	set $\boldsymbol{s}_e= \boldsymbol{u}_{r_e e}$
+			\STATE	set $t_e =t_{e-1} + \min_j\tau_{je}$
 			\ENDIF
@@
 	\subsection*{Appendix B: Normalizing constant of MB$_{G}$}\label{appendix: non-empty Gibbs measure}
-	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure---defines the probability of sender $a$ selecting the binary receiver vector $\boldsymbol{u}_{ad}$ as
+	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure---defines the probability of sender $i$ selecting the binary receiver vector $\boldsymbol{u}_{ie}$ as
 	\begin{equation*} 
 		\begin{aligned}
-			& \Pr(\boldsymbol{u}_{ad}|\,\boldsymbol{b}, \boldsymbol{x}_{ad}) = \frac{1}{Z(\boldsymbol{\lambda}_{ad})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big),
+			& \Pr(\boldsymbol{u}_{ie}|\,\boldsymbol{b}, \boldsymbol{x}_{ie}) = \frac{1}{Z(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ie} \rVert_1 > 0)\big) + \sum_{j \neq i} \lambda_{iej}u_{iej} \Big),
 		\end{aligned}
 	\end{equation*}
-	where the receiver intensity is a linear combination of edge covariates---i.e., $\lambda_{adr} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{adr}$---as defined in Secton \ref{subsec: Tie}.
+	where the receiver intensity is a linear combination of receiver selection features---i.e., $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$---as defined in Secton \ref{subsec: Tie}.
 
-	To use this distribution efficiently, we derive a closed-form expression for $Z(\boldsymbol{\lambda}_{ad})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ad}$ (i.e., $\forall \boldsymbol{u}_{ad} \in [0,1]^A$).
-We recognize that if $\boldsymbol{u}_{ad}$ were drawn via independent Bernoulli distributions in which $\Pr({u}_{adr}=1|\,\boldsymbol{b}, \boldsymbol{x}_{ad})$ was given by logit$(\lambda_{adr})$, then
+	To use this distribution efficiently, we derive a closed-form expression for $Z(\boldsymbol{\lambda}_{ie})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ie}$ (i.e., $\forall \boldsymbol{u}_{ie} \in [0,1]^A$).
+We recognize that if $\boldsymbol{u}_{ie}$ were drawn via independent Bernoulli distributions in which $\Pr({u}_{iej}=1|\,\boldsymbol{b}, \boldsymbol{x}_{ie})$ was given by logit$(\lambda_{iej})$, then
 	\begin{equation*}
-		\Pr(\boldsymbol{u}_{ad}|\,\boldsymbol{b}, \boldsymbol{x}_{ad}) \propto \exp\Big(\sum_{r \neq a } \lambda_{adr}u_{adr}\Big).
+		\Pr(\boldsymbol{u}_{ie}|\,\boldsymbol{b}, \boldsymbol{x}_{ie}) \propto \exp\Big(\sum_{j\neq i} \lambda_{iej}u_{iej}\Big).
 	\end{equation*}
@@
 		\begin{aligned}
-			&\Pr(u_{adr}=1|\,\boldsymbol{u}_{ad[-r]}, \boldsymbol{b}, \boldsymbol{x}_{ad})
-			=\frac{\exp{(\lambda_{adr})}}{\exp{(\lambda_{adr})} + 1}.
+			&\Pr(u_{iej}=1|\,\boldsymbol{u}_{ie\backslash j}, \boldsymbol{b}, \boldsymbol{x}_{ie})
+			=\frac{\exp{(\lambda_{iej})}}{\exp{(\lambda_{iej})} + 1},
 		\end{aligned}\end{equation*}
-		We denote the logistic-Bernoulli normalizing constant as $Z^{l}(\boldsymbol{\lambda}_{ad})$, which is defined as 
+		where the subscript ``$\backslash j$'' denotes a quantity excluding data from position $j$.
+Now we denote the logistic-Bernoulli normalizing constant as $Z^{l}(\boldsymbol{\lambda}_{ie})$, which is defined as
 		\begin{equation*}
-			Z^{l}( \boldsymbol{\lambda}_{ad})=\sum_{\boldsymbol{u}_{ad} \in [0,1]^{A}} \exp\Big(\sum_{r\neq a} \lambda_{adr}u_{adr}\Big).
+			Z^{l}( \boldsymbol{\lambda}_{ie})=\sum_{\boldsymbol{u}_{ie} \in [0,1]^{A}} \exp\Big(\sum_{j\neq i} \lambda_{iej}u_{iej}\Big).
 		\end{equation*}
@@
 			\begin{aligned}
-				&\exp\Big(\mbox{log}\Big(\text{I}(\lVert \boldsymbol{u}_{ad} \rVert_1 > 0)\Big) + \sum_{r \neq a} \lambda_{adr}u_{adr} \Big)= \exp\Big( \sum_{r \neq a} \lambda_{adr}u_{adr} \Big),
+				&\exp\Big(\mbox{log}\Big(\text{I}(\lVert \boldsymbol{u}_{ie} \rVert_1 > 0)\Big) + \sum_{j\neq i} \lambda_{iej}u_{iej} \Big)= \exp\Big( \sum_{j \neq i} \lambda_{iej}u_{iej} \Big),
 			\end{aligned}
 		\end{equation*}
-		except when $\lVert \boldsymbol{u}_{ad} \rVert_1=0$, we note that 
+		except when $\lVert \boldsymbol{u}_{ie} \rVert_1=0$, we note that 
 		\begin{equation*}
 			\begin{aligned}
-				Z(\boldsymbol{\lambda}_{ad})& = Z^{l}(\boldsymbol{\lambda}_{ad}) -\exp\Big( \sum\limits_{\forall u_{adr}=0}\lambda_{adr}u_{adr} \Big)
-				\\& = Z^{l}(\boldsymbol{\lambda}_{ad}) -  1.
+				Z(\boldsymbol{\lambda}_{ie})& = Z^{l}(\boldsymbol{\lambda}_{ie}) -\exp\Big( \sum\limits_{\forall u_{iej}=0}\lambda_{iej}u_{iej} \Big)
+				\\& = Z^{l}(\boldsymbol{\lambda}_{ie}) -  1.
 			\end{aligned}
 		\end{equation*}
-		We can therefore derive a closed form expression for $Z(\boldsymbol{\lambda}_{ad})$ via a closed form expression for $Z^{l}(\boldsymbol{\lambda}_{ad})$.
+		We can therefore derive a closed form expression for $Z(\boldsymbol{\lambda}_{ie})$ via a closed form expression for $Z^{l}(\boldsymbol{\lambda}_{ie})$.
 This can be done by looking at the probability of the zero vector under the logistic-Bernoulli model:
@@
 			\begin{aligned}
-				&\frac{1}{Z^{l}(\boldsymbol{\lambda}_{ad})}\exp\Big(\sum\limits_{\forall u_{adr}=0}\lambda_{adr}u_{adr} \Big)= \prod_{r \neq a}   \Big(1-\frac{ \exp{(\lambda_{adr})}}{\exp{(\lambda_{adr})} + 1}\Big).
+				&\frac{1}{Z^{l}(\boldsymbol{\lambda}_{ie})}\exp\Big(\sum\limits_{\forall u_{iej}=0}\lambda_{iej}u_{iej} \Big)= \prod_{j \neq i}   \Big(1-\frac{ \exp{(\lambda_{iej})}}{\exp{(\lambda_{iej})} + 1}\Big).
 			\end{aligned}  
@@
 			\begin{aligned}
-				& \frac{1}{Z^{l}(\boldsymbol{\lambda}_{ad})} &= \prod\limits_{r \neq a}\frac{1}{ \exp(\lambda_{adr})+ 1}.
+				& \frac{1}{Z^{l}(\boldsymbol{\lambda}_{ie})} &= \prod\limits_{j \neq i}\frac{1}{ \exp(\lambda_{iej})+ 1}.
 			\end{aligned}  
@@
 		\begin{equation*}
-			\begin{aligned}Z(\boldsymbol{\lambda}_{ad}) = \prod_{r \neq a } \big(\mbox{exp}(\lambda_{adr}) + 1\big)-1.
+			\begin{aligned}Z(\boldsymbol{\lambda}_{ie}) = \prod_{j \neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1.
 			\end{aligned}  
@@
 					\centering
-					\caption{PPplot for time increments}
+					\caption{P--P plot for time increments}
 					\includegraphics[width=0.56\textwidth]{img/timePPplot2-1.png}

### 2018-06-22 paper/ba-HEM/ba-sample.tex
made edits to sections 1-3 and beginning of 4

@@
 			}
-			\address[addr4]{ Microsoft Research NYC
+			\address[addr4]{Microsoft Research NYC
 				\printead{e4}
@@
 Event-based network models \citep{Butts2008,Vu2011,hunter2011dynamic,PerryWolfe2012} provide a general framework for modeling the realization of edges that occur as instances in continuous time streams of events.
-These models are flexible enough to specify a generative model that accounts for the ways in which past network structure begets future network structure (e.g., nodes that sent a lot of edges in the past will send a lot in the future, if node $i$ sent a tie to node $j$ recently, then node $j$ will send one to node $i$ in the near future).
-Thus, dynamic network models are very useful to understand which traits and behaviours are predictive of interactions.
+This family of models is flexible enough to account for the many ways in which past network structures beget future ones---e.g., if node $i$ directed a tie to node $j$ recently, then node $j$ will direct one to node $i$ in the near future---and useful for understanding the traits and behaviours that are predictive of interactions.
 
 	A major limitation of existing dynamic network models is that they apply to edges with one sender and one receiver.
-A lot of dynamic network data arise as ``hyperedges'' \citep{karypis1999multilevel,ghoshal2009random,zlatic2009hypergraph,zhang2010hypergraph} that include one sender and multiple receivers or one receiver and multiple senders.
-For example, email networks \citep{newman2002email} arise with one sender and possibly multiple receviers;  networks formed between neurons via axons and dendrites have one sender and multiple receivers (axons) or one receiver and multiple senders (dendrites) \citep{partzsch2012developing}.
-Networks formed through the analysis of legislative bill cosponsorhip \citep{fowler2006legislative} arise with multiple senders (cosponsors) and one receiver (sponsor); and networks formed through the analysis of economic sanctions \citep{cranmer2014reciprocity} between countries arise with multiple sending countries and one target country.
+Dynamic network data often naturally arise as ``hyperedges'' \citep{karypis1999multilevel,ghoshal2009random,zlatic2009hypergraph,zhang2010hypergraph} that include one sender and multiple receivers or one receiver and multiple senders.
+For example, in email networks \citep{newman2002email}, each email encodes a hyperedge from one sender to one or more receviers.
+Networks formed between neurons via axons and dendrites involve hyperedges with one sender and multiple receivers (axons) or one receiver and multiple senders (dendrites) \citep{partzsch2012developing}.
+Networks formed through the cosponsorhip of legislative bills \citep{fowler2006legislative} involve hyperedges with multiple senders (cosponsors) and one receiver (sponsor).
+Economic sanctions between countries \citep{cranmer2014reciprocity} induce networks with hyperedges between multiple sending countries and one target country.
 Existing models require researchers to alter hyperedge data to fit with the pairwise edge structure of the model.
-For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involves one sender and one or more receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), to construct approximate likelihood function in their inferential framework for model parameters.
-Similarly, \cite{fan2009learning} duplicate emails sent from one sender to one or more receivers and randomly jitter the sent times in order to avoid the violation of the assumption that two events cannot occur at the exact same time.
+For instance, \cite{PerryWolfe2012} treat multicast interactions---one type of directed hyperedge which involves one sender and one or more receivers---via duplication (i.e., obtain pairwise interactions from the original multicast), to construct an approximate likelihood function in their inferential framework for model parameters.
+Similarly, \cite{fan2009learning} duplicate emails sent from one sender to one or more receivers and randomly jitter the sent times in order to avoid violating the assumption that two events cannot occur at the exact same time.
 % There have been numerous studies for hyperedges under the hypergraph theory \citep{karypis1999multilevel} in phyics literature, including a random hypergraph model \citep{ghoshal2009random}, but most of them are designed specifically for engineering applications---e.g., multiple tagging networks \citep{zlatic2009hypergraph,zhang2010hypergraph}, cellular networks \citep{klamt2009hypergraphs}, and personalized recommendations \citep{zhang2010personalized,blattner2009b}---with lack of extensive efforts to incorportate hyperedge modeling into general statistical framework.
 
-	We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern time-stamped event formation: 1) the formation of the vertices that are incident to the hyperedge, and 2) the timing of the event in which the hyperedge manifests.
-In what follows, we introduce the HEM by defining a generative process for time and hyperedge attributed event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference and present tests of our software implementation (Section \ref{sec:inference}).
-After defining the structure of and deriving Bayesian inference methods for the HEM, we demonstrate the model's applicability by analyzing data from a corpus of internal county government emails.
-In the application we illustrate model selection, posterior predictive checks, and exploratory analysis (Section \ref{sec:Emails}).
-Finally, the paper finishes in Section \ref{sec:conclusion} with conclusion and discussion.
+	We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern hyperedge event formation: (1) the formation of the vertices that are incident to the hyperedge, and (2) the timing of the hyperedge event.
+In what follows, we define the HEM's generative process for hyperedge event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference, and present tests of our software implementation (Section \ref{sec:inference}).
+We then demonstrate our model's applicability in a case study (Section \ref{sec:Emails}) where we analyze a corpus of internal county government emails and illustrate how to perform model selection, posterior predictive checks, and exploratory analysis using our model.
+We conclude in Section \ref{sec:conclusion}.~\looseness=-1
 
@@
 
-	In this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time.
-Data generated under our model consists of $E$ unique hyperedge events occured between $A$ number of nodes.
-A single hyperedge event indexed by $e \in [E]$, where $[E]$ denotes a categorical set with $E$ levels $[E] = \{1,\ldots,E\}$, is represented by the three components: the sender $s_e \in [A]$, an indicator vector of receivers $\boldsymbol{r}_e$, such that $r_{ej}=1$ if $j \in [A]$ is a receiver of hyperedge event $e$ and 0 otherwise, and the timestamp $t_e \in (0, \infty)$.
+	% In this section we define the HEM by describing a process according to which hyperedge events are generated in continuous time.
+
+	The hyperedge event model (HEM) specifies a generative process for $E$ unique hyperedge events that occur between $A$ nodes.
+A single hyperedge event is indexed by $e \in [E]$---where $[E]$ denotes a categorical set with $E$ levels $[E] = \{1,\ldots,E\}$---and consists of three components: the sender $s_e \in [A]$, an indicator vector of receivers $\boldsymbol{r}_e$---where $r_{ej}=1$ if $j \in [A]$ is a receiver of hyperedge event $e$ and 0 otherwise---and the timestamp $t_e \in (0, \infty)$.
 For simplicity, we assume that events are ordered by time such that $t_e \leq t_{e+1}$.
@@
 We explain these steps in more detail below.
-For hyperedge events that involve one receiver and one or more senders, we treat $s_e$ to be an indicator vector of senders $\boldsymbol{s}_e$ and $r_e$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).
+For hyperedge events that involve one receiver and one or more senders, we treat $s_e$ to be an indicator vector of senders $\boldsymbol{s}_e$ and $r_e$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).~\looseness=-1
 
 	\subsection{Candidate receivers}\label{subsec: Tie}
-	For every possible sender--receiver pair $(i,j)_{i \neq j}$, we define the ``receiver intensity"---the conditional logit of the probability that hyperedge event $e$ is being directed from sender $i$ to receiver $j$---as a linear combination of statistics relevant to the receiver selection process:
+	% For every possible sender--receiver pair $(i,j)$ where $i \!\neq\!
+j$, we define the ``receiver intensity"---i.e., the conditional logit of the probability that hyperedge event $e$ is being directed from sender $i$ to receiver $j$---as a linear combination of statistics relevant to the receiver selection process:
+	For every possible sender--receiver pair $(i,j)$ where $i \!\neq\! j$, we define the ``receiver intensity" as a linear combination of statistics relevant to the receiver selection process:
 	\begin{equation}
@@
 	\end{equation}
-	where $\boldsymbol{b}$ is a $P$--dimensional vector of coefficients and $\boldsymbol{x}_{iej}$ is a set of receiver selection features.
-$\lambda_{iej}$ is the logit of the probability that hyperedge event $e$ is directed from sender $i$ to receiver $j$, conditional upon there being at least one other receiver to which sender $i$ directs event $e$.
-In the case that there are no other receivers to which sender $i$ directs event $e$, the logit of the probability that sender $i$ directs event $e$ to receiver $j$ is $\infty$.
-The features in equation (2.1) can capture common network processes that include, but are not limited to, popularity, reciprocity, and transitivity, as well as the effects of attribute features defined on the sender, receivers, and/or sender-receiver pairs (e.g., the gender of the sender and/or receiver, an indicator of whether the sender is a supervisor of the receiver's).
-In addition, we include an intercept term to account for the average (or baseline) number of receivers.
-We place a Normal prior $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$.
+	where $\boldsymbol{b}$ is a $P$-dimensional vector of coefficients and $\boldsymbol{x}_{iej}$ is a set of receiver selection features.
+As we show below, this intensity contributes to the probability that $i$ directs event $e$ towards receiver $j$.
+The features $\boldsymbol{x}_{iej}$ can capture common network processes like popularity, reciprocity, and transitivity, as well as the effects of attributes of the sender and receivers (e.g., their gender), or attributes of sender--receiver pairs (e.g., whether the sender is a supervisor of the receiver's).
+We also include a normally distributed intercept term to account for the average (or baseline) number of receivers: $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$.~\looseness=-1
 
-	As we describe in greater detail below, under the HEM the sender of each hyperedge event is selected to be the sender that would create the respective event with the greatest urgency.
-As such, under the HEM we assume that each sender would plan on directing each event toward some set of receivers at some time point.
-For each event $e$ and each sender $i$, our model draws a list of candidate receivers that would be receivers of event $e$ if $i$ were the sender.
-For an event $e$, we first define an $A\times A$ matrix $\boldsymbol{u}_e$ where the $i$th row denotes sender $i$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $i$ intends to direct event $e$.
+	The HEM assumes that the sender of each hyperedge event is the sender that would initiate their respective event with the greatest urgency (i.e., the earliest timestamp).
+Our model thus assumes that for every event $e$, every possible sender $i$ generates a candidate receiver set that would be the receiver set of event $e$ if sender $i$ were the sender.
+For an event $e$, we first define an $A\times A$ matrix $\boldsymbol{u}_e$ where the $i^{\textrm{th}}$ row denotes sender $i$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $i$ intends to direct event $e$.
 We then assume that each receiver vector $\boldsymbol{u}_{ie}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
@@
 The probability measure we define amounts to a non-empty Gibbs measure, in which the all-zero vector is excluded from the support of the multivariate Bernoulli distribution.
-As a result, this measure helps us to 1) allow a sender to select multiple receivers for a single event, 2) force the sender to select at least one receiver, and 3) ensure a tractable normalizing constant for the receiver selection distribution.
+As a result, this measure helps us to (1) allow a sender to select multiple receivers for a single event, (2) force the sender to select at least one receiver, and (3) ensure a tractable normalizing constant for the receiver selection distribution.
 To be specific, we draw a binary vector $\boldsymbol{u}_{ie}= (u_{ie1},
@@
 	\end{equation}
-	where $Z(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$ is the normalizing constant and $\lVert \cdot \rVert_1$ is the $l_1$--norm.
-Again, this is approximately equivalent to assuming that each $u_{iej}$ is drawn with the probability of 1 being logit($\lambda_{iej}$), excluding the case when $u_{iej}=0$ for all $j \in [A]$.
-This allows efficient inference since we can derive a closed-form normalizing constant which does not require brute-force summation over the support of $\boldsymbol{u}_{ie}$ (i.e., $\forall \boldsymbol{u}_{ie} \in [0,1]^A$).
+	where $Z(\boldsymbol{\lambda}_{ie})$ is the normalizing constant, $\lVert \cdot \rVert_1$ is the $\ell_1$-norm, and the log-indicator term $\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0 )\big)$ ensures that empty receiver sets are excluded from the distribution's support.
+These modeling assumptions facilitate efficient posterior inference since we can derive a closed form expression for the normalizing constant---i.e., $Z(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$---and thus do not need to perform brute-force summation over the support of $\boldsymbol{u}_{ie} \in [0,1]^A$.
 We provide detailed derivation steps for the normalizing constant $Z(\boldsymbol{\lambda}_{ie})$ in Appendix B.
 
+	% $Z(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$
+
 	\subsection{Candidate timestamps}\label{subsec:Time}
-	To generate timing for each event, the HEM first draws a candidate time at which the event would be created given the candidate sender and receiver combinations.
+	To generate timing for each event, the HEM first draws a candidate timestamp at which the event would be created given the candidate sender and receiver combinations.
 The timing rate for sender $i$ and event $e$ is
@@
 	\end{equation}
-	where $\boldsymbol{\eta}$ is a $Q$--dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features---covariates that could affect timestamps of events, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
+	where $\boldsymbol{\eta}$ is a $Q$-dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features---covariates that could affect timestamps of events, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
 
@@
 We define the time increment from event $e-1$ to event $e$ as $\tau_{e}$ (i.e., $\tau_{e}= t_e-t_{e-1}$) and specify the distribution of candidate timestamps with sender-specfic mean $\mu_{ie}$.
-Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume the mean and variance of the $\tau_{ie}$ satistify
+Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume the mean and variance of the $\tau_{ie}$ satistify~\looseness=-1
 	\begin{equation}
@@
 	\end{equation}
+		% \footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_e)$.} 
 	where $\tau_{ie}$ here is a positive real number.
-Possible choices of distribution include exponential, Weibull, gamma, and log-normal\footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_e)$.} distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
+Possible choices of distribution include exponential, Weibull, gamma, and log-normal distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
 Based on the specific distribution, we may need other latent variables to draw the time increment, to account for the variance of time increments, beyond the coefficients for the features used to model the rate.
 $V(\mu)$---e.g., the shape parameter $k$ for the Weibull, the shape parameter $\theta$ for the gamma, and the variance parameter $\sigma_\tau^2$ for the log-normal.
-We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
+We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.~\looseness=-1
 
 	\subsection{Senders, receivers, and timestamps}\label{subsec:Observed}
-	Finally, under the HEM the observed sender, receivers, and timestamp of hyperedge event $e$ is generated by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
+	Finally, our model assumes that the observed sender, receivers, and timestamp of hyperedge event $e$ are generated by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
 	\begin{equation}
@@
 	\end{figure}	
-		Therefore, it is a sender-driven process in that the receivers and timestamps of an event are jointly determined by the sender's urgency to direct the event to the selected receivers.
-Note that our generative process accounts for tied events such that in case of tied events (i.e., multiple senders draw exactly same candidate timestamps), we observe all of the tied events without assigning the orders of tied events.
-Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers, and Figure \ref{figure:diagram} presents an illustrative example on how the $e$th event is generated, assuming $t_{e-1} = 0$ and $A=5$ for simplicity.
+		Therefore, the HEM assumes a sender-driven process---i.e., the receivers and timestamp of an event are jointly determined by the sender's urgency to direct the event to those selected receivers.
+Note that our generative process allows for tied events.
+In the case of tied events---i.e., multiple senders draw exactly the same candidate timestamps---we assume that all events are generated and occur simultaneously.
+Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers, and Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $A=5$.~\looseness=-1
 	\begin{algorithm}[!t]
@@
 We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each latent variable from its conditional posterior via a Metropolis-within-Gibbs sampling algorithm.
-In this section, we provide each latent variable's conditional posterior, and demonstrate how we perform the prior-posterior simulator test of \cite{geweke2004getting}, in which we evaluate the integrity of both our mathematical derivations and the sampling code, for the HEM.
-At the end of this section, we provide the pseudocode of our MCMC algorithm in Algorithm \ref{alg:MCMC}.
+In the next subsection, we provide each latent variable's conditional posterior along with pseudocode of MCMC in Algorithm \ref{alg:MCMC}.
+We also evaluate the correctness of both our mathematical derivations and software implemenation using the prior--posterior simulator test of \cite{geweke2004getting}.
 
@@
 %from $P(\boldsymbol{b}, \boldsymbol{u}|\,\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}|\, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$.
-	We use this common tool in Bayesian statistics called ``data augmentation" \citep{tanner1987calculation,neal2015exact}.
-Since $u_{iej}$ is a binary random variable, its new value may be sampled directly from a Bernoulli distribution with probability $p_{iej} =\frac{\exp(\lambda_{iej})}{\exp(\lambda_{iej})+\text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 )}$, since
+	This approach---i.e., ``data augmentation"---is commonly used throughout Bayesian statistics \citep{tanner1987calculation,neal2015exact}.
+Since $u_{iej}$ is a binary random variable, it may be sampled from a Bernoulli distribution with probability $p_{iej} =\frac{\exp(\lambda_{iej})}{\exp(\lambda_{iej})+\text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 )}$, since
 	\begin{equation}
 		\begin{aligned}
-			&\Pr(u_{iej}=1| \,\boldsymbol{u}_{ie\backslash j}, \boldsymbol{b}, \boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})
-			\propto \mbox{exp}(\lambda_{iej});\\
+			&\Pr(u_{iej}=1| \,\boldsymbol{u}_{ie\backslash j}, \boldsymbol{b}, \boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t}) \propto \exp(\lambda_{iej}) \\
 			&\Pr(u_{iej}=0|\, \boldsymbol{u}_{ie\backslash j},\boldsymbol{b}, \boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 ),
@@
 	\end{equation}
-	where the subscript ``$\backslash j$'' denotes a quantity excluding data from position $j$ and $I(\cdot)$ is the indicator function that is used to prevent from the instances where a sender selects zero number of receivers.
+	where the subscript ``$\backslash j$'' denotes a quantity excluding data from position $j$ and $\text{I}(\cdots)$ is the indicator function that prevents empty receiver sets. 
 	\subsubsection{Coefficients for receiver selection features}
-	Unlike the candidate receivers above, new values for $\boldsymbol{b}$ cannot be sampled directly from its conditional posterior, but may instead be obtained using the Metropolis--Hastings (M--H) algorithm.
-Assuming an uninformative prior (i.e., $N({0},\infty)$), the conditional posterior over $\boldsymbol{b}$ is
+	Unlike the candidate receivers above, the conditional posterior for $\boldsymbol{b}$ does not have a closed form; however $\boldsymbol{b}$ may instead be re-sampled using the Metropolis--Hastings (MH) algorithm.
+Assuming an uninformative prior (i.e., $N({0},\infty)$), the conditional posterior for $\boldsymbol{b}$ is proportional to~\looseness=-1
 	\begin{equation}
@@
 			\FOR{$n=1$ to $I_1$}
-			\STATE update $\boldsymbol{b}$ using M--H algorithm---equation (\ref{eqn:latentedge})
+			\STATE update $\boldsymbol{b}$ using MH algorithm---equation (\ref{eqn:latentedge})
 			\ENDFOR
 			\FOR{$n=1$ to $I_2$}
-			\STATE update $\boldsymbol{\eta}$ using M--H algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
+			\STATE update $\boldsymbol{\eta}$ using MH algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
 			\ENDFOR
 			\IF {extra parameter for $V(\mu)$} 
-			\STATE update the variance parameter using M--H algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
+			\STATE update the variance parameter using MH algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
 			\ENDIF
@@
 	\subsubsection{Coefficients for event timing features}
-	Likewise, we use the M--H algorithm to update the latent variable $\boldsymbol{\eta}$.
-Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for an untied event case is
+	Likewise, we use the MH algorithm to update the latent variable $\boldsymbol{\eta}$.
+Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for an untied event case is proportional to~\looseness=-1
 	\begin{equation}
@@
 	\end{equation}
-	where $f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))$ is the probability that the $e$th observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{s_e e}$, and $\prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie},V(\mu)) \big)$ is the probability that the rest of (unobserved) senders for event $e$ all draw time increments greater than $\tau_e$.
-Moreover, under the existence of tied events, the conditional posterior of $\boldsymbol{\eta}$ is written as
+	where $f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))$ is the probability that the $e^{\textrm{th}}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{s_e e}$, and $\prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie},V(\mu)) \big)$ is the probability that the rest of (unobserved) senders for event $e$ all draw time increments greater than $\tau_e$.
+Moreover, under the existence of tied events, the conditional posterior of $\boldsymbol{\eta}$ is written as proportional to
 	\begin{equation}
@@
 If $M=E$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
-Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional M--H update---e.g., $\Pr(k|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \,\boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for log-normal distribution.
+Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional MH update---e.g., $\Pr(k|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \,\boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for log-normal.~\looseness=-1
 	\subsection{Getting it Right (GiR) test} \label{subec:GiR}
@@
 	Our data come from the North Carolina county government email dataset collected by \cite{ben2017transparency} that includes internal email corpora covering the inboxes and outboxes of managerial-level employees of North Carolina county governments.
-Out of over twenty counties, we chose Montgomery County to 1) test our model using data with a large proportion of hyperedges (16.76\%), all of which are emails sent from one sender to two or more receivers, and 2) limit the scope of this initial application.
+Out of over twenty counties, we chose Montgomery County to (1) test our model using data with a large proportion of hyperedges (16.76\%), all of which are emails sent from one sender to two or more receivers, and (2) limit the scope of this initial application.
 The Montgomery County email network contains 680 emails, sent and received by 18 department managers over a period of 3 months (March--May) in 2012.
@@
 We speculate that this difference can be explained by overdispersion in exponential distribution, because there exists greater variability in the time increments of emails than would be expected under exponential distribution.
-As illustrated above, we can use this out-of-sample prediction task for two uses---1) to provide an effective answer to the question ``how does the HEM perform at filling in the missing components of time-stamped network data?" and 2) to offer one standard way to determine the distribution of time increments in Section \ref{subsec:Time}.
+As illustrated above, we can use this out-of-sample prediction task for two uses---(1) to provide an effective answer to the question ``how does the HEM perform at filling in the missing components of time-stamped network data?" and (2) to offer one standard way to determine the distribution of time increments in Section \ref{subsec:Time}.
 
@@
 	\end{equation*}
-	The posterior estimates of two temporal effects---``weekend$(e)$" and ``PM$(e)$"---indicate that if the ${(e-1)}$th email was sent during the weekend or after midday, then the time to $e$th email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+	The posterior estimates of two temporal effects---``weekend$(e)$" and ``PM$(e)$"---indicate that if the ${(e-1)}$th email was sent during the weekend or after midday, then the time to $e^{\textrm{th}}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
 On the contrary, the covariates ``manager$(i)$", ``outdegree$(i)$", and ``indegree$(i)$"  shorten the amount of time to next email.

### 2018-06-26 paper/ba-HEM/ba-sample.tex
edits to the remaining sections

@@
 	where $I(\cdot)$ is an indicator function.
-The network statistics (5--14) are designed so that their coefficients have a straightforward interpretations.
+The network statistics (5--14) are designed so that their coefficients have a straightforward interpretation.
 The function ``outdegree$(i)$" and ``indegree$(j)$" measure the gregariousness and popularity effects of the node by counting the number of emails sent from $i$ and received by $j$, respectively, within the last 7 days.
@@
 	\subsubsection{Event timing features}
-For the event timing features $\boldsymbol{y}$, introduced in Section \ref{subsec:Time}, we identify a set of covariates which may affect ``time to the next event." Similar to the receiver selection features, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
-In addition, we select some event-specific covariates based on the temporal aspect of the $(e-1)$th event---e.g., whether the previous email was sent (1) during the weekend and (2) before or past midday (AM/PM)---since we expect the email interactions within county government to be less active during the weekend and in the evening.
+For the event timing features $\boldsymbol{y}$, introduced in Section \ref{subsec:Time}, we identify a set of covariates which may affect the time until the next event.
+Similar to the receiver selection features, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
+In addition, we select some event-specific covariates based on the temporal aspect of the $(e-1)^{\textrm{th}}$ event---e.g., whether the previous email was sent (1) during the weekend and (2) before or past midday (AM/PM)---since we expect the email interactions within county government to be less active during the weekend and in the evening.
 To be specific, the timestamp statistics are defined as
@@
 
-	The HEM defines a flexible family of models, each of which is indexed/defined by a set of features (i.e., the receiver selection features $\boldsymbol{x}$, the selection of event timing features $\boldsymbol{y}$, and the distribution of time increments $f$).
+	The HEM defines a flexible family of models, each of which is defined by a set of features (i.e., the receiver selection features $\boldsymbol{x}$, the selection of event timing features $\boldsymbol{y}$, and the distribution of time increments $f$).
 Many of these components will be specified based on user expertise (e.g., regarding which features would drive receiver selection), but some decisions may require a data-driven approach to model specification.
@@
 Here, we specifically compare the predictive performance from two distributions---log-normal and exponential.
-We particularly choose the log-normal distribution based on some exploratory analysis (e.g., histogram and simple regressions) on raw time increments data, and take exponential distribution as an alternative since exponential is the most commonly specified distribution for time-to-event data, and is also used in the stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
+We particularly choose the log-normal distribution based on some exploratory analysis (e.g., histogram and simple regressions) on raw time increments data, and select the exponential distribution as a baseline alternative that is a commonly specified distribution for time-to-event data, and is also used in the stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
 	\begin{algorithm}[!t]
@@
 
-	We evaluated the model’s ability to predict out-of-sample events and timestamps on Montgomery County email data.
-We generated a train—test split of the data by randomly selecting 10\% of senders, receivers, and timestamp variables to be held out.
+	We evaluated the models' ability to predict out-of-sample events and timestamps on Montgomery County email data.
+We generated a train--test split of the data by randomly selecting 10\% of senders, receivers, and timestamp variables to be held out.
 Our model then imputed these missing variables during inference, sampling them from their conditional posterior along with the other latent variables.
@@
 First, we compare the posterior probability of correct senders for each of the missing emails $\{e:s_e=\mbox{NA}\}$, which corresponds to $\pi_{es_e}$ in Algorithm \ref{alg:PPE}.
-We call this measure the ``correct sender posterior probability." On Figure \ref{figure:PPEresults} (a), we draw boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{es_{e}} = \frac{1}{N}\sum_{n=1}^N \pi^n_{es_{e}}$---across the missing emails.
-The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with log-normal distribution showing better performance than exponential distribution.
+We call this measure the ``correct sender posterior probability." In Figure \ref{subfigure:PPEresults1}, we display boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{es_{e}} = \frac{1}{N}\sum_{n=1}^N \pi^{(n)}_{es_{e}}$---across the missing emails.
+The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with the log-normal model showing better performance than the exponential model.
 Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $e$ and $j$ with $r_{ej}$=NA) by taking the harmonic mean of precision and recall:
@@
 with TP denoting true positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{ej}=\boldsymbol{r}^{\textrm{(pred)}}_{ej}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{ej}=1$ but $\boldsymbol{r}^{\textrm{(pred)}}_{ej}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{ej}=0$ but $\boldsymbol{r}^{\textrm{(pred)}}_{ej}=1$).
-Although the generative process for events (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{figure:PPEresults} (b) reveals slight difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal on average outperforms exponential.
-Finally, the prediction error for $d$th missing timestamp is estimated using the median of absolute relative errors, often referred to as  median absolute percentage error (MdAPE), across $N=500$ predictions:
+Although the generative process for events (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{subfigure:PPEresults2} reveals slight difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal on average outperforms exponential.
+Finally, we define the prediction error for the $d^{\textrm{th}}$ missing timestamp bot be the median of the absolute relative errors, often referred to as median absolute percentage error (MdAPE), across $N=500$ predictions:
 	\begin{figure}[!t]
@@
 				\includegraphics[width=\textwidth]{img/senderpredict-1.png}	
+				\label{subfigure:PPEresults1}
 			\end{subfigure}
@@
 				\includegraphics[width=\textwidth]{img/receiverpredict-1.png}	
+				\label{subfigure:PPEresults2}
 			\end{subfigure}
@@
 				\includegraphics[width=\textwidth]{img/timepredict-1.png}
+				\label{subfigure:PPEresults3}	
 			\end{subfigure}
@@
 	\end{equation}
-	Figure \ref{figure:PPEresults} (c) presents boxplots for the median absolute percentage errors.
-where plot the estimates in a log-scale.
-Surprisingly, we have a huge benefit in the performance of timestamp prediction when we assume log-normal distribution for time increments compared to exponential distribution.
-We speculate that this difference can be explained by overdispersion in exponential distribution, because there exists greater variability in the time increments of emails than would be expected under exponential distribution.
+	Figure \ref{subfigure:PPEresults3} presents boxplots for the median absolute percentage errors on a log scale.
+These plots show that the log-normal distribution fits the time increments significantly better than the exponential distribution.
+We speculate that this difference can be simply explained by a lack of flexibility in the one-parameter exponential distribution.
 As illustrated above, we can use this out-of-sample prediction task for two uses---(1) to provide an effective answer to the question ``how does the HEM perform at filling in the missing components of time-stamped network data?" and (2) to offer one standard way to determine the distribution of time increments in Section \ref{subsec:Time}.
@@
 	In this section, we perform posterior predictive checks (PPC) \citep{rubin1984bayesianly} to evaluate the appropriateness of our model specification for Montgomery County email data.
-We formally generated entirely new data by simulating $N=500$ synthetic email datasets $\{(s_{e}, \boldsymbol{r}_{e}, t_{e})\}_{e=1}^E$ from the generative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from the inference in Section \ref{subsec:Result_email}\iffalse, where the pseudocode is outlined in Algorithm \ref{alg:PPC}\fi.
+We formally generated entirely new data by simulating $N=500$ synthetic email datasets $\{(s_{e}, \boldsymbol{r}_{e}, t_{e})\}_{e=1}^E$ from the generative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from inference in Section \ref{subsec:Result_email}\iffalse, where the pseudocode is outlined in Algorithm \ref{alg:PPC}\fi.
 For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution---the number of emails sent by each node, indegree distribution---the number of emails received by each node, receiver size distribution---the number of receivers on each emails, and a probability--probability (P--P) plot for time increments.
@@
 
-	Figure \ref{figure:PPCresults} illustrates the results of poterior predictive checks using the log-normal distribution, which shows better performance in Section \ref{subsec:Experiment_email}.
-The upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic samples, where the left one for outdegree statistic and the right plot is for indegree statistic.
-For both plots, the x-axis represents the nodes ($A=1,\ldots,18$), and the y-axis represents the number of emails sent or received by the node.
-When compared with the observed outdegree and indegree statistics (red lines), our model recovers the overall distribution of sending and receiving activities across the nodes.
-For example, node 1 and 10 show significantly higher level of both sending and receiving activities relative to the rest, and the model-simulated data captures those big jumps, showing acceptable fit to the data.
-Outdegree distribution of some low-activity nodes are not precisely recovered, however, indegree distribution looks much better.
+	Figure \ref{figure:PPCresults} illustrates the results of posterior predictive checks using the log-normal model, which fit the timestamps better than the exponential model (Section \ref{subsec:Experiment_email}).
+The upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic samples, where the left one is for the outdegree statistic and the right plot is for the indegree statistic.
+For both plots, the x-axis represents the nodes ($a=1,\ldots,18$), and the y-axis represents the number of emails sent or received by the node.
+When compared with the observed outdegree and indegree statistics (red lines), our model appears to fit the overall distribution of sending and receiving activities across the nodes.
+For example, node 1 and 10 have a significantly higher level of both sending and receiving activities relative to the rest and this is captured in the model-simulated data.
+The outdegree distribution of some low-activity nodes are not precisely recovered; however, the  indegree distribution looks much better.
 Since we use more information in the receiver selection process (i.e., network effects) while we rely solely on minimum time increments when choosing the observed sender, these results are expected.
@@
 The result shows that our model is underestimating emails with one receiver while overestimating emails with two, three, and four receivers.
-One explanation behind what we observe is that the model is trying to recover so-called ``broadcast'' emails, which are the emails with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right.
+One explanation behind what we observe is that the model is trying to recover broadcast emails, which are the emails with $\geq 10$ number of receivers, so that the intercept estimate $b_1$ is slightly moved toward right.
 It would be an interesting problem in future research to consider how the hyperedge size distribution can be further modified to capture this distribution more accurately.
@@
 	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we interpret the results from the HEM using the log-normal distribution, with emphasis on understanding the effects of receiver selection and event timing features defined in Section \ref{subsec:Covariates_email}.
-We assume weakly informative priors for latent variables such as $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b=\boldsymbol{0}, \Sigma_b = 2\times I_P)$, $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta=\boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, and $\sigma_\tau^2 \sim \mbox{inverse-Gamma}(a=2, b=1)$, and run MCMC algorithm in Algorithm \ref{alg:MCMC} with $O=55,000$ outer iterations with a burn-in of 15,000, where we thin by keeping every 40th sample.
+We assume weakly informative priors for latent variables such as $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b=\boldsymbol{0}, \Sigma_b = 2\times I_P)$, $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta=\boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, and $\sigma_\tau^2 \sim \mbox{inverse-Gamma}(a=2, b=1)$, and MCMC (Algorithm \ref{alg:MCMC}) with $O=55,000$ outer iterations and a burn-in of 15,000, where we thin by keeping every $40^{\textrm{th}}$ sample.
 While the inner iterations for $\sigma_\tau^2$ is fixed as 1, we specify the inner iterations $I_1=20$ for $\boldsymbol{b}$ and $I_2=10$ for $\boldsymbol{\eta}$ to adjust for slower convergence rates.
@@
 	\subsubsection{Coefficients for receiver selection features}
-	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$, where Figure \ref{figure:betaresults} (a) displays the coefficients for nodal covariates and \ref{figure:betaresults} (b) displays the coefficients for dyadic and triadic covariates.
+	Figure \ref{figure:betaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{b}$, where Figure \ref{subfigure:betaresults1} displays the coefficients for nodal covariates and \ref{subfigure:betaresults2} displays the coefficients for dyadic and triadic covariates.
 Since we use the logit functional form
@@
 First of all, we find the effects of nodal coavariates ``gender\_\,sender$(i)$" and ``gender\_\,receiver$(j)$" are both nearly always negative in the posterior samples.
-The log odds that any other node will be added as a receiver of an email is approximately 0.5 less if the sender is a woman.
+The log odds that any other node will be added as a receiver of an email is approximately two times less if the sender is a woman.
 The posterior distribution of the statistic ``outdegree$(i)$" is mostly negative, if sender $i$ sent $n$ number of emails to anyone last week, then sender $i$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $j$.
@@
 The scenario in which a sender sends a lot of low-hyperedge-size emails may arise due to the use of email for a one-on-one conversation.
-The large positive estimates of the interaction between hyperedge size and outdegree indicate that those who have recently sent many emails with many receivers on each email are likely to continue sending these ``broadcast'' style emails.
+The large positive estimates of the interaction between hyperedge size and outdegree indicate that those who have recently sent many emails with many receivers on each email are likely to continue sending broadcast emails.
 This scenario may arise from someone being responsible for distributing timely announcements.
@@
 						\includegraphics[width=\textwidth]{img/betanewplot2-1.png}
+						\label{subfigure:betaresults1}	
 					\end{subfigure}
@@
 						\includegraphics[width=\textwidth]{img/betanewplot3-1.png}
+						\label{subfigure:betaresults2}	
 					\end{subfigure}
@@
 	For event timing features, Figure \ref{figure:etaresults} shows the boxplots summarizing posterior samples of $\boldsymbol{\eta}$.
-Note that interpretations of the estimated coefficients for $\hat{\boldsymbol{\eta}}$ should be based on the specified timeunit of the datset, which we use ``hour" for Montgomery county email data.
-Moreover, since we assume log-normal distribution for time increments, the coefficients are interpreted in terms of the change in the average log time.
+Note that interpretations of the estimated coefficients for $\hat{\boldsymbol{\eta}}$ should be based on the specified time unit of the datset; we specify time units to be hours for the Montgomery county email data.
+Moreover, since we assume the log-normal distribution for time increments, the coefficients are interpreted in terms of the change in the average log time.
 	\begin{equation*}
@@
 	\end{equation*}
-	The posterior estimates of two temporal effects---``weekend$(e)$" and ``PM$(e)$"---indicate that if the ${(e-1)}$th email was sent during the weekend or after midday, then the time to $e^{\textrm{th}}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
-On the contrary, the covariates ``manager$(i)$", ``outdegree$(i)$", and ``indegree$(i)$"  shorten the amount of time to next email.
-For example, being a county manager (i.e., the lead county administrator) lowers the expected value of $\log(\tau_{ie})$ by $\hat{\eta}_3 = -1.070$, since the manager in general sends or receives a lot more emails which may shorten the response time and many of those emails.
-The posterior estimates for the  ``outdegree$(i)$" and ``indegree$(i)$" statistics, where the posterior means are approximately $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
+	The posterior estimates of two temporal effects---``weekend$(e)$" and ``PM$(e)$"---indicate that if the $(e-1)^{\textrm{th}}$ email was sent during the weekend or after midday, then the time to the $e^{\textrm{th}}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+On the contrary, the covariates ``manager$(i)$", ``outdegree$(i)$", and ``indegree$(i)$"  shorten the amount of time until the next email.
+For example, being a county manager (i.e., the lead county administrator) lowers the expected value of $\log(\tau_{ie})$ by $\hat{\eta}_3 = -1.070$.
+The posterior mean estimates for the  ``outdegree$(i)$" and ``indegree$(i)$" statistics are $\hat{\eta}_4=-0.206$ and $\hat{\eta}_5=-0.060$, respectively.
 These effects indicate that those who are involved in either sending or receiving a lot of emails recently are likely to send emails with greater speed.
-The posterior distribution for the effect of the gender of the manager is pretty evenly spread around zero.
-In addition, the posterior mean estimates for variance parameter $\sigma^2_\tau$ in the lognormal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists large variability in the time increments of emails.
+The posterior distribution for the effect of the gender of the manager is evenly spread around zero.
+In addition, the posterior mean estimates for the variance parameter $\sigma^2_\tau$ in the log-normal distribution is approximately $\hat{\sigma}^2_\tau=14.093$ with its 95\% credible interval $(12.709, 15.555)$, indicating that there exists large variability in the time increments of emails.
 			\begin{figure}[!t]
@@
 	Motivated by a growing class of dynamic network models which deal with events recorded in continuous time, the hyperedge event model (HEM) can effectively learn the underlying dynamics in events and their corresponding timestamp formations, providing novel insights to the literature.
-The HEM explicitly models hyperedges through a receiver selection distribution that forces the sender to select at least one recevier, which is a more realistic approach for events with one sender and one or more receivers and one or more sender and one receiver compared to treating them as pure duplicates.
+The HEM explicitly models hyperedges through a receiver selection distribution that forces the sender to select at least one receiver; this obviates the need to preprocess hyperedge data---e.g., by ``duplicating'' hyperedges---to match the assumptions of traditional network models.
+Our model treating them as pure duplicates.
 In modeling the timestamps (more precisely time increments) of events, our generalized linear model (GLM) based formulation offers new innovations by eliminating the need to stick with one parameter distribution (e.g., exponential distribution).
@@
 	We have demonstrated the effectiveness of our model by analyzing the Montgomery County government emails, where emails serve as a canonical example of directed hyperedge events with one sender and one or more receivers.
-The estimated effects for receiver selection features reveal that our model is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM), but we also learn about the effects of event timing features by integrating a survival model for event timing.
+The estimated effects for receiver selection features reveal that our model is able to understand the structural dynamics similar to those used in the exponential random graph model (ERGM).
+Our model also learns the effects of event timing features by integrating a survival model for event timing.
 Although we illustrate the entire framework and application in the context of one type of hyperedge, one sender and one or more receivers, our model can be easily extended to allow the opposite case, one or more sender and one receiver, by slight modification of the generative process (shown in Appendix A).

### 2018-06-27 paper/ba-HEM/ba-sample.tex
rearranged figures

@@
 	\end{equation}
-	\begin{figure}[!t]
-		\centering
-		\includegraphics[width=0.625\textwidth]{img/diagramnew.png}	
-		\caption {An illustrative example of the generative process of the HEM.}
-		\label{figure:diagram}
-	\end{figure}	
-		Therefore, the HEM assumes a sender-driven process---i.e., the receivers and timestamp of an event are jointly determined by the sender's urgency to direct the event to those selected receivers.
-Note that our generative process allows for tied events.
-In the case of tied events---i.e., multiple senders draw exactly the same candidate timestamps---we assume that all events are generated and occur simultaneously.
-Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers, and Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $A=5$.~\looseness=-1
 	\begin{algorithm}[!t]
@@
 	\end{algorithm}
+		Therefore, the HEM assumes a sender-driven process---i.e., the receivers and timestamp of an event are jointly determined by the sender's urgency to direct the event to those selected receivers.
+Note that our generative process allows for tied events.
+In the case of tied events---i.e., multiple senders draw exactly the same candidate timestamps---we assume that all events are generated and occur simultaneously.
+Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers, and Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $A=5$.~\looseness=-1
+		\begin{figure}[!t]
+			\centering
+			\includegraphics[width=0.625\textwidth]{img/diagramnew.png}	
+			\caption {An illustrative example of the generative process of the HEM.}
+			\label{figure:diagram}
+		\end{figure}
 
@@
 	\end{equation}
+	\subsubsection{Coefficients for event timing features}
+	Likewise, we use the MH algorithm to update the latent variable $\boldsymbol{\eta}$.
+Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for an untied event case is proportional to~\looseness=-1
+	\begin{equation}
+		\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{e=1}^E\Big(f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, V(\mu)) \big)\Big),
+		\label{eqn:latenttime}
+	\end{equation}
+	where $f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))$ is the probability that the $e^{\textrm{th}}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{s_e e}$, and $\prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie},V(\mu)) \big)$ is the probability that the rest of (unobserved) senders for event $e$ all draw time increments greater than $\tau_e$.
+Moreover, under the existence of tied events, the conditional posterior of $\boldsymbol{\eta}$ is written as proportional to
+	\begin{equation}
+		\begin{aligned}
+			\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{e:t_e=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{s_e e}, V(\mu)) \\&\times \prod_{i \notin \{s_e\}_{e:t_e=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{ie}, V(\mu)) \big)\Big),
+		\end{aligned}
+		\label{eqn:latenttime2}
+	\end{equation}
+	where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $E$ events ($M \leq E$).
+If $M=E$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
+Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional MH update---e.g., $\Pr(k|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \,\boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for log-normal.~\looseness=-1
 		\begin{algorithm}[!t]
@@
 		\end{algorithm}
-	\subsubsection{Coefficients for event timing features}
-	Likewise, we use the MH algorithm to update the latent variable $\boldsymbol{\eta}$.
-Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for an untied event case is proportional to~\looseness=-1
-	\begin{equation}
-		\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{e=1}^E\Big(f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, V(\mu)) \big)\Big),
-		\label{eqn:latenttime}
-	\end{equation}
-	where $f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))$ is the probability that the $e^{\textrm{th}}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{s_e e}$, and $\prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie},V(\mu)) \big)$ is the probability that the rest of (unobserved) senders for event $e$ all draw time increments greater than $\tau_e$.
-Moreover, under the existence of tied events, the conditional posterior of $\boldsymbol{\eta}$ is written as proportional to
-	\begin{equation}
-		\begin{aligned}
-			\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{e:t_e=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{s_e e}, V(\mu)) \\&\times \prod_{i \notin \{s_e\}_{e:t_e=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{ie}, V(\mu)) \big)\Big),
-		\end{aligned}
-		\label{eqn:latenttime2}
-	\end{equation}
-	where $t_1^*,\ldots,t_M^*$ are the unique timepoints across $E$ events ($M \leq E$).
-If $M=E$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
-Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional MH update---e.g., $\Pr(k|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \,\boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for log-normal.~\looseness=-1
+
 	\subsection{Getting it Right (GiR) test} \label{subec:GiR}
@@
 In the backward samples, unobservable variables are generated using the sampling equations for inference, which we derived in Section \ref{subsec:conditionaldist}.
-For each forward and backward sample that consists of $E$ number of events, we save these statistics:
+For each forward and backward sample that consists of $E$ number of events, we save these statistics:\\
 	\begin{itemize}
@@
 If the receiver $j$ received $n$ number of emails over the last week, sender $i$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $j$.
-
-	When we look at the effects of dyadic and triadic covariates, one thing that stands out is the large and positive posterior distribution of the statistic ``send$(i,j)$" (i.e., number of times $i$ sent emails to $j$ over the last week) with the posterior mean $\hat{b}_9 = 0.274$, implying that if $i$ sent $n$ number of emails to $j$ last week, then sender $i$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $j$.
-The posterior distributions for the reciprocity effect (i.e., ``receive$(i, j)$''), and the four triadic effects, are all fairly evenly spread around zero, so our results do not justify conclusions regarding the nature of these effects in the Montgomery county email network.
 			\begin{figure}[!t]
@@
 			\end{figure}
+
+	When we look at the effects of dyadic and triadic covariates, one thing that stands out is the large and positive posterior distribution of the statistic ``send$(i,j)$" (i.e., number of times $i$ sent emails to $j$ over the last week) with the posterior mean $\hat{b}_9 = 0.274$, implying that if $i$ sent $n$ number of emails to $j$ last week, then sender $i$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $j$.
+The posterior distributions for the reciprocity effect (i.e., ``receive$(i, j)$''), and the four triadic effects, are all fairly evenly spread around zero, so our results do not justify conclusions regarding the nature of these effects in the Montgomery county email network.
 	\subsubsection{Coefficients for event timing features}
@@
 		\fi
-
+		\newpage
 		\bibliographystyle{ba}

### 2018-07-18 paper/ba-HEM/HEM_arxiv.tex
arxiv version added

--- 2018-06-27 paper/ba-HEM/ba-sample.tex
@@
 \csdef{input@path}{%
-	{sty/}% cls, sty files
+	{sty2/}% cls, sty files
 	{img/}% eps files
@@
 %
-\pubyear{0000}
-\volume{00}
-\issue{0}
-\doi{0000}
+%\pubyear{0000}
+%\volume{00}
+%\issue{0}
+%\doi{0000}
 \firstpage{1}
@@
 	\subsubsection{Candidate receivers}
-	In our model, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\,\boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\,\boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
+	In our model, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $\Pr(\boldsymbol{b}|\,\boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ and $\Pr(\boldsymbol{\eta}|\,\boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
 However, it is possible to augment the data by candidate receivers $\boldsymbol{u}$ such that we can obtain their conditional posterior by conditioning on samples of $\boldsymbol{u}$.
@@
 	\end{equation}
-	where the subscript ``$\backslash j$'' denotes a quantity excluding data from position $j$ and $\text{I}(\cdots)$ is the indicator function that prevents empty receiver sets. 
+	where the subscript ``$\backslash j$'' denotes a quantity excluding data from position $j$ and $\text{I}(\cdot)$ is the indicator function that prevents empty receiver sets. 
 	\subsubsection{Coefficients for receiver selection features}
@@
 
+		\newpage
+		\bibliographystyle{ba}
+			\bibliography{baHEM}	
 	\section*{Appendix}
@@
 		\fi
-		\newpage
-		\bibliographystyle{ba}
-		\bibliography{baHEM}
 

### 2018-07-20 presentation/JSM_Bomin.tex
presentation folder added

\documentclass{beamer}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{ragged2e}
\usepackage{adjustbox}
\title{The Hyperedge Event Model}
\author{Bomin Kim\\ \vspace{0.25cm} Department of Statistics\\Pennsylvania State University}
\date{July 29, 2018\\\vspace{0.5cm} Joint Statistical Meetings 2018}
\begin{document}
\maketitle
\begin{frame}
		\frametitle{Collaborators}
		\hspace{0.5cm}
		\begin{figure}
								{\includegraphics[width=.3\textwidth]{aaron.jpg}}
			{\includegraphics[width=.2245\textwidth]{Bruce.jpeg}}
				{\includegraphics[width=.3\textwidth]{Hanna.jpeg}}
		\end{figure}
\begin{itemize}
	\item \textcolor{blue}{Aaron Schein}\\\footnotesize{College of Information and Computer Sciences, UMass Amherst}
	\normalsize
	\item \textcolor{blue}{Bruce Desmarais}\\\footnotesize{Department of Political Science, Pennylvania State University}
\item		\normalsize\textcolor{blue}{Hanna Wallach}\\ \footnotesize{Microsoft Research NYC}	\normalsize
		\end{itemize}
\end{frame}
\begin{frame}
		\frametitle{Motivations: \textcolor{red}{H}yperedge \textcolor{red}{E}vent \textcolor{red}{M}odel}
		\begin{itemize}
			\item \textcolor{red}{H}\textcolor{blue}{yperedge}\\
			edges including one sender and multiple receivers or one receiver and multiple
senders.
			\item \textcolor{red}{E}\textcolor{blue}{vent}\\
			timestamped events
			\item  \textcolor{red}{M}\textcolor{blue}{odel}\\
			statistical framework to jointly \\
		\end{itemize}
		\centering\Large
		``who interacts with whom, and when?"
\end{frame}

\begin{frame}
	\frametitle{Generative Process: ``\textcolor{red}{Who} Interacts with \textcolor{red}{Whom}"}
For each edge or event $e = 1,\ldots, E,$ 	\normalsize\vspace{0.15cm}
	\begin{itemize}
		\item \textcolor{blue}{Receiver intensity} for every sender-receiver pair $(i, j)_{i\neq j}$
		\begin{equation*}
		\lambda_{iej} = \boldsymbol{b}^T \boldsymbol{x}_{iej},
		\end{equation*}
		where $\boldsymbol{x}_{iej}$ is a set of receiver selection features or covariates. \vspace{0.15cm}
		\item Every sender selects \textcolor{red}{candidate receivers} from non-empty \textcolor{blue}{multivariate Bernoulli distribution} $\boldsymbol{u}_{ie} \sim \mbox{MB}_G ({\lambda}_{ie1},\ldots, {\lambda}_{ieA})$
				\begin{equation*}
			P(\boldsymbol{u}_{ie}|\boldsymbol{b}, \boldsymbol{x}_{iej}) \propto \exp\Big(\log(I(||\boldsymbol{u}_{ie}||_1 > 0))+\sum_{j\neq i} \lambda_{iej}u_{iej}\Big)
				\end{equation*}
	\end{itemize}

\end{frame}
\begin{frame}
	\frametitle{Generative Process: ``and \textcolor{red}{When}"}
		\begin{itemize}
			\item \textcolor{blue}{Timing rate} for each sender
			\begin{equation*}
			\mu_{ie} = g^{-1}(\boldsymbol{\eta}^T \boldsymbol{y}_{ie})
			\end{equation*}
			\item \textcolor{blue}{Generalized linear model} (GLM) such that time increment $\tau_{ie}$ satisfy
			\begin{equation*}
			E(\tau_{ie}) = 	\mu_{ie} \mbox{ and } V(\tau_{ie}) = V(	\mu_{ie})
			\end{equation*}
			\item Select the sender-receiver-set with \textcolor{blue}{the smallest time increment}
						\begin{equation*}
						\begin{aligned}
						s_e &= \mbox{argmin}_{i}(\tau_{ie}),\\
						\boldsymbol{r}_e &= \boldsymbol{u}_{s_e e},\\
						t_e &=t_{e-1} + \tau_{s_e e}.
						\end{aligned}
						\end{equation*}
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Generative Process: \textcolor{red}{Sender}, \textcolor{red}{Receivers}, and \textcolor{red}{Timestamps}}
					\begin{figure}[H]
						\centering
						\includegraphics[width=1\textwidth]{diagramnew.png}	
						\label{figure:diagram}
					\end{figure}						
			\end{frame}

				\begin{frame}
			\frametitle{Application: Montgomery County Government
\textcolor{red}{Email} Data}
\begin{itemize}
				\item Coefficients for receiver selection features
			\item Coefficients for event timing features
			\end{itemize}
		\end{frame}				
		\begin{frame}
			\frametitle{Results: Exploratory Analysis}
			\begin{itemize}
				\item Coefficients for receiver selection features
				\item Coefficients for event timing features
			\end{itemize}

		\end{frame}				
				\begin{frame}
					\frametitle{Comparison: Lognormal vs. Exponential}
					\begin{itemize}
						\item Covariates
					\end{itemize}
				\end{frame}	
							\begin{frame}
								\frametitle{Conclusions}
								\begin{itemize}
									\item Covariates
								\end{itemize}
							\end{frame}

\end{document}

### 2018-07-27 presentation/JSM_Bomin.tex
slides added

@@
 \title{The Hyperedge Event Model}
-\author{Bomin Kim\\ \vspace{0.25cm} Department of Statistics\\Pennsylvania State University}
+\author{\textbf{Bomin Kim}\\ \vspace{0.25cm} Department of Statistics\\Pensylvania State University}
 \date{July 29, 2018\\\vspace{0.5cm} Joint Statistical Meetings 2018}
@@
 		\frametitle{Motivations: \textcolor{red}{H}yperedge \textcolor{red}{E}vent \textcolor{red}{M}odel}
-		\begin{itemize}
-			\item \textcolor{red}{H}\textcolor{blue}{yperedge}\\
-			edges including one sender and multiple receivers or one receiver and multiple
-senders.
-			\item \textcolor{red}{E}\textcolor{blue}{vent}\\
-			timestamped events
-			\item  \textcolor{red}{M}\textcolor{blue}{odel}\\
-			statistical framework to jointly \\
+		\normalsize	\begin{itemize}
+			\item \textcolor{red}{H}\textcolor{blue}{yperedge}: directed edges from one sender to multiple receivers or from multiple senders to one receiver\vspace{0.15cm}
+			\item \textcolor{red}{E}\textcolor{blue}{vent}:
+			timestamped events in the continous-time scale\vspace{0.15cm}
+			\item  \textcolor{red}{M}\textcolor{blue}{odel}: statistical framework to jointly understand\\\vspace{0.15cm}
 		\end{itemize}
@@
 	\frametitle{Generative Process: ``\textcolor{red}{Who} Interacts with \textcolor{red}{Whom}"}
-For each edge or event $e = 1,\ldots, E,$ 	\normalsize\vspace{0.15cm}
+For event $e = 1,\ldots, E,$ between $i \in \{1,\ldots,A\}$ \& $j \in \{1,\ldots,A\}$,\normalsize\vspace{0.15cm}
 	\begin{itemize}
@@
 		\end{equation*}
-		where $\boldsymbol{x}_{iej}$ is a set of receiver selection features or covariates. \vspace{0.15cm}
-		\item Every sender selects \textcolor{red}{candidate receivers} from non-empty \textcolor{blue}{multivariate Bernoulli distribution} $\boldsymbol{u}_{ie} \sim \mbox{MB}_G ({\lambda}_{ie1},\ldots, {\lambda}_{ieA})$
+		where $\boldsymbol{x}_{iej}$ is a set of receiver selection features or covariates and $\boldsymbol{b}$ is the corresponding $P$-dimensional coefficient. \vspace{0.15cm}
+		\item Every sender $i$ selects \textcolor{red}{candidate receivers} from non-empty \textcolor{blue}{multivariate Bernoulli distribution}\footnote{\scriptsize Fellows and Handcock (2017); Dai et al.
+(2013)} $\boldsymbol{u}_{ie} \sim \mbox{MB}_G ({\lambda}_{ie1},\ldots, {\lambda}_{ieA})$
 				\begin{equation*}
@@
 		\begin{itemize}
-			\item \textcolor{blue}{Timing rate} for each sender
+			\item \textcolor{blue}{Timing rate} for each sender $i$
 			\begin{equation*}
-			\mu_{ie} = g^{-1}(\boldsymbol{\eta}^T \boldsymbol{y}_{ie})
+			\mu_{ie} = g^{-1}(\boldsymbol{\eta}^T \boldsymbol{y}_{ie}),
 			\end{equation*}
-			\item \textcolor{blue}{Generalized linear model} (GLM) such that time increment $\tau_{ie}$ satisfy
+				where $\boldsymbol{y}_{ie}$ is a set of timing features or covariates and $\boldsymbol{\eta}$ is the corresponding $Q$-dimensional coefficient. \vspace{0.15cm}
+			\item \textcolor{blue}{Generalized linear model} (GLM) for time increment $\tau_{ie}$ so that
 			\begin{equation*}
-			E(\tau_{ie}) = 	\mu_{ie} \mbox{ and } V(\tau_{ie}) = V(	\mu_{ie})
+			E(\tau_{ie}) = 	\mu_{ie} \mbox{ and } V(\tau_{ie}) = V(	\mu_{ie}),
 			\end{equation*}
-			\item Select the sender-receiver-set with \textcolor{blue}{the smallest time increment}
+			with a choice of distribution from exponential family.\vspace{0.15cm}
+			\item Select the sender-receiver-set with \textcolor{blue}{the smallest time increment}\footnote{\scriptsize Snijders (1996)}
 						\begin{equation*}
@@
 	\begin{frame}
-		\frametitle{Generative Process: \textcolor{red}{Sender}, \textcolor{red}{Receivers}, and \textcolor{red}{Timestamps}}
+		\frametitle{Generative Process: \textcolor{red}{Sender}, \textcolor{red}{Receivers}, and \textcolor{red}{Timestamps}\footnote{\scriptsize Assuming $t_{e-1}=0$ for simplicity.}}
 					\begin{figure}[H]
@@
 					\end{figure}
+				\normalsize
+					\begin{itemize}
+						\item \textcolor{blue}{Bayesian inference}: invert the generative process to obtain the posterior
+distribution over the latent variables---i.e., ($\boldsymbol{u},\boldsymbol{b},\boldsymbol{\eta})$.
+					\end{itemize}						
 			\end{frame}
@@
 			\frametitle{Application: Montgomery County Government
-\textcolor{red}{Email} Data}
+\textcolor{red}{Email} Data\footnote{\scriptsize ben Aaron et al. (2017)}}
 \begin{itemize}
-				\item Coefficients for receiver selection features
-			\item Coefficients for event timing features
+	\item Email corpora covering inboxes and outboxes of \textcolor{blue}{Montgomery county government managers} in North Carolina \vspace{0.15cm}
+	\item Contains \textcolor{blue}{$E=680$} emails, sent and received by \textcolor{blue}{$A=18$} department managers over 3 months (March--May) in 2012.\vspace{0.15cm}
+			\end{itemize}
+					\centering\Large``To what extent are \textcolor{blue}{nodal, dyadic or triadic network effects} relevant to predicting future emails?"
+
+		\end{frame}				
+		\begin{frame}
+			\frametitle{Results: Exploratory Analysis on \textcolor{red}{$\boldsymbol{b}$}}
+					\begin{equation*}
+	\mbox{logit}(\lambda_{iej})=\log\Big(\frac{\lambda_{iej}}{1-\lambda_{iej}}\Big) =b_{1}+b_{2} x_{iej2}\ldots+b_{14}x_{iej14},\normalsize
+					\end{equation*}
+						\begin{figure}[!t]
+						\centering
+								\includegraphics[width=0.45\textwidth]{betanewplot2-1.png}
+								\includegraphics[width=0.45\textwidth]{betanewplot3-1.png}
+					\end{figure}
+					\begin{itemize}
+						\item Log odds is two times less if the sender is a woman.\vspace{0.15cm}
+						\item If $i$ sent $n$ number of emails to $j$ last week, then $i$ is $e^{0.27n} \approx (1.32)^n$ times more likely to send an email to $j$.
+
+					\end{itemize}				
+		\end{frame}
+
+				\begin{frame}
+					\frametitle{Results: Exploratory Analysis on \textcolor{red}{$\boldsymbol{\eta}$}}
+					\begin{equation*}
+					\begin{aligned}
+					&\log(\tau_{ie}) \sim N(\mu_{ie}, \sigma_\tau^2), \mbox{ with }
+\mu_{ie} = \eta_{1}+\eta_{2} y_{ie2}\ldots+\eta_{7}y_{ie7}.
+					\end{aligned}
+					\normalsize
+					\end{equation*}
+			\begin{figure}[H]
+				\centering
+				\includegraphics[width=0.45\textwidth]{etaplotnew-1.png}	
+			\end{figure}	
+								\begin{itemize}
+						\item If an email was sent during weekend or PM, then time
+						to next email takes $e^{1.55} \approx 4.72$ and $e^{0.98}\approx 2.67$
+hours longer.\vspace{0.15cm}
+						\item manager, outdegree, and indegree shorten time to next email.						
+					\end{itemize}				
+				\end{frame}
+
+				\begin{frame}
+					\frametitle{Comparison: \textcolor{red}{Lognormal} vs. \textcolor{red}{Exponential}}
+					\begin{itemize}
+						\item \textcolor{blue}{Out-of-sample predictions}: sender, receiver, and timestamp 
+							\begin{figure}[!t]
+								\centering
+										\includegraphics[width=0.3\textwidth]{senderpredict-1.png}	
+										\includegraphics[width=0.3\textwidth]{receiverpredict-1.png}	
+										\includegraphics[width=0.3\textwidth]{timepredict-1.png}
+							\end{figure}
+
+						\item \textcolor{blue}{Posterior predictive checks} (PPC)
+							\begin{figure}[t]
+								\centering
+										\includegraphics[width=.54\textwidth]{outdegree2-1.png}	
+										\includegraphics[width=0.3\textwidth]{timePPplot2-1.png}
+							\end{figure}
+
 					\end{itemize}
@@
 							\begin{frame}
-			\frametitle{Results: Exploratory Analysis}
+								\frametitle{Conclusion and Discussion}
 								\begin{itemize}
-				\item Coefficients for receiver selection features
-				\item Coefficients for event timing features
-			\end{itemize}
+									\item Account for \textcolor{blue}{hyperedges} without duplications\vspace{0.15cm}
+									\item Flexible choice of \textcolor{blue}{continuous-time distribution} via GLM\vspace{0.15cm}
+									\item Reverse the process for  \textcolor{blue}{multiple senders to one receiver}\\ (e.g., international sanctions and co-sponsorship of bills)\vspace{0.15cm}
+									\item Sources: http://arxiv.org/abs/1807.08225 \\
+						https://github.com/desmarais-lab/MulticastNetwork
 
-		\end{frame}				
-				\begin{frame}
-					\frametitle{Comparison: Lognormal vs. Exponential}
-					\begin{itemize}
-						\item Covariates
-					\end{itemize}
-				\end{frame}	
-							\begin{frame}
-								\frametitle{Conclusions}
-								\begin{itemize}
-									\item Covariates
 								\end{itemize}

### 2018-09-05 paper/revision1/HEM-reply.tex
Revision 1 folder created

\documentclass[12pt]{article}

\topmargin 0pt \advance \topmargin by -\headheight \advance
\topmargin by -\headsep \textheight 8.9in \oddsidemargin 0pt
\evensidemargin \oddsidemargin \marginparwidth 0.5in \textwidth
6.5in

\renewcommand{\baselinestretch}{1.33}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{exscale}
\usepackage{multirow}
\usepackage[mathscr]{eucal}
\usepackage{bm}
\usepackage{eqlist} % Makes for a nice list of symbols.
\usepackage[final]{graphicx}
\usepackage[dvipsnames]{color}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{caption}
\usepackage{enumerate}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}

\usepackage{etoolbox}

\newtheorem{thm}{Theorem}

\newcommand{\aset}{{\mathcal A}}
\newcommand{\boldbeta}{{\boldsymbol{\beta}}}

\def\red{\color{red}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\def\sgn{\mathrm{sign}}
\def\E{\mathrm{E}}
\def\Var{\mathrm{Var}}
\def\pr{\mathrm{Pr}}
\def\tr{\mathrm{tr}}
\def\ve{\mathrm{vec}}
\def\diag{\mathrm{diag}}

\newcommand{\bff}{\mathrm{\bf f}}
\def\aset{\mathcal{A}}
\def\bset{\mathcal{B}}
\def\sset{\mathcal{S}}
\def\ba{\boldsymbol{a}}
\def\hba{\boldsymbol{\hat a}}
\newcommand{\hf}{\widehat \bff}
\newcommand{\bphi}{\mbox{\boldmath $\phi$}}
\newcommand{\hphi}{\widehat\bphi}
\newcommand{\Sig}{\mathbf{\Sigma}}
\newcommand{\hSig}{\widehat\Sig}
\newcommand{\hbSig}{\widehat\bSigma}
\newcommand{\hlam}{\widehat\lambda}
\newcommand{\hLam}{\widehat \bLam}
\newcommand{\bLam}{\mbox{\boldmath $\Lambda$}}
\def\br{\boldsymbol{r}}
\def\hbr{\boldsymbol{\hat r}}
\def\bu{\boldsymbol{u}}
\def\bv{\boldsymbol{v}}
\def\bx{\boldsymbol{x}}
\def\bxi{\boldsymbol{\xi}}
\def\by{\boldsymbol{y}}
\def\bZ{\boldsymbol{Z}}
\def\bz{\boldsymbol{z}}
\def\bp{\boldsymbol{p}}
\def\bX{\boldsymbol{X}}
\def\bW{\boldsymbol{W}}
\def\bY{\boldsymbol{Y}}
\def\bQ{\boldsymbol{Q}}
\def\hbQ{\boldsymbol{\hat Q}}
\def\bA{\boldsymbol{A}}
\def\hbA{\boldsymbol{\hat A}}
\def\bD{\boldsymbol{D}}
\def\hbD{\boldsymbol{\hat D}}
\def\bI{\boldsymbol{I}}
\def\bS{\boldsymbol{S}}
\def\bV{\boldsymbol{V}}
\def\bR{\boldsymbol{R}}
\def\hbR{\boldsymbol{\hat R}}
\def\tbR{\boldsymbol{\tilde R}}
\def\bH{\boldsymbol{H}}
\def\bL{\boldsymbol{L}}
\def\bM{\boldsymbol{M}}
\def\bN{\boldsymbol{N}}
\def\boldf{\boldsymbol{f}}

\def\bpi{\boldsymbol{\pi}}
\def\bmu{\boldsymbol{\mu}}
\def\hbmu{\boldsymbol{\hat\mu}}
\def\bzero{\boldsymbol{0}}
\def\bSigma{\boldsymbol{\Sigma}}
\def\hbSigma{\boldsymbol{\hat\Sigma}}
\def\bOmega{\boldsymbol{\Omega}}
\def\bPsi{\boldsymbol{\Psi}}
\def\bDelta{\boldsymbol{\Delta}}

\def\bG{\boldsymbol{\Gamma}}
%\def\hbGamma{\boldsymbol{\hat\Gamma}}
%\def\bgamma{\boldsymbol{\gamma}}
%\def\hbgamma{\boldsymbol{\hat\gamma}}

\def\bGamma{\boldsymbol{\Sigma}}
\def\hbGamma{\boldsymbol{\hat\Sigma}}
\def\bgamma{\boldsymbol{\sigma}}
\def\hbgamma{\boldsymbol{\hat\sigma}}

\def\bbeta{\boldsymbol{\beta}}
\def\bpsi{\boldsymbol{\psi}}
\def\btheta{\boldsymbol{\theta}}
\def\mvnorm{N_k(\bzero,\mathbf{\Sigma})}

\def\F{\mathcal{F}}
\def\G{\mathcal{G}}
\def\H{\mathcal{H}}
\def\P{\mathcal{P}}
\def\U{\mathcal{U}}

\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ben{\begin{equation*}}
\def\een{\end{equation*}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\bean{\begin{eqnarray*}}
\def\eean{\end{eqnarray*}}

\date{\today}
\begin{document}
%\begin{flushright}
%March 31, 2012
%\end{flushright}

\begin{center}
\textbf{Authors' Responses to Associate Editor}
\end{center}
\begin{center}
\textsl{The Hyperedge Event Model}
\end{center}

Thank you for acknowledging our efforts and contributions, and also for your constructive suggestions, which are very helpful to improve the quality of our paper.

\begin{itemize}
	\item Presentation

	\textbf{  Response:} 
	\begin{itemize}
		\item Unusual notations such as actor $A$ and covariates $y$. Also $u_{ie}$ is the $i$th line of matrix $u_e$, while $\tau_e = min_i(\tau_{ie})$. \textcolor{red}{(discuss)} 
		\item Change the order of Equation (2.2) and (2.1) and not use `intensity'. \textcolor{blue}{(done)}
		\item Hard to understand 2.2 without 2.3. More explanation on $\tau_{ie}$ above Equation (2.5) and what $\mu$ represents in $V(\mu)$. \textcolor{blue}{(done)}
	\end{itemize}

	\item Discussion of relevant literature

	\textbf{  Response:} 
	\begin{itemize}
		\item Perry and Wolfe (2013) arxiv version has a model for multicast. Any differences/advantages?
		\item Why cite Snijders (1996) in 2.3? Be specific. \textcolor{blue}{(done)}
	\end{itemize}

	\item Model, covariates and missing data

		\textbf{  Response:} 
		\begin{itemize}
			\item Observations $(s_e, r_e, t_e)_{e=1,\ldots,E}$ are not conditionaly independent since covariates depend on last 7 days. State this in Section 2 and modify out-of-sample algorithm using $(s_{e'}, r_{e'}, t_{e'})_{e':t_e<t_e'<t_e+l_e}$.  \textcolor{red}{(discuss)} 
		\end{itemize}
	\item MCMC sampler

		\textbf{  Response:} 
		\begin{itemize}
			\item Details on M-H proposals for $\boldsymbol{b}$ and $\boldsymbol{\eta}$ in Section 3.2. \textcolor{blue}{(done)}
			\item Inefficient sampler for $u_{iej}$ especially when most are one-to-one. Comment on this and the mixing of MCMC samplers.  \textcolor{red}{(discuss)} 
			\item Move Geweke to appendix \textcolor{blue}{(done)} and use larger number of nodes and events.
			\item Computational complexity per iterations of the samplers.
		\end{itemize}

	\item Typos \textcolor{blue}{(done)}

		\textbf{  Response:} We fixed all the typos identified by the reviewer as well as other writing issues, and we highly appreciate your considerable comments on these which were extremely helpful.
\end{itemize}

\newpage

\begin{center}

\textbf{Authors' Responses to Reviewer 1}
\end{center}
\begin{center}
\textsl{The Hyperedge Event Model}
\end{center}

Thank you for acknowledging our efforts and contributions, and also for your constructive suggestions, which are very helpful to improve the quality of our paper.
\begin{itemize}
	\item Presentation and writing

	\textbf{  Response:} We fixed all the typos, unclear parts, and issues in the bibliography \textcolor{blue}{(bib not working)} identified by the reviewer. We highly appreciate your considerable comments on these which were extremely helpful. \textcolor{blue}{(done)}

  \item Literature review

\textbf{  Response:} 
\begin{itemize}
	\item More comprehensive review including temporal ERGMS and dynamic latent variable models, and discuss contributions and novelties in the light of alternatives
\end{itemize}

\item Section 2

\textbf{  Response:} Rewrite Section 2 to provide a much clear picture of the model.

\item Prior specification

\textbf{  Response:} 
\begin{itemize}
	\item Use weakly informative priors as generic priors instead of assuming $N(0, \infty)$
	\item Sensitivity analyses to check how much posterior inference is affected by the hyperparameters' settings, and, possibly, suggest some default values.  \textcolor{red}{(discuss)} 
\end{itemize}

\item Posterior computation  \textcolor{red}{(discuss)}

\textbf{  Response:} 
\begin{itemize}
	\item Type of MH, proposal distribution, acceptance rate, smart proposal
	\item Comment on poor mixing on data augmentation
	\item Extent of scaling, bigger dataset, information on computational time
\end{itemize}
\item Application  \textcolor{red}{(discuss)}

\textbf{  Response:} 
\begin{itemize}
	\item Better baseline than random guess $1/18$ 
	\item Compare with SAOMs and extensions in PPE and PPC 
	\item Bad results in predicting timestamps (MdAPE)
	\item More conservative interpretations 
\end{itemize}
\end{itemize}

\end{document}

### 2018-09-05 paper/revision1/ba-sample.tex
Revision 1 folder created

--- 2018-06-27 paper/ba-HEM/ba-sample.tex
@@
 Dynamic network data often naturally arise as ``hyperedges'' \citep{karypis1999multilevel,ghoshal2009random,zlatic2009hypergraph,zhang2010hypergraph} that include one sender and multiple receivers or one receiver and multiple senders.
-For example, in email networks \citep{newman2002email}, each email encodes a hyperedge from one sender to one or more receviers.
+For example, in email networks \citep{newman2002email}, each email encodes a hyperedge from one sender to one or more receivers.
 Networks formed between neurons via axons and dendrites involve hyperedges with one sender and multiple receivers (axons) or one receiver and multiple senders (dendrites) \citep{partzsch2012developing}.
-Networks formed through the cosponsorhip of legislative bills \citep{fowler2006legislative} involve hyperedges with multiple senders (cosponsors) and one receiver (sponsor).
+Networks formed through the cosponsorship of legislative bills \citep{fowler2006legislative} involve hyperedges with multiple senders (cosponsors) and one receiver (sponsor).
 Economic sanctions between countries \citep{cranmer2014reciprocity} induce networks with hyperedges between multiple sending countries and one target country.
@@
 We explain these steps in more detail below.
+Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $A=5$.
 For hyperedge events that involve one receiver and one or more senders, we treat $s_e$ to be an indicator vector of senders $\boldsymbol{s}_e$ and $r_e$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).~\looseness=-1
-
+			\begin{figure}[!t]
+				\centering
+				\includegraphics[width=0.625\textwidth]{img/diagramnew.png}	
+				\caption {An illustrative example of the generative process of the HEM.}
+				\label{figure:diagram}
+			\end{figure}	
 	\subsection{Candidate receivers}\label{subsec: Tie}
@@
 j$, we define the ``receiver intensity"---i.e., the conditional logit of the probability that hyperedge event $e$ is being directed from sender $i$ to receiver $j$---as a linear combination of statistics relevant to the receiver selection process:
-	For every possible sender--receiver pair $(i,j)$ where $i \!\neq\! j$, we define the ``receiver intensity" as a linear combination of statistics relevant to the receiver selection process:
+	The HEM assumes that the sender of each hyperedge event is the sender that would initiate their respective event with the greatest urgency (i.e., the earliest timestamp).
+Our model thus assumes that for every event $e$, every possible sender $i$ generates a candidate receiver set that would be the receiver set of event $e$ if sender $i$ were the sender.
+For an event $e$, we first define an $A\times A$ matrix $\boldsymbol{u}_e$ where the $i^{\textrm{th}}$ row denotes sender $i$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $i$ intends to direct event $e$.
+We then assume that each receiver vector $\boldsymbol{u}_{ie}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
+Motivated by the Gibbs measure \citep{fellows2017removing}, we define a probability measure ``MB$_{G}$" in order to avoid drawing hyperedge events with no receiver.
+This probability measure amounts to a non-empty Gibbs measure, in which the all-zero vector is excluded from the support of the multivariate Bernoulli distribution.
+As a result, this measure helps us to (1) allow a sender to select multiple receivers for a single event, (2) force the sender to select at least one receiver, and (3) ensure a tractable normalizing constant for the receiver selection distribution.
+To be specific, we draw a binary vector $\boldsymbol{u}_{ie}= (u_{ie1},
+	\ldots, u_{ieA})$ for $i$th row of matrix $\boldsymbol{u}$ using
+	\begin{equation} \boldsymbol{u}_{ie}  \sim
+		\mbox{MB}_{G}(\boldsymbol{\lambda}_{ie}),
+	\end{equation}
+	where $\boldsymbol{\lambda}_{ie}= (\lambda_{ie1},
+	\ldots, \lambda_{ieA})$ and $\lambda_{iej}$ is the linear combination of statistics relevant to the receiver selection process for every possible sender--receiver pair $(i,j)$ where $i \!\neq\!
+j$.
+In other words, we define
 	\begin{equation}
@@
 	where $\boldsymbol{b}$ is a $P$-dimensional vector of coefficients and $\boldsymbol{x}_{iej}$ is a set of receiver selection features.
-As we show below, this intensity contributes to the probability that $i$ directs event $e$ towards receiver $j$.
+As we show below, $\lambda_{iej}$ contributes to the probability that $i$ directs event $e$ towards receiver $j$.
 The features $\boldsymbol{x}_{iej}$ can capture common network processes like popularity, reciprocity, and transitivity, as well as the effects of attributes of the sender and receivers (e.g., their gender), or attributes of sender--receiver pairs (e.g., whether the sender is a supervisor of the receiver's).
-We also include a normally distributed intercept term to account for the average (or baseline) number of receivers: $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$.~\looseness=-1
+We also include a normally distributed intercept term to account for the average (or baseline) number of receivers: $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$.
+~\looseness=-1
 
-	The HEM assumes that the sender of each hyperedge event is the sender that would initiate their respective event with the greatest urgency (i.e., the earliest timestamp).
-Our model thus assumes that for every event $e$, every possible sender $i$ generates a candidate receiver set that would be the receiver set of event $e$ if sender $i$ were the sender.
-For an event $e$, we first define an $A\times A$ matrix $\boldsymbol{u}_e$ where the $i^{\textrm{th}}$ row denotes sender $i$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $i$ intends to direct event $e$.
-We then assume that each receiver vector $\boldsymbol{u}_{ie}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
-In order to avoid drawing hyperedge events with no receivers, we define a probability measure ``MB$_{G}$" motivated by the Gibbs measure \citep{fellows2017removing}.
-The probability measure we define amounts to a non-empty Gibbs measure, in which the all-zero vector is excluded from the support of the multivariate Bernoulli distribution.
-As a result, this measure helps us to (1) allow a sender to select multiple receivers for a single event, (2) force the sender to select at least one receiver, and (3) ensure a tractable normalizing constant for the receiver selection distribution.
-To be specific, we draw a binary vector $\boldsymbol{u}_{ie}= (u_{ie1},
-	\ldots, u_{ieA})$ 
-	\begin{equation} \boldsymbol{u}_{ie}  \sim
-		\mbox{MB}_{G}(\boldsymbol{\lambda}_{ie}),
-	\end{equation}
-	where $\boldsymbol{\lambda}_{ie}= (\lambda_{ie1},
-	\ldots, \lambda_{ieA})$. In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ie})$ as
+	In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ie})$ as
 	\begin{equation}
@@
 	where $Z(\boldsymbol{\lambda}_{ie})$ is the normalizing constant, $\lVert \cdot \rVert_1$ is the $\ell_1$-norm, and the log-indicator term $\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0 )\big)$ ensures that empty receiver sets are excluded from the distribution's support.
-These modeling assumptions facilitate efficient posterior inference since we can derive a closed form expression for the normalizing constant---i.e., $Z(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$---and thus do not need to perform brute-force summation over the support of $\boldsymbol{u}_{ie} \in [0,1]^A$.
+These modeling assumptions facilitate efficient posterior inference since we can derive a closed form expression for the normalizing constant---i.e., $Z(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$---and thus do not need to perform brute-force summation over the support of $\boldsymbol{u}_{ie} \in \{0,1\}^A$.
 We provide detailed derivation steps for the normalizing constant $Z(\boldsymbol{\lambda}_{ie})$ in Appendix B.
@@
 	\subsection{Candidate timestamps}\label{subsec:Time}	
-	To generate timing for each event, the HEM first draws a candidate timestamp at which the event would be created given the candidate sender and receiver combinations.
-The timing rate for sender $i$ and event $e$ is
-	\begin{equation}
-		\mu_{ie} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ie}),
-	\end{equation}
-	where $\boldsymbol{\eta}$ is a $Q$-dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features---covariates that could affect timestamps of events, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
-
 	 In modeling ``when," we do not directly model the timestamp $t_e$.
 Instead, we assume that each sender's ``time increment"---i.e., waiting time to next event since $t_{e-1}$---is drawn from a specific exponential family distribution.
-We define the time increment from event $e-1$ to event $e$ as $\tau_{e}$ (i.e., $\tau_{e}= t_e-t_{e-1}$) and specify the distribution of candidate timestamps with sender-specfic mean $\mu_{ie}$.
-Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume the mean and variance of the $\tau_{ie}$ satistify~\looseness=-1
+We assume that every sender $i \in [A]$ generates his/her own time increment from event $e-1$ to event $e$, which we define as $\tau_{ie}$.
+We further specify that the distribution of $\tau_{ie}$ has sender-specific mean $\mu_{ie}$ and common variance $V(\mu)$.
+Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume that sender $i$'s time increment $\tau_{ie}$ satisfy~\looseness=-1
 	\begin{equation}
@@
 Possible choices of distribution include exponential, Weibull, gamma, and log-normal distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
-Based on the specific distribution, we may need other latent variables to draw the time increment, to account for the variance of time increments, beyond the coefficients for the features used to model the rate.
-$V(\mu)$---e.g., the shape parameter $k$ for the Weibull, the shape parameter $\theta$ for the gamma, and the variance parameter $\sigma_\tau^2$ for the log-normal.
-We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.~\looseness=-1
+Based on the specific distribution, we may need other latent variables to draw the time increment, to account for the variance of time increments $V(\mu)$---e.g., the shape parameter $k$ for the Weibull, the shape parameter $\theta$ for the gamma, and the variance parameter $\sigma_\tau^2$ for the log-normal---beyond the coefficients for the features used to model the rate.
+We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
+Similar to Section \ref{subsec: Tie}, the timing rate $\mu_{ie}$ for sender $i$ and event $e$ follows
+	\begin{equation}
+	\mu_{ie} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ie}),
+	\end{equation}
+	where $\boldsymbol{\eta}$ is a $Q$-dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features---covariates that could affect timestamps of events, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
 
 	\subsection{Senders, receivers, and timestamps}\label{subsec:Observed}
-	Finally, our model assumes that the observed sender, receivers, and timestamp of hyperedge event $e$ are generated by selecting the sender--receiver-set pair with the smallest time increment \citep{snijders1996stochastic}:
+		After the HEM draws the candidate timestamp vector $\boldsymbol{\tau}_e=\{\tau_{1e},\ldots,\tau_{Ae}\}$ at which the event would be created given the candidate sender and receiver combinations, finally our model assumes that the observed sender, receivers, and timestamp of hyperedge event $e$ are generated by selecting the sender--receiver-set pair with the smallest time increment:
 	\begin{equation}
@@
 	\end{algorithm}
-		Therefore, the HEM assumes a sender-driven process---i.e., the receivers and timestamp of an event are jointly determined by the sender's urgency to direct the event to those selected receivers.
-Note that our generative process allows for tied events.
+		Therefore, the HEM assumes a sender-driven process---i.e., the receivers and timestamp of an event are jointly determined by the sender's urgency to direct the event to those selected receivers---which is similar to \cite{snijders1996stochastic} in that each actor gets his/her own rate function to determine ``who will make the next change in network." Note that our generative process allows for tied events.
 In the case of tied events---i.e., multiple senders draw exactly the same candidate timestamps---we assume that all events are generated and occur simultaneously.
-Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers, and Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $A=5$.~\looseness=-1
-		\begin{figure}[!t]
-			\centering
-			\includegraphics[width=0.625\textwidth]{img/diagramnew.png}	
-			\caption {An illustrative example of the generative process of the HEM.}
-			\label{figure:diagram}
-		\end{figure}
+Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers.~\looseness=-1
 
 	\section{Posterior inference}\label{sec:inference}
-	In this section we describe how we invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_e\}_{e=1}^E$, coefficients for receiver selection features $\boldsymbol{b}$, and coefficients for event timing features $\boldsymbol{\eta}$---conditioned on the observed data $\{(s_e, \boldsymbol{r}_e, t_e)\}_{e=1}^E$, covariates $\{(\boldsymbol{x}_e, \boldsymbol{y}_e)\}_{e=1}^E$, and hyperparamters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
+	In this section we describe how we invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_e\}_{e=1}^E$, coefficients for receiver selection features $\boldsymbol{b}$, and coefficients for event timing features $\boldsymbol{\eta}$---conditioned on the observed data $\{(s_e, \boldsymbol{r}_e, t_e)\}_{e=1}^E$, covariates $\{(\boldsymbol{x}_e, \boldsymbol{y}_e)\}_{e=1}^E$, and hyperparameters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
 We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each latent variable from its conditional posterior via a Metropolis-within-Gibbs sampling algorithm.
 In the next subsection, we provide each latent variable's conditional posterior along with pseudocode of MCMC in Algorithm \ref{alg:MCMC}.
-We also evaluate the correctness of both our mathematical derivations and software implemenation using the prior--posterior simulator test of \cite{geweke2004getting}.
+We also evaluate the correctness of both our mathematical derivations and software implemenation using the prior--posterior simulator test of \cite{geweke2004getting} in Appendix C.
 
-	\subsection{Conditional posteriors}\label{subsec:conditionaldist}
+	%\subsection{Conditional posteriors}\label{subsec:conditionaldist}
 	\subsubsection{Candidate receivers}
-	In our model, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $P(\boldsymbol{b}|\,\boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}|\,\boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
+	In our model, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $\Pr(\boldsymbol{b}|\,\boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ and $\Pr(\boldsymbol{\eta}|\,\boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
 However, it is possible to augment the data by candidate receivers $\boldsymbol{u}$ such that we can obtain their conditional posterior by conditioning on samples of $\boldsymbol{u}$.
@@
 	\end{equation}
-	where the subscript ``$\backslash j$'' denotes a quantity excluding data from position $j$ and $\text{I}(\cdots)$ is the indicator function that prevents empty receiver sets. 
+	where the subscript ``$\backslash j$'' denotes a quantity excluding data from position $j$ and $\text{I}(\cdot)$ is the indicator function that prevents empty receiver sets. 
 	\subsubsection{Coefficients for receiver selection features}
-	Unlike the candidate receivers above, the conditional posterior for $\boldsymbol{b}$ does not have a closed form; however $\boldsymbol{b}$ may instead be re-sampled using the Metropolis--Hastings (MH) algorithm.
-Assuming an uninformative prior (i.e., $N({0},\infty)$), the conditional posterior for $\boldsymbol{b}$ is proportional to~\looseness=-1
+	Unlike the candidate receivers above, the conditional posterior for $\boldsymbol{b}$ does not have a closed form; however $\boldsymbol{b}$ may instead be re-sampled using the Metropolis--Hastings (MH) algorithm using the proposal distribution $N(\boldsymbol{0}, \delta_b\times I_P)$, where $\delta_b$ is the proposal variance parameter for $\boldsymbol{b}$.
+Assuming an uninformative prior (i.e., $N(\boldsymbol{0},\infty)$), the conditional posterior for $\boldsymbol{b}$ is proportional to~\looseness=-1
 	\begin{equation}
@@
 	\subsubsection{Coefficients for event timing features}
-	Likewise, we use the MH algorithm to update the latent variable $\boldsymbol{\eta}$.
-Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N({0},\infty)$), the conditional posterior for an untied event case is proportional to~\looseness=-1
+	Likewise, we use the MH algorithm to update the latent variable $\boldsymbol{\eta}$ using the proposal distribution $N(\boldsymbol{0}, \delta_\eta\times I_Q)$, where $\delta_\eta$ is the proposal variance parameter for $\boldsymbol{\eta}$.
+Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N(\boldsymbol{0},\infty)$), the conditional posterior for an untied event case is proportional to~\looseness=-1
 	\begin{equation}
@@
 
-	\subsection{Getting it Right (GiR) test} \label{subec:GiR}
-	Software development is integral to the objective of applying our model to real world data.
-Code review is a valuable process in any research computing context, and the prevalence of software bugs in statistical software is well documented \citep[e.g., ][]{altman2004numerical,mccullough2009accuracy}.
-With highly complex models such as the HEM, there are many ways in which software bugs can be introduced and go unnoticed.
-As such, we present a joint analysis of the integrity of our generative model, sampling equations, and software implementation.
-
-	\cite{geweke2004getting} introduced the ``Getting it Right'' (GiR) test---a joint distribution test of posterior simulators which can detect errors in sampling equations as well as software bugs---and it has been used to test the implementation of Bayesian inference algorithms \citep{zhao2016bayesian}.
-The test involves comparing the distributions of variables simulated from two joint distribution samplers, which we call ``forward" and ``backward" samplers.
-The ``forward" sampler draws joint samples of the latent and observable variables from the prior.
-The ``backward" sampler begins by first drawing a joint sample of the latent and observed variables from the prior.
-It then alternates between re-sampling the latent variables, conditioned on the observable variables, from the MCMC transition operator, and then re-sampling the observable variable, conditioned on the latent variables, from the model likelihood.
-If the MCMC transition operator is correctly derived and implemented, this process should asymptotically generate joint samples of the latent and observable variables from the prior, like the forward sampler.
-
-	In the forward sampler, both observable and unobservable variables are generated using Algorithm \ref{alg:generative}.
-In the backward samples, unobservable variables are generated using the sampling equations for inference, which we derived in Section \ref{subsec:conditionaldist}.
-For each forward and backward sample that consists of $E$ number of events, we save these statistics:\\
-	\begin{itemize}
-		\item[1.] Mean of observed receiver sizes $ \lVert \boldsymbol{r}_{e} \rVert_1 $ across $e=1,\ldots,E$,
-		\item[2.] Variance of observed receiver sizes $ \lVert \boldsymbol{r}_{e} \rVert_1 $ across $e=1,\ldots,E$,
-		\item[3.] Mean of time increments $\tau_e$ across $e=1,...,E$,
-		\item[4.] Variance of time increments $\tau_e$ across $e=1,...,E$,
-		\item[5.] $b_p$ value used to generate the samples $p = 1,...,P$,
-		\item[6.] $\eta_q$ value used to generate the samples $q = 1,...,Q$,
-		\item[7.] $\sigma^2_\tau$ value used to generate the samples in log-normal distribution
-	\end{itemize}
-
-	To keep the computational burden of re-running thousands of rounds of inference manageable, we run the GiR using a relatively small artificial sample, consisting of $E=100$ events, $A=5$ nodes, $P=4$ number of receiver selection features, and $Q=3$ number of event timing features per each forward or backward sampler, using log-normal distibution for the time increments $f_\tau$.
-We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
-We also calculated t-test and Mann-Whitney test p-values in order to test for differences in the distributions generated in the forward and backward samples.
-Before we calculated these statistics, we thinned our samples by taking every 9th sample starting at the 10,000th sample for a resulting sample size of 10,000, in order to reduce the autocorrelation in the Markov chains.
-In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
-We depict the GiR results using probability--probability (P--P) plots, in which the empirical CDF values of the forward and backward samples are plotted on the $x$ and $y$ axes, respectively.
-If the two samples are from equivalent distributions, the empirical CDF values should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
-The GiR test results are depicted in Figure \ref{figure:GiRplot}.
-These results indicate that our sampling equations and software implementation pass the test on every statistic.
-		\begin{figure}[!t]
-			\centering
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Mean of $\lVert \boldsymbol{r}_{e} \rVert_1 $}
-				\includegraphics[width=\textwidth]{img/plot1.png}	
-			\end{subfigure}
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Variance of $\lVert \boldsymbol{r}_{e} \rVert_1 $}
-				\includegraphics[width=\textwidth]{img/plot2.png}	
-			\end{subfigure}
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Mean of $\tau_e$}
-				\includegraphics[width=\textwidth]{img/plot3.png}	
-			\end{subfigure}
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Variance of $\tau_e$}
-				\includegraphics[width=\textwidth]{img/plot4.png}	
-			\end{subfigure}
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Value of $b_1$}
-				\includegraphics[width=\textwidth]{img/plot5.png}	
-			\end{subfigure}
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Value of $b_2$}
-				\includegraphics[width=\textwidth]{img/plot6.png}	
-			\end{subfigure}   	   	   	   	   	   	   	
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Value of $b_3$}
-				\includegraphics[width=\textwidth]{img/plot7.png}	
-			\end{subfigure}   	   		   	   	
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Value of $b_4$}
-				\includegraphics[width=\textwidth]{img/plot8.png}	
-			\end{subfigure}   	   		   	   	
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Value of $\eta_1$}
-				\includegraphics[width=\textwidth]{img/plot9.png}	
-			\end{subfigure}   	   		   	   	
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Value of $\eta_2$}
-				\includegraphics[width=\textwidth]{img/plot10.png}	
-			\end{subfigure}   	   		   	   	
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Value of $\eta_3$}
-				\includegraphics[width=\textwidth]{img/plot11.png}	
-			\end{subfigure}   	   		   	   	  		   	   	 	
-			\begin{subfigure}[b]{0.2425\textwidth}
-				\caption{Value of $\sigma^2_\tau$}
-				\includegraphics[width=\textwidth]{img/plot12.png}	
-			\end{subfigure}   	   		   	   	   	   		   	   	   		   	   	
-			\caption{Probability--probability (P--P) plots for the GiR test statistics.}
-			\label{figure:GiRplot}
-		\end{figure}   
 	\section{Application to email data}\label{sec:Emails}
@@
 Algorithm \ref{alg:PPE} outlines this procedure in detail.
-We compare the predictive performance of two versions of our model, each with a different timing distribution over the time increments using $N=500$.
+We compare the predictive performance of two versions of our model, each with a different timing distribution over the time increments, by repeating the predictive assessments$N=500$ times where we make new predictions each time for the fixed held out data.
 We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
@@
 Although the generative process for events (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{subfigure:PPEresults2} reveals slight difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal on average outperforms exponential.
-Finally, we define the prediction error for the $d^{\textrm{th}}$ missing timestamp bot be the median of the absolute relative errors, often referred to as median absolute percentage error (MdAPE), across $N=500$ predictions:
+Finally, the prediction error for the $d^{\textrm{th}}$ missing timestamp is estimated using the median of the absolute relative errors, often referred to as median absolute percentage error (MdAPE), across $N=500$ predictions:
 	\begin{figure}[!t]
@@
 We formally generated entirely new data by simulating $N=500$ synthetic email datasets $\{(s_{e}, \boldsymbol{r}_{e}, t_{e})\}_{e=1}^E$ from the generative process in Section \ref{sec:generative process}, conditional upon a set of inferred latent variables from inference in Section \ref{subsec:Result_email}\iffalse, where the pseudocode is outlined in Algorithm \ref{alg:PPC}\fi.
-For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: outdegree distribution---the number of emails sent by each node, indegree distribution---the number of emails received by each node, receiver size distribution---the number of receivers on each emails, and a probability--probability (P--P) plot for time increments.
+For the test of goodness-of-fit in terms of network dynamics, we use multiple statistics that summarize meaningful aspects of the data: (1) outdegree distribution and (2) indegree distribution, which is the number of emails sent by and received by each node respectively, (3) receiver size distribution (i.e., the number of receivers on each emails), and (4) a probability--probability (P--P) plot for time increments.
 	\iffalse
@@
 
-	Figure \ref{figure:PPCresults} illustrates the results of posterior predictive checks using the log-normal model, which fit the timestamps better than the exponential model (Section \ref{subsec:Experiment_email}).
+	Figure \ref{figure:PPCresults} illustrates the results of posterior predictive checks using the log-normal model, which fits the timestamps better than the exponential model (Section \ref{subsec:Experiment_email}).
 The upper two plots show node-specific posterior predictive degree distributions across $N=500$ synthetic samples, where the left one is for the outdegree statistic and the right plot is for the indegree statistic.
@@
 Here, the closeness to the diagonal line connecting $(0, 0)$ and $(1, 1)$ gives a measure of difference between the simulated and observed time increments, and our P--P plot shows that we have great performance in reproducing the observed timing distribution.
-Our findings from the predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are presented in Appendix C.
+Our findings from the predictive experiments in Section \ref{subsec:Experiment_email} are further revealed in the PPC from exponential distribution, where the PPC plots comparing log-normal and exponential distributions are presented in Appendix D.
 
@@
 While the inner iterations for $\sigma_\tau^2$ is fixed as 1, we specify the inner iterations $I_1=20$ for $\boldsymbol{b}$ and $I_2=10$ for $\boldsymbol{\eta}$ to adjust for slower convergence rates.
-Convergence diagnostics including the traceplots and Geweke diagnostics \citep{geweke1991evaluating} are provided in Appendix D.
+Convergence diagnostics including the traceplots and Geweke diagnostics \citep{geweke1991evaluating} are provided in Appendix E.
 
@@
 	\begin{equation*}
-		\mbox{logit}(\lambda_{iej})=\log\Big(\frac{\lambda_{iej}}{1-\lambda_{iej}}\Big) =b_{1}+b_{2} x_{iej2}\ldots+b_{14}x_{iej14},
+		\mbox{logit}(\lambda_{iej})=\log\Big(\frac{\lambda_{iej}}{1-\lambda_{iej}}\Big) =b_{1}+b_{2} x_{iej2}+\ldots+b_{14}x_{iej14},
 	\end{equation*}
-	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratios $\frac{\lambda_{iej}}{1-\lambda_{iej}}=\exp(b_{1}+b_{2} x_{iej2}\ldots+b_{14}x_{iej14})$.
-First of all, we find the effects of nodal coavariates ``gender\_\,sender$(i)$" and ``gender\_\,receiver$(j)$" are both nearly always negative in the posterior samples.
+	and can interpret the $\boldsymbol{b}$ estimates in terms of odds ratios $\frac{\lambda_{iej}}{1-\lambda_{iej}}=\exp(b_{1}+b_{2} x_{iej2}+\ldots+b_{14}x_{iej14})$.
+First of all, we find the effects of nodal covariates ``gender\_\,sender$(i)$" and ``gender\_\,receiver$(j)$" are both nearly always negative in the posterior samples.
 The log odds that any other node will be added as a receiver of an email is approximately two times less if the sender is a woman.
-The posterior distribution of the statistic ``outdegree$(i)$" is mostly negative, if sender $i$ sent $n$ number of emails to anyone last week, then sender $i$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $j$.
+The posterior distribution of the statistic ``outdegree$(i)$" is mostly negative, if node $i$ sent $n$ emails to anyone last week, then node $i$ is approximately $\exp(-0.109\times n)\approx(0.897)^n$ times less likely to send an email to $j$.
 However, this straightforward interpretation of the outdegree statistic only applies when the hyperedge size is low.
-The scenario in which a sender sends a lot of low-hyperedge-size emails may arise due to the use of email for a one-on-one conversation.
+The scenario in which a node sends a lot of low-hyperedge-size emails may arise due to the use of email for a one-on-one conversation.
 The large positive estimates of the interaction between hyperedge size and outdegree indicate that those who have recently sent many emails with many receivers on each email are likely to continue sending broadcast emails.
 This scenario may arise from someone being responsible for distributing timely announcements.
-When we look at the effect of ``indegree$(j)$," we see a clear popularity effect---those who have received a lot of emails a lot recently are likely to continue receiving a lot of emails.
-If the receiver $j$ received $n$ number of emails over the last week, sender $i$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $j$.
+When we look at the effect of ``indegree$(j)$," we see a clear popularity effect---those who have recently received a lot of emails are likely to continue receiving a lot of emails.
+If the receiver $j$ received $n$ emails over the last week, node $i$ is $\exp(0.086\times n)\approx(1.091)^n $ times more likely to send an email to $j$.
 			\begin{figure}[!t]
@@
 
-	When we look at the effects of dyadic and triadic covariates, one thing that stands out is the large and positive posterior distribution of the statistic ``send$(i,j)$" (i.e., number of times $i$ sent emails to $j$ over the last week) with the posterior mean $\hat{b}_9 = 0.274$, implying that if $i$ sent $n$ number of emails to $j$ last week, then sender $i$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $j$.
+	When we look at the effects of dyadic and triadic covariates, one thing that stands out is the large and positive posterior distribution of the statistic ``send$(i,j)$" (i.e., number of times $i$ sent emails to $j$ over the last week) with the posterior mean $\hat{b}_9 = 0.274$, implying that if $i$ sent $n$ emails to $j$ last week, then node $i$ is approximately $\exp(0.274\times n)\approx(1.315)^n$ times more likely to send an email to $j$.
 The posterior distributions for the reciprocity effect (i.e., ``receive$(i, j)$''), and the four triadic effects, are all fairly evenly spread around zero, so our results do not justify conclusions regarding the nature of these effects in the Montgomery county email network.
@@
 			&\log(\tau_{ie}) \sim N(\mu_{ie}, \sigma_\tau^2), \mbox{ with }\\
-			&\mu_{ie} = \eta_{1}+\eta_{2} y_{ie2}\ldots+\eta_{7}y_{ie7}.
+			&\mu_{ie} = \eta_{1}+\eta_{2} y_{ie2}+\ldots+\eta_{7}y_{ie7}.
 		\end{aligned}
@@
 To our knowledge, the HEM is the only existing model that can be used to generate the sender, receivers, and timestamp of interactions in real time.
-To make better use of the proposed model, we provide an algorithm for predictive experiments that help to learn which specification of HEM provides a better fit to the data.
+To make better use of the proposed model, we provide an algorithm for predictive experiments that helps to learn which specification of HEM provides a better fit to the data.
 
@@
 	\end{acknowledgement}
+
+		\newpage
+		\bibliographystyle{ba}
+	\bibliography{baHEM}
 
@@
 	\end{equation*}
-	where the receiver intensity is a linear combination of receiver selection features---i.e., $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$---as defined in Secton \ref{subsec: Tie}.
+	where $\lambda_{iej}$ is a linear combination of receiver selection features---i.e., $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$---as defined in Secton \ref{subsec: Tie}.
 
@@
 		\end{equation*}
+	\subsection*{Appendix C: Getting it Right (GiR) test} \label{subec:GiR}
+	Software development is integral to the objective of applying our model to real world data.
+Code review is a valuable process in any research computing context, and the prevalence of software bugs in statistical software is well documented \citep[e.g., ][]{altman2004numerical,mccullough2009accuracy}.
+With highly complex models such as the HEM, there are many ways in which software bugs can be introduced and go unnoticed.
+As such, we present a joint analysis of the integrity of our generative model, sampling equations, and software implementation.
 
-		\subsection*{Appendix C: Comparison of PPC results: log-normal vs. exponential}\label{appendix: PPCexp}
+	\cite{geweke2004getting} introduced the ``Getting it Right'' (GiR) test---a joint distribution test of posterior simulators which can detect errors in sampling equations as well as software bugs---and it has been used to test the implementation of Bayesian inference algorithms \citep{zhao2016bayesian}.
+The test involves comparing the distributions of variables simulated from two joint distribution samplers, which we call ``forward" and ``backward" samplers.
+The ``forward" sampler draws joint samples of the latent and observable variables from the prior.
+The ``backward" sampler begins by first drawing a joint sample of the latent and observed variables from the prior.
+It then alternates between re-sampling the latent variables, conditioned on the observable variables, from the MCMC transition operator, and then re-sampling the observable variable, conditioned on the latent variables, from the model likelihood.
+If the MCMC transition operator is correctly derived and implemented, this process should asymptotically generate joint samples of the latent and observable variables from the prior, like the forward sampler.
+
+	In the forward sampler, both observable and unobservable variables are generated using Algorithm \ref{alg:generative}.
+In the backward samples, unobservable variables are generated using the sampling equations for inference, which we derived in Section \ref{sec:inference}.
+For each forward and backward sample that consists of $E$ number of events, we save these statistics:\\
+	\begin{itemize}
+		\item[1.] Mean of observed receiver sizes $ \lVert \boldsymbol{r}_{e} \rVert_1 $ across $e=1,\ldots,E$,
+		\item[2.] Variance of observed receiver sizes $ \lVert \boldsymbol{r}_{e} \rVert_1 $ across $e=1,\ldots,E$,
+		\item[3.] Mean of time increments $\tau_e$ across $e=1,...,E$,
+		\item[4.] Variance of time increments $\tau_e$ across $e=1,...,E$,
+		\item[5.] $b_p$ value used to generate the samples $p = 1,...,P$,
+		\item[6.] $\eta_q$ value used to generate the samples $q = 1,...,Q$,
+		\item[7.] $\sigma^2_\tau$ value used to generate the samples in log-normal distribution
+	\end{itemize}
+
+	To keep the computational burden of repeated inference manageable, we run the GiR using a relatively small artificial sample, consisting of $E=100$ events, $A=5$ nodes, $P=4$ number of receiver selection features, and $Q=3$ number of event timing features per each forward or backward sampler, using log-normal distibution for the time increments $f_\tau$.
+We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.
+We also calculated $t$-test and Mann-Whitney test $p$-values in order to test for differences in the distributions generated in the forward and backward samples.
+Before we calculated these statistics, we thinned our samples by taking every 9th sample starting at the 10,000th sample for a resulting sample size of 10,000, in order to reduce the autocorrelation in the Markov chains.
+In each case, if we observe a large p-value, this gives us evidence that the distributions generated under forward and backward sampling have the same locations.
+We depict the GiR results using probability--probability (P--P) plots, in which the empirical CDF values of the forward and backward samples are plotted on the $x$ and $y$ axes, respectively.
+If the two samples are from equivalent distributions, the empirical CDF values should line up on a line with zero $y$-intercept, and unit slope (i.e., a 45-degree line).
+The GiR test results are depicted in Figure \ref{figure:GiRplot}.
+These results indicate that our sampling equations and software implementation pass the test on every statistic.
+	\begin{figure}[!t]
+		\centering
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Mean of $\lVert \boldsymbol{r}_{e} \rVert_1 $}
+			\includegraphics[width=\textwidth]{img/plot1.png}	
+		\end{subfigure}
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Variance of $\lVert \boldsymbol{r}_{e} \rVert_1 $}
+			\includegraphics[width=\textwidth]{img/plot2.png}	
+		\end{subfigure}
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Mean of $\tau_e$}
+			\includegraphics[width=\textwidth]{img/plot3.png}	
+		\end{subfigure}
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Variance of $\tau_e$}
+			\includegraphics[width=\textwidth]{img/plot4.png}	
+		\end{subfigure}
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Value of $b_1$}
+			\includegraphics[width=\textwidth]{img/plot5.png}	
+		\end{subfigure}
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Value of $b_2$}
+			\includegraphics[width=\textwidth]{img/plot6.png}	
+		\end{subfigure}   	   	   	   	   	   	   	
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Value of $b_3$}
+			\includegraphics[width=\textwidth]{img/plot7.png}	
+		\end{subfigure}   	   		   	   	
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Value of $b_4$}
+			\includegraphics[width=\textwidth]{img/plot8.png}	
+		\end{subfigure}   	   		   	   	
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Value of $\eta_1$}
+			\includegraphics[width=\textwidth]{img/plot9.png}	
+		\end{subfigure}   	   		   	   	
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Value of $\eta_2$}
+			\includegraphics[width=\textwidth]{img/plot10.png}	
+		\end{subfigure}   	   		   	   	
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Value of $\eta_3$}
+			\includegraphics[width=\textwidth]{img/plot11.png}	
+		\end{subfigure}   	   		   	   	  		   	   	 	
+		\begin{subfigure}[b]{0.2425\textwidth}
+			\caption{Value of $\sigma^2_\tau$}
+			\includegraphics[width=\textwidth]{img/plot12.png}	
+		\end{subfigure}   	   		   	   	   	   		   	   	   		   	   	
+		\caption{Probability--probability (P--P) plots for the GiR test statistics.}
+		\label{figure:GiRplot}
+	\end{figure}   
+		\subsection*{Appendix D: Comparison of PPC results: log-normal vs. exponential}\label{appendix: PPCexp}
 		\begin{figure}[H]
@@
 		\newpage
-		\subsection*{Appendix D: Convergence diagnostics}\label{appendix: convergence}
+		\subsection*{Appendix E: Convergence diagnostics}\label{appendix: convergence}
 		\begin{figure}[H]

### 2018-09-07 paper/revision1/HEM-reply.tex
revision plan added

@@
 
-\newpage
-
 \begin{center}
@@
 
+\newpage
+\begin{center}
+
+	\textbf{Revision Plans}
+\end{center}
+\begin{enumerate}
+	\item Section 1: Literature review
+	\begin{itemize}
+		\item Bomin: add literature review on Perry and Wolfe (2013) arxiv version and comment how our model differs from point process based models (AE1 bullet 2)
+		\item Bruce: add literature review on the general class of dynamic network inference including temporal ERGMS and dynamic latent variable models (R1 comment 2)
+	\end{itemize}
+	\item Section 2: Generative process
+		\begin{itemize}
+			\item Bomin: change few notations and add notation table in Appendix (AE1 bullet 1)
+			\item Bruce: overall rewriting such as rephrasing or clarification (R1 comment 3 \& AE1 bullet 1, minor ones already resolved)
+		\end{itemize}
+			\item Section 3: Inference
+			\begin{itemize}
+		\item Bomin: add more MH details and add a subsection 3.2 for computational issues---e.g., complexity and limitations (R1 comment 4, 5 \& AE1 bullet 4)
+				\item Bruce: check the added subsection 3.2 and revise
+			\end{itemize}
+			\item Section 4: Application
+			\begin{itemize}
+				\item Bomin: re-run PPE considering conditional dependence (section 4.2) and update results \& interpretations in 4.2 \& 4.4 (R1 comment 6 \& AE1 bullet 2)
+				\item Bruce: add why direct comparison with SAOMs not possible and come up with better idea than random guess...? (R1 comment 6)
+			\end{itemize}
+
+				\item Section 5: Conclusion
+				\begin{itemize}
+					\item Bruce: possibly further discussing our contribution in the light of alternatives added in the literature review (R1 comment 2)
+				\end{itemize}
+
+					\item Bibliography
+					\begin{itemize}
+						\item Bomin: tons of issues but somehow changes are not reflected...? Double check! (R1 comment 1)
+					\end{itemize}
+
+					\item Discuss: sensitivity analysis?					
+\end{enumerate}
+
 \end{document}

### 2018-09-09 paper/revision1/ba-sample.tex
revised notations

@@
 
-	The hyperedge event model (HEM) specifies a generative process for $E$ unique hyperedge events that occur between $A$ nodes.
-A single hyperedge event is indexed by $e \in [E]$---where $[E]$ denotes a categorical set with $E$ levels $[E] = \{1,\ldots,E\}$---and consists of three components: the sender $s_e \in [A]$, an indicator vector of receivers $\boldsymbol{r}_e$---where $r_{ej}=1$ if $j \in [A]$ is a receiver of hyperedge event $e$ and 0 otherwise---and the timestamp $t_e \in (0, \infty)$.
+	The hyperedge event model (HEM) specifies a generative process for $E$ unique hyperedge events that occur between $V$ number of nodes.
+A single hyperedge event is indexed by $e \in [E]$---where $[E]$ denotes a categorical set with $E$ levels $[E] = \{1,\ldots,E\}$---and consists of three components: the sender $s_e \in [V]$, an indicator vector of receivers $\boldsymbol{r}_e$---where $r_{ej}=1$ if $j \in [V]$ is a receiver of hyperedge event $e$ and 0 otherwise---and the timestamp $t_e \in (0, \infty)$.
 For simplicity, we assume that events are ordered by time such that $t_e \leq t_{e+1}$.
@@
 Data is generated from the HEM through a sampling process applied to the auxiliary variables.
-The auxiliary variables drawn for event $e$ include, for each possible sender $i \in [A]$, a time increment from event $e-1$ at which sender $i$ would create event $e$, and an $A-1$ length vector indicating which nodes would be the receivers of event $e$ if it were directed by sender $i$.
+The auxiliary variables drawn for event $e$ include, for each possible sender $i \in [V]$, a time increment from event $e-1$ at which sender $i$ would create event $e$, and an $V-1$ length vector indicating which nodes would be the receivers of event $e$ if it were directed by sender $i$.
 The data generated for event $e$ under the HEM corresponds to the sender that would create event $e$ the soonest---at the smallest time increment from event $e-1$.
@@
 We explain these steps in more detail below.
-Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $A=5$.
+Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $V=5$.
 For hyperedge events that involve one receiver and one or more senders, we treat $s_e$ to be an indicator vector of senders $\boldsymbol{s}_e$ and $r_e$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).~\looseness=-1
@@
 Our model thus assumes that for every event $e$, every possible sender $i$ generates a candidate receiver set that would be the receiver set of event $e$ if sender $i$ were the sender.
-For an event $e$, we first define an $A\times A$ matrix $\boldsymbol{u}_e$ where the $i^{\textrm{th}}$ row denotes sender $i$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $i$ intends to direct event $e$.
+For an event $e$, we first define an $V\times V$ matrix $\boldsymbol{u}_e$ where the $i^{\textrm{th}}$ row denotes sender $i$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $i$ intends to direct event $e$.
 We then assume that each receiver vector $\boldsymbol{u}_{ie}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
@@
 To be specific, we draw a binary vector $\boldsymbol{u}_{ie}= (u_{ie1},
-	\ldots, u_{ieA})$ for $i$th row of matrix $\boldsymbol{u}$ using
+	\ldots, u_{ieV})$ for $i$th row of matrix $\boldsymbol{u}$ using
 	\begin{equation} \boldsymbol{u}_{ie}  \sim
@@
 	where $\boldsymbol{\lambda}_{ie}= (\lambda_{ie1},
-	\ldots, \lambda_{ieA})$ and $\lambda_{iej}$ is the linear combination of statistics relevant to the receiver selection process for every possible sender--receiver pair $(i,j)$ where $i \!\neq\!
+	\ldots, \lambda_{ieV})$ and $\lambda_{iej}$ is the linear combination of statistics relevant to the receiver selection process for every possible sender--receiver pair $(i,j)$ where $i \!\neq\!
 j$.
@@
 		\begin{aligned}
-			&\Pr(\boldsymbol{u}_{ie}|\,\boldsymbol{b}, \boldsymbol{x}_{ie}) = \frac{1}{Z(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0 )\big) + \sum_{j\neq i} \lambda_{iej}u_{iej}\Big) ,
+			&\Pr(\boldsymbol{u}_{ie}|\,\boldsymbol{b}, \boldsymbol{x}_{ie}) = \frac{1}{C(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0 )\big) + \sum_{j\neq i} \lambda_{iej}u_{iej}\Big) ,
 		\end{aligned}
@@
 	\end{equation}
-	where $Z(\boldsymbol{\lambda}_{ie})$ is the normalizing constant, $\lVert \cdot \rVert_1$ is the $\ell_1$-norm, and the log-indicator term $\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0 )\big)$ ensures that empty receiver sets are excluded from the distribution's support.
-These modeling assumptions facilitate efficient posterior inference since we can derive a closed form expression for the normalizing constant---i.e., $Z(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$---and thus do not need to perform brute-force summation over the support of $\boldsymbol{u}_{ie} \in \{0,1\}^A$.
-We provide detailed derivation steps for the normalizing constant $Z(\boldsymbol{\lambda}_{ie})$ in Appendix B.
+	where $C(\boldsymbol{\lambda}_{ie})$ is the normalizing constant, $\lVert \cdot \rVert_1$ is the $\ell_1$-norm, and the log-indicator term $\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0 )\big)$ ensures that empty receiver sets are excluded from the distribution's support.
+These modeling assumptions facilitate efficient posterior inference since we can derive a closed form expression for the normalizing constant---i.e., $C(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$---and thus do not need to perform brute-force summation over the support of $\boldsymbol{u}_{ie} \in \{0,1\}^V$.
+We provide detailed derivation steps for the normalizing constant $C(\boldsymbol{\lambda}_{ie})$ in Appendix B.
 
-	% $Z(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$
+	% $C(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$
 
@@
 Instead, we assume that each sender's ``time increment"---i.e., waiting time to next event since $t_{e-1}$---is drawn from a specific exponential family distribution.
-We assume that every sender $i \in [A]$ generates his/her own time increment from event $e-1$ to event $e$, which we define as $\tau_{ie}$.
-We further specify that the distribution of $\tau_{ie}$ has sender-specific mean $\mu_{ie}$ and common variance $V(\mu)$.
-Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume that sender $i$'s time increment $\tau_{ie}$ satisfy~\looseness=-1
+We assume that every sender $i \in [V]$ generates his/her own time increment from event $e-1$ to event $e$, which we define as $\tau_{ie}$.
+We further specify that the distribution of $\tau_{ie}$ has sender-specific mean $\mu_{ie}$ and common variance $\sigma_\tau^2$.
+Following the generalized linear model (GLM) framework \citep{nelder1972generalized}, we assume that sender $i$'s time increment $\tau_{ie} > 0$ satisfy~\looseness=-1
 	\begin{equation}
 		\begin{aligned}
-			E(\tau_{ie}) &= \mu_{ie},\\
-			V(\tau_{ie}) &= V(\mu),
+\mbox{E}(\tau_{ie}) &= \mu_{ie},\\
+\mbox{Var}(\tau_{ie}) &= \sigma_\tau^2,
 		\end{aligned}
@@
 		% \footnote{The log-normal distribution is not exponential family but can be used via modeling of $\log(\tau_e)$.} 
-	where $\tau_{ie}$ here is a positive real number.
+	where the timing rate $\mu_{ie}$ for sender $i$ and event $e$ is determined by the linear combination of statistics relevant to timing selection process, similar to Section \ref{subsec: Tie}.
+Specifically, we define
+	\begin{equation}
+		\mu_{ie} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{z}_{ie}),
+	\end{equation}
+	where $\boldsymbol{\eta}$ is a $Q$-dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{z}_{ad}$ is a set of event timing features---covariates that could affect timestamps of events, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
 Possible choices of distribution include exponential, Weibull, gamma, and log-normal distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
-Based on the specific distribution, we may need other latent variables to draw the time increment, to account for the variance of time increments $V(\mu)$---e.g., the shape parameter $k$ for the Weibull, the shape parameter $\theta$ for the gamma, and the variance parameter $\sigma_\tau^2$ for the log-normal---beyond the coefficients for the features used to model the rate.
-We use $f_\tau(\cdot; \mu, V(\mu))$ and $F_\tau(\cdot; \mu, V(\mu))$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $V(\mu)$.
-Similar to Section \ref{subsec: Tie}, the timing rate $\mu_{ie}$ for sender $i$ and event $e$ follows
-	\begin{equation}
-	\mu_{ie} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ie}),
-	\end{equation}
-	where $\boldsymbol{\eta}$ is a $Q$-dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{y}_{ad}$ is a set of event timing features---covariates that could affect timestamps of events, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
-
+Based on the specific distribution, we may need another latent variable to account for the variance of time increments, such as the shape parameter for Weibull and gamma, or the variance parameter for log-normal, which is commonly used across $i\in [V]$ and $e \in [E]$.
+We use $f_\tau(\cdot; \mu, \sigma_\tau^2)$ and $F_\tau(\cdot; \mu, \sigma_\tau^2)$ to denote the probability density function (p.d.f) and cumulative density function (c.d.f), respectively, with mean $\mu$ and variance $\sigma_\tau^2$.
 	\subsection{Senders, receivers, and timestamps}\label{subsec:Observed}
-		After the HEM draws the candidate timestamp vector $\boldsymbol{\tau}_e=\{\tau_{1e},\ldots,\tau_{Ae}\}$ at which the event would be created given the candidate sender and receiver combinations, finally our model assumes that the observed sender, receivers, and timestamp of hyperedge event $e$ are generated by selecting the sender--receiver-set pair with the smallest time increment:
-	\begin{equation}
-		\begin{aligned}
-			s_e &= \mbox{argmin}_{i}(\tau_{ie}),\\
-			\boldsymbol{r}_e &= \boldsymbol{u}_{s_e e},\\
-			t_e &=t_{e-1} + \tau_{s_e e}.
-		\end{aligned}
-	\end{equation}
+		After the HEM draws the candidate timestamp vector $\boldsymbol{\tau}_e=\{\tau_{1e},\ldots,\tau_{Ve}\}$ at which the event would be created given the candidate sender and receiver combinations, finally our model assumes that the observed sender, receivers, and timestamp of hyperedge event $e$ are generated by selecting the sender--receiver-set pair with the smallest time increment:
 			\begin{algorithm}[!t]
@@
 				\begin{algorithmic}
-			\STATE \textbf{Input}: number of events and nodes $(E, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
+					\STATE \textbf{Input}: number of events and nodes $(E, V)$, covariates $(\boldsymbol{x}, \boldsymbol{z})$, and coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
 					\vskip 0.1in
 					\FOR{$e=1$ to $E$}
-			\FOR{$i=1$ to $A$}
-			\FOR{$j=1$ to $A$ ($j \neq i$)}
+					\FOR{$i=1$ to $V$}
+					\FOR{$j=1$ to $V$ ($j \neq i$)}
 					\STATE	set $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$
@@
 					\mbox{MB}_G(\boldsymbol{\lambda}_{ie})$
-			\STATE		set $\mu_{ie} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{ie})$
-			\STATE		draw $\tau_{ie} \sim f_\tau(\mu_{ie}, V(\mu))$
+					\STATE		set $\mu_{ie} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{z}_{ie})$
+					\STATE		draw $\tau_{ie} \sim f_\tau(\mu_{ie}, \sigma_\tau^2)$
 					\ENDFOR
@@
 			\end{algorithm}
+	\begin{equation}
+		\begin{aligned}
+			s_e &= \mbox{argmin}_{i}(\tau_{ie}),\\
+			\boldsymbol{r}_e &= \boldsymbol{u}_{s_e e},\\
+			t_e &=t_{e-1} + \tau_{s_e e}.
+		\end{aligned}
+	\end{equation}
 		Therefore, the HEM assumes a sender-driven process---i.e., the receivers and timestamp of an event are jointly determined by the sender's urgency to direct the event to those selected receivers---which is similar to \cite{snijders1996stochastic} in that each actor gets his/her own rate function to determine ``who will make the next change in network." Note that our generative process allows for tied events.
@@
 	\section{Posterior inference}\label{sec:inference}
-	In this section we describe how we invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_e\}_{e=1}^E$, coefficients for receiver selection features $\boldsymbol{b}$, and coefficients for event timing features $\boldsymbol{\eta}$---conditioned on the observed data $\{(s_e, \boldsymbol{r}_e, t_e)\}_{e=1}^E$, covariates $\{(\boldsymbol{x}_e, \boldsymbol{y}_e)\}_{e=1}^E$, and hyperparameters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
+	In this section we describe how we invert the generative process to obtain the posterior distribution over the latent variables---candidate receivers $\{\boldsymbol{u}_e\}_{e=1}^E$, coefficients for receiver selection features $\boldsymbol{b}$, and coefficients for event timing features $\boldsymbol{\eta}$---conditioned on the observed data $\{(s_e, \boldsymbol{r}_e, t_e)\}_{e=1}^E$, covariates $\{(\boldsymbol{x}_e, \boldsymbol{z}_e)\}_{e=1}^E$, and hyperparameters $(\boldsymbol{\mu}_b, \Sigma_b, \boldsymbol{\mu}_\eta, \Sigma_\eta)$.
 We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each latent variable from its conditional posterior via a Metropolis-within-Gibbs sampling algorithm.
@@
 	\subsubsection{Candidate receivers}
-	In our model, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $\Pr(\boldsymbol{b}|\,\boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ and $\Pr(\boldsymbol{\eta}|\,\boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
+	In our model, direct computation of the posterior densities for the latent variables $\boldsymbol{b}$ and $\boldsymbol{\eta}$---i.e., $\Pr(\boldsymbol{b}|\,\boldsymbol{x},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ and $\Pr(\boldsymbol{\eta}|\,\boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$---is not possible.
 However, it is possible to augment the data by candidate receivers $\boldsymbol{u}$ such that we can obtain their conditional posterior by conditioning on samples of $\boldsymbol{u}$.
-%from $P(\boldsymbol{b}, \boldsymbol{u}|\,\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}|\, \boldsymbol{y},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$.
+%from $P(\boldsymbol{b}, \boldsymbol{u}|\,\boldsymbol{x},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$ and $P(\boldsymbol{\eta}, \boldsymbol{u}|\, \boldsymbol{z},\boldsymbol{a}, \boldsymbol{r},\boldsymbol{t})$.
 	This approach---i.e., ``data augmentation"---is commonly used throughout Bayesian statistics \citep{tanner1987calculation,neal2015exact}.
@@
 		\Pr(\boldsymbol{b}| \,\boldsymbol{u}, \boldsymbol{x}, \boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{e=1}^E
-		\prod_{i=1}^A \frac{1}{Z(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0)\big) + \sum\limits_{j \neq i} \lambda_{iej}u_{iej}\Big).
+		\prod_{i=1}^V \frac{1}{C(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0)\big) + \sum\limits_{j \neq i} \lambda_{iej}u_{iej}\Big).
 		\label{eqn:latentedge}
@@
 	\begin{equation}
-		\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{e=1}^E\Big(f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, V(\mu)) \big)\Big),
+		\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{e=1}^E\Big(f_{\tau}(\tau_{e}; \mu_{s_e e}, \sigma_\tau^2)\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2) \big)\Big),
 		\label{eqn:latenttime}
 	\end{equation}
-	where $f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))$ is the probability that the $e^{\textrm{th}}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{s_e e}$, and $\prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie},V(\mu)) \big)$ is the probability that the rest of (unobserved) senders for event $e$ all draw time increments greater than $\tau_e$.
+	where $f_{\tau}(\tau_{e}; \mu_{s_e e}, \sigma_\tau^2)$ is the probability that the $e^{\textrm{th}}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{s_e e}$, and $\prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie},\sigma_\tau^2) \big)$ is the probability that the rest of (unobserved) senders for event $e$ all draw time increments greater than $\tau_e$.
 Moreover, under the existence of tied events, the conditional posterior of $\boldsymbol{\eta}$ is written as proportional to
@@
 		\begin{aligned}
-			\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{e:t_e=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{s_e e}, V(\mu)) \\&\times \prod_{i \notin \{s_e\}_{e:t_e=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{ie}, V(\mu)) \big)\Big),
+			\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{e:t_e=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{s_e e}, \sigma_\tau^2) \\&\times \prod_{i \notin \{s_e\}_{e:t_e=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{ie}, \sigma_\tau^2) \big)\Big),
 		\end{aligned}
@@
 If $M=E$ (i.e., no tied events), equation (\ref{eqn:latenttime2}) reduces to equation (\ref{eqn:latenttime}).
-Note that when we have the latent variable to quantify the variance in time increments $V(\mu)$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional MH update---e.g., $\Pr(k|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \,\boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{y},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for log-normal.~\looseness=-1
+Note that when we have the latent variable to quantify the variance in time increments $\sigma_\tau^2$ (based on the choice of timestamp distribution in Section \ref{subsec:Time}), we also use equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2}) in case there exist tied events) for the additional MH update---e.g., $\Pr(k|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for Weibull, $\Pr(\theta|\, \boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for gamma, and  $\Pr(\sigma^2_\tau| \,\boldsymbol{\eta},\boldsymbol{u}, \boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})$ for log-normal.~\looseness=-1
 		\begin{algorithm}[!t]
@@
 				\FOR{$e=1$ to $E$}
-				\FOR{$i = 1$ to $A$}
-				\FOR{$j = 1$ to $A$ ($j \neq i$)}
+				\FOR{$i = 1$ to $V$}
+				\FOR{$j = 1$ to $V$ ($j \neq i$)}
 				\STATE update $u_{iej}$ using Gibbs update ---equation (\ref{eqn:latentreceiver})
@@
 				\ENDFOR
-				\IF {extra parameter for $V(\mu)$} 
+				\IF {extra parameter for $\sigma_\tau^2$}
 				\STATE update the variance parameter using MH algorithm---equation (\ref{eqn:latenttime}) or (\ref{eqn:latenttime2}) 
@@
 For this case study,
-	we formulate our model specification through definitions of the receiver selection features $\boldsymbol{x}$ and event timing features $\boldsymbol{y}$.
+	we formulate our model specification through definitions of the receiver selection features $\boldsymbol{x}$ and event timing features $\boldsymbol{z}$.
 We then report a suite of experiments---out-of-sample prediction for model selection and posterior predictive checks---that illustrate how alternative formulations of the HEM can be compared, and evaluate how well our model recovers the distribution of the observed data.
@@
 Specifically, our time interval tracks 7 days prior to the last email was sent $l_e= (t_{e-1}-7\mbox{ days}, t_{e-1}]$.
-For $i \in [A], j\in [A]$, and $e \in [E]$, we define 14 covariates for $\boldsymbol{x}_{iej}$:
+For $i \in [V], j\in [V]$, and $e \in [E]$, we define 14 covariates for $\boldsymbol{x}_{iej}$:
 	\begin{itemize}
@@
 		\item[6.] $\mbox{indegree}(r)$: ${x}_{iej6}=\sum_{d^\prime: t_{e^\prime} \in l_e} I(u_{e^\prime j} = 1)$;
-		\item[7.] $\mbox{hyperedge}\_\,\mbox{size}(i)$: ${x}_{iej7}=\sum_{e^\prime: t_{e^\prime} \in l_e} \sum_{j=1}^A I(s_{e^\prime} = i)\,I(u_{e^\prime j} = 1)$;
+		\item[7.] $\mbox{hyperedge}\_\,\mbox{size}(i)$: ${x}_{iej7}=\sum_{e^\prime: t_{e^\prime} \in l_e} \sum_{j=1}^V I(s_{e^\prime} = i)\,I(u_{e^\prime j} = 1)$;
 		\item[8.] $\mbox{interaction}(i)$: ${x}_{iej8} = {x}_{iej5}\times{x}_{iej7};$
@@
 	\subsubsection{Event timing features}
-For the event timing features $\boldsymbol{y}$, introduced in Section \ref{subsec:Time}, we identify a set of covariates which may affect the time until the next event.
+For the event timing features $\boldsymbol{z}$, introduced in Section \ref{subsec:Time}, we identify a set of covariates which may affect the time until the next event.
 Similar to the receiver selection features, we include nodal statistics which are time-invariant (such as gender or manager status) or time-dependent (such as the network statistics used for $\boldsymbol{x}$).
@@
 	\begin{itemize}
-		\item[1.] intercept: ${y}_{ie1} =1$;
-		\item[2.] $\mbox{gender}(i)$: ${y}_{ie2}=I(\mbox{gender of sender }i= \mbox{female})$;
-		\item[3.] $\mbox{manager}(i)$: ${y}_{ie3}=I(\mbox{sender }i \mbox{ is the County Manager})$;
-		\item[4.] $\mbox{outdegree}(i)$: ${y}_{ie4} =\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)$;
-		\item[5.] $\mbox{indegree}(i)$: ${y}_{ie5}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(u_{e^\prime i} = 1)$;
-		\item[6.] $\mbox{weekend}(e)$: ${y}_{ie6} = I(t_{e-1} \mbox{ is during the } \mbox{weekend})$;
-		\item[7.] $\mbox{PM}(e)$: ${y}_{ie7}= I(t_{e-1} \mbox{ in } \mbox{PM})$.
+		\item[1.] intercept: ${z}_{ie1} =1$;
+		\item[2.] $\mbox{gender}(i)$: ${z}_{ie2}=I(\mbox{gender of sender }i= \mbox{female})$;
+		\item[3.] $\mbox{manager}(i)$: ${z}_{ie3}=I(\mbox{sender }i \mbox{ is the County Manager})$;
+		\item[4.] $\mbox{outdegree}(i)$: ${z}_{ie4} =\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)$;
+		\item[5.] $\mbox{indegree}(i)$: ${z}_{ie5}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(u_{e^\prime i} = 1)$;
+		\item[6.] $\mbox{weekend}(e)$: ${z}_{ie6} = I(t_{e-1} \mbox{ is during the } \mbox{weekend})$;
+		\item[7.] $\mbox{PM}(e)$: ${z}_{ie7}= I(t_{e-1} \mbox{ in } \mbox{PM})$.
 	\end{itemize}
@@
 
-	The HEM defines a flexible family of models, each of which is defined by a set of features (i.e., the receiver selection features $\boldsymbol{x}$, the selection of event timing features $\boldsymbol{y}$, and the distribution of time increments $f$).
+	The HEM defines a flexible family of models, each of which is defined by a set of features (i.e., the receiver selection features $\boldsymbol{x}$, the selection of event timing features $\boldsymbol{z}$, and the distribution of time increments $f$).
 Many of these components will be specified based on user expertise (e.g., regarding which features would drive receiver selection), but some decisions may require a data-driven approach to model specification.
@@
 			\STATE draw test senders (out of $E$ senders) 
-			\STATE draw test receivers (out of $E\times (A-1)$ receiver indicators $\{\{\boldsymbol{r}_{ej}\}_{j\in [A]_{\backslash s_e}}\}_{e=1}^E$)
+			\STATE draw test receivers (out of $E\times (V-1)$ receiver indicators $\{\{\boldsymbol{r}_{ej}\}_{j\in [V]_{\backslash s_e}}\}_{e=1}^E$)
 			\STATE draw test timestamps  (out of $E$ timestamps) 
@@
 			\IF{$s_e=$  NA}
-			\STATE compute $\boldsymbol{\pi}_e$, where $\pi_{ei}=f_{\tau}(\tau_{e}; \mu_{ie}, V(\mu))\times \prod_{i^\prime\neq i}\big(1-F_{\tau}(\tau_{e}; \mu_{i^\prime e}, V(\mu)) \big)$
+			\STATE compute $\boldsymbol{\pi}_e$, where $\pi_{ei}=f_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2)\times \prod_{i^\prime\neq i}\big(1-F_{\tau}(\tau_{e}; \mu_{i^\prime e}, \sigma_\tau^2) \big)$
 			\STATE draw $s_e \sim \mbox{Categorical}(\boldsymbol{\pi}_e)$ 
 			\ENDIF
-			\FOR{$j\in [A]_{\backslash s_e}$}
+			\FOR{$j\in [V]_{\backslash s_e}$}
 			\IF{$r_{ej}=$ NA}
@@
 			\STATE draw ${\tau}_e$ from its conditional distribution using importance sampling, %from equation (\ref{eqn:latenttime}) (without the product term) 
-	      where $P({\tau}_e|\, \cdot)\propto f_{\tau}(\tau_{e}; \mu_{s_e e}, V(\mu))\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, V(\mu)) \big)$%\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
+	      where $P({\tau}_e|\, \cdot)\propto f_{\tau}(\tau_{e}; \mu_{s_e e}, \sigma_\tau^2)\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2) \big)$%\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
 			\ENDIF
@@
 We call this measure the ``correct sender posterior probability." In Figure \ref{subfigure:PPEresults1}, we display boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{es_{e}} = \frac{1}{N}\sum_{n=1}^N \pi^{(n)}_{es_{e}}$---across the missing emails.
-The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $A$ possible senders $=1/18$), with the log-normal model showing better performance than the exponential model.
+The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $V$ possible senders $=1/18$), with the log-normal model showing better performance than the exponential model.
 Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $e$ and $j$ with $r_{ej}$=NA) by taking the harmonic mean of precision and recall:
@@
 		\caption {Comparison of predictive performance between log-normal and exponential distributions: (a) correct sender posterior probability from sender predictions, (b) $F_1$ scores from receiver predictions, and (c) median absolute relative error from timestamp predictions.
-Blue line in (a) represents the correct sender probability expected by random guess---i.e., $1/A=1/18\approx0.056$.}
+Blue line in (a) represents the correct sender probability expected by random guess---i.e., $1/V=1/18\approx0.056$.}
 		\label{figure:PPEresults}
@@
 		\begin{algorithmic}
-			\STATE \textbf{Input}: number of data to generate $D$, covariates $(\boldsymbol{x},\boldsymbol{y})$, and estimated values of $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta})$\\
+			\STATE \textbf{Input}: number of data to generate $D$, covariates $(\boldsymbol{x},\boldsymbol{z})$, and estimated values of $(\boldsymbol{u}, \boldsymbol{b}, \boldsymbol{\eta})$\\
 			\vskip 0.1in
@@
 			&\log(\tau_{ie}) \sim N(\mu_{ie}, \sigma_\tau^2), \mbox{ with }\\
-			&\mu_{ie} = \eta_{1}+\eta_{2} y_{ie2}+\ldots+\eta_{7}y_{ie7}.
+			&\mu_{ie} = \eta_{1}+\eta_{2} z_{ie2}+\ldots+\eta_{7}z_{ie7}.
 		\end{aligned}
@@
 		\begin{algorithmic}
-			\STATE \textbf{Input}: number of events and nodes $(E, A)$, covariates $(\boldsymbol{x}, \boldsymbol{y})$, and coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
+			\STATE \textbf{Input}: number of events and nodes $(E, V)$, covariates $(\boldsymbol{x}, \boldsymbol{z})$, and coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
 			\vskip 0.1in				
 			\FOR{$e=1$ to $E$}
-			\FOR{$j=1$ to $A$}
-			\FOR{$i=1$ to $A$ ($i \neq j$)}
+			\FOR{$j=1$ to $V$}
+			\FOR{$i=1$ to $V$ ($i \neq j$)}
 			\STATE	set $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$
@@
 			\mbox{MB}_G(\boldsymbol{\lambda}_{je})$
-			\STATE		set $\mu_{je} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{y}_{je})$
-			\STATE		draw $\tau_{je} \sim f_\tau(\mu_{je}, V(\mu))$
+			\STATE		set $\mu_{je} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{z}_{je})$
+			\STATE		draw $\tau_{je} \sim f_\tau(\mu_{je}, \sigma_\tau^2)$
 			\ENDFOR
@@
 		\begin{aligned}
-			& \Pr(\boldsymbol{u}_{ie}|\,\boldsymbol{b}, \boldsymbol{x}_{ie}) = \frac{1}{Z(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ie} \rVert_1 > 0)\big) + \sum_{j \neq i} \lambda_{iej}u_{iej} \Big),
+			& \Pr(\boldsymbol{u}_{ie}|\,\boldsymbol{b}, \boldsymbol{x}_{ie}) = \frac{1}{C(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ie} \rVert_1 > 0)\big) + \sum_{j \neq i} \lambda_{iej}u_{iej} \Big),
 		\end{aligned}
@@
 
-	To use this distribution efficiently, we derive a closed-form expression for $Z(\boldsymbol{\lambda}_{ie})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ie}$ (i.e., $\forall \boldsymbol{u}_{ie} \in [0,1]^A$).
+	To use this distribution efficiently, we derive a closed-form expression for $C(\boldsymbol{\lambda}_{ie})$ that does not require brute-force summation over the support of $\boldsymbol{u}_{ie}$ (i.e., $\forall \boldsymbol{u}_{ie} \in [0,1]^V$).
 We recognize that if $\boldsymbol{u}_{ie}$ were drawn via independent Bernoulli distributions in which $\Pr({u}_{iej}=1|\,\boldsymbol{b}, \boldsymbol{x}_{ie})$ was given by logit$(\lambda_{iej})$, then
@@
 		where the subscript ``$\backslash j$'' denotes a quantity excluding data from position $j$.
-Now we denote the logistic-Bernoulli normalizing constant as $Z^{l}(\boldsymbol{\lambda}_{ie})$, which is defined as
+Now we denote the logistic-Bernoulli normalizing constant as $C^{l}(\boldsymbol{\lambda}_{ie})$, which is defined as
 		\begin{equation*}
-			Z^{l}( \boldsymbol{\lambda}_{ie})=\sum_{\boldsymbol{u}_{ie} \in [0,1]^{A}} \exp\Big(\sum_{j\neq i} \lambda_{iej}u_{iej}\Big).
+			C^{l}( \boldsymbol{\lambda}_{ie})=\sum_{\boldsymbol{u}_{ie} \in [0,1]^{V}} \exp\Big(\sum_{j\neq i} \lambda_{iej}u_{iej}\Big).
 		\end{equation*}
@@
 			\begin{aligned}
-				Z(\boldsymbol{\lambda}_{ie})& = Z^{l}(\boldsymbol{\lambda}_{ie}) -\exp\Big( \sum\limits_{\forall u_{iej}=0}\lambda_{iej}u_{iej} \Big)
-				\\& = Z^{l}(\boldsymbol{\lambda}_{ie}) -  1.
+				C(\boldsymbol{\lambda}_{ie})& = C^{l}(\boldsymbol{\lambda}_{ie}) -\exp\Big( \sum\limits_{\forall u_{iej}=0}\lambda_{iej}u_{iej} \Big)
+				\\& = C^{l}(\boldsymbol{\lambda}_{ie}) -  1.
 			\end{aligned}
 		\end{equation*}
-		We can therefore derive a closed form expression for $Z(\boldsymbol{\lambda}_{ie})$ via a closed form expression for $Z^{l}(\boldsymbol{\lambda}_{ie})$.
+		We can therefore derive a closed form expression for $C(\boldsymbol{\lambda}_{ie})$ via a closed form expression for $C^{l}(\boldsymbol{\lambda}_{ie})$.
 This can be done by looking at the probability of the zero vector under the logistic-Bernoulli model:
@@
 			\begin{aligned}
-				&\frac{1}{Z^{l}(\boldsymbol{\lambda}_{ie})}\exp\Big(\sum\limits_{\forall u_{iej}=0}\lambda_{iej}u_{iej} \Big)= \prod_{j \neq i}   \Big(1-\frac{ \exp{(\lambda_{iej})}}{\exp{(\lambda_{iej})} + 1}\Big).
+				&\frac{1}{C^{l}(\boldsymbol{\lambda}_{ie})}\exp\Big(\sum\limits_{\forall u_{iej}=0}\lambda_{iej}u_{iej} \Big)= \prod_{j \neq i}   \Big(1-\frac{ \exp{(\lambda_{iej})}}{\exp{(\lambda_{iej})} + 1}\Big).
 			\end{aligned}  
@@
 			\begin{aligned}
-				& \frac{1}{Z^{l}(\boldsymbol{\lambda}_{ie})} &= \prod\limits_{j \neq i}\frac{1}{ \exp(\lambda_{iej})+ 1}.
+				& \frac{1}{C^{l}(\boldsymbol{\lambda}_{ie})} &= \prod\limits_{j \neq i}\frac{1}{ \exp(\lambda_{iej})+ 1}.
 			\end{aligned}  
@@
 		\begin{equation*}
-			\begin{aligned}Z(\boldsymbol{\lambda}_{ie}) = \prod_{j \neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1.
+			\begin{aligned}C(\boldsymbol{\lambda}_{ie}) = \prod_{j \neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1.
 			\end{aligned}  
@@
 
-	To keep the computational burden of repeated inference manageable, we run the GiR using a relatively small artificial sample, consisting of $E=100$ events, $A=5$ nodes, $P=4$ number of receiver selection features, and $Q=3$ number of event timing features per each forward or backward sampler, using log-normal distibution for the time increments $f_\tau$.
+	To keep the computational burden of repeated inference manageable, we run the GiR using a relatively small artificial sample, consisting of $E=100$ events, $V=5$ nodes, $P=4$ number of receiver selection features, and $Q=3$ number of event timing features per each forward or backward sampler, using log-normal distibution for the time increments $f_\tau$.
 We generated $10^5$ sets of forward and backward samples, and then calculated 1,000 quantiles for each of the statistics.

### 2018-10-06 paper/revision1/ba-sample.tex
adding lit discussion

@@
 	We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern hyperedge event formation: (1) the formation of the vertices that are incident to the hyperedge, and (2) the timing of the hyperedge event.
+Though the HEM, based on our knowledge of the literature, is unique in modeling hyperedge events in continuous time, we build our model using features inspired by many of the existing models for dynamic network data.
+First, the features that govern which receivers are selected by a given sender are defined using subgraph configuration counts (e.g., the number of triangles formed through sending the tie, the number of previous hyperedges that would be reciprocated by the tie).
+The HEM's use of subgraph configuration formation follows very similar aspects of the continuous-time event model proposed by \cite{PerryWolfe2012}, [HERE]
+
 In what follows, we define the HEM's generative process for hyperedge event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference, and present tests of our software implementation (Section \ref{sec:inference}).

### 2018-10-31 paper/revision1/ba-sample.tex
added subsection discussing HEM in the context of existing models

@@
 	We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern hyperedge event formation: (1) the formation of the vertices that are incident to the hyperedge, and (2) the timing of the hyperedge event.
-Though the HEM, based on our knowledge of the literature, is unique in modeling hyperedge events in continuous time, we build our model using features inspired by many of the existing models for dynamic network data.
-First, the features that govern which receivers are selected by a given sender are defined using subgraph configuration counts (e.g., the number of triangles formed through sending the tie, the number of previous hyperedges that would be reciprocated by the tie).
-The HEM's use of subgraph configuration formation follows very similar aspects of the continuous-time event model proposed by \cite{PerryWolfe2012}, [HERE]
-
 In what follows, we define the HEM's generative process for hyperedge event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference, and present tests of our software implementation (Section \ref{sec:inference}).
@@
 In the case of tied events---i.e., multiple senders draw exactly the same candidate timestamps---we assume that all events are generated and occur simultaneously.
-Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers.~\looseness=-1
+Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers.
+~\looseness=-1
+
+\subsection{Basis in existing models}
+
+Though the HEM, based on our knowledge of the literature, is unique in modeling hyperedge events in continuous time, we build our model using features inspired by many of the existing models for dynamic network data.
+First, the features that govern which receivers are selected by a given sender are defined using subgraph configuration counts (e.g., the number of triangles formed through sending the tie, the number of previous hyperedges that would be reciprocated by the tie).
+The HEM's use of subgraph configuration formation follows a similar process underlying network change in the the continuous-time event model proposed by \cite{PerryWolfe2012} as well as the relational event model \citep{Butts2008}, and is also related to the subgraph completion processes used to model discrete-time network change in the temporal ERGM \citep{hanneke2010discrete}.
+Second, the use of candidate receivers as a mechanism through which continuous network change is modeled is related to the use of latent changes between snapshot network observations in the stochastic actor oriented model (SAOM) by \cite{snijders1996stochastic}.
+Third, also like the SAOM, the HEM includes separate sets of parameters that are used to model event timing and edge generation.
+Though unique in modeling hyperedges, the HEM is grounded in existing continuous-time models of networks, ERGM-style models, and the SAOM.
+
+The models discussed above are those, like HEM,  in which edge formation is driven by subgraph structure.
+There is another class of network models, originating with the latent space model introduced by \cite{hoff2002}, in which tie formation is modeled by embedding nodes in a space of latent attributes.
+Under this modeling framework, each node is attributed with a coordinate in a metric space, and the likelihood of a tie between two nodes is inversely related to the distance between the two nodes in the metric space.
+The latent space model has seen several extensions, the latest of which tis the latent factor model proposed by \cite{minhas2016inferential}.
+A number of dynamic extensions of the latent space framework have been developed \citep[e.g., ][]{sarkar2005dynamic,sewell2015latent,ward2013gravity}.
+The HEM, as we have presented it, does not involve latent node attributes, but in future work the HEM could be extended to incorporate latent node features---resulting in a latent space model for dynamic hyperedges.
 

### 2018-11-01 paper/revision1/ba-sample.tex
adding SBM

@@
 A number of dynamic extensions of the latent space framework have been developed \citep[e.g., ][]{sarkar2005dynamic,sewell2015latent,ward2013gravity}.
-The HEM, as we have presented it, does not involve latent node attributes, but in future work the HEM could be extended to incorporate latent node features---resulting in a latent space model for dynamic hyperedges.
+Another popular form of latent variable model for networks is the stochastic block model (SBM) \citep{holland1983stochastic,airoldi2008mixed}.
+In the SBM, each vertex is associated with one or more blocks, and each block is attributed with a vector of parameters that determines the rate at which members of the respective block form ties with members of each block.
+The blocks reduce vertex-to-vertex tie probabilities to block-to-block tie probabilities.
+Like the latent space model, the SBM has been extended to model discrete-time longitudinal networks  \citep{matias2017statistical}.
+The HEM, as we have presented it, does not involve latent node attributes, but in future work the HEM could be extended to incorporate latent node features---resulting in a latent space model and/or SBM for dynamic hyperedges.
 

### 2018-11-11 paper/revision1/HEM-reply.tex
added subsection discussing HEM in the context of existing models
adding SBM
notations and general writing issues addressed

@@
 	\begin{itemize}
-		\item Unusual notations such as actor $A$ and covariates $y$. Also $u_{ie}$ is the $i$th line of matrix $u_e$, while $\tau_e = min_i(\tau_{ie})$. \textcolor{red}{(discuss)} 
+		\item Unusual notations such as actor $A$ and covariates $y$. Also $u_{ie}$ is the $i$th line of matrix $u_e$, while $\tau_e = min_i(\tau_{ie})$.  \textcolor{blue}{(done)}
 		\item Change the order of Equation (2.2) and (2.1) and not use `intensity'. \textcolor{blue}{(done)}
@@
 	\begin{itemize}
-		\item Perry and Wolfe (2013) arxiv version has a model for multicast. Any differences/advantages?
+		\item Perry and Wolfe (2013) arxiv version has a model for multicast. Any differences/advantages? \textcolor{blue}{(done)}
 		\item Why cite Snijders (1996) in 2.3? Be specific. \textcolor{blue}{(done)}
@@
 
-\textbf{  Response:} 
+\textbf{  Response:}  We added a subsection following the description of the HEM in which we ground it in the structure of existing models for networks. 
 \begin{itemize}
@@
 \begin{itemize}
-	\item Use weakly informative priors as generic priors instead of assuming $N(0, \infty)$
+	\item Use weakly informative priors as generic priors instead of assuming $N(0, \infty)$  \textcolor{blue}{(done)}
 	\item Sensitivity analyses to check how much posterior inference is affected by the hyperparameters' settings, and, possibly, suggest some default values.  \textcolor{red}{(discuss)} 
@@
 	\item Compare with SAOMs and extensions in PPE and PPC 
-	\item Bad results in predicting timestamps (MdAPE)
-	\item More conservative interpretations 
+	\item Bad results in predicting timestamps (MdAPE)  \textcolor{blue}{(done)}
+	\item More conservative interpretations \textcolor{blue}{(done)}
 \end{itemize}

### 2018-11-11 paper/revision1/ba-sample.tex
notations and general writing issues addressed

@@
 	The hyperedge event model (HEM) specifies a generative process for $E$ unique hyperedge events that occur between $V$ number of nodes.
-A single hyperedge event is indexed by $e \in [E]$---where $[E]$ denotes a categorical set with $E$ levels $[E] = \{1,\ldots,E\}$---and consists of three components: the sender $s_e \in [V]$, an indicator vector of receivers $\boldsymbol{r}_e$---where $r_{ej}=1$ if $j \in [V]$ is a receiver of hyperedge event $e$ and 0 otherwise---and the timestamp $t_e \in (0, \infty)$.
+A single hyperedge event is indexed by $e \in [E]$---where $[E]$ denotes a categorical set with $E$ levels $[E] = \{1,\ldots,E\}$---and consists of three components: the sender $s_e \in [V]$, an indicator vector of receivers $\boldsymbol{r}_e$---where the element 1 indicates ``receiving" the hyperedge event $e$ and 0 otherwise---and the timestamp $t_e \in (0, \infty)$.
 For simplicity, we assume that events are ordered by time such that $t_e \leq t_{e+1}$.
@@
 Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $V=5$.
-For hyperedge events that involve one receiver and one or more senders, we treat $s_e$ to be an indicator vector of senders $\boldsymbol{s}_e$ and $r_e$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).~\looseness=-1
+For hyperedge events that involve one receiver and one or more senders, we treat $s_e$ to be an indicator vector of senders $\boldsymbol{s}_e$ and $r_e$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers).
+Throughout the paper, we use the notation $y_{iej}$ to imply ``sender $i$ directs an event $e$ to receiver $j$," where $y$ can be any parameter or covariate introduced in the HEM.
+When it is relevant to sender or receiver only, we use $y_{ie}$ and $y_{ej}$ to imply ``sender $i$ of an event $e$" and ``receiver $j$ of event $e$," respectively.
+~\looseness=-1
 			\begin{figure}[!t]
@@
 	Our model thus assumes that for every event $e$, every possible sender $i$ generates a candidate receiver set that would be the receiver set of event $e$ if sender $i$ were the sender.
-For an event $e$, we first define an $V\times V$ matrix $\boldsymbol{u}_e$ where the $i^{\textrm{th}}$ row denotes sender $i$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $i$ intends to direct event $e$.
+While \cite{PerryWolfe2012} limits the possible receiver sets as combinations of nodes with the same cardinality as the observed receiver set, we take more realistic approach and allow all possible combination of nodes (except the no receiver case) to be considered.
+For an event $e$, we first define a series of vectors $\boldsymbol{u}_{ie}$ for $i = 1,\ldots, V$, where $\boldsymbol{u}_{ie}$ denotes sender $i$'s receiver vector of zeros and 1's---i.e., 1's indicate the nodes to which $i$ intends to direct event $e$.
 We then assume that each receiver vector $\boldsymbol{u}_{ie}$ comes from a modification of the multivariate Bernoulli (MB) distribution \citep{dai2013multivariate}---a model that has been used to model graphs in which the state of each edge indicator is drawn independently from an edge-specific Bernoulli distribution.
@@
 As a result, this measure helps us to (1) allow a sender to select multiple receivers for a single event, (2) force the sender to select at least one receiver, and (3) ensure a tractable normalizing constant for the receiver selection distribution.
-To be specific, we draw a binary vector $\boldsymbol{u}_{ie}= (u_{ie1},
-	\ldots, u_{ieV})$ for $i$th row of matrix $\boldsymbol{u}$ using
-	\begin{equation} \boldsymbol{u}_{ie}  \sim
-		\mbox{MB}_{G}(\boldsymbol{\lambda}_{ie}),
-	\end{equation}
-	where $\boldsymbol{\lambda}_{ie}= (\lambda_{ie1},
-	\ldots, \lambda_{ieV})$ and $\lambda_{iej}$ is the linear combination of statistics relevant to the receiver selection process for every possible sender--receiver pair $(i,j)$ where $i \!\neq\!
-j$.
-In other words, we define
-	\begin{equation}
-	\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej},
-	\end{equation}
-	where $\boldsymbol{b}$ is a $P$-dimensional vector of coefficients and $\boldsymbol{x}_{iej}$ is a set of receiver selection features.
-As we show below, $\lambda_{iej}$ contributes to the probability that $i$ directs event $e$ towards receiver $j$.
-The features $\boldsymbol{x}_{iej}$ can capture common network processes like popularity, reciprocity, and transitivity, as well as the effects of attributes of the sender and receivers (e.g., their gender), or attributes of sender--receiver pairs (e.g., whether the sender is a supervisor of the receiver's).
-We also include a normally distributed intercept term to account for the average (or baseline) number of receivers: $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$.
-~\looseness=-1
-
-	In particular, we define $\mbox{MB}_{G}(\boldsymbol{\lambda}_{ie})$ as
+To summarize, for each node $i \in [V]$ we draw a binary vector $\boldsymbol{u}_{ie}= (u_{ie1},
+	\ldots, u_{ieV})$ using $\boldsymbol{u}_{ie}  \sim \mbox{MB}_{G}(\boldsymbol{\lambda}_{ie})$ which we define as
 	\begin{equation}
@@
 	\end{equation}
-	where $C(\boldsymbol{\lambda}_{ie})$ is the normalizing constant, $\lVert \cdot \rVert_1$ is the $\ell_1$-norm, and the log-indicator term $\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0 )\big)$ ensures that empty receiver sets are excluded from the distribution's support.
+	where $C(\boldsymbol{\lambda}_{ie})$ is the normalizing constant with $\boldsymbol{\lambda}_{ie}= (\lambda_{ie1},
+	\ldots, \lambda_{ieV})$, $\lVert \cdot \rVert_1$ is the $\ell_1$-norm, and the log-indicator term $\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0 )\big)$ ensures that empty receiver sets are excluded from the distribution's support.
 These modeling assumptions facilitate efficient posterior inference since we can derive a closed form expression for the normalizing constant---i.e., $C(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$---and thus do not need to perform brute-force summation over the support of $\boldsymbol{u}_{ie} \in \{0,1\}^V$.
@@
 
-	% $C(\boldsymbol{\lambda}_{ie})= \prod_{j\neq i} \big(\mbox{exp}(\lambda_{iej}) + 1\big)-1$
+	Here, we assume that $\lambda_{iej}$ is the linear combination of statistics relevant to the receiver selection process for every possible sender--receiver pair $(i,j)$ where $i \!\neq\!
+j$.
+In other words, we define
+	\begin{equation}
+	\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej},
+	\end{equation}
+	where $\boldsymbol{b}$ is a $P$-dimensional vector of coefficients with a Normal prior $\boldsymbol{b} \sim N(\boldsymbol{\mu}_b, \Sigma_b)$, and $\boldsymbol{x}_{iej}$ is a set of receiver selection features.
+As we show below, $\lambda_{iej}$ contributes to the probability that $i$ directs event $e$ towards receiver $j$.
+The features $\boldsymbol{x}_{iej}$ can capture common network processes like popularity, reciprocity, and transitivity, as well as the effects of attributes of the sender and receivers (e.g., their gender), or attributes of sender--receiver pairs (e.g., whether the sender is a supervisor of the receiver's).
+Moreover, we allow the covariates could depend on the observed interaction data (e.g., how many times $i$ and $j$ interacted in the last 7 days), thus in such case the observed events are not conditionally independent given the model parameters.
+~\looseness=-1
 
@@
 	\end{equation}
-	where $\boldsymbol{\eta}$ is a $Q$-dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{z}_{ad}$ is a set of event timing features---covariates that could affect timestamps of events, and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
+	where $\boldsymbol{\eta}$ is a $Q$-dimensional vector of coefficients with a Normal prior $\boldsymbol{\eta} \sim N(\boldsymbol{\mu}_\eta,\Sigma_\eta)$, $\boldsymbol{z}_{ie}$ is a set of event timing features or covariates that could affect timestamps of events (including those depending on the observed interactions), and $g(\cdot)$ is the appropriate link function such as identity, log, or inverse.
 Possible choices of distribution include exponential, Weibull, gamma, and log-normal distributions, which are commonly used in time-to-event modeling \citep{rao2000applied,rizopoulos2012joint}.
@@
 		After the HEM draws the candidate timestamp vector $\boldsymbol{\tau}_e=\{\tau_{1e},\ldots,\tau_{Ve}\}$ at which the event would be created given the candidate sender and receiver combinations, finally our model assumes that the observed sender, receivers, and timestamp of hyperedge event $e$ are generated by selecting the sender--receiver-set pair with the smallest time increment:
+	\begin{equation}
+		\begin{aligned}
+			s_e &= \mbox{argmin}_{i}(\tau_{ie}),\\
+			\boldsymbol{r}_e &= \boldsymbol{u}_{s_e e},\\
+			t_e &=t_{e-1} + \tau_{s_e e}.
+		\end{aligned}
+	\end{equation}
+		Therefore, the HEM assumes a sender-driven process---i.e., the receivers and timestamp of an event are jointly determined by the sender's urgency to direct the event to those selected receivers---which is similar to \cite{snijders1996stochastic} in that each actor gets his/her own rate function to determine ``who will make the next change in network." Note that our generative process allows for tied events.
+In the case of tied events---i.e., multiple senders draw exactly the same candidate timestamps---we assume that all events are generated and occur simultaneously.
+Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers.
+~\looseness=-1
 			\begin{algorithm}[!t]
@@
 			\end{algorithm}
-	\begin{equation}
-		\begin{aligned}
-			s_e &= \mbox{argmin}_{i}(\tau_{ie}),\\
-			\boldsymbol{r}_e &= \boldsymbol{u}_{s_e e},\\
-			t_e &=t_{e-1} + \tau_{s_e e}.
-		\end{aligned}
-	\end{equation}
-		Therefore, the HEM assumes a sender-driven process---i.e., the receivers and timestamp of an event are jointly determined by the sender's urgency to direct the event to those selected receivers---which is similar to \cite{snijders1996stochastic} in that each actor gets his/her own rate function to determine ``who will make the next change in network." Note that our generative process allows for tied events.
-In the case of tied events---i.e., multiple senders draw exactly the same candidate timestamps---we assume that all events are generated and occur simultaneously.
-Algorithm \ref{alg:generative} summarizes the entire generative process for hyperedge events with one sender and one or more receivers.
-~\looseness=-1
-
 \subsection{Basis in existing models}
@@
 We draw the samples using Markov chain Monte Carlo (MCMC) methods, repeatedly resampling the value of each latent variable from its conditional posterior via a Metropolis-within-Gibbs sampling algorithm.
-In the next subsection, we provide each latent variable's conditional posterior along with pseudocode of MCMC in Algorithm \ref{alg:MCMC}.
+In the next subsections, we provide each latent variable's conditional posterior along with pseudocode of MCMC in Algorithm \ref{alg:MCMC} and some discussion on the computational complexity of our algorithm.
 We also evaluate the correctness of both our mathematical derivations and software implemenation using the prior--posterior simulator test of \cite{geweke2004getting} in Appendix C.
 
-	%\subsection{Conditional posteriors}\label{subsec:conditionaldist}
+	\subsection{Conditional posteriors}\label{subsec:conditionaldist}
 	\subsubsection{Candidate receivers}
@@
 	\subsubsection{Coefficients for receiver selection features}
-	Unlike the candidate receivers above, the conditional posterior for $\boldsymbol{b}$ does not have a closed form; however $\boldsymbol{b}$ may instead be re-sampled using the Metropolis--Hastings (MH) algorithm using the proposal distribution $N(\boldsymbol{0}, \delta_b\times I_P)$, where $\delta_b$ is the proposal variance parameter for $\boldsymbol{b}$.
-Assuming an uninformative prior (i.e., $N(\boldsymbol{0},\infty)$), the conditional posterior for $\boldsymbol{b}$ is proportional to~\looseness=-1
+	Unlike the candidate receivers above, the conditional posterior density of $\boldsymbol{b}$ does not have a closed form; however $\boldsymbol{b}$ may instead be re-sampled using the Metropolis--Hastings (MH) algorithm.
+Assuming a generic Normal prior $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b, \Sigma_b)$, the conditional posterior distribution of $\boldsymbol{b}$ is proportional to~\looseness=-1
 	\begin{equation}
-		\Pr(\boldsymbol{b}| \,\boldsymbol{u}, \boldsymbol{x}, \boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{e=1}^E
-		\prod_{i=1}^V \frac{1}{C(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0)\big) + \sum\limits_{j \neq i} \lambda_{iej}u_{iej}\Big).
+		\Pr(\boldsymbol{b}| \,\boldsymbol{u}, \boldsymbol{x}, \boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \phi(\boldsymbol{b}; \boldsymbol{\mu}_b, \Sigma_b)\times \prod_{e=1}^E
+		\prod_{i=1}^V \frac{1}{C(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}( \lVert \boldsymbol{u}_{ie}\rVert_1 > 0)\big) + \sum\limits_{j \neq i} \lambda_{iej}u_{iej}\Big),
 		\label{eqn:latentedge}
 	\end{equation}
+	where $\phi(\boldsymbol{b}; \boldsymbol{\mu}_b, \Sigma_b)$ denotes the multivariate normal density of $\boldsymbol{b}$ with mean $\boldsymbol{\mu}_b$ and covariance matrix $\Sigma_b$.
+We re-sample the new value of $\boldsymbol{b}$ using the proposal distribution $\boldsymbol{b}^{new}\sim N(\boldsymbol{b}, \delta_b\times I_P)$, where $\delta_b$ is the proposal variance parameter for $\boldsymbol{b}$, and make the accept/reject decision based on the evaluation of conditional posterior above.
 	\subsubsection{Coefficients for event timing features}
-	Likewise, we use the MH algorithm to update the latent variable $\boldsymbol{\eta}$ using the proposal distribution $N(\boldsymbol{0}, \delta_\eta\times I_Q)$, where $\delta_\eta$ is the proposal variance parameter for $\boldsymbol{\eta}$.
-Assuming an uninformative prior $\boldsymbol{\eta}$ (i.e., $N(\boldsymbol{0},\infty)$), the conditional posterior for an untied event case is proportional to~\looseness=-1
+	Likewise, we use the MH algorithm to update the latent variable $\boldsymbol{\eta}$.
+Assuming a Normal prior $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta = \boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, the conditional posterior distribution of $\boldsymbol{\eta}$ for an untied event case is proportional to~\looseness=-1
 	\begin{equation}
-		\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \prod_{e=1}^E\Big(f_{\tau}(\tau_{e}; \mu_{s_e e}, \sigma_\tau^2)\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2) \big)\Big),
+		\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto  \phi(\boldsymbol{\eta}; \boldsymbol{\mu}_\eta, \Sigma_\eta)\times\prod_{e=1}^E\Big(f_{\tau}(\tau_{e}; \mu_{s_e e}, \sigma_\tau^2)\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2) \big)\Big),
 		\label{eqn:latenttime}
@@
 	where $f_{\tau}(\tau_{e}; \mu_{s_e e}, \sigma_\tau^2)$ is the probability that the $e^{\textrm{th}}$ observed time increment comes from the specified distribution $f_\tau(\cdot)$ with the observed sender's mean $\mu_{s_e e}$, and $\prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie},\sigma_\tau^2) \big)$ is the probability that the rest of (unobserved) senders for event $e$ all draw time increments greater than $\tau_e$.
-Moreover, under the existence of tied events, the conditional posterior of $\boldsymbol{\eta}$ is written as proportional to
+	Again, we re-sample the new value of $\boldsymbol{\eta}$ using the proposal distribution $\boldsymbol{\eta}^{new}\sim N(\boldsymbol{\eta}, \delta_\eta\times I_Q)$, where $\delta_\eta$ is the proposal variance parameter for $\boldsymbol{\eta}$.
+Moreover, under the existence of tied events, the conditional posterior distribution of $\boldsymbol{\eta}$ is written as proportional to
 	\begin{equation}
 		\begin{aligned}
-			\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})&\propto \prod_{m=1}^M\Big(\prod_{e:t_e=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{s_e e}, \sigma_\tau^2) \\&\times \prod_{i \notin \{s_e\}_{e:t_e=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{ie}, \sigma_\tau^2) \big)\Big),
+			&\Pr(\boldsymbol{\eta}|\, \boldsymbol{u}, \boldsymbol{z},\boldsymbol{s}, \boldsymbol{r},\boldsymbol{t})\propto \phi(\boldsymbol{\eta}; \boldsymbol{\mu}_\eta, \Sigma_\eta)\\&\times \prod_{m=1}^M\Big(\prod_{e:t_e=t_m^*}f_{\tau}(t_m^*-t_{m-1}^*; \mu_{s_e e}, \sigma_\tau^2) \times \prod_{i \notin \{s_e\}_{e:t_e=t_m^*}}\big(1-F_{\tau}(t_m^*-t_{m-1}^*; \mu_{ie}, \sigma_\tau^2) \big)\Big),
 		\end{aligned}
@@
 		\end{algorithm}
+	\subsection{Computational complexity}\label{subsec:computation}
 
@@
 This email application specifically gives rise to the following question: ``To what extent are nodal, dyadic or triadic network effects relevant to predicting future emails?" As an illustrative example, we form the receiver selection features $\boldsymbol{x}$ for Montgomery County email data using nodal, dyadic, and triadic covariates.
-First, as we want to test whether gender plays a role in receiver selection process, we include three nodal covariates---the gender information of sender and receiver, and their homophily indicator (i.e., an indicator of whether the sender and receiver are of the same gender).
+First, by default we include a normally distributed intercept term to account for the average (or baseline) number of receivers.
+Next, as we want to test whether gender plays a role in receiver selection process, we include three nodal covariates---the gender information of sender and receiver, and their homophily indicator (i.e., an indicator of whether the sender and receiver are of the same gender).
 Additionally, we include four interval-based nodal network covariates---outdegree of sender (i.e., the number of emails sent), indegree of receiver (i.e., the number of emails received), hyperedge size of sender (i.e., the number of total receivers directed from the sender), and the interaction between (i.e., scalar product of) outdegree and hyperedge size---to study the effect of nodal behaviors on future interactions.
@@
 		\item[5.] $\mbox{outdegree}(i)$: ${x}_{iej5} =\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)$;
-		\item[6.] $\mbox{indegree}(r)$: ${x}_{iej6}=\sum_{d^\prime: t_{e^\prime} \in l_e} I(u_{e^\prime j} = 1)$;
-		\item[7.] $\mbox{hyperedge}\_\,\mbox{size}(i)$: ${x}_{iej7}=\sum_{e^\prime: t_{e^\prime} \in l_e} \sum_{j=1}^V I(s_{e^\prime} = i)\,I(u_{e^\prime j} = 1)$;
+		\item[6.] $\mbox{indegree}(r)$: ${x}_{iej6}=\sum_{d^\prime: t_{e^\prime} \in l_e} I(r_{e^\prime j} = 1)$;
+		\item[7.] $\mbox{hyperedge}\_\,\mbox{size}(i)$: ${x}_{iej7}=\sum_{e^\prime: t_{e^\prime} \in l_e} \sum_{j=1}^V I(s_{e^\prime} = i)\,I(r_{e^\prime j} = 1)$;
 		\item[8.] $\mbox{interaction}(i)$: ${x}_{iej8} = {x}_{iej5}\times{x}_{iej7};$
-		\item[9.] $\mbox{send}(i, j)$: ${x}_{iej9}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)\,I(u_{e^\prime j} = 1)$;
+		\item[9.] $\mbox{send}(i, j)$: ${x}_{iej9}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)\,I(r_{e^\prime j} = 1)$;
 		\item[10.] $\mbox{receive}(i,j)$: ${x}_{iej10}=\mbox{send}(j,i)$;
@@
 	\begin{itemize}
-		\item[1.] intercept: ${z}_{ie1} =1$;
-		\item[2.] $\mbox{gender}(i)$: ${z}_{ie2}=I(\mbox{gender of sender }i= \mbox{female})$;
-		\item[3.] $\mbox{manager}(i)$: ${z}_{ie3}=I(\mbox{sender }i \mbox{ is the County Manager})$;
-		\item[4.] $\mbox{outdegree}(i)$: ${z}_{ie4} =\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)$;
-		\item[5.] $\mbox{indegree}(i)$: ${z}_{ie5}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(u_{e^\prime i} = 1)$;
-		\item[6.] $\mbox{weekend}(e)$: ${z}_{ie6} = I(t_{e-1} \mbox{ is during the } \mbox{weekend})$;
-		\item[7.] $\mbox{PM}(e)$: ${z}_{ie7}= I(t_{e-1} \mbox{ in } \mbox{PM})$.
+		\item[1.] intercept: ${z}_{ie\cdot1} =1$;
+		\item[2.] $\mbox{gender}(i)$: ${z}_{ie\cdot2}=I(\mbox{gender of sender }i= \mbox{female})$;
+		\item[3.] $\mbox{manager}(i)$: ${z}_{ie\cdot3}=I(\mbox{sender }i \mbox{ is the County Manager})$;
+		\item[4.] $\mbox{outdegree}(i)$: ${z}_{ie\cdot4} =\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)$;
+		\item[5.] $\mbox{indegree}(i)$: ${z}_{ie\cdot5}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(r_{e^\prime i} = 1)$;
+		\item[6.] $\mbox{weekend}(e)$: ${z}_{ie\cdot6} = I(t_{e-1} \mbox{ is during the } \mbox{weekend})$;
+		\item[7.] $\mbox{PM}(e)$: ${z}_{ie\cdot7}= I(t_{e-1} \mbox{ in } \mbox{PM})$.
 	\end{itemize}
@@
 			\STATE draw test senders (out of $E$ senders) 
-			\STATE draw test receivers (out of $E\times (V-1)$ receiver indicators $\{\{\boldsymbol{r}_{ej}\}_{j\in [V]_{\backslash s_e}}\}_{e=1}^E$)
+			\STATE draw test receivers (out of $E\times (V-1)$ receiver indicators $\{\{{r}_{ej}\}_{j\in [V]_{\backslash s_e}}\}_{e=1}^E$)
 			\STATE draw test timestamps  (out of $E$ timestamps) 
@@
 			\IF{$s_e=$  NA}
-			\STATE compute $\boldsymbol{\pi}_e$, where $\pi_{ei}=f_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2)\times \prod_{i^\prime\neq i}\big(1-F_{\tau}(\tau_{e}; \mu_{i^\prime e}, \sigma_\tau^2) \big)$
+			\STATE compute $\boldsymbol{\pi}_e = (\pi_{1e},\ldots,\pi_{Ve})$, where \\$\pi_{ie}=\Big(f_{\tau}(\tau_{ e}; \mu_{i e}, \sigma_\tau^2)\times \prod_{i^\prime\neq i}\big(1-F_{\tau}(\tau_{ e}; \mu_{i^\prime  e}, \sigma_\tau^2) \big)\Big) \times$
 			\STATE draw $s_e \sim \mbox{Categorical}(\boldsymbol{\pi}_e)$ 
@@
 			\STATE draw ${\tau}_e$ from its conditional distribution using importance sampling, %from equation (\ref{eqn:latenttime}) (without the product term) 
-	      where $P({\tau}_e|\, \cdot)\propto f_{\tau}(\tau_{e}; \mu_{s_e e}, \sigma_\tau^2)\times \prod_{i\neq s_e}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2) \big)$%\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
+	      where $P({\tau}_e|\, \cdot)\propto \Big(f_{\tau}(\tau_{e}; \mu_{s_{e} e}, \sigma_\tau^2)\times \prod_{i\neq s_{e}}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2)\big)\Big) \times $%\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
 			\ENDIF
@@
 We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
-First, we compare the posterior probability of correct senders for each of the missing emails $\{e:s_e=\mbox{NA}\}$, which corresponds to $\pi_{es_e}$ in Algorithm \ref{alg:PPE}.
-We call this measure the ``correct sender posterior probability." In Figure \ref{subfigure:PPEresults1}, we display boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{es_{e}} = \frac{1}{N}\sum_{n=1}^N \pi^{(n)}_{es_{e}}$---across the missing emails.
+First, we compare the posterior probability of correct senders for each of the missing emails $\{e:s_e=\mbox{NA}\}$, which corresponds to $\pi_{s_ee}$ in Algorithm \ref{alg:PPE}.
+We call this measure the ``correct sender posterior probability." In Figure \ref{subfigure:PPEresults1}, we display boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{s_{e}e} = \frac{1}{N}\sum_{n=1}^N \pi^{(n)}_{s_{e}e}$---across the missing emails.
 The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $V$ possible senders $=1/18$), with the log-normal model showing better performance than the exponential model.
@@
 	\end{equation}
-with TP denoting true positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{ej}=\boldsymbol{r}^{\textrm{(pred)}}_{ej}=1$), FN denoting false negative (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{ej}=1$ but $\boldsymbol{r}^{\textrm{(pred)}}_{ej}=0$), and FP denoting false positive (i.e., $\boldsymbol{r}^{\textrm{(obs)}}_{ej}=0$ but $\boldsymbol{r}^{\textrm{(pred)}}_{ej}=1$).
+with TP denoting true positive (i.e., ${r}^{\textrm{(obs)}}_{ej}=r^{\textrm{(pred)}}_{ej}=1$), FN denoting false negative (i.e., ${r}^{\textrm{(obs)}}_{ej}=1$ but ${r}^{\textrm{(pred)}}_{ej}=0$), and FP denoting false positive (i.e., ${r}^{\textrm{(obs)}}_{ej}=0$ but ${r}^{\textrm{(pred)}}_{ej}=1$).
 Although the generative process for events (Section \ref{subsec: Tie}) is not directly affected by the choice of timestamp distribution, Figure \ref{subfigure:PPEresults2} reveals slight difference between log-normal and exponential in their performance in predicting missing receiver indicators, where log-normal on average outperforms exponential.
@@
 	\end{equation}
-	Figure \ref{subfigure:PPEresults3} presents boxplots for the median absolute percentage errors on a log scale.
+	Figure \ref{subfigure:PPEresults3} presents boxplots for the median absolute percentage errors.
 These plots show that the log-normal distribution fits the time increments significantly better than the exponential distribution.
@@
 	Based on the prediction experiments in Section \ref{subsec:Experiment_email}, we interpret the results from the HEM using the log-normal distribution, with emphasis on understanding the effects of receiver selection and event timing features defined in Section \ref{subsec:Covariates_email}.
-We assume weakly informative priors for latent variables such as $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b=\boldsymbol{0}, \Sigma_b = 2\times I_P)$, $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta=\boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, and $\sigma_\tau^2 \sim \mbox{inverse-Gamma}(a=2, b=1)$, and MCMC (Algorithm \ref{alg:MCMC}) with $O=55,000$ outer iterations and a burn-in of 15,000, where we thin by keeping every $40^{\textrm{th}}$ sample.
+We assume weakly informative priors for latent variables such as $\boldsymbol{b}\sim N(\boldsymbol{\mu}_b=\boldsymbol{0}, \Sigma_b = 2\times I_P)$, $\boldsymbol{\eta}\sim N(\boldsymbol{\mu}_\eta=\boldsymbol{0}, \Sigma_\eta = 2\times I_Q)$, and $\sigma_\tau^2 \sim \mbox{inverse-Gamma}(a=2, b=1)$, and then run the MCMC (Algorithm \ref{alg:MCMC}) with $O=55,000$ outer iterations and a burn-in of 15,000, where we thin by keeping every $40^{\textrm{th}}$ sample.
 While the inner iterations for $\sigma_\tau^2$ is fixed as 1, we specify the inner iterations $I_1=20$ for $\boldsymbol{b}$ and $I_2=10$ for $\boldsymbol{\eta}$ to adjust for slower convergence rates.
@@
 			&\log(\tau_{ie}) \sim N(\mu_{ie}, \sigma_\tau^2), \mbox{ with }\\
-			&\mu_{ie} = \eta_{1}+\eta_{2} z_{ie2}+\ldots+\eta_{7}z_{ie7}.
+			&\mu_{ie} = \eta_{1}+\eta_{2} z_{ie\cdot2}+\ldots+\eta_{7}z_{ie\cdot7}.
 		\end{aligned}
 	\end{equation*}
-	The posterior estimates of two temporal effects---``weekend$(e)$" and ``PM$(e)$"---indicate that if the $(e-1)^{\textrm{th}}$ email was sent during the weekend or after midday, then the time to the $e^{\textrm{th}}$ email is expected to take $\exp(1.552)\approx 4.722$ hours and $\exp(0.980)\approx2.665$ hours longer, respectively, compared to their counterparts (i.e., weekdays and am).
+	The posterior estimates of two temporal effects ``weekend$(e)$" and ``PM$(e)$" imply that if the $(e-1)^{\textrm{th}}$ email was sent during the weekend or after midday, then the time from $(e-1)^{\textrm{th}}$ email to $e^{\textrm{th}}$ email is expected to take longer than what is expected under their counterparts (i.e., weekdays and am).
+Specifically, these effects increase the expected value of $\log(\tau_{ie})$ by $\hat{\eta}_6 =1.552$ and $\hat{\eta}_7= 0.980$, respectively.
 On the contrary, the covariates ``manager$(i)$", ``outdegree$(i)$", and ``indegree$(i)$"  shorten the amount of time until the next email.
@@
 			\STATE	set ${r}_e,\ldots, r_{e+n-1}=\mbox{argmin}_{j}(\tau_{je})$
-			\STATE	set $\boldsymbol{s}_e=\boldsymbol{u}_{r_e e},\ldots,\boldsymbol{s}_{e+n-1}=\boldsymbol{u}_{r_{e+n-1} d}$
+			\STATE	set $\boldsymbol{s}_e=\boldsymbol{u}_{r_e e},\ldots,\boldsymbol{s}_{e+n-1}=\boldsymbol{u}_{r_{e+n-1} e}$
 			\STATE	set $t_e, \ldots, t_{e+n-1}=t_{e-1} + \min_j\tau_{je}$
@@
 	In the forward sampler, both observable and unobservable variables are generated using Algorithm \ref{alg:generative}.
-In the backward samples, unobservable variables are generated using the sampling equations for inference, which we derived in Section \ref{sec:inference}.
+In the backward samples, unobservable variables are generated using the sampling equations for inference, which we derived in Section \ref{subsec:conditionaldist}.
 For each forward and backward sample that consists of $E$ number of events, we save these statistics:\\

### 2018-11-13 paper/revision1/ba-sample.tex
most recent version
computational complexity section added

@@
 	\subsection{Computational complexity}\label{subsec:computation}
+The sampler uses a blocked Gibbs sampler for the $u_{iej}$.
+Given the constraint that $\sum_j u_{iej} > 0$, this sampler may be rather inefficient in the case where there are many one-to-one interactions (as is the case in the application, where 83\% of the interactions are dyadic).
+In
+order to go from the state $u_{ie} = (1, 0, 0, 0, 0, 0)$ to $u_{ie} = (0, 1, 0, 0, 0, 0)$ one needs to go through a state where two receivers are activated, which has low probability in this case.
+It would be good to comment on this, and in general on the mixing of the MCMC sampler.
+
+The authors should provide some indication of the computational complexity per iterations of their sampler.
+The application to email interaction data is rather small (18 nodes and 680 emails), so it would be good to know how many nodes/events the proposed approach can handle.
+Your quantitative assessments are based on 5 nodes in the simulation and 18 nodes in the application.
+These are quite small networks compared to those one would expect in real{world settings (such as those you list in the introduction).
+To what extent are your computational methods able to scale to much larger networks?
+An application to a bigger dataset would be useful.
+Moreover, more information on computational time should be provided.
+
+Given that the model is relatively complex, some sensitivity analyses should be carried out to check how much posterior inference is affected by the hyperparameters' settings, and, possibly, suggest some default values.
+
+There are many MH routines in the literature.
+Which type of MH do you consider?
+What is the proposal distribution?
+What about the acceptance rate?
+Is there any smart proposal in this case which helps in increasing the acceptance rate.
+
+You rely on data augmentation MCMC, which has been shown to mix quite poorly (also in recent theoretical papers).
+Indeed, as expected, you end up thinning the chains every 40 samples in the application.
+However, there is no comment on this in the paper.
+I think it should be highlighted and not just hidden in the thinning.
 
@@
 	\begin{itemize}
-		\item[1.] intercept: ${z}_{ie\cdot1} =1$;
-		\item[2.] $\mbox{gender}(i)$: ${z}_{ie\cdot2}=I(\mbox{gender of sender }i= \mbox{female})$;
-		\item[3.] $\mbox{manager}(i)$: ${z}_{ie\cdot3}=I(\mbox{sender }i \mbox{ is the County Manager})$;
-		\item[4.] $\mbox{outdegree}(i)$: ${z}_{ie\cdot4} =\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)$;
-		\item[5.] $\mbox{indegree}(i)$: ${z}_{ie\cdot5}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(r_{e^\prime i} = 1)$;
-		\item[6.] $\mbox{weekend}(e)$: ${z}_{ie\cdot6} = I(t_{e-1} \mbox{ is during the } \mbox{weekend})$;
-		\item[7.] $\mbox{PM}(e)$: ${z}_{ie\cdot7}= I(t_{e-1} \mbox{ in } \mbox{PM})$.
+		\item[1.] intercept: ${z}_{ie1} =1$;
+		\item[2.] $\mbox{gender}(i)$: ${z}_{ie2}=I(\mbox{gender of sender }i= \mbox{female})$;
+		\item[3.] $\mbox{manager}(i)$: ${z}_{ie3}=I(\mbox{sender }i \mbox{ is the County Manager})$;
+		\item[4.] $\mbox{outdegree}(i)$: ${z}_{ie4} =\sum_{e^\prime: t_{e^\prime} \in l_e} I(s_{e^\prime} = i)$;
+		\item[5.] $\mbox{indegree}(i)$: ${z}_{ie5}=\sum_{e^\prime: t_{e^\prime} \in l_e} I(r_{e^\prime i} = 1)$;
+		\item[6.] $\mbox{weekend}(e)$: ${z}_{ie6} = I(t_{e-1} \mbox{ is during the } \mbox{weekend})$;
+		\item[7.] $\mbox{PM}(e)$: ${z}_{ie7}= I(t_{e-1} \mbox{ in } \mbox{PM})$.
 	\end{itemize}
@@
 We particularly choose the log-normal distribution based on some exploratory analysis (e.g., histogram and simple regressions) on raw time increments data, and select the exponential distribution as a baseline alternative that is a commonly specified distribution for time-to-event data, and is also used in the stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic} as well as their extensions \citep{snijders2007modeling}.
+
+	We evaluated the models' ability to predict out-of-sample events and timestamps on Montgomery County email data.
+We generated a train--test split of the data by randomly selecting 10\% of senders, receivers, and timestamp variables to be held out.
+Our model then imputed these missing variables during inference, sampling them from their conditional posterior along with the other latent variables.
+Algorithm \ref{alg:PPE} outlines this procedure in detail.
+We compare the predictive performance of two versions of our model, each with a different timing distribution over the time increments, by repeating the predictive assessments$N=500$ times where we make new predictions each time for the fixed held out data.
+We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
+First, we compare the posterior probability of correct senders for each of the missing emails $\{e:s_e=\mbox{NA}\}$, which corresponds to $\pi_{s_ee}$ in Algorithm \ref{alg:PPE}.
+We call this measure the ``correct sender posterior probability." In Figure \ref{subfigure:PPEresults1}, we display boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{s_{e}e} = \frac{1}{N}\sum_{n=1}^N \pi^{(n)}_{s_{e}e}$---across the missing emails.
+The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $V$ possible senders $=1/18$), with the log-normal model showing better performance than the exponential model.
+Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $e$ and $j$ with $r_{ej}$=NA) by taking the harmonic mean of precision and recall:
+	\begin{equation}
+		\begin{aligned}
+			F_1 =2\times\frac{\mbox{precision}\cdot \mbox{recall}}{\mbox{precision}+ \mbox{recall}}, &\mbox{ where } \\
+			\mbox{recall}  = \frac{\mbox{TP}}{\mbox{TP+FN}} \mbox{ and } \mbox{precision} & =\frac{\mbox{TP}}{\mbox{TP+FP}},
+		\end{aligned}
+	\end{equation}
 		\begin{algorithm}[!t]
@@
 		\end{algorithm}
-
-	We evaluated the models' ability to predict out-of-sample events and timestamps on Montgomery County email data.
-We generated a train--test split of the data by randomly selecting 10\% of senders, receivers, and timestamp variables to be held out.
-Our model then imputed these missing variables during inference, sampling them from their conditional posterior along with the other latent variables.
-Algorithm \ref{alg:PPE} outlines this procedure in detail.
-We compare the predictive performance of two versions of our model, each with a different timing distribution over the time increments, by repeating the predictive assessments$N=500$ times where we make new predictions each time for the fixed held out data.
-We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
-First, we compare the posterior probability of correct senders for each of the missing emails $\{e:s_e=\mbox{NA}\}$, which corresponds to $\pi_{s_ee}$ in Algorithm \ref{alg:PPE}.
-We call this measure the ``correct sender posterior probability." In Figure \ref{subfigure:PPEresults1}, we display boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{s_{e}e} = \frac{1}{N}\sum_{n=1}^N \pi^{(n)}_{s_{e}e}$---across the missing emails.
-The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $V$ possible senders $=1/18$), with the log-normal model showing better performance than the exponential model.
-Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $e$ and $j$ with $r_{ej}$=NA) by taking the harmonic mean of precision and recall:
-	\begin{equation}
-		\begin{aligned}
-			F_1 =2\cdot\frac{\mbox{precision}\cdot \mbox{recall}}{\mbox{precision}+ \mbox{recall}}, &\mbox{ where } \\
-			\mbox{recall}  = \frac{\mbox{TP}}{\mbox{TP+FN}} \mbox{ and } \mbox{precision} & =\frac{\mbox{TP}}{\mbox{TP+FP}},
-		\end{aligned}
-	\end{equation}
 with TP denoting true positive (i.e., ${r}^{\textrm{(obs)}}_{ej}=r^{\textrm{(pred)}}_{ej}=1$), FN denoting false negative (i.e., ${r}^{\textrm{(obs)}}_{ej}=1$ but ${r}^{\textrm{(pred)}}_{ej}=0$), and FP denoting false positive (i.e., ${r}^{\textrm{(obs)}}_{ej}=0$ but ${r}^{\textrm{(pred)}}_{ej}=1$).
@@
 			&\log(\tau_{ie}) \sim N(\mu_{ie}, \sigma_\tau^2), \mbox{ with }\\
-			&\mu_{ie} = \eta_{1}+\eta_{2} z_{ie\cdot2}+\ldots+\eta_{7}z_{ie\cdot7}.
+			&\mu_{ie} = \eta_{1}+\eta_{2} z_{ie2}+\ldots+\eta_{7}z_{ie7}.
 		\end{aligned}

### 2018-11-14 code/Montgomery_processing2.R
out of sample experiment section edits & bibliography all fixed

@@ -94,6 +94,9 @@ trim = which(email$timepoints >=7*24*timeunit+email$timepoints[1])
 edge = edge[trim]
 X = X[trim,,,]
 Y = Y[trim,,]
+
+prior.beta = list(mean = c(-3.5, rep(0, P-1)), var = 1*diag(P))
+prior.eta = list(mean = c(7, rep(0, Q-1)), var = 1*diag(Q))
 Montgomery_infer = Inference(edge, X, Y, 55000, c(20,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
                              proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "lognormal")
 save(Montgomery_infer, file= "/Users/bomin8319/Desktop/Montgomery_infer.RData")

### 2018-11-16 paper/ba-HEM/ba-sample.tex
splitting paper and manuscript for submission
updating memo

@@
 
+		\newpage
+		\bibliographystyle{ba}
+		\bibliography{baHEM}
+
 	\section*{Appendix}

### 2018-11-16 paper/revision1/HEM-reply.tex
updating memo

@@
 \usepackage{booktabs}
+
+\newcommand{\pjm}[1]{{\color{blue}#1}}
+\definecolor{MyGreen}{cmyk}{1.0,0.0,1.0,0.2}
+\newcommand{\sjc}[1]{{\color{MyGreen}#1}}
+\definecolor{MyFuschia}{cmyk}{0.07,0.95,0,0}
+\newcommand{\ejm}[1]{{\color{MyFuschia}#1}}
+\definecolor{bloodred}{RGB}{102,0,0}
+\newcommand{\blood}[1]{{\color{bloodred}#1}}
+\definecolor{mygrey}{gray}{0.45}
+\newcommand{\grey}[1]{{\color{mygrey}#1}}
+\definecolor{orange}{RGB}{255,102,0}
+\newcommand{\orange}[1]{{\color{orange}#1}}
+\newcommand{\red}[1]{{\color{red}#1}}
+\newcommand{\blue}[1]{{\color{blue}#1}}
+% The official Dartmouth green: 
+\definecolor{dartmouthgreen}{rgb}{0,.41,.24}
 
@@
 
+\noindent \textbf{Point-by-point discussion of Reviews and Response to Comments}\\
+
+First, we thank the editor...
+
+\bigskip
+\bigskip
+
+\noindent \underline{\textbf{Response to the Editor's Comments}}\\
+
+\noindent {\bf E1} \grey{\emph{Presentation: I found the presentation rather lacking; in particular, the description of the model in Section 2 is very difficult to follow, due to the numerous variables introduced, the order in which the different elements of the model are introduced, and the lack of definition for some of them.
+I think a major rewriting is needed here.
+}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor.. \\
+
+\noindent  {\bf E2} \grey{\emph{Some notations are rather unusual, for example $A$ for nodes.
+Although this is not indicated in the text, I assume this comes from the term ``actor'' in the stochastic actor-oriented model (SAOM) of Snijders, cited by the author?
+If this is the case, it would be worth mentioning it so that the reader recalls this later on.
+$y$ for the covariates is also rather unusual.
+Some notations are inconsistent.
+For example $u_{ie}$ denotes the first line of the matrix $u_e$, but $\tau_e = \text{min}_i(\tau_{ie})$.
+}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E3} \grey{\emph{In section 2.1, I think it makes more sense to First introduce Equation (2.2) then (2.1).
+The term ``intensity'' used for $\lambda_{iej}$ is rather confusing.
+As the paper is concerned with a continuous-time model, one would expect that the term intensity refers to some point process, which is not the case here.
+}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E4} \grey{\emph{It is difficult to understand Section 2.2 without reading section 2.3.
+The authors introduce the notation $\tau_{ie}$ above Equation (2.5), but do not explain what this represents (at this stage I thought it was a component of the vector $\tau_e$).
+I do not see what the variable $\mu$ represents in Equation (2.5), and if it is related to $\mu_{ie}$ in Equation (2.4)
+ }}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E5} \grey{\emph{ Some sentences are di¢ cult to understand:
+Page 3: ``we define a probability measure ``MBG'' motivated by the Gibbs measure'' }}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E6} \grey{\emph{ Discussion of relevant literature: The authors should provide a better discussion of how their model differs from other approaches, in particular the approach of Perry and Wolfe (2013), and Snijders (1996), based on point processes.
+Perry and Wolfe propose a specific model for multicast interaction (Equation (6) in the arxiv version of their paper).
+What are the differences/advantages between both constructions?
+In Section 2.3, the author cite Snijders (1996) when they introduce the model for the interaction arrival times.
+I am not sure what is meant here: is this part of the model already introduced in Snijders (1996)?
+The authors should be more specific here.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E7} \grey{\emph{ Model, covariates and missing data: This is not explicitly mentioned in the definition of the model in Section 2, but the covariates $x_e$ and $y_e$ depend on the observed interaction data ($s_{e'}$ , $r_{e'}$ , $t_{e'}$ ) in the last 7 days, as written in Section 4.1.
+Hence the observations ($s_e$, $r_e$, $t_e$)$_{e=1,...,E}$ are not conditionally independent given the model parameters.
+This should be clearly stated in Section 2.
+For this reason, I do not think that the out-of-sample algorithm described in Algorithm 3 is correct.
+The conditional distribution for the missing observations $s_e$,$r_e$ and $t_e$ should depend on ($s_{e'}$ ; $r_{e'}$ ; $t_{e'}$ )$_{e': t_e < t_{e'} < t_{e} + l_e }$, which is not what is done.
+}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E8} \grey{\emph{The authors should provide more details on the Metropolis-Hastings
+proposals for the parameters $b$ and $\eta$ in Section 3.2. }}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E9} \grey{\emph{The sampler usePs a blocked Gibbs sampler for the $u_{iej}$.
+Given the constraint that $\sum_j u_{iej} > 0$, this sampler may be rather inefficient in the case where there are many one-to-one interactions (as is the case in the application, where 83\% of the interactions are dyadic).
+In order to go from the state $u_{ie}$ = (1,0,0,0,0,0) to $u_{ie}$ = (0,1,0,0,0,0) one needs to go through a state where two receivers are activated, which has low probability in this case.
+It would be good to comment on this, and in general on the mixing of the MCMC sampler.
+}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E10} \grey{\emph{The authors provide in Section 3.2.
+some sanity checks on the sampler.
+While this is good practice to perform such checks, I am not sure it is very useful to include this in the main body (could be moved to the appendix), as this is done on a very small scale example with 5 nodes and 100 events, and does not really give an indication on the convergence properties of the algorithm in a more realistic scenario.
+I suggest the authors perform a simulation study with a larger number of nodes and events to demonstrate that the algorithm is able to approximate the posterior distribution well in that case.
+}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E11} \grey{\emph{The authors should provide some indication of the computational complexity per iterations of their sampler.
+The application to email interaction data is rather small (18 nodes and 680 emails), so it would be good to know how many nodes/events the proposed approach can handle.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent  {\bf E12} \grey{\emph{Typos: The article contains numerous typos. Here are some of them:}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+
+\noindent \underline{\textbf{Response to Comments by the Reviewer}}\\
+
+\noindent {\bf R1} \grey{\emph{ TYPOS...}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R2} \grey{\emph{UNCLEAR PARTS...}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
 \end{document}

### 2018-11-16 paper/revision1/ba-sample.tex

@@
 For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} characterize that network evolutions occur as the senders decide to create or remove an edge from the existing network, one edge at a time.
-Event-based network models \citep{Butts2008,Vu2011,hunter2011dynamic,PerryWolfe2012} provide a general framework for modeling the realization of edges that occur as instances in continuous time streams of events.
+Event-based network models \citep{butts2008,Vu2011,hunter2011dynamic,PerryWolfe2012} provide a general framework for modeling the realization of edges that occur as instances in continuous time streams of events.
 This family of models is flexible enough to account for the many ways in which past network structures beget future ones---e.g., if node $i$ directed a tie to node $j$ recently, then node $j$ will direct one to node $i$ in the near future---and useful for understanding the traits and behaviours that are predictive of interactions.
@@
 When it is relevant to sender or receiver only, we use $y_{ie}$ and $y_{ej}$ to imply ``sender $i$ of an event $e$" and ``receiver $j$ of event $e$," respectively.
-~\looseness=-1
+Similarly, we use $y_e$ to denote the quantity associated with ``event $e$".~\looseness=-1
 			\begin{figure}[!t]
@@
 First, the features that govern which receivers are selected by a given sender are defined using subgraph configuration counts (e.g., the number of triangles formed through sending the tie, the number of previous hyperedges that would be reciprocated by the tie).
-The HEM's use of subgraph configuration formation follows a similar process underlying network change in the the continuous-time event model proposed by \cite{PerryWolfe2012} as well as the relational event model \citep{Butts2008}, and is also related to the subgraph completion processes used to model discrete-time network change in the temporal ERGM \citep{hanneke2010discrete}.
+The HEM's use of subgraph configuration formation follows a similar process underlying network change in the the continuous-time event model proposed by \cite{PerryWolfe2012} as well as the relational event model \citep{butts2008}, and is also related to the subgraph completion processes used to model discrete-time network change in the temporal ERGM \citep{hanneke2010discrete}.
 Second, the use of candidate receivers as a mechanism through which continuous network change is modeled is related to the use of latent changes between snapshot network observations in the stochastic actor oriented model (SAOM) by \cite{snijders1996stochastic}.
@@
 				\FOR{$j = 1$ to $V$ ($j \neq i$)}
-				\STATE update $u_{iej}$ using Gibbs update ---equation (\ref{eqn:latentreceiver})
+				\STATE update $u_{iej}$ using Gibbs update---equation (\ref{eqn:latentreceiver})
 				\ENDFOR
@@
 
-There are many MH routines in the literature.
-Which type of MH do you consider?
-What is the proposal distribution?
-What about the acceptance rate?
-Is there any smart proposal in this case which helps in increasing the acceptance rate.
+There are many MH routines in the literature. Which type of MH do you consider? What about the acceptance rate? Is there any smart proposal in this case which helps in increasing the acceptance rate.
 
@@
 Our model then imputed these missing variables during inference, sampling them from their conditional posterior along with the other latent variables.
-Algorithm \ref{alg:PPE} outlines this procedure in detail.
-We compare the predictive performance of two versions of our model, each with a different timing distribution over the time increments, by repeating the predictive assessments$N=500$ times where we make new predictions each time for the fixed held out data.
+One important point is that our covariates $\boldsymbol{x}$ and $\boldsymbol{z}$
+depend on the observed interaction data in the last 7 days, as written in Section \ref{subsec:Covariates_email}, hence the observations $ \{ (s_e, \boldsymbol{r}_e, t_e)\}_{e=1}^E$ are not conditionally independent given the model parameters.
+If the sender of event $e$ is missing, we draw from the categorical distribution using the sender probability vector $\boldsymbol{\pi}_e = (\pi_{1e},\ldots,\pi_{Ve})$.
+As a result, the conditional distribution for the missing observations $s_e$, $r_{ej}$, and $t_e$ should depend on $ \{ (s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime})\}_{e^\prime \in m_e}$, where $m_e = (t_e, t_e+\mbox{7 days}]$.
+In particular, if the sender $s_e$ is missing, then we draw from the categorical distribution using the sender probability $\boldsymbol{\pi}_e = (\pi_{1e},\ldots,\pi_{Ve})$, where $\pi_{ie}$ follows
+		\begin{equation}
+		\begin{aligned}
+\pi_{ie}=\Big(f_{\tau}(\tau_{ e}; \mu_{i e}, \sigma_\tau^2)\times \prod_{i^\prime\neq i}\big(1-F_{\tau}(\tau_{ e}; \mu_{i^\prime  e}, \sigma_\tau^2) \big)\Big) \times \prod_{e^\prime:t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|s_{e}=i)
+		\end{aligned}
+				\label{eqn:missingsender}
+		\end{equation}
+		with $L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|s_{e}=i)$ denoting the joint likelihood of $(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime})$ conditioned on the covariates $\boldsymbol{x}_{e^\prime}$ and $\boldsymbol{z}_{e^\prime}$ calculated assuming $s_{e}=i$.
+Here, the term $\prod_{e^\prime:t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime})$ is proportional to the multiplication of equation (\ref{eqn:latentedge}) and equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2})), with the product over $e=1,\ldots,E$ replaced by $\{e^\prime:t_{e^\prime} \in m_e\}$.
+Similarly, if the $j$th receiver indicator $r_{ej}$ is missing, we sample from Bernoulli distribution where
+				\begin{equation}
+				\begin{aligned}
+			P(r_{ej}=1)&=\exp(\lambda_{iej})\times \prod_{e^\prime:t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|r_{ej}=1),\\
+			P(r_{ej}=0) &= \text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 )\times \prod_{e^\prime: t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|r_{ej}=0).
+				\end{aligned}
+								\label{eqn:missingreceiver}
+				\end{equation}
+	Finally, when the timestamp $t_e$ is missing, we draw the time increment $\tau_e$ via importance sampling using the proposal distribution $g \sim \mbox{halfcauchy}(5)$, where its conditional distribution follows
+			\begin{equation}
+			\begin{aligned}
+P({\tau}_e|\, \cdot)\propto \Big(f_{\tau}(\tau_{e}; \mu_{s_{e} e}, \sigma_\tau^2)\times \prod_{i\neq s_{e}}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2)\big)\Big) \times\prod_{e^\prime:t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|\tau_{e}).
+			\end{aligned}
+							\label{eqn:missingtime}
+			\end{equation}
+	Algorithm \ref{alg:PPE} outlines this procedure.
+
+	We compare the predictive performance of two versions of our model, each with a different timing distribution over the time increments, by repeating the predictive assessments $N=500$ times where we make new predictions each time for the fixed held out data.
 We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}.
@@
 				\IF{$s_e=$  NA}
-				\STATE compute $\boldsymbol{\pi}_e = (\pi_{1e},\ldots,\pi_{Ve})$, where \\$\pi_{ie}=\Big(f_{\tau}(\tau_{ e}; \mu_{i e}, \sigma_\tau^2)\times \prod_{i^\prime\neq i}\big(1-F_{\tau}(\tau_{ e}; \mu_{i^\prime  e}, \sigma_\tau^2) \big)\Big) \times$
+				\STATE compute $\boldsymbol{\pi}_e = (\pi_{1e},\ldots,\pi_{Ve})$---equation (\ref{eqn:missingsender})
 				\STATE draw $s_e \sim \mbox{Categorical}(\boldsymbol{\pi}_e)$ 
@@
 				\STATE draw $r_{ej} \sim \mbox{Bernoulli}(p_{ej}),$
-				where $p_{ej}=\frac{\exp(\lambda_{iej})}{\exp(\lambda_{iej})+\text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 )}$ %as defined in equation (\ref{eqn:latentreceiver})
+				where $p_{ej}=\frac{P(r_{ej}=1)}{P(r_{ej}=1)+P(r_{ej}=0)}$---equation (\ref{eqn:missingreceiver})
 				\ENDIF
@@
 				\IF{$t_e=$ NA}
-				\STATE draw ${\tau}_e$ from its conditional distribution using importance sampling, %from equation (\ref{eqn:latenttime}) (without the product term) 
-				where $P({\tau}_e|\, \cdot)\propto \Big(f_{\tau}(\tau_{e}; \mu_{s_{e} e}, \sigma_\tau^2)\times \prod_{i\neq s_{e}}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2)\big)\Big) \times $%\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}
+				\STATE draw ${\tau}_e$ using importance sampling---equation (\ref{eqn:missingtime})%from equation (\ref{eqn:latenttime}) (without the product term) 
 				\ENDIF
@@
 			\bibliography{baHEM}	
-
 	\section*{Appendix}

### 2018-11-16 paper/revision1/HEM-reply.tex
revised memo

@@
 
+\noindent {\bf R3} \grey{\emph{BIBLIOGRAPHY:...}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R4} \grey{\emph{As already mentioned, the authors focus on the somewhat less explored area of continuous?time relational event models where each edge has its own different time index?instead of considering time?varying models for snap- shots of networks collected on a pre?specified time grid.
+However, the contribution is still within the general class of dynamic network inference.
+In this respect, the literature review provides a poor picture for the state-of-the-art in this wider framework.
+I think the authors should provide a more comprehensive literature review including also temporal ERGMs and dynamic latent variable models (e.g.
+dynamic stochastic block models, dynamic mixed membership stochastic block models, dynamic latent space models, .
+.
+.).
+Discussing your contribution in the light of these alternative (and quite different) models would further clarify the key novelties our the proposed methods.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R5} \grey{\emph{I fully understood the first paragraph in page 3 (summarizing HEMs) after reading the subsections 2.1, 2.2 and 2.3.
+This part should provide a much clear picture of your model instead of creating confusion.
+I suggest to improve it, leveraging also some intuitive illustrative figure.
+For example you could place Figure 1 much early and comment it while summarizing the HEM at the beginning of Section 2.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R6} \grey{\emph{You present the full conditionals in page 7 assuming uninformative $N(0, \infty)$ priors, but then you rely on weakly informative priors in the application (see page 17).
+I found this confusing.
+I?d present results in page 7 for generic Gaussian priors.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R7} \grey{\emph{Given that the model is relatively complex, some sensitivity analyses should be carried out to check how much posterior inference is affected by the hyperparameters?
+settings, and, possibly, suggest some default values.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R8} \grey{\emph{There are many MH routines in the literature.
+Which type of MH do you consider?
+What is the proposal distribution?
+What about the acceptance rate?
+Is there any smart proposal in this case which helps in increasing the acceptance rate.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R9} \grey{\emph{You rely on data augmentation MCMC, which has been shown to mix quite poorly (also in recent theoretical papers).
+Indeed, as expected, you end up thinning the chains every 40 samples in the application.
+However, there is no comment on this in the paper.
+I think it should be highlighted and not just hidden in the thinning.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R9} \grey{\emph{Your quantitative assessments are based on 5 nodes in the simulation and 18 nodes in the application.
+These are quite small networks compared to those one would expect in real?world settings (such as those you list in the introduction).
+To what extent are your computational methods able to scale to much larger networks?
+An application to a bigger dataset would be useful.
+Moreover, more information on computational time should be provided.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R10} \grey{\emph{You compare performance in predicting missing senders with random guess 1/18.
+This is a quite naive competitor and I am sure the authors can find much better ones?still relatively simple.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R11} \grey{\emph{In Figure 4c the choice of the logarithmic scale for MdAPE seems to hide a quite poor performance of your model in predicting the timestamps.
+It is true that the log?normal improves over the exponential, but the log?normal boxplot has still a third quartile providing an MdAPE of exp(7.36) which looks quite big.
+This is to me a negative result, which should be discussed and addressed in the paper.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R12} \grey{\emph{Based on your comments in the paper you are interpreting the posterior expectations of exp($\eta_6$) and exp($\eta_7$)--i.e.
+E[exp($\eta_6$) | data] and E[exp($\eta_7$) | data].
+However you seem to compute this as exp[E(exp($\eta_6$) | data)] = exp(1.552) and exp[E(exp($\eta_7$) | data)] = exp(0.980).
+By Jensen inequality this is wrong.}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
+\noindent {\bf R13} \grey{\emph{It is also not correct to claim that the $e^{th}$ email is expected to take E[exp($\eta$) | data] longer compared to their counterpart.
+The term longer seems to refer to an additive effect on the event timing, which is not the case here since you assume a log?normal for the event timing and hence the effect is on the scale of the timing and not on the location?note that, if $X \sim \text{log-normal}(\mu, \sigma^2)$, then $E(X) = exp(\mu + \sigma^2/2)$.
+The authors should be more careful in the interpretations on the original time scale, or, more conservatively, they could simply comment on the effects on the log-time (as done immediately after).}}\\
+
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+
 \end{document}

### 2018-11-16 code/Montgomery_PPE_baseline.R
updates on baseline using DirichletMultinomial

@@ -1,0 +1,220 @@
+#source("/Users/bomin8319/Desktop/MulticastNetwork/code/Multicast.R")
+library(MulticastNetwork)
+library(lubridate)
+load('~/Desktop/MulticastNetwork/code/Temporal_Email_Data.Rdata')
+Montgomery = Temporal_Email_Data$Montgomery
+email = Montgomery$email_data
+email = unique(email)
+email$timepoints =  as.numeric(as.POSIXct(strptime(email[,1], "%d %b %Y %H:%M:%S")))
+email = email[order(email$timepoints), ]
+edge = list()
+initialtime =  as.numeric(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S")))
+for (d in 1:nrow(email)) {
+	t_d = email[d, 21] - initialtime
+	edge[[d]] = list(a_d = email[d,2], r_d = as.numeric(email[d,-c(1:2, 21)]), t_d = t_d)
+}
+
+uniqtime = unique(email$timepoints)
+# construct time covariates Y
+D = length(edge)
+A = length(Montgomery$manager_gender)
+Q = 7
+Y = array(1, dim = c(D,A,Q))
+for (a in 1:A) {
+	Y[,a,2] = 1* (Montgomery$manager_gender[a]=="Female")
+	Y[,a,3] = 1* (Montgomery$manager_department[a]=="County Manager")
+}
+timeunit = 3600
+Y[1,,6] = rep(as.numeric(wday(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
+Y[1,,7] = rep(pm(as.POSIXct(strptime("01 Mar 2012 00:00:00", "%d %b %Y %H:%M:%S"))), A)
+for (d in 2:D) {
+	index = which(email$timepoints >= uniqtime[which(uniqtime==email$timepoints[d])-1]-7*24*timeunit & email$timepoints < email$timepoints[d])
+	sent = email[index, 2]
+	received = email[index, 3:(2+A)]
+	Y[d, ,4] = tabulate(sent, A) 
+	Y[d, ,5] = colSums(received)
+	Y[d,,6] = rep(as.numeric(wday(as.POSIXct(strptime(email[d-1,1], "%d %b %Y %H:%M:%S"))) %in% c(1, 7)), A)
[…]

### 2018-11-16 code/Montgomery_processing2.R

@@ -100,6 +100,12 @@ prior.eta = list(mean = c(7, rep(0, Q-1)), var = 1*diag(Q))
 Montgomery_infer = Inference(edge, X, Y, 55000, c(20,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
                              proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "lognormal")
 save(Montgomery_infer, file= "/Users/bomin8319/Desktop/Montgomery_infer.RData")
+
+prior.eta = list(mean = c(7, rep(0, Q-1)), var = 4*diag(Q))
+Montgomery_infer4 = Inference(edge, X, Y, 55000, c(20,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
+                             proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "lognormal")
+save(Montgomery_infer, file= "/Users/bomin8319/Desktop/Montgomery_infer.RData")
+
 ############################################################################
 Montgomery_infer2 = Inference(edge, X, Y, 55000, c(20,10,1), 15000, prior.beta, prior.eta, prior.sigma2, initialval = NULL,
                              proposal.var = c(0.00001, 0.001, 0.1), timeunit = 3600, lasttime = email[min(trim-1), 21] - initialtime, timedist = "exponential")

### 2019-01-19 paper/revision1/HEM-reply.tex
revised memo

@@
 \begin{center}
-\textbf{Authors' Responses to Associate Editor}
-\end{center}
-\begin{center}
 \textsl{The Hyperedge Event Model}
 \end{center}
-
+\iffalse
 Thank you for acknowledging our efforts and contributions, and also for your constructive suggestions, which are very helpful to improve the quality of our paper.
@@
 
+\fi
+
 \noindent \textbf{Point-by-point discussion of Reviews and Response to Comments}\\
 
-First, we thank the editor...
+First, we thank the editor for acknowledging our efforts and contributions, and also for your constructive suggestions, which are very helpful to improve the quality of our paper.
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor.. \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor pointed out the lack of detailed and coherent explanation on the model in Section 2, suggesting better definition of variables and improvement on writing.
+We have significantly revised Section 2 by changing the order of subsections along with general rewriting---see E2 to E5 for details.
+\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor identified some unusual notations which are not consistent with the literature.
+Instead of $A$ for nodes (which we got idea from SAOM as the Editor assumed) we now use $V$ for nodes (referring to vertex in network literature), and we also replaced $y$ by $z$ for time-related covariates---which are clearly stated in Section 2.
+We also added detailed definition on the variables and notations, such as the usage of subscripts $i$, $e$, $j$ right before Section 2.1.
+\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} Following the Editor's suggestion, we changed the order of Equation (2.2) and (2.1) as well as their following texts to help readers' understandability.
+Moreover, we agree that the term ``intensity'' could be a confusing term so we revised the sentence withut using the term.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor expressed difficulty in understanding Section 2.2 and 2.3, and suggested further clarification on the variables $\tau$ and $\mu$.
+We moved Fig.
+1 to earlier parts of Section 2 and briefly summarized the entire Section 2, such that the readers can understand Section 2.2 without reading Section 2.3.
+We also further explained the concepts and notations related to timestamp variables, $\tau$ and $\mu$, to avoid any confusion.\\
 
-\noindent  {\bf E5} \grey{\emph{ Some sentences are di¢ cult to understand:
+\noindent  {\bf E5} \grey{\emph{ Some sentences are difficult to understand:
 Page 3: ``we define a probability measure ``MBG'' motivated by the Gibbs measure'' }}\\
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} According to the Editor's comment, we revised the sentence mentioned above and also went through entire draft to revise sentences that were not clearly written before.
+\\
 

### 2019-01-19 paper/revision1/HEM-reply.tex
revised memo

@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor indicated lack of discussion on the relavent literature, including specific comparison between other papers we mentioned (e.g., Perry and Wolfe (2013) and Snijders (1996)).
+We created new section 2.4 ``Basis in existing models" which provides detailed summaries and comparisons about existing models that affected the HEM.
+Furthermore, we added more comments when we introduce/cite the papers with emphasis on what are the motivation and how our model uses differently.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor called attention to a very important point about conditional dependency that we were missing.
+Our out-of-sample algorithm (Algorithm 3) was not correct, and the conditional distribution for missing observations had to be changed as the Editor illustrated.
+We modified our algorithm to consider those dependencies, and Section 4.2 is fully updated based on new conditional distribution and experiment results.
+\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor asked to provide more details on the proposals we used for the Metropolis-Hastings algorithm, thus we added further explanations for both parameters $b$ and $\eta$ in Section 3.1.\\
 
-\noindent  {\bf E9} \grey{\emph{The sampler usePs a blocked Gibbs sampler for the $u_{iej}$.
+\noindent  {\bf E9} \grey{\emph{The sampler uses a blocked Gibbs sampler for the $u_{iej}$.
 Given the constraint that $\sum_j u_{iej} > 0$, this sampler may be rather inefficient in the case where there are many one-to-one interactions (as is the case in the application, where 83\% of the interactions are dyadic).
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor identified some inefficiency issue in our inference algorithm, which we did not fully commented.
+Considering our general need to discuss more about our model's computational complexity, we generated new section 3.2 about ``computaional complexity" and left various comments including the usage of a blocked Gibbs sampler and the mixing of our MCMC sampler.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor suggested more detailed explanation on the computational complexity, especially since our application data is rather small, so (as mentioned in E9) we generated new section 3.2 about ``computaional complexity" and left comments on our computational limitation.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor identified numerous typos, and we properly fixed all those. \\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer dentified numerous typos, and we properly fixed all those.  \\
 
@@
 
-\noindent {\bf R4} \grey{\emph{As already mentioned, the authors focus on the somewhat less explored area of continuous?time relational event models where each edge has its own different time index?instead of considering time?varying models for snap- shots of networks collected on a pre?specified time grid.
+\noindent {\bf R4} \grey{\emph{As already mentioned, the authors focus on the somewhat less explored area of continuous-time relational event models where each edge has its own different time index, instead of considering time-varying models for snap-shots of networks collected on a pre-specified time grid.
 However, the contribution is still within the general class of dynamic network inference.
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer indicated lack of discussion on our model's contribution on the general class of dynamic network literature, specifically in lights of temporal ERGMs and dynamic latent variable models.
+We created new section 2.4 ``Basis in existing models" which provides detailed summaries on our contribution and comparisons with other existing models in wider framework.
+\\
 
@@
 I found this confusing.
-I?d present results in page 7 for generic Gaussian priors.}}\\
+I'd present results in page 7 for generic Gaussian priors.}}\\
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer suggested to use generic Gaussian priors in page 7, instead of introducing the full conditionals assuming uninformative $N(0, \infty)$ priors.
+We addressed this issue by assuming generic Normal priors $N(\mu, \Sigma)$ for both $b$ and $\eta$ and revised our equations and corresponding explanations in page 7.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer suggested more sensitivity analyses on hyperparameter specification.
+We tried two alternative specification of prior distribution---one with half size of current variance and another with double size of current variance--- and summarized the results in Appendix.
+Also, we left some comments on these settings in Section 3.2.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor suggested more detailed explanation on the computational complexity, especially because we had slow mixing of MCMC samples and thus end up with large thinning.
+We generated new section 3.2 about ``computaional complexity" and left comments on our computational limitations, including poor mixing of data augmentation.\\
 
@@
 \noindent {\bf R11} \grey{\emph{In Figure 4c the choice of the logarithmic scale for MdAPE seems to hide a quite poor performance of your model in predicting the timestamps.
-It is true that the log?normal improves over the exponential, but the log?normal boxplot has still a third quartile providing an MdAPE of exp(7.36) which looks quite big.
+It is true that the log?normal improves over the exponential, but the log-normal boxplot has still a third quartile providing an MdAPE of exp(7.36) which looks quite big.
 This is to me a negative result, which should be discussed and addressed in the paper.}}\\

### 2019-02-16 paper/revision1/HEM-reply.tex
Response letter done (need to be reviewed later)

@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor called attention to a very important point about conditional dependency that we were missing.
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} \textcolor{red}{The Editor called attention to a very important point about conditional dependency that we were missing.
 Our out-of-sample algorithm (Algorithm 3) was not correct, and the conditional distribution for missing observations had to be changed as the Editor illustrated.
 We modified our algorithm to consider those dependencies, and Section 4.2 is fully updated based on new conditional distribution and experiment results.
-\\
+}\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor identified some inefficiency issue in our inference algorithm, which we did not fully commented.
-Considering our general need to discuss more about our model's computational complexity, we generated new section 3.2 about ``computaional complexity" and left various comments including the usage of a blocked Gibbs sampler and the mixing of our MCMC sampler.\\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} \textcolor{red}{The Editor identified some inefficiency issue in our inference algorithm, which we did not fully commented.
+Considering our general need to discuss more about our model's computational complexity, we generated new section 3.2 about ``computaional complexity" and left various comments including the usage of a blocked Gibbs sampler and the mixing of our MCMC sampler.}\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} Previously we presented Section 3.2.
+as an effective way to check the validity of our derivation and code using small scale example, which is slightly different from traditional simulation studies that are designed to provide realistic scenario under the model and/or show convergence properties.
+Although we believe that GiR test is a good practice and should be highly recommended, we still admit that Section 3.2.
+does not provide significant amount of additional information on the HEM itself (other than sanity checks) and thus moved this section to Appendix C.
+For convergence properties of the algorithm, we created new section 3.2 about ``computaional complexity" and left some comments on convergence using our application data.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor suggested more detailed explanation on the computational complexity, especially since our application data is rather small, so (as mentioned in E9) we generated new section 3.2 about ``computaional complexity" and left comments on our computational limitation.\\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor suggested more detailed explanation on the computational complexity, especially since our application data is rather small, so (as mentioned in E9) we generated new section 3.2 about ``computaional complexity" and left comments on our computational limitation.
+As the Editor pointed out in E9, we have some inefficiency issue in our inference algorithm which limits the applicability of our model for large scale dataset (with huge number of nodes/events).
+We admitted this limitation in new section 3.2.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor identified numerous typos, and we properly fixed all those. \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor identified numerous typos, and we properly fixed all those. We greatly appreciate the Editor's help on these.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer dentified numerous typos, and we properly fixed all those.  \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer identified numerous typos, and we properly fixed all those. We greatly appreciate the Editor's help on these.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer pointed out multiple unclear parts such as notation issues and sentences that needs more clarification.
+We went through each item and revised our draft as suggested by the reviewer.
+\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer asked the authors to carefully review the bibliography and correct all the misspecifications (e.g., uncapitalized book title, wrong upper/lower cased letters).
+We revisited each bibliography and addressed the existing issues.
+We are very thankful for your comment.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} As suggested by the reviewer (as well as the Editor), we found out the lack of detailed and coherent explanation on the model in Section 2.
+We have significantly revised Section 2 by changing the order of subsections along with the general rewriting, and Figure 1 is also moved to earlier parts when summarizing the HEM at the beginning of Section 2.
+\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer suggested more detailed explanation on the inference scheme such as the type of MH, proposal distribution, acceptance rate, and any recommendation on proposals.
+We not only provided additional explanation on some generic proposal distribution in Section 3.1, but also generated new section 3.2 about ``computaional complexity" for other information on our inference scheme in general.\\
 
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor suggested more detailed explanation on the computational complexity, especially because we had slow mixing of MCMC samples and thus end up with large thinning.
-We generated new section 3.2 about ``computaional complexity" and left comments on our computational limitations, including poor mixing of data augmentation.\\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer suggested more detailed explanation on the computational complexity, especially because we had slow mixing of MCMC samples and thus end up with large thinning.
+In our new section 3.2 about ``computaional complexity", we left comments on our computational limitations, including poor mixing of data augmentation.\\
 
 \noindent {\bf R9} \grey{\emph{Your quantitative assessments are based on 5 nodes in the simulation and 18 nodes in the application.
-These are quite small networks compared to those one would expect in real?world settings (such as those you list in the introduction).
+These are quite small networks compared to those one would expect in real-world settings (such as those you list in the introduction).
 To what extent are your computational methods able to scale to much larger networks?
@@
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} Again, we created a new section 3.2 to discuss more about the HEM's computational complexity.
+Here we acknowledged the HEM's limitation on its applicability to a bigger dataset, by outlining the scalability of the model and computational time.
+We also mentioned some possible ways to improve the model's scalability as a future direction of research.
+\\
 
 \noindent {\bf R10} \grey{\emph{You compare performance in predicting missing senders with random guess 1/18.
-This is a quite naive competitor and I am sure the authors can find much better ones?still relatively simple.}}\\
+This is a quite naive competitor and I am sure the authors can find much better ones still relatively simple.}}\\
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer suggested to consider alternative measure to compare our performance in Section 4.2., instead of our current comparison (i.e., random guess 1/18).
+We came up with the idea to use Dirichlet Multinomial as a baseline to sender prediction, and updated our comparison in Section 4.2.
+with some explanations.
+\\
 
 \noindent {\bf R11} \grey{\emph{In Figure 4c the choice of the logarithmic scale for MdAPE seems to hide a quite poor performance of your model in predicting the timestamps.
-It is true that the log?normal improves over the exponential, but the log-normal boxplot has still a third quartile providing an MdAPE of exp(7.36) which looks quite big.
+It is true that the log-normal improves over the exponential, but the log-normal boxplot has still a third quartile providing an MdAPE of exp(7.36) which looks quite big.
 This is to me a negative result, which should be discussed and addressed in the paper.}}\\
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer misunderstood Figure 4c due to our lack of explanation on using the logarithmic scale.
+We used the logarithmic scale to draw the boxplot (since original scale was highly right-skewed, making the plot less informative), however, we maintained the original scale on the axis.
+As a result, the third quartile provides an MdAPE of 7.36 (not exp(7.36)).
+We revised the draft such that the readers are not confused with log-scale.
+\\
 
-\noindent {\bf R12} \grey{\emph{Based on your comments in the paper you are interpreting the posterior expectations of exp($\eta_6$) and exp($\eta_7$)--i.e.
-E[exp($\eta_6$) | data] and E[exp($\eta_7$) | data].
-However you seem to compute this as exp[E(exp($\eta_6$) | data)] = exp(1.552) and exp[E(exp($\eta_7$) | data)] = exp(0.980).
+\noindent {\bf R12} \grey{\emph{Based on your comments in the paper you are interpreting the posterior expectations of $exp(\eta_6)$ and $exp(\eta_7)$--i.e.
+$E[exp(\eta_6)| data]$ and $E[exp(\eta_7) |data]$.
+However you seem to compute this as $exp[E(exp(\eta_6) | data)]$ = exp(1.552) and $exp[E(exp(\eta_7) |data)]$ = exp(0.980).
 By Jensen inequality this is wrong.}}\\
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer commented on our misinterpretation of coefficients.
+We changed the way we summarize the estimated value of $\eta_6$ and $\eta_6$ (as we did with other $\eta$'s) so that we no longer provide wrong interpretation.\\
 
-\noindent {\bf R13} \grey{\emph{It is also not correct to claim that the $e^{th}$ email is expected to take E[exp($\eta$) | data] longer compared to their counterpart.
-The term longer seems to refer to an additive effect on the event timing, which is not the case here since you assume a log?normal for the event timing and hence the effect is on the scale of the timing and not on the location?note that, if $X \sim \text{log-normal}(\mu, \sigma^2)$, then $E(X) = exp(\mu + \sigma^2/2)$.
+\noindent {\bf R13} \grey{\emph{It is also not correct to claim that the $e^{th}$ email is expected to take $E[exp(\eta) | data]$ longer compared to their counterpart.
+The term longer seems to refer to an additive effect on the event timing, which is not the case here since you assume a log-normal for the event timing and hence the effect is on the scale of the timing and not on the location---note that, if $X \sim \text{log-normal}(\mu, \sigma^2)$, then $E(X) = exp(\mu + \sigma^2/2)$.
 The authors should be more careful in the interpretations on the original time scale, or, more conservatively, they could simply comment on the effects on the log-time (as done immediately after).}}\\
 
-\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer... \\
+\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer also pointed out additional mistake when we provided the interpretation of coefficients on the original time scale.
+As suggested, we simply commented on the effects on the log-time (as done immediately after) instead of using the original time scale.\\
 
